### 2025-05-09 paper/paper_draft.qmd
Add quarto paper writing and functions required for processing

---
title: Future climate resilience of the Great Barrier Reef
author:
  - name: Benjamin Grier
    email: grierben777@gmail.com
    affiliations: 
        - id: AIMS
          name: Australian Institute of Marine Science
          address: Cape Cleveland Rd
          state: QLD
    attributes:
        corresponding: true
  - name: Takuya Iwanaga
    email: t.iwanaga@aims.gov.au
    affiliations:
        - id: AIMS
          name: Australian Institute of Marine Science
          address: Cape Cleveland Rd
          city: Cape Cleveland
          state: QLD
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - Coral reef
  - Climate change
  - Ecosystem resilience
  - Reef depth
  - Reef connectivity
date: last-modified
format:
  elsevier-docx:
    journal:
      name: Journal Name
      formatting: preprint
      cite-style: authoryear
bibliography: references.bib
engine: julia
crossref:
    custom:
    - kind: float
      reference-prefix: SFigure
      key: sfig
---

```{julia}
#| include: false

cd("../src")
include("../src/common.jl")

ecs_width = fig_sizes["ecs_width"]
timeseries_width = fig_sizes["timeseries_width"]
violin_width = fig_sizes["violin_width"]
```

# Introduction

Climate change is impacting species survival, persistence and ecosystem functioning globally, including coral. Coral reefs are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading ([@foster2021]; [@gattuso2014]). Mass bleaching and mortality events linked to climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts (Arif et al. 2022; Wild et al. 2011). Climate impacts on coral reefs are, and will continue to, decrease the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling (Foster & Attrill 2021; Williams & Graham 2019) as well as ecosystem services such as food, protection, tourism and Indigenous cultural value (Eddy et al. 2021; Stoeckl et al. 2021). We aim to assess the impacts of possible climate futures and identify the characteristics of resilient reefs using the latest generation of larval connectivity research with scenario-based population modelling for the Great Barrier Reef ecosystem.

The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of thousands of individual reefs. They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes (Grimaldi et al. 2022). Severe declines in coral cover are projected due to compounding impacts such as ocean warming and acidification, intensification of Tropical Cyclones, and Crown of Thorns Starfish outbreaks (De’ath et al. 2012; Fox-Kemper et al. 2021; Seneviratne et al. 2021; Sweatman et al. 2011; Wolff et al. 2018). Ominously, the 2023-24 Summer mass bleaching event (Cantin et al. 2024) may be signalling a shift towards this reef future.

Environmental abiotic factors influence how reefs will experience climate change pressures, including the spatio-temporal patterns of thermal stress itself, and indirect factors that influence the stress experienced by corals. Environmental factors such as tropical cyclones and wind driven mixing (Lin et al. 2023; McClanahan et al. 2005); currents (Grimaldi et al. 2022) and depth (Álvarez-Noriega et al. 2018; Baird et al. 2018; Smith et al. 2014) can decrease the magnitude of thermal stress corals experience. On the other hand, high light intensity and nutrient levels in the benthic zone can increase coral bleaching (DeCarlo et al. 2020; Higuchi et al. 2015). These environmental factors influence the resilience of reefs to climate change pressures in combination with related biological factors such as larval connectivity and thermal tolerance.

Connectivity in systems such as the GBR is an important contributor to system resilience, as strong connections are required to repopulate locations after disturbance, and drive adaptation to climate pressures (Angeler et al. 2023; Elmhirst et al. 2009; Hock et al. 2017). When populations that are strong larval suppliers to external reefs are impacted by disturbances, increased adult coral mortality will cause decreased outgoing larvae in the following years. Weaker larval connections then slow the recovery of the externally connected locations (Figueiredo et al. 2022; Hock et al. 2017; Munday et al. 2009). Populations with greater strength and number of outgoing than incoming larval connections - herein referred to as larval sources - have lower resilience to pressures than populations with greater incoming than outgoing larval flows - referred to as larval sinks - as larval source populations lack external sources of larvae that are important in contributing to reef recovery and recruitment of juveniles after disturbances to existing populations (Ani et al. 2024; Hock et al. 2017). Larval source populations are an important component of overall reef resilience as they can contribute larvae to recovering populations at other locations (Hock et al. 2017; Thomas et al. 2015). Connectivity will be altered by future climate change impacts such as population fragmentation, increasing larval mortality, and changes to coastal hydrodynamics (Figueiredo et al. 2022; Munday et al. 2009), and influences the biology of surrounding reef populations.

Many additional biological factors including coral size (Brandt 2009), taxa (Álvarez-Noriega et al. 2018; McClanahan et al. 2005), and acclimation and inherited thermal tolerance (Humanes et al. 2022; Lachs et al. 2024), influence the outcome of high coral heat stress. It has been shown that corals have the adaptive capacity to develop thermal tolerance levels capable of delaying climate impacts under low emissions scenarios (Bairos-Novak et al. 2021; Humanes et al. 2022).

Incorporating the latest advancements in whole ecosystem larval connectivity modelling and research on the mechanisms behind coral bleaching and thermal adaptation responses into coral population modelling allows us to investigate how these abiotic and biotic factors interact and will influence coral climate change resilience into the future. Improvements in coral reef climate response modelling, including sampling from a range of possible climate futures, allow for fine-scale timeseries analyses of uncertain climate change and ecological scenarios (Bode et al. 2017; Chollett et al. 2022; Donner et al. 2018; Klein et al. 2024; Uusitalo et al. 2015).

It is hypothesised that sink reefs are more likely to be resilient under climate change, compared to source reefs, due to greater influx of coral recruits post disturbance. It is hypothesised that reefs with greater depths are more likely to be resilient under future thermal stress, compared to reefs at shallow depths, as they benefit from thermal refugia. It is hypothesised that reef cover will decline by greater magnitude as the Equilibrium Climate Sensitivity (ECS) of each Global Climate Model (GCM) increases.

# Methods

## Environmental modelling context

The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas, as used in ReefMod-GBR (Bozec et al. 2022). Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future thermal stress at each reef location. Five Global Climate Models (GCMs) (EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6) were selected for this study. Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great Barrier Reef were obtained from the HighResCoralStress database (Dixon et al. 2023, 2022). Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology (Liu et al. 2017; Skirving et al. 2020). These GCMs were selected from available GCMs downscaled by Dixon et al. (2023) based on evaluation by Grose et al. (2023), which found high correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms in these GCMs. Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming caused by a doubling of carbon dioxide above its pre-industrial concentration (Forster et al. 2021). The four GCMs span a range of ECS values within the IPCC assessed likely range, and GCM development families, allowing for a range of possible climate futures to be explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs; Grose et al. 2023; Shepherd et al. 2018). The following analyses are performed using each GCM separately. SSP 2-4.5 is used as a plausible emission pathway under current emission trajectories, with similar atmospheric CO2 levels remaining until 2050 (Hausfather & Peters 2020; IPCC 2023).

![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values). The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al., 2021).](/../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs width=`{julia} ecs_width`}

## Coral reef ecosystem model - ADRIA x CoralBlox

CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time (CoralBlox citation). This model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony. Environmental disturbances and reproduction are not directly considered within CoralBlox. Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform (ADRIA citation). Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.

CoralBlox uses user-defined size classes that influence size-dependent growth and mortality rates, through which the coral colonies progress as they grow in diameter. Within ADRIA, we define the distributions of these parameters, and the size classes based on ecological monitoring data from the [EcoRRAP program](https://gbrrestoration.org/program/ecorrap/).

Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes (1996). Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling). Viable larvae settle at a reef location and are incorporated into the model as the smallest size class, but are not directly impacted by modelled bleaching mortality as it is assumed the high background mortality of juveniles includes thermal stress.

### Factors influencing bleaching mortality

We track the thermal tolerance of each functional group and size class as a truncated normal distribution that is updated in each timestep following growth and recruitment. This distribution determines that proportion of the population on a reef that is susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value). Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al. (2021) and unpublished data from Hughes et al. (2018). Tropical cyclones and wave impacts to reefs are not included in this investigation. We scale coral bleaching impacts by a coefficient determined by the median depth of each reef location, following Baird et al. (2018), reducing the proportion of coral colonies on a reef impacted by high heat stress as depth increases. Median depths for each reef location have been extracted from satellite derived bathymetry data for the Great Barrier Reef (GBRMPA 2020). Due to varying degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs with less than 5% coverage of valid bathymetry data have been removed from this investigation. Furthermore, reefs that are not allocated to a GBRMPA management area or bioregion have been removed from the investigation, as well as reefs with relative coral cover values greater than five.

### Connectivity modelling

\*\* need information on GBR1 connectivity used \*\*

## Timeseries analysis

### Reef health metrics

ADRIA output absolute coral cover was used to calculate relative coral cover (relative to initial cover), a reef’s absolute coral cover at each timestep divided by initial coral cover. Initial coral cover is consistent throughout all simulated and GCM scenarios. To limit the influence of reefs with very low initial cover on the results, reefs with future total cover levels that exceed five times their initial cover level were removed from clustering and further analyses. The proportion of each functional group occupying the reef (taxa evenness) was also investigated as a metric for timeseries analysis, but was found to not sufficiently capture the declining condition of reefs suffering from very low absolute coral cover.

### Timeseries clustering

Timeseries analysis is performed by first grouping reefs into three different scales, GBRMPA reefal bioregion, GBRMPA management area and GBR-wide, to investigate the consistency of cluster identification. To identify groups of reefs at each analysis scale that are resilient, intermediate and non-resilient we clustered reef relative coral cover timeseries into three clusters at each scale. To quantify the behaviour of timeseries and identify timeseries that behave similarly we calculate the complexity-invariant distance (CID) between each timeseries. The complexity-invariant distance refers to the Euclidean distance between two timeseries multiplied (corrected) by the ratio of the complexities of the timeseries (Batista et al. 2014). These values create a distance matrix of n \* n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm (Steinmann et al. 2020).

### Further analyses

Reefs in each cluster are compared to identify characteristics that differ between low, medium and high coral cover clusters. These characteristics include reef median depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation between total coral cover and inversed DHW timeseries, proportion of coral habitable area occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and total strength of larval connections between reefs. To analyse the DHW - tolerance levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa \* reef \* scenario matrix. The mean timeseries was calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then used to calculate an overall mean DHW – tolerance value for each reef under each GCM.

# Results

## Global Climate Model future trajectories

Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’ coral cover and contextual analysis factors, thus visual further comparisons of these clusters for each analysis factor are only shown for ACCESS-ESM1-5 GCM (intermediate ECS scenario). Results for the additional GCMs are displayed in the supplementary material. However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus relative coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-trajectories).

NorESM2-MM has the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline dynamics up to 2074 under this possible climate future. While recovery phases are predominantly seen in the ‘high’ cover cluster, the ‘medium’ cluster, and to a lesser degree the ‘low’ cluster, also exhibit periods of increasing relative coral cover up to 2045. Under NorESM2-MM GCM the Far Northern management area does not see relative coral cover maintenance as high as the three remaining management regions. Under the second lowest ECS projection (GFDL-CM4, 2.9°C) all clusters in each management area exhibit largely declining future trajectories with periods of recovery from 2030 to 2040. ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which results in intermediate levels of coral cover maintenance (between those of lower and higher ECS GCMs). In all management areas reefs in the high cluster are able to maintain relative coral cover levels to 2050 under ACCESS-ESM1-5. Under ACCESS-CM2 (4.72°C) and EC-Earth3-Veg (4.31°C) GCMs relative cover trajectories are largely declining, with the exception of ‘high/medium’ clusters in the Cairns-Cooktown management area under EC-Earth3-Veg that display prolonged relative cover maintenance.

![Reef relative coral cover timeseries clustered within each management area, for each GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals. Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#fig-gcm-trajectories width=`{julia} timeseries_width`}

Across the five GCMs, 50% (1812) of reefs, at management region scale, remain in the same ‘low, medium, high’ cluster assignment. 1757 Reefs (49%) that changed clusters by one level across the GCMs (e.g. a reef is assigned ‘low’ and ‘medium’ in different GCMs), while 46 (1%) reefs changed clusters by two levels across the GCMs (e.g. a reef is assigned ‘low’ and ‘high’ in different GCMs).

## Bioregion scale clustering

Within bioregions timeseries clustering analysis was able to identify three clusters of relative cover timeseries. Across many bioregions timeseries clustering identified a ‘low’ cluster containing reefs that suffer larger declines and generally have lower levels of relative coral cover than the other clusters, a ‘medium’ cluster with intermediate levels of relative coral cover, and a ‘high’ cluster with cover recovery that persists to 2050 in many bioregions (@fig-access-esm1-5-bioregion-timeseries).

![Reef relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#fig-access-esm1-5-bioregion-timeseries width=`{julia} timeseries_width`}

In many bioregions, median reef depth decreases as cluster relative coral cover decreases, with reefs within the ‘high’ cluster commonly having the greatest median reef depths within the bioregion (@fig-access-esm1-5-bioregion-depth).

![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth width=`{julia} violin_width`}

Correlation between reef total coral cover and reef DHW timeseries decreases as cluster relative coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total cover – DHW timeseries correlation levels (@fig-access-esm1-5-bioregion-dhwcor).

![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median cover – DHW correlation level for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwcor width=`{julia} violin_width`}

Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@fig-access-esm1-5-bioregion-dhwmean).

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW level for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}

In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially lower mean thermal tolerance levels compared to reefs in other clusters. However, many bioregions do not show strong differences in thermal tolerance levels (@fig-access-esm1-5-bioregion-dhwtol).

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}

In many bioregions reefs with high relative coral cover levels (‘high’ cluster) have the lowest initial proportions of habitable area occupied by corals, while reefs in the ‘low’ cluster often have the highest initial proportions of coral habitable area occupied by corals (@fig-access-esm1-5-bioregion-initialproportion).

![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median proportion of habitable area occupied for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#fig-access-esm1-5-bioregion-initialproportion width=`{julia} violin_width`}

Across most bioregions there are not consistent differences between clusters in connectivity metrics such as source-to-sink connectivity ratio (@fig-access-esm1-5-bioregion-logsosi) and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).

![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#fig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}

## Management area scale clustering
Within the four management areas, timeseries clustering analysis identified three clusters of reefs using relative coral cover timeseries. These clusters form groups of reefs with ‘low, medium and high’ relative coral cover, categorised by their median coral cover between 2030 and 2040. The ‘high’ cover cluster of reefs contains reefs that have continuing recovery of corals throughout the future climate scenario. The medium and low clusters contain many reefs that decrease to half their initial coral cover levels and largely do not display the levels of recurring recovery that reefs in high clusters experience (@fig-access-esm1-5-manarea-timeseries).

![Reef relative coral cover timeseries clustered within each management area. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}

Within each bioregion reef median depth level increases with increasing reef relative coral cover. Reefs in the low cluster have the lowest median depth levels, while reefs in the high cluster have the highest median depth levels within each management area (@fig-access-esm1-5-manarea-depth).

![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}

Correlation between reef total coral cover and the DHW levels they experience throughout the time period increases as coral relative cover increases, with reefs in the high cluster having the highest median total cover – DHW correlation (@fig-access-esm1-5-manarea-dhwcor).

![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_cover_cor_management_area_violin.png){#fig-access-esm1-5-manarea-dhwcor width=`{julia} violin_width`}

However, reefs with higher relative coral cover levels do not experience lower mean DHW levels throughout their timeseries. There are no consistent substantial differences in mean DHW levels across the identified timeseries clusters (@fig-access-esm1-5-manarea-dhwmean).

![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/mean_dhw_management_area_violin.png){#fig-access-esm1-5-manarea-dhwmean width=`{julia} violin_width`}

Within the Far Northern management area ‘low’ cluster reefs have substantially lower median DHW – tolerance levels than ‘medium’ and ‘high’ clusters, while there are no substantial differences in DHW – tolerance between clusters in other management areas (@fig-access-esm1-5-manarea-dhwtol).

![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median DHW – tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_tolerance_management_area_violin.png){#fig-access-esm1-5-manarea-dhwtol width=`{julia} violin_width`}

Like clusters identified within bioregions, within the Mackay-Capricorn, Far Northern and Cairns-Cooktown management areas the initial proportion of coral-habitable area initially occupied by corals decreases in clusters with higher relative coral cover (@fig-access-esm1-5-manarea-initialproportion).

![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/initial_proportion_management_area_violin.png){#fig-access-esm1-5-manarea-initialproportion width=`{julia} violin_width`}

At management area analysis scales, there are not consistent substantial differences in source – to – sink ratios (@fig-access-esm1-5-manarea-logsosi) and total connectivity strength (@sfig-access-esm1-5-manarea-totalconnectivity).

![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/so_to_si_management_area_violin.png){#fig-access-esm1-5-manarea-logsosi width=`{julia} violin_width`}

## Great Barrier Reef scale clustering
Timeseries clustering identified three clusters in reef relative cover timeseries for the whole GBR scale. A ‘low’ cluster of reefs with little recovery following initial declines, a medium cluster of reefs with median relative cover below 0.5 post 2028, and a high cluster of reefs with median relative cover above 0.5 until 2050 (@fig-access-esm1-5-gbr-timeseries).

![Reef relative coral cover timeseries clustered across the Great Barrier Reef. The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040. The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040. The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040. Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}

The clusters identified with timeseries clustering at the GBR scale show similar patterns to clusters identified at bioregion and management area scales. Reef depth (@fig-access-esm1-5-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels. There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol) levels of reefs. Similarly, there are no substantial differences between clusters in connectivity metrics source – to – sink ratio and total connectivity strength (@sfig-access-esm1-5-gbr-logsosi, @sfig-access-esm1-5-gbr-totalconnectivity).

![Median depth for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}

# Discussion
Timeseries analysis has been used to identify three groups of reefs with similar declining (low), recovering (high), and intermediate (medium) coral cover trajectories throughout future scenarios. Throughout all analysis scales, reefs in high cover clusters exhibit spans of recovery up to 2050, while low and medium clusters commonly remain at levels below half their initial cover from 2030. Furthermore, at all analysis scales reef clusters show similar patterns in their reef characteristics such as depth and proportion of habitable area initially occupied.

A key factor that influences the relative coral cover values on a reef is the initial total coral cover used to calculate the metric. This is seen where low and medium reefs have higher proportions of their coral-habitable area occupied by corals initially, while some high-cluster reefs exhibit absolute coral cover levels greater than their initial coral cover, leading to future relative cover values greater than one.

Reefs in different clusters largely do not differ in mean modelled DHW levels experienced, and exhibit overall similar DHW timeseries. While these reefs experience similar magnitude DHWs based on SST, the proportion of the reef’s coral population impacted by heat stress events depends on the depth of the reef. Analysis from Baird et al. (2018) is used to calculate the degree of protection provided to a reef based on the median depth. Our results suggest that within shallow reef ecosystems (depth < 30m), depth contributes greatly to reef resilience and the ability of the reef to recover following heat stress. While similar findings have been demonstrated in the eastern Pacific (Smith et al. 2014), depth refugia analyses have often focussed on the potential of mesophotic reefs (> 30m deep) as thermal refugia (Bongaerts et al. 2010; Holstein et al. 2015; Semmler et al. 2017). In contrast, Venegas et al. (2019) found no association between depth and the alleviation of heat stress across a range of shallow reefs in the Pacific. The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels. Reefs in low and medium clusters have lower levels of cover – DHW correlation than those in high clusters, due to their initial sharp declines in coral cover combined with low depth – refugia in the face of persistently high thermal stress these reefs do not recover post 2030, leaving little ability to decline further in periods of high thermal stress and recover in periods of low thermal stress.

Overall, these findings support the hypothesis that reefs at greater depths will experience refugia benefits and more prolonged resilience under climate change compared to shallower reefs. A caveat to these findings is the quality of the bathymetry data used to calculate depth refugia benefits in ADRIA. This data (GBRMPA 2020) is derived from satellite imagery and is limited in its alignment with the established GBRMPA reef outlines used in the investigation to characterise reef locations. As a result, 842 reefs (22% of the 3806) were removed from the analyses before depth comparisons due to having less than 5% coverage of depth data.

Current reef restoration and intervention-investigation efforts on the Great Barrier Reef, such as deployment of coral seeding and fragment devices target reefs with suitable restoration sites in the 1-10m depth range (Howlett et al. 2021; Randall et al. 2021; Whitman et al. 2024). One of the main depth constraints is being able to visually identify the target site from the surface for deployment and ongoing monitoring, in combination with factors such as deployment method and tourism return value. Our results suggest that many reefs with a median depth in this range are likely to fall into the low and medium clusters, suffering large future declines in reef health under climate change and possibly limiting the potential of interventions to deliver recovery in these locations. Reef intervention planning is a complex and challenging decision making process (Anthony et al. 2020), and our results suggest that deployment site depth is likely an important factor to consider when assessing the long-term resilience of reef sites.

Overall, our findings do not suggest that resilient reefs in ‘high’ cover clusters have greater thermal tolerance than reefs in lower coral cover clusters. This is in contrast with literature suggesting corals have the capacity to adapt to increasing climate change pressures (Humanes et al. 2022; Lachs et al. 2024), including the investigation by Bairos-Novak et al. (2021) that revealed high heritability of bleaching and survival response traits used to inform the distributions of thermal tolerance traits used in this investigation. The lack of influence of thermal tolerance on reef outcomes is likely due to reef being impacted by overall similar levels of thermal stress, combined with the greater importance of factors such as reef depth and initial coral cover.

It has been suggested that a primary facet of reef resilience is the degree of larval connectivity between reefs and the supply of recruits that a reef receives following disturbance (Hock et al. 2017). It was expected that resilient reefs would have greater incoming than outgoing larval connectivity to promote recovery in years following thermal stress, while non-resilient reefs would have greater outgoing than incoming connectivity inhibiting recruitment of corals ability post thermal stress. In contrast, our results suggest that there are few differences between resilient and non-resilient reefs in connectivity metrics such as the ratio of outgoing to incoming larval connectivity and total connectivity strength. Hock et al. (2017) used larval connectivity modelling to identify resilient reefs that may supply up to 47% of the wider Great Barrier Reef ecosystem with larvae following disturbance. A criticism of this approach (Bode et al. 2018) is that results obtained are highly sensitive to the biophysical dispersal model used, limiting the application of specific identified reefs. Reef depth was not considered in these investigations of reef network resilience. These investigations were performed using prior generations of larval connectivity models parameterised for 2008-2013 (Hock et al. 2017) and 1996-2002 (Bode et al. 2018) time periods respectively. Using updated 1km resolution larval connectivity across the whole GBR, our results suggest that larval connectivity alone is not as important for reef resilience and recovery as environmental refugia from thermal stress such as environmental refugia factors such as depth.

Five different GCMs were included in analyses to capture uncertainty in climate system responses to increasing atmospheric carbon dioxide levels. The large differences in relative cover timeseries seen across the GCMs suggest that it is important to consider this uncertainty in analyses of biological climate change responses. This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model climate change responses using a range of climate models separately (Shepherd et al. 2018). However, the patterns identified between low, medium and high clusters of reefs suggest that the importance of depth refugia is consistent across scenarios. Similarly, at the management area scale, only 1% of reefs were assigned a ‘low’ and ‘high’ cluster in different GCMs, suggesting that intrinsic reef properties can prevent high cover resilient reefs from crashing under a different future climate scenario.

# Conclusions
Overall, our results suggest that when modelled as part of a large and complex ecosystem, reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in support of depth as a form of refugia for shallow reefs. While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts (Anthony et al. 2020; Hock et al. 2017), our results suggest that resilient reefs do not have greater incoming or total connectivity to contribute to their resilience. Instead, we suggest that depth, and likely other environmental thermal refugia mechanisms contribute greater to overall reef resilience and recovery. Further investigation could utilise the scenario modelling and dynamic intervention capabilities of the ADRIA platform to explore the effectiveness of prioritising reef depth compared to larval connectivity in reef intervention decision making.

# References

::: {#refs}
:::

# Supplementary Material
## ACCESS-ESM1-5

![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion. Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}

![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area. Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/log_total_strength_management_area_violin.png){#sfig-access-esm1-5-manarea-totalconnectivity width=`{julia} violin_width`}

![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median total cover – DHW correlation value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwcor width=`{julia} violin_width`}

![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median occupied proportion value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/initial_proportion_gbr_violin.png){#sfig-access-esm1-5-gbr-initialproportion width=`{julia} violin_width`}

![Mean DHW for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median DHW value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/mean_dhw_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwmean width=`{julia} violin_width`}

![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median DHW - tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwtol width=`{julia} violin_width`}

![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef. Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels..](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/so_to_si_gbr_violin.png){#sfig-access-esm1-5-gbr-logsosi width=`{julia} violin_width`}

![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040. ‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040. ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040. Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}

## ACCESS-CM2

## EC-Earth3-Veg

## GFDL-ESM4

## NorESM2-MM

### 2025-05-09 src/ADRIA/HighResCoralStress/1_GCM_model_runs.jl

@@ -1,5 +1,8 @@
 using Revise, Infiltrator
 using YAXArrays
+
+change_ADRIA_debug(false) # Ensure ADRIA debug mode is set to false to allow parallel processing.
+
 using ADRIA
 
 GBR_domain_path = "../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/"
@@ -12,14 +15,14 @@ context_layers = gbr_dom.loc_data
 
 for (g, GCM) in enumerate(gcms)
 
-# generate 4096 sample scenarios from counterfactual scenarios
-scens = ADRIA.sample_cf(gbr_dom, 4096)
+    # generate 4096 sample scenarios from counterfactual scenarios
+    scens = ADRIA.sample_cf(gbr_dom, 4096)
 
-# change dhw scenarios to GFDL-CM4
-scens[!, :dhw_scenario] .= g
+    # change dhw scenarios to GFDL-CM4
+    scens[!, :dhw_scenario] .= g
 
-# Run sampled scenarios for a given RCP
-rs = ADRIA.run_scenarios(gbr_dom, scens, "45")
+    # Run sampled scenarios for a given RCP
+    rs = ADRIA.run_scenarios(gbr_dom, scens, "45")
 
-# Rename result store directory according to GCM that is chosen
+    # Rename result store directory according to GCM that is chosen
 end

### 2025-05-09 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -8,11 +8,13 @@ using DataFrames, Statistics, YAXArrays
 
 using GLMakie, GeoMakie, GraphMakie
 
-using ADRIA
-
 import GeoDataFrames as GDF
 
 import GeoFormatTypes as GFT
+
+change_ADRIA_debug(true) # Change ADRIA debug mode to true to extract DHW tolerance data from runs
+
+using ADRIA
 
 include("../../common.jl")
 
@@ -143,7 +145,16 @@ for (i_gcm, GCM) in enumerate(dhw_scenarios.dhw.properties["members"])
 
     end
 
-    context_layers[!, "$(GCM)_dhw_cover_cor"] = dhw_cover_cor   
+    context_layers[!, "$(GCM)_dhw_cover_cor"] = dhw_cover_cor
+
+    # 4. Re-run 5 scenarios for each GCM and extract mean DHW tolerance from timeseries
+    scens = rs.inputs[1:4, Not(318)] # Only use 1st 5 scenarios for speed and remove RCP variable in inputs
+    scens.wave_scenario .= 1.0
+    rs_dhw = ADRIA.run_scenarios(gbr_dom, scens, "45")
+    dhw_tol_log = Float64.(mapslices(median, rs_dhw.coral_dhw_tol_log, dims = [:scenarios, :species]))
+    dhw_tol_mean = dropdims(mean(dhw_tol_log[10:end, :], dims = 1), dims = 1).data
+    
+    context_layers[!, "$(GCM)_mean_DHW_tol"] = dhw_tol_mean
 end
 
 # 5. Calculate the number of reefs in each bioregion
@@ -151,6 +162,13 @@ context_layers.bioregion_count .= 1
 for reef in eachrow(context_layers)
     reef.bioregion_count = count(context_layers.bioregion .== [reef.bioregion])
 end
+
+# 6. Add average latitude for each bioregion
+bioregion_average_latitude = combine(groupby(context_layers, :bioregion)) do sdf
+    return average_latitude = mean([ArchGDAL.gety(ArchGDAL.centroid(geom), 0) for geom in sdf.geometry])
+end
+rename!(bioregion_average_latitude, :x1 => :bioregion_average_latitude)
+context_layers = leftjoin(context_layers, bioregion_average_latitude, on=:bioregion)
 
 # Format columns for writing to geopackage
 context_layers.income_strength = Float64.(context_layers.income_strength)
[…]

### 2025-05-09 src/ADRIA/HighResCoralStress/4_analysis_and_plots_clustering.jl

@@ -8,7 +8,7 @@ using CairoMakie
 using ADRIA
 
 include("../../common.jl")
-includet("../../plotting_functions.jl")
+include("../../plotting_functions.jl")
 
 CairoMakie.activate!()
 
@@ -22,6 +22,8 @@ context_layers.log_so_to_si = log10.(context_layers.so_to_si)
 context_layers.log_total_strength = log10.(context_layers.total_strength)
 
 gbr_dom = ADRIA.load_domain("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/", "45")
+
+
 
 for (i_gcm, GCM) in enumerate(GCMs)
     # Select GCM and load relevant results
@@ -58,8 +60,8 @@ man_area_gcm_cluster_cols = [Symbol("$(GCM)_management_area_clusters") for GCM i
 bioregion_gcm_cluster_cols = [Symbol("$(GCM)_bioregion_clusters") for GCM in GCMs]
 gbr_gcm_cluster_cols = [Symbol("$(GCM)_gbr_clusters") for GCM in GCMs]
 analysis_layers_long = stack(
-    context_layers[:, [:UNIQUE_ID, :management_area, gcm_cluster_cols...]], 
-    gcm_cluster_cols
+    context_layers[:, [:UNIQUE_ID, :management_area, gbr_gcm_cluster_cols...]], 
+    gbr_gcm_cluster_cols
 )
 analysis_layers_long.GCM = [first(split(name, "_")) for name in analysis_layers_long.variable]
 
@@ -75,7 +77,11 @@ GCM_comparison_plot = grouped_GCM_cluster_timeseries_plots(
     [:management_area, :GCM],
     1:50
 )
-save("../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png", GCM_comparison_plot)
+save(
+    "../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png", 
+    GCM_comparison_plot,
+    px_per_unit = dpi
+)
 
 analysis_layers = context_layers[context_layers.UNIQUE_ID .∈ [unique(analysis_layers_long.UNIQUE_ID)], :]
 reefs_with_clusters = (
@@ -94,40 +100,40 @@ consistent_reefs = (
 )
 sum(consistent_reefs) / length(consistent_reefs)
 
-fig = Figure()
-ax = Axis(
-    fig[1,1],
[…]

### 2025-05-09 src/common.jl

@@ -30,6 +30,7 @@ import GeoDataFrames as GDF
 import GeoFormatTypes as GFT
 import ArchGDAL as AG
 import GeoInterface as GI
+using ADRIA
 
 include("plotting_functions.jl")
 include("ADRIA_DataCube_functions.jl")
@@ -409,20 +410,24 @@ end
 
 """
     grouping_counts(
-        grouping_col::Symbol, 
+        grouping_col::Union{Symbol, String}, 
         dataset::DataFrame, 
         clustering_col::Union{Symbol, String}, 
-        n_clusters::Int64
-    )
+        n_clusters::Int64,
+        n_reefs::Int64
+    )::Vector{String}
 
 Calculate the number of clusters within each grouping. If the number of clusters is less
-than expected then a group is returned in `removed_groups`.
+than expected (`n_clusters`) then a group is returned in `removed_groups`. Calculate the number of reefs
+within each cluster of each group. If the number of reefs is less than desired (`n_reefs`) then
+a group is returned in `removed_groups`.
 
 # Arguments
 - `grouping_col` : Name of column containing group assignments.
 - `dataset` : Dataframe containing `grouping_col` and `clustering_col` information.
 - `clustering_col` : Name of column containing clustered assignments.
 - `n_clusters` : Desired minimum number of unique clusters within each group.
+- `n_reefs` : Desired minimum number of reefs within each cluster of each group.
 
 # Examples
 ```
@@ -430,7 +435,8 @@ groups_too_few_clusters = grouping_counts(
     :bioregion,
     context_layers,
     :bioregion_timeseries_clusters,
-    3
+    3,
+    5
 )
 ```
 """
@@ -438,14 +444,18 @@ function grouping_counts(
     grouping_col::Union{Symbol, String}, 
     dataset::DataFrame, 
     clustering_col::Union{Symbol, String}, 
-    n_clusters::Int64
-)
-    reef_counts = combine(groupby(dataset, grouping_col)) do sdf
+    n_clusters::Int64,
+    n_reefs::Int64
+)::Vector{String}
+    reef_counts = combine(groupby(dataset, [String(grouping_col), clustering_col]), nrow => :nrow)
+    groups_few_reefs = unique(reef_counts[reef_counts.nrow .< n_reefs, grouping_col])
+
+    cluster_counts = combine(groupby(dataset, grouping_col)) do sdf
[…]

### 2025-05-09 src/plotting_functions.jl

@@ -5,6 +5,22 @@ File includes the plotting functions for ADRIA-reef-indicators analysis.
 using Printf
 using Colors
 using Random
+using TOML
+
+config = TOML.parsefile("config.toml")
+
+# Extract figure sizes and convert to pixel measurement
+fig_sizes = config["fig_formats_cm"]
+cm = 37.7952755906 # Size of 1cm in pixels
+map!(x -> x*cm, values(fig_sizes))
+
+# Extract figure fontsize and convert to pixel measurement
+pt = 1.33 # size of 1 pt in pixels
+fontsize = config["fig_fontsize"]
+fontsize = fontsize["fontsize"] * pt
+
+inch = 96 # size of 1 inch in pixels
+dpi = 300 / inch
 
 function _convert_plottable(gdf::Union{DataFrame,DataFrameRow}, geom_col::Symbol)
     local plottable
@@ -292,9 +308,9 @@ function skipmissing_median(x)
     return new_median
 end
 
-function label_lines(label)
-    if length(label) > 25
-        label_new = replace(label, r"(.{25} )" => s"\1\n")
+function label_lines(label; l_length=25)
+    if length(label) > l_length
+        label_new = replace(label, r"(.{l_length} )" => s"\1\n")
 
         return label_new
     end
@@ -351,12 +367,12 @@ function _setup_grouped_figure(dataframe, bellwether_reefs_col, grouping; x_fig_
     return fig, gdf, plot_layout, colors, categories
 end
 
-function _setup_grouped_figure(dataframe, grouping; x_fig_size=2130, y_fig_size=1500, marker=LineElement, order=:management_area, multi_axis=true)
+function _setup_grouped_figure(dataframe, grouping; x_fig_size=2130, y_fig_size=1500, marker=LineElement, order=:bioregion_average_latitude, multi_axis=true, fontsize=11pt)
     dataframe = sort(dataframe, order; rev=true)
     
     gdf = DataFrames.groupby(dataframe, grouping)
 
-    fig = Figure(backgroundcolor = RGBf(0.98, 0.98, 0.98), size = (x_fig_size, y_fig_size), fontsize = 7pt)
+    fig = Figure(size = (x_fig_size, y_fig_size), fontsize = fontsize)
     plot_layout = nothing
 
     if multi_axis
@@ -507,15 +523,14 @@ function GCM_label(x,y,GCM)
[…]

### 2025-05-09 paper/paper_draft.qmd
Add figures and captions for ACCESS-ESM1-5 to quarto

@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#fig-access-esm1-5-bioregion-timeseries width=`{julia} timeseries_width`}
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#fig-access-esm1-5-bioregion-timeseries width=`{julia} timeseries_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median depth for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth width=`{julia} violin_width`}
+Solid lines represent the median depth for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwcor width=`{julia} violin_width`}
+Solid lines represent the median cover – DHW correlation level for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwcor width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW level for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
+Solid lines represent the median DHW level for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}
+Solid lines represent the median DHW tolerance value for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#fig-access-esm1-5-bioregion-initialproportion width=`{julia} violin_width`}
+Solid lines represent the median proportion of habitable area occupied for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#fig-access-esm1-5-bioregion-initialproportion width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#fig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#fig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_cover_cor_management_area_violin.png){#fig-access-esm1-5-manarea-dhwcor width=`{julia} violin_width`}
+Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_cover_cor_management_area_violin.png){#fig-access-esm1-5-manarea-dhwcor width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/mean_dhw_management_area_violin.png){#fig-access-esm1-5-manarea-dhwmean width=`{julia} violin_width`}
+Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/mean_dhw_management_area_violin.png){#fig-access-esm1-5-manarea-dhwmean width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median DHW – tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_tolerance_management_area_violin.png){#fig-access-esm1-5-manarea-dhwtol width=`{julia} violin_width`}
+Solid lines represent the median DHW – tolerance value for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_tolerance_management_area_violin.png){#fig-access-esm1-5-manarea-dhwtol width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/initial_proportion_management_area_violin.png){#fig-access-esm1-5-manarea-initialproportion width=`{julia} violin_width`}
+Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/initial_proportion_management_area_violin.png){#fig-access-esm1-5-manarea-initialproportion width=`{julia} violin_width`}
 
@@
 Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/so_to_si_management_area_violin.png){#fig-access-esm1-5-manarea-logsosi width=`{julia} violin_width`}
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/so_to_si_management_area_violin.png){#fig-access-esm1-5-manarea-logsosi width=`{julia} violin_width`}
 
@@
 The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/log_total_strength_management_area_violin.png){#sfig-access-esm1-5-manarea-totalconnectivity width=`{julia} violin_width`}
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/log_total_strength_management_area_violin.png){#sfig-access-esm1-5-manarea-totalconnectivity width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median total cover – DHW correlation value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwcor width=`{julia} violin_width`}
+Solid lines represent the median total cover – DHW correlation value for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwcor width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median occupied proportion value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/initial_proportion_gbr_violin.png){#sfig-access-esm1-5-gbr-initialproportion width=`{julia} violin_width`}
+Solid lines represent the median occupied proportion value for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/initial_proportion_gbr_violin.png){#sfig-access-esm1-5-gbr-initialproportion width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/mean_dhw_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwmean width=`{julia} violin_width`}
+Solid lines represent the median DHW value for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/mean_dhw_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwmean width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW - tolerance value for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwtol width=`{julia} violin_width`}
+Solid lines represent the median DHW - tolerance value for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwtol width=`{julia} violin_width`}
 
@@
 Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels..](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/so_to_si_gbr_violin.png){#sfig-access-esm1-5-gbr-logsosi width=`{julia} violin_width`}
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/so_to_si_gbr_violin.png){#sfig-access-esm1-5-gbr-logsosi width=`{julia} violin_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}
 

### 2025-05-09 src/plotting_functions.jl

@@ -735,8 +735,8 @@ function grouped_cluster_ridgeline_plot(
     fig, gdf, plot_layout = _setup_grouped_figure(
         dataframe,
         grouping;
-        x_fig_size=fig_y_size,
-        y_fig_size=fig_x_size,
+        x_fig_size=fig_x_size,
+        y_fig_size=fig_y_size,
         fontsize=fontsize,
         marker=PolyElement,
         multi_axis=false

### 2025-05-30 paper/paper_draft.qmd
Add paper qmd edits and possible carbonate factored cover analyses

@@
 ---
-title: Future climate resilience of the Great Barrier Reef
+title: Think deep for reef resilience
 author:
@@
           state: QLD
+    attributes:
+        corresponding: true
 abstract: |
-  This is the abstract.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit.
-Nam placerat turpis purus, eu tristique ex tincidunt et.
-Mauris sed augue eget turpis ultrices tincidunt.
-Sed et mi in leo porta egestas.
-Aliquam non laoreet velit.
-Nunc quis ex vitae eros aliquet auctor nec ac libero.
-Duis laoreet sapien eu mi luctus, in bibendum leo molestie.
-Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
-Aliquam bibendum varius libero, eu efficitur justo rutrum at.
-Sed at tempus elit.
+    Coral reefs globally face unprecedented threats from climate change, with the Great Barrier Reef (GBR) experiencing severe declines in coral cover from thermal stress events.
+Understanding which reefs exhibit resilience to climate impacts is critical for conservation planning and intervention strategies.
+A scenario-based population modelling approach was adopted with larval connectivity dynamics, thermal adaptation, and environmental factors to assess coral reef resilience across GBR locations under future climate projections.
+Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities, three distinct reef trajectories are identified: resilient reefs maintaining coral cover through 2050, intermediate reefs with moderate declines, and vulnerable reefs experiencing severe degradation.
+Contrary to expectations, larval connectivity patterns did not substantially differentiate resilient from vulnerable reefs.
+Instead, reef depth emerged as the primary predictor of resilience, with deeper reefs benefiting from thermal refugia that reduced bleaching impacts.
+Initial coral cover also influenced trajectories, with reefs having lower initial cover showing greater relative resilience.
+Our findings suggest that depth provides critical protection against thermal stress, contrasting current restoration practices that primarily target easily accessible shallow sites.
+These results have important implications for reef management, indicating that depth refugia should be prioritized for further consideration in conservation planning alongside connectivity considerations to maximize coral survival under continuing climate change.
 keywords: 
@@
 
+map_width = fig_sizes["map_width"]
 ecs_width = fig_sizes["ecs_width"]
@@
 
-Climate change is impacting species survival, persistence and ecosystem functioning globally, including coral.
+Climate change is impacting species survival, persistence and ecosystem functions globally, including coral.
 Coral reefs are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading ([@foster2021]; [@gattuso2014]).
-Mass bleaching and mortality events linked to climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts (Arif et al.
-2022; Wild et al.
-2011).
-Climate impacts on coral reefs are, and will continue to, decrease the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling (Foster & Attrill 2021; Williams & Graham 2019) as well as ecosystem services such as food, protection, tourism and Indigenous cultural value (Eddy et al.
-2021; Stoeckl et al.
-2021).
+Mass bleaching and mortality events linked to climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts ([@arif2022]; [@wild2011]).
+Climate impacts on coral reefs are, and will continue to, decrease the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling ([@forster2021]; [@williams2019]) as well as ecosystem services such as food, protection, tourism and Indigenous cultural value ([@eddy2021]; [@stoeckl2021]).
 We aim to assess the impacts of possible climate futures and identify the characteristics of resilient reefs using the latest generation of larval connectivity research with scenario-based population modelling for the Great Barrier Reef ecosystem.
@@
 The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of thousands of individual reefs.
-They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes (Grimaldi et al.
-2022).
-Severe declines in coral cover are projected due to compounding impacts such as ocean warming and acidification, intensification of Tropical Cyclones, and Crown of Thorns Starfish outbreaks (De’ath et al.
-2012; Fox-Kemper et al.
-2021; Seneviratne et al.
-2021; Sweatman et al.
-2011; Wolff et al.
-2018).
-Ominously, the 2023-24 Summer mass bleaching event (Cantin et al.
-2024) may be signalling a shift towards this reef future.
+They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes ([@grimaldi2022]).
+Severe declines in coral cover are projected due to compounding impacts such as ocean warming and acidification, intensification of Tropical Cyclones, and Crown of Thorns Starfish outbreaks ([@death2012]; [@fox-kemper2021]; [@seneviratne2021]; [@sweatman2011]; [@wolff2018]).
+Ominously, the 2023-24 Summer mass bleaching event ([@cantin2024]) may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs.
 
 Environmental abiotic factors influence how reefs will experience climate change pressures, including the spatio-temporal patterns of thermal stress itself, and indirect factors that influence the stress experienced by corals.
-Environmental factors such as tropical cyclones and wind driven mixing (Lin et al.
-2023; McClanahan et al.
-2005); currents (Grimaldi et al.
-2022) and depth (Álvarez-Noriega et al.
-2018; Baird et al.
-2018; Smith et al.
-2014) can decrease the magnitude of thermal stress corals experience.
-On the other hand, high light intensity and nutrient levels in the benthic zone can increase coral bleaching (DeCarlo et al.
-2020; Higuchi et al.
-2015).
+Environmental factors such as tropical cyclones and wind driven mixing ([@lin2023]; [@mcclanahan2005]); currents ([@grimaldi2022]) and depth ([@álvarez-noriega2018]; [@baird2018]; [@smith2014]) can decrease the magnitude of thermal stress corals experience.
+On the other hand, high light intensity and nutrient levels in the benthic zone can increase coral bleaching ([@decarlo2020]; [@higuchi2015]).
 These environmental factors influence the resilience of reefs to climate change pressures in combination with related biological factors such as larval connectivity and thermal tolerance.
 
-Connectivity in systems such as the GBR is an important contributor to system resilience, as strong connections are required to repopulate locations after disturbance, and drive adaptation to climate pressures (Angeler et al.
-2023; Elmhirst et al.
-2009; Hock et al.
-2017).
+Connectivity in systems such as the GBR is an important contributor to system resilience, as strong connections are required to repopulate locations after disturbance, and drive adaptation to climate pressures ([@angeler2023]; [@elmhirst2009]; [@hock2017]).
 When populations that are strong larval suppliers to external reefs are impacted by disturbances, increased adult coral mortality will cause decreased outgoing larvae in the following years.
-Weaker larval connections then slow the recovery of the externally connected locations (Figueiredo et al.
-2022; Hock et al.
-2017; Munday et al.
-2009).
-Populations with greater strength and number of outgoing than incoming larval connections - herein referred to as larval sources - have lower resilience to pressures than populations with greater incoming than outgoing larval flows - referred to as larval sinks - as larval source populations lack external sources of larvae that are important in contributing to reef recovery and recruitment of juveniles after disturbances to existing populations (Ani et al.
-2024; Hock et al.
-2017).
-Larval source populations are an important component of overall reef resilience as they can contribute larvae to recovering populations at other locations (Hock et al.
-2017; Thomas et al.
-2015).
-Connectivity will be altered by future climate change impacts such as population fragmentation, increasing larval mortality, and changes to coastal hydrodynamics (Figueiredo et al.
-2022; Munday et al.
-2009), and influences the biology of surrounding reef populations.
+Weaker larval connections then slow the recovery of the externally connected locations ([@figueiredo2022]; [@hock2017]; [@munday2009]).
+Populations with greater strength and number of outgoing than incoming larval connections - herein referred to as larval sources - have lower resilience to pressures than populations with greater incoming than outgoing larval flows - referred to as larval sinks - as larval source populations lack external sources of larvae that are important in contributing to reef recovery and recruitment of juveniles after disturbances to existing populations ([@ani2024]; [@hock2017]).
+Larval source populations are an important component of overall reef resilience as they can contribute larvae to recovering populations at other locations ([@hock2017]; [@thomas2015]).
+Connectivity will be altered by future climate change impacts such as population fragmentation, increasing larval mortality, and changes to coastal hydrodynamics ([@figueiredo2022]; [@munday2009]), and influences the biology of surrounding reef populations.
 
-Many additional biological factors including coral size (Brandt 2009), taxa (Álvarez-Noriega et al.
-2018; McClanahan et al.
-2005), and acclimation and inherited thermal tolerance (Humanes et al.
-2022; Lachs et al.
-2024), influence the outcome of high coral heat stress.
-It has been shown that corals have the adaptive capacity to develop thermal tolerance levels capable of delaying climate impacts under low emissions scenarios (Bairos-Novak et al.
-2021; Humanes et al.
-2022).
+Many additional biological factors including coral size ([@brandt2009]), taxa ([@álvarez-noriega2018]; [@mcclanahan2005]), and acclimation and inherited thermal tolerance ([@humanes2022]; [@lachs2024]), influence the outcome of high coral heat stress.
+It has been shown that corals have the adaptive capacity to develop thermal tolerance levels capable of delaying the onset of widespread bleaching under low emissions scenarios ([@bairos-novak2021]; [@humanes2022]).
 
-Incorporating the latest advancements in whole ecosystem larval connectivity modelling and research on the mechanisms behind coral bleaching and thermal adaptation responses into coral population modelling allows us to investigate how these abiotic and biotic factors interact and will influence coral climate change resilience into the future.
-Improvements in coral reef climate response modelling, including sampling from a range of possible climate futures, allow for fine-scale timeseries analyses of uncertain climate change and ecological scenarios (Bode et al.
-2017; Chollett et al.
-2022; Donner et al.
-2018; Klein et al.
-2024; Uusitalo et al.
-2015).
+Incorporating the latest advancements in whole ecosystem larval connectivity modelling and coral thermal response and adaptation research into coral population modelling allows us to investigate how these abiotic and biotic factors interact and will influence coral climate change resilience into the future.
+Improvements in coral reef climate response modelling, including sampling from a range of possible climate futures, allow for fine-scale timeseries analyses of uncertain climate change and ecological scenarios ([@bode2017]; [@chollett2022]; [@donner2018]; [@klein2024]; [@uusitalo2015]).
 
@@
 ## Environmental modelling context
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points).
+The green polygon represents the Far Northern management area, the yellow polygon represents the Cairns/Cooktown management area, the pink polygon represents the Townsville/Whitsunday management area and the blue polygon represents the Mackay/Capricorn management area.
+The centroid of each reef is represented as a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion.
+An annotation represents the approximate location of the Australian Institute of Marine Science Townsville site at Cape Cleveland.](/../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map width=`{julia} map_width`}
 
-The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas, as used in ReefMod-GBR (Bozec et al.
-2022).
+The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas.
+It follows the reef definitions as adopted in ReefMod-GBR ([@bozec2022]) (@fig-region-map).
 Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future thermal stress at each reef location.
 Five Global Climate Models (GCMs) (EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6) were selected for this study.
-Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great Barrier Reef were obtained from the HighResCoralStress database (Dixon et al.
-2023, 2022).
-Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology (Liu et al.
-2017; Skirving et al.
-2020).
+Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great Barrier Reef were obtained from the HighResCoralStress database ([@dixon2022][@dixon]).
+Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology ([@liu2017]; [@skirving2020]).
 These GCMs were selected from available GCMs downscaled by Dixon et al.
-(2023) based on evaluation by Grose et al.
-(2023), which found high correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms in these GCMs.
-Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming caused by a doubling of carbon dioxide above its pre-industrial concentration (Forster et al.
-2021).
-The four GCMs span a range of ECS values within the IPCC assessed likely range, and GCM development families, allowing for a range of possible climate futures to be explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs; Grose et al.
-2023; Shepherd et al.
-2018).
+[-@dixon] based on evaluation by Grose et al.
+[-@grose2023], which found high correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms in these GCMs.
+Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming caused by a doubling of carbon dioxide above its pre-industrial concentration ([@forster2021]).
+The four GCMs span a range of ECS values within the IPCC assessed likely range, and GCM development families, allowing for a range of possible climate futures to be explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs; [@grose2023]; [@shepherd2018]).
 The following analyses are performed using each GCM separately.
-SSP 2-4.5 is used as a plausible emission pathway under current emission trajectories, with similar atmospheric CO2 levels remaining until 2050 (Hausfather & Peters 2020; IPCC 2023).
+SSP 2-4.5 is used as a plausible emission pathway under current emission trajectories, with similar atmospheric CO2 levels remaining until 2050 ([@hausfather2020]; IPCC [-@climate2023]).
 
@@
 
-CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time (CoralBlox citation).
+CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time ([@ribeirodealmeida2024]).
 This model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
 Environmental disturbances and reproduction are not directly considered within CoralBlox.
-Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform (ADRIA citation).
+Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform ([@iwanaga2023]).
 Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
+As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.
 
-CoralBlox uses user-defined size classes that influence size-dependent growth and mortality rates, through which the coral colonies progress as they grow in diameter.
-Within ADRIA, we define the distributions of these parameters, and the size classes based on ecological monitoring data from the [EcoRRAP program](https://gbrrestoration.org/program/ecorrap/).
-
-Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes (1996).
+Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996].
 Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
-Viable larvae settle at a reef location and are incorporated into the model as the smallest size class, but are not directly impacted by modelled bleaching mortality as it is assumed the high background mortality of juveniles includes thermal stress.
+Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality as it is assumed the high background mortality of juveniles includes thermal stress.
 
@@
 Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
-(2021) and unpublished data from Hughes et al.
-(2018).
+[-@bairos-novak2021] and unpublished data from Hughes et al.
+[-@hughes2018].
+
 Tropical cyclones and wave impacts to reefs are not included in this investigation.
 We scale coral bleaching impacts by a coefficient determined by the median depth of each reef location, following Baird et al.
-(2018), reducing the proportion of coral colonies on a reef impacted by high heat stress as depth increases.
-Median depths for each reef location have been extracted from satellite derived bathymetry data for the Great Barrier Reef (GBRMPA 2020).
+[@baird2018], reducing the proportion of coral colonies on a reef impacted by high heat stress as depth increases.
+Median depths for each reef location have been extracted from satellite derived bathymetry data for the Great Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details).
 Due to varying degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs with less than 5% coverage of valid bathymetry data have been removed from this investigation.
@@
 
-\*\* need information on GBR1 connectivity used \*\*
+** need information on GBR1 connectivity used **
 
@@
 To quantify the behaviour of timeseries and identify timeseries that behave similarly we calculate the complexity-invariant distance (CID) between each timeseries.
-The complexity-invariant distance refers to the Euclidean distance between two timeseries multiplied (corrected) by the ratio of the complexities of the timeseries (Batista et al.
-2014).
-These values create a distance matrix of n \* n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm (Steinmann et al.
-2020).
+The complexity-invariant distance refers to the Euclidean distance between two timeseries multiplied (corrected) by the ratio of the complexities of the timeseries ([@batista2014]).
+These values create a distance matrix of n * n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm ([@steinmann2020]).
 
@@
 These characteristics include reef median depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation between total coral cover and inversed DHW timeseries, proportion of coral habitable area occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and total strength of larval connections between reefs.
-To analyse the DHW - tolerance levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa \* reef \* scenario matrix.
+To analyse the DHW - tolerance levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep * taxa * reef * scenario matrix.
 The mean timeseries was calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then used to calculate an overall mean DHW – tolerance value for each reef under each GCM.
@@
 Within bioregions timeseries clustering analysis was able to identify three clusters of relative cover timeseries.
-Across many bioregions timeseries clustering identified a ‘low’ cluster containing reefs that suffer larger declines and generally have lower levels of relative coral cover than the other clusters, a ‘medium’ cluster with intermediate levels of relative coral cover, and a ‘high’ cluster with cover recovery that persists to 2050 in many bioregions (@fig-access-esm1-5-bioregion-timeseries).
+Across many bioregions timeseries clustering identified a ‘low’ cluster containing reefs that suffer larger declines and generally have lower levels of relative coral cover than the other clusters, a ‘medium’ cluster with intermediate levels of relative coral cover, and a ‘high’ cluster with cover recovery that persists to 2050 in many bioregions (@sfig-access-esm1-5-bioregion-timeseries; @sfig-access-cm2-bioregion-timeseries; @sfig-ec-earth3-veg-bioregion-timeseries; @sfig-gfdl-cm4-bioregion-timeseries; @sfig-noresm2-mm-bioregion-timeseries).
 
-![Reef relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#fig-access-esm1-5-bioregion-timeseries width=`{julia} timeseries_width`}
-
-In many bioregions, median reef depth decreases as cluster relative coral cover decreases, with reefs within the ‘high’ cluster commonly having the greatest median reef depths within the bioregion (@fig-access-esm1-5-bioregion-depth).
+In many bioregions, median reef depth decreases as cluster relative coral cover decreases, with reefs within the ‘high’ cluster commonly having the greatest median reef depths within the bioregion (@fig-access-esm1-5-bioregion-depth; @sfig-access-cm2-bioregion-depth; @sfig-ec-earth3-veg-bioregion-depth; @sfig-gfdl-cm4-bioregion-depth; @sfig-noresm2-mm-bioregion-depth).
 
@@
 
-Correlation between reef total coral cover and reef DHW timeseries decreases as cluster relative coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total cover – DHW timeseries correlation levels (@fig-access-esm1-5-bioregion-dhwcor).
+Correlation between reef total coral cover and reef DHW timeseries decreases as cluster relative coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total cover – DHW timeseries correlation levels (@sfig-access-esm1-5-bioregion-dhwcor; @sfig-access-cm2-bioregion-dhwcor; @sfig-ec-earth3-veg-bioregion-dhwcor; @sfig-gfdl-cm4-bioregion-dhwcor; @sfig-noresm2-mm-bioregion-dhwcor).
 
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwcor width=`{julia} violin_width`}
-
-Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@fig-access-esm1-5-bioregion-dhwmean).
+Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@fig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).
 
@@
 In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially lower mean thermal tolerance levels compared to reefs in other clusters.
-However, many bioregions do not show strong differences in thermal tolerance levels (@fig-access-esm1-5-bioregion-dhwtol).
+However, many bioregions do not show strong differences in thermal tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol; @sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol; @sfig-noresm2-mm-bioregion-dhwtol).
 
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}
+In many bioregions reefs with high relative coral cover levels (‘high’ cluster) have the lowest initial proportions of habitable area occupied by corals, while reefs in the ‘low’ cluster often have the highest initial proportions of coral habitable area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion; @sfig-access-cm2-bioregion-initialproportion; @sfig-ec-earth3-veg-bioregion-initialproportion; @sfig-gfdl-cm4-bioregion-initialproportion; @sfig-noresm2-mm-bioregion-initialproportion).
 
-In many bioregions reefs with high relative coral cover levels (‘high’ cluster) have the lowest initial proportions of habitable area occupied by corals, while reefs in the ‘low’ cluster often have the highest initial proportions of coral habitable area occupied by corals (@fig-access-esm1-5-bioregion-initialproportion).
-
-![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#fig-access-esm1-5-bioregion-initialproportion width=`{julia} violin_width`}
-
-Across most bioregions there are not consistent differences between clusters in connectivity metrics such as source-to-sink connectivity ratio (@fig-access-esm1-5-bioregion-logsosi) and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
-
-![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#fig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}
+Across most bioregions there are not consistent differences between clusters in connectivity metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi; @sfig-access-cm2-bioregion-logsosi; @sfig-ec-earth3-veg-bioregion-logsosi; @sfig-gfdl-cm4-bioregion-logsosi; @sfig-noresm2-mm-bioregion-logsosi) and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity; @sfig-access-cm2-bioregion-totalconnectivity; @sfig-ec-earth3-veg-bioregion-totalconnectivity; @sfig-gfdl-cm4-bioregion-totalconnectivity; @sfig-noresm2-mm-bioregion-totalconnectivity).
 
 ## Management area scale clustering
+
 Within the four management areas, timeseries clustering analysis identified three clusters of reefs using relative coral cover timeseries.
@@
 The ‘high’ cover cluster of reefs contains reefs that have continuing recovery of corals throughout the future climate scenario.
-The medium and low clusters contain many reefs that decrease to half their initial coral cover levels and largely do not display the levels of recurring recovery that reefs in high clusters experience (@fig-access-esm1-5-manarea-timeseries).
+The medium and low clusters contain many reefs that decrease to half their initial coral cover levels and largely do not display the levels of recurring recovery that reefs in high clusters experience (@fig-access-esm1-5-manarea-timeseries; @sfig-access-cm2-manarea-timeseries; @sfig-ec-earth3-veg-manarea-timeseries; @sfig-gfdl-cm4-manarea-timeseries; @sfig-noresm2-mm-manarea-timeseries).
 
@@
 Within each bioregion reef median depth level increases with increasing reef relative coral cover.
-Reefs in the low cluster have the lowest median depth levels, while reefs in the high cluster have the highest median depth levels within each management area (@fig-access-esm1-5-manarea-depth).
+Reefs in the low cluster have the lowest median depth levels, while reefs in the high cluster have the highest median depth levels within each management area (@fig-access-esm1-5-manarea-depth; @sfig-access-cm2-manarea-depth; @sfig-ec-earth3-veg-manarea-depth; @sfig-gfdl-cm4-manarea-depth; @sfig-noresm2-mm-manarea-depth).
 
@@
 
-Correlation between reef total coral cover and the DHW levels they experience throughout the time period increases as coral relative cover increases, with reefs in the high cluster having the highest median total cover – DHW correlation (@fig-access-esm1-5-manarea-dhwcor).
-
-![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_cover_cor_management_area_violin.png){#fig-access-esm1-5-manarea-dhwcor width=`{julia} violin_width`}
+Correlation between reef total coral cover and the DHW levels they experience throughout the time period increases as coral relative cover increases, with reefs in the high cluster having the highest median total cover – DHW correlation (@sfig-access-esm1-5-manarea-dhwcor; @sfig-access-cm2-manarea-dhwcor; @sfig-ec-earth3-veg-manarea-dhwcor; @sfig-gfdl-cm4-manarea-dhwcor; @sfig-noresm2-mm-manarea-dhwcor).
 
 However, reefs with higher relative coral cover levels do not experience lower mean DHW levels throughout their timeseries.
-There are no consistent substantial differences in mean DHW levels across the identified timeseries clusters (@fig-access-esm1-5-manarea-dhwmean).
+There are no consistent substantial differences in mean DHW levels across the identified timeseries clusters (@sfig-access-esm1-5-manarea-dhwmean; @sfig-access-cm2-manarea-dhwmean; @sfig-ec-earth3-veg-manarea-dhwmean; @sfig-gfdl-cm4-manarea-dhwmean; @sfig-noresm2-mm-manarea-dhwmean).
 
-![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/mean_dhw_management_area_violin.png){#fig-access-esm1-5-manarea-dhwmean width=`{julia} violin_width`}
+Within the Far Northern management area ‘low’ cluster reefs have substantially lower median DHW – tolerance levels than ‘medium’ and ‘high’ clusters, while there are no substantial differences in DHW – tolerance between clusters in other management areas (@sfig-access-esm1-5-manarea-dhwtol; @sfig-access-cm2-manarea-dhwtol; @sfig-ec-earth3-veg-manarea-dhwtol; @sfig-gfdl-cm4-manarea-dhwtol; @sfig-noresm2-mm-manarea-dhwtol).
 
-Within the Far Northern management area ‘low’ cluster reefs have substantially lower median DHW – tolerance levels than ‘medium’ and ‘high’ clusters, while there are no substantial differences in DHW – tolerance between clusters in other management areas (@fig-access-esm1-5-manarea-dhwtol).
+Like clusters identified within bioregions, within the Mackay-Capricorn, Far Northern and Cairns-Cooktown management areas the initial proportion of coral-habitable area initially occupied by corals decreases in clusters with higher relative coral cover (@sfig-access-esm1-5-manarea-initialproportion; @sfig-access-cm2-manarea-initialproportion; @sfig-ec-earth3-veg-manarea-initialproportion; @sfig-gfdl-cm4-manarea-initialproportion; @sfig-noresm2-mm-manarea-initialproportion).
 
-![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_tolerance_management_area_violin.png){#fig-access-esm1-5-manarea-dhwtol width=`{julia} violin_width`}
-
-Like clusters identified within bioregions, within the Mackay-Capricorn, Far Northern and Cairns-Cooktown management areas the initial proportion of coral-habitable area initially occupied by corals decreases in clusters with higher relative coral cover (@fig-access-esm1-5-manarea-initialproportion).
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/initial_proportion_management_area_violin.png){#fig-access-esm1-5-manarea-initialproportion width=`{julia} violin_width`}
-
-At management area analysis scales, there are not consistent substantial differences in source – to – sink ratios (@fig-access-esm1-5-manarea-logsosi) and total connectivity strength (@sfig-access-esm1-5-manarea-totalconnectivity).
-
-![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/so_to_si_management_area_violin.png){#fig-access-esm1-5-manarea-logsosi width=`{julia} violin_width`}
+At management area analysis scales, there are not consistent substantial differences in source – to – sink ratios (@sfig-access-esm1-5-manarea-logsosi; @sfig-access-cm2-manarea-logsosi; @sfig-ec-earth3-veg-manarea-logsosi; @sfig-gfdl-cm4-manarea-logsosi; @sfig-noresm2-mm-manarea-logsosi) and total connectivity strength (@sfig-access-esm1-5-manarea-totalconnectivity; @sfig-access-cm4-manarea-totalconnectivity; @sfig-ec-earth3-veg-manarea-totalconnectivity; @sfig-gfdl-cm4-manarea-totalconnectivity; @sfig-noresm2-mm-manarea-totalconnectivity).
 
 ## Great Barrier Reef scale clustering
+
 Timeseries clustering identified three clusters in reef relative cover timeseries for the whole GBR scale.
-A ‘low’ cluster of reefs with little recovery following initial declines, a medium cluster of reefs with median relative cover below 0.5 post 2028, and a high cluster of reefs with median relative cover above 0.5 until 2050 (@fig-access-esm1-5-gbr-timeseries).
+A ‘low’ cluster of reefs with little recovery following initial declines, a medium cluster of reefs with median relative cover below 0.5 post 2028, and a high cluster of reefs with median relative cover above 0.5 until 2050 (@fig-access-esm1-5-gbr-timeseries; @sfig-access-cm2-gbr-timeseries; @sfig-ec-earth3-veg-gbr-timeseries; @sfig-gfdl-cm4-gbr-timeseries; @sfig-noresm2-mm-gbr-timeseries).
 
@@
 The clusters identified with timeseries clustering at the GBR scale show similar patterns to clusters identified at bioregion and management area scales.
-Reef depth (@fig-access-esm1-5-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels.
-There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol) levels of reefs.
-Similarly, there are no substantial differences between clusters in connectivity metrics source – to – sink ratio and total connectivity strength (@sfig-access-esm1-5-gbr-logsosi, @sfig-access-esm1-5-gbr-totalconnectivity).
+Reef depth (@fig-access-esm1-5-gbr-depth; @sfig-access-cm2-gbr-depth; @sfig-ec-earth3-veg-gbr-depth; @sfig-gfdl-cm4-gbr-depth; @sfig-noresm2-mm-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor; @sfig-access-cm2-gbr-dhwcor; @sfig-ec-earth3-veg-gbr-dhwcor; @sfig-gfdl-cm4-gbr-dhwcor; @sfig-noresm2-mm-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion; @sfig-access-cm2-gbr-initialproportion; @sfig-ec-earth3-veg-gbr-initialproportion; @sfig-gfdl-cm4-gbr-initialproportion; @sfig-noresm2-mm-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels.
+There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean; @sfig-access-cm4-gbr-dhwmean; @sfig-ec-earth3-veg-gbr-dhwmean; @sfig-gfdl-cm4-gbr-dhwmean; @sfig-noresm2-mm-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol; @sfig-access-cm2-gbr-dhwtol; @sfig-ec-earth3-veg-gbr-dhwtol; @sfig-gfdl-cm4-gbr-dhwtol; @sfig-noresm2-mm-gbr-dhwtol) levels of reefs.
+Similarly, there are no substantial differences between clusters in connectivity metrics source – to – sink ratio and total connectivity strength (@sfig-access-esm1-5-gbr-logsosi; @sfig-access-cm2-gbr-logsosi; @sfig-ec-earth3-veg-gbr-logsosi; @sfig-gfdl-cm4-gbr-logsosi; @sfig-noresm2-mm-gbr-logsosi; @sfig-access-esm1-5-gbr-totalconnectivity; @sfig-access-cm2-gbr-totalconnectivity; @sfig-ec-earth3-veg-gbr-totalconnectivity; @sfig-gfdl-cm4-gbr-totalconnectivity; @sfig-noresm2-mm-gbr-totalconnectivity).
 
@@
 # Discussion
+
 Timeseries analysis has been used to identify three groups of reefs with similar declining (low), recovering (high), and intermediate (medium) coral cover trajectories throughout future scenarios.
@@
 Analysis from Baird et al.
-(2018) is used to calculate the degree of protection provided to a reef based on the median depth.
+[-@baird2018] is used to calculate the degree of protection provided to a reef based on the median depth.
 Our results suggest that within shallow reef ecosystems (depth < 30m), depth contributes greatly to reef resilience and the ability of the reef to recover following heat stress.
-While similar findings have been demonstrated in the eastern Pacific (Smith et al.
-2014), depth refugia analyses have often focussed on the potential of mesophotic reefs (> 30m deep) as thermal refugia (Bongaerts et al.
-2010; Holstein et al.
-2015; Semmler et al.
-2017).
+While similar findings have been demonstrated in the eastern Pacific ([@smith2014]), depth refugia analyses have often focussed on the potential of mesophotic reefs (> 30m deep) as thermal refugia ([@bongaerts2010]; [@holstein2015]; [@semmler2017]).
 In contrast, Venegas et al.
-(2019) found no association between depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
+[-@venegas2019] found no association between depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
 The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels.
@@
 Overall, these findings support the hypothesis that reefs at greater depths will experience refugia benefits and more prolonged resilience under climate change compared to shallower reefs.
+Additionally, [-@liu2024] suggest that rubble instability is inversely correlated with reef depth, possibly limiting the larval recruitment capacity of shallow reefs.
 A caveat to these findings is the quality of the bathymetry data used to calculate depth refugia benefits in ADRIA.
-This data (GBRMPA 2020) is derived from satellite imagery and is limited in its alignment with the established GBRMPA reef outlines used in the investigation to characterise reef locations.
+This data (GBRMPA [-@gbr10gb2020]) is derived from satellite imagery and is limited in its alignment with the established GBRMPA reef outlines used in the investigation to characterise reef locations.
 As a result, 842 reefs (22% of the 3806) were removed from the analyses before depth comparisons due to having less than 5% coverage of depth data.
+Additionally, deriving estimates of depth from satellite imagery is prone to high degrees of uncertainty.
+Data adopted for the given assessment are said to be accurate up to 15m from Mean Sea Level [@gbr10gb2020].
+Furthermore, an estimated median depth is determined for each reef, using the established GBRMPA reef outlines to provide an indication of “true” reef extent.
+Therefore, the estimates of reef depths are taken as a useful indication rather than an accurate and precise report of reef depths across the GBR.
 
-Current reef restoration and intervention-investigation efforts on the Great Barrier Reef, such as deployment of coral seeding and fragment devices target reefs with suitable restoration sites in the 1-10m depth range (Howlett et al.
-2021; Randall et al.
-2021; Whitman et al.
-2024).
+<!-- liu2024 citation -->
+
+Current reef restoration and intervention-investigation efforts on the Great Barrier Reef, such as deployment of coral seeding and fragment devices target reefs with suitable restoration sites in the 1-10m depth range ([@howlett2021]; [@randall2021]; [@whitman2024]).
 One of the main depth constraints is being able to visually identify the target site from the surface for deployment and ongoing monitoring, in combination with factors such as deployment method and tourism return value.
-Our results suggest that many reefs with a median depth in this range are likely to fall into the low and medium clusters, suffering large future declines in reef health under climate change and possibly limiting the potential of interventions to deliver recovery in these locations.
-Reef intervention planning is a complex and challenging decision making process (Anthony et al.
-2020), and our results suggest that deployment site depth is likely an important factor to consider when assessing the long-term resilience of reef sites.
+Our results suggest that of the reefs analysed within the 1-10m depth range (1800) 87% (1569) of reefs fall into the low and medium clusters (at the Great Barrier Reef scale), with many suffering large future declines in reef health under climate change and possibly limiting the potential of interventions to deliver recovery in these locations.
+Reef intervention planning is a complex and challenging decision making process ([@anthony2020]), and our results suggest that deployment site depth is likely an important factor to consider when assessing the long-term resilience of reef sites.
 
 Overall, our findings do not suggest that resilient reefs in ‘high’ cover clusters have greater thermal tolerance than reefs in lower coral cover clusters.
-This is in contrast with literature suggesting corals have the capacity to adapt to increasing climate change pressures (Humanes et al.
-2022; Lachs et al.
-2024), including the investigation by Bairos-Novak et al.
-(2021) that revealed high heritability of bleaching and survival response traits used to inform the distributions of thermal tolerance traits used in this investigation.
+This is in contrast with literature suggesting corals have the capacity to adapt to increasing climate change pressures ([@humanes2022]; [@lachs2024]), including the investigation by Bairos-Novak et al.
+[-@bairos-novak2021] that revealed high heritability of bleaching and survival response traits used to inform the distributions of thermal tolerance traits used in this investigation.
 The lack of influence of thermal tolerance on reef outcomes is likely due to reef being impacted by overall similar levels of thermal stress, combined with the greater importance of factors such as reef depth and initial coral cover.
 
-It has been suggested that a primary facet of reef resilience is the degree of larval connectivity between reefs and the supply of recruits that a reef receives following disturbance (Hock et al.
-2017).
+It has been suggested that a primary facet of reef resilience is the degree of larval connectivity between reefs and the supply of recruits that a reef receives following disturbance ([@hock2017]).
 It was expected that resilient reefs would have greater incoming than outgoing larval connectivity to promote recovery in years following thermal stress, while non-resilient reefs would have greater outgoing than incoming connectivity inhibiting recruitment of corals ability post thermal stress.
@@
 Hock et al.
-(2017) used larval connectivity modelling to identify resilient reefs that may supply up to 47% of the wider Great Barrier Reef ecosystem with larvae following disturbance.
-A criticism of this approach (Bode et al.
-2018) is that results obtained are highly sensitive to the biophysical dispersal model used, limiting the application of specific identified reefs.
+([-@hock2017]) used larval connectivity modelling to identify resilient reefs that may supply up to 47% of the wider Great Barrier Reef ecosystem with larvae following disturbance.
+A critique of this approach ([@bode2018]) is that results obtained are highly sensitive to the biophysical dispersal model used, limiting the application of specific identified reefs.
 Reef depth was not considered in these investigations of reef network resilience.
-These investigations were performed using prior generations of larval connectivity models parameterised for 2008-2013 (Hock et al.
-2017) and 1996-2002 (Bode et al.
-2018) time periods respectively.
-Using updated 1km resolution larval connectivity across the whole GBR, our results suggest that larval connectivity alone is not as important for reef resilience and recovery as environmental refugia from thermal stress such as environmental refugia factors such as depth.
+These investigations were performed using prior generations of larval connectivity models parameterised for 2008-2013 ([@hock2017]) and 1996-2002 ([@bode2018]) time periods respectively.
+Using updated 1km resolution larval connectivity across the whole GBR, our results suggest that larval connectivity alone is not as important for reef resilience and recovery as environmental refugia from thermal stress such as depth.
 
@@
 The large differences in relative cover timeseries seen across the GCMs suggest that it is important to consider this uncertainty in analyses of biological climate change responses.
-This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model climate change responses using a range of climate models separately (Shepherd et al.
-2018).
+This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model climate change responses using a range of climate models separately ([@shepherd2018]).
 However, the patterns identified between low, medium and high clusters of reefs suggest that the importance of depth refugia is consistent across scenarios.
@@
 
+There are multiple caveats in how coral ecosystem dynamics are modelled in this investigation.
+We model coral colonies as objects with circular diameter values and track these diameters over timesteps through growth.
+Due to the availability of quality future projected data we do not consider the impacts of waves, cyclones and currents on coral colony survival and bleaching (insert citations for waves affecting survival and bleaching).
+We do not consider the impacts of Crown of Thorns Starfish (CoTS) on coral survival and reef resilience (insert citation for cots affecting corals).
+Furthermore, there are multiple caveats to acknowledge in the data sources used in this investigation.
+Uncertainty in connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress projections are likely to influence the results obtained in this investigation.
+To limit the influence of bathymetry data on results, reefs with less than 5% data coverage are removed from analyses.
+We investigate a range of future climate responses and thermal projections, and our results suggest the factors that influence reef resilience are consistent across the tested futures.
+
+Further investigations could...
+
 # Conclusions
+
 Overall, our results suggest that when modelled as part of a large and complex ecosystem, reef depth is a key factor contributing to ongoing reef resilience.
 We provide evidence in support of depth as a form of refugia for shallow reefs.
-While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts (Anthony et al.
-2020; Hock et al.
-2017), our results suggest that resilient reefs do not have greater incoming or total connectivity to contribute to their resilience.
+While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts ([@anthony2020]; [@hock2017]), our results suggest that resilient reefs do not have greater incoming or total connectivity to contribute to their resilience.
 Instead, we suggest that depth, and likely other environmental thermal refugia mechanisms contribute greater to overall reef resilience and recovery.
@@
 # Supplementary Material
+
+## Model parameterisation
+CoralBlox uses user-defined size classes that influence size-dependent growth and mortality rates, through which the coral colonies progress as they grow in diameter.
+Within ADRIA, we define the distributions of these parameters, and the size classes based on ecological monitoring data from the Ecological Intelligence for Reef Restoration Program (EcoRRAP) ([@australian-institute-of-marine-science2025]; [@ribeirodealmeida2024]).
+
 ## ACCESS-ESM1-5
+### Bioregion scale
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries width=`{julia} timeseries_width`}
+
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median cover – DHW correlation level for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW tolerance value for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median proportion of habitable area occupied for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion width=`{julia} violin_width`}
+
+![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}
 
@@
 
+### Management area scale
+![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_cover_cor_management_area_violin.png){#sfig-access-esm1-5-manarea-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/mean_dhw_management_area_violin.png){#sfig-access-esm1-5-manarea-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median DHW – tolerance value for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_tolerance_management_area_violin.png){#sfig-access-esm1-5-manarea-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/initial_proportion_management_area_violin.png){#sfig-access-esm1-5-manarea-initialproportion width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/so_to_si_management_area_violin.png){#sfig-access-esm1-5-manarea-logsosi width=`{julia} violin_width`}
+
 ![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
@@
 Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/log_total_strength_management_area_violin.png){#sfig-access-esm1-5-manarea-totalconnectivity width=`{julia} violin_width`}
+
+### GBR scale
 
@@
 ## ACCESS-CM2
+### Bioregion scale
+![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median depth for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth width=`{julia} violin_width`}
+
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW level for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean width=`{julia} violin_width`}
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries width=`{julia} timeseries_width`}
+
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median cover – DHW correlation level for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW tolerance value for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median proportion of habitable area occupied for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion width=`{julia} violin_width`}
+
+![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity width=`{julia} violin_width`}
+
+### Management area scale
+![Reef relative coral cover timeseries clustered within each management area.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/management_area_cover_timeseries.png){#sfig-access-cm2-manarea-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/depth_management_area_violin.png){#sfig-access-cm2-manarea-depth width=`{julia} violin_width`}
+
+![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/dhw_cover_cor_management_area_violin.png){#sfig-access-cm2-manarea-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/mean_dhw_management_area_violin.png){#sfig-access-cm2-manarea-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median DHW – tolerance value for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/dhw_tolerance_management_area_violin.png){#sfig-access-cm2-manarea-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/initial_proportion_management_area_violin.png){#sfig-access-cm2-manarea-initialproportion width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/so_to_si_management_area_violin.png){#sfig-access-cm2-manarea-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/log_total_strength_management_area_violin.png){#sfig-access-cm2-manarea-totalconnectivity width=`{julia} violin_width`}
+
+### GBR scale
+![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
+The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
+The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
+The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/gbr_cover_timeseries.png){#sfig-access-cm2-gbr-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/depth_gbr_violin.png){#sfig-access-cm2-gbr-depth width=`{julia} violin_width`}
+
+![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median total cover – DHW correlation value for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-cm2-gbr-dhwcor width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median occupied proportion value for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/initial_proportion_gbr_violin.png){#sfig-access-cm2-gbr-initialproportion width=`{julia} violin_width`}
+
+![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW value for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/mean_dhw_gbr_violin.png){#sfig-access-cm2-gbr-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW - tolerance value for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-cm2-gbr-dhwtol width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/so_to_si_gbr_violin.png){#sfig-access-cm2-gbr-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/log_total_strength_gbr_violin.png){#sfig-access-cm2-gbr-totalconnectivity width=`{julia} violin_width`}
 
 ## EC-Earth3-Veg
+### Bioregion scale
+![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median depth for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth width=`{julia} violin_width`}
 
-## GFDL-ESM4
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW level for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean width=`{julia} violin_width`}
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries width=`{julia} timeseries_width`}
+
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median cover – DHW correlation level for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW tolerance value for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median proportion of habitable area occupied for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion width=`{julia} violin_width`}
+
+![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity width=`{julia} violin_width`}
+
+### Management area scale
+![Reef relative coral cover timeseries clustered within each management area.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/management_area_cover_timeseries.png){#sfig-ec-earth3-veg-manarea-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/depth_management_area_violin.png){#sfig-ec-earth3-veg-manarea-depth width=`{julia} violin_width`}
+
+![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/dhw_cover_cor_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/mean_dhw_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median DHW – tolerance value for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/dhw_tolerance_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/initial_proportion_management_area_violin.png){#sfig-ec-earth3-veg-manarea-initialproportion width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/so_to_si_management_area_violin.png){#sfig-ec-earth3-veg-manarea-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/log_total_strength_management_area_violin.png){#sfig-ec-earth3-veg-manarea-totalconnectivity width=`{julia} violin_width`}
+
+### GBR scale
+![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
+The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
+The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
+The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/gbr_cover_timeseries.png){#sfig-ec-earth3-veg-gbr-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/depth_gbr_violin.png){#sfig-ec-earth3-veg-gbr-depth width=`{julia} violin_width`}
+
+![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median total cover – DHW correlation value for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/dhw_cover_cor_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwcor width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median occupied proportion value for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/initial_proportion_gbr_violin.png){#sfig-ec-earth3-veg-gbr-initialproportion width=`{julia} violin_width`}
+
+![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW value for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/mean_dhw_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW - tolerance value for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/dhw_tolerance_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwtol width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/so_to_si_gbr_violin.png){#sfig-ec-earth3-veg-gbr-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/log_total_strength_gbr_violin.png){#sfig-ec-earth3-veg-gbr-totalconnectivity width=`{julia} violin_width`}
+
+## GFDL-CM4
+### Bioregion scale
+![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median depth for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth width=`{julia} violin_width`}
+
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW level for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean width=`{julia} violin_width`}
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries width=`{julia} timeseries_width`}
+
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median cover – DHW correlation level for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW tolerance value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median proportion of habitable area occupied for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion width=`{julia} violin_width`}
+
+![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity width=`{julia} violin_width`}
+
+### Management area scale
+![Reef relative coral cover timeseries clustered within each management area.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/management_area_cover_timeseries.png){#sfig-gfdl-cm4-manarea-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/depth_management_area_violin.png){#sfig-gfdl-cm4-manarea-depth width=`{julia} violin_width`}
+
+![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/dhw_cover_cor_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/mean_dhw_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median DHW – tolerance value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/dhw_tolerance_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/initial_proportion_management_area_violin.png){#sfig-gfdl-cm4-manarea-initialproportion width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/so_to_si_management_area_violin.png){#sfig-gfdl-cm4-manarea-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/log_total_strength_management_area_violin.png){#sfig-gfdl-cm4-manarea-totalconnectivity width=`{julia} violin_width`}
+
+### GBR scale
+![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
+The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
+The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
+The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/gbr_cover_timeseries.png){#sfig-gfdl-cm4-gbr-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/depth_gbr_violin.png){#sfig-gfdl-cm4-gbr-depth width=`{julia} violin_width`}
+
+![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median total cover – DHW correlation value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/dhw_cover_cor_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwcor width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median occupied proportion value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/initial_proportion_gbr_violin.png){#sfig-gfdl-cm4-gbr-initialproportion width=`{julia} violin_width`}
+
+![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/mean_dhw_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW - tolerance value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/dhw_tolerance_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwtol width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/so_to_si_gbr_violin.png){#sfig-gfdl-cm4-gbr-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/log_total_strength_gbr_violin.png){#sfig-gfdl-cm4-gbr-totalconnectivity width=`{julia} violin_width`}
 
 ## NorESM2-MM
+### Bioregion scale
+![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median depth for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth width=`{julia} violin_width`}
+
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW level for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean width=`{julia} violin_width`}
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries width=`{julia} timeseries_width`}
+
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median cover – DHW correlation level for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW tolerance value for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median proportion of habitable area occupied for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion width=`{julia} violin_width`}
+
+![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity width=`{julia} violin_width`}
+
+### Management area scale
+![Reef relative coral cover timeseries clustered within each management area.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/management_area_cover_timeseries.png){#sfig-noresm2-mm-manarea-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/depth_management_area_violin.png){#sfig-noresm2-mm-manarea-depth width=`{julia} violin_width`}
+
+![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/dhw_cover_cor_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/mean_dhw_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median DHW – tolerance value for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/dhw_tolerance_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/initial_proportion_management_area_violin.png){#sfig-noresm2-mm-manarea-initialproportion width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/so_to_si_management_area_violin.png){#sfig-noresm2-mm-manarea-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/log_total_strength_management_area_violin.png){#sfig-noresm2-mm-manarea-totalconnectivity width=`{julia} violin_width`}
+
+### GBR scale
+![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
+The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
+The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
+The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/gbr_cover_timeseries.png){#sfig-noresm2-mm-gbr-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/depth_gbr_violin.png){#sfig-noresm2-mm-gbr-depth width=`{julia} violin_width`}
+
+![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median total cover – DHW correlation value for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/dhw_cover_cor_gbr_violin.png){#sfig-noresm2-mm-gbr-dhwcor width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median occupied proportion value for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/initial_proportion_gbr_violin.png){#sfig-noresm2-mm-gbr-initialproportion width=`{julia} violin_width`}
+
+![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW value for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/mean_dhw_gbr_violin.png){#sfig-noresm2-mm-gbr-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW - tolerance value for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/dhw_tolerance_gbr_violin.png){#sfig-noresm2-mm-gbr-dhwtol width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/so_to_si_gbr_violin.png){#sfig-noresm2-mm-gbr-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/log_total_strength_gbr_violin.png){#sfig-noresm2-mm-gbr-totalconnectivity width=`{julia} violin_width`}

### 2025-05-30 src/ADRIA/HighResCoralStress/2_1_timeseries_clustering_carbonate.jl

@@ -1,0 +1,121 @@
+using Revise, Infiltrator
+
+using GLMakie, GeoMakie, GraphMakie
+using Statistics
+using YAXArrays
+import GeoDataFrames as GDF
+
+using ADRIA
+
+include("../../common.jl")
+include("../../plotting_functions.jl")
+
+GCM = "ACCESS-ESM1-5"
+# Select the target GCM from
+dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
+
+GBR_domain_path = "../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/"
+gbr_dom = ADRIA.load_domain(GBR_domain_path, "45")
+context_layers = gbr_dom.loc_data
+
+# Attach bioregion level data to context_layers
+bioregions = GDF.read("../data/GBRMPA_reefal_bioregions.gpkg")
+context_bioregion = find_intersections(context_layers, bioregions, :GBRMPA_ID, :DESCRIP, :SHAPE)
+context_layers = leftjoin(context_layers, context_bioregion; on=:GBRMPA_ID, matchmissing=:notequal, order=:left)
+rename!(context_layers, :area_ID => :bioregion)
+context_layers.bioregion .= ifelse.(ismissing.(context_layers.bioregion), "NA", context_layers.bioregion)
+context_layers.bioregion = convert.(String, context_layers.bioregion)
+
+n_clusters = 3
+
+thresholds = collect(2:1:20) ./ 100
+
+rs = ADRIA.load_results("../outputs/ADRIA_results/HighResCoralStress/GBR_2024_10_15_HighResCoralStress__RCPs_45_$(GCM)")
+GCM_results = GCM_analysis_results(rs)
+# Convert absolute cover to cover relative to carbonate budjet area
+areas = gbr_dom.loc_data.k .* gbr_dom.loc_data.area
+cover = GCM_results.absolute_median_cover
+
+n_timesteps = size(cover, 1)
+n_locations = size(cover, 2)
+n_thresholds = length(thresholds)
+threshold_cover = YAXArray(
+    (
+        cover.timesteps,
+        cover.locations,
+        Dim{:thresholds}(thresholds)
+    ),
+    zeros(n_timesteps, n_locations, n_thresholds)
+)
+threshold_clusters = YAXArray(
+    (
+        cover.locations,
[…]

### 2025-05-30 src/ADRIA/HighResCoralStress/2_timeseries_clustering.jl

@@ -56,6 +56,6 @@ for GCM in dhw_scenarios.dhw.properties["members"]
     context_layers[rel_cover_less_than_5_ind, "$(GCM)_management_area_cluster_cats"] = man_region_cluster_cats
     context_layers[rel_cover_less_than_5_ind, "$(GCM)_gbr_clusters"] = gbr_clusters
     context_layers[rel_cover_less_than_5_ind, "$(GCM)_gbr_cluster_cats"] = gbr_cluster_cats
-    
 end
+
 GDF.write("../outputs/ADRIA_results/HighResCoralStress/bellwether_reefs.gpkg", context_layers)

### 2025-05-30 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -4,7 +4,7 @@ connections for each reef. Run after running 3_.jl to include the bioregions and
 reef layers.
 """
 
-using DataFrames, Statistics, YAXArrays
+using DataFrames, Statistics, YAXArrays, ArchGDAL
 
 using GLMakie, GeoMakie, GraphMakie
 

### 2025-05-30 src/ADRIA/HighResCoralStress/4_analysis_and_plots_clustering.jl

@@ -23,8 +23,6 @@ context_layers.log_total_strength = log10.(context_layers.total_strength)
 
 gbr_dom = ADRIA.load_domain("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/", "45")
 
-
-
 for (i_gcm, GCM) in enumerate(GCMs)
     # Select GCM and load relevant results
     @info "analysing reef clustering for $(GCM)"
@@ -50,9 +48,9 @@ for (i_gcm, GCM) in enumerate(GCMs)
     analysis_layers = analysis_layers[(analysis_layers.management_area .!= "NA") .& (analysis_layers.bioregion .!= "NA"), :]
 
     # Analysing clusters identified at bioregion level
-    cluster_analysis_plots(analysis_layers, rel_cover, dhw_ts, :bioregion, fig_out_dir)
-    cluster_analysis_plots(analysis_layers, rel_cover, dhw_ts, :management_area, fig_out_dir)
-    cluster_analysis_plots(analysis_layers, rel_cover, dhw_ts, :gbr, fig_out_dir)
+    cluster_analysis_plots(GCM, analysis_layers, rel_cover, dhw_ts, :bioregion, fig_out_dir)
+    cluster_analysis_plots(GCM, analysis_layers, rel_cover, dhw_ts, :management_area, fig_out_dir)
+    cluster_analysis_plots(GCM, analysis_layers, rel_cover, dhw_ts, :gbr, fig_out_dir)
 
 end
 
@@ -60,8 +58,8 @@ man_area_gcm_cluster_cols = [Symbol("$(GCM)_management_area_clusters") for GCM i
 bioregion_gcm_cluster_cols = [Symbol("$(GCM)_bioregion_clusters") for GCM in GCMs]
 gbr_gcm_cluster_cols = [Symbol("$(GCM)_gbr_clusters") for GCM in GCMs]
 analysis_layers_long = stack(
-    context_layers[:, [:UNIQUE_ID, :management_area, gbr_gcm_cluster_cols...]], 
-    gbr_gcm_cluster_cols
+    context_layers[:, [:UNIQUE_ID, :management_area, man_area_gcm_cluster_cols...]], 
+    man_area_gcm_cluster_cols
 )
 analysis_layers_long.GCM = [first(split(name, "_")) for name in analysis_layers_long.variable]
 
[…]

### 2025-05-30 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -1,0 +1,109 @@
+"""
+Script to create additional plots required for publication.
+"""
+
+using Revise, Infiltrator
+
+using GLMakie, GeoMakie, GraphMakie
+using Statistics
+using YAXArrays
+using CairoMakie
+
+using ADRIA
+
+import GeometryOps as GO
+
+include("../../common.jl")
+include("../../plotting_functions.jl")
+
+CairoMakie.activate!()
+
+context_layers = GDF.read("../outputs/ADRIA_results/HighResCoralStress/analysis_context_layers.gpkg")
+
+# ECS plot - methods
+ecs_values = Dict(
+    "EC-Earth3-Veg" => 4.31,
+    "ACCESS-ESM1-5" => 3.87,
+    "ACCESS-CM2" => 4.72,
+    "GFDL-CM4" => 2.9,
+    "NorESM2-MM" => 2.5
+)
+ecs = ecs_plot(collect(values(ecs_values)), [2.5,5.1], [2.1,7.7], collect(keys(ecs_values)))
+save("../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png", ecs, px_per_unit = 300/inch)
+
+# GBR map plot - methods
+investigation_reefs = context_layers[
+    (context_layers.management_area .!= "NA") .& 
+    (context_layers.bioregion .!= "NA"),
+:]
+regions = GDF.read("../data/GBRMPA_Management_Areas.gpkg")
+regions.region_name = ["Mackay/Capricorn", "Cairns/Cooktown", "Far Northern", "Townsville Whitsunday"]
+qld = GDF.read("../data/GBRMPA_Reef_Features.gpkg")
+qld = qld[qld.FEAT_NAME .== "Mainland", :SHAPE]
+
+map_width = fig_sizes["map_width"]
+map_height = fig_sizes["map_height"]
+region_col = tuple.(Makie.wong_colors()[1:4], repeat([0.3], 4)) # Manually set alpha value to 0.3
+
+ordered_reefs = sort(investigation_reefs, :bioregion_average_latitude; rev=true)
+bioregion_colors_labels = DataFrame(
+    bioregion = unique(investigation_reefs.bioregion),
+    ref = 1:length(unique(investigation_reefs.bioregion)),
+    color = distinguishable_colors(length(unique(investigation_reefs.bioregion))),
+    label = label_lines.((unique(investigation_reefs.bioregion)); l_length=17)
+)
[…]

### 2025-05-30 src/plotting_functions.jl

@@ -22,240 +22,10 @@ fontsize = fontsize["fontsize"] * pt
 inch = 96 # size of 1 inch in pixels
 dpi = 300 / inch
 
-function _convert_plottable(gdf::Union{DataFrame,DataFrameRow}, geom_col::Symbol)
-    local plottable
-    try
-        if gdf isa DataFrame
-            plottable = GeoMakie.geo2basic(AG.forceto.(gdf[!, geom_col], AG.wkbPolygon))
-        else
-            plottable = GeoMakie.geo2basic(AG.forceto(gdf[geom_col], AG.wkbPolygon))
-        end
-    catch
-        # Column is already in a plottable form, or some unrelated error occurred
-        if gdf isa DataFrame
-            plottable = gdf[:, geom_col]
-        else
-            plottable = [gdf[geom_col]]
-        end
-    end
-
-    return plottable
-end
-
-"""
-    plot_map(gdf::DataFrame; geom_col::Symbol=:geometry, color_by::Symbol)
-
-Convenience plot function.
-
-# Arguments
-- `gdf` : GeoDataFrame
-- `color_by` : Column name holding factor to color reefs by (e.g. :management_area)
-- `geom_col` : Column name holding geometries to plot
-"""
-function plot_map(gdf::Union{DataFrame,DataFrameRow}; geom_col::Symbol=:geometry)
-    f = Figure(; size=(600, 900))
-    ga = GeoAxis(
-        f[1, 1];
-        dest="+proj=latlong +datum=WGS84",
-        xlabel="Longitude",
-        ylabel="Latitude",
-        xticklabelpad=15,
-        yticklabelpad=40,
-        xticklabelsize=10,
-        yticklabelsize=10,
-        aspect=AxisAspect(0.75),
-        xgridwidth=0.5,
-        ygridwidth=0.5,
-    )
-
-    plottable = _convert_plottable(gdf, geom_col)
-    poly!(ga, plottable)
-
-    display(f)
-
-    return f, ga
-end
-
-function plot_map!(ga::GeoAxis, gdf::DataFrame; geom_col=:geometry, color=nothing)::Nothing
-
-    plottable = _convert_plottable(gdf, geom_col)
-    if !isnothing(color)
-        poly!(ga, plottable, color=color)
-    else
-        poly!(ga, plottable)
-    end
-
-    # Set figure limits explicitly
-    xlims!(ga)
-    ylims!(ga)
-
-    return nothing
-end
-
[…]

### 2025-06-05 paper/paper_draft.qmd
Edit citation formatting and add config file for paper-specific sizes

@@
 Climate change is impacting species survival, persistence and ecosystem functions globally, including coral.
-Coral reefs are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading ([@foster2021]; [@gattuso2014]).
-Mass bleaching and mortality events linked to climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts ([@arif2022]; [@wild2011]).
-Climate impacts on coral reefs are, and will continue to, decrease the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling ([@forster2021]; [@williams2019]) as well as ecosystem services such as food, protection, tourism and Indigenous cultural value ([@eddy2021]; [@stoeckl2021]).
+Coral reefs are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading [@foster2021; @gattuso2014].
+Mass bleaching and mortality events linked to climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
+Climate impacts on coral reefs are, and will continue to, decrease the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well as ecosystem services such as food, protection, tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
 We aim to assess the impacts of possible climate futures and identify the characteristics of resilient reefs using the latest generation of larval connectivity research with scenario-based population modelling for the Great Barrier Reef ecosystem.
@@
 The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of thousands of individual reefs.
-They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes ([@grimaldi2022]).
-Severe declines in coral cover are projected due to compounding impacts such as ocean warming and acidification, intensification of Tropical Cyclones, and Crown of Thorns Starfish outbreaks ([@death2012]; [@fox-kemper2021]; [@seneviratne2021]; [@sweatman2011]; [@wolff2018]).
+They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@grimaldi2022].
+Severe declines in coral cover are projected due to compounding impacts such as ocean warming and acidification, intensification of Tropical Cyclones, and Crown of Thorns Starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
 Ominously, the 2023-24 Summer mass bleaching event ([@cantin2024]) may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs.
@@
 Environmental abiotic factors influence how reefs will experience climate change pressures, including the spatio-temporal patterns of thermal stress itself, and indirect factors that influence the stress experienced by corals.
-Environmental factors such as tropical cyclones and wind driven mixing ([@lin2023]; [@mcclanahan2005]); currents ([@grimaldi2022]) and depth ([@álvarez-noriega2018]; [@baird2018]; [@smith2014]) can decrease the magnitude of thermal stress corals experience.
-On the other hand, high light intensity and nutrient levels in the benthic zone can increase coral bleaching ([@decarlo2020]; [@higuchi2015]).
+Environmental factors such as tropical cyclones and wind driven mixing [@lin2023; @mcclanahan2005]; currents [@grimaldi2022] and depth [@álvarez-noriega2018; @baird2018; @smith2014] can decrease the magnitude of thermal stress corals experience.
+On the other hand, high light intensity and nutrient levels in the benthic zone can increase coral bleaching [@decarlo2020; @higuchi2015].
 These environmental factors influence the resilience of reefs to climate change pressures in combination with related biological factors such as larval connectivity and thermal tolerance.
 
-Connectivity in systems such as the GBR is an important contributor to system resilience, as strong connections are required to repopulate locations after disturbance, and drive adaptation to climate pressures ([@angeler2023]; [@elmhirst2009]; [@hock2017]).
+Connectivity in systems such as the GBR is an important contributor to system resilience, as strong connections are required to repopulate locations after disturbance, and drive adaptation to climate pressures [@angeler2023; @elmhirst2009; @hock2017].
 When populations that are strong larval suppliers to external reefs are impacted by disturbances, increased adult coral mortality will cause decreased outgoing larvae in the following years.
-Weaker larval connections then slow the recovery of the externally connected locations ([@figueiredo2022]; [@hock2017]; [@munday2009]).
-Populations with greater strength and number of outgoing than incoming larval connections - herein referred to as larval sources - have lower resilience to pressures than populations with greater incoming than outgoing larval flows - referred to as larval sinks - as larval source populations lack external sources of larvae that are important in contributing to reef recovery and recruitment of juveniles after disturbances to existing populations ([@ani2024]; [@hock2017]).
-Larval source populations are an important component of overall reef resilience as they can contribute larvae to recovering populations at other locations ([@hock2017]; [@thomas2015]).
-Connectivity will be altered by future climate change impacts such as population fragmentation, increasing larval mortality, and changes to coastal hydrodynamics ([@figueiredo2022]; [@munday2009]), and influences the biology of surrounding reef populations.
-
-Many additional biological factors including coral size ([@brandt2009]), taxa ([@álvarez-noriega2018]; [@mcclanahan2005]), and acclimation and inherited thermal tolerance ([@humanes2022]; [@lachs2024]), influence the outcome of high coral heat stress.
-It has been shown that corals have the adaptive capacity to develop thermal tolerance levels capable of delaying the onset of widespread bleaching under low emissions scenarios ([@bairos-novak2021]; [@humanes2022]).
+Weaker larval connections then slow the recovery of the externally connected locations [@figueiredo2022; @hock2017; @munday2009].
+Populations with greater strength and number of outgoing than incoming larval connections - herein referred to as larval sources - have lower resilience to pressures than populations with greater incoming than outgoing larval flows - referred to as larval sinks - as larval source populations lack external sources of larvae that are important in contributing to reef recovery and recruitment of juveniles after disturbances to existing populations [@ani2024; @hock2017].
+Larval source populations are an important component of overall reef resilience as they can contribute larvae to recovering populations at other locations [@hock2017; @thomas2015].
+Connectivity will be altered by future climate change impacts such as population fragmentation, increasing larval mortality, and changes to coastal hydrodynamics [@figueiredo2022; @munday2009], and influences the biology of surrounding reef populations.
+
+Many additional biological factors including coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and acclimation and inherited thermal tolerance[@humanes2022; @lachs2024], influence the outcome of high coral heat stress.
+It has been shown that corals have the adaptive capacity to develop thermal tolerance levels capable of delaying the onset of widespread bleaching under low emissions scenarios [@bairos-novak2021; @humanes2022].
 
 Incorporating the latest advancements in whole ecosystem larval connectivity modelling and coral thermal response and adaptation research into coral population modelling allows us to investigate how these abiotic and biotic factors interact and will influence coral climate change resilience into the future.
-Improvements in coral reef climate response modelling, including sampling from a range of possible climate futures, allow for fine-scale timeseries analyses of uncertain climate change and ecological scenarios ([@bode2017]; [@chollett2022]; [@donner2018]; [@klein2024]; [@uusitalo2015]).
+Improvements in coral reef climate response modelling, including sampling from a range of possible climate futures, allow for fine-scale timeseries analyses of uncertain climate change and ecological scenarios [@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].
 
@@
 ## Environmental modelling context
+
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points).
@@
 The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas.
-It follows the reef definitions as adopted in ReefMod-GBR ([@bozec2022]) (@fig-region-map).
+It follows the reef definitions as adopted in ReefMod-GBR [@bozec2022] (@fig-region-map).
 Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future thermal stress at each reef location.
 Five Global Climate Models (GCMs) (EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6) were selected for this study.
-Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great Barrier Reef were obtained from the HighResCoralStress database ([@dixon2022][@dixon]).
-Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology ([@liu2017]; [@skirving2020]).
+Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great Barrier Reef were obtained from the HighResCoralStress database [@dixon2022; @dixon].
+Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology [@liu2017; @skirving2020].
 These GCMs were selected from available GCMs downscaled by Dixon et al.
@@
 [-@grose2023], which found high correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms in these GCMs.
-Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming caused by a doubling of carbon dioxide above its pre-industrial concentration ([@forster2021]).
-The four GCMs span a range of ECS values within the IPCC assessed likely range, and GCM development families, allowing for a range of possible climate futures to be explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs; [@grose2023]; [@shepherd2018]).
+Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming caused by a doubling of carbon dioxide above its pre-industrial concentration [@forster2021].
+The four GCMs span a range of ECS values within the IPCC assessed likely range, and GCM development families, allowing for a range of possible climate futures to be explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs; [@grose2023; @shepherd2018]).
 The following analyses are performed using each GCM separately.
-SSP 2-4.5 is used as a plausible emission pathway under current emission trajectories, with similar atmospheric CO2 levels remaining until 2050 ([@hausfather2020]; IPCC [-@climate2023]).
+SSP 2-4.5 is used as a plausible emission pathway under current emission trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020; IPCC -@climate2023].
 
@@
 
-CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time ([@ribeirodealmeida2024]).
+CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time [@ribeirodealmeida2024].
 This model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
 Environmental disturbances and reproduction are not directly considered within CoralBlox.
-Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform ([@iwanaga2023]).
+Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
 Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
@@
 To quantify the behaviour of timeseries and identify timeseries that behave similarly we calculate the complexity-invariant distance (CID) between each timeseries.
-The complexity-invariant distance refers to the Euclidean distance between two timeseries multiplied (corrected) by the ratio of the complexities of the timeseries ([@batista2014]).
-These values create a distance matrix of n * n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm ([@steinmann2020]).
+The complexity-invariant distance refers to the Euclidean distance between two timeseries multiplied (corrected) by the ratio of the complexities of the timeseries [@batista2014].
+These values create a distance matrix of n * n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm [@steinmann2020].
 
@@
 
-At management area analysis scales, there are not consistent substantial differences in source – to – sink ratios (@sfig-access-esm1-5-manarea-logsosi; @sfig-access-cm2-manarea-logsosi; @sfig-ec-earth3-veg-manarea-logsosi; @sfig-gfdl-cm4-manarea-logsosi; @sfig-noresm2-mm-manarea-logsosi) and total connectivity strength (@sfig-access-esm1-5-manarea-totalconnectivity; @sfig-access-cm4-manarea-totalconnectivity; @sfig-ec-earth3-veg-manarea-totalconnectivity; @sfig-gfdl-cm4-manarea-totalconnectivity; @sfig-noresm2-mm-manarea-totalconnectivity).
+At management area analysis scales, there are not consistent substantial differences in source – to – sink ratios (@sfig-access-esm1-5-manarea-logsosi; @sfig-access-cm2-manarea-logsosi; @sfig-ec-earth3-veg-manarea-logsosi; @sfig-gfdl-cm4-manarea-logsosi; @sfig-noresm2-mm-manarea-logsosi) and total connectivity strength (@sfig-access-esm1-5-manarea-totalconnectivity; @sfig-access-cm2-manarea-totalconnectivity; @sfig-ec-earth3-veg-manarea-totalconnectivity; @sfig-gfdl-cm4-manarea-totalconnectivity; @sfig-noresm2-mm-manarea-totalconnectivity).
 
@@
 Reef depth (@fig-access-esm1-5-gbr-depth; @sfig-access-cm2-gbr-depth; @sfig-ec-earth3-veg-gbr-depth; @sfig-gfdl-cm4-gbr-depth; @sfig-noresm2-mm-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor; @sfig-access-cm2-gbr-dhwcor; @sfig-ec-earth3-veg-gbr-dhwcor; @sfig-gfdl-cm4-gbr-dhwcor; @sfig-noresm2-mm-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion; @sfig-access-cm2-gbr-initialproportion; @sfig-ec-earth3-veg-gbr-initialproportion; @sfig-gfdl-cm4-gbr-initialproportion; @sfig-noresm2-mm-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels.
-There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean; @sfig-access-cm4-gbr-dhwmean; @sfig-ec-earth3-veg-gbr-dhwmean; @sfig-gfdl-cm4-gbr-dhwmean; @sfig-noresm2-mm-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol; @sfig-access-cm2-gbr-dhwtol; @sfig-ec-earth3-veg-gbr-dhwtol; @sfig-gfdl-cm4-gbr-dhwtol; @sfig-noresm2-mm-gbr-dhwtol) levels of reefs.
+There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean; @sfig-access-cm2-gbr-dhwmean; @sfig-ec-earth3-veg-gbr-dhwmean; @sfig-gfdl-cm4-gbr-dhwmean; @sfig-noresm2-mm-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol; @sfig-access-cm2-gbr-dhwtol; @sfig-ec-earth3-veg-gbr-dhwtol; @sfig-gfdl-cm4-gbr-dhwtol; @sfig-noresm2-mm-gbr-dhwtol) levels of reefs.
 Similarly, there are no substantial differences between clusters in connectivity metrics source – to – sink ratio and total connectivity strength (@sfig-access-esm1-5-gbr-logsosi; @sfig-access-cm2-gbr-logsosi; @sfig-ec-earth3-veg-gbr-logsosi; @sfig-gfdl-cm4-gbr-logsosi; @sfig-noresm2-mm-gbr-logsosi; @sfig-access-esm1-5-gbr-totalconnectivity; @sfig-access-cm2-gbr-totalconnectivity; @sfig-ec-earth3-veg-gbr-totalconnectivity; @sfig-gfdl-cm4-gbr-totalconnectivity; @sfig-noresm2-mm-gbr-totalconnectivity).
@@
 Our results suggest that within shallow reef ecosystems (depth < 30m), depth contributes greatly to reef resilience and the ability of the reef to recover following heat stress.
-While similar findings have been demonstrated in the eastern Pacific ([@smith2014]), depth refugia analyses have often focussed on the potential of mesophotic reefs (> 30m deep) as thermal refugia ([@bongaerts2010]; [@holstein2015]; [@semmler2017]).
+While similar findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses have often focussed on the potential of mesophotic reefs (> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017].
 In contrast, Venegas et al.
@@
 
-Current reef restoration and intervention-investigation efforts on the Great Barrier Reef, such as deployment of coral seeding and fragment devices target reefs with suitable restoration sites in the 1-10m depth range ([@howlett2021]; [@randall2021]; [@whitman2024]).
+Current reef restoration and intervention-investigation efforts on the Great Barrier Reef, such as deployment of coral seeding and fragment devices target reefs with suitable restoration sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024].
 One of the main depth constraints is being able to visually identify the target site from the surface for deployment and ongoing monitoring, in combination with factors such as deployment method and tourism return value.
 Our results suggest that of the reefs analysed within the 1-10m depth range (1800) 87% (1569) of reefs fall into the low and medium clusters (at the Great Barrier Reef scale), with many suffering large future declines in reef health under climate change and possibly limiting the potential of interventions to deliver recovery in these locations.
-Reef intervention planning is a complex and challenging decision making process ([@anthony2020]), and our results suggest that deployment site depth is likely an important factor to consider when assessing the long-term resilience of reef sites.
+Reef intervention planning is a complex and challenging decision making process [@anthony2020], and our results suggest that deployment site depth is likely an important factor to consider when assessing the long-term resilience of reef sites.
 
 Overall, our findings do not suggest that resilient reefs in ‘high’ cover clusters have greater thermal tolerance than reefs in lower coral cover clusters.
-This is in contrast with literature suggesting corals have the capacity to adapt to increasing climate change pressures ([@humanes2022]; [@lachs2024]), including the investigation by Bairos-Novak et al.
+This is in contrast with literature suggesting corals have the capacity to adapt to increasing climate change pressures [@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
 [-@bairos-novak2021] that revealed high heritability of bleaching and survival response traits used to inform the distributions of thermal tolerance traits used in this investigation.
@@
 
-It has been suggested that a primary facet of reef resilience is the degree of larval connectivity between reefs and the supply of recruits that a reef receives following disturbance ([@hock2017]).
+It has been suggested that a primary facet of reef resilience is the degree of larval connectivity between reefs and the supply of recruits that a reef receives following disturbance [@hock2017].
 It was expected that resilient reefs would have greater incoming than outgoing larval connectivity to promote recovery in years following thermal stress, while non-resilient reefs would have greater outgoing than incoming connectivity inhibiting recruitment of corals ability post thermal stress.
@@
 Hock et al.
-([-@hock2017]) used larval connectivity modelling to identify resilient reefs that may supply up to 47% of the wider Great Barrier Reef ecosystem with larvae following disturbance.
-A critique of this approach ([@bode2018]) is that results obtained are highly sensitive to the biophysical dispersal model used, limiting the application of specific identified reefs.
+[-@hock2017] used larval connectivity modelling to identify resilient reefs that may supply up to 47% of the wider Great Barrier Reef ecosystem with larvae following disturbance.
+A critique of this approach [@bode2018] is that results obtained are highly sensitive to the biophysical dispersal model used, limiting the application of specific identified reefs.
 Reef depth was not considered in these investigations of reef network resilience.
-These investigations were performed using prior generations of larval connectivity models parameterised for 2008-2013 ([@hock2017]) and 1996-2002 ([@bode2018]) time periods respectively.
+These investigations were performed using prior generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods respectively.
 Using updated 1km resolution larval connectivity across the whole GBR, our results suggest that larval connectivity alone is not as important for reef resilience and recovery as environmental refugia from thermal stress such as depth.
@@
 The large differences in relative cover timeseries seen across the GCMs suggest that it is important to consider this uncertainty in analyses of biological climate change responses.
-This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model climate change responses using a range of climate models separately ([@shepherd2018]).
+This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model climate change responses using a range of climate models separately [@shepherd2018].
 However, the patterns identified between low, medium and high clusters of reefs suggest that the importance of depth refugia is consistent across scenarios.
@@
 To limit the influence of bathymetry data on results, reefs with less than 5% data coverage are removed from analyses.
-We investigate a range of future climate responses and thermal projections, and our results suggest the factors that influence reef resilience are consistent across the tested futures.
-
-Further investigations could...
+We investigate a range of future climate responses and thermal projections to account for a range of possible futures, and our results suggest the factors that influence reef resilience are consistent across these scenarios.
+
+Further analyses could build on the findings of this study by analysing the impacts of prioritising reef depth in reef restoration intervention decision making.
+The ADRIA platform is developed as a modelling tool to incorporate multi-criteria decision analysis (MCDA) and ecosystem scenario modelling into reef restoration decision analysis.
+The platform allows for the investigation of different reef characteristics to be targetted in decision making and models the evolving outcomes as a result of reef interventions at various locations.
+The capability of ADRIA-CoralBlox could be further expanded by incorporating the impacts of waves, cyclones, CoTS and currents into reef resilience investigations [@lin2023; @mcclanahan2005; @grimaldi2022; @liu2024].
 
@@
 We provide evidence in support of depth as a form of refugia for shallow reefs.
-While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts ([@anthony2020]; [@hock2017]), our results suggest that resilient reefs do not have greater incoming or total connectivity to contribute to their resilience.
+While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts [@anthony2020; @hock2017], our results suggest that resilient reefs do not have greater incoming or total connectivity to contribute to their resilience.
 Instead, we suggest that depth, and likely other environmental thermal refugia mechanisms contribute greater to overall reef resilience and recovery.
-Further investigation could utilise the scenario modelling and dynamic intervention capabilities of the ADRIA platform to explore the effectiveness of prioritising reef depth compared to larval connectivity in reef intervention decision making.
+We suggest further analyses that investigate the benefits of incorporating depth-based resilience into reef decision making.
 
@@
 ## Model parameterisation
+
 CoralBlox uses user-defined size classes that influence size-dependent growth and mortality rates, through which the coral colonies progress as they grow in diameter.
-Within ADRIA, we define the distributions of these parameters, and the size classes based on ecological monitoring data from the Ecological Intelligence for Reef Restoration Program (EcoRRAP) ([@australian-institute-of-marine-science2025]; [@ribeirodealmeida2024]).
+Within ADRIA, we define the distributions of these parameters, and the size classes based on ecological monitoring data from the Ecological Intelligence for Reef Restoration Program (EcoRRAP) ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
 
 ## ACCESS-ESM1-5
+
 ### Bioregion scale
+
 ![Reef relative coral cover timeseries clustered within each bioregion.
@@
 ### Management area scale
+
 ![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
@@
 ## ACCESS-CM2
+
 ### Bioregion scale
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries width=`{julia} timeseries_width`}
+
 ![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 
-![Reef relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries width=`{julia} timeseries_width`}
-
 ![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 ### Management area scale
+
 ![Reef relative coral cover timeseries clustered within each management area.
@@
 ### GBR scale
+
 ![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
@@
 ## EC-Earth3-Veg
+
 ### Bioregion scale
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries width=`{julia} timeseries_width`}
+
 ![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 
-![Reef relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries width=`{julia} timeseries_width`}
-
 ![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 ## GFDL-CM4
+
 ### Bioregion scale
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries width=`{julia} timeseries_width`}
+
 ![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 
-![Reef relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries width=`{julia} timeseries_width`}
-
 ![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 ## NorESM2-MM
+
 ### Bioregion scale
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries width=`{julia} timeseries_width`}
+
 ![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 
-![Reef relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries width=`{julia} timeseries_width`}
-
 ![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.

### 2025-06-05 src/plotting_functions.jl

@@ -280,9 +280,9 @@ function grouped_cluster_timeseries_plots(
     grouping,
     length_t;
     fig_sizes=fig_sizes,
-    fontsize=fontsize
+    fontsize=fontsize,
+    ytitle=""
 )
-
     fig_x_size = fig_sizes["timeseries_width"]
     fig_y_size = fig_sizes["timeseries_height"]
     n_col = optimum_columns(length(unique(dataframe[:, grouping])))
@@ -315,6 +315,7 @@ function grouped_cluster_timeseries_plots(
             clusters;
             opts = Dict{Symbol, Any}(:legend => false),
             axis_opts = Dict(
+                :ylabel => ytitle,
                 :title => labels[xi], 
                 :xticks => (
                     first(length_t):10:last(length_t), 
@@ -327,10 +328,14 @@ function grouped_cluster_timeseries_plots(
     end
 
     axes_after_1 = filter(x -> x isa Axis, fig.content)[2:end]
-    map(x -> hidexdecorations!(x, grid=true), axes_after_1)
+    map(x -> hidexdecorations!(x; grid = false, ticks = false), axes_after_1)
+    map(x -> hideydecorations!(x, ticks = false, ticklabels = false, grid = false, label = false), axes_after_1)
 
-    rowgap!(fig.layout, 5)
-    colgap!(fig.layout, 5)
+    if grouping == :bioregion
+        rowgap!(fig.layout, 5)
+        colgap!(fig.layout, 5)
+        map(x -> colsize!(fig.layout, x, Relative(1 / n_col)), 1:n_col)
+    end
 
     # resize_to_layout!(fig)
     display(fig)
@@ -563,7 +568,7 @@ function cluster_analysis_plots(
 
     overlap = 0.8
     # Filter out groups that don't have 3 clusters due to earlier filtering.
-    groups_too_few_clusters = grouping_counts(grouping, analysis_layers, "$(GCM)_$(grouping)_clusters", 3, 7)
+    groups_too_few_clusters = grouping_counts(grouping, analysis_layers, "$(GCM)_$(grouping)_clusters", 3, 5)
     analysis_layers = analysis_layers[analysis_layers[:, grouping] .∉ [groups_too_few_clusters], :]
     rel_cover = rel_cover = rel_cover[:, rel_cover.locations .∈ [analysis_layers.UNIQUE_ID]]
     dhw_ts = dhw_ts[:, dhw_ts.locations .∈ [rel_cover.locations]]
[…]

### 2025-06-23 paper/paper_draft.qmd
Add analysis based on cover as a percentage of reef area

@@
 Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
-Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality as it is assumed the high background mortality of juveniles includes thermal stress.
+Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality.
+There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
 

### 2025-06-23 src/ADRIA/HighResCoralStress/2_1_timeseries_clustering_carbonate.jl

@@ -165,7 +165,8 @@ for GCM in dhw_scenarios.dhw.properties["members"]
     GCM_results = GCM_analysis_results(rs)
     absolute_cover = GCM_results.absolute_median_cover
 
-    threshold_cover = threshold_cover_timeseries(areas, absolute_cover, 0.17)
+    # threshold_cover = threshold_cover_timeseries(areas, absolute_cover, 0.17)
+    threshold_cover = percentage_cover_timeseries(areas, absolute_cover)
 
     (bioregion_clusters, bioregion_cluster_cats) = grouped_timeseries_clustering(threshold_cover.data, context_layers.bioregion; n_clusters=n_clusters, length_t=1:50)
     (man_region_clusters, man_region_cluster_cats) = grouped_timeseries_clustering(threshold_cover, context_layers.management_area; n_clusters=n_clusters, length_t=1:50)
@@ -181,3 +182,8 @@ for GCM in dhw_scenarios.dhw.properties["members"]
 end
 
 GDF.write("../outputs/ADRIA_results/HighResCoralStress/bellwether_reefs_carbonate.gpkg", context_layers)
+
+# threshold_cover = absolute_cover
+# for loc in eachindex(absolute_cover.locations)
+#     threshold_cover[:, loc] = normalise(threshold_cover[:, loc], (0,1))
+# end

### 2025-06-23 src/ADRIA/HighResCoralStress/4_1_analysis_and_plots_clustering_carbonate.jl

@@ -16,12 +16,13 @@ CairoMakie.activate!()
 dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
 GCMs = dhw_scenarios.dhw.properties["members"]
 
-context_layers = GDF.read("../outputs/ADRIA_results/HighResCoralStress/analysis_context_layers.gpkg")
+context_layers = GDF.read("../outputs/ADRIA_results/HighResCoralStress/analysis_context_layers_carbonate.gpkg")
 context_layers.gbr .= "Great Barrier Reef"
 context_layers.log_so_to_si = log10.(context_layers.so_to_si)
 context_layers.log_total_strength = log10.(context_layers.total_strength)
 
 gbr_dom = ADRIA.load_domain("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/", "45")
+areas = gbr_dom.loc_data.area
 
 for (i_gcm, GCM) in enumerate(GCMs)
     # Select GCM and load relevant results
@@ -31,10 +32,9 @@ for (i_gcm, GCM) in enumerate(GCMs)
 
     rs = ADRIA.load_results("../outputs/ADRIA_results/HighResCoralStress/GBR_2024_10_15_HighResCoralStress__RCPs_45_$(GCM)")
     GCM_results = GCM_analysis_results(rs)
-    rel_cover = GCM_results.relative_cover
-
-    rel_cover_less_than_5 = [all(rel_cover[:, i].data .< 5) for i in 1:size(rel_cover, 2)]
-    rel_cover_less_than_5_ind = findall(rel_cover_less_than_5)
+    absolute_cover = GCM_results.absolute_median_cover
+    # threshold_cover = threshold_cover_timeseries(areas, absolute_cover, 0.17)
+    threshold_cover = percentage_cover_timeseries(areas, absolute_cover)
 
     dhw_ts = gbr_dom.dhw_scens[:,:,i_gcm]
     ax = (
@@ -44,13 +44,12 @@ for (i_gcm, GCM) in enumerate(GCMs)
     dhw_ts = rebuild(dhw_ts, dims=ax)
 
     # Subset layers to remove reefs that start with very low coral cover
-    analysis_layers = context_layers[rel_cover_less_than_5, :]
[…]

### 2025-06-23 src/common.jl

@@ -706,3 +706,25 @@ function threshold_cover_timeseries(areas, cover_timeseries, threshold)
 
     return threshold_cover
 end
+
+function percentage_cover_timeseries(areas, cover_timeseries)
+    props = Dict(
+        :metric_feature => "Cover",
+        :axes_names => ["timesteps", "locations"],
+        :metric_name => "Cover of reef area",
+        :axes_units => ["years", ""],
+        :is_relative => true,
+        :metric_unit => "%"
+    )
+    percentage_cover = YAXArray(
+        (cover_timeseries.timesteps, cover_timeseries.locations),
+        zeros(size(cover_timeseries)), props
+    )
+
+    for loc in eachindex(areas)
+        percentage_cover[:, loc] = cover_timeseries[:, loc] ./ areas[loc] .* 100
+    end
+
+    return percentage_cover
+end
+

### 2025-06-23 src/plotting_functions.jl

@@ -585,17 +585,17 @@ function cluster_analysis_plots(
         px_per_unit = dpi
     )
 
-    dhw_tol_violin = grouped_cluster_ridgeline_plot(
-        analysis_layers,
-        Symbol("$(GCM)_$(grouping)_clusters"),
-        grouping, Symbol("$(GCM)_mean_DHW_tol");
-        xlabel="mean reef DHW tolerance", ylabel="$(grouping_fn)", overlap = overlap
-    )
-    save(
-        joinpath(fig_out_dir, "$(grouping)", "dhw_tolerance_$(grouping)_violin.png"),
-        dhw_tol_violin,
-        px_per_unit = dpi
-    )
+    # dhw_tol_violin = grouped_cluster_ridgeline_plot(
+    #     analysis_layers,
+    #     Symbol("$(GCM)_$(grouping)_clusters"),
+    #     grouping, Symbol("$(GCM)_mean_DHW_tol");
+    #     xlabel="mean reef DHW tolerance", ylabel="$(grouping_fn)", overlap = overlap
+    # )
+    # save(
+    #     joinpath(fig_out_dir, "$(grouping)", "dhw_tolerance_$(grouping)_violin.png"),
+    #     dhw_tol_violin,
+    #     px_per_unit = dpi
+    # )
 
     so_to_si_violin = grouped_cluster_ridgeline_plot(
         analysis_layers,
@@ -722,6 +722,7 @@ function grouped_GCM_cluster_timeseries_plots(
     labels = label_lines.("$(first(df.management_area)) - $(first(df.GCM))" for df in gdf; l_length=15)
 
     for (xi, groupdf) in enumerate(gdf)
+        # println("$(xi)")
         plot_layout_xi = plot_layout[xi]
         groupdf = sort(groupdf, cluster_col)
 
@@ -731,9 +732,9 @@ function grouped_GCM_cluster_timeseries_plots(
         group_timeseries = group_timeseries[locations = (group_timeseries.locations .∈ [groupdf.UNIQUE_ID])]
         group_timeseries = group_timeseries[length_t, indexin(groupdf.UNIQUE_ID, String.(group_timeseries.locations))]
         
-        group_timeseries_less_than_5 = [all(group_timeseries[:, i].data .< 5) for i in 1:size(group_timeseries, 2)]
-        group_timeseries_less_than_5_ind = findall(group_timeseries_less_than_5)
-        group_timeseries = group_timeseries[:, group_timeseries_less_than_5_ind]
[…]

### 2025-06-26 paper/paper_draft.qmd
Add carbonate budget analysis plots and clean up notes on scripts

@@
 violin_width = fig_sizes["violin_width"]
+carb_width = fig_sizes["carb_width"]
 ```
@@
 
-ADRIA output absolute coral cover was used to calculate relative coral cover (relative to initial cover), a reef’s absolute coral cover at each timestep divided by initial coral cover.
-Initial coral cover is consistent throughout all simulated and GCM scenarios.
-To limit the influence of reefs with very low initial cover on the results, reefs with future total cover levels that exceed five times their initial cover level were removed from clustering and further analyses.
+ADRIA-CoralBlox was run for 4096 *sampled* scenarios per GCM.
+A median absolute coral cover timeseries for each reef was calculated for each GCM.
+For use in timeseries clustering reef cover timeseries were scaled by the total area of the reef to represent timeseries as a percentage of total reef area (range 0 - 100%).
 The proportion of each functional group occupying the reef (taxa evenness) was also investigated as a metric for timeseries analysis, but was found to not sufficiently capture the declining condition of reefs suffering from very low absolute coral cover.
@@
 Timeseries analysis is performed by first grouping reefs into three different scales, GBRMPA reefal bioregion, GBRMPA management area and GBR-wide, to investigate the consistency of cluster identification.
-To identify groups of reefs at each analysis scale that are resilient, intermediate and non-resilient we clustered reef relative coral cover timeseries into three clusters at each scale.
+To identify groups of reefs at each analysis scale that are resilient, intermediate and non-resilient we clustered reef coral cover timeseries into three clusters at each scale.
 To quantify the behaviour of timeseries and identify timeseries that behave similarly we calculate the complexity-invariant distance (CID) between each timeseries.
@@
 These values create a distance matrix of n * n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm [@steinmann2020].
+
+## Carbonate budget analysis
+
+To maintain coral cover over time coral reefs require a threshold of coral cover known as a carbonate budget.
+Estimates of the carbonate budget required to maintain a healthy coral reef range from 10 to 20% of a reef's total area.
+Using median absolute cover timeseries for each reef we calculated the number of years each reef maintains coral cover above a carbonate budget threshold level.
+Threshold values from 10 to 20% (inclusive) were used in analyses.
 
@@
 
+## Reef carbonate budget
+The number of years reefs maintain coral cover above a required carbonate budget level substantially decreases as the required carbonate budget threshold (as a percentage of reef area) increases.
+Reefs with greater median depth levels maintain coral cover above required carbonate budget levels for longer than reefs at shallow depths [@fig-access-esm1-5-depth-carbonate].
+There are no clear relationships between reef total connectivity levels and the number of years reefs maintain coral cover above carbonate budget threshold levels [@sfig-access-esm1-5-conn-carbonate].
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Point colour represents the median reef depth level in metres.
+Displays results from median timeseries using ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate width=`{julia} carb_width`}
+
 ## Bioregion scale clustering
@@
 
-Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@fig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).
-
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW level for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
+Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).
 
@@
 The ‘high’ cover cluster of reefs contains reefs that have continuing recovery of corals throughout the future climate scenario.
-The medium and low clusters contain many reefs that decrease to half their initial coral cover levels and largely do not display the levels of recurring recovery that reefs in high clusters experience (@fig-access-esm1-5-manarea-timeseries; @sfig-access-cm2-manarea-timeseries; @sfig-ec-earth3-veg-manarea-timeseries; @sfig-gfdl-cm4-manarea-timeseries; @sfig-noresm2-mm-manarea-timeseries).
-
-![Reef relative coral cover timeseries clustered within each management area.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}
+The medium and low clusters contain many reefs that decrease to half their initial coral cover levels and largely do not display the levels of recurring recovery that reefs in high clusters experience (@sfig-access-esm1-5-manarea-timeseries; @sfig-access-cm2-manarea-timeseries; @sfig-ec-earth3-veg-manarea-timeseries; @sfig-gfdl-cm4-manarea-timeseries; @sfig-noresm2-mm-manarea-timeseries).
 
 Within each bioregion reef median depth level increases with increasing reef relative coral cover.
-Reefs in the low cluster have the lowest median depth levels, while reefs in the high cluster have the highest median depth levels within each management area (@fig-access-esm1-5-manarea-depth; @sfig-access-cm2-manarea-depth; @sfig-ec-earth3-veg-manarea-depth; @sfig-gfdl-cm4-manarea-depth; @sfig-noresm2-mm-manarea-depth).
-
-![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}
+Reefs in the low cluster have the lowest median depth levels, while reefs in the high cluster have the highest median depth levels within each management area (@sfig-access-esm1-5-manarea-depth; @sfig-access-cm2-manarea-depth; @sfig-ec-earth3-veg-manarea-depth; @sfig-gfdl-cm4-manarea-depth; @sfig-noresm2-mm-manarea-depth).
 
@@
 Timeseries clustering identified three clusters in reef relative cover timeseries for the whole GBR scale.
-A ‘low’ cluster of reefs with little recovery following initial declines, a medium cluster of reefs with median relative cover below 0.5 post 2028, and a high cluster of reefs with median relative cover above 0.5 until 2050 (@fig-access-esm1-5-gbr-timeseries; @sfig-access-cm2-gbr-timeseries; @sfig-ec-earth3-veg-gbr-timeseries; @sfig-gfdl-cm4-gbr-timeseries; @sfig-noresm2-mm-gbr-timeseries).
-
-![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
-The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
-The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
-The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}
+A ‘low’ cluster of reefs with little recovery following initial declines, a medium cluster of reefs with median relative cover below 0.5 post 2028, and a high cluster of reefs with median relative cover above 0.5 until 2050 (@sfig-access-esm1-5-gbr-timeseries; @sfig-access-cm2-gbr-timeseries; @sfig-ec-earth3-veg-gbr-timeseries; @sfig-gfdl-cm4-gbr-timeseries; @sfig-noresm2-mm-gbr-timeseries).
 
 The clusters identified with timeseries clustering at the GBR scale show similar patterns to clusters identified at bioregion and management area scales.
-Reef depth (@fig-access-esm1-5-gbr-depth; @sfig-access-cm2-gbr-depth; @sfig-ec-earth3-veg-gbr-depth; @sfig-gfdl-cm4-gbr-depth; @sfig-noresm2-mm-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor; @sfig-access-cm2-gbr-dhwcor; @sfig-ec-earth3-veg-gbr-dhwcor; @sfig-gfdl-cm4-gbr-dhwcor; @sfig-noresm2-mm-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion; @sfig-access-cm2-gbr-initialproportion; @sfig-ec-earth3-veg-gbr-initialproportion; @sfig-gfdl-cm4-gbr-initialproportion; @sfig-noresm2-mm-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels.
+Reef depth (@sfig-access-esm1-5-gbr-depth; @sfig-access-cm2-gbr-depth; @sfig-ec-earth3-veg-gbr-depth; @sfig-gfdl-cm4-gbr-depth; @sfig-noresm2-mm-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor; @sfig-access-cm2-gbr-dhwcor; @sfig-ec-earth3-veg-gbr-dhwcor; @sfig-gfdl-cm4-gbr-dhwcor; @sfig-noresm2-mm-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion; @sfig-access-cm2-gbr-initialproportion; @sfig-ec-earth3-veg-gbr-initialproportion; @sfig-gfdl-cm4-gbr-initialproportion; @sfig-noresm2-mm-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels.
 There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean; @sfig-access-cm2-gbr-dhwmean; @sfig-ec-earth3-veg-gbr-dhwmean; @sfig-gfdl-cm4-gbr-dhwmean; @sfig-noresm2-mm-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol; @sfig-access-cm2-gbr-dhwtol; @sfig-ec-earth3-veg-gbr-dhwtol; @sfig-gfdl-cm4-gbr-dhwtol; @sfig-noresm2-mm-gbr-dhwtol) levels of reefs.
@@
 
-![Median depth for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}
-
 # Discussion
@@
 Timeseries analysis has been used to identify three groups of reefs with similar declining (low), recovering (high), and intermediate (medium) coral cover trajectories throughout future scenarios.
-Throughout all analysis scales, reefs in high cover clusters exhibit spans of recovery up to 2050, while low and medium clusters commonly remain at levels below half their initial cover from 2030.
-Furthermore, at all analysis scales reef clusters show similar patterns in their reef characteristics such as depth and proportion of habitable area initially occupied.
-
-A key factor that influences the relative coral cover values on a reef is the initial total coral cover used to calculate the metric.
-This is seen where low and medium reefs have higher proportions of their coral-habitable area occupied by corals initially, while some high-cluster reefs exhibit absolute coral cover levels greater than their initial coral cover, leading to future relative cover values greater than one.
+Under all GCMs most reefs suffer substantial declines in coral cover from 2025 levels.
+NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintanance into the future.
+The differences between low, medium and high reef clusters in their timeseries are most notable under these two GCMs.
+At all analysis scales reef clusters show similar patterns in their reef characteristics such as depth and proportion of habitable area initially occupied.
 
@@
 [-@baird2018] is used to calculate the degree of protection provided to a reef based on the median depth.
-Our results suggest that within shallow reef ecosystems (depth < 30m), depth contributes greatly to reef resilience and the ability of the reef to recover following heat stress.
+Our results suggest that within shallow reef ecosystems (depth < 30m), depth contributes greatly to reef resilience and the ability of the reef to maintain cover under heat stress.
 While similar findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses have often focussed on the potential of mesophotic reefs (> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017].
@@
 [-@venegas2019] found no association between depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
-The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels.
+<!-- The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels.
 Reefs in low and medium clusters have lower levels of cover – DHW correlation than those in high clusters, due to their initial sharp declines in coral cover combined with low depth – refugia in the face of persistently high thermal stress these reefs do not recover post 2030, leaving little ability to decline further in periods of high thermal stress and recover in periods of low thermal stress.
+-->
 
@@
 One of the main depth constraints is being able to visually identify the target site from the surface for deployment and ongoing monitoring, in combination with factors such as deployment method and tourism return value.
-Our results suggest that of the reefs analysed within the 1-10m depth range (1800) 87% (1569) of reefs fall into the low and medium clusters (at the Great Barrier Reef scale), with many suffering large future declines in reef health under climate change and possibly limiting the potential of interventions to deliver recovery in these locations.
-Reef intervention planning is a complex and challenging decision making process [@anthony2020], and our results suggest that deployment site depth is likely an important factor to consider when assessing the long-term resilience of reef sites.
+Our results suggest that of the reefs analysed within the 1-10m depth range (1800 reefs) 74% (1328) of reefs fall into the low and medium clusters (across all GCMs at the GBRMPA management region scale), with many suffering large future declines in reef health under climate change and possibly limiting the potential of interventions to deliver recovery in these locations.
+Reef intervention planning is a complex and challenging decision making process [@anthony2020], and our results suggest that deployment site depth is an important factor to consider when assessing the long-term resilience of reef sites.
 
@@
 
+Furthermore, our results suggest that the capacity of reefs to maintain healthy coral habitat by being above positive net carbonate budget levels is greater for reefs at deeper depths than shallow depths.
+While the maintanence of positive carbonate budget levels does not appear to be influenced by reef connectivity metrics.
+The maintanence of positive carbonate budgets is important for reef resilience under climate change.
+
 Five different GCMs were included in analyses to capture uncertainty in climate system responses to increasing atmospheric carbon dioxide levels.
@@
 The capability of ADRIA-CoralBlox could be further expanded by incorporating the impacts of waves, cyclones, CoTS and currents into reef resilience investigations [@lin2023; @mcclanahan2005; @grimaldi2022; @liu2024].
+Additionally, the investigation could be enhanced by incorporating future ocean acidification into considerations of coral carbonate budgets required for healthy habitat production.
 
@@
 
+![Reef Degree Heating Week timeseries clustered within each management area, for each GCM analysed.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#fig-gcm-trajectories width=`{julia} timeseries_width`}
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Point colour represents log scaled reef total connectivity strength.
+Displays results from median timeseries using ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate width=`{julia} carb_width`}
+
 ### Bioregion scale
@@
 
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW level for each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
+
 ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 
+![Reef relative coral cover timeseries clustered within each management area.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}
+
 ![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
@@
 Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/log_total_strength_management_area_violin.png){#sfig-access-esm1-5-manarea-totalconnectivity width=`{julia} violin_width`}
-
-### GBR scale
-
-![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwcor width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median occupied proportion value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/initial_proportion_gbr_violin.png){#sfig-access-esm1-5-gbr-initialproportion width=`{julia} violin_width`}
-
-![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/mean_dhw_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwtol width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/so_to_si_gbr_violin.png){#sfig-access-esm1-5-gbr-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}
-
-## ACCESS-CM2
-
-### Bioregion scale
-
-![Reef relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median depth for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth width=`{julia} violin_width`}
-
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW level for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean width=`{julia} violin_width`}
-
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor width=`{julia} violin_width`}
-
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`}
-
-![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion width=`{julia} violin_width`}
-
-![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity width=`{julia} violin_width`}
-
-### Management area scale
-
-![Reef relative coral cover timeseries clustered within each management area.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/management_area_cover_timeseries.png){#sfig-access-cm2-manarea-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/depth_management_area_violin.png){#sfig-access-cm2-manarea-depth width=`{julia} violin_width`}
-
-![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/dhw_cover_cor_management_area_violin.png){#sfig-access-cm2-manarea-dhwcor width=`{julia} violin_width`}
-
-![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/mean_dhw_management_area_violin.png){#sfig-access-cm2-manarea-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/dhw_tolerance_management_area_violin.png){#sfig-access-cm2-manarea-dhwtol width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/initial_proportion_management_area_violin.png){#sfig-access-cm2-manarea-initialproportion width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/so_to_si_management_area_violin.png){#sfig-access-cm2-manarea-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/log_total_strength_management_area_violin.png){#sfig-access-cm2-manarea-totalconnectivity width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/gbr_cover_timeseries.png){#sfig-access-cm2-gbr-timeseries width=`{julia} timeseries_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/depth_gbr_violin.png){#sfig-access-cm2-gbr-depth width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-cm2-gbr-dhwcor width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median occupied proportion value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/initial_proportion_gbr_violin.png){#sfig-access-cm2-gbr-initialproportion width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/initial_proportion_gbr_violin.png){#sfig-access-esm1-5-gbr-initialproportion width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/mean_dhw_gbr_violin.png){#sfig-access-cm2-gbr-dhwmean width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/mean_dhw_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-cm2-gbr-dhwtol width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwtol width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/so_to_si_gbr_violin.png){#sfig-access-cm2-gbr-logsosi width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/so_to_si_gbr_violin.png){#sfig-access-esm1-5-gbr-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/log_total_strength_gbr_violin.png){#sfig-access-cm2-gbr-totalconnectivity width=`{julia} violin_width`}
-
-## EC-Earth3-Veg
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}
+
+## ACCESS-CM2
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries width=`{julia} timeseries_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW level for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`}
 
@@
 Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/management_area_cover_timeseries.png){#sfig-ec-earth3-veg-manarea-timeseries width=`{julia} timeseries_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/management_area_cover_timeseries.png){#sfig-access-cm2-manarea-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/depth_management_area_violin.png){#sfig-ec-earth3-veg-manarea-depth width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/depth_management_area_violin.png){#sfig-access-cm2-manarea-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/dhw_cover_cor_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwcor width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/dhw_cover_cor_management_area_violin.png){#sfig-access-cm2-manarea-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/mean_dhw_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwmean width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/mean_dhw_management_area_violin.png){#sfig-access-cm2-manarea-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/dhw_tolerance_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwtol width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/dhw_tolerance_management_area_violin.png){#sfig-access-cm2-manarea-dhwtol width=`{julia} violin_width`}
 
@@
 Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/initial_proportion_management_area_violin.png){#sfig-ec-earth3-veg-manarea-initialproportion width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/initial_proportion_management_area_violin.png){#sfig-access-cm2-manarea-initialproportion width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/so_to_si_management_area_violin.png){#sfig-ec-earth3-veg-manarea-logsosi width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/so_to_si_management_area_violin.png){#sfig-access-cm2-manarea-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/log_total_strength_management_area_violin.png){#sfig-ec-earth3-veg-manarea-totalconnectivity width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/log_total_strength_management_area_violin.png){#sfig-access-cm2-manarea-totalconnectivity width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/gbr_cover_timeseries.png){#sfig-ec-earth3-veg-gbr-timeseries width=`{julia} timeseries_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/gbr_cover_timeseries.png){#sfig-access-cm2-gbr-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/depth_gbr_violin.png){#sfig-ec-earth3-veg-gbr-depth width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/depth_gbr_violin.png){#sfig-access-cm2-gbr-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/dhw_cover_cor_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwcor width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-cm2-gbr-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median occupied proportion value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/initial_proportion_gbr_violin.png){#sfig-ec-earth3-veg-gbr-initialproportion width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/initial_proportion_gbr_violin.png){#sfig-access-cm2-gbr-initialproportion width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/mean_dhw_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwmean width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/mean_dhw_gbr_violin.png){#sfig-access-cm2-gbr-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/dhw_tolerance_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwtol width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-cm2-gbr-dhwtol width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/so_to_si_gbr_violin.png){#sfig-ec-earth3-veg-gbr-logsosi width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/so_to_si_gbr_violin.png){#sfig-access-cm2-gbr-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/log_total_strength_gbr_violin.png){#sfig-ec-earth3-veg-gbr-totalconnectivity width=`{julia} violin_width`}
-
-## GFDL-CM4
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/log_total_strength_gbr_violin.png){#sfig-access-cm2-gbr-totalconnectivity width=`{julia} violin_width`}
+
+## EC-Earth3-Veg
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries width=`{julia} timeseries_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW level for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`}
 
@@
 Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/management_area_cover_timeseries.png){#sfig-gfdl-cm4-manarea-timeseries width=`{julia} timeseries_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/management_area_cover_timeseries.png){#sfig-ec-earth3-veg-manarea-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/depth_management_area_violin.png){#sfig-gfdl-cm4-manarea-depth width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/depth_management_area_violin.png){#sfig-ec-earth3-veg-manarea-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/dhw_cover_cor_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwcor width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/dhw_cover_cor_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/mean_dhw_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwmean width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/mean_dhw_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/dhw_tolerance_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwtol width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/dhw_tolerance_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwtol width=`{julia} violin_width`}
 
@@
 Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/initial_proportion_management_area_violin.png){#sfig-gfdl-cm4-manarea-initialproportion width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/initial_proportion_management_area_violin.png){#sfig-ec-earth3-veg-manarea-initialproportion width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/so_to_si_management_area_violin.png){#sfig-gfdl-cm4-manarea-logsosi width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/so_to_si_management_area_violin.png){#sfig-ec-earth3-veg-manarea-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/log_total_strength_management_area_violin.png){#sfig-gfdl-cm4-manarea-totalconnectivity width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/log_total_strength_management_area_violin.png){#sfig-ec-earth3-veg-manarea-totalconnectivity width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/gbr_cover_timeseries.png){#sfig-gfdl-cm4-gbr-timeseries width=`{julia} timeseries_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/gbr_cover_timeseries.png){#sfig-ec-earth3-veg-gbr-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/depth_gbr_violin.png){#sfig-gfdl-cm4-gbr-depth width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/depth_gbr_violin.png){#sfig-ec-earth3-veg-gbr-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/dhw_cover_cor_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwcor width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/dhw_cover_cor_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median occupied proportion value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/initial_proportion_gbr_violin.png){#sfig-gfdl-cm4-gbr-initialproportion width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/initial_proportion_gbr_violin.png){#sfig-ec-earth3-veg-gbr-initialproportion width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/mean_dhw_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwmean width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/mean_dhw_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/dhw_tolerance_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwtol width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/dhw_tolerance_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwtol width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/so_to_si_gbr_violin.png){#sfig-gfdl-cm4-gbr-logsosi width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/so_to_si_gbr_violin.png){#sfig-ec-earth3-veg-gbr-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/log_total_strength_gbr_violin.png){#sfig-gfdl-cm4-gbr-totalconnectivity width=`{julia} violin_width`}
-
-## NorESM2-MM
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/log_total_strength_gbr_violin.png){#sfig-ec-earth3-veg-gbr-totalconnectivity width=`{julia} violin_width`}
+
+## GFDL-CM4
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries width=`{julia} timeseries_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW level for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`}
 
@@
 Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/management_area_cover_timeseries.png){#sfig-noresm2-mm-manarea-timeseries width=`{julia} timeseries_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/management_area_cover_timeseries.png){#sfig-gfdl-cm4-manarea-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/depth_management_area_violin.png){#sfig-noresm2-mm-manarea-depth width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/depth_management_area_violin.png){#sfig-gfdl-cm4-manarea-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/dhw_cover_cor_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwcor width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/dhw_cover_cor_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwcor width=`{julia} violin_width`}
 
@@
 Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/mean_dhw_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwmean width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/mean_dhw_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/dhw_tolerance_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwtol width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/dhw_tolerance_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwtol width=`{julia} violin_width`}
 
@@
 Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/initial_proportion_management_area_violin.png){#sfig-noresm2-mm-manarea-initialproportion width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/initial_proportion_management_area_violin.png){#sfig-gfdl-cm4-manarea-initialproportion width=`{julia} violin_width`}
 
@@
 Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/so_to_si_management_area_violin.png){#sfig-noresm2-mm-manarea-logsosi width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/so_to_si_management_area_violin.png){#sfig-gfdl-cm4-manarea-logsosi width=`{julia} violin_width`}
 
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/log_total_strength_management_area_violin.png){#sfig-noresm2-mm-manarea-totalconnectivity width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/log_total_strength_management_area_violin.png){#sfig-gfdl-cm4-manarea-totalconnectivity width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/gbr_cover_timeseries.png){#sfig-gfdl-cm4-gbr-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/depth_gbr_violin.png){#sfig-gfdl-cm4-gbr-depth width=`{julia} violin_width`}
+
+![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median total cover – DHW correlation value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/dhw_cover_cor_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwcor width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median occupied proportion value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/initial_proportion_gbr_violin.png){#sfig-gfdl-cm4-gbr-initialproportion width=`{julia} violin_width`}
+
+![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/mean_dhw_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median DHW - tolerance value for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/dhw_tolerance_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwtol width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/so_to_si_gbr_violin.png){#sfig-gfdl-cm4-gbr-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/log_total_strength_gbr_violin.png){#sfig-gfdl-cm4-gbr-totalconnectivity width=`{julia} violin_width`}
+
+## NorESM2-MM
+
+### Bioregion scale
+
+![Reef relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median depth for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth width=`{julia} violin_width`}
+
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW level for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean width=`{julia} violin_width`}
+
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median cover – DHW correlation level for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median DHW tolerance value for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines represent the median proportion of habitable area occupied for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion width=`{julia} violin_width`}
+
+![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity width=`{julia} violin_width`}
+
+### Management area scale
+
+![Reef relative coral cover timeseries clustered within each management area.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/management_area_cover_timeseries.png){#sfig-noresm2-mm-manarea-timeseries width=`{julia} timeseries_width`}
+
+![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/depth_management_area_violin.png){#sfig-noresm2-mm-manarea-depth width=`{julia} violin_width`}
+
+![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/dhw_cover_cor_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwcor width=`{julia} violin_width`}
+
+![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/mean_dhw_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwmean width=`{julia} violin_width`}
+
+![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median DHW – tolerance value for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/dhw_tolerance_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwtol width=`{julia} violin_width`}
+
+![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/initial_proportion_management_area_violin.png){#sfig-noresm2-mm-manarea-initialproportion width=`{julia} violin_width`}
+
+![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
+Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/so_to_si_management_area_violin.png){#sfig-noresm2-mm-manarea-logsosi width=`{julia} violin_width`}
+
+![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
+‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
+‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
+‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
+Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/log_total_strength_management_area_violin.png){#sfig-noresm2-mm-manarea-totalconnectivity width=`{julia} violin_width`}
+
+### GBR scale
+
+![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
+The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
+The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
+The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
+Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
 Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/gbr_cover_timeseries.png){#sfig-noresm2-mm-gbr-timeseries width=`{julia} timeseries_width`}

### 2025-06-26 src/ADRIA/HighResCoralStress/2_1_timeseries_clustering_carbonate.jl

@@ -1,3 +1,8 @@
+"""
+Cluster reef cover timeseries at three different scales across the GBR. For clustering,
+reef cover as a percentage of total reef area is used.
+"""
+
 using Revise, Infiltrator
 
 using GLMakie, GeoMakie, GraphMakie
@@ -6,133 +11,6 @@ using YAXArrays
 import GeoDataFrames as GDF
 
 using ADRIA
-
-# include("../../common.jl")
-# include("../../plotting_functions.jl")
-
-# GCM = "ACCESS-ESM1-5"
-# # Select the target GCM from
-# dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
-
-# GBR_domain_path = "../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/"
-# gbr_dom = ADRIA.load_domain(GBR_domain_path, "45")
-# context_layers = gbr_dom.loc_data
-
-# # Attach bioregion level data to context_layers
-# bioregions = GDF.read("../data/GBRMPA_reefal_bioregions.gpkg")
-# context_bioregion = find_intersections(context_layers, bioregions, :GBRMPA_ID, :DESCRIP, :SHAPE)
-# context_layers = leftjoin(context_layers, context_bioregion; on=:GBRMPA_ID, matchmissing=:notequal, order=:left)
-# rename!(context_layers, :area_ID => :bioregion)
-# context_layers.bioregion .= ifelse.(ismissing.(context_layers.bioregion), "NA", context_layers.bioregion)
-# context_layers.bioregion = convert.(String, context_layers.bioregion)
-
-# n_clusters = 3
-
-# thresholds = collect(2:1:20) ./ 100
-
-# rs = ADRIA.load_results("../outputs/ADRIA_results/HighResCoralStress/GBR_2024_10_15_HighResCoralStress__RCPs_45_$(GCM)")
-# GCM_results = GCM_analysis_results(rs)
-# # Convert absolute cover to cover relative to carbonate budjet area
-# areas = gbr_dom.loc_data.k .* gbr_dom.loc_data.area
-# cover = GCM_results.absolute_median_cover
-
-# n_timesteps = size(cover, 1)
-# n_locations = size(cover, 2)
-# n_thresholds = length(thresholds)
-# threshold_cover = YAXArray(
-#     (
-#         cover.timesteps,
-#         cover.locations,
-#         Dim{:thresholds}(thresholds)
-#     ),
[…]

### 2025-06-26 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -1,7 +1,7 @@
 """
 Access the domain connectivity and calculate the strength and number of outgoing/incoming
-connections for each reef. Run after running 3_.jl to include the bioregions and identified
-reef layers.
+connections for each reef. Add context information such as reef DHW levels, years above carbonate
+budget thresholds, DHW tolerance levels and number of reefs in each bioregion.
 """
 
 using DataFrames, Statistics, YAXArrays, ArchGDAL
@@ -15,7 +15,6 @@ import GeoFormatTypes as GFT
 change_ADRIA_debug(true) # Change ADRIA debug mode to true to extract DHW tolerance data from runs
 
 using ADRIA
-using ArchGDAL
 
 include("../../common.jl")
 
@@ -160,13 +159,13 @@ for (i_gcm, GCM) in enumerate(dhw_scenarios.dhw.properties["members"])
     context_layers[!, "$(GCM)_dhw_cover_cor"] = dhw_cover_cor
 
     # 4. Re-run 5 scenarios for each GCM and extract mean DHW tolerance from timeseries
-    scens = rs.inputs[1:4, Not(318)] # Only use 1st 5 scenarios for speed and remove RCP variable in inputs
-    scens.wave_scenario .= 1.0
-    rs_dhw = ADRIA.run_scenarios(gbr_dom, scens, "45")
-    dhw_tol_log = Float64.(mapslices(median, rs_dhw.coral_dhw_tol_log, dims = [:scenarios, :species]))
-    dhw_tol_mean = dropdims(mean(dhw_tol_log[10:end, :], dims = 1), dims = 1).data
+    # scens = rs.inputs[1:4, Not(318)] # Only use 1st 5 scenarios for speed and remove RCP variable in inputs
+    # scens.wave_scenario .= 1.0
+    # rs_dhw = ADRIA.run_scenarios(gbr_dom, scens, "45")
+    # dhw_tol_log = Float64.(mapslices(median, rs_dhw.coral_dhw_tol_log, dims = [:scenarios, :species]))
+    # dhw_tol_mean = dropdims(mean(dhw_tol_log[10:end, :], dims = 1), dims = 1).data
     
-    context_layers[!, "$(GCM)_mean_DHW_tol"] = dhw_tol_mean
+    # context_layers[!, "$(GCM)_mean_DHW_tol"] = dhw_tol_mean
 end
 
 # 5. Calculate the number of reefs in each bioregion
[…]

### 2025-06-26 src/ADRIA/HighResCoralStress/4_1_analysis_and_plots_clustering_carbonate.jl

@@ -1,3 +1,8 @@
+"""
+Create analysis plots for clustering and carbonate budget analyses. Performed for each GCM separately,
+and multi-GCM comparison plot created at end of the script.
+"""
+
 using Revise, Infiltrator
 
 using GLMakie, GeoMakie, GraphMakie
@@ -23,6 +28,18 @@ context_layers.log_total_strength = log10.(context_layers.total_strength)
 
 gbr_dom = ADRIA.load_domain("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/", "45")
 areas = gbr_dom.loc_data.area
+
+year_cols = Vector{String}()
+for GCM in GCMs
+    for threshold in thresholds
+        push!(year_cols, "$(GCM)_years_above_$(threshold)")
+    end
+end
+
+reefs_long = stack(
+    context_layers[:, ["UNIQUE_ID", "depth_med", "log_total_strength", year_cols...]],
+    year_cols
+)
 
 for (i_gcm, GCM) in enumerate(GCMs)
     # Select GCM and load relevant results
@@ -50,6 +67,25 @@ for (i_gcm, GCM) in enumerate(GCMs)
     cluster_analysis_plots(GCM, analysis_layers, threshold_cover, dhw_ts, :bioregion, fig_out_dir)
     cluster_analysis_plots(GCM, analysis_layers, threshold_cover, dhw_ts, :management_area, fig_out_dir)
     cluster_analysis_plots(GCM, analysis_layers, threshold_cover, dhw_ts, :gbr, fig_out_dir)
+
+    gcm_reefs_long = reefs_long[contains.(long_depth_reefs.variable, GCM), :]
+    gcm_reefs_long.variable = last.(split.(gcm_reefs_long.variable, "_"))
+    gcm_reefs_long_depth = gcm_reefs_long[
+        gcm_reefs_long.UNIQUE_ID .∈ context_layers[context_layers.depth .!= 7, :UNIQUE_ID],
+    :]
+
+    depth_carbonate_scatter = carbonate_budget_variable_scatter(gcm_reefs_long_depth, :depth_med, :value, :variable; color_label = "Median reef depth (m)")
+    save(
+        joinpath(fig_out_dir, "depth_carbonate_scatter.png"), 
+        depth_carbonate_scatter, 
+        px_per_unit = dpi
+    )
[…]

### 2025-06-26 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -1,5 +1,5 @@
 """
-Script to create additional plots required for publication.
+Script to create additional plots required for publication. E.g. maps and GCM plots.
 """
 
 using Revise, Infiltrator

### 2025-06-26 src/common.jl

@@ -709,7 +709,7 @@ end
 
 function percentage_cover_timeseries(areas, cover_timeseries)
     props = Dict(
-        :metric_feature => "Cover",
+        :metric_feature => "Cover of reef area",
         :axes_names => ["timesteps", "locations"],
         :metric_name => "Cover of reef area",
         :axes_units => ["years", ""],

### 2025-06-26 src/plotting_functions.jl

@@ -762,3 +762,47 @@ function grouped_GCM_cluster_timeseries_plots(
 
     return fig
 end
+
+function carbonate_budget_variable_scatter(
+    long_df,
+    color_variable_col,
+    year_col,
+    carbonate_budget_col;
+    xlabel="Carbonate budget threshold (%)",
+    ylabel="Years above carbonate budget threshold",
+    color_label="",
+    fig_sizes=fig_sizes,
+    fontsize=fontsize
+)
+    x_fig_size = fig_sizes["carb_width"]
+    y_fig_size = fig_sizes["carb_height"]
+
+    fig = Figure(size = (x_fig_size, y_fig_size), fontsize = fontsize)
+    ax = Axis(
+        fig[1,1],
+        ylabel = ylabel,
+        xlabel = xlabel,
+        xticks = (1:1:11, unique(long_df[:, carbonate_budget_col]))
+    )
+    rain = rainclouds!(
+        long_df[:, carbonate_budget_col], 
+        long_df[:, year_col];
+        color=long_df[:, color_variable_col], 
+        plot_boxplots=false, 
+        clouds=nothing,
+        show_median=false, 
+        markersize=6, 
+        jitter_width=0.9
+    )
+    # scat = scatter!(
+    #     ACCESS_ESM1_5_long.variable,
+    #     ACCESS_ESM1_5_long.value,
+    #     color=ACCESS_ESM1_5_long.depth_med,
+    #     alpha = 0.5
+    # )
+    Colorbar(fig[1,2], rain, label = color_label)
+
+    display(fig)
+
+    return fig
+end

### 2025-06-26 paper/paper_draft.qmd
Add writing of median timeseries to script for easier data sharing

@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#fig-gcm-trajectories width=`{julia} timeseries_width`}
+Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#sfig-gcm-trajectories width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median DHW level for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#fig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#fig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#sfig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#fig-access-esm1-5-manarea-depth width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#sfig-access-esm1-5-manarea-depth width=`{julia} violin_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#fig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#sfig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#fig-access-esm1-5-gbr-depth width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#sfig-access-esm1-5-gbr-depth width=`{julia} violin_width`}
 

### 2025-06-26 src/ADRIA/HighResCoralStress/1_GCM_model_runs.jl

@@ -1,6 +1,7 @@
 using Revise, Infiltrator
-using YAXArrays
+using YAXArrays, NetCDF
 
+include("../../common.jl")
 change_ADRIA_debug(false) # Ensure ADRIA debug mode is set to false to allow parallel processing.
 
 using ADRIA
@@ -25,4 +26,26 @@ for (g, GCM) in enumerate(gcms)
     rs = ADRIA.run_scenarios(gbr_dom, scens, "45")
 
     # Rename result store directory according to GCM that is chosen
+end
+
+# Save output absolute median cover to allow for data sharing.
+for GCM in gcms
+    processed_outputs = "../outputs/ADRIA_results/HighResCoralStress/processed_model_outputs/median_cover_$(GCM).nc"
+    if !isfile(processed_outputs)
+
+        rs = ADRIA.load_results("../outputs/ADRIA_results/HighResCoralStress/GBR_2024_10_15_HighResCoralStress__RCPs_45_$(GCM)")
+        scenario_cover = ADRIA.metrics.total_absolute_cover(rs)
+        median_cover = ADRIA.metrics.loc_trajectory(median, scenario_cover)
+
+        dims = (
+            Dim{:timesteps}(string.(scenario_cover.timesteps)),
+            Dim{:locations}(string.(scenario_cover.locations))
+        )
+        properties=median_cover.properties
+        pop!(properties, :is_relative)
+        properties = Dict{String, Any}([(string.(k), v) for (k,v) in properties])
+
+        median_cover = rebuild(median_cover, dims=dims, metadata=properties)
+        savecube(median_cover, processed_outputs, driver=:netcdf, overwrite=true)
+    end
 end

### 2025-06-27 paper/paper_draft.qmd
Edit scripts to allow generation of figures from shared results data
Additionally remove management and gbr scale analyses from the quarto paper document.

@@
 Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).
-
+<!-- 
 In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially lower mean thermal tolerance levels compared to reefs in other clusters.
 However, many bioregions do not show strong differences in thermal tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol; @sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol; @sfig-noresm2-mm-bioregion-dhwtol).
+-->
 
@@
 Across most bioregions there are not consistent differences between clusters in connectivity metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi; @sfig-access-cm2-bioregion-logsosi; @sfig-ec-earth3-veg-bioregion-logsosi; @sfig-gfdl-cm4-bioregion-logsosi; @sfig-noresm2-mm-bioregion-logsosi) and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity; @sfig-access-cm2-bioregion-totalconnectivity; @sfig-ec-earth3-veg-bioregion-totalconnectivity; @sfig-gfdl-cm4-bioregion-totalconnectivity; @sfig-noresm2-mm-bioregion-totalconnectivity).
-
+<!-- 
 ## Management area scale clustering
@@
 Similarly, there are no substantial differences between clusters in connectivity metrics source – to – sink ratio and total connectivity strength (@sfig-access-esm1-5-gbr-logsosi; @sfig-access-cm2-gbr-logsosi; @sfig-ec-earth3-veg-gbr-logsosi; @sfig-gfdl-cm4-gbr-logsosi; @sfig-noresm2-mm-gbr-logsosi; @sfig-access-esm1-5-gbr-totalconnectivity; @sfig-access-cm2-gbr-totalconnectivity; @sfig-ec-earth3-veg-gbr-totalconnectivity; @sfig-gfdl-cm4-gbr-totalconnectivity; @sfig-noresm2-mm-gbr-totalconnectivity).
+-->
 
@@
 Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
-
+<!-- 
 ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}
-
+<!-- 
 ### Management area scale
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`}
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`} -->
 
@@
 
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity width=`{julia} violin_width`}
-
+<!-- 
 ### Management area scale
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/log_total_strength_gbr_violin.png){#sfig-access-cm2-gbr-totalconnectivity width=`{julia} violin_width`}
+Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/log_total_strength_gbr_violin.png){#sfig-access-cm2-gbr-totalconnectivity width=`{julia} violin_width`} -->
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity width=`{julia} violin_width`}
-
+<!-- 
 ### Management area scale
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/log_total_strength_gbr_violin.png){#sfig-ec-earth3-veg-gbr-totalconnectivity width=`{julia} violin_width`}
+Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/log_total_strength_gbr_violin.png){#sfig-ec-earth3-veg-gbr-totalconnectivity width=`{julia} violin_width`} -->
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity width=`{julia} violin_width`}
-
+<!-- 
 ### Management area scale
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/log_total_strength_gbr_violin.png){#sfig-gfdl-cm4-gbr-totalconnectivity width=`{julia} violin_width`}
+Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/log_total_strength_gbr_violin.png){#sfig-gfdl-cm4-gbr-totalconnectivity width=`{julia} violin_width`} -->
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`}
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity width=`{julia} violin_width`}
-
+<!-- 
 ### Management area scale
@@
 Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/log_total_strength_gbr_violin.png){#sfig-noresm2-mm-gbr-totalconnectivity width=`{julia} violin_width`}
+Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/log_total_strength_gbr_violin.png){#sfig-noresm2-mm-gbr-totalconnectivity width=`{julia} violin_width`} -->

### 2025-06-27 src/ADRIA/HighResCoralStress/1_GCM_model_runs.jl

@@ -38,7 +38,7 @@ for GCM in gcms
         median_cover = ADRIA.metrics.loc_trajectory(median, scenario_cover)
 
         dims = (
-            Dim{:timesteps}(string.(scenario_cover.timesteps)),
+            Dim{:timesteps}(Int64.(scenario_cover.timesteps)),
             Dim{:locations}(string.(scenario_cover.locations))
         )
         properties=median_cover.properties

### 2025-06-27 src/ADRIA/HighResCoralStress/2_timeseries_clustering.jl

@@ -1,62 +1,0 @@
-using Revise, Infiltrator
-
-using GLMakie, GeoMakie, GraphMakie
-using Statistics
-using YAXArrays
-import GeoDataFrames as GDF
-
-using ADRIA
-
-include("../../common.jl")
-includet("../../plotting_functions.jl")
-
-# Select the target GCM from
-dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
-
-GBR_domain_path = "../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/"
-gbr_dom = ADRIA.load_domain(GBR_domain_path, "45")
-context_layers = gbr_dom.loc_data
-
-# Attach bioregion level data to context_layers
-bioregions = GDF.read("../data/GBRMPA_reefal_bioregions.gpkg")
-context_bioregion = find_intersections(context_layers, bioregions, :GBRMPA_ID, :DESCRIP, :SHAPE)
-context_layers = leftjoin(context_layers, context_bioregion; on=:GBRMPA_ID, matchmissing=:notequal, order=:left)
-rename!(context_layers, :area_ID => :bioregion)
-context_layers.bioregion .= ifelse.(ismissing.(context_layers.bioregion), "NA", context_layers.bioregion)
-context_layers.bioregion = convert.(String, context_layers.bioregion)
-
-n_clusters = 3
-
-for GCM in dhw_scenarios.dhw.properties["members"]
-    
-    # Select GCM and load relevant results
-    @info "Performing timeseries clustering for $(GCM)"
-
-    rs = ADRIA.load_results("../outputs/ADRIA_results/HighResCoralStress/GBR_2024_10_15_HighResCoralStress__RCPs_45_$(GCM)")
-    GCM_results = GCM_analysis_results(rs)
-    rel_cover = GCM_results.relative_cover
-
-    rel_cover_less_than_5 = [all(rel_cover[:, i].data .< 5) for i in 1:size(rel_cover, 2)]
-    rel_cover_less_than_5_ind = findall(rel_cover_less_than_5)
-    # rel_cover_less_than_5 = ones(size(context_layers, 1))
-
[…]

### 2025-06-27 src/ADRIA/HighResCoralStress/2_timeseries_clustering_absolute.jl

@@ -39,9 +39,7 @@ for GCM in dhw_scenarios.dhw.properties["members"]
     # Select GCM and load relevant results
     @info "Performing timeseries clustering for $(GCM)"
 
-    rs = ADRIA.load_results("../outputs/ADRIA_results/HighResCoralStress/GBR_2024_10_15_HighResCoralStress__RCPs_45_$(GCM)")
-    GCM_results = GCM_analysis_results(rs)
-    absolute_cover = GCM_results.absolute_median_cover
+    absolute_cover = open_dataset("../outputs/ADRIA_results/HighResCoralStress/processed_model_outputs/median_cover_$(GCM).nc").layer
 
     # threshold_cover = threshold_cover_timeseries(areas, absolute_cover, 0.17)
     percentage_cover = percentage_cover_timeseries(areas, absolute_cover)

### 2025-06-27 src/ADRIA/HighResCoralStress/4_analysis_and_plots_clustering.jl

@@ -1,193 +1,0 @@
-using Revise, Infiltrator
-
-using GLMakie, GeoMakie, GraphMakie
-using Statistics
-using YAXArrays
-using CairoMakie
-
-using ADRIA
-
-include("../../common.jl")
-include("../../plotting_functions.jl")
-
-CairoMakie.activate!()
-
-# Select the target GCM from
-dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
-GCMs = dhw_scenarios.dhw.properties["members"]
-
-context_layers = GDF.read("../outputs/ADRIA_results/HighResCoralStress/analysis_context_layers.gpkg")
-context_layers.gbr .= "Great Barrier Reef"
-context_layers.log_so_to_si = log10.(context_layers.so_to_si)
-context_layers.log_total_strength = log10.(context_layers.total_strength)
-
-gbr_dom = ADRIA.load_domain("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/", "45")
-
-for (i_gcm, GCM) in enumerate(GCMs)
-    # Select GCM and load relevant results
-    @info "analysing reef clustering for $(GCM)"
-
-    fig_out_dir = "../outputs/ADRIA_results/HighResCoralStress/figs/$(GCM)"
-
-    rs = ADRIA.load_results("../outputs/ADRIA_results/HighResCoralStress/GBR_2024_10_15_HighResCoralStress__RCPs_45_$(GCM)")
-    GCM_results = GCM_analysis_results(rs)
-    rel_cover = GCM_results.relative_cover
-
-    rel_cover_less_than_5 = [all(rel_cover[:, i].data .< 5) for i in 1:size(rel_cover, 2)]
-    rel_cover_less_than_5_ind = findall(rel_cover_less_than_5)
-
-    dhw_ts = gbr_dom.dhw_scens[:,:,i_gcm]
-    ax = (
-        Dim{:timesteps}(2025:2099),
-        Dim{:locations}(collect(GCM_results.relative_cover.locations))
-    )
-    dhw_ts = rebuild(dhw_ts, dims=ax)
-
-    # Subset layers to remove reefs that start with very low coral cover
-    analysis_layers = context_layers[rel_cover_less_than_5, :]
[…]

### 2025-06-27 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -17,18 +17,26 @@ include("../../plotting_functions.jl")
 
 CairoMakie.activate!()
 
-# Select the target GCM from
-dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
-GCMs = dhw_scenarios.dhw.properties["members"]
+# # Select the target GCM from
+# dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
+# GCMs = dhw_scenarios.dhw.properties["members"]
+GCMs = [
+    "EC-Earth3-Veg",
+    "ACCESS-ESM1-5",
+    "ACCESS-CM2",
+    "NorESM2-MM",
+    "GFDL-CM4"
+]
 
-context_layers = GDF.read("../outputs/ADRIA_results/HighResCoralStress/analysis_context_layers_carbonate.gpkg")
+context_layers = GDF.read(joinpath(output_path, "analysis_context_layers_carbonate.gpkg"))
 context_layers.gbr .= "Great Barrier Reef"
 context_layers.log_so_to_si = log10.(context_layers.so_to_si)
 context_layers.log_total_strength = log10.(context_layers.total_strength)
 
-gbr_dom = ADRIA.load_domain("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/", "45")
+gbr_dom = ADRIA.load_domain(gbr_domain_path, "45")
 areas = gbr_dom.loc_data.area
 
+thresholds = 10:1:20
 year_cols = Vector{String}()
 for GCM in GCMs
     for threshold in thresholds
@@ -45,20 +53,14 @@ for (i_gcm, GCM) in enumerate(GCMs)
     # Select GCM and load relevant results
     @info "analysing reef clustering for $(GCM)"
 
-    fig_out_dir = "../outputs/ADRIA_results/HighResCoralStress/figs/$(GCM)"
+    fig_out_dir = joinpath(output_path, "figs/$(GCM)")
 
-    rs = ADRIA.load_results("../outputs/ADRIA_results/HighResCoralStress/GBR_2024_10_15_HighResCoralStress__RCPs_45_$(GCM)")
-    GCM_results = GCM_analysis_results(rs)
-    absolute_cover = GCM_results.absolute_median_cover
[…]

### 2025-06-27 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -18,7 +18,7 @@ include("../../plotting_functions.jl")
 
 CairoMakie.activate!()
 
-context_layers = GDF.read("../outputs/ADRIA_results/HighResCoralStress/analysis_context_layers.gpkg")
+context_layers = GDF.read(joinpath(output_path, "analysis_context_layers_carbonate.gpkg"))
 
 # ECS plot - methods
 ecs_values = Dict(
@@ -29,7 +29,7 @@ ecs_values = Dict(
     "NorESM2-MM" => 2.5
 )
 ecs = ecs_plot(collect(values(ecs_values)), [2.5,5.1], [2.1,7.7], collect(keys(ecs_values)))
-save("../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png", ecs, px_per_unit = 300/inch)
+save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit = 300/inch)
 
 # GBR map plot - methods
 investigation_reefs = context_layers[
@@ -97,13 +97,13 @@ Legend(
     rowgap=1,
     backgroundcolor=bgcol
 )
-save("../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png", fig, px_per_unit = 300/inch)
+save(joinpath(output_path, "figs/region_map.png"), fig, px_per_unit = 300/inch)
 
-fig = Figure()
-ax = Axis(
-    fig[1,1],
-    limits = (nothing, (-0.1, 400)),
-    ylabel="Initial cover",
-    xlabel="Reefs with <5x initial cover in timeseries"
-)
-scatter!((context_layers[:, "ACCESS-ESM1-5_gbr_clusters"] .!= 0.0), context_layers.initial_coral_cover)
+# fig = Figure()
+# ax = Axis(
+#     fig[1,1],
+#     limits = (nothing, (-0.1, 400)),
+#     ylabel="Initial cover",
+#     xlabel="Reefs with <5x initial cover in timeseries"
+# )
+# scatter!((context_layers[:, "ACCESS-ESM1-5_gbr_clusters"] .!= 0.0), context_layers.initial_coral_cover)

### 2025-06-27 src/common.jl

@@ -35,8 +35,8 @@ using ADRIA
 include("plotting_functions.jl")
 include("ADRIA_DataCube_functions.jl")
 
-gbr_domain_path = "c:/Users/bgrier/Documents/Projects/ADRIA_Domains/rme_ml_2024_01_08/"
-conn_path = joinpath(gbr_domain_path, "data_files/con_bin")
+gbr_domain_path = config["domain"]["domain_dir"]
+output_path = config["results"]["output_dir"]
 
 """
     find_intersections(

### 2025-06-27 src/plotting_functions.jl

@@ -7,6 +7,7 @@ using Colors
 using Random
 using TOML
 
+
 config = TOML.parsefile("config.toml")
 
 # Extract figure sizes and convert to pixel measurement
@@ -315,7 +316,6 @@ function grouped_cluster_timeseries_plots(
             clusters;
             opts = Dict{Symbol, Any}(:legend => false),
             axis_opts = Dict(
-                :ylabel => ytitle,
                 :title => labels[xi], 
                 :xticks => (
                     first(length_t):10:last(length_t), 

### 2025-07-02 paper/paper_draft.qmd
Remove management area information and add carbonate budget text

@@
 
-### Reef health metrics
-
 ADRIA-CoralBlox was run for 4096 *sampled* scenarios per GCM.
 A median absolute coral cover timeseries for each reef was calculated for each GCM.
-For use in timeseries clustering reef cover timeseries were scaled by the total area of the reef to represent timeseries as a percentage of total reef area (range 0 - 100%).
-The proportion of each functional group occupying the reef (taxa evenness) was also investigated as a metric for timeseries analysis, but was found to not sufficiently capture the declining condition of reefs suffering from very low absolute coral cover.
+For timeseries clustering reef cover timeseries were scaled by the total area of the reef to represent timeseries as a percentage of the total reef area.
+The proportion of each functional group occupying the reef (group evenness) was also investigated as a metric for timeseries analysis, but was found to not sufficiently capture the declined condition of reefs suffering from very low absolute coral cover.
 
@@
 
-Timeseries analysis is performed by first grouping reefs into three different scales, GBRMPA reefal bioregion, GBRMPA management area and GBR-wide, to investigate the consistency of cluster identification.
 To identify groups of reefs at each analysis scale that are resilient, intermediate and non-resilient we clustered reef coral cover timeseries into three clusters at each scale.
@@
 
-## Carbonate budget analysis
-
-To maintain coral cover over time coral reefs require a threshold of coral cover known as a carbonate budget.
-Estimates of the carbonate budget required to maintain a healthy coral reef range from 10 to 20% of a reef's total area.
-Using median absolute cover timeseries for each reef we calculated the number of years each reef maintains coral cover above a carbonate budget threshold level.
-Threshold values from 10 to 20% (inclusive) were used in analyses.
-
-### Further analyses
+Timeseries clustering analyses were performed at the reefal bioregion scale to capture groups of biogeographically similar reefs, as determined by *insert citation for bioregions*.
+Analyses were also performed at higher spatial scales, GBRMPA management regions and whole GBR scale.
+Similar results were found at large spatial scales, these can be found at *insert citation for repository*.
 
@@
 
+## Carbonate budget analysis
+
+Scleractinian corals are primary habitat structures on coral reefs.
+The accumulation and erosion of coral reef carbonate frameworks is controlled by a range of processes such as coral accumulation *Perry*, bioerosion *Tribollet*, physical damage generating coral rubble *Kenyon*, and calcificationa and *CaCO3* dissolution rates *Eyre 2014, 2018*.
+The balance of these processes and occurrance of net carbonate framework production (referred to as a positive carbonate budget) are influenced by factors such as coral cover and complexity *Perry, Desbiens*, rates of physical environmental processes and ocean acidity *Perry, Eyre*.
+It has been suggested that total live coral cover on a reef highly influences the maintainence of net positive carbonate budgets.
+Estimates of live coral cover required to maintain net positive carbonate budget levels range from 10 to 20% *Perry* of a reef's total area, with a level of 17% live coral cover for the Great Barrier Reef *Desbiens*.
+Using median absolute cover timeseries for each reef we calculated the number of years each reef maintains coral cover above these live coral cover threshold levels, inferring the number of years each reef maintains a net positive carbonate budget, accumulating reef framework.
+As in situ carbonate budgets are influenced by a range of processes, our calculations of carbonate budget maintainence are intended as estimates and do not reflect the conditions that will be experienced on a reef, but indicate relative levels of health across reefs.
+To capture the wide influence of environmental factors on carbonate budget levels, we analyse live coral cover thresholds required for positive carbonate budgets from 10 to 20% (inclusive, at step 1%).
+
 # Results
+
+## Reef carbonate budget
+The number of years reefs maintain coral cover above a required carbonate budget level substantially decreases as the required carbonate budget threshold (as a percentage of reef area) increases.
+Reefs with greater median depth levels maintain coral cover above required carbonate budget levels for longer than reefs at shallow depths [@fig-access-esm1-5-depth-carbonate].
+Reef median depth has a moderate positive correlation with the number of years a reef maintains coral cover above the required threshold [@fig-access-esm1-5-depth-carbonate].
+Depth - carbonate budget maintainence correlation decreases as the required carbonate budget threshold increases.
+This is likely due to an increasing number of reefs being unable to maintain coral cover above threshold levels as the threshold increases.
+There are no clear relationships between reef total connectivity levels and the number of years reefs maintain coral cover above carbonate budget threshold levels [@sfig-access-esm1-5-conn-carbonate].
+Reef log (natural) total connectivity strength has no correlation with the number of years a reef maintains cover above the required thresholds.
+Log connectivity strength - carbonate budget maintainence correlation slightly decreases as the required carbonate budget threshold increases.
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents the median reef depth level in metres.
+Displays results from median timeseries using ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate width=`{julia} carb_width`}
 
@@
 
-## Reef carbonate budget
-The number of years reefs maintain coral cover above a required carbonate budget level substantially decreases as the required carbonate budget threshold (as a percentage of reef area) increases.
-Reefs with greater median depth levels maintain coral cover above required carbonate budget levels for longer than reefs at shallow depths [@fig-access-esm1-5-depth-carbonate].
-There are no clear relationships between reef total connectivity levels and the number of years reefs maintain coral cover above carbonate budget threshold levels [@sfig-access-esm1-5-conn-carbonate].
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Point colour represents the median reef depth level in metres.
-Displays results from median timeseries using ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate width=`{julia} carb_width`}
-
 ## Bioregion scale clustering
@@
 Across most bioregions there are not consistent differences between clusters in connectivity metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi; @sfig-access-cm2-bioregion-logsosi; @sfig-ec-earth3-veg-bioregion-logsosi; @sfig-gfdl-cm4-bioregion-logsosi; @sfig-noresm2-mm-bioregion-logsosi) and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity; @sfig-access-cm2-bioregion-totalconnectivity; @sfig-ec-earth3-veg-bioregion-totalconnectivity; @sfig-gfdl-cm4-bioregion-totalconnectivity; @sfig-noresm2-mm-bioregion-totalconnectivity).
-<!-- 
-## Management area scale clustering
-
-Within the four management areas, timeseries clustering analysis identified three clusters of reefs using relative coral cover timeseries.
-These clusters form groups of reefs with ‘low, medium and high’ relative coral cover, categorised by their median coral cover between 2030 and 2040.
-The ‘high’ cover cluster of reefs contains reefs that have continuing recovery of corals throughout the future climate scenario.
-The medium and low clusters contain many reefs that decrease to half their initial coral cover levels and largely do not display the levels of recurring recovery that reefs in high clusters experience (@sfig-access-esm1-5-manarea-timeseries; @sfig-access-cm2-manarea-timeseries; @sfig-ec-earth3-veg-manarea-timeseries; @sfig-gfdl-cm4-manarea-timeseries; @sfig-noresm2-mm-manarea-timeseries).
-
-Within each bioregion reef median depth level increases with increasing reef relative coral cover.
-Reefs in the low cluster have the lowest median depth levels, while reefs in the high cluster have the highest median depth levels within each management area (@sfig-access-esm1-5-manarea-depth; @sfig-access-cm2-manarea-depth; @sfig-ec-earth3-veg-manarea-depth; @sfig-gfdl-cm4-manarea-depth; @sfig-noresm2-mm-manarea-depth).
-
-Correlation between reef total coral cover and the DHW levels they experience throughout the time period increases as coral relative cover increases, with reefs in the high cluster having the highest median total cover – DHW correlation (@sfig-access-esm1-5-manarea-dhwcor; @sfig-access-cm2-manarea-dhwcor; @sfig-ec-earth3-veg-manarea-dhwcor; @sfig-gfdl-cm4-manarea-dhwcor; @sfig-noresm2-mm-manarea-dhwcor).
-
-However, reefs with higher relative coral cover levels do not experience lower mean DHW levels throughout their timeseries.
-There are no consistent substantial differences in mean DHW levels across the identified timeseries clusters (@sfig-access-esm1-5-manarea-dhwmean; @sfig-access-cm2-manarea-dhwmean; @sfig-ec-earth3-veg-manarea-dhwmean; @sfig-gfdl-cm4-manarea-dhwmean; @sfig-noresm2-mm-manarea-dhwmean).
-
-Within the Far Northern management area ‘low’ cluster reefs have substantially lower median DHW – tolerance levels than ‘medium’ and ‘high’ clusters, while there are no substantial differences in DHW – tolerance between clusters in other management areas (@sfig-access-esm1-5-manarea-dhwtol; @sfig-access-cm2-manarea-dhwtol; @sfig-ec-earth3-veg-manarea-dhwtol; @sfig-gfdl-cm4-manarea-dhwtol; @sfig-noresm2-mm-manarea-dhwtol).
-
-Like clusters identified within bioregions, within the Mackay-Capricorn, Far Northern and Cairns-Cooktown management areas the initial proportion of coral-habitable area initially occupied by corals decreases in clusters with higher relative coral cover (@sfig-access-esm1-5-manarea-initialproportion; @sfig-access-cm2-manarea-initialproportion; @sfig-ec-earth3-veg-manarea-initialproportion; @sfig-gfdl-cm4-manarea-initialproportion; @sfig-noresm2-mm-manarea-initialproportion).
-
-At management area analysis scales, there are not consistent substantial differences in source – to – sink ratios (@sfig-access-esm1-5-manarea-logsosi; @sfig-access-cm2-manarea-logsosi; @sfig-ec-earth3-veg-manarea-logsosi; @sfig-gfdl-cm4-manarea-logsosi; @sfig-noresm2-mm-manarea-logsosi) and total connectivity strength (@sfig-access-esm1-5-manarea-totalconnectivity; @sfig-access-cm2-manarea-totalconnectivity; @sfig-ec-earth3-veg-manarea-totalconnectivity; @sfig-gfdl-cm4-manarea-totalconnectivity; @sfig-noresm2-mm-manarea-totalconnectivity).
-
-## Great Barrier Reef scale clustering
-
-Timeseries clustering identified three clusters in reef relative cover timeseries for the whole GBR scale.
-A ‘low’ cluster of reefs with little recovery following initial declines, a medium cluster of reefs with median relative cover below 0.5 post 2028, and a high cluster of reefs with median relative cover above 0.5 until 2050 (@sfig-access-esm1-5-gbr-timeseries; @sfig-access-cm2-gbr-timeseries; @sfig-ec-earth3-veg-gbr-timeseries; @sfig-gfdl-cm4-gbr-timeseries; @sfig-noresm2-mm-gbr-timeseries).
-
-The clusters identified with timeseries clustering at the GBR scale show similar patterns to clusters identified at bioregion and management area scales.
-Reef depth (@sfig-access-esm1-5-gbr-depth; @sfig-access-cm2-gbr-depth; @sfig-ec-earth3-veg-gbr-depth; @sfig-gfdl-cm4-gbr-depth; @sfig-noresm2-mm-gbr-depth) and total cover – DHW correlation (@sfig-access-esm1-5-gbr-dhwcor; @sfig-access-cm2-gbr-dhwcor; @sfig-ec-earth3-veg-gbr-dhwcor; @sfig-gfdl-cm4-gbr-dhwcor; @sfig-noresm2-mm-gbr-dhwcor) decrease, while the proportion of coral-habitable area initially occupied by corals increases (@sfig-access-esm1-5-gbr-initialproportion; @sfig-access-cm2-gbr-initialproportion; @sfig-ec-earth3-veg-gbr-initialproportion; @sfig-gfdl-cm4-gbr-initialproportion; @sfig-noresm2-mm-gbr-initialproportion), as the clusters decrease from ‘high’ to ‘low’ cover levels.
-There are no substantial differences between the clusters in mean DHW (@sfig-access-esm1-5-gbr-dhwmean; @sfig-access-cm2-gbr-dhwmean; @sfig-ec-earth3-veg-gbr-dhwmean; @sfig-gfdl-cm4-gbr-dhwmean; @sfig-noresm2-mm-gbr-dhwmean) and DHW tolerance (@sfig-access-esm1-5-gbr-dhwtol; @sfig-access-cm2-gbr-dhwtol; @sfig-ec-earth3-veg-gbr-dhwtol; @sfig-gfdl-cm4-gbr-dhwtol; @sfig-noresm2-mm-gbr-dhwtol) levels of reefs.
-Similarly, there are no substantial differences between clusters in connectivity metrics source – to – sink ratio and total connectivity strength (@sfig-access-esm1-5-gbr-logsosi; @sfig-access-cm2-gbr-logsosi; @sfig-ec-earth3-veg-gbr-logsosi; @sfig-gfdl-cm4-gbr-logsosi; @sfig-noresm2-mm-gbr-logsosi; @sfig-access-esm1-5-gbr-totalconnectivity; @sfig-access-cm2-gbr-totalconnectivity; @sfig-ec-earth3-veg-gbr-totalconnectivity; @sfig-gfdl-cm4-gbr-totalconnectivity; @sfig-noresm2-mm-gbr-totalconnectivity).
--->
 
@@
 NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintanance into the future.
-The differences between low, medium and high reef clusters in their timeseries are most notable under these two GCMs.
-At all analysis scales reef clusters show similar patterns in their reef characteristics such as depth and proportion of habitable area initially occupied.
+Differences between low, medium and high reef clusters in their timeseries are most notable under these two GCMs.
 
@@
 
-Overall, our findings do not suggest that resilient reefs in ‘high’ cover clusters have greater thermal tolerance than reefs in lower coral cover clusters.
+Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater thermal tolerance than reefs in lower coral cover clusters.
 This is in contrast with literature suggesting corals have the capacity to adapt to increasing climate change pressures [@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
@@
 Furthermore, our results suggest that the capacity of reefs to maintain healthy coral habitat by being above positive net carbonate budget levels is greater for reefs at deeper depths than shallow depths.
-While the maintanence of positive carbonate budget levels does not appear to be influenced by reef connectivity metrics.
+While the maintanence of positive carbonate budget levels does not appear to be linked to reef connectivity metrics.
 The maintanence of positive carbonate budgets is important for reef resilience under climate change.
@@
 We investigate a range of future climate responses and thermal projections to account for a range of possible futures, and our results suggest the factors that influence reef resilience are consistent across these scenarios.
+
+ADRIA - CoralBlox has not been calibrated or validated at the GBR-wide scale.
+Accordingly, the purpose of this investigation is to assess the relative influence of reef characteristics on future resilience and highlight possible outcomes under highly uncertain future scenarios, rather than provide spatially explicit predictions of future resilience.
 
@@
 
-## ACCESS-ESM1-5
-
 ![Reef Degree Heating Week timeseries clustered within each management area, for each GCM analysed.
@@
 
+## ACCESS-ESM1-5
+
 ![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
 The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Point colour represents log scaled reef total connectivity strength.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents log (natural) scaled reef total connectivity strength.
 Displays results from median timeseries using ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate width=`{julia} carb_width`}
@@
 
-![Log source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
 Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}
 
-![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
 Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}
-<!-- 
-### Management area scale
-
-![Reef relative coral cover timeseries clustered within each management area.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/management_area_cover_timeseries.png){#sfig-access-esm1-5-manarea-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/depth_management_area_violin.png){#sfig-access-esm1-5-manarea-depth width=`{julia} violin_width`}
-
-![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_cover_cor_management_area_violin.png){#sfig-access-esm1-5-manarea-dhwcor width=`{julia} violin_width`}
-
-![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/mean_dhw_management_area_violin.png){#sfig-access-esm1-5-manarea-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/dhw_tolerance_management_area_violin.png){#sfig-access-esm1-5-manarea-dhwtol width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/initial_proportion_management_area_violin.png){#sfig-access-esm1-5-manarea-initialproportion width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/so_to_si_management_area_violin.png){#sfig-access-esm1-5-manarea-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/management_area/log_total_strength_management_area_violin.png){#sfig-access-esm1-5-manarea-totalconnectivity width=`{julia} violin_width`}
-
-### GBR scale
-
-![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
-The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
-The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
-The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/gbr_cover_timeseries.png){#sfig-access-esm1-5-gbr-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/depth_gbr_violin.png){#sfig-access-esm1-5-gbr-depth width=`{julia} violin_width`}
-
-![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwcor width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median occupied proportion value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/initial_proportion_gbr_violin.png){#sfig-access-esm1-5-gbr-initialproportion width=`{julia} violin_width`}
-
-![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/mean_dhw_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-esm1-5-gbr-dhwtol width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/so_to_si_gbr_violin.png){#sfig-access-esm1-5-gbr-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/gbr/log_total_strength_gbr_violin.png){#sfig-access-esm1-5-gbr-totalconnectivity width=`{julia} violin_width`} -->
 
 ## ACCESS-CM2
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents the median reef depth level in metres.
+Displays results from median timeseries using ACCESS-CM2.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate width=`{julia} carb_width`}
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using ACCESS-CM2.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate width=`{julia} carb_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
 Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi width=`{julia} violin_width`}
 
-![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
 Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity width=`{julia} violin_width`}
-<!-- 
-### Management area scale
-
-![Reef relative coral cover timeseries clustered within each management area.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/management_area_cover_timeseries.png){#sfig-access-cm2-manarea-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/depth_management_area_violin.png){#sfig-access-cm2-manarea-depth width=`{julia} violin_width`}
-
-![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/dhw_cover_cor_management_area_violin.png){#sfig-access-cm2-manarea-dhwcor width=`{julia} violin_width`}
-
-![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/mean_dhw_management_area_violin.png){#sfig-access-cm2-manarea-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/dhw_tolerance_management_area_violin.png){#sfig-access-cm2-manarea-dhwtol width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/initial_proportion_management_area_violin.png){#sfig-access-cm2-manarea-initialproportion width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/so_to_si_management_area_violin.png){#sfig-access-cm2-manarea-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/management_area/log_total_strength_management_area_violin.png){#sfig-access-cm2-manarea-totalconnectivity width=`{julia} violin_width`}
-
-### GBR scale
-
-![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
-The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
-The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
-The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/gbr_cover_timeseries.png){#sfig-access-cm2-gbr-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/depth_gbr_violin.png){#sfig-access-cm2-gbr-depth width=`{julia} violin_width`}
-
-![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/dhw_cover_cor_gbr_violin.png){#sfig-access-cm2-gbr-dhwcor width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median occupied proportion value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/initial_proportion_gbr_violin.png){#sfig-access-cm2-gbr-initialproportion width=`{julia} violin_width`}
-
-![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/mean_dhw_gbr_violin.png){#sfig-access-cm2-gbr-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/dhw_tolerance_gbr_violin.png){#sfig-access-cm2-gbr-dhwtol width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/so_to_si_gbr_violin.png){#sfig-access-cm2-gbr-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/gbr/log_total_strength_gbr_violin.png){#sfig-access-cm2-gbr-totalconnectivity width=`{julia} violin_width`} -->
 
 ## EC-Earth3-Veg
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents the median reef depth level in metres.
+Displays results from median timeseries using EC-Earth3-Veg.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate width=`{julia} carb_width`}
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using EC-Earth3-Veg.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate width=`{julia} carb_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
 Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi width=`{julia} violin_width`}
 
-![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
 Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity width=`{julia} violin_width`}
-<!-- 
-### Management area scale
-
-![Reef relative coral cover timeseries clustered within each management area.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/management_area_cover_timeseries.png){#sfig-ec-earth3-veg-manarea-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/depth_management_area_violin.png){#sfig-ec-earth3-veg-manarea-depth width=`{julia} violin_width`}
-
-![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/dhw_cover_cor_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwcor width=`{julia} violin_width`}
-
-![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/mean_dhw_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/dhw_tolerance_management_area_violin.png){#sfig-ec-earth3-veg-manarea-dhwtol width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/initial_proportion_management_area_violin.png){#sfig-ec-earth3-veg-manarea-initialproportion width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/so_to_si_management_area_violin.png){#sfig-ec-earth3-veg-manarea-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/management_area/log_total_strength_management_area_violin.png){#sfig-ec-earth3-veg-manarea-totalconnectivity width=`{julia} violin_width`}
-
-### GBR scale
-
-![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
-The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
-The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
-The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/gbr_cover_timeseries.png){#sfig-ec-earth3-veg-gbr-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/depth_gbr_violin.png){#sfig-ec-earth3-veg-gbr-depth width=`{julia} violin_width`}
-
-![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/dhw_cover_cor_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwcor width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median occupied proportion value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/initial_proportion_gbr_violin.png){#sfig-ec-earth3-veg-gbr-initialproportion width=`{julia} violin_width`}
-
-![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/mean_dhw_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/dhw_tolerance_gbr_violin.png){#sfig-ec-earth3-veg-gbr-dhwtol width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/so_to_si_gbr_violin.png){#sfig-ec-earth3-veg-gbr-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/gbr/log_total_strength_gbr_violin.png){#sfig-ec-earth3-veg-gbr-totalconnectivity width=`{julia} violin_width`} -->
 
 ## GFDL-CM4
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents the median reef depth level in metres.
+Displays results from median timeseries using GFDL-CM4.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate width=`{julia} carb_width`}
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using GFDL-CM4.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate width=`{julia} carb_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
 Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi width=`{julia} violin_width`}
 
-![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
 Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity width=`{julia} violin_width`}
-<!-- 
-### Management area scale
-
-![Reef relative coral cover timeseries clustered within each management area.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/management_area_cover_timeseries.png){#sfig-gfdl-cm4-manarea-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/depth_management_area_violin.png){#sfig-gfdl-cm4-manarea-depth width=`{julia} violin_width`}
-
-![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/dhw_cover_cor_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwcor width=`{julia} violin_width`}
-
-![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/mean_dhw_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/dhw_tolerance_management_area_violin.png){#sfig-gfdl-cm4-manarea-dhwtol width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/initial_proportion_management_area_violin.png){#sfig-gfdl-cm4-manarea-initialproportion width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/so_to_si_management_area_violin.png){#sfig-gfdl-cm4-manarea-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/management_area/log_total_strength_management_area_violin.png){#sfig-gfdl-cm4-manarea-totalconnectivity width=`{julia} violin_width`}
-
-### GBR scale
-
-![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
-The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
-The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
-The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/gbr_cover_timeseries.png){#sfig-gfdl-cm4-gbr-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/depth_gbr_violin.png){#sfig-gfdl-cm4-gbr-depth width=`{julia} violin_width`}
-
-![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/dhw_cover_cor_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwcor width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median occupied proportion value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/initial_proportion_gbr_violin.png){#sfig-gfdl-cm4-gbr-initialproportion width=`{julia} violin_width`}
-
-![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/mean_dhw_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/dhw_tolerance_gbr_violin.png){#sfig-gfdl-cm4-gbr-dhwtol width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/so_to_si_gbr_violin.png){#sfig-gfdl-cm4-gbr-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/gbr/log_total_strength_gbr_violin.png){#sfig-gfdl-cm4-gbr-totalconnectivity width=`{julia} violin_width`} -->
 
 ## NorESM2-MM
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents the median reef depth level in metres.
+Displays results from median timeseries using NorESM2-MM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate width=`{julia} carb_width`}
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
+The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using NorESM2-MM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate width=`{julia} carb_width`}
 
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
+Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
+Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
 Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi width=`{julia} violin_width`}
 
-![Log total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
@@
 ‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
+Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
 Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity width=`{julia} violin_width`}
-<!-- 
-### Management area scale
-
-![Reef relative coral cover timeseries clustered within each management area.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/management_area_cover_timeseries.png){#sfig-noresm2-mm-manarea-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/depth_management_area_violin.png){#sfig-noresm2-mm-manarea-depth width=`{julia} violin_width`}
-
-![Total coral cover – DHW Pearson’s correlation for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median cover – DHW correlation value for each cluster and grey points represent the total cover – DHW correlation value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/dhw_cover_cor_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwcor width=`{julia} violin_width`}
-
-![Mean timeseries DHW for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median mean - DHW value for each cluster and grey points represent the mean - DHW value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/mean_dhw_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median DHW – tolerance value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/dhw_tolerance_management_area_violin.png){#sfig-noresm2-mm-manarea-dhwtol width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median occupied proportion value for each cluster and grey points represent the value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/initial_proportion_management_area_violin.png){#sfig-noresm2-mm-manarea-initialproportion width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/so_to_si_management_area_violin.png){#sfig-noresm2-mm-manarea-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs within each management area, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each management area.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each management area.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each management area.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/management_area/log_total_strength_management_area_violin.png){#sfig-noresm2-mm-manarea-totalconnectivity width=`{julia} violin_width`}
-
-### GBR scale
-
-![Reef relative coral cover timeseries clustered across the Great Barrier Reef.
-The ‘Low’ cluster (green) is the cluster with the lowest median relative cover between 2030 and 2040.
-The ‘Medium’ cluster (orange) is the cluster with intermediate median relative cover between 2030 and 2040.
-The ‘High’ cluster (blue) is the cluster with the highest median relative cover between 2030 and 2040.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/gbr_cover_timeseries.png){#sfig-noresm2-mm-gbr-timeseries width=`{julia} timeseries_width`}
-
-![Median depth for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median depth for each cluster and grey points represent the depth value for each reef.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/depth_gbr_violin.png){#sfig-noresm2-mm-gbr-depth width=`{julia} violin_width`}
-
-![Total coral cover - DHW pearson's correlation for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median total cover – DHW correlation value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/dhw_cover_cor_gbr_violin.png){#sfig-noresm2-mm-gbr-dhwcor width=`{julia} violin_width`}
-
-![Initial proportion of coral-habitable area occupied by coral cover for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median occupied proportion value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/initial_proportion_gbr_violin.png){#sfig-noresm2-mm-gbr-initialproportion width=`{julia} violin_width`}
-
-![Mean DHW for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/mean_dhw_gbr_violin.png){#sfig-noresm2-mm-gbr-dhwmean width=`{julia} violin_width`}
-
-![Mean timeseries DHW – tolerance value for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median DHW - tolerance value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/dhw_tolerance_gbr_violin.png){#sfig-noresm2-mm-gbr-dhwtol width=`{julia} violin_width`}
-
-![Source – to – sink connectivity ratio for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines represent the median source – to – sink ratio value for each cluster and grey points represent the mean source – to – sink value for each reef.
-Vertical grey lines represent a log source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/so_to_si_gbr_violin.png){#sfig-noresm2-mm-gbr-logsosi width=`{julia} violin_width`}
-
-![Log total connectivity strength for reefs, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040.
-Solid lines within each violin represent the median log total connectivity strength for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/gbr/log_total_strength_gbr_violin.png){#sfig-noresm2-mm-gbr-totalconnectivity width=`{julia} violin_width`} -->

### 2025-07-02 paper/paper_draft.qmd
Add justification on spearmans correlation

@@
 To capture the wide influence of environmental factors on carbonate budget levels, we analyse live coral cover thresholds required for positive carbonate budgets from 10 to 20% (inclusive, at step 1%).
+
+The distribution of number of years above carbonate-cover thresholds is right-skewed, with many reefs experiencing low numbers of years above thresholds.
+Similarly, reef median depth levels and log (natural) total connectivity strength levels follow right-skewed distributions.
+Therefore, we analyse the correlation between number of years above carbonate-cover thresholds and these characteristics using Spearman's correlation coefficient.
 

### 2025-07-02 paper/paper_draft.qmd
Add info on carbonate budgets and start of DHW timeseries plotting

@@
 
-Incorporating the latest advancements in whole ecosystem larval connectivity modelling and coral thermal response and adaptation research into coral population modelling allows us to investigate how these abiotic and biotic factors interact and will influence coral climate change resilience into the future.
+Scleractinian corals are primary habitat structures on coral reefs.
+The accumulation and erosion of coral reef carbonate frameworks is controlled by a range of processes such as coral accumulation *Perry*, bioerosion *Tribollet*, physical damage generating coral rubble *Kenyon*, and calcificationa and *CaCO3* dissolution rates *Eyre 2014, 2018*.
+The balance of these processes and occurrance of net carbonate framework production (referred to as a positive carbonate budget) are influenced by factors such as coral cover and complexity *Perry, Desbiens*, rates of physical environmental processes and ocean acidity *Perry, Eyre*.
+It has been suggested that total live coral cover on a reef highly influences the maintainence of net positive carbonate budgets.
+Estimates of live coral cover required to maintain net positive carbonate budget levels range from 10 to 20% *Perry* of a reef's total area, with a level of 17% live coral cover for mid and outershelf reefs on the Great Barrier Reef *Desbiens*.
+
+Incorporating the latest advancements in whole ecosystem larval connectivity modelling and coral thermal response and adaptation research into coral population modelling allows us to investigate how abiotic and biotic factors interact and will influence coral climate change resilience and the maintainence of positive carbonate budgets into the future.
 Improvements in coral reef climate response modelling, including sampling from a range of possible climate futures, allow for fine-scale timeseries analyses of uncertain climate change and ecological scenarios [@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].
@@
 It is hypothesised that sink reefs are more likely to be resilient under climate change, compared to source reefs, due to greater influx of coral recruits post disturbance.
+We predict that increasing connectivity levels will correlate with increasing maintainence of positive carbonate budgets.
 It is hypothesised that reefs with greater depths are more likely to be resilient under future thermal stress, compared to reefs at shallow depths, as they benefit from thermal refugia.
+We predict that increasing reef depth will correlate with increasing maintainence of positive carbonate budgets.
 It is hypothesised that reef cover will decline by greater magnitude as the Equilibrium Climate Sensitivity (ECS) of each Global Climate Model (GCM) increases.
@@
 
+### Carbonate budget analysis
+
+Using median coral cover timeseries for each reef we calculated the number of years each reef maintains coral cover above these live coral cover threshold levels, inferring the number of years each reef maintains a net positive carbonate budget, accumulating reef framework.
+As in situ carbonate budgets are influenced by a range of processes, our calculations of carbonate budget maintainence are intended as estimates and do not reflect the conditions that will be experienced on a reef, but indicate relative levels of health across reefs.
+To capture the wide influence of environmental factors on carbonate budget levels, we analyse live coral cover thresholds required for positive carbonate budgets from 10 to 20% (inclusive, at step 1%).
+
+The distribution of number of years above carbonate-cover thresholds is right-skewed, with many reefs experiencing low numbers of years above thresholds.
+Similarly, reef median depth levels and log (natural) total connectivity strength levels follow right-skewed distributions.
+Therefore, we analyse the correlation between number of years above carbonate-cover thresholds and these characteristics using Spearman's correlation coefficient.
+
 ### Timeseries clustering
@@
 The mean timeseries was calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then used to calculate an overall mean DHW – tolerance value for each reef under each GCM.
-
-## Carbonate budget analysis
-
-Scleractinian corals are primary habitat structures on coral reefs.
-The accumulation and erosion of coral reef carbonate frameworks is controlled by a range of processes such as coral accumulation *Perry*, bioerosion *Tribollet*, physical damage generating coral rubble *Kenyon*, and calcificationa and *CaCO3* dissolution rates *Eyre 2014, 2018*.
-The balance of these processes and occurrance of net carbonate framework production (referred to as a positive carbonate budget) are influenced by factors such as coral cover and complexity *Perry, Desbiens*, rates of physical environmental processes and ocean acidity *Perry, Eyre*.
-It has been suggested that total live coral cover on a reef highly influences the maintainence of net positive carbonate budgets.
-Estimates of live coral cover required to maintain net positive carbonate budget levels range from 10 to 20% *Perry* of a reef's total area, with a level of 17% live coral cover for the Great Barrier Reef *Desbiens*.
-Using median absolute cover timeseries for each reef we calculated the number of years each reef maintains coral cover above these live coral cover threshold levels, inferring the number of years each reef maintains a net positive carbonate budget, accumulating reef framework.
-As in situ carbonate budgets are influenced by a range of processes, our calculations of carbonate budget maintainence are intended as estimates and do not reflect the conditions that will be experienced on a reef, but indicate relative levels of health across reefs.
-To capture the wide influence of environmental factors on carbonate budget levels, we analyse live coral cover thresholds required for positive carbonate budgets from 10 to 20% (inclusive, at step 1%).
-
-The distribution of number of years above carbonate-cover thresholds is right-skewed, with many reefs experiencing low numbers of years above thresholds.
-Similarly, reef median depth levels and log (natural) total connectivity strength levels follow right-skewed distributions.
-Therefore, we analyse the correlation between number of years above carbonate-cover thresholds and these characteristics using Spearman's correlation coefficient.
 
@@
 
-Timeseries analysis has been used to identify three groups of reefs with similar declining (low), recovering (high), and intermediate (medium) coral cover trajectories throughout future scenarios.
 Under all GCMs most reefs suffer substantial declines in coral cover from 2025 levels.
 NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintanance into the future.
-Differences between low, medium and high reef clusters in their timeseries are most notable under these two GCMs.
+Differences between low, medium and high reef clusters in cover timeseries are most notable under these two GCMs.
 
@@
 Therefore, the estimates of reef depths are taken as a useful indication rather than an accurate and precise report of reef depths across the GBR.
-
-<!-- liu2024 citation -->
 

### 2025-07-02 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -131,6 +131,7 @@ analysis_layers_long = stack(
 )
 analysis_layers_long.GCM = [first(split(name, "_")) for name in analysis_layers_long.variable]
 
+# Collate all cover timeseries and plot them grouped by management area
 rel_cover_arrays = [
     percentage_cover_timeseries(
         areas, 
@@ -154,6 +155,8 @@ save(
     GCM_comparison_plot,
     px_per_unit = dpi
 )
+
+# Collate all DHW timeseries and plot them grouped by management area
 
 analysis_layers = context_layers[context_layers.UNIQUE_ID .∈ [unique(analysis_layers_long.UNIQUE_ID)], :]
 reefs_with_clusters = (

### 2025-07-03 paper/paper_draft.qmd
Add text on DHW timeseries plot

@@
 Results for the additional GCMs are displayed in the supplementary material.
-However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus relative coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-trajectories).
+However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus relative coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
+
+Under each GCM, in all management areas, low, medium and high cluster reefs have low differences between DHW trajectories (@sfig-gcm-dhw-trajectories).
+The highest peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHW timeseries occur under ACCESS-CM2.
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#fig-gcm-trajectories width=`{julia} timeseries_width`}
+Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories width=`{julia} timeseries_width`}
 
@@
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_timeseries_plot.png){#sfig-gcm-trajectories width=`{julia} timeseries_width`}
+Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories width=`{julia} timeseries_width`}
 

### 2025-07-05 src/ADRIA/HighResCoralStress/1_GCM_model_runs.jl
Remove duplicate imports
Packages were already imported in `common.jl`

Remove unused packages

@@ -4,8 +4,6 @@ using YAXArrays, NetCDF
 include("../../common.jl")
 change_ADRIA_debug(false) # Ensure ADRIA debug mode is set to false to allow parallel processing.
 
-using ADRIA
-
 GBR_domain_path = "../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/"
 dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
 gcms = dhw_scenarios.dhw.properties["members"]

### 2025-07-05 src/ADRIA/HighResCoralStress/2_timeseries_clustering_absolute.jl

@@ -5,13 +5,6 @@ reef cover as a percentage of total reef area is used.
 
 using Revise, Infiltrator
 
-using GLMakie, GeoMakie, GraphMakie
-using Statistics
-using YAXArrays
-import GeoDataFrames as GDF
-
-using ADRIA
-
 include("../../common.jl")
 includet("../../plotting_functions.jl")
 

### 2025-07-05 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -4,17 +4,9 @@ connections for each reef. Add context information such as reef DHW levels, year
 budget thresholds, DHW tolerance levels and number of reefs in each bioregion.
 """
 
-using DataFrames, Statistics, YAXArrays, ArchGDAL
-
-using GLMakie, GeoMakie, GraphMakie
-
-import GeoDataFrames as GDF
-
-import GeoFormatTypes as GFT
+using ArchGDAL
 
 change_ADRIA_debug(true) # Change ADRIA debug mode to true to extract DHW tolerance data from runs
-
-using ADRIA
 
 include("../../common.jl")
 

### 2025-07-05 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -5,13 +5,6 @@ and multi-GCM comparison plot created at end of the script.
 
 using Revise, Infiltrator
 
-using GLMakie, GeoMakie, GraphMakie
-using Statistics
-using YAXArrays
-using CairoMakie
-
-using ADRIA
-
 include("../../common.jl")
 include("../../plotting_functions.jl")
 

### 2025-07-05 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -4,13 +4,6 @@ Script to create additional plots required for publication. E.g. maps and GCM pl
 
 using Revise, Infiltrator
 
-using GLMakie, GeoMakie, GraphMakie
-using Statistics
-using YAXArrays
-using CairoMakie
-
-using ADRIA
-
 import GeometryOps as GO
 
 include("../../common.jl")

### 2025-07-05 src/common.jl

@@ -16,7 +16,7 @@ using
 using
     ColorSchemes,
     GeoMakie,
-    # GLMakie,
+    CairoMakie,
     GraphMakie
 
 using

### 2025-07-05 src/ADRIA/HighResCoralStress/1_GCM_model_runs.jl
Auto-format code, clear whitespace

@@ -39,9 +39,9 @@ for GCM in gcms
             Dim{:timesteps}(Int64.(scenario_cover.timesteps)),
             Dim{:locations}(string.(scenario_cover.locations))
         )
-        properties=median_cover.properties
+        properties = median_cover.properties
         pop!(properties, :is_relative)
-        properties = Dict{String, Any}([(string.(k), v) for (k,v) in properties])
+        properties = Dict{String,Any}([(string.(k), v) for (k, v) in properties])
 
         median_cover = rebuild(median_cover, dims=dims, metadata=properties)
         savecube(median_cover, processed_outputs, driver=:netcdf, overwrite=true)

### 2025-07-05 src/ADRIA/HighResCoralStress/2_timeseries_clustering_absolute.jl

@@ -28,7 +28,7 @@ n_clusters = 3
 areas = gbr_dom.loc_data.area
 
 for GCM in dhw_scenarios.dhw.properties["members"]
-    
+
     # Select GCM and load relevant results
     @info "Performing timeseries clustering for $(GCM)"
 

### 2025-07-05 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -40,24 +40,24 @@ col_types = [
 source_to_sink = DataFrame(
     [T[] for T in col_types],
     [
-    :UNIQUE_ID,
-    :income_strength,
-    :income_count,
-    :income_comb,
-    :out_strength,
-    :out_count,
-    :out_comb,
-    :total_strength,
-    :total_count,
-    :total_comb,
-    :so_to_si,
+        :UNIQUE_ID,
+        :income_strength,
+        :income_count,
+        :income_comb,
+        :out_strength,
+        :out_count,
+        :out_comb,
+        :total_strength,
+        :total_count,
+        :total_comb,
+        :so_to_si,
     ]
 )
 
 for reef in eachindex(reefs)
     reef_id = reefs[reef]
-    outgoing = connectivity_matrix[connectivity_matrix.Source .== reef_id, :]
-    incoming = connectivity_matrix[:, connectivity_matrix.Sink .== reef_id]
+    outgoing = connectivity_matrix[connectivity_matrix.Source.==reef_id, :]
+    incoming = connectivity_matrix[:, connectivity_matrix.Sink.==reef_id]
 
     income_strength = sum(incoming)
     income_count = count(incoming .> 0)
@@ -83,17 +83,17 @@ for reef in eachindex(reefs)
     push!(
         source_to_sink,
         [
-        reef_id,
-        income_strength,
-        income_count,
-        income_comb,
-        out_strength,
-        out_count,
-        out_comb,
-        total_strength,
-        total_count,
-        total_comb,
-        so_to_si
+            reef_id,
+            income_strength,
+            income_count,
+            income_comb,
+            out_strength,
+            out_count,
+            out_comb,
+            total_strength,
+            total_count,
+            total_comb,
+            so_to_si
         ]
     )
 end
@@ -101,7 +101,7 @@ end
 context_layers = leftjoin(context_layers, source_to_sink; on=:UNIQUE_ID, order=:left)
 
 context_layers.initial_coral_cover = vec(
-    sum(gbr_dom.init_coral_cover; dims=1).data' .* 
+    sum(gbr_dom.init_coral_cover; dims=1).data' .*
     gbr_dom.loc_data.area .*
     gbr_dom.loc_data.k
 )
[…]

### 2025-07-05 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -52,11 +52,11 @@ for (i_gcm, GCM) in enumerate(GCMs)
     # threshold_cover = threshold_cover_timeseries(areas, absolute_cover, 0.17)
     threshold_cover = percentage_cover_timeseries(areas, absolute_cover)
 
-    dhw_ts = gbr_dom.dhw_scens[:,:,i_gcm]
+    dhw_ts = gbr_dom.dhw_scens[:, :, i_gcm]
     dhw_ts = rebuild(dhw_ts, dims=threshold_cover.axes)
 
     # Subset layers to remove reefs that start with very low coral cover
-    analysis_layers = context_layers[(context_layers.management_area .!= "NA") .& (context_layers.bioregion .!= "NA"), :]
+    analysis_layers = context_layers[(context_layers.management_area.!="NA").&(context_layers.bioregion.!="NA"), :]
 
     # Analysing clusters identified at bioregion level
     cluster_analysis_plots(GCM, analysis_layers, threshold_cover, dhw_ts, :bioregion, fig_out_dir)
@@ -66,51 +66,51 @@ for (i_gcm, GCM) in enumerate(GCMs)
     gcm_reefs_long = reefs_long[contains.(reefs_long.variable, GCM), :]
     gcm_reefs_long.variable = last.(split.(gcm_reefs_long.variable, "_"))
     gcm_reefs_long_depth = gcm_reefs_long[
-        gcm_reefs_long.UNIQUE_ID .∈ [context_layers[context_layers.depth_qc .== 0, :UNIQUE_ID]],
-    :]
+        gcm_reefs_long.UNIQUE_ID.∈[context_layers[context_layers.depth_qc.==0, :UNIQUE_ID]],
+        :]
 
     depth_year_correlation = Dict([
         (thresh, corspearman(
-            gcm_reefs_long_depth[gcm_reefs_long_depth.variable .== thresh, :value],
-            gcm_reefs_long_depth[gcm_reefs_long_depth.variable .== thresh, :depth_med]
+            gcm_reefs_long_depth[gcm_reefs_long_depth.variable.==thresh, :value],
+            gcm_reefs_long_depth[gcm_reefs_long_depth.variable.==thresh, :depth_med]
         ))
         for thresh in string.(thresholds)
     ])
 
     depth_carbonate_scatter = carbonate_budget_variable_scatter(
-        gcm_reefs_long_depth, 
-        :depth_med, 
[…]

### 2025-07-05 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -21,18 +21,17 @@ ecs_values = Dict(
     "GFDL-CM4" => 2.9,
     "NorESM2-MM" => 2.5
 )
-ecs = ecs_plot(collect(values(ecs_values)), [2.5,5.1], [2.1,7.7], collect(keys(ecs_values)))
-save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit = 300/inch)
+ecs = ecs_plot(collect(values(ecs_values)), [2.5, 5.1], [2.1, 7.7], collect(keys(ecs_values)))
+save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit=300 / inch)
 
 # GBR map plot - methods
 investigation_reefs = context_layers[
-    (context_layers.management_area .!= "NA") .& 
-    (context_layers.bioregion .!= "NA"),
-:]
+    (context_layers.management_area.!="NA").&(context_layers.bioregion.!="NA"),
+    :]
 regions = GDF.read("../data/GBRMPA_Management_Areas.gpkg")
 regions.region_name = ["Mackay/Capricorn", "Cairns/Cooktown", "Far Northern", "Townsville Whitsunday"]
 qld = GDF.read("../data/GBRMPA_Reef_Features.gpkg")
-qld = qld[qld.FEAT_NAME .== "Mainland", :SHAPE]
+qld = qld[qld.FEAT_NAME.=="Mainland", :SHAPE]
 
 map_width = fig_sizes["map_width"]
 map_height = fig_sizes["map_height"]
@@ -40,26 +39,26 @@ region_col = tuple.(Makie.wong_colors()[1:4], repeat([0.3], 4)) # Manually set a
 
 ordered_reefs = sort(investigation_reefs, :bioregion_average_latitude; rev=true)
 bioregion_colors_labels = DataFrame(
-    bioregion = unique(investigation_reefs.bioregion),
-    ref = 1:length(unique(investigation_reefs.bioregion)),
-    color = distinguishable_colors(length(unique(investigation_reefs.bioregion))),
-    label = label_lines.((unique(investigation_reefs.bioregion)); l_length=17)
+    bioregion=unique(investigation_reefs.bioregion),
+    ref=1:length(unique(investigation_reefs.bioregion)),
+    color=distinguishable_colors(length(unique(investigation_reefs.bioregion))),
+    label=label_lines.((unique(investigation_reefs.bioregion)); l_length=17)
 )
[…]

### 2025-07-05 src/common.jl

@@ -193,7 +193,7 @@ Calculate the cover of a site at each timestep of x relative to the site's initi
 function relative_site_cover(x)
     init = x[1]
     for (index, step) in enumerate(x)
-        x[index] = x[index]/init
+        x[index] = x[index] / init
     end
 
     return x
@@ -204,10 +204,10 @@ canonical_reefs = GDF.read(canonical_reefs)
 
 # Get location indices
 REGION_REEFS = DataStructures.OrderedDict(
-    "Far Northern Management Area"=>Int64[],
-    "Cairns/Cooktown Management Area"=>Int64[],
-    "Townsville/Whitsunday Management Area"=>Int64[],
-    "Mackay/Capricorn Management Area"=>Int64[],
+    "Far Northern Management Area" => Int64[],
+    "Cairns/Cooktown Management Area" => Int64[],
+    "Townsville/Whitsunday Management Area" => Int64[],
+    "Mackay/Capricorn Management Area" => Int64[],
 )
 
 for mgmt_area in collect(keys(REGION_REEFS))
@@ -246,20 +246,20 @@ function connectivity_scoring(
 )::DataFrame
     RME_UNIQUE_ID = collect(getAxis("Source", conn_matrix).val)
     connectivity_scores = DataFrame(
-        [RME_UNIQUE_ID, Vector{Union{Missing, Float64}}(missing, 3806)],
+        [RME_UNIQUE_ID, Vector{Union{Missing,Float64}}(missing, 3806)],
         [:RME_UNIQUE_ID, :conn_score]
     )
 
     if by_layer
         for level in unique(gdf[:, context_layer])
-            level_reefs = gdf[gdf[:, context_layer] .== level, :RME_UNIQUE_ID]
-            level_matrix = conn_matrix[conn_matrix.Source .∈ [level_reefs], conn_matrix.Sink .∈ [level_reefs]]
+            level_reefs = gdf[gdf[:, context_layer].==level, :RME_UNIQUE_ID]
+            level_matrix = conn_matrix[conn_matrix.Source.∈[level_reefs], conn_matrix.Sink.∈[level_reefs]]
 
             g = SimpleWeightedDiGraph(level_matrix)
             conn_scores = Dict(zip(collect(level_matrix.Source), eigenvector_centrality(g)))
 
             for (k, v) in conn_scores
-                connectivity_scores[connectivity_scores.RME_UNIQUE_ID .== k, :conn_score] .= v
[…]

### 2025-07-05 paper/paper_draft.qmd
clear whitespace
Revisions for clarity/flow

@@
 
-Climate change is impacting species survival, persistence and ecosystem functions globally, including coral.
+Climate change is impacting species survival, persistence and ecosystem functions globally, including coral reefs.
 Coral reefs are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading [@foster2021; @gattuso2014].
@@
 They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@grimaldi2022].
-Severe declines in coral cover are projected due to compounding impacts such as ocean warming and acidification, intensification of Tropical Cyclones, and Crown of Thorns Starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
-Ominously, the 2023-24 Summer mass bleaching event ([@cantin2024]) may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs.
+Current modelling project severe declines in coral cover under projections of Degree Heating Weeks [https://www.biorxiv.org/content/10.1101/2025.01.23.634487v1].
+These coral cover declines will be compounded by ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
+Ominously, the 2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs [@cantin2024].
 
+Connectivity is said to play a crucial role in Great Barrier Reef resilience by enabling recolonization after disturbances and facilitating adaptation to climate pressures [@angeler2023; @elmhirst2009; @hock2017].
+This connectivity, however, creates both strengths and vulnerabilities within the system.
+Larval source populations (those exporting more larvae than they import) are essential for system-wide resilience, as they provide larvae that enable recovery at distant locations after disturbances [@hock2017; @thomas2015].
+Individually, however, they are more vulnerable to extreme disturbances as they rely more heavily on local recruitment to support recovery.
+In contrast, sink populations can draw on external larval inputs from multiple and diverse sources [@ani2024; @hock2017].
+When disturbances impact major larval source populations, the cascading effects extend throughout the network.
+Increased adult mortality reduces larval export in subsequent years, slowing recovery at the connected sink locations that depend on this external supply [@figueiredo2022; @hock2017; @munday2009].
+Future climate change will further complicate these dynamics through population fragmentation, increased larval mortality, and altered hydrodynamics, potentially disrupting the connectivity patterns that currently maintain reef resilience.
+
+Beyond connectivity, coral resilience to climate change is determined by the complex interplay of environmental and biological factors.
 Environmental abiotic factors influence how reefs will experience climate change pressures, including the spatio-temporal patterns of thermal stress itself, and indirect factors that influence the stress experienced by corals.
 Environmental factors such as tropical cyclones and wind driven mixing [@lin2023; @mcclanahan2005]; currents [@grimaldi2022] and depth [@álvarez-noriega2018; @baird2018; @smith2014] can decrease the magnitude of thermal stress corals experience.
-On the other hand, high light intensity and nutrient levels in the benthic zone can increase coral bleaching [@decarlo2020; @higuchi2015].
-These environmental factors influence the resilience of reefs to climate change pressures in combination with related biological factors such as larval connectivity and thermal tolerance.
+Conversely, high light intensity and nutrient levels in the benthic zone can increase coral bleaching [@decarlo2020; @higuchi2015].
 
-Connectivity in systems such as the GBR is an important contributor to system resilience, as strong connections are required to repopulate locations after disturbance, and drive adaptation to climate pressures [@angeler2023; @elmhirst2009; @hock2017].
-When populations that are strong larval suppliers to external reefs are impacted by disturbances, increased adult coral mortality will cause decreased outgoing larvae in the following years.
-Weaker larval connections then slow the recovery of the externally connected locations [@figueiredo2022; @hock2017; @munday2009].
-Populations with greater strength and number of outgoing than incoming larval connections - herein referred to as larval sources - have lower resilience to pressures than populations with greater incoming than outgoing larval flows - referred to as larval sinks - as larval source populations lack external sources of larvae that are important in contributing to reef recovery and recruitment of juveniles after disturbances to existing populations [@ani2024; @hock2017].
-Larval source populations are an important component of overall reef resilience as they can contribute larvae to recovering populations at other locations [@hock2017; @thomas2015].
-Connectivity will be altered by future climate change impacts such as population fragmentation, increasing larval mortality, and changes to coastal hydrodynamics [@figueiredo2022; @munday2009], and influences the biology of surrounding reef populations.
+Individual coral resilience also depends on multiple biological factors beyond connectivity.
+Coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and acclimation and inherited thermal tolerance [@humanes2022; @lachs2024] all influence the outcome of high coral heat stress events.
+Importantly, corals have demonstrated adaptive capacity to develop thermal tolerance levels capable of delaying the onset of widespread bleaching under low emissions scenarios [@bairos-novak2021; @humanes2022].
+This adaptive potential represents a crucial mechanism for reef persistence under moderate climate change, working in concert with the environmental factors that modulate thermal stress exposure.
 
-Many additional biological factors including coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and acclimation and inherited thermal tolerance[@humanes2022; @lachs2024], influence the outcome of high coral heat stress.
-It has been shown that corals have the adaptive capacity to develop thermal tolerance levels capable of delaying the onset of widespread bleaching under low emissions scenarios [@bairos-novak2021; @humanes2022].
+While these environmental and biological factors determine whether individual corals survive thermal stress events, the long-term viability of coral reefs depends not only on coral survival but also on the maintenance of reef structure through positive carbonate budgets.
+Scleractinian corals are primary habitat structures on coral reefs, and the accumulation and erosion of coral reef carbonate frameworks is controlled by a range of processes including coral accumulation [**Perry**], bioerosion [**Tribollet**], physical damage generating coral rubble [**Kenyon**], and calcification and CaCO₃ dissolution rates [**Eyre 2014, 2018**].
+The balance of these processes and occurrence of net carbonate framework production (referred to as a positive carbonate budget) are influenced by factors such as coral cover and complexity [**Perry, Desbiens**], rates of physical environmental processes, and ocean acidity [**Perry, Eyre**].
+Total live coral cover on a reef highly influences the maintenance of net positive carbonate budgets, with estimates ranging from 10 to 20% [**Perry**] of a reef's total area required to maintain positive budgets.
+For mid and outer shelf reefs on the Great Barrier Reef, this threshold is approximately 17% live coral cover [**Desbiens**].
 
-Scleractinian corals are primary habitat structures on coral reefs.
-The accumulation and erosion of coral reef carbonate frameworks is controlled by a range of processes such as coral accumulation *Perry*, bioerosion *Tribollet*, physical damage generating coral rubble *Kenyon*, and calcificationa and *CaCO3* dissolution rates *Eyre 2014, 2018*.
-The balance of these processes and occurrance of net carbonate framework production (referred to as a positive carbonate budget) are influenced by factors such as coral cover and complexity *Perry, Desbiens*, rates of physical environmental processes and ocean acidity *Perry, Eyre*.
-It has been suggested that total live coral cover on a reef highly influences the maintainence of net positive carbonate budgets.
-Estimates of live coral cover required to maintain net positive carbonate budget levels range from 10 to 20% *Perry* of a reef's total area, with a level of 17% live coral cover for mid and outershelf reefs on the Great Barrier Reef *Desbiens*.
-
-Incorporating the latest advancements in whole ecosystem larval connectivity modelling and coral thermal response and adaptation research into coral population modelling allows us to investigate how abiotic and biotic factors interact and will influence coral climate change resilience and the maintainence of positive carbonate budgets into the future.
-Improvements in coral reef climate response modelling, including sampling from a range of possible climate futures, allow for fine-scale timeseries analyses of uncertain climate change and ecological scenarios [@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].
-
-It is hypothesised that sink reefs are more likely to be resilient under climate change, compared to source reefs, due to greater influx of coral recruits post disturbance.
-We predict that increasing connectivity levels will correlate with increasing maintainence of positive carbonate budgets.
-It is hypothesised that reefs with greater depths are more likely to be resilient under future thermal stress, compared to reefs at shallow depths, as they benefit from thermal refugia.
-We predict that increasing reef depth will correlate with increasing maintainence of positive carbonate budgets.
-It is hypothesised that reef cover will decline by greater magnitude as the Equilibrium Climate Sensitivity (ECS) of each Global Climate Model (GCM) increases.
+Incorporating the latest advancements in whole ecosystem larval connectivity modeling and coral thermal response and adaptation research into coral population modeling allows an investigation into how abiotic and biotic factors interact to influence coral climate change resilience and the maintenance of positive carbonate budgets.
+Improvements in coral reef climate response modeling, including sampling from a range of possible climate futures, enable timeseries analyses of uncertain climate change and ecological scenarios [@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].
+While it has previously been suggested that highly connected source reefs that are resilient to bleaching and CoTS outbreaks are likely to play a critical role in supporting future reef recovery across the entire GBR [@hock2017], integrated modelling under current projections of Degree Heating Weeks indicate that depth, rather than connectivity, plays the critical role in determining reef resilience.
+It is further demonstrated that depth ameliorates reef cover declines and supports maintenance of a postive carbonate budget as the Equilibrium Climate Sensitivity (ECS) of each Global Climate Model (GCM) increases.
 
@@
 
-![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points).
-The green polygon represents the Far Northern management area, the yellow polygon represents the Cairns/Cooktown management area, the pink polygon represents the Townsville/Whitsunday management area and the blue polygon represents the Mackay/Capricorn management area.
-The centroid of each reef is represented as a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion.
-An annotation represents the approximate location of the Australian Institute of Marine Science Townsville site at Cape Cleveland.](/../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map width=`{julia} map_width`}
-
 The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas.
-It follows the reef definitions as adopted in ReefMod-GBR [@bozec2022] (@fig-region-map).
+It follows the reef definitions as provided by the Great Barrier Reef Marine Park Authority [https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94].
 Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future thermal stress at each reef location.
-Five Global Climate Models (GCMs) (EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6) were selected for this study.
+Five Global Climate Models (GCMs) (EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6; **citation**) were selected for this study.
 Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great Barrier Reef were obtained from the HighResCoralStress database [@dixon2022; @dixon].
@@
 
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points).
+The green polygon represents the Far Northern management area, the yellow polygon represents the Cairns/Cooktown management area, the pink polygon represents the Townsville/Whitsunday management area and the blue polygon represents the Mackay/Capricorn management area.
+The centroid of each reef is represented as a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion.
+An annotation represents the approximate location of the Australian Institute of Marine Science Townsville site at Cape Cleveland.](/../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map width=`{julia} map_width`}
+
 ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
@@
 
-## Coral reef ecosystem model - ADRIA x CoralBlox
+## Coral reef ecosystem model - ADRIA-CoralBlox
 
@@
 Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
-[-@bairos-novak2021] and unpublished data from Hughes et al.
-[-@hughes2018].
+[-@bairos-novak2021].
 
-Tropical cyclones and wave impacts to reefs are not included in this investigation.
+Tropical cyclones and impact of wave activity to reefs are not included in this investigation.
 We scale coral bleaching impacts by a coefficient determined by the median depth of each reef location, following Baird et al.
@@
 Due to varying degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs with less than 5% coverage of valid bathymetry data have been removed from this investigation.
-Furthermore, reefs that are not allocated to a GBRMPA management area or bioregion have been removed from the investigation, as well as reefs with relative coral cover values greater than five.
+Furthermore, reefs that were outside the GBRMPA management areas or not associated with a bioregion were removed from the investigation, as well as reefs with relative coral cover values greater than five [**five what???**].
 
@@
 
-To identify groups of reefs at each analysis scale that are resilient, intermediate and non-resilient we clustered reef coral cover timeseries into three clusters at each scale.
-To quantify the behaviour of timeseries and identify timeseries that behave similarly we calculate the complexity-invariant distance (CID) between each timeseries.
-The complexity-invariant distance refers to the Euclidean distance between two timeseries multiplied (corrected) by the ratio of the complexities of the timeseries [@batista2014].
-These values create a distance matrix of n * n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm [@steinmann2020].
+To identify groups of reefs that are resilient, intermediate, and non-resilient, we clustered reefs by their temporal behaviour as indicated by their coral cover over time.
+The Complexity-Invariant Distance (CID) between each timeseries was calculated to identify timeseries that behave similarly [@batista2014].
+The CID corrects the Euclidean distance between pairs of timeseries (which accounts for magnitude differences) with the complexity of each timeseries (obtained through a measure of their variability) to ensure reefs are clustered based on their underlying temporal dynamics rather than simply their average coral cover.
+The process creates a distance matrix of n * n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm [cf.
+@steinmann2020].
 
-Timeseries clustering analyses were performed at the reefal bioregion scale to capture groups of biogeographically similar reefs, as determined by *insert citation for bioregions*.
-Analyses were also performed at higher spatial scales, GBRMPA management regions and whole GBR scale.
-Similar results were found at large spatial scales, these can be found at *insert citation for repository*.
+Timeseries clustering analyses were performed at the reefal bioregion scale (defined in [https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::reefal-marine-bioregions/about]).
+Additional analyses were also performed at larger spatial scales, such as the GBRMPA management regions and whole-of-GBR scale.
+These were found to lead to identical conclusions and so are not shown here.
+Results of these analyses can be found at [**insert citation for repository**] for those interested.
 
-Reefs in each cluster are compared to identify characteristics that differ between low, medium and high coral cover clusters.
+Reefs in each timeseries cluster are compared to identify characteristics that differ between low, medium and high coral cover clusters.
 These characteristics include reef median depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation between total coral cover and inversed DHW timeseries, proportion of coral habitable area occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and total strength of larval connections between reefs.
@@
 We provide evidence in support of depth as a form of refugia for shallow reefs.
-While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts [@anthony2020; @hock2017], our results suggest that resilient reefs do not have greater incoming or total connectivity to contribute to their resilience.
+While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts [@anthony2020; @hock2017], our results suggest that resilient reefs do not have greater incoming or total connectivity to contribute to their resilience under modelled projected conditions.
 Instead, we suggest that depth, and likely other environmental thermal refugia mechanisms contribute greater to overall reef resilience and recovery.

### 2025-07-05 paper/paper_draft.qmd
Remove unneeded information from 'relative' coral cover analyses

@@
 Due to varying degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs with less than 5% coverage of valid bathymetry data have been removed from this investigation.
-Furthermore, reefs that were outside the GBRMPA management areas or not associated with a bioregion were removed from the investigation, as well as reefs with relative coral cover values greater than five [**five what???**].
+Furthermore, reefs that were outside the GBRMPA management areas or not associated with a bioregion were removed from the investigation.
 
@@
 Results for the additional GCMs are displayed in the supplementary material.
-However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus relative coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
+However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
 

### 2025-07-07 paper/paper_draft.qmd
Reduce use of certain language and specify where coral cover is relative
Specified in figure captions that coral cover is relative to reef area, rather than relative to other reefs or initial conditions. Additionally updated the text on cover timeseries and make clear reminders of where text/citations need to be added.

@@
 They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@grimaldi2022].
-Current modelling project severe declines in coral cover under projections of Degree Heating Weeks [https://www.biorxiv.org/content/10.1101/2025.01.23.634487v1].
+Current modelling projects severe declines in coral cover under projections of Degree Heating Weeks [**Bozec 2025**].
 These coral cover declines will be compounded by ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
@@
 
-Individual coral resilience also depends on multiple biological factors beyond connectivity.
+Individual coral resilience depends on multiple biological factors beyond connectivity.
 Coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and acclimation and inherited thermal tolerance [@humanes2022; @lachs2024] all influence the outcome of high coral heat stress events.
@@
 Improvements in coral reef climate response modeling, including sampling from a range of possible climate futures, enable timeseries analyses of uncertain climate change and ecological scenarios [@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].
-While it has previously been suggested that highly connected source reefs that are resilient to bleaching and CoTS outbreaks are likely to play a critical role in supporting future reef recovery across the entire GBR [@hock2017], integrated modelling under current projections of Degree Heating Weeks indicate that depth, rather than connectivity, plays the critical role in determining reef resilience.
-It is further demonstrated that depth ameliorates reef cover declines and supports maintenance of a postive carbonate budget as the Equilibrium Climate Sensitivity (ECS) of each Global Climate Model (GCM) increases.
+While it has previously been suggested that highly connected source reefs that are resilient to bleaching and CoTS outbreaks are likely to play a critical role in supporting future reef recovery across the entire GBR [@hock2017], integrated modelling under current projections of Degree Heating Weeks indicate that depth, rather than connectivity, plays a critical role in determining reef resilience.
+It is further demonstrated that depth supports the maintenance of a postive carbonate budget under all Global Climate Models.
 
@@
 
-ADRIA-CoralBlox was run for 4096 *sampled* scenarios per GCM.
+ADRIA-CoralBlox was run for 4096 **sampled** scenarios per GCM.
 A median absolute coral cover timeseries for each reef was calculated for each GCM.
@@
 
-Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’ coral cover and contextual analysis factors, thus visual further comparisons of these clusters for each analysis factor are only shown for ACCESS-ESM1-5 GCM (intermediate ECS scenario).
+Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’ coral cover and contextual analysis factors, thus further comparisons of these clusters for each analysis factor are only shown for ACCESS-ESM1-5 (intermediate ECS scenario).
 Results for the additional GCMs are displayed in the supplementary material.
-However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
+However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover timeseries are displayed for each GCM (displayed clustered at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
+
+NorESM2-MM has the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline dynamics up to 2075 under this possible climate future.
+While recovery phases are predominantly seen in the ‘high’ cover cluster, the ‘medium’ cluster, and to a lesser degree the ‘low’ cluster, also exhibit periods of recovery and increasing proportions of coral cover up to 2045.
+Under NorESM2-MM GCM the Far Northern management area does not see coral cover maintenance as high as the three remaining management regions.
+Under the second lowest ECS projection (GFDL-CM4, 2.9°C) all clusters in each management area exhibit largely declining future trajectories with periods of recovery from 2030 to 2040.
+ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which results in intermediate levels of coral cover maintenance (between those of lower and higher ECS GCMs).
+In Townsville/Whitsunday and Far Northern management areas reefs in the high cluster are able to maintain coral cover levels around 20% to 2050 under ACCESS-ESM1-5.
+Under ACCESS-CM2 (4.72°C) and EC-Earth3-Veg (4.31°C) GCMs cover trajectories are largely declining in all management areas.
 
@@
 
-NorESM2-MM has the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline dynamics up to 2074 under this possible climate future.
-While recovery phases are predominantly seen in the ‘high’ cover cluster, the ‘medium’ cluster, and to a lesser degree the ‘low’ cluster, also exhibit periods of increasing relative coral cover up to 2045.
-Under NorESM2-MM GCM the Far Northern management area does not see relative coral cover maintenance as high as the three remaining management regions.
-Under the second lowest ECS projection (GFDL-CM4, 2.9°C) all clusters in each management area exhibit largely declining future trajectories with periods of recovery from 2030 to 2040.
-ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which results in intermediate levels of coral cover maintenance (between those of lower and higher ECS GCMs).
-In all management areas reefs in the high cluster are able to maintain relative coral cover levels to 2050 under ACCESS-ESM1-5.
-Under ACCESS-CM2 (4.72°C) and EC-Earth3-Veg (4.31°C) GCMs relative cover trajectories are largely declining, with the exception of ‘high/medium’ clusters in the Cairns-Cooktown management area under EC-Earth3-Veg that display prolonged relative cover maintenance.
-
-![Reef relative coral cover timeseries clustered within each management area, for each GCM analysed.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+![Reef area-relative coral cover timeseries clustered within each management area, for each GCM analysed.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
@@
 
-Within bioregions timeseries clustering analysis was able to identify three clusters of relative cover timeseries.
-Across many bioregions timeseries clustering identified a ‘low’ cluster containing reefs that suffer larger declines and generally have lower levels of relative coral cover than the other clusters, a ‘medium’ cluster with intermediate levels of relative coral cover, and a ‘high’ cluster with cover recovery that persists to 2050 in many bioregions (@sfig-access-esm1-5-bioregion-timeseries; @sfig-access-cm2-bioregion-timeseries; @sfig-ec-earth3-veg-bioregion-timeseries; @sfig-gfdl-cm4-bioregion-timeseries; @sfig-noresm2-mm-bioregion-timeseries).
+Within bioregions timeseries clustering analysis was able to identify three clusters of area-relative cover timeseries.
+Across many bioregions timeseries clustering identified a ‘low’ cluster containing reefs that suffer larger declines and generally have lower levels of coral cover than the other clusters, a ‘medium’ cluster with intermediate levels of coral cover, and a ‘high’ cluster with greater levels of cover recovery, with persistence to 2050 in some bioregions (@sfig-access-esm1-5-bioregion-timeseries; @sfig-access-cm2-bioregion-timeseries; @sfig-ec-earth3-veg-bioregion-timeseries; @sfig-gfdl-cm4-bioregion-timeseries; @sfig-noresm2-mm-bioregion-timeseries).
 
-In many bioregions, median reef depth decreases as cluster relative coral cover decreases, with reefs within the ‘high’ cluster commonly having the greatest median reef depths within the bioregion (@fig-access-esm1-5-bioregion-depth; @sfig-access-cm2-bioregion-depth; @sfig-ec-earth3-veg-bioregion-depth; @sfig-gfdl-cm4-bioregion-depth; @sfig-noresm2-mm-bioregion-depth).
+In many bioregions, median reef depth decreases as cluster coral cover decreases, with reefs within the ‘high’ cluster commonly having the greatest median reef depths within the bioregion (@fig-access-esm1-5-bioregion-depth; @sfig-access-cm2-bioregion-depth; @sfig-ec-earth3-veg-bioregion-depth; @sfig-gfdl-cm4-bioregion-depth; @sfig-noresm2-mm-bioregion-depth).
 
 ![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the median depth for each cluster.
@@
 
-Correlation between reef total coral cover and reef DHW timeseries decreases as cluster relative coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total cover – DHW timeseries correlation levels (@sfig-access-esm1-5-bioregion-dhwcor; @sfig-access-cm2-bioregion-dhwcor; @sfig-ec-earth3-veg-bioregion-dhwcor; @sfig-gfdl-cm4-bioregion-dhwcor; @sfig-noresm2-mm-bioregion-dhwcor).
+Correlation between reef total coral cover and reef DHW timeseries decreases as cluster coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total cover – DHW timeseries correlation levels (@sfig-access-esm1-5-bioregion-dhwcor; @sfig-access-cm2-bioregion-dhwcor; @sfig-ec-earth3-veg-bioregion-dhwcor; @sfig-gfdl-cm4-bioregion-dhwcor; @sfig-noresm2-mm-bioregion-dhwcor).
 
-Conversely, there are no consistent patterns across bioregions in reef relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).
+Conversely, there are no consistent patterns across bioregions in reef area-relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).
 <!-- 
@@
 
-In many bioregions reefs with high relative coral cover levels (‘high’ cluster) have the lowest initial proportions of habitable area occupied by corals, while reefs in the ‘low’ cluster often have the highest initial proportions of coral habitable area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion; @sfig-access-cm2-bioregion-initialproportion; @sfig-ec-earth3-veg-bioregion-initialproportion; @sfig-gfdl-cm4-bioregion-initialproportion; @sfig-noresm2-mm-bioregion-initialproportion).
+In many bioregions reefs with high area-relative coral cover levels (‘high’ cluster) have the lowest initial proportions of habitable area occupied by corals, while reefs in the ‘low’ cluster often have the highest initial proportions of coral habitable area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion; @sfig-access-cm2-bioregion-initialproportion; @sfig-ec-earth3-veg-bioregion-initialproportion; @sfig-gfdl-cm4-bioregion-initialproportion; @sfig-noresm2-mm-bioregion-initialproportion).
 
@@
 
-Under all GCMs most reefs suffer substantial declines in coral cover from 2025 levels.
+Under all GCMs most reefs are projected to suffer substantial declines in coral cover from 2025 levels.
 NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintanance into the future.
 Differences between low, medium and high reef clusters in cover timeseries are most notable under these two GCMs.
+Maintainance of coral cover into the future is not clearly linked to the Equilibrium Climate Sensitivity of each GCM used as ACCESS-ESM1-5 has a higher ECS value than GFDL-CM4, with reefs experiencing large continuous declines under GFDL-CM4.
 
@@
 
-Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater thermal tolerance than reefs in lower coral cover clusters.
+Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater thermal tolerance than reefs in lower coral cover clusters **need to replot tolerance values**.
 This is in contrast with literature suggesting corals have the capacity to adapt to increasing climate change pressures [@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
 [-@bairos-novak2021] that revealed high heritability of bleaching and survival response traits used to inform the distributions of thermal tolerance traits used in this investigation.
-The lack of influence of thermal tolerance on reef outcomes is likely due to reef being impacted by overall similar levels of thermal stress, combined with the greater importance of factors such as reef depth and initial coral cover.
+The lack of influence of thermal tolerance on reef outcomes is likely due to reef being impacted by overall similar levels of thermal stress, combined with the greater importance of factors such as reef depth.
 
@@
 Five different GCMs were included in analyses to capture uncertainty in climate system responses to increasing atmospheric carbon dioxide levels.
-The large differences in relative cover timeseries seen across the GCMs suggest that it is important to consider this uncertainty in analyses of biological climate change responses.
+The large differences in cover timeseries seen across the GCMs suggest that it is important to consider this uncertainty in analyses of biological climate change responses.
 This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model climate change responses using a range of climate models separately [@shepherd2018].
@@
 ![Reef Degree Heating Week timeseries clustered within each management area, for each GCM analysed.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
@@
 
-![Reef relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+![Reef area-relative coral cover timeseries clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
@@
 ![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the median cover – DHW correlation level for each cluster.
@@
 ![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the median DHW level for each cluster.
@@
 ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the median DHW tolerance value for each cluster.
@@
 ![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the median proportion of habitable area occupied for each cluster.
@@
 ![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
@@
 ![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
@@
 ![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the median depth for each cluster.
@@
 <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median relative cover between 2030 and 2040 within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
 Solid lines represent the median DHW tolerance value for each cluster.

### 2025-07-10 paper/paper_draft.qmd
Improve grouped timeseries plotting and increase sizes/dpi
Also move model info to supplementary

@@
 CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time [@ribeirodealmeida2024].
-This model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
-Environmental disturbances and reproduction are not directly considered within CoralBlox.
-Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
-Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
-As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.
-
-Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996].
-Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
-Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality.
-There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
+Details on how coral demographic processes are implemented in ADRIA - CoralBlox can be found in the supplementary material [**link ADRIA - CoralBlox**].
 
@@
 
-## Model parameterisation
+## ADRIA - CoralBlox
+CoralBlox model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
+Environmental disturbances and reproduction are not directly considered within CoralBlox.
+Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
+Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
+As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.
+
+Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996].
+Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
+Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality.
+There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
+
+### Model parameterisation
 

### 2025-07-10 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -137,6 +137,11 @@ dhw_arrays = [
     rebuild(gbr_dom.dhw_scens[:, :, i_gcm], dims=rel_cover_arrays.axes[1:2]) for i_gcm in eachindex(GCMs)
 ]
 dhw_arrays = concatenatecubes(dhw_arrays, Dim{:GCM}(GCMs))
+dhw_properties = rel_cover_arrays.properties
+dhw_properties[:is_relative] = false
+dhw_properties[:metric_feature] = "Degree Heating Weeks"
+dhw_properties[:metric_unit] = "°C"
+dhw_arrays = rebuild(dhw_arrays, metadata = dhw_properties)
 
 analysis_layers_long = analysis_layers_long[analysis_layers_long.management_area.!="NA", :]
 rel_cover_arrays = rel_cover_arrays[locations=(rel_cover_arrays.locations .∈ [unique(analysis_layers_long.UNIQUE_ID)])]

### 2025-07-10 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -22,7 +22,7 @@ ecs_values = Dict(
     "NorESM2-MM" => 2.5
 )
 ecs = ecs_plot(collect(values(ecs_values)), [2.5, 5.1], [2.1, 7.7], collect(keys(ecs_values)))
-save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit=300 / inch)
+save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit=dpi)
 
 # GBR map plot - methods
 investigation_reefs = context_layers[
@@ -89,7 +89,7 @@ Legend(
     rowgap=1,
     backgroundcolor=bgcol
 )
-save(joinpath(output_path, "figs/region_map.png"), fig, px_per_unit=300 / inch)
+save(joinpath(output_path, "figs/region_map.png"), fig, px_per_unit=dpi)
 
 # fig = Figure()
 # ax = Axis(

### 2025-07-10 src/plotting_functions.jl

@@ -17,11 +17,11 @@ map!(x -> x*cm, values(fig_sizes))
 
 # Extract figure fontsize and convert to pixel measurement
 pt = 1.33 # size of 1 pt in pixels
-fontsize = config["fig_fontsize"]
-fontsize = fontsize["fontsize"] * pt
+misc_sizes = config["fig_misc"]
+fontsize = misc_sizes["fontsize"] * pt
 
 inch = 96 # size of 1 inch in pixels
-dpi = 300 / inch
+dpi = misc_sizes["dpi"] / inch
 
 function colorscheme_alpha(cscheme::ColorScheme, alpha = 0.5)
     ncolors = length(cscheme)
@@ -752,6 +752,10 @@ function grouped_GCM_cluster_timeseries_plots(
         )
     end
 
+    axes_after_1 = filter(x -> x isa Axis, fig.content)[2:end]
+    map(x -> hidexdecorations!(x; grid = false, ticks = false), axes_after_1)
+    map(x -> hideydecorations!(x, ticks = false, ticklabels = false, grid = false), axes_after_1)
+    
     # Tweak layout defaults
     # fig.layout.colgap = 5  # Default ~10, reduce to make plots tighter horizontally
     # fig.layout.rowgap = 5  # Same for vertical spacing

### 2025-07-10 paper/paper_draft.qmd
Add transparency and adjust plotting for carbonate budget plots

--- 2025-07-07 paper/paper_draft.qmd
@@
 They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@grimaldi2022].
-Current modelling projects severe declines in coral cover under projections of Degree Heating Weeks [**Bozec 2025**].
+Current modelling projects severe declines in coral cover under projections of Degree Heating Weeks \[**Bozec 2025**\].
 These coral cover declines will be compounded by ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
@@
 While these environmental and biological factors determine whether individual corals survive thermal stress events, the long-term viability of coral reefs depends not only on coral survival but also on the maintenance of reef structure through positive carbonate budgets.
-Scleractinian corals are primary habitat structures on coral reefs, and the accumulation and erosion of coral reef carbonate frameworks is controlled by a range of processes including coral accumulation [**Perry**], bioerosion [**Tribollet**], physical damage generating coral rubble [**Kenyon**], and calcification and CaCO₃ dissolution rates [**Eyre 2014, 2018**].
-The balance of these processes and occurrence of net carbonate framework production (referred to as a positive carbonate budget) are influenced by factors such as coral cover and complexity [**Perry, Desbiens**], rates of physical environmental processes, and ocean acidity [**Perry, Eyre**].
-Total live coral cover on a reef highly influences the maintenance of net positive carbonate budgets, with estimates ranging from 10 to 20% [**Perry**] of a reef's total area required to maintain positive budgets.
-For mid and outer shelf reefs on the Great Barrier Reef, this threshold is approximately 17% live coral cover [**Desbiens**].
+Scleractinian corals are primary habitat structures on coral reefs, and the accumulation and erosion of coral reef carbonate frameworks is controlled by a range of processes including coral accumulation \[**Perry**\], bioerosion , physical damage generating coral rubble \[**Kenyon**\], and calcification and CaCO₃ dissolution rates \[**Eyre 2014, 2018**\].
+The balance of these processes and occurrence of net carbonate framework production (referred to as a positive carbonate budget) are influenced by factors such as coral cover and complexity \[**Perry, Desbiens**\], rates of physical environmental processes, and ocean acidity \[**Perry, Eyre**\].
+Total live coral cover on a reef highly influences the maintenance of net positive carbonate budgets, with estimates ranging from 10 to 20% \[**Perry**\] of a reef's total area required to maintain positive budgets.
+For mid and outer shelf reefs on the Great Barrier Reef, this threshold is approximately 17% live coral cover \[**Desbiens**\].
 
@@
 The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas. 
-It follows the reef definitions as provided by the Great Barrier Reef Marine Park Authority [https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94].
+It follows the reef definitions as provided by the Great Barrier Reef Marine Park Authority \[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94\].
 Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future thermal stress at each reef location.
@@
 CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time [@ribeirodealmeida2024].
-This model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
-Environmental disturbances and reproduction are not directly considered within CoralBlox.
-Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
-Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
-As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.
-
-Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996].
-Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
-Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality.
-There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
+Details on how coral demographic processes are implemented in ADRIA - CoralBlox can be found in the supplementary material \[**link ADRIA - CoralBlox**\].
 
@@
 
-** need information on GBR1 connectivity used **
+\*\* need information on GBR1 connectivity used \*\*
 
@@
 The CID corrects the Euclidean distance between pairs of timeseries (which accounts for magnitude differences) with the complexity of each timeseries (obtained through a measure of their variability) to ensure reefs are clustered based on their underlying temporal dynamics rather than simply their average coral cover.
-The process creates a distance matrix of n * n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm [cf.
+The process creates a distance matrix of n \* n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm [cf.
 @steinmann2020].
 
-Timeseries clustering analyses were performed at the reefal bioregion scale (defined in [https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::reefal-marine-bioregions/about]).
+Timeseries clustering analyses were performed at the reefal bioregion scale (defined in \[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::reefal-marine-bioregions/about\]).
 Additional analyses were also performed at larger spatial scales, such as the GBRMPA management regions and whole-of-GBR scale.
 These were found to lead to identical conclusions and so are not shown here.
-Results of these analyses can be found at [**insert citation for repository**] for those interested.
+Results of these analyses can be found at \[**insert citation for repository**\] for those interested.
 
@@
 These characteristics include reef median depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation between total coral cover and inversed DHW timeseries, proportion of coral habitable area occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and total strength of larval connections between reefs.
-To analyse the DHW - tolerance levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep * taxa * reef * scenario matrix.
+To analyse the DHW - tolerance levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa \* reef \* scenario matrix.
 The mean timeseries was calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then used to calculate an overall mean DHW – tolerance value for each reef under each GCM.
@@
 ## Reef carbonate budget
+
 The number of years reefs maintain coral cover above a required carbonate budget level substantially decreases as the required carbonate budget threshold (as a percentage of reef area) increases.
@@
 [-@baird2018] is used to calculate the degree of protection provided to a reef based on the median depth.
-Our results suggest that within shallow reef ecosystems (depth < 30m), depth contributes greatly to reef resilience and the ability of the reef to maintain cover under heat stress.
-While similar findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses have often focussed on the potential of mesophotic reefs (> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017].
+Our results suggest that within shallow reef ecosystems (depth \< 30m), depth contributes greatly to reef resilience and the ability of the reef to maintain cover under heat stress.
+While similar findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017].
 In contrast, Venegas et al.
@@
 
-## Model parameterisation
+## ADRIA - CoralBlox
+
+CoralBlox model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
+Environmental disturbances and reproduction are not directly considered within CoralBlox.
+Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
+Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
+As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.
+
+Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996].
+Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
+Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality.
+There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
+
+### Model parameterisation
 
@@
 Solid lines represent the median DHW level for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`}
-<!--
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`} <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`} -->
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`} --\>
 

### 2025-07-10 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -83,7 +83,7 @@ for (i_gcm, GCM) in enumerate(GCMs)
         :value,
         :variable,
         depth_year_correlation;
-        color_label="Median reef depth (m)"
+        color_label="Median reef depth [m]"
     )
     save(
         joinpath(fig_out_dir, "depth_carbonate_scatter.png"),

### 2025-07-10 src/plotting_functions.jl

@@ -661,7 +661,7 @@ function cluster_analysis_plots(
         analysis_layers_depth,
         Symbol("$(GCM)_$(grouping)_clusters"),
         grouping, Symbol("depth_med");
-        xlabel="Median Depth (m)", ylabel="$(grouping_fn)", overlap = overlap
+        xlabel="Median Depth [m]", ylabel="$(grouping_fn)", overlap = overlap
     );
     save(
         joinpath(fig_out_dir, "$(grouping)", "depth_$(grouping)_violin.png"), 
@@ -773,17 +773,26 @@ function carbonate_budget_variable_scatter(
     year_col,
     carbonate_budget_col,
     year_variable_correlation;
-    xlabel="Carbonate budget threshold (%) (correlation)",
+    xlabel="Carbonate budget threshold [%] (correlation)",
     ylabel="Years above carbonate budget threshold",
     color_label="",
     fig_sizes=fig_sizes,
-    fontsize=fontsize
+    fontsize=fontsize,
+    alpha=0.5
 )
     x_fig_size = fig_sizes["carb_width"]
     y_fig_size = fig_sizes["carb_height"]
 
     labels = unique(long_df[:, carbonate_budget_col])
-    labels = ["$(lab) ($(round(year_variable_correlation[lab], digits=2)))" for lab in labels]
+    labels = ["$(lab)\n($(round(year_variable_correlation[lab], digits=2)))" for lab in labels]
+
+    # Get the default colormap (as a gradient with 256 colors)
+    base_cmap = cgrad(:viridis, 256)
+    # Convert all colors to RGBA with alpha = 0.4 (adjust as needed)
+    transparent_colors = [RGBA(c.r, c.g, c.b, alpha) for c in base_cmap.colors]
+    # Wrap into a ColorScheme object
+    transparent_cmap = ColorScheme(transparent_colors)
+
 
     fig = Figure(size = (x_fig_size, y_fig_size), fontsize = fontsize)
     ax = Axis(
@@ -800,8 +809,10 @@ function carbonate_budget_variable_scatter(
         clouds=nothing,
         show_median=false, 
         markersize=6, 
-        jitter_width=0.9
+        jitter_width=1
     )
+    rain.plots[1].colormap = transparent_cmap
+
     # scat = scatter!(
     #     ACCESS_ESM1_5_long.variable,
     #     ACCESS_ESM1_5_long.value,

### 2025-07-11 paper/paper_draft.qmd
Auto-format with line breaks for clarity

@@
     key: sfig
+editor:
+  markdown:
+    wrap: 92
 ---
@@
 
-Climate change is impacting species survival, persistence and ecosystem functions globally, including coral reefs.
-Coral reefs are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading [@foster2021; @gattuso2014].
-Mass bleaching and mortality events linked to climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
-Climate impacts on coral reefs are, and will continue to, decrease the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well as ecosystem services such as food, protection, tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
-We aim to assess the impacts of possible climate futures and identify the characteristics of resilient reefs using the latest generation of larval connectivity research with scenario-based population modelling for the Great Barrier Reef ecosystem.
+Climate change is impacting species survival, persistence and ecosystem functions globally,
+including coral reefs. Coral reefs are vulnerable to increasing magnitude and variation in
+environmental stressors such as ocean temperature, acidification and nutrient loading
+[@foster2021; @gattuso2014]. Mass bleaching and mortality events linked to climate change
+can cause reef-building coral population declines, possibly leading to long-term and
+large-scale coral-macroalgae regime shifts [@arif2022; @wild2011]. Climate impacts on coral
+reefs are, and will continue to, decrease the ability of coral reefs to provide ecological
+functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well
+as ecosystem services such as food, protection, tourism and Indigenous cultural value
+[@eddy2021; @stoeckl2021]. We aim to assess the impacts of possible climate futures and
+identify the characteristics of resilient reefs using the latest generation of larval
+connectivity research with scenario-based population modelling for the Great Barrier Reef
+ecosystem.
 
-The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of thousands of individual reefs.
-They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@grimaldi2022].
-Current modelling projects severe declines in coral cover under projections of Degree Heating Weeks \[**Bozec 2025**\].
-These coral cover declines will be compounded by ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
-Ominously, the 2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs [@cantin2024].
+The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of
+thousands of individual reefs. They are interconnected through coral and fish larval
+dispersal patterns mediated by hydrodynamic, spatial, and ecological processes
+[@grimaldi2022]. Current modelling projects severe declines in coral cover under projections
+of Degree Heating Weeks \[**Bozec 2025**\]. These coral cover declines will be compounded by
+ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks
+[@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. Ominously, the
+2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with
+some level of bleaching recorded on 79% of surveyed reefs [@cantin2024].
 
-Connectivity is said to play a crucial role in Great Barrier Reef resilience by enabling recolonization after disturbances and facilitating adaptation to climate pressures [@angeler2023; @elmhirst2009; @hock2017].
-This connectivity, however, creates both strengths and vulnerabilities within the system.
-Larval source populations (those exporting more larvae than they import) are essential for system-wide resilience, as they provide larvae that enable recovery at distant locations after disturbances [@hock2017; @thomas2015].
-Individually, however, they are more vulnerable to extreme disturbances as they rely more heavily on local recruitment to support recovery.
-In contrast, sink populations can draw on external larval inputs from multiple and diverse sources [@ani2024; @hock2017].
-When disturbances impact major larval source populations, the cascading effects extend throughout the network.
-Increased adult mortality reduces larval export in subsequent years, slowing recovery at the connected sink locations that depend on this external supply [@figueiredo2022; @hock2017; @munday2009].
-Future climate change will further complicate these dynamics through population fragmentation, increased larval mortality, and altered hydrodynamics, potentially disrupting the connectivity patterns that currently maintain reef resilience.
+Connectivity is said to play a crucial role in Great Barrier Reef resilience by enabling
+recolonization after disturbances and facilitating adaptation to climate pressures
+[@angeler2023; @elmhirst2009; @hock2017]. This connectivity, however, creates both strengths
+and vulnerabilities within the system. Larval source populations (those exporting more
+larvae than they import) are essential for system-wide resilience, as they provide larvae
+that enable recovery at distant locations after disturbances [@hock2017; @thomas2015].
+Individually, however, they are more vulnerable to extreme disturbances as they rely more
+heavily on local recruitment to support recovery. In contrast, sink populations can draw on
+external larval inputs from multiple and diverse sources [@ani2024; @hock2017]. When
+disturbances impact major larval source populations, the cascading effects extend throughout
+the network. Increased adult mortality reduces larval export in subsequent years, slowing
+recovery at the connected sink locations that depend on this external supply
+[@figueiredo2022; @hock2017; @munday2009]. Future climate change will further complicate
+these dynamics through population fragmentation, increased larval mortality, and altered
+hydrodynamics, potentially disrupting the connectivity patterns that currently maintain reef
+resilience.
 
-Beyond connectivity, coral resilience to climate change is determined by the complex interplay of environmental and biological factors.
-Environmental abiotic factors influence how reefs will experience climate change pressures, including the spatio-temporal patterns of thermal stress itself, and indirect factors that influence the stress experienced by corals.
-Environmental factors such as tropical cyclones and wind driven mixing [@lin2023; @mcclanahan2005]; currents [@grimaldi2022] and depth [@álvarez-noriega2018; @baird2018; @smith2014] can decrease the magnitude of thermal stress corals experience.
-Conversely, high light intensity and nutrient levels in the benthic zone can increase coral bleaching [@decarlo2020; @higuchi2015].
+Beyond connectivity, coral resilience to climate change is determined by the complex
+interplay of environmental and biological factors. Environmental abiotic factors influence
+how reefs will experience climate change pressures, including the spatio-temporal patterns
+of thermal stress itself, and indirect factors that influence the stress experienced by
+corals. Environmental factors such as tropical cyclones and wind driven mixing [@lin2023;
+@mcclanahan2005]; currents [@grimaldi2022] and depth [@álvarez-noriega2018; @baird2018;
+@smith2014] can decrease the magnitude of thermal stress corals experience. Conversely, high
+light intensity and nutrient levels in the benthic zone can increase coral bleaching
+[@decarlo2020; @higuchi2015].
 
 Individual coral resilience depends on multiple biological factors beyond connectivity.
-Coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and acclimation and inherited thermal tolerance [@humanes2022; @lachs2024] all influence the outcome of high coral heat stress events.
-Importantly, corals have demonstrated adaptive capacity to develop thermal tolerance levels capable of delaying the onset of widespread bleaching under low emissions scenarios [@bairos-novak2021; @humanes2022].
-This adaptive potential represents a crucial mechanism for reef persistence under moderate climate change, working in concert with the environmental factors that modulate thermal stress exposure.
+Coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and acclimation and
+inherited thermal tolerance [@humanes2022; @lachs2024] all influence the outcome of high
+coral heat stress events. Importantly, corals have demonstrated adaptive capacity to develop
+thermal tolerance levels capable of delaying the onset of widespread bleaching under low
+emissions scenarios [@bairos-novak2021; @humanes2022]. This adaptive potential represents a
+crucial mechanism for reef persistence under moderate climate change, working in concert
+with the environmental factors that modulate thermal stress exposure.
 
-While these environmental and biological factors determine whether individual corals survive thermal stress events, the long-term viability of coral reefs depends not only on coral survival but also on the maintenance of reef structure through positive carbonate budgets.
-Scleractinian corals are primary habitat structures on coral reefs, and the accumulation and erosion of coral reef carbonate frameworks is controlled by a range of processes including coral accumulation \[**Perry**\], bioerosion , physical damage generating coral rubble \[**Kenyon**\], and calcification and CaCO₃ dissolution rates \[**Eyre 2014, 2018**\].
-The balance of these processes and occurrence of net carbonate framework production (referred to as a positive carbonate budget) are influenced by factors such as coral cover and complexity \[**Perry, Desbiens**\], rates of physical environmental processes, and ocean acidity \[**Perry, Eyre**\].
-Total live coral cover on a reef highly influences the maintenance of net positive carbonate budgets, with estimates ranging from 10 to 20% \[**Perry**\] of a reef's total area required to maintain positive budgets.
-For mid and outer shelf reefs on the Great Barrier Reef, this threshold is approximately 17% live coral cover \[**Desbiens**\].
+While these environmental and biological factors determine whether individual corals survive
+thermal stress events, the long-term viability of coral reefs depends not only on coral
+survival but also on the maintenance of reef structure through positive carbonate budgets.
+Scleractinian corals are primary habitat structures on coral reefs, and the accumulation and
+erosion of coral reef carbonate frameworks is controlled by a range of processes including
+coral accumulation \[**Perry**\], bioerosion , physical damage generating coral rubble
+\[**Kenyon**\], and calcification and CaCO₃ dissolution rates \[**Eyre 2014, 2018**\]. The
+balance of these processes and occurrence of net carbonate framework production (referred to
+as a positive carbonate budget) are influenced by factors such as coral cover and complexity
+\[**Perry, Desbiens**\], rates of physical environmental processes, and ocean acidity
+\[**Perry, Eyre**\]. Total live coral cover on a reef highly influences the maintenance of
+net positive carbonate budgets, with estimates ranging from 10 to 20% \[**Perry**\] of a
+reef's total area required to maintain positive budgets. For mid and outer shelf reefs on
+the Great Barrier Reef, this threshold is approximately 17% live coral cover
+\[**Desbiens**\].
 
-Incorporating the latest advancements in whole ecosystem larval connectivity modeling and coral thermal response and adaptation research into coral population modeling allows an investigation into how abiotic and biotic factors interact to influence coral climate change resilience and the maintenance of positive carbonate budgets.
-Improvements in coral reef climate response modeling, including sampling from a range of possible climate futures, enable timeseries analyses of uncertain climate change and ecological scenarios [@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].
-While it has previously been suggested that highly connected source reefs that are resilient to bleaching and CoTS outbreaks are likely to play a critical role in supporting future reef recovery across the entire GBR [@hock2017], integrated modelling under current projections of Degree Heating Weeks indicate that depth, rather than connectivity, plays a critical role in determining reef resilience.
-It is further demonstrated that depth supports the maintenance of a postive carbonate budget under all Global Climate Models.
+Incorporating the latest advancements in whole ecosystem larval connectivity modeling and
+coral thermal response and adaptation research into coral population modeling allows an
+investigation into how abiotic and biotic factors interact to influence coral climate change
+resilience and the maintenance of positive carbonate budgets. Improvements in coral reef
+climate response modeling, including sampling from a range of possible climate futures,
+enable timeseries analyses of uncertain climate change and ecological scenarios [@bode2017;
+@chollett2022; @donner2018; @klein2024; @uusitalo2015]. While it has previously been
+suggested that highly connected source reefs that are resilient to bleaching and CoTS
+outbreaks are likely to play a critical role in supporting future reef recovery across the
+entire GBR [@hock2017], integrated modelling under current projections of Degree Heating
+Weeks indicate that depth, rather than connectivity, plays a critical role in determining
+reef resilience. It is further demonstrated that depth supports the maintenance of a postive
+carbonate budget under all Global Climate Models.
 
@@
 The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas.
-It follows the reef definitions as provided by the Great Barrier Reef Marine Park Authority \[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94\].
-Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future thermal stress at each reef location.
-Five Global Climate Models (GCMs) (EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6; **citation**) were selected for this study.
-Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great Barrier Reef were obtained from the HighResCoralStress database [@dixon2022; @dixon].
-Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology [@liu2017; @skirving2020].
-These GCMs were selected from available GCMs downscaled by Dixon et al.
-[-@dixon] based on evaluation by Grose et al.
-[-@grose2023], which found high correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms in these GCMs.
-Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming caused by a doubling of carbon dioxide above its pre-industrial concentration [@forster2021].
-The four GCMs span a range of ECS values within the IPCC assessed likely range, and GCM development families, allowing for a range of possible climate futures to be explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs; [@grose2023; @shepherd2018]).
-The following analyses are performed using each GCM separately.
-SSP 2-4.5 is used as a plausible emission pathway under current emission trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020; IPCC -@climate2023].
+It follows the reef definitions as provided by the Great Barrier Reef Marine Park Authority
+\[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94\].
+Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future
+thermal stress at each reef location. Five Global Climate Models (GCMs) (EC-Earth3-Veg,
+ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled
+Model Intercomparison Project (CMIP6; **citation**) were selected for this study.
+Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great
+Barrier Reef were obtained from the HighResCoralStress database [@dixon2022; @dixon].
+Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
+[@liu2017; @skirving2020]. These GCMs were selected from available GCMs downscaled by Dixon
+et al. [-@dixon] based on evaluation by Grose et al. [-@grose2023], which found high
+correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian
+Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms
+in these GCMs. Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long
+term warming caused by a doubling of carbon dioxide above its pre-industrial concentration
+[@forster2021]. The four GCMs span a range of ECS values within the IPCC assessed likely
+range, and GCM development families, allowing for a range of possible climate futures to be
+explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs;
+[@grose2023; @shepherd2018]). The following analyses are performed using each GCM
+separately. SSP 2-4.5 is used as a plausible emission pathway under current emission
+trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020;
+IPCC -@climate2023].
 
-![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points).
-The green polygon represents the Far Northern management area, the yellow polygon represents the Cairns/Cooktown management area, the pink polygon represents the Townsville/Whitsunday management area and the blue polygon represents the Mackay/Capricorn management area.
-The centroid of each reef is represented as a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion.
-An annotation represents the approximate location of the Australian Institute of Marine Science Townsville site at Cape Cleveland.](/../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map width=`{julia} map_width`}
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points). The green polygon represents the Far Northern management area,
+the yellow polygon represents the Cairns/Cooktown management area, the pink polygon
+represents the Townsville/Whitsunday management area and the blue polygon represents the
+Mackay/Capricorn management area. The centroid of each reef is represented as a point for
+visual clarity, and is coloured according to its GBRMPA reefal bioregion. An annotation
+represents the approximate location of the Australian Institute of Marine Science Townsville
+site at Cape
+Cleveland.](/../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
+width="`{julia"} map_width\`}
 
 ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
-The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al., 2021).](/../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs width=`{julia} ecs_width`}
+The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
+the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
+2021).](/../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs
+width="`{julia"} ecs_width\`}
 
@@
 
-CoralBlox is a coral population growth and mortality model that simulates groups of corals growing in diameter and competing for limited space over time [@ribeirodealmeida2024].
-Details on how coral demographic processes are implemented in ADRIA - CoralBlox can be found in the supplementary material \[**link ADRIA - CoralBlox**\].
+CoralBlox is a coral population growth and mortality model that simulates groups of corals
+growing in diameter and competing for limited space over time [@ribeirodealmeida2024].
+Details on how coral demographic processes are implemented in ADRIA - CoralBlox can be found
+in the supplementary material \[**link ADRIA - CoralBlox**\].
 
@@
 
-We track the thermal tolerance of each functional group and size class as a truncated normal distribution that is updated in each timestep following growth and recruitment.
-This distribution determines that proportion of the population on a reef that is susceptible to bleaching (i.e.
-has a thermal threshold below the experienced DHW value).
-Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
+We track the thermal tolerance of each functional group and size class as a truncated normal
+distribution that is updated in each timestep following growth and recruitment. This
+distribution determines that proportion of the population on a reef that is susceptible to
+bleaching (i.e. has a thermal threshold below the experienced DHW value). Starting
+distributions for thermal tolerance levels are informed by Bairos-Novak et al.
 [-@bairos-novak2021].
 
-Tropical cyclones and impact of wave activity to reefs are not included in this investigation.
-We scale coral bleaching impacts by a coefficient determined by the median depth of each reef location, following Baird et al.
-[@baird2018], reducing the proportion of coral colonies on a reef impacted by high heat stress as depth increases.
-Median depths for each reef location have been extracted from satellite derived bathymetry data for the Great Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details).
-Due to varying degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs with less than 5% coverage of valid bathymetry data have been removed from this investigation.
-Furthermore, reefs that were outside the GBRMPA management areas or not associated with a bioregion were removed from the investigation.
+Tropical cyclones and impact of wave activity to reefs are not included in this
+investigation. We scale coral bleaching impacts by a coefficient determined by the median
+depth of each reef location, following Baird et al. [@baird2018], reducing the proportion of
+coral colonies on a reef impacted by high heat stress as depth increases. Median depths for
+each reef location have been extracted from satellite derived bathymetry data for the Great
+Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due to varying
+degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs
+with less than 5% coverage of valid bathymetry data have been removed from this
+investigation. Furthermore, reefs that were outside the GBRMPA management areas or not
+associated with a bioregion were removed from the investigation.
 
@@
 
-ADRIA-CoralBlox was run for 4096 **sampled** scenarios per GCM.
-A median absolute coral cover timeseries for each reef was calculated for each GCM.
-For timeseries clustering reef cover timeseries were scaled by the total area of the reef to represent timeseries as a percentage of the total reef area.
-The proportion of each functional group occupying the reef (group evenness) was also investigated as a metric for timeseries analysis, but was found to not sufficiently capture the declined condition of reefs suffering from very low absolute coral cover.
+ADRIA-CoralBlox was run for 4096 **sampled** scenarios per GCM. A median absolute coral
+cover timeseries for each reef was calculated for each GCM. For timeseries clustering reef
+cover timeseries were scaled by the total area of the reef to represent timeseries as a
+percentage of the total reef area. The proportion of each functional group occupying the
+reef (group evenness) was also investigated as a metric for timeseries analysis, but was
+found to not sufficiently capture the declined condition of reefs suffering from very low
+absolute coral cover.
 
@@
 
-Using median coral cover timeseries for each reef we calculated the number of years each reef maintains coral cover above these live coral cover threshold levels, inferring the number of years each reef maintains a net positive carbonate budget, accumulating reef framework.
-As in situ carbonate budgets are influenced by a range of processes, our calculations of carbonate budget maintainence are intended as estimates and do not reflect the conditions that will be experienced on a reef, but indicate relative levels of health across reefs.
-To capture the wide influence of environmental factors on carbonate budget levels, we analyse live coral cover thresholds required for positive carbonate budgets from 10 to 20% (inclusive, at step 1%).
+Using median coral cover timeseries for each reef we calculated the number of years each
+reef maintains coral cover above these live coral cover threshold levels, inferring the
+number of years each reef maintains a net positive carbonate budget, accumulating reef
+framework. As in situ carbonate budgets are influenced by a range of processes, our
+calculations of carbonate budget maintainence are intended as estimates and do not reflect
+the conditions that will be experienced on a reef, but indicate relative levels of health
+across reefs. To capture the wide influence of environmental factors on carbonate budget
+levels, we analyse live coral cover thresholds required for positive carbonate budgets from
+10 to 20% (inclusive, at step 1%).
 
-The distribution of number of years above carbonate-cover thresholds is right-skewed, with many reefs experiencing low numbers of years above thresholds.
-Similarly, reef median depth levels and log (natural) total connectivity strength levels follow right-skewed distributions.
-Therefore, we analyse the correlation between number of years above carbonate-cover thresholds and these characteristics using Spearman's correlation coefficient.
+The distribution of number of years above carbonate-cover thresholds is right-skewed, with
+many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth
+levels and log (natural) total connectivity strength levels follow right-skewed
+distributions. Therefore, we analyse the correlation between number of years above
+carbonate-cover thresholds and these characteristics using Spearman's correlation
+coefficient.
 
@@
 
-To identify groups of reefs that are resilient, intermediate, and non-resilient, we clustered reefs by their temporal behaviour as indicated by their coral cover over time.
-The Complexity-Invariant Distance (CID) between each timeseries was calculated to identify timeseries that behave similarly [@batista2014].
-The CID corrects the Euclidean distance between pairs of timeseries (which accounts for magnitude differences) with the complexity of each timeseries (obtained through a measure of their variability) to ensure reefs are clustered based on their underlying temporal dynamics rather than simply their average coral cover.
-The process creates a distance matrix of n \* n dimensions (where n is the number of timeseries in the group) that is clustered using a k-medoids clustering algorithm [cf.
+To identify groups of reefs that are resilient, intermediate, and non-resilient, we
+clustered reefs by their temporal behaviour as indicated by their coral cover over time. The
+Complexity-Invariant Distance (CID) between each timeseries was calculated to identify
+timeseries that behave similarly [@batista2014]. The CID corrects the Euclidean distance
+between pairs of timeseries (which accounts for magnitude differences) with the complexity
+of each timeseries (obtained through a measure of their variability) to ensure reefs are
+clustered based on their underlying temporal dynamics rather than simply their average coral
+cover. The process creates a distance matrix of n \* n dimensions (where n is the number of
+timeseries in the group) that is clustered using a k-medoids clustering algorithm [cf.
 @steinmann2020].
 
-Timeseries clustering analyses were performed at the reefal bioregion scale (defined in \[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::reefal-marine-bioregions/about\]).
-Additional analyses were also performed at larger spatial scales, such as the GBRMPA management regions and whole-of-GBR scale.
-These were found to lead to identical conclusions and so are not shown here.
-Results of these analyses can be found at \[**insert citation for repository**\] for those interested.
+Timeseries clustering analyses were performed at the reefal bioregion scale (defined in
+\[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::reefal-marine-bioregions/about\]).
+Additional analyses were also performed at larger spatial scales, such as the GBRMPA
+management regions and whole-of-GBR scale. These were found to lead to identical conclusions
+and so are not shown here. Results of these analyses can be found at \[**insert citation for
+repository**\] for those interested.
 
-Reefs in each timeseries cluster are compared to identify characteristics that differ between low, medium and high coral cover clusters.
-These characteristics include reef median depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation between total coral cover and inversed DHW timeseries, proportion of coral habitable area occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and total strength of larval connections between reefs.
-To analyse the DHW - tolerance levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa \* reef \* scenario matrix.
-The mean timeseries was calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then used to calculate an overall mean DHW – tolerance value for each reef under each GCM.
+Reefs in each timeseries cluster are compared to identify characteristics that differ
+between low, medium and high coral cover clusters. These characteristics include reef median
+depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation
+between total coral cover and inversed DHW timeseries, proportion of coral habitable area
+occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and
+total strength of larval connections between reefs. To analyse the DHW - tolerance levels of
+reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa
+\* reef \* scenario matrix. The mean timeseries was calculated over the first four scenarios
+for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then
+used to calculate an overall mean DHW – tolerance value for each reef under each GCM.
 
@@
 
-The number of years reefs maintain coral cover above a required carbonate budget level substantially decreases as the required carbonate budget threshold (as a percentage of reef area) increases.
-Reefs with greater median depth levels maintain coral cover above required carbonate budget levels for longer than reefs at shallow depths [@fig-access-esm1-5-depth-carbonate].
-Reef median depth has a moderate positive correlation with the number of years a reef maintains coral cover above the required threshold [@fig-access-esm1-5-depth-carbonate].
-Depth - carbonate budget maintainence correlation decreases as the required carbonate budget threshold increases.
-This is likely due to an increasing number of reefs being unable to maintain coral cover above threshold levels as the threshold increases.
-There are no clear relationships between reef total connectivity levels and the number of years reefs maintain coral cover above carbonate budget threshold levels [@sfig-access-esm1-5-conn-carbonate].
-Reef log (natural) total connectivity strength has no correlation with the number of years a reef maintains cover above the required thresholds.
-Log connectivity strength - carbonate budget maintainence correlation slightly decreases as the required carbonate budget threshold increases.
+The number of years reefs maintain coral cover above a required carbonate budget level
+substantially decreases as the required carbonate budget threshold (as a percentage of reef
+area) increases. Reefs with greater median depth levels maintain coral cover above required
+carbonate budget levels for longer than reefs at shallow depths
+[@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate positive correlation
+with the number of years a reef maintains coral cover above the required threshold
+[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintainence correlation
+decreases as the required carbonate budget threshold increases. This is likely due to an
+increasing number of reefs being unable to maintain coral cover above threshold levels as
+the threshold increases. There are no clear relationships between reef total connectivity
+levels and the number of years reefs maintain coral cover above carbonate budget threshold
+levels [@sfig-access-esm1-5-conn-carbonate]. Reef log (natural) total connectivity strength
+has no correlation with the number of years a reef maintains cover above the required
+thresholds. Log connectivity strength - carbonate budget maintainence correlation slightly
+decreases as the required carbonate budget threshold increases.
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents the median reef depth level in metres.
-Displays results from median timeseries using ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the
+number of years cover exceeds the carbonate budget threshold. Point colour represents the
+median reef depth level in metres. Displays results from median timeseries using
+ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
+width="`{julia"} carb_width\`}
 
@@
 
-Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’ coral cover and contextual analysis factors, thus further comparisons of these clusters for each analysis factor are only shown for ACCESS-ESM1-5 (intermediate ECS scenario).
-Results for the additional GCMs are displayed in the supplementary material.
-However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover timeseries are displayed for each GCM (displayed clustered at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
+Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’
+coral cover and contextual analysis factors, thus further comparisons of these clusters for
+each analysis factor are only shown for ACCESS-ESM1-5 (intermediate ECS scenario). Results
+for the additional GCMs are displayed in the supplementary material. However, there are
+substantial differences in the longevity of reef resilience and maintenance of coral cover
+post 2030 between the GCMs, thus coral cover timeseries are displayed for each GCM
+(displayed clustered at management-area scale to preserve coarse spatial differences in
+coral trajectories) (@fig-gcm-cover-trajectories).
 
-NorESM2-MM has the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline dynamics up to 2075 under this possible climate future.
-While recovery phases are predominantly seen in the ‘high’ cover cluster, the ‘medium’ cluster, and to a lesser degree the ‘low’ cluster, also exhibit periods of recovery and increasing proportions of coral cover up to 2045.
-Under NorESM2-MM GCM the Far Northern management area does not see coral cover maintenance as high as the three remaining management regions.
-Under the second lowest ECS projection (GFDL-CM4, 2.9°C) all clusters in each management area exhibit largely declining future trajectories with periods of recovery from 2030 to 2040.
-ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which results in intermediate levels of coral cover maintenance (between those of lower and higher ECS GCMs).
-In Townsville/Whitsunday and Far Northern management areas reefs in the high cluster are able to maintain coral cover levels around 20% to 2050 under ACCESS-ESM1-5.
-Under ACCESS-CM2 (4.72°C) and EC-Earth3-Veg (4.31°C) GCMs cover trajectories are largely declining in all management areas.
+NorESM2-MM has the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit
+continuing recovery and decline dynamics up to 2075 under this possible climate future.
+While recovery phases are predominantly seen in the ‘high’ cover cluster, the ‘medium’
+cluster, and to a lesser degree the ‘low’ cluster, also exhibit periods of recovery and
+increasing proportions of coral cover up to 2045. Under NorESM2-MM GCM the Far Northern
+management area does not see coral cover maintenance as high as the three remaining
+management regions. Under the second lowest ECS projection (GFDL-CM4, 2.9°C) all clusters in
+each management area exhibit largely declining future trajectories with periods of recovery
+from 2030 to 2040. ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which results in
+intermediate levels of coral cover maintenance (between those of lower and higher ECS GCMs).
+In Townsville/Whitsunday and Far Northern management areas reefs in the high cluster are
+able to maintain coral cover levels around 20% to 2050 under ACCESS-ESM1-5. Under ACCESS-CM2
+(4.72°C) and EC-Earth3-Veg (4.31°C) GCMs cover trajectories are largely declining in all
+management areas.
 
-Under each GCM, in all management areas, low, medium and high cluster reefs have low differences between DHW trajectories (@sfig-gcm-dhw-trajectories).
-The highest peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHW timeseries occur under ACCESS-CM2.
+Under each GCM, in all management areas, low, medium and high cluster reefs have low
+differences between DHW trajectories (@sfig-gcm-dhw-trajectories). The highest peak DHW
+levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHW
+timeseries occur under ACCESS-CM2.
 
-![Reef area-relative coral cover timeseries clustered within each management area, for each GCM analysed.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories width=`{julia} timeseries_width`}
+![Reef area-relative coral cover timeseries clustered within each management area, for each
+GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
+between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
+represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
+represented five times (for each GCM), with each GCM displayed
+horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
+width="`{julia"} timeseries_width\`}
 
-Across the five GCMs, 50% (1812) of reefs, at management region scale, remain in the same ‘low, medium, high’ cluster assignment.
-1757 Reefs (49%) that changed clusters by one level across the GCMs (e.g.
-a reef is assigned ‘low’ and ‘medium’ in different GCMs), while 46 (1%) reefs changed clusters by two levels across the GCMs (e.g.
-a reef is assigned ‘low’ and ‘high’ in different GCMs).
+Across the five GCMs, 50% (1812) of reefs, at management region scale, remain in the same
+‘low, medium, high’ cluster assignment. 1757 Reefs (49%) that changed clusters by one level
+across the GCMs (e.g. a reef is assigned ‘low’ and ‘medium’ in different GCMs), while 46
+(1%) reefs changed clusters by two levels across the GCMs (e.g. a reef is assigned ‘low’ and
+‘high’ in different GCMs).
 
@@
 
-Within bioregions timeseries clustering analysis was able to identify three clusters of area-relative cover timeseries.
-Across many bioregions timeseries clustering identified a ‘low’ cluster containing reefs that suffer larger declines and generally have lower levels of coral cover than the other clusters, a ‘medium’ cluster with intermediate levels of coral cover, and a ‘high’ cluster with greater levels of cover recovery, with persistence to 2050 in some bioregions (@sfig-access-esm1-5-bioregion-timeseries; @sfig-access-cm2-bioregion-timeseries; @sfig-ec-earth3-veg-bioregion-timeseries; @sfig-gfdl-cm4-bioregion-timeseries; @sfig-noresm2-mm-bioregion-timeseries).
+Within bioregions timeseries clustering analysis was able to identify three clusters of
+area-relative cover timeseries. Across many bioregions timeseries clustering identified a
+‘low’ cluster containing reefs that suffer larger declines and generally have lower levels
+of coral cover than the other clusters, a ‘medium’ cluster with intermediate levels of coral
+cover, and a ‘high’ cluster with greater levels of cover recovery, with persistence to 2050
+in some bioregions (@sfig-access-esm1-5-bioregion-timeseries;
+@sfig-access-cm2-bioregion-timeseries; @sfig-ec-earth3-veg-bioregion-timeseries;
+@sfig-gfdl-cm4-bioregion-timeseries; @sfig-noresm2-mm-bioregion-timeseries).
 
-In many bioregions, median reef depth decreases as cluster coral cover decreases, with reefs within the ‘high’ cluster commonly having the greatest median reef depths within the bioregion (@fig-access-esm1-5-bioregion-depth; @sfig-access-cm2-bioregion-depth; @sfig-ec-earth3-veg-bioregion-depth; @sfig-gfdl-cm4-bioregion-depth; @sfig-noresm2-mm-bioregion-depth).
+In many bioregions, median reef depth decreases as cluster coral cover decreases, with reefs
+within the ‘high’ cluster commonly having the greatest median reef depths within the
+bioregion (@fig-access-esm1-5-bioregion-depth; @sfig-access-cm2-bioregion-depth;
+@sfig-ec-earth3-veg-bioregion-depth; @sfig-gfdl-cm4-bioregion-depth;
+@sfig-noresm2-mm-bioregion-depth).
 
-![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median depth for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth width=`{julia} violin_width`}
+![Median depth for reefs within each bioregion, separated into clusters assigned by
+timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
+area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
+are clusters with intermediate median area-relative cover between 2030 and 2040 within each
+bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
+between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
+cluster. Displays results for ACCESS-ESM1-5
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
+width="`{julia"} violin_width\`}
 
-Correlation between reef total coral cover and reef DHW timeseries decreases as cluster coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total cover – DHW timeseries correlation levels (@sfig-access-esm1-5-bioregion-dhwcor; @sfig-access-cm2-bioregion-dhwcor; @sfig-ec-earth3-veg-bioregion-dhwcor; @sfig-gfdl-cm4-bioregion-dhwcor; @sfig-noresm2-mm-bioregion-dhwcor).
+Correlation between reef total coral cover and reef DHW timeseries decreases as cluster
+coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total
+cover – DHW timeseries correlation levels (@sfig-access-esm1-5-bioregion-dhwcor;
+@sfig-access-cm2-bioregion-dhwcor; @sfig-ec-earth3-veg-bioregion-dhwcor;
+@sfig-gfdl-cm4-bioregion-dhwcor; @sfig-noresm2-mm-bioregion-dhwcor).
 
-Conversely, there are no consistent patterns across bioregions in reef area-relative cover and mean timeseries DHW levels, with clusters having similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean; @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean; @sfig-noresm2-mm-bioregion-dhwmean).
-<!--
+Conversely, there are no consistent patterns across bioregions in reef area-relative cover
+and mean timeseries DHW levels, with clusters having similar mean DHW levels in many
+bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean;
+@sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean;
+@sfig-noresm2-mm-bioregion-dhwmean). <!--
 In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially lower mean thermal tolerance levels compared to reefs in other clusters.
@@
 
-In many bioregions reefs with high area-relative coral cover levels (‘high’ cluster) have the lowest initial proportions of habitable area occupied by corals, while reefs in the ‘low’ cluster often have the highest initial proportions of coral habitable area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion; @sfig-access-cm2-bioregion-initialproportion; @sfig-ec-earth3-veg-bioregion-initialproportion; @sfig-gfdl-cm4-bioregion-initialproportion; @sfig-noresm2-mm-bioregion-initialproportion).
+In many bioregions reefs with high area-relative coral cover levels (‘high’ cluster) have
+the lowest initial proportions of habitable area occupied by corals, while reefs in the
+‘low’ cluster often have the highest initial proportions of coral habitable area occupied by
+corals (@sfig-access-esm1-5-bioregion-initialproportion;
+@sfig-access-cm2-bioregion-initialproportion;
+@sfig-ec-earth3-veg-bioregion-initialproportion; @sfig-gfdl-cm4-bioregion-initialproportion;
+@sfig-noresm2-mm-bioregion-initialproportion).
 
-Across most bioregions there are not consistent differences between clusters in connectivity metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi; @sfig-access-cm2-bioregion-logsosi; @sfig-ec-earth3-veg-bioregion-logsosi; @sfig-gfdl-cm4-bioregion-logsosi; @sfig-noresm2-mm-bioregion-logsosi) and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity; @sfig-access-cm2-bioregion-totalconnectivity; @sfig-ec-earth3-veg-bioregion-totalconnectivity; @sfig-gfdl-cm4-bioregion-totalconnectivity; @sfig-noresm2-mm-bioregion-totalconnectivity).
+Across most bioregions there are not consistent differences between clusters in connectivity
+metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi;
+@sfig-access-cm2-bioregion-logsosi; @sfig-ec-earth3-veg-bioregion-logsosi;
+@sfig-gfdl-cm4-bioregion-logsosi; @sfig-noresm2-mm-bioregion-logsosi) and total connectivity
+strength (@sfig-access-esm1-5-bioregion-totalconnectivity;
+@sfig-access-cm2-bioregion-totalconnectivity;
+@sfig-ec-earth3-veg-bioregion-totalconnectivity; @sfig-gfdl-cm4-bioregion-totalconnectivity;
+@sfig-noresm2-mm-bioregion-totalconnectivity).
 
@@
 
-Under all GCMs most reefs are projected to suffer substantial declines in coral cover from 2025 levels.
-NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintanance into the future.
-Differences between low, medium and high reef clusters in cover timeseries are most notable under these two GCMs.
-Maintainance of coral cover into the future is not clearly linked to the Equilibrium Climate Sensitivity of each GCM used as ACCESS-ESM1-5 has a higher ECS value than GFDL-CM4, with reefs experiencing large continuous declines under GFDL-CM4.
+Under all GCMs most reefs are projected to suffer substantial declines in coral cover from
+2025 levels. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintanance into
+the future. Differences between low, medium and high reef clusters in cover timeseries are
+most notable under these two GCMs. Maintainance of coral cover into the future is not
+clearly linked to the Equilibrium Climate Sensitivity of each GCM used as ACCESS-ESM1-5 has
+a higher ECS value than GFDL-CM4, with reefs experiencing large continuous declines under
+GFDL-CM4.
 
-Reefs in different clusters largely do not differ in mean modelled DHW levels experienced, and exhibit overall similar DHW timeseries.
-While these reefs experience similar magnitude DHWs based on SST, the proportion of the reef’s coral population impacted by heat stress events depends on the depth of the reef.
-Analysis from Baird et al.
-[-@baird2018] is used to calculate the degree of protection provided to a reef based on the median depth.
-Our results suggest that within shallow reef ecosystems (depth \< 30m), depth contributes greatly to reef resilience and the ability of the reef to maintain cover under heat stress.
-While similar findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017].
-In contrast, Venegas et al.
-[-@venegas2019] found no association between depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
+Reefs in different clusters largely do not differ in mean modelled DHW levels experienced,
+and exhibit overall similar DHW timeseries. While these reefs experience similar magnitude
+DHWs based on SST, the proportion of the reef’s coral population impacted by heat stress
+events depends on the depth of the reef. Analysis from Baird et al. [-@baird2018] is used to
+calculate the degree of protection provided to a reef based on the median depth. Our results
+suggest that within shallow reef ecosystems (depth \< 30m), depth contributes greatly to
+reef resilience and the ability of the reef to maintain cover under heat stress. While
+similar findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia
+analyses have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal
+refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al.
+[-@venegas2019] found no association between depth and the alleviation of heat stress across
+a range of shallow reefs in the Pacific.
 <!-- The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels.
@@
 
-Overall, these findings support the hypothesis that reefs at greater depths will experience refugia benefits and more prolonged resilience under climate change compared to shallower reefs.
-Additionally, [-@liu2024] suggest that rubble instability is inversely correlated with reef depth, possibly limiting the larval recruitment capacity of shallow reefs.
-A caveat to these findings is the quality of the bathymetry data used to calculate depth refugia benefits in ADRIA.
-This data (GBRMPA [-@gbr10gb2020]) is derived from satellite imagery and is limited in its alignment with the established GBRMPA reef outlines used in the investigation to characterise reef locations.
-As a result, 842 reefs (22% of the 3806) were removed from the analyses before depth comparisons due to having less than 5% coverage of depth data.
-Additionally, deriving estimates of depth from satellite imagery is prone to high degrees of uncertainty.
-Data adopted for the given assessment are said to be accurate up to 15m from Mean Sea Level [@gbr10gb2020].
-Furthermore, an estimated median depth is determined for each reef, using the established GBRMPA reef outlines to provide an indication of “true” reef extent.
-Therefore, the estimates of reef depths are taken as a useful indication rather than an accurate and precise report of reef depths across the GBR.
+Overall, these findings support the hypothesis that reefs at greater depths will experience
+refugia benefits and more prolonged resilience under climate change compared to shallower
+reefs. Additionally, [-@liu2024] suggest that rubble instability is inversely correlated
+with reef depth, possibly limiting the larval recruitment capacity of shallow reefs. A
+caveat to these findings is the quality of the bathymetry data used to calculate depth
+refugia benefits in ADRIA. This data (GBRMPA [-@gbr10gb2020]) is derived from satellite
+imagery and is limited in its alignment with the established GBRMPA reef outlines used in
+the investigation to characterise reef locations. As a result, 842 reefs (22% of the 3806)
+were removed from the analyses before depth comparisons due to having less than 5% coverage
+of depth data. Additionally, deriving estimates of depth from satellite imagery is prone to
+high degrees of uncertainty. Data adopted for the given assessment are said to be accurate
+up to 15m from Mean Sea Level [@gbr10gb2020]. Furthermore, an estimated median depth is
+determined for each reef, using the established GBRMPA reef outlines to provide an
+indication of “true” reef extent. Therefore, the estimates of reef depths are taken as a
+useful indication rather than an accurate and precise report of reef depths across the GBR.
 
-Current reef restoration and intervention-investigation efforts on the Great Barrier Reef, such as deployment of coral seeding and fragment devices target reefs with suitable restoration sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024].
-One of the main depth constraints is being able to visually identify the target site from the surface for deployment and ongoing monitoring, in combination with factors such as deployment method and tourism return value.
-Our results suggest that of the reefs analysed within the 1-10m depth range (1800 reefs) 74% (1328) of reefs fall into the low and medium clusters (across all GCMs at the GBRMPA management region scale), with many suffering large future declines in reef health under climate change and possibly limiting the potential of interventions to deliver recovery in these locations.
-Reef intervention planning is a complex and challenging decision making process [@anthony2020], and our results suggest that deployment site depth is an important factor to consider when assessing the long-term resilience of reef sites.
+Current reef restoration and intervention-investigation efforts on the Great Barrier Reef,
+such as deployment of coral seeding and fragment devices target reefs with suitable
+restoration sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. One
+of the main depth constraints is being able to visually identify the target site from the
+surface for deployment and ongoing monitoring, in combination with factors such as
+deployment method and tourism return value. Our results suggest that of the reefs analysed
+within the 1-10m depth range (1800 reefs) 74% (1328) of reefs fall into the low and medium
+clusters (across all GCMs at the GBRMPA management region scale), with many suffering large
+future declines in reef health under climate change and possibly limiting the potential of
+interventions to deliver recovery in these locations. Reef intervention planning is a
+complex and challenging decision making process [@anthony2020], and our results suggest that
+deployment site depth is an important factor to consider when assessing the long-term
+resilience of reef sites.
 
-Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater thermal tolerance than reefs in lower coral cover clusters **need to replot tolerance values**.
-This is in contrast with literature suggesting corals have the capacity to adapt to increasing climate change pressures [@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
-[-@bairos-novak2021] that revealed high heritability of bleaching and survival response traits used to inform the distributions of thermal tolerance traits used in this investigation.
-The lack of influence of thermal tolerance on reef outcomes is likely due to reef being impacted by overall similar levels of thermal stress, combined with the greater importance of factors such as reef depth.
+Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater
+thermal tolerance than reefs in lower coral cover clusters **need to replot tolerance
+values**. This is in contrast with literature suggesting corals have the capacity to adapt
+to increasing climate change pressures [@humanes2022; @lachs2024], including the
+investigation by Bairos-Novak et al. [-@bairos-novak2021] that revealed high heritability of
+bleaching and survival response traits used to inform the distributions of thermal tolerance
+traits used in this investigation. The lack of influence of thermal tolerance on reef
+outcomes is likely due to reef being impacted by overall similar levels of thermal stress,
+combined with the greater importance of factors such as reef depth.
 
-It has been suggested that a primary facet of reef resilience is the degree of larval connectivity between reefs and the supply of recruits that a reef receives following disturbance [@hock2017].
-It was expected that resilient reefs would have greater incoming than outgoing larval connectivity to promote recovery in years following thermal stress, while non-resilient reefs would have greater outgoing than incoming connectivity inhibiting recruitment of corals ability post thermal stress.
-In contrast, our results suggest that there are few differences between resilient and non-resilient reefs in connectivity metrics such as the ratio of outgoing to incoming larval connectivity and total connectivity strength.
-Hock et al.
-[-@hock2017] used larval connectivity modelling to identify resilient reefs that may supply up to 47% of the wider Great Barrier Reef ecosystem with larvae following disturbance.
-A critique of this approach [@bode2018] is that results obtained are highly sensitive to the biophysical dispersal model used, limiting the application of specific identified reefs.
-Reef depth was not considered in these investigations of reef network resilience.
-These investigations were performed using prior generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods respectively.
-Using updated 1km resolution larval connectivity across the whole GBR, our results suggest that larval connectivity alone is not as important for reef resilience and recovery as environmental refugia from thermal stress such as depth.
+It has been suggested that a primary facet of reef resilience is the degree of larval
+connectivity between reefs and the supply of recruits that a reef receives following
+disturbance [@hock2017]. It was expected that resilient reefs would have greater incoming
+than outgoing larval connectivity to promote recovery in years following thermal stress,
+while non-resilient reefs would have greater outgoing than incoming connectivity inhibiting
+recruitment of corals ability post thermal stress. In contrast, our results suggest that
+there are few differences between resilient and non-resilient reefs in connectivity metrics
+such as the ratio of outgoing to incoming larval connectivity and total connectivity
+strength. Hock et al. [-@hock2017] used larval connectivity modelling to identify resilient
+reefs that may supply up to 47% of the wider Great Barrier Reef ecosystem with larvae
+following disturbance. A critique of this approach [@bode2018] is that results obtained are
+highly sensitive to the biophysical dispersal model used, limiting the application of
+specific identified reefs. Reef depth was not considered in these investigations of reef
+network resilience. These investigations were performed using prior generations of larval
+connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time
+periods respectively. Using updated 1km resolution larval connectivity across the whole GBR,
+our results suggest that larval connectivity alone is not as important for reef resilience
+and recovery as environmental refugia from thermal stress such as depth.
 
-Furthermore, our results suggest that the capacity of reefs to maintain healthy coral habitat by being above positive net carbonate budget levels is greater for reefs at deeper depths than shallow depths.
-While the maintanence of positive carbonate budget levels does not appear to be linked to reef connectivity metrics.
-The maintanence of positive carbonate budgets is important for reef resilience under climate change.
+Furthermore, our results suggest that the capacity of reefs to maintain healthy coral
+habitat by being above positive net carbonate budget levels is greater for reefs at deeper
+depths than shallow depths. While the maintanence of positive carbonate budget levels does
+not appear to be linked to reef connectivity metrics. The maintanence of positive carbonate
+budgets is important for reef resilience under climate change.
 
-Five different GCMs were included in analyses to capture uncertainty in climate system responses to increasing atmospheric carbon dioxide levels.
-The large differences in cover timeseries seen across the GCMs suggest that it is important to consider this uncertainty in analyses of biological climate change responses.
-This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model climate change responses using a range of climate models separately [@shepherd2018].
-However, the patterns identified between low, medium and high clusters of reefs suggest that the importance of depth refugia is consistent across scenarios.
-Similarly, at the management area scale, only 1% of reefs were assigned a ‘low’ and ‘high’ cluster in different GCMs, suggesting that intrinsic reef properties can prevent high cover resilient reefs from crashing under a different future climate scenario.
+Five different GCMs were included in analyses to capture uncertainty in climate system
+responses to increasing atmospheric carbon dioxide levels. The large differences in cover
+timeseries seen across the GCMs suggest that it is important to consider this uncertainty in
+analyses of biological climate change responses. This is supported by recent literature
+suggesting an effective approach to capturing climate change uncertainty is to model climate
+change responses using a range of climate models separately [@shepherd2018]. However, the
+patterns identified between low, medium and high clusters of reefs suggest that the
+importance of depth refugia is consistent across scenarios. Similarly, at the management
+area scale, only 1% of reefs were assigned a ‘low’ and ‘high’ cluster in different GCMs,
+suggesting that intrinsic reef properties can prevent high cover resilient reefs from
+crashing under a different future climate scenario.
 
-There are multiple caveats in how coral ecosystem dynamics are modelled in this investigation.
-We model coral colonies as objects with circular diameter values and track these diameters over timesteps through growth.
-Due to the availability of quality future projected data we do not consider the impacts of waves, cyclones and currents on coral colony survival and bleaching (insert citations for waves affecting survival and bleaching).
-We do not consider the impacts of Crown of Thorns Starfish (CoTS) on coral survival and reef resilience (insert citation for cots affecting corals).
-Furthermore, there are multiple caveats to acknowledge in the data sources used in this investigation.
-Uncertainty in connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress projections are likely to influence the results obtained in this investigation.
-To limit the influence of bathymetry data on results, reefs with less than 5% data coverage are removed from analyses.
-We investigate a range of future climate responses and thermal projections to account for a range of possible futures, and our results suggest the factors that influence reef resilience are consistent across these scenarios.
+There are multiple caveats in how coral ecosystem dynamics are modelled in this
+investigation. We model coral colonies as objects with circular diameter values and track
+these diameters over timesteps through growth. Due to the availability of quality future
+projected data we do not consider the impacts of waves, cyclones and currents on coral
+colony survival and bleaching (insert citations for waves affecting survival and bleaching).
+We do not consider the impacts of Crown of Thorns Starfish (CoTS) on coral survival and reef
+resilience (insert citation for cots affecting corals). Furthermore, there are multiple
+caveats to acknowledge in the data sources used in this investigation. Uncertainty in
+connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress
+projections are likely to influence the results obtained in this investigation. To limit the
+influence of bathymetry data on results, reefs with less than 5% data coverage are removed
+from analyses. We investigate a range of future climate responses and thermal projections to
+account for a range of possible futures, and our results suggest the factors that influence
+reef resilience are consistent across these scenarios.
 
-ADRIA - CoralBlox has not been calibrated or validated at the GBR-wide scale.
-Accordingly, the purpose of this investigation is to assess the relative influence of reef characteristics on future resilience and highlight possible outcomes under highly uncertain future scenarios, rather than provide spatially explicit predictions of future resilience.
+ADRIA - CoralBlox has not been calibrated or validated at the GBR-wide scale. Accordingly,
+the purpose of this investigation is to assess the relative influence of reef
+characteristics on future resilience and highlight possible outcomes under highly uncertain
+future scenarios, rather than provide spatially explicit predictions of future resilience.
 
-Further analyses could build on the findings of this study by analysing the impacts of prioritising reef depth in reef restoration intervention decision making.
-The ADRIA platform is developed as a modelling tool to incorporate multi-criteria decision analysis (MCDA) and ecosystem scenario modelling into reef restoration decision analysis.
-The platform allows for the investigation of different reef characteristics to be targetted in decision making and models the evolving outcomes as a result of reef interventions at various locations.
-The capability of ADRIA-CoralBlox could be further expanded by incorporating the impacts of waves, cyclones, CoTS and currents into reef resilience investigations [@lin2023; @mcclanahan2005; @grimaldi2022; @liu2024].
-Additionally, the investigation could be enhanced by incorporating future ocean acidification into considerations of coral carbonate budgets required for healthy habitat production.
+Further analyses could build on the findings of this study by analysing the impacts of
+prioritising reef depth in reef restoration intervention decision making. The ADRIA platform
+is developed as a modelling tool to incorporate multi-criteria decision analysis (MCDA) and
+ecosystem scenario modelling into reef restoration decision analysis. The platform allows
+for the investigation of different reef characteristics to be targetted in decision making
+and models the evolving outcomes as a result of reef interventions at various locations. The
+capability of ADRIA-CoralBlox could be further expanded by incorporating the impacts of
+waves, cyclones, CoTS and currents into reef resilience investigations [@lin2023;
+@mcclanahan2005; @grimaldi2022; @liu2024]. Additionally, the investigation could be enhanced
+by incorporating future ocean acidification into considerations of coral carbonate budgets
+required for healthy habitat production.
 
@@
 
-Overall, our results suggest that when modelled as part of a large and complex ecosystem, reef depth is a key factor contributing to ongoing reef resilience.
-We provide evidence in support of depth as a form of refugia for shallow reefs.
-While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts [@anthony2020; @hock2017], our results suggest that resilient reefs do not have greater incoming or total connectivity to contribute to their resilience under modelled projected conditions.
-Instead, we suggest that depth, and likely other environmental thermal refugia mechanisms contribute greater to overall reef resilience and recovery.
-We suggest further analyses that investigate the benefits of incorporating depth-based resilience into reef decision making.
+Overall, our results suggest that when modelled as part of a large and complex ecosystem,
+reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in
+support of depth as a form of refugia for shallow reefs. While protecting ‘key node’ reefs
+in larval connectivity networks is an important consideration for reef restoration efforts
+[@anthony2020; @hock2017], our results suggest that resilient reefs do not have greater
+incoming or total connectivity to contribute to their resilience under modelled projected
+conditions. Instead, we suggest that depth, and likely other environmental thermal refugia
+mechanisms contribute greater to overall reef resilience and recovery. We suggest further
+analyses that investigate the benefits of incorporating depth-based resilience into reef
+decision making.
 
@@
 
-CoralBlox model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
-Environmental disturbances and reproduction are not directly considered within CoralBlox.
-Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
-Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
-As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.
+CoralBlox model incorporates linear extension (growth) and background mortality rates that
+are dependent on the size and functional group of a coral colony. Environmental disturbances
+and reproduction are not directly considered within CoralBlox. Instead, these factors are
+considered by making changes to the distribution of colonies within CoralBlox timesteps
+using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
+Within ADRIA, we incorporate coral life history and environmental events in the following
+order: coral colony growth; coral reproduction; larval connectivity and settlement; and
+coral bleaching due to heat stress. As ADRIA and CoralBlox are coupled together to represent
+the system, we refer to both as ADRIA-CoralBlox.
 
-Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996].
-Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
-Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality.
-There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
+Coral fecundity rates are dependent on colony size and functional group following the
+results of Hall & Hughes [-@hall1996]. Coral fertilization rates are not considered within
+this model, however larval survival and viability are incorporated in connectivity modelling
+(see Connectivity modelling). Viable larvae settle at a reef location and are incorporated
+into the model as the smallest size class but are not directly impacted by modelled
+bleaching mortality. There has been contrasting evidence for juvenile corals being immune to
+thermal bleaching events [@depczynski2013], we assume the high background mortality of
+juveniles includes thermal stress [@álvarez-noriega2018].
 
@@
 
-CoralBlox uses user-defined size classes that influence size-dependent growth and mortality rates, through which the coral colonies progress as they grow in diameter.
-Within ADRIA, we define the distributions of these parameters, and the size classes based on ecological monitoring data from the Ecological Intelligence for Reef Restoration Program (EcoRRAP) ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
+CoralBlox uses user-defined size classes that influence size-dependent growth and mortality
+rates, through which the coral colonies progress as they grow in diameter. Within ADRIA, we
+define the distributions of these parameters, and the size classes based on ecological
+monitoring data from the Ecological Intelligence for Reef Restoration Program (EcoRRAP)
+([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
 
-![Reef Degree Heating Week timeseries clustered within each management area, for each GCM analysed.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories width=`{julia} timeseries_width`}
+![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
+analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
+between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
+represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
+represented five times (for each GCM), with each GCM displayed
+horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
+width="`{julia"} timeseries_width\`}
 
@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
+total connectivity strength and the number of years cover exceeds the carbonate budget
+threshold. Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using
+ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
+width="`{julia"} carb_width\`}
 
@@
 
-![Reef area-relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries width=`{julia} timeseries_width`}
+![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
+(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
+each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
+area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2040 within each
+bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
+to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
+width="`{julia"} timeseries_width\`}
 
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor width=`{julia} violin_width`}
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median cover – DHW correlation level for each cluster. Displays results
+for ACCESS-ESM1-5
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
+width="`{julia"} violin_width\`}
 
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW level for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean width=`{julia} violin_width`} <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
+assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
+median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
+(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
+within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW level for each cluster. Displays results for ACCESS-ESM1-5
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
+width="`{julia"}
+violin_width`} <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia} violin_width`} --\>
+Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia}
+violin_width\`} --\>
 
-![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion width=`{julia} violin_width`}
+![Initial proportion of coral habitable area occupied by corals for reefs within each
+bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
+are clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median proportion of habitable area occupied for each cluster. Displays
+results for ACCESS-ESM1-5
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
+width="`{julia"} violin_width\`}
 
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi width=`{julia} violin_width`}
+![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines within each violin represent the median log (natural) source – to – sink ratio for
+each cluster and grey points represent the ratio value for each reef. Vertical grey lines
+represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
+incoming connectivity levels. Displays results for ACCESS-ESM1-5
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
+width="`{julia"} violin_width\`}
 
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity width=`{julia} violin_width`}
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
+violin represent the median log (natural) total connectivity strength for each cluster.
+Displays results for ACCESS-ESM1-5
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
+width="`{julia"} violin_width\`}
 
@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents the median reef depth level in metres.
-Displays results from median timeseries using ACCESS-CM2.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the
+number of years cover exceeds the carbonate budget threshold. Point colour represents the
+median reef depth level in metres. Displays results from median timeseries using
+ACCESS-CM2.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate
+width="`{julia"} carb_width\`}
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using ACCESS-CM2.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
+total connectivity strength and the number of years cover exceeds the carbonate budget
+threshold. Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using
+ACCESS-CM2.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate
+width="`{julia"} carb_width\`}
 
@@
 
-![Reef area-relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries width=`{julia} timeseries_width`}
+![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
+(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
+each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
+area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2040 within each
+bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
+to 97.5 percentile confidence intervals. Displays results for ACCESS-CM2
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries
+width="`{julia"} timeseries_width\`}
 
-![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median depth for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth width=`{julia} violin_width`}
+![Median depth for reefs within each bioregion, separated into clusters assigned by
+timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
+area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
+are clusters with intermediate median area-relative cover between 2030 and 2040 within each
+bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
+between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
+cluster. Displays results for ACCESS-CM2
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth
+width="`{julia"} violin_width\`}
 
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW level for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean width=`{julia} violin_width`}
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
+assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
+median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
+(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
+within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW level for each cluster. Displays results for ACCESS-CM2
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean
+width="`{julia"} violin_width\`}
 
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor width=`{julia} violin_width`}
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median cover – DHW correlation level for each cluster. Displays results
+for ACCESS-CM2
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor
+width="`{julia"} violin_width\`}
 
@@
 
-![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion width=`{julia} violin_width`}
+![Initial proportion of coral habitable area occupied by corals for reefs within each
+bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
+are clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median proportion of habitable area occupied for each cluster. Displays
+results for ACCESS-CM2
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion
+width="`{julia"} violin_width\`}
 
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi width=`{julia} violin_width`}
+![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines within each violin represent the median log (natural) source – to – sink ratio for
+each cluster and grey points represent the ratio value for each reef. Vertical grey lines
+represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
+incoming connectivity levels. Displays results for ACCESS-CM2
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi
+width="`{julia"} violin_width\`}
 
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity width=`{julia} violin_width`}
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
+violin represent the median log (natural) total connectivity strength for each cluster.
+Displays results for ACCESS-CM2
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity
+width="`{julia"} violin_width\`}
 
@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents the median reef depth level in metres.
-Displays results from median timeseries using EC-Earth3-Veg.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the
+number of years cover exceeds the carbonate budget threshold. Point colour represents the
+median reef depth level in metres. Displays results from median timeseries using
+EC-Earth3-Veg.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate
+width="`{julia"} carb_width\`}
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using EC-Earth3-Veg.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
+total connectivity strength and the number of years cover exceeds the carbonate budget
+threshold. Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using
+EC-Earth3-Veg.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate
+width="`{julia"} carb_width\`}
 
@@
 
-![Reef area-relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries width=`{julia} timeseries_width`}
+![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
+(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
+each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
+area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2040 within each
+bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
+to 97.5 percentile confidence intervals. Displays results for EC-Earth3-Veg
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries
+width="`{julia"} timeseries_width\`}
 
-![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median depth for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth width=`{julia} violin_width`}
+![Median depth for reefs within each bioregion, separated into clusters assigned by
+timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
+area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
+are clusters with intermediate median area-relative cover between 2030 and 2040 within each
+bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
+between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
+cluster. Displays results for EC-Earth3-Veg
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth
+width="`{julia"} violin_width\`}
 
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW level for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean width=`{julia} violin_width`}
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
+assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
+median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
+(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
+within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW level for each cluster. Displays results for EC-Earth3-Veg
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean
+width="`{julia"} violin_width\`}
 
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor width=`{julia} violin_width`}
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median cover – DHW correlation level for each cluster. Displays results
+for EC-Earth3-Veg
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor
+width="`{julia"} violin_width\`}
 
@@
 
-![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion width=`{julia} violin_width`}
+![Initial proportion of coral habitable area occupied by corals for reefs within each
+bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
+are clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median proportion of habitable area occupied for each cluster. Displays
+results for EC-Earth3-Veg
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion
+width="`{julia"} violin_width\`}
 
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi width=`{julia} violin_width`}
+![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines within each violin represent the median log (natural) source – to – sink ratio for
+each cluster and grey points represent the ratio value for each reef. Vertical grey lines
+represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
+incoming connectivity levels. Displays results for EC-Earth3-Veg
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi
+width="`{julia"} violin_width\`}
 
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity width=`{julia} violin_width`}
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
+violin represent the median log (natural) total connectivity strength for each cluster.
+Displays results for EC-Earth3-Veg
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity
+width="`{julia"} violin_width\`}
 
@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents the median reef depth level in metres.
-Displays results from median timeseries using GFDL-CM4.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the
+number of years cover exceeds the carbonate budget threshold. Point colour represents the
+median reef depth level in metres. Displays results from median timeseries using
+GFDL-CM4.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate
+width="`{julia"} carb_width\`}
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using GFDL-CM4.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
+total connectivity strength and the number of years cover exceeds the carbonate budget
+threshold. Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using
+GFDL-CM4.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate
+width="`{julia"} carb_width\`}
 
@@
 
-![Reef area-relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries width=`{julia} timeseries_width`}
+![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
+(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
+each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
+area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2040 within each
+bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
+to 97.5 percentile confidence intervals. Displays results for GFDL-CM4
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries
+width="`{julia"} timeseries_width\`}
 
-![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median depth for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth width=`{julia} violin_width`}
+![Median depth for reefs within each bioregion, separated into clusters assigned by
+timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
+area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
+are clusters with intermediate median area-relative cover between 2030 and 2040 within each
+bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
+between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
+cluster. Displays results for GFDL-CM4
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth
+width="`{julia"} violin_width\`}
 
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW level for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean width=`{julia} violin_width`}
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
+assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
+median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
+(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
+within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW level for each cluster. Displays results for GFDL-CM4
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean
+width="`{julia"} violin_width\`}
 
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor width=`{julia} violin_width`}
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median cover – DHW correlation level for each cluster. Displays results
+for GFDL-CM4
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor
+width="`{julia"} violin_width\`}
 
@@
 
-![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion width=`{julia} violin_width`}
+![Initial proportion of coral habitable area occupied by corals for reefs within each
+bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
+are clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median proportion of habitable area occupied for each cluster. Displays
+results for GFDL-CM4
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion
+width="`{julia"} violin_width\`}
 
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi width=`{julia} violin_width`}
+![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines within each violin represent the median log (natural) source – to – sink ratio for
+each cluster and grey points represent the ratio value for each reef. Vertical grey lines
+represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
+incoming connectivity levels. Displays results for GFDL-CM4
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi
+width="`{julia"} violin_width\`}
 
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity width=`{julia} violin_width`}
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
+violin represent the median log (natural) total connectivity strength for each cluster.
+Displays results for GFDL-CM4
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity
+width="`{julia"} violin_width\`}
 
@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents the median reef depth level in metres.
-Displays results from median timeseries using NorESM2-MM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the
+number of years cover exceeds the carbonate budget threshold. Point colour represents the
+median reef depth level in metres. Displays results from median timeseries using
+NorESM2-MM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate
+width="`{julia"} carb_width\`}
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2099.
-The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural) total connectivity strength and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using NorESM2-MM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate width=`{julia} carb_width`}
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
+total connectivity strength and the number of years cover exceeds the carbonate budget
+threshold. Point colour represents log (natural) scaled reef total connectivity strength.
+Displays results from median timeseries using
+NorESM2-MM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate
+width="`{julia"} carb_width\`}
 
@@
 
-![Reef area-relative coral cover timeseries clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the cluster median timeseries and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries width=`{julia} timeseries_width`}
+![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
+(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
+each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
+area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2040 within each
+bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
+to 97.5 percentile confidence intervals. Displays results for NorESM2-MM
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries
+width="`{julia"} timeseries_width\`}
 
-![Median depth for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median depth for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth width=`{julia} violin_width`}
+![Median depth for reefs within each bioregion, separated into clusters assigned by
+timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
+area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
+are clusters with intermediate median area-relative cover between 2030 and 2040 within each
+bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
+between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
+cluster. Displays results for NorESM2-MM
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth
+width="`{julia"} violin_width\`}
 
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW level for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean width=`{julia} violin_width`}
+![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
+assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
+median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
+(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
+within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW level for each cluster. Displays results for NorESM2-MM
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean
+width="`{julia"} violin_width\`}
 
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor width=`{julia} violin_width`}
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median cover – DHW correlation level for each cluster. Displays results
+for NorESM2-MM
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor
+width="`{julia"} violin_width\`}
 
@@
 
-![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion width=`{julia} violin_width`}
+![Initial proportion of coral habitable area occupied by corals for reefs within each
+bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
+are clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines represent the median proportion of habitable area occupied for each cluster. Displays
+results for NorESM2-MM
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion
+width="`{julia"} violin_width\`}
 
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) source – to – sink ratio for each cluster and grey points represent the ratio value for each reef.
-Vertical grey lines represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and incoming connectivity levels.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi width=`{julia} violin_width`}
+![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines within each violin represent the median log (natural) source – to – sink ratio for
+each cluster and grey points represent the ratio value for each reef. Vertical grey lines
+represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
+incoming connectivity levels. Displays results for NorESM2-MM
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi
+width="`{julia"} violin_width\`}
 
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines within each violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity width=`{julia} violin_width`}
+![Log (natural) total connectivity strength for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
+violin represent the median log (natural) total connectivity strength for each cluster.
+Displays results for NorESM2-MM
+GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity
+width="`{julia"} violin_width\`}

### 2025-07-11 paper/paper_draft.qmd
Add references

@@
 [@grimaldi2022]. Current modelling projects severe declines in coral cover under projections
-of Degree Heating Weeks \[**Bozec 2025**\]. These coral cover declines will be compounded by
-ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks
+of Degree Heating Weeks [@bozec]. These coral cover declines will be compounded by ocean
+acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks
 [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. Ominously, the
@@
 erosion of coral reef carbonate frameworks is controlled by a range of processes including
-coral accumulation \[**Perry**\], bioerosion , physical damage generating coral rubble
-\[**Kenyon**\], and calcification and CaCO₃ dissolution rates \[**Eyre 2014, 2018**\]. The
-balance of these processes and occurrence of net carbonate framework production (referred to
-as a positive carbonate budget) are influenced by factors such as coral cover and complexity
-\[**Perry, Desbiens**\], rates of physical environmental processes, and ocean acidity
-\[**Perry, Eyre**\]. Total live coral cover on a reef highly influences the maintenance of
-net positive carbonate budgets, with estimates ranging from 10 to 20% \[**Perry**\] of a
+coral accumulation [@perry2015], bioerosion , physical damage generating coral rubble
+[@kenyon], and calcification and CaCO₃ dissolution rates [@eyre2014; @eyre2018]. The balance
+of these processes and occurrence of net carbonate framework production (referred to as a
+positive carbonate budget) are influenced by factors such as coral cover and complexity
+[@perry2012; @desbiens], rates of physical environmental processes, and ocean acidity
+[@perry2015; @eyre2018]. Total live coral cover on a reef highly influences the maintenance
+of net positive carbonate budgets, with estimates ranging from 10 to 20% [@perry2015] of a
 reef's total area required to maintain positive budgets. For mid and outer shelf reefs on
-the Great Barrier Reef, this threshold is approximately 17% live coral cover
-\[**Desbiens**\].
+the Great Barrier Reef, this threshold is reportedly 17% live coral cover [@desbiens].
 

### 2025-07-11 paper/paper_draft.qmd
Adjust last paragraph
Ideally we'd think of moving these closer to the start

@@
 resilience and the maintenance of positive carbonate budgets. Improvements in coral reef
-climate response modeling, including sampling from a range of possible climate futures,
-enable timeseries analyses of uncertain climate change and ecological scenarios [@bode2017;
-@chollett2022; @donner2018; @klein2024; @uusitalo2015]. While it has previously been
-suggested that highly connected source reefs that are resilient to bleaching and CoTS
-outbreaks are likely to play a critical role in supporting future reef recovery across the
-entire GBR [@hock2017], integrated modelling under current projections of Degree Heating
-Weeks indicate that depth, rather than connectivity, plays a critical role in determining
-reef resilience. It is further demonstrated that depth supports the maintenance of a postive
-carbonate budget under all Global Climate Models.
+climate response modeling, including sampling from a range of current projected climate
+futures, enable timeseries analyses of uncertain climate change and ecological scenarios
+[@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].
+
+It has previously been suggested that highly connected source reefs that are resilient to
+bleaching and CoTS outbreaks are likely to play a critical role in supporting future reef
+recovery across the entire GBR [@hock2017]. Integrated modelling incorporating data from the
+latest advancements in coral population modelling [@ribeirodealmeida2024], whole of
+ecosystem larval connectivity \[**citation**\], and current projections of Degree Heating
+Weeks [@dixon2022; @dixon] indicate that depth, rather than connectivity, plays a more
+critical role in reef resilience under projected conditions. It is further demonstrated that
+deeper reefs support maintenance of positive carbonate budget under all climate projections.
 

### 2025-07-11 paper/paper_draft.qmd
Fix image links

@@
 site at Cape
-Cleveland.](/../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
-width="`{julia"} map_width\`}
+Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
+width="`{julia} map_width`"}
 
@@
 the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
-2021).](/../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs
-width="`{julia"} ecs_width\`}
+2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs
+width="`{julia} ecs_width`" height=500 align="center"}
 
@@
 median reef depth level in metres. Displays results from median timeseries using
-ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
-width="`{julia"} carb_width\`}
+ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
+width="`{julia} carb_width`}
 
@@
 represented five times (for each GCM), with each GCM displayed
-horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
-width="`{julia"} timeseries_width\`}
+horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
+width="`{julia} timeseries_width`}
 
@@
 cluster. Displays results for ACCESS-ESM1-5
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
+width="`{julia} violin_width`}
 
@@
 represented five times (for each GCM), with each GCM displayed
-horizontally.](/../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
-width="`{julia"} timeseries_width\`}
+horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
+width="`{julia} timeseries_width`}
 
@@
 Displays results from median timeseries using
-ACCESS-ESM1-5.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
-width="`{julia"} carb_width\`}
+ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
+width="`{julia} carb_width`}
 
@@
 to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
-width="`{julia"} timeseries_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
+width="`{julia} timeseries_width`}
 
@@
 for ACCESS-ESM1-5
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
+width="`{julia} violin_width`}
 
@@
 median DHW level for each cluster. Displays results for ACCESS-ESM1-5
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-width="`{julia"}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
+width="`{julia}
 violin_width`} <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia}
-violin_width\`} --\>
+Displays results for ACCESS-ESM1-5 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia}
+violin_width`} --\>
 
@@
 results for ACCESS-ESM1-5
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
+width="`{julia} violin_width`}
 
@@
 incoming connectivity levels. Displays results for ACCESS-ESM1-5
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
+width="`{julia} violin_width`}
 
@@
 Displays results for ACCESS-ESM1-5
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
+width="`{julia} violin_width`}
 
@@
 median reef depth level in metres. Displays results from median timeseries using
-ACCESS-CM2.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate
-width="`{julia"} carb_width\`}
+ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate
+width="`{julia} carb_width`}
 
@@
 Displays results from median timeseries using
-ACCESS-CM2.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate
-width="`{julia"} carb_width\`}
+ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate
+width="`{julia} carb_width`}
 
@@
 to 97.5 percentile confidence intervals. Displays results for ACCESS-CM2
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries
-width="`{julia"} timeseries_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries
+width="`{julia} timeseries_width`}
 
@@
 cluster. Displays results for ACCESS-CM2
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth
+width="`{julia} violin_width`}
 
@@
 median DHW level for each cluster. Displays results for ACCESS-CM2
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean
+width="`{julia} violin_width`}
 
@@
 for ACCESS-CM2
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor
+width="`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-CM2 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`} -->
+Displays results for ACCESS-CM2 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 results for ACCESS-CM2
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion
+width="`{julia} violin_width`}
 
@@
 incoming connectivity levels. Displays results for ACCESS-CM2
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi
+width="`{julia} violin_width`}
 
@@
 Displays results for ACCESS-CM2
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity
+width="`{julia} violin_width`}
 
@@
 median reef depth level in metres. Displays results from median timeseries using
-EC-Earth3-Veg.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate
-width="`{julia"} carb_width\`}
+EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate
+width="`{julia} carb_width`}
 
@@
 Displays results from median timeseries using
-EC-Earth3-Veg.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate
-width="`{julia"} carb_width\`}
+EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate
+width="`{julia} carb_width`}
 
@@
 to 97.5 percentile confidence intervals. Displays results for EC-Earth3-Veg
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries
-width="`{julia"} timeseries_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries
+width="`{julia} timeseries_width`}
 
@@
 cluster. Displays results for EC-Earth3-Veg
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth
+width="`{julia} violin_width`}
 
@@
 median DHW level for each cluster. Displays results for EC-Earth3-Veg
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean
+width="`{julia} violin_width`}
 
@@
 for EC-Earth3-Veg
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor
+width="`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`} -->
+Displays results for EC-Earth3-Veg GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 results for EC-Earth3-Veg
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion
+width="`{julia} violin_width`}
 
@@
 incoming connectivity levels. Displays results for EC-Earth3-Veg
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi
+width="`{julia} violin_width`}
 
@@
 Displays results for EC-Earth3-Veg
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity
+width="`{julia} violin_width`}
 
@@
 median reef depth level in metres. Displays results from median timeseries using
-GFDL-CM4.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate
-width="`{julia"} carb_width\`}
+GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate
+width="`{julia} carb_width`}
 
@@
 Displays results from median timeseries using
-GFDL-CM4.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate
-width="`{julia"} carb_width\`}
+GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate
+width="`{julia} carb_width`}
 
@@
 to 97.5 percentile confidence intervals. Displays results for GFDL-CM4
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries
-width="`{julia"} timeseries_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries
+width="`{julia} timeseries_width`}
 
@@
 cluster. Displays results for GFDL-CM4
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth
+width="`{julia} violin_width`}
 
@@
 median DHW level for each cluster. Displays results for GFDL-CM4
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean
+width="`{julia} violin_width`}
 
@@
 for GFDL-CM4
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor
+width="`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for GFDL-CM4 GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`} -->
+Displays results for GFDL-CM4 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 results for GFDL-CM4
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion
+width="`{julia} violin_width`}
 
@@
 incoming connectivity levels. Displays results for GFDL-CM4
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi
+width="`{julia} violin_width`}
 
@@
 Displays results for GFDL-CM4
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity
+width="`{julia} violin_width`}
 
@@
 median reef depth level in metres. Displays results from median timeseries using
-NorESM2-MM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate
-width="`{julia"} carb_width\`}
+NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate
+width="`{julia} carb_width`}
 
@@
 Displays results from median timeseries using
-NorESM2-MM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate
-width="`{julia"} carb_width\`}
+NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate
+width="`{julia} carb_width`}
 
@@
 to 97.5 percentile confidence intervals. Displays results for NorESM2-MM
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries
-width="`{julia"} timeseries_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries
+width="`{julia} timeseries_width`}
 
@@
 cluster. Displays results for NorESM2-MM
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth
+width="`{julia} violin_width`}
 
@@
 median DHW level for each cluster. Displays results for NorESM2-MM
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean
+width="`{julia} violin_width`}
 
@@
 for NorESM2-MM
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor
+width="`{julia} violin_width`}
 
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for NorESM2-MM GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`} -->
+Displays results for NorESM2-MM GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`} -->
 
@@
 results for NorESM2-MM
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion
+width="`{julia} violin_width`}
 
@@
 incoming connectivity levels. Displays results for NorESM2-MM
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi
+width="`{julia} violin_width`}
 
@@
 Displays results for NorESM2-MM
-GCM.](/../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity
-width="`{julia"} violin_width\`}
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity
+width="`{julia} violin_width`}

### 2025-07-11 paper/paper_draft.qmd
Minor tweaks to section

@@
 #| include: false
-
 cd("../src")
@@
 
-The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas.
-It follows the reef definitions as provided by the Great Barrier Reef Marine Park Authority
+The spatial extent of the GBR coral reefs represented in this investigation follows the reef
+definitions available via the Great Barrier Reef Marine Park Authority
 \[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94\].
-Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future
-thermal stress at each reef location. Five Global Climate Models (GCMs) (EC-Earth3-Veg,
-ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled
-Model Intercomparison Project (CMIP6; **citation**) were selected for this study.
+In total this covers 3806 reef areas across the GBR marine park. Annually and spatially
+averaged Degree Heating Week (DHW) data was used to represent future thermal stress at each
+reef location.
+
 Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great
@@
 Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
-[@liu2017; @skirving2020]. These GCMs were selected from available GCMs downscaled by Dixon
-et al. [-@dixon] based on evaluation by Grose et al. [-@grose2023], which found high
-correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian
-Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms
-in these GCMs. Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long
-term warming caused by a doubling of carbon dioxide above its pre-industrial concentration
+[@liu2017; @skirving2020]. The SSTs are represented by a selection of five Global Climate
+Models (GCMs) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6;
+**citation**). These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and
+GDFL-CM4, and their inclusion were based on evaluation by Grose et al. [-@grose2023], which
+found high correlation between observed temperature, rainfall, El Niño Southern Oscillation
+and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding
+mechanisms in these GCMs.
+
+Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming
+caused by a doubling of carbon dioxide above its pre-industrial concentration
 [@forster2021]. The four GCMs span a range of ECS values within the IPCC assessed likely

### 2025-07-11 paper/paper_draft.qmd
Comments for @eco-ben

@@
 mechanisms in these GCMs.
+<!-- @Ben, the last sentence above is quite long and doesn't explain why the five GCMs
+were selected. -->
 
@@
 caused by a doubling of carbon dioxide above its pre-industrial concentration
-[@forster2021]. The four GCMs span a range of ECS values within the IPCC assessed likely
+[@forster2021]. The four GCMs
+<!-- @Ben, says "four GCMs" here, but we used five? -->
+span a range of ECS values within the IPCC assessed likely
 range, and GCM development families, allowing for a range of possible climate futures to be
@@
 [@grose2023; @shepherd2018]). The following analyses are performed using each GCM
-separately. SSP 2-4.5 is used as a plausible emission pathway under current emission
+separately. SSP 2-4.5 was
+<!-- I changed "is" to "was" - anything to do with the analysis making the decision to
+standardise to past tense as currently there is a mix. -->
+used as a plausible emission pathway under current emission
 trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020;

### 2025-07-11 paper/paper_draft.qmd
Fix image links again
Missed last quote the last time which lead to links getting broken again!

@@
 ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
-width="`{julia} timeseries_width`}
+width="`{julia} timeseries_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
-width="`{julia} timeseries_width`}
+width="`{julia} timeseries_width`"}
 
@@
 ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
-width="`{julia} timeseries_width`}
+width="`{julia} timeseries_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-width="`{julia}
-violin_width`} <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
+width="`{julia"}
+violin_width`"} <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
 ‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
@@
 Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width=`{julia}
-violin_width`} --\>
+Displays results for ACCESS-ESM1-5 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width="`{julia}
+violin_width\`"} --\>
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries
-width="`{julia} timeseries_width`}
+width="`{julia} timeseries_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries
-width="`{julia} timeseries_width`}
+width="`{julia} timeseries_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries
-width="`{julia} timeseries_width`}
+width="`{julia} timeseries_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate
-width="`{julia} carb_width`}
+width="`{julia} carb_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries
-width="`{julia} timeseries_width`}
+width="`{julia} timeseries_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity
-width="`{julia} violin_width`}
+width="`{julia} violin_width`"}

### 2025-07-11 paper/paper_draft.qmd
quarto reformatting
Reducing height of figure
Otherwise in visual mode it takes up the entire screen!

@@
 caused by a doubling of carbon dioxide above its pre-industrial concentration
-[@forster2021]. The four GCMs
-<!-- @Ben, says "four GCMs" here, but we used five? -->
-span a range of ECS values within the IPCC assessed likely
-range, and GCM development families, allowing for a range of possible climate futures to be
-explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs;
-[@grose2023; @shepherd2018]). The following analyses are performed using each GCM
-separately. SSP 2-4.5 was
+[@forster2021]. The four GCMs <!-- @Ben, says "four GCMs" here, but we used five? --> span a
+range of ECS values within the IPCC assessed likely range, and GCM development families,
+allowing for a range of possible climate futures to be explored, capturing the uncertainty
+in future responses to CO2 increases (@fig-ecs; [@grose2023; @shepherd2018]). The following
+analyses are performed using each GCM separately. SSP 2-4.5 was
 <!-- I changed "is" to "was" - anything to do with the analysis making the decision to
-standardise to past tense as currently there is a mix. -->
-used as a plausible emission pathway under current emission
-trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020;
-IPCC -@climate2023].
+standardise to past tense as currently there is a mix. --> used as a plausible emission
+pathway under current emission trajectories, with similar atmospheric CO2 levels remaining
+until 2050 [@hausfather2020; IPCC -@climate2023].
 
@@
 2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs
-width="`{julia} ecs_width`" height=500 align="center"}
+width="`{julia} ecs_width`" height="500" align="center"}
 

### 2025-07-11 paper/paper_draft.qmd
Introduce uncertainty exploration of carbonate budget in narrative

@@
 Using median coral cover timeseries for each reef we calculated the number of years each
-reef maintains coral cover above these live coral cover threshold levels, inferring the
-number of years each reef maintains a net positive carbonate budget, accumulating reef
-framework. As in situ carbonate budgets are influenced by a range of processes, our
-calculations of carbonate budget maintainence are intended as estimates and do not reflect
-the conditions that will be experienced on a reef, but indicate relative levels of health
-across reefs. To capture the wide influence of environmental factors on carbonate budget
-levels, we analyse live coral cover thresholds required for positive carbonate budgets from
-10 to 20% (inclusive, at step 1%).
-
+reef maintains coral cover above a given percent threshold. The threshold represents the
+level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
+$\beta_{0}$ to indicate the budget equilibrium). Greater number of years above $\beta_{0}$
+therefore suggests greater resilience and opportunity for recovery.
+
+Recent analyses suggest a general threshold of ~17% live coral cover in the case of
+the GBR [@desbiens]. Given in situ carbonate budgets are influenced by (1) a range of
+processes; (2) the variety of approaches that could be used to measure those processes; and
+(3) the uncertainty surrounding these, it would be unreasonable to assume all
+reefs adhere to a single precise $\beta_{0}$ value. Concurrently, it is difficult to
+ascertain a suitable $\beta_{0}$ value for each individual reef.
+
+Given the uncertainties present, the proportion of reefs that display capacity to maintain
+coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of 10 to
+20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
+[-@perry2015] and Desbians et al., [-@desbiens] providing indications of the lower and upper
+bounds respectively. Spearman's correlation coefficient was adopted to assessed the
+relationship between connectivity strength and the number of years above $\beta_{0}$.
+The process was then repeated with median reef depth.
+
+<!-- Split and move below to results/discussion -->
 The distribution of number of years above carbonate-cover thresholds is right-skewed, with
 many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth
-levels and log (natural) total connectivity strength levels follow right-skewed
+levels and natural log total connectivity strength levels follow right-skewed
 distributions. Therefore, we analyse the correlation between number of years above

### 2025-07-11 paper/paper_draft.qmd
Explain why spearman's was adopted
@eco-ben to check and adjust.

@@
 [-@perry2015] and Desbians et al., [-@desbiens] providing indications of the lower and upper
-bounds respectively. Spearman's correlation coefficient was adopted to assessed the
-relationship between connectivity strength and the number of years above $\beta_{0}$.
-The process was then repeated with median reef depth.
+bounds respectively.
+
+The relationship between the number of years above $\beta_{0}$ and median reef depth was
+then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
+adopted as reef depth distributions are expected to be non-normal and highly skewed.
+Furthermore, reefs are naturally of different types and experience different conditions,
+and so the monotonic trends (whether the relationship consistently increase or decrease)
+rather than the exact quantative relationship is of interest.
 

### 2025-07-11 src/common.jl
Remove unneeded and problematic code from common that impacts setup

@@ -199,114 +199,6 @@ function relative_site_cover(x)
     return x
 end
 
-canonical_reefs = find_latest_file("../../canonical-reefs/output/")
-canonical_reefs = GDF.read(canonical_reefs)
-
-# Get location indices
-REGION_REEFS = DataStructures.OrderedDict(
-    "Far Northern Management Area" => Int64[],
-    "Cairns/Cooktown Management Area" => Int64[],
-    "Townsville/Whitsunday Management Area" => Int64[],
-    "Mackay/Capricorn Management Area" => Int64[],
-)
-
-for mgmt_area in collect(keys(REGION_REEFS))
-    if mgmt_area == "NA"
-        continue
-    end
-
-    REGION_REEFS[mgmt_area] = findall(canonical_reefs.management_area .== mgmt_area)
-end
-
-"""
-    connectivity_scoring(
-        conn_matrix::YAXArray;
-        gdf::DataFrame=nothing,
-        context_layer::Symbol=nothing,
-        conn_col_name::Symbol=nothing,
-        by_layer::Bool=false
-    )::DataFrame
-
-Calculate eigenvector_centrality connectivity scores for GBR reefs at different spatial scales.
-When by_layer=true and a DataFrame is given for gdf and a layer symbol is given for context_layer,
-then reefs are subset into categories via context_layer groups and then eigenvectors are calculated.
-
-# Arguments
-- `conn_matrix` : YAXArray containing the connectivity values. Diagonal should be set to 0 prior to use.
-- `gdf` : DataFrame containing context_layer.
-- `context_layer` : Categorical column with levels for grouping.
-- `by_layer` : Calculate by grouping reefs by context_layer (vs whole GBR connectivity).
-"""
-function connectivity_scoring(
-    conn_matrix::YAXArray;
-    gdf=nothing,
-    context_layer=nothing,
-    conn_col_name=nothing,
-    by_layer::Bool=false
-)::DataFrame
-    RME_UNIQUE_ID = collect(getAxis("Source", conn_matrix).val)
-    connectivity_scores = DataFrame(
-        [RME_UNIQUE_ID, Vector{Union{Missing,Float64}}(missing, 3806)],
-        [:RME_UNIQUE_ID, :conn_score]
-    )
-
-    if by_layer
-        for level in unique(gdf[:, context_layer])
-            level_reefs = gdf[gdf[:, context_layer].==level, :RME_UNIQUE_ID]
[…]

### 2025-07-11 paper/paper_draft.qmd
Indicate why the range is used
Avoid false precision!

@@
 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
-[-@perry2015] and Desbians et al., [-@desbiens] providing indications of the lower and upper
-bounds respectively.
+[-@perry2015] and Desbians et al., [-@desbiens] providing plausible indications of the
+lower and upper bounds respectively. Robustness of the conclusions drawn to the uncertainty
+in the precise value of $\beta_{0}$ for all reefs can then be assessed by using a range.
 

### 2025-07-11 paper/paper_draft.qmd
Initial light pass at rewriting carbonate threshold result section

@@
 
-The number of years reefs maintain coral cover above a required carbonate budget level
-substantially decreases as the required carbonate budget threshold (as a percentage of reef
-area) increases. Reefs with greater median depth levels maintain coral cover above required
-carbonate budget levels for longer than reefs at shallow depths
-[@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate positive correlation
-with the number of years a reef maintains coral cover above the required threshold
-[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintainence correlation
-decreases as the required carbonate budget threshold increases. This is likely due to an
-increasing number of reefs being unable to maintain coral cover above threshold levels as
-the threshold increases. There are no clear relationships between reef total connectivity
-levels and the number of years reefs maintain coral cover above carbonate budget threshold
-levels [@sfig-access-esm1-5-conn-carbonate]. Reef log (natural) total connectivity strength
-has no correlation with the number of years a reef maintains cover above the required
-thresholds. Log connectivity strength - carbonate budget maintainence correlation slightly
-decreases as the required carbonate budget threshold increases.
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+As one might expect, the number of years above $\beta_{0}$ (the assumed positive carbonate
+budget threshold) substantially decreases as $\beta_{0}$ increases.
+
+Reefs with greater median depth levels maintain coral cover above
+indicative carbonate budget levels for a longer time frame compared to reefs with shallower
+median depths [@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate
+positive correlation with the number of years a reef maintains coral cover above the
+required threshold [@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget
+maintainence correlation decreases as the required carbonate budget threshold increases.
+This is likely due to an increasing number of reefs being unable to maintain coral cover
+above threshold levels as the threshold increases. There are no clear relationships between
+reef total connectivity levels and the number of years reefs maintain coral cover above
+carbonate budget threshold levels [@sfig-access-esm1-5-conn-carbonate]. The natural log of
+total connectivity strength was found to have no correlation with the number of years a reef
+maintains cover above the required thresholds. Log connectivity strength - carbonate budget
+maintainence correlation slightly decreases as the required carbonate budget threshold
+increases.
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025
+to 1. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
 Bracketed x-axis values represent the Spearman's correlation between reef depth and the

### 2025-07-11 paper/paper_draft.qmd
qualify "range"
Standardise methods to past tense

@@
 In total this covers 3806 reef areas across the GBR marine park. Annually and spatially
-averaged Degree Heating Week (DHW) data was used to represent future thermal stress at each
+averaged Degree Heating Week (DHW) data were used to represent future thermal stress at each
 reef location.
@@
 Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
-[@liu2017; @skirving2020]. The SSTs are represented by a selection of five Global Climate
+[@liu2017; @skirving2020]. DHWs were represented by a selection of five Global Climate
 Models (GCMs) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6;
 **citation**). These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and
-GDFL-CM4, and their inclusion were based on evaluation by Grose et al. [-@grose2023], which
-found high correlation between observed temperature, rainfall, El Niño Southern Oscillation
-and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding
-mechanisms in these GCMs.
+GDFL-CM4, and their inclusion were based on evaluation by Grose et al.
+[-@grose2023].
+Grose et al.
+[-@grose2023] found high correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms in these GCMs.
 <!-- @Ben, the last sentence above is quite long and doesn't explain why the five GCMs
@@
 caused by a doubling of carbon dioxide above its pre-industrial concentration
-[@forster2021]. The four GCMs <!-- @Ben, says "four GCMs" here, but we used five? --> span a
-range of ECS values within the IPCC assessed likely range, and GCM development families,
-allowing for a range of possible climate futures to be explored, capturing the uncertainty
-in future responses to CO2 increases (@fig-ecs; [@grose2023; @shepherd2018]). The following
-analyses are performed using each GCM separately. SSP 2-4.5 was
-<!-- I changed "is" to "was" - anything to do with the analysis making the decision to
-standardise to past tense as currently there is a mix. --> used as a plausible emission
-pathway under current emission trajectories, with similar atmospheric CO2 levels remaining
-until 2050 [@hausfather2020; IPCC -@climate2023].
+[@forster2021].
+The five GCMs span a range of ECS values within the IPCC assessed likely range, and GCM development families, allowing for a range of possible climate futures to be explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs; [@grose2023; @shepherd2018]).
+The following analyses were performed using each GCM separately.
+SSP 2-4.5 was
+used as a plausible emission pathway under current emission trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020; IPCC -@climate2023].
 
@@
 
-We track the thermal tolerance of each functional group and size class as a truncated normal
-distribution that is updated in each timestep following growth and recruitment. This
+In ADRIA we track the thermal tolerance of each functional group and size class as a truncated normal distribution that is updated in each timestep following growth and recruitment. This
 distribution determines that proportion of the population on a reef that is susceptible to
@@
 
-Tropical cyclones and impact of wave activity to reefs are not included in this
+Tropical cyclones and impact of wave activity to reefs were not included in this
 investigation. We scale coral bleaching impacts by a coefficient determined by the median
@@
 coral colonies on a reef impacted by high heat stress as depth increases. Median depths for
-each reef location have been extracted from satellite derived bathymetry data for the Great
+each reef location were extracted from satellite derived bathymetry data for the Great
 Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due to varying
 degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs
-with less than 5% coverage of valid bathymetry data have been removed from this
+with less than 5% coverage of valid bathymetry data were removed from this
 investigation. Furthermore, reefs that were outside the GBRMPA management areas or not
@@
 lower and upper bounds respectively. Robustness of the conclusions drawn to the uncertainty
-in the precise value of $\beta_{0}$ for all reefs can then be assessed by using a range.
+in the precise value of $\beta_{0}$ for all reefs can then be assessed by using the
+indicative range.
 
@@
 
-Reefs in each timeseries cluster are compared to identify characteristics that differ
+Reefs in each timeseries cluster were compared to identify characteristics that differ
 between low, medium and high coral cover clusters. These characteristics include reef median
@@
 reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa
-\* reef \* scenario matrix. The mean timeseries was calculated over the first four scenarios
-for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then
-used to calculate an overall mean DHW – tolerance value for each reef under each GCM.
+\* reef \* scenario matrix.
+The mean timeseries DHW - tolerance was calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then used to calculate an overall mean DHW – tolerance value for each reef under each GCM.
 

### 2025-07-11 paper/paper_draft.qmd
Slight adjustments to carbonate budget methods and results

@@
 then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
-adopted as reef depth distributions are expected to be non-normal and highly skewed.
-Furthermore, reefs are naturally of different types and experience different conditions,
-and so the monotonic trends (whether the relationship consistently increase or decrease)
-rather than the exact quantative relationship is of interest.
+adopted as reef depth and connectivity strength distributions are expected to be non-normal and
+highly skewed. Furthermore, reefs are naturally of different types and experience different 
+conditions, and so the monotonic trends (whether the relationship consistently increase or 
+decrease) rather than the exact quantative relationship is of interest.
 
@@
 This is likely due to an increasing number of reefs being unable to maintain coral cover
-above threshold levels as the threshold increases. There are no clear relationships between
-reef total connectivity levels and the number of years reefs maintain coral cover above
-carbonate budget threshold levels [@sfig-access-esm1-5-conn-carbonate]. The natural log of
-total connectivity strength was found to have no correlation with the number of years a reef
-maintains cover above the required thresholds. Log connectivity strength - carbonate budget
+above threshold levels as the threshold increases, with values becoming increasingly
+right-skewed. The natural log of total connectivity strength was found to have no 
+correlation with the number of years a reef maintains cover above the required thresholds
+[@sfig-access-esm1-5-conn-carbonate]. Log connectivity strength - carbonate budget 
 maintainence correlation slightly decreases as the required carbonate budget threshold

### 2025-07-11 paper/paper_draft.qmd
line formatting

@@
 **citation**). These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and
-GDFL-CM4, and their inclusion were based on evaluation by Grose et al.
-[-@grose2023].
-Grose et al.
-[-@grose2023] found high correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms in these GCMs.
+GDFL-CM4, and their inclusion were based on evaluation by Grose et al. [-@grose2023]. Grose
+et al. [-@grose2023] found high correlation between observed temperature, rainfall, El Niño
+Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region,
+and the corresponding mechanisms in these GCMs.
 <!-- @Ben, the last sentence above is quite long and doesn't explain why the five GCMs
@@
 caused by a doubling of carbon dioxide above its pre-industrial concentration
-[@forster2021].
-The five GCMs span a range of ECS values within the IPCC assessed likely range, and GCM development families, allowing for a range of possible climate futures to be explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs; [@grose2023; @shepherd2018]).
-The following analyses were performed using each GCM separately.
-SSP 2-4.5 was
-used as a plausible emission pathway under current emission trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020; IPCC -@climate2023].
+[@forster2021]. The five GCMs span a range of ECS values within the IPCC assessed likely
+range, and GCM development families, allowing for a range of possible climate futures to be
+explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs;
+[@grose2023; @shepherd2018]). The following analyses were performed using each GCM
+separately. SSP 2-4.5 was used as a plausible emission pathway under current emission
+trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020;
+IPCC -@climate2023].
 
@@
 
-In ADRIA we track the thermal tolerance of each functional group and size class as a truncated normal distribution that is updated in each timestep following growth and recruitment. This
-distribution determines that proportion of the population on a reef that is susceptible to
-bleaching (i.e. has a thermal threshold below the experienced DHW value). Starting
-distributions for thermal tolerance levels are informed by Bairos-Novak et al.
+In ADRIA we track the thermal tolerance of each functional group and size class as a
+truncated normal distribution that is updated in each timestep following growth and
+recruitment. This distribution determines that proportion of the population on a reef that
+is susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
+Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
 [-@bairos-novak2021].
@@
 degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs
-with less than 5% coverage of valid bathymetry data were removed from this
-investigation. Furthermore, reefs that were outside the GBRMPA management areas or not
-associated with a bioregion were removed from the investigation.
+with less than 5% coverage of valid bathymetry data were removed from this investigation.
+Furthermore, reefs that were outside the GBRMPA management areas or not associated with a
+bioregion were removed from the investigation.
 
@@
 
-Recent analyses suggest a general threshold of ~17% live coral cover in the case of
-the GBR [@desbiens]. Given in situ carbonate budgets are influenced by (1) a range of
-processes; (2) the variety of approaches that could be used to measure those processes; and
-(3) the uncertainty surrounding these, it would be unreasonable to assume all
-reefs adhere to a single precise $\beta_{0}$ value. Concurrently, it is difficult to
-ascertain a suitable $\beta_{0}$ value for each individual reef.
+Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
+[@desbiens]. Given in situ carbonate budgets are influenced by (1) a range of processes; (2)
+the variety of approaches that could be used to measure those processes; and (3) the
+uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
+single precise $\beta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
+$\beta_{0}$ value for each individual reef.
 
@@
 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
-[-@perry2015] and Desbians et al., [-@desbiens] providing plausible indications of the
-lower and upper bounds respectively. Robustness of the conclusions drawn to the uncertainty
-in the precise value of $\beta_{0}$ for all reefs can then be assessed by using the
-indicative range.
+[-@perry2015] and Desbians et al., [-@desbiens] providing plausible indications of the lower
+and upper bounds respectively. Robustness of the conclusions drawn to the uncertainty in the
+precise value of $\beta_{0}$ for all reefs can then be assessed by using the indicative
+range.
 
@@
 then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
-adopted as reef depth and connectivity strength distributions are expected to be non-normal and
-highly skewed. Furthermore, reefs are naturally of different types and experience different 
-conditions, and so the monotonic trends (whether the relationship consistently increase or 
-decrease) rather than the exact quantative relationship is of interest.
+adopted as reef depth and connectivity strength distributions are expected to be non-normal
+and highly skewed. Furthermore, reefs are naturally of different types and experience
+different conditions, and so the monotonic trends (whether the relationship consistently
+increase or decrease) rather than the exact quantative relationship is of interest.
 
 <!-- Split and move below to results/discussion -->
+
 The distribution of number of years above carbonate-cover thresholds is right-skewed, with
 many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth
-levels and natural log total connectivity strength levels follow right-skewed
-distributions. Therefore, we analyse the correlation between number of years above
-carbonate-cover thresholds and these characteristics using Spearman's correlation
-coefficient.
+levels and natural log total connectivity strength levels follow right-skewed distributions.
+Therefore, we analyse the correlation between number of years above carbonate-cover
+thresholds and these characteristics using Spearman's correlation coefficient.
 
@@
 reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa
-\* reef \* scenario matrix.
-The mean timeseries DHW - tolerance was calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational restraints, and then used to calculate an overall mean DHW – tolerance value for each reef under each GCM.
+\* reef \* scenario matrix. The mean timeseries DHW - tolerance was calculated over the
+first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational
+restraints, and then used to calculate an overall mean DHW – tolerance value for each reef
+under each GCM.
 
@@
 
-Reefs with greater median depth levels maintain coral cover above
-indicative carbonate budget levels for a longer time frame compared to reefs with shallower
-median depths [@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate
-positive correlation with the number of years a reef maintains coral cover above the
-required threshold [@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget
-maintainence correlation decreases as the required carbonate budget threshold increases.
-This is likely due to an increasing number of reefs being unable to maintain coral cover
-above threshold levels as the threshold increases, with values becoming increasingly
-right-skewed. The natural log of total connectivity strength was found to have no 
-correlation with the number of years a reef maintains cover above the required thresholds
-[@sfig-access-esm1-5-conn-carbonate]. Log connectivity strength - carbonate budget 
-maintainence correlation slightly decreases as the required carbonate budget threshold
-increases.
+Reefs with greater median depth levels maintain coral cover above indicative carbonate
+budget levels for a longer time frame compared to reefs with shallower median depths
+[@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate positive correlation
+with the number of years a reef maintains coral cover above the required threshold
+[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintainence correlation
+decreases as the required carbonate budget threshold increases. This is likely due to an
+increasing number of reefs being unable to maintain coral cover above threshold levels as
+the threshold increases, with values becoming increasingly right-skewed. The natural log of
+total connectivity strength was found to have no correlation with the number of years a reef
+maintains cover above the required thresholds [@sfig-access-esm1-5-conn-carbonate]. Log
+connectivity strength - carbonate budget maintainence correlation slightly decreases as the
+required carbonate budget threshold increases.
 

### 2025-07-13 paper/paper_draft.qmd
Initial rework of discussion around carbonate budgets

@@
 suggest that within shallow reef ecosystems (depth \< 30m), depth contributes greatly to
-reef resilience and the ability of the reef to maintain cover under heat stress. While
-similar findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia
-analyses have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal
-refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al.
-[-@venegas2019] found no association between depth and the alleviation of heat stress across
-a range of shallow reefs in the Pacific.
+reef resilience and the ability of the reef to maintain positive carbonate budgets under
+future conditions. While similar findings have been demonstrated in the eastern Pacific
+[@smith2014], depth refugia analyses have often focussed on the potential of mesophotic
+reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In
+contrast, Venegas et al. [-@venegas2019] found no association between depth and the
+alleviation of heat stress across a range of shallow reefs in the Pacific. Reefs at shallow
+depths experience no, or few, years with coral cover exceeding levels likely required to
+maintain positive carbonate budgets. Movement of reefs towards negative cabonate budgets
+under increasing future thermal stress over time may contribute to phase shifts in reef
+dominant $CaCO_3$ production from coral driven to coralline encrusting algae driven
+production, or to bioerosion dominated systems with rapid erosion of physical reef
+frameworks [@dudgeon2010; @perry2008].
 <!-- The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels.
@@
 within the 1-10m depth range (1800 reefs) 74% (1328) of reefs fall into the low and medium
-clusters (across all GCMs at the GBRMPA management region scale), with many suffering large
-future declines in reef health under climate change and possibly limiting the potential of
-interventions to deliver recovery in these locations. Reef intervention planning is a
+clusters (across all GCMs at the GBRMPA management region scale), with many unable to
+maintain positive carbonate budgets under future conditions. Reef intervention planning is a
 complex and challenging decision making process [@anthony2020], and our results suggest that
@@
 
-Furthermore, our results suggest that the capacity of reefs to maintain healthy coral
-habitat by being above positive net carbonate budget levels is greater for reefs at deeper
-depths than shallow depths. While the maintanence of positive carbonate budget levels does
-not appear to be linked to reef connectivity metrics. The maintanence of positive carbonate
-budgets is important for reef resilience under climate change.
-
 Five different GCMs were included in analyses to capture uncertainty in climate system
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-width="`{julia"}
-violin_width`"} <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width="`{julia}
-violin_width\`"} --\>
+width="`{julia"} violin_width\`"}
+
+<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into 
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the 
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ 
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 
+and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest 
+median area-relative cover between 2030 and 2040 within each bioregion. Solid lines 
+represent the median DHW tolerance value for each cluster. Displays results for 
+ACCESS-ESM1-5 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width="`{julia}
+violin_width\`"} -->
 

### 2025-07-13 src/plotting_functions.jl
reverse colormap for carbonate budget plots

@@ -787,7 +787,7 @@ function carbonate_budget_variable_scatter(
     labels = ["$(lab)\n($(round(year_variable_correlation[lab], digits=2)))" for lab in labels]
 
     # Get the default colormap (as a gradient with 256 colors)
-    base_cmap = cgrad(:viridis, 256)
+    base_cmap = cgrad(:viridis, 256; rev=true)
     # Convert all colors to RGBA with alpha = 0.4 (adjust as needed)
     transparent_colors = [RGBA(c.r, c.g, c.b, alpha) for c in base_cmap.colors]
     # Wrap into a ColorScheme object

### 2025-07-15 paper/paper_draft.qmd
Add caveat about non- bias corrected DHW data
Edit intro for flow, conciseness
Remove reference to nutrients, cyclones etc, that aren't explored/relevant to the study.

@@
 as ecosystem services such as food, protection, tourism and Indigenous cultural value
-[@eddy2021; @stoeckl2021]. We aim to assess the impacts of possible climate futures and
-identify the characteristics of resilient reefs using the latest generation of larval
-connectivity research with scenario-based population modelling for the Great Barrier Reef
-ecosystem.
+[@eddy2021; @stoeckl2021].
+
+Understanding the characteristics of reefs that will persist under projected climate
+conditions requires examining reef resilience across multiple scales and processes.
+Structural resilience - the capacity to maintain coral populations and avoid ecosystem
+regime shifts - depends on three interconnected mechanisms. First, the ability of individual
+corals to survival thermal stress. Second, the connectivity networks that enable
+recolonisation after disturbances. Third, the maintenance of carbonate framework that
+provides reef structure. We aim to assess how these mechanisms interact under current
+projected climate conditions to identify the characteristics of structurally resilient reefs through scenario-based coral population modelling for the Great Barrier Reef ecosystem.
 
@@
 dispersal patterns mediated by hydrodynamic, spatial, and ecological processes
-[@grimaldi2022]. Current modelling projects severe declines in coral cover under projections
-of Degree Heating Weeks [@bozec]. These coral cover declines will be compounded by ocean
-acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks
-[@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. Ominously, the
-2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with
-some level of bleaching recorded on 79% of surveyed reefs [@cantin2024].
-
-Connectivity is said to play a crucial role in Great Barrier Reef resilience by enabling
-recolonization after disturbances and facilitating adaptation to climate pressures
-[@angeler2023; @elmhirst2009; @hock2017]. This connectivity, however, creates both strengths
-and vulnerabilities within the system. Larval source populations (those exporting more
-larvae than they import) are essential for system-wide resilience, as they provide larvae
-that enable recovery at distant locations after disturbances [@hock2017; @thomas2015].
-Individually, however, they are more vulnerable to extreme disturbances as they rely more
-heavily on local recruitment to support recovery. In contrast, sink populations can draw on
-external larval inputs from multiple and diverse sources [@ani2024; @hock2017]. When
-disturbances impact major larval source populations, the cascading effects extend throughout
-the network. Increased adult mortality reduces larval export in subsequent years, slowing
-recovery at the connected sink locations that depend on this external supply
-[@figueiredo2022; @hock2017; @munday2009]. Future climate change will further complicate
-these dynamics through population fragmentation, increased larval mortality, and altered
-hydrodynamics, potentially disrupting the connectivity patterns that currently maintain reef
-resilience.
-
-Beyond connectivity, coral resilience to climate change is determined by the complex
-interplay of environmental and biological factors. Environmental abiotic factors influence
-how reefs will experience climate change pressures, including the spatio-temporal patterns
-of thermal stress itself, and indirect factors that influence the stress experienced by
-corals. Environmental factors such as tropical cyclones and wind driven mixing [@lin2023;
-@mcclanahan2005]; currents [@grimaldi2022] and depth [@álvarez-noriega2018; @baird2018;
-@smith2014] can decrease the magnitude of thermal stress corals experience. Conversely, high
-light intensity and nutrient levels in the benthic zone can increase coral bleaching
-[@decarlo2020; @higuchi2015].
-
-Individual coral resilience depends on multiple biological factors beyond connectivity.
-Coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and acclimation and
-inherited thermal tolerance [@humanes2022; @lachs2024] all influence the outcome of high
-coral heat stress events. Importantly, corals have demonstrated adaptive capacity to develop
-thermal tolerance levels capable of delaying the onset of widespread bleaching under low
-emissions scenarios [@bairos-novak2021; @humanes2022]. This adaptive potential represents a
-crucial mechanism for reef persistence under moderate climate change, working in concert
-with the environmental factors that modulate thermal stress exposure.
-
-While these environmental and biological factors determine whether individual corals survive
-thermal stress events, the long-term viability of coral reefs depends not only on coral
-survival but also on the maintenance of reef structure through positive carbonate budgets.
-Scleractinian corals are primary habitat structures on coral reefs, and the accumulation and
-erosion of coral reef carbonate frameworks is controlled by a range of processes including
-coral accumulation [@perry2015], bioerosion , physical damage generating coral rubble
-[@kenyon], and calcification and CaCO₃ dissolution rates [@eyre2014; @eyre2018]. The balance
-of these processes and occurrence of net carbonate framework production (referred to as a
-positive carbonate budget) are influenced by factors such as coral cover and complexity
-[@perry2012; @desbiens], rates of physical environmental processes, and ocean acidity
-[@perry2015; @eyre2018]. Total live coral cover on a reef highly influences the maintenance
-of net positive carbonate budgets, with estimates ranging from 10 to 20% [@perry2015] of a
-reef's total area required to maintain positive budgets. For mid and outer shelf reefs on
-the Great Barrier Reef, this threshold is reportedly 17% live coral cover [@desbiens].
-
-Incorporating the latest advancements in whole ecosystem larval connectivity modeling and
-coral thermal response and adaptation research into coral population modeling allows an
-investigation into how abiotic and biotic factors interact to influence coral climate change
-resilience and the maintenance of positive carbonate budgets. Improvements in coral reef
-climate response modeling, including sampling from a range of current projected climate
-futures, enable timeseries analyses of uncertain climate change and ecological scenarios
-[@bode2017; @chollett2022; @donner2018; @klein2024; @uusitalo2015].
-
-It has previously been suggested that highly connected source reefs that are resilient to
-bleaching and CoTS outbreaks are likely to play a critical role in supporting future reef
-recovery across the entire GBR [@hock2017]. Integrated modelling incorporating data from the
-latest advancements in coral population modelling [@ribeirodealmeida2024], whole of
-ecosystem larval connectivity \[**citation**\], and current projections of Degree Heating
-Weeks [@dixon2022; @dixon] indicate that depth, rather than connectivity, plays a more
-critical role in reef resilience under projected conditions. It is further demonstrated that
-deeper reefs support maintenance of positive carbonate budget under all climate projections.
+[@grimaldi2022].
+The GBR faces severe projected coral cover declines under climate change [@bozec].
+These coral cover declines will be compounded by ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks
+[@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24
+Summer mass bleaching event may be signalling a shift towards this reef future, with some
+level of bleaching recorded on 79% of surveyed reefs [@cantin2024].
+
+At the individual coral scale, survival during thermal stress events depends on both
+environmental and biological factors. Environmental factors can either amplify or reduce
+thermal stress exposure. Depth has been suggested as one crucial factor that can provide
+a refuge from thermal stress [@álvarez-noriega2018; @baird2018; @smith2014]. Biological
+factors including coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005],
+and thermal tolerance through acclimation and inheritance [@humanes2022; @lachs2024] all
+influence survival outcomes. Importantly, corals demonstrate adaptive capacity to develop
+thermal tolerance that could delay widespread bleaching under moderate emissions scenarios
+[@bairos-novak2021; @humanes2022], representing a crucial mechanism for reef persistence.
+
+Beyond individual survival, reef-scale resilience depends on connectivity networks that
+enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017]. However,
+connectivity creates both strengths and vulnerabilities. Larval source populations that
+export more larvae than they import are essential for system-wide recovery, providing larvae
+that enable recolonization at distant locations [@hock2017; @thomas2015]. Yet these source
+reefs are paradoxically more vulnerable individually, relying heavily on local recruitment
+for their own recovery. When disturbances impact major source populations, cascading effects
+reduce larval export and slow recovery throughout the connected network [@figueiredo2022;
+@hock2017; @munday2009].
+
+Long-term reef viability requires not only coral survival and recolonization, but also
+maintenance of the physical reef structure through positive carbonate budgets. Scleractinian
+corals build the primary habitat framework, but reef persistence depends on the balance
+between carbonate accumulation [@perry2015] and loss through bioerosion, physical damage
+[@kenyon], and dissolution [@eyre2014; @eyre2018]. This balance is influenced by coral cover
+and complexity [@perry2012; @desbiens], environmental processes, and ocean chemistry
+[@perry2015; @eyre2018]. For Great Barrier Reef mid and outer shelf reefs, maintaining
+positive carbonate budgets requires approximately 17% live coral cover [@desbiens].
+
+Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response
+research enable integrated investigation of how these multiple factors interact to determine
+climate resilience. By incorporating the latest coral population models
+[@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections
+[@dixon2022], we can examine which factors most strongly influence reef persistence under
+different scenarios. While connectivity has been emphasized as critical for GBR resilience
+[@hock2017], our integrated modelling reveals that environmental factors - particularly
+depth - may play a more fundamental role in determining which reefs maintain viable coral
+populations and positive carbonate budgets under projected climate conditions.
 
@@
 influence of bathymetry data on results, reefs with less than 5% data coverage are removed
-from analyses. We investigate a range of future climate responses and thermal projections to
-account for a range of possible futures, and our results suggest the factors that influence
-reef resilience are consistent across these scenarios.
+from analyses. The DHW data used in this investigation have not been bias corrected for the 
+Great Barrier Reef region and is part of a wider Australian dataset [@dixon2022] developed 
+using statistical downscaling. We investigate a range of future climate responses and 
+thermal projections to account for a range of possible futures, and our results suggest 
+the factors that influence reef resilience are consistent across these scenarios.
 

### 2025-07-15 paper/paper_draft.qmd
Soften/qualify language

@@
 different scenarios. While connectivity has been emphasized as critical for GBR resilience
-[@hock2017], our integrated modelling reveals that environmental factors - particularly
-depth - may play a more fundamental role in determining which reefs maintain viable coral
-populations and positive carbonate budgets under projected climate conditions.
+[@hock2017], and remains an important consideration, our integrated modelling reveals depth
+may play a fundamental role in determining maintenance of reef coral population and positive
+carbonate budgets under current projections of climate change.
 

### 2025-07-16 paper/paper_draft.qmd
Add stub section for depth to fill in later
Possible discussion text on connectivity modelling methods
Still need to emphasise it's importance. And would be good to add similar changes for DHW-tolerance and possible improvements in understanding

@@
 
+### Depth estimation
+
+\*\* Describe process of estimating median depth for each reef \*\*
+
 ## Timeseries analysis
 
-ADRIA-CoralBlox was run for 4096 **sampled** scenarios per GCM. A median absolute coral
-cover timeseries for each reef was calculated for each GCM. For timeseries clustering reef
-cover timeseries were scaled by the total area of the reef to represent timeseries as a
-percentage of the total reef area. The proportion of each functional group occupying the
-reef (group evenness) was also investigated as a metric for timeseries analysis, but was
-found to not sufficiently capture the declined condition of reefs suffering from very low
-absolute coral cover.
+ADRIA-CoralBlox was run for 4096 **sampled** scenarios for each of the five GCMs.
+A median absolute coral cover timeseries for each reef was calculated for each GCM.
+For timeseries clustering reef cover timeseries were scaled by the total area of the reef
+to represent timeseries as a percentage of the total reef area. The proportion of each
+functional group occupying the reef (group evenness) was also investigated as a metric for
+timeseries analysis, but was found to not sufficiently capture the declined condition of reefs
+suffering from very low absolute coral cover.
 
@@
 
-It has been suggested that a primary facet of reef resilience is the degree of larval
-connectivity between reefs and the supply of recruits that a reef receives following
-disturbance [@hock2017]. It was expected that resilient reefs would have greater incoming
-than outgoing larval connectivity to promote recovery in years following thermal stress,
-while non-resilient reefs would have greater outgoing than incoming connectivity inhibiting
-recruitment of corals ability post thermal stress. In contrast, our results suggest that
-there are few differences between resilient and non-resilient reefs in connectivity metrics
-such as the ratio of outgoing to incoming larval connectivity and total connectivity
-strength. Hock et al. [-@hock2017] used larval connectivity modelling to identify resilient
-reefs that may supply up to 47% of the wider Great Barrier Reef ecosystem with larvae
-following disturbance. A critique of this approach [@bode2018] is that results obtained are
-highly sensitive to the biophysical dispersal model used, limiting the application of
-specific identified reefs. Reef depth was not considered in these investigations of reef
-network resilience. These investigations were performed using prior generations of larval
-connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time
-periods respectively. Using updated 1km resolution larval connectivity across the whole GBR,
-our results suggest that larval connectivity alone is not as important for reef resilience
-and recovery as environmental refugia from thermal stress such as depth.
+It is a strongly held conclusion in coral reef ecology that a primary facet of reef resilience 
+is the degree of larval connectivity between reefs and the supply of recruits that a 
+reef receives following disturbance [@hock2017] **expand citations**. It was expected that resilient reefs would
+have greater incoming than outgoing larval connectivity to promote recovery in years 
+following thermal stress, while non-resilient reefs would have greater outgoing than 
+incoming connectivity inhibiting recruitment of corals ability post thermal stress. In 
+contrast, our results suggest that there are few differences between resilient and 
+non-resilient reefs in connectivity metrics such as the ratio of outgoing to incoming larval 
+connectivity and total connectivity strength. Hock et al. [-@hock2017] used larval 
+connectivity modelling to identify resilient reefs that may supply up to 47% of the wider 
+Great Barrier Reef ecosystem with larvae following disturbance. A critique of this 
+approach [@bode2018] is that results obtained are highly sensitive to the biophysical 
+dispersal model used, limiting the application of specific identified reefs. Reef depth was
+not considered in these investigations of reef network resilience. These investigations 
+were performed using prior generations of larval connectivity models parameterised for 
+2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods respectively. Using updated 
+1km resolution larval connectivity across the whole GBR, with a limited temporal sample of
+particle flows, our results suggest that larval connectivity alone is not as important for
+reef resilience and recovery as environmental refugia from thermal stress such as depth. 
+Our findings may differ due to the highly uncertain nature of connectivity methods used 
+**citation**, the way larval flows and juvenile recruitment are implemented in ADRIA - 
+CoralBlox, and the magnitude of early bleaching events decreasing the breeding capacity 
+of strongly connected reefs. Further improvements in connectivity modelling are necessary 
+to provide a robust comparison of the factors influencing reef resilience.
 

### 2025-07-18 paper/paper_draft.qmd
Add section on connectivity improvements for further analyses
Currently unclear of what 'improvements' refers to other than larger datasets

@@
 patterns identified between low, medium and high clusters of reefs suggest that the
-importance of depth refugia is consistent across scenarios. Similarly, at the management
+importance of depth refugia is consistent across scenarios. 
+<!-- Similarly, at the management
 area scale, only 1% of reefs were assigned a ‘low’ and ‘high’ cluster in different GCMs,
 suggesting that intrinsic reef properties can prevent high cover resilient reefs from
-crashing under a different future climate scenario.
+crashing under a different future climate scenario. -->
 
@@
 connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress
-projections are likely to influence the results obtained in this investigation. To limit the
-influence of bathymetry data on results, reefs with less than 5% data coverage are removed
-from analyses. The DHW data used in this investigation have not been bias corrected for the
-Great Barrier Reef region and is part of a wider Australian dataset [@dixon2022] developed
-using statistical downscaling. We investigate a range of future climate responses and
-thermal projections to account for a range of possible futures, and our results suggest
-the factors that influence reef resilience are consistent across these scenarios.
+projections are likely to influence the results obtained in this investigation. Incorporating 
+further improvements in connectivity modelling and understanding of the influence of 
+climate change on reef connectivity would improve certainty in the conclusions suggested 
+in this investigation. To limit the influence of bathymetry data on results, reefs with 
+less than 5% data coverage are removed from analyses. The DHW data used in this 
+investigation have not been bias corrected for the Great Barrier Reef region and is part of
+a wider Australian dataset [@dixon2022] developed using statistical downscaling. We 
+investigate a range of future climate responses and thermal projections to account for 
+a range of possible futures, and our results suggest the factors that influence reef 
+resilience are consistent across these scenarios.
 

### 2025-07-21 src/ADRIA/HighResCoralStress/1_GCM_model_runs.jl
Quick fix for ADRIA.run_scenarios() issues with geodataframes geometry
geometry col gets loaded as GDF.GeometryVector{ArchGDAL.IGeometry} but ADRIA._get_geom_col() requires Vector{ArchGDAL.IGeometry}, preventing ADRIA.run_scenarios() from working. This may be an issue with the pinned version of GeoDataFrames in the project having an unrecognised type.

@@ -1,5 +1,6 @@
 using Revise, Infiltrator
 using YAXArrays, NetCDF
+using ArchGDAL
 
 include("../../common.jl")
 change_ADRIA_debug(false) # Ensure ADRIA debug mode is set to false to allow parallel processing.
@@ -11,6 +12,7 @@ gcms = dhw_scenarios.dhw.properties["members"]
 # GBR wide domain
 gbr_dom = ADRIA.load_domain(GBR_domain_path, "45")
 context_layers = gbr_dom.loc_data
+gbr_dom.loc_data.geometry = Vector{ArchGDAL.IGeometry}(gbr_dom.loc_data.geometry) # Need to recast gbr_dom geometry col for ADRIA.run_scenarios(). Possibly issue with GeoDataFrames version.
 
 for (g, GCM) in enumerate(gcms)
 

### 2025-07-21 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -6,9 +6,11 @@ budget thresholds, DHW tolerance levels and number of reefs in each bioregion.
 
 using ArchGDAL
 
+include("../../common.jl")
+
 change_ADRIA_debug(true) # Change ADRIA debug mode to true to extract DHW tolerance data from runs
 
-include("../../common.jl")
+using ADRIA
 
 # Load context layers with bioregions and target reefs
 context_layers = GDF.read("../outputs/ADRIA_results/HighResCoralStress/bellwether_reefs_carbonate.gpkg")
@@ -16,7 +18,7 @@ context_layers = GDF.read("../outputs/ADRIA_results/HighResCoralStress/bellwethe
 # GBR wide domain
 gbr_dom = ADRIA.load_domain("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/", "45")
 dhw_scenarios = open_dataset("../../ADRIA Domains/GBR_2024_10_15_HighResCoralStress/DHWs/dhwRCP45.nc")
-
+gbr_dom.loc_data.geometry = Vector{ArchGDAL.IGeometry}(gbr_dom.loc_data.geometry) # Need to recast gbr_dom geometry col for ADRIA.run_scenarios(). Possibly issue with GeoDataFrames version.
 # 1. Attach connectivity data to context_layers
 connectivity_matrix = gbr_dom.conn
 

### 2025-07-21 paper/paper_draft.qmd
Various grammar and content changes to improve flow

--- 2025-07-16 paper/paper_draft.qmd
@@
 regime shifts - depends on three interconnected mechanisms. First, the ability of individual
-corals to survival thermal stress. Second, the connectivity networks that enable
-recolonisation after disturbances. Third, the maintenance of carbonate framework that
-provides reef structure. We aim to assess how these mechanisms interact under current
-projected climate conditions to identify the characteristics of structurally resilient reefs through scenario-based coral population modelling for the Great Barrier Reef ecosystem.
+corals to survive thermal stress. Second, the connectivity networks that enable
+recolonisation after disturbances. Third, the maintenance of the carbonate framework that
+provides reef structure. We aim to assess how these mechanisms interact under projected
+climate conditions to identify the characteristics of structurally resilient reefs through
+scenario-based coral population modelling for the Great Barrier Reef ecosystem.
 
@@
 dispersal patterns mediated by hydrodynamic, spatial, and ecological processes
-[@grimaldi2022].
-The GBR faces severe projected coral cover declines under climate change [@bozec].
-These coral cover declines will be compounded by ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks
-[@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24
-Summer mass bleaching event may be signalling a shift towards this reef future, with some
-level of bleaching recorded on 79% of surveyed reefs [@cantin2024].
+[@grimaldi2022]. The GBR faces severe projected coral cover declines under climate change
+[@bozec2022]. These coral cover declines will be compounded by ocean acidification,
+intensifying tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012;
+@fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24 Summer mass
+bleaching event may be signalling a shift towards this reef future, with some level of
+bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs) [@cantin2024].
 
@@
 environmental and biological factors. Environmental factors can either amplify or reduce
-thermal stress exposure. Depth has been suggested as one crucial factor that can provide
-a refuge from thermal stress [@álvarez-noriega2018; @baird2018; @smith2014]. Biological
+thermal stress exposure. Depth has been suggested as one crucial factor that can provide a
+refuge from thermal stress [@álvarez-noriega2018; @baird2018; @smith2014]. Biological
 factors including coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005],
@@
 influence survival outcomes. Importantly, corals demonstrate adaptive capacity to develop
-thermal tolerance that could delay widespread bleaching under moderate emissions scenarios
+thermal tolerance that could delay widespread bleaching under moderate emission scenarios
 [@bairos-novak2021; @humanes2022], representing a crucial mechanism for reef persistence.
@@
 between carbonate accumulation [@perry2015] and loss through bioerosion, physical damage
-[@kenyon], and dissolution [@eyre2014; @eyre2018]. This balance is influenced by coral cover
-and complexity [@perry2012; @desbiens], environmental processes, and ocean chemistry
-[@perry2015; @eyre2018]. For Great Barrier Reef mid and outer shelf reefs, maintaining
-positive carbonate budgets requires approximately 17% live coral cover [@desbiens].
+[@kenyon2023], and dissolution [@eyre2014; @eyre2018]. This balance is influenced by coral
+cover and community complexity [@perry2012; @desbiens2021], environmental processes, and
+ocean chemistry [@perry2015; @eyre2018]. For Great Barrier Reef mid and outer shelf reefs,
+maintaining positive carbonate budgets requires approximately 17% live coral cover
+[@desbiens2021].
 
@@
 [@hock2017], and remains an important consideration, our integrated modelling reveals depth
-may play a fundamental role in determining maintenance of reef coral population and positive
-carbonate budgets under current projections of climate change.
+may play a fundamental role in determining maintenance of reef coral populations and
+positive carbonate budgets under current projections of climate change.
 
@@
 
-The spatial extent of the GBR coral reefs represented in this investigation follows the reef
-definitions available via the Great Barrier Reef Marine Park Authority
-\[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94\].
-In total this covers 3806 reef areas across the GBR marine park. Annually and spatially
-averaged Degree Heating Week (DHW) data were used to represent future thermal stress at each
-reef location.
-
-Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great
-Barrier Reef were obtained from the HighResCoralStress database [@dixon2022; @dixon].
-Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
-[@liu2017; @skirving2020]. DHWs were represented by a selection of five Global Climate
-Models (GCMs) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6;
-**citation**). These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and
-GDFL-CM4, and their inclusion were based on evaluation by Grose et al. [-@grose2023]. Grose
-et al. [-@grose2023] found high correlation between observed temperature, rainfall, El Niño
-Southern Oscillation and Indian Ocean Dipole patterns in the Australian terrestrial region,
-and the corresponding mechanisms in these GCMs.
-<!-- @Ben, the last sentence above is quite long and doesn't explain why the five GCMs
-were selected. -->
+The spatial extent of the GBR reefs represented in this investigation follows the reef
+definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. In
+total this covers 3806 reef areas across the GBR marine park. Reefs that are outside the
+GBRMPA management areas or are not associated with a GBRMPA reefal bioregion were removed
+from the investigation, leaving 3531 reefs. Annually and spatially averaged Degree Heating
+Week (DHW) data were used to represent future thermal stress at each reef location.
+
+Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the GBR were
+obtained from the HighResCoralStress database [@dixon2022; @dixon2023]. Maximum monthly mean
+DHW levels were calculated from the SST data following NOAA methodology [@liu2017;
+@skirving2020]. DHWs were represented by a selection of five Global Climate Models (GCMs)
+from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6; **citation**).
+These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4, and
+their inclusion were based on evaluation by Grose et al. [-@grose2023]. Grose et al.
+[-@grose2023] found these GCMs to rank highly, among 50 GCMs, in recreation of historical atmospheric temperature and precipitation conditions in the Australasian region.
+While this assessment does not consider oceanic data, Grose et al.
+[@-grose2023] provide a region-specific selection mechanism which we use as an indicator of general performance of GCMs for the region.
 
@@
 range, and GCM development families, allowing for a range of possible climate futures to be
-explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs;
+explored, capturing the uncertainty in future responses to CO2 increases (@sfig-ecs;
 [@grose2023; @shepherd2018]). The following analyses were performed using each GCM
@@
 
-![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
-The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
-the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
-2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#fig-ecs
-width="`{julia} ecs_width`" height="500" align="center"}
-
 ## Coral reef ecosystem model - ADRIA-CoralBlox
 
-CoralBlox is a coral population growth and mortality model that simulates groups of corals
-growing in diameter and competing for limited space over time [@ribeirodealmeida2024].
-Details on how coral demographic processes are implemented in ADRIA - CoralBlox can be found
-in the supplementary material \[**link ADRIA - CoralBlox**\].
+ADRIA.jl is a decision support platform that combines scenario analysis with biotic and
+abiotic processes such as bleaching responses, thermal tolerance and flows of larvae between
+reefs [@iwanaga2023]. CoralBlox.jl is a coral population growth and mortality model that
+simulates groups of corals growing in diameter and competing for limited space over time
+[@ribeirodealmeida2024]. We combine these tools to model the populations of corals across
+the GBR. Details on how coral demographic processes are implemented in ADRIA - CoralBlox can
+be found in the supplementary material.
 
@@
 truncated normal distribution that is updated in each timestep following growth and
-recruitment. This distribution determines that proportion of the population on a reef that
-is susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
+recruitment. This distribution determines the proportion of the population on a reef that is
+susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
 Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
@@
 depth of each reef location, following Baird et al. [@baird2018], reducing the proportion of
-coral colonies on a reef impacted by high heat stress as depth increases. Median depths for
-each reef location were extracted from satellite derived bathymetry data for the Great
-Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due to varying
-degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs
-with less than 5% coverage of valid bathymetry data were removed from this investigation.
-Furthermore, reefs that were outside the GBRMPA management areas or not associated with a
-bioregion were removed from the investigation.
+coral colonies on a reef impacted by high heat stress as depth increases.
 
@@
 
-\*\* Describe process of estimating median depth for each reef \*\*
+Median depths for each reef location were extracted from satellite derived bathymetry data
+for the Great Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due
+to varying degrees of alignment between bathymetry data and the defined outlines for GBR
+reefs, reefs with less than 5% coverage of valid bathymetry data were removed from analyses
+involving depth as a resilience factor.
 
@@
 
-ADRIA-CoralBlox was run for 4096 **sampled** scenarios for each of the five GCMs.
-A median absolute coral cover timeseries for each reef was calculated for each GCM.
-For timeseries clustering reef cover timeseries were scaled by the total area of the reef
-to represent timeseries as a percentage of the total reef area. The proportion of each
+ADRIA-CoralBlox was run for 4096 **sampled** scenarios for each of the five GCMs (20,480
+total model runs). A median absolute coral cover timeseries for each reef was calculated for
+each GCM. For timeseries clustering reef cover timeseries were scaled by the total area of
+the reef to represent cover as a percentage of the total reef area. The proportion of each
 functional group occupying the reef (group evenness) was also investigated as a metric for
-timeseries analysis, but was found to not sufficiently capture the declined condition of reefs
-suffering from very low absolute coral cover.
+timeseries analysis, but was found to not sufficiently capture the declined condition of
+reefs suffering from very low absolute coral cover.
 
@@
 Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
-[@desbiens]. Given in situ carbonate budgets are influenced by (1) a range of processes; (2)
-the variety of approaches that could be used to measure those processes; and (3) the
+[@desbiens2021]. Given in situ carbonate budgets are influenced by (1) a range of processes;
+(2) the variety of approaches that could be used to measure those processes; and (3) the
 uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
@@
 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
-[-@perry2015] and Desbians et al., [-@desbiens] providing plausible indications of the lower
-and upper bounds respectively. Robustness of the conclusions drawn to the uncertainty in the
-precise value of $\beta_{0}$ for all reefs can then be assessed by using the indicative
-range.
+[-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of the
+lower and upper bounds respectively. Robustness of the conclusions drawn to the uncertainty
+in the precise value of $\beta_{0}$ for all reefs can then be assessed by using the
+indicative range.
 
@@
 
-The distribution of number of years above carbonate-cover thresholds is right-skewed, with
-many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth
-levels and natural log total connectivity strength levels follow right-skewed distributions.
-Therefore, we analyse the correlation between number of years above carbonate-cover
-thresholds and these characteristics using Spearman's correlation coefficient.
-
 ### Timeseries clustering
@@
 To identify groups of reefs that are resilient, intermediate, and non-resilient, we
-clustered reefs by their temporal behaviour as indicated by their coral cover over time. The
-Complexity-Invariant Distance (CID) between each timeseries was calculated to identify
-timeseries that behave similarly [@batista2014]. The CID corrects the Euclidean distance
-between pairs of timeseries (which accounts for magnitude differences) with the complexity
-of each timeseries (obtained through a measure of their variability) to ensure reefs are
-clustered based on their underlying temporal dynamics rather than simply their average coral
-cover. The process creates a distance matrix of n \* n dimensions (where n is the number of
-timeseries in the group) that is clustered using a k-medoids clustering algorithm [cf.
-@steinmann2020].
+clustered reefs into three clusters based on their temporal behaviour as indicated by coral
+cover over time. The Complexity-Invariant Distance (CID) between each timeseries was
+calculated to identify timeseries that behave similarly [@batista2014]. The CID corrects the
+Euclidean distance between pairs of timeseries (which accounts for magnitude differences)
+with the complexity of each timeseries (obtained through a measure of their variability) to
+ensure reefs are clustered based on their underlying temporal dynamics rather than simply
+their average coral cover. The process creates a distance matrix of n \* n dimensions (where
+n is the number of timeseries in the group) that is clustered using a k-medoids clustering
+algorithm [cf. @steinmann2020].
 
@@
 
-As one might expect, the number of years above $\beta_{0}$ (the assumed positive carbonate
-budget threshold) substantially decreases as $\beta_{0}$ increases.
+As one might expect, the number of years experience cover above $\beta_{0}$ (the assumed
+positive carbonate budget threshold) substantially decreases as $\beta_{0}$ increases. The
+distribution of number of years above carbonate-cover thresholds is right-skewed, with many
+reefs experiencing low numbers of years above thresholds.
 
@@
 [@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintainence correlation
-decreases as the required carbonate budget threshold increases. This is likely due to an
-increasing number of reefs being unable to maintain coral cover above threshold levels as
-the threshold increases, with values becoming increasingly right-skewed. The natural log of
-total connectivity strength was found to have no correlation with the number of years a reef
-maintains cover above the required thresholds [@sfig-access-esm1-5-conn-carbonate]. Log
-connectivity strength - carbonate budget maintainence correlation slightly decreases as the
-required carbonate budget threshold increases.
+decreases as $\beta_{0}$ increases. This is likely due to an increasing number of reefs
+being unable to maintain coral cover above threshold levels as the threshold increases, with
+values becoming increasingly right-skewed. The natural log of total connectivity strength
+was found to have no correlation with the number of years a reef maintains cover above the
+required thresholds [@sfig-access-esm1-5-conn-carbonate]. Log connectivity strength -
+carbonate budget maintainence correlation slightly decreases as the required carbonate
+budget threshold increases.
 
@@
 
-Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’
-coral cover and contextual analysis factors, thus further comparisons of these clusters for
-each analysis factor are only shown for ACCESS-ESM1-5 (intermediate ECS scenario). Results
-for the additional GCMs are displayed in the supplementary material. However, there are
-substantial differences in the longevity of reef resilience and maintenance of coral cover
-post 2030 between the GCMs, thus coral cover timeseries are displayed for each GCM
-(displayed clustered at management-area scale to preserve coarse spatial differences in
-coral trajectories) (@fig-gcm-cover-trajectories).
+Each GCM shows similar relationships between reef clusters and contextual analysis factors,
+thus further comparisons of these clusters for each analysis factor are only shown for
+ACCESS-ESM1-5 (intermediate ECS scenario). Results for the additional GCMs are displayed in
+the supplementary material. However, there are substantial differences in the longevity of
+reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover
+timeseries are displayed for each GCM (displayed clustered at management-area scale to
+preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
 
@@
 cluster, and to a lesser degree the ‘low’ cluster, also exhibit periods of recovery and
-increasing proportions of coral cover up to 2045. Under NorESM2-MM GCM the Far Northern
+increasing proportions of coral cover up to 2045. Under NorESM2-MM the Far Northern
 management area does not see coral cover maintenance as high as the three remaining
@@
 Under each GCM, in all management areas, low, medium and high cluster reefs have low
-differences between DHW trajectories (@sfig-gcm-dhw-trajectories). The highest peak DHW
+differences between DHW trajectories (@fig-gcm-dhw-trajectories). The highest peak DHW
 levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHW
@@
 
-Across the five GCMs, 50% (1812) of reefs, at management region scale, remain in the same
+![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
+analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
+between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
+represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
+represented five times (for each GCM), with each GCM displayed
+horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
+width="`{julia} timeseries_width`"}
+
+```{=html}
+<!-- Across the five GCMs, 50% (1812) of reefs, at management region scale, remain in the same
 ‘low, medium, high’ cluster assignment. 1757 Reefs (49%) that changed clusters by one level
@@
 (1%) reefs changed clusters by two levels across the GCMs (e.g. a reef is assigned ‘low’ and
-‘high’ in different GCMs).
+‘high’ in different GCMs). -->
+```
 
@@
 
-Within bioregions timeseries clustering analysis was able to identify three clusters of
-area-relative cover timeseries. Across many bioregions timeseries clustering identified a
-‘low’ cluster containing reefs that suffer larger declines and generally have lower levels
-of coral cover than the other clusters, a ‘medium’ cluster with intermediate levels of coral
-cover, and a ‘high’ cluster with greater levels of cover recovery, with persistence to 2050
-in some bioregions (@sfig-access-esm1-5-bioregion-timeseries;
-@sfig-access-cm2-bioregion-timeseries; @sfig-ec-earth3-veg-bioregion-timeseries;
-@sfig-gfdl-cm4-bioregion-timeseries; @sfig-noresm2-mm-bioregion-timeseries).
+Across many bioregions timeseries clustering identified a ‘low’ cluster containing reefs
+that suffer larger declines and generally have lower levels of coral cover than the other
+clusters, a ‘medium’ cluster with intermediate levels of coral cover, and a ‘high’ cluster
+with greater levels of cover recovery, with persistence to 2050 in some bioregions
+(@sfig-access-esm1-5-bioregion-timeseries; @sfig-access-cm2-bioregion-timeseries;
+@sfig-ec-earth3-veg-bioregion-timeseries; @sfig-gfdl-cm4-bioregion-timeseries;
+@sfig-noresm2-mm-bioregion-timeseries).
 
@@
 @sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean;
-@sfig-noresm2-mm-bioregion-dhwmean). <!--
-In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially lower mean thermal tolerance levels compared to reefs in other clusters.
-However, many bioregions do not show strong differences in thermal tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol; @sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol; @sfig-noresm2-mm-bioregion-dhwtol).
--->
+@sfig-noresm2-mm-bioregion-dhwmean).
+
+<!-- In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially 
+lower mean thermal tolerance levels compared to reefs in other clusters. However, many 
+bioregions do not show strong differences in thermal tolerance levels 
+(@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol; 
+@sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol; 
+@sfig-noresm2-mm-bioregion-dhwtol). -->
 
@@
 a higher ECS value than GFDL-CM4, with reefs experiencing large continuous declines under
-GFDL-CM4.
+GFDL-CM4. These large declines are likely due to the high peak thermal stress levels above
+10°C-weeks experienced in the first ten years of the timeseries under GFDL-CM4.
+
+The large differences in cover timeseries seen across the GCMs suggest that it is important
+to consider this uncertainty in future conditions when assessing possible biological
+responses to change. This is supported by recent literature suggesting an effective approach
+to capturing climate change uncertainty is to model climate change responses using a range
+of climate models separately [@shepherd2018]. Despite large differences in coral cover
+across GCMs, the patterns identified between low, medium and high clusters of reefs suggest
+that the importance of depth refugia is consistent across scenarios.
 
@@
 and exhibit overall similar DHW timeseries. While these reefs experience similar magnitude
-DHWs based on SST, the proportion of the reef’s coral population impacted by heat stress
-events depends on the depth of the reef. Analysis from Baird et al. [-@baird2018] is used to
-calculate the degree of protection provided to a reef based on the median depth. Our results
-suggest that within shallow reef ecosystems (depth \< 30m), depth contributes greatly to
-reef resilience and the ability of the reef to maintain positive carbonate budgets under
-future conditions. While similar findings have been demonstrated in the eastern Pacific
-[@smith2014], depth refugia analyses have often focussed on the potential of mesophotic
-reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In
-contrast, Venegas et al. [-@venegas2019] found no association between depth and the
-alleviation of heat stress across a range of shallow reefs in the Pacific. Reefs at shallow
-depths experience no, or few, years with coral cover exceeding levels likely required to
-maintain positive carbonate budgets. Movement of reefs towards negative cabonate budgets
-under increasing future thermal stress over time may contribute to phase shifts in reef
-dominant $CaCO_3$ production from coral driven to coralline encrusting algae driven
-production, or to bioerosion dominated systems with rapid erosion of physical reef
-frameworks [@dudgeon2010; @perry2008].
+DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress
+events depends on reef depth. Our results suggest that within shallow-water reef ecosystems
+(non-mesophotic, depth \< 30m), depth contributes greatly to reef resilience and the ability
+of the reef to maintain positive carbonate budgets under future conditions. While similar
+findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses
+have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia
+[@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al. [-@venegas2019]
+found no association between depth and the alleviation of heat stress across a range of
+shallow reefs in the Pacific. Reefs at shallow depths experience no, or few, years with
+coral cover exceeding levels likely required to maintain positive carbonate budgets.
+Movement of shallow reefs towards negative cabonate budgets under increasing future thermal
+stress over time may contribute to phase shifts in reef dominant CaCO~3~ production.
+Shifting from coral driven to coralline encrusting algae driven production, or to bioerosion
+dominated systems with rapid erosion of physical reef frameworks [@dudgeon2010; @perry2008].
+While reefs at increased depths may be able to maintain coral driven CaCO~3~ production and
+accumulation into the future for longer.
 <!-- The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels.
@@
 refugia benefits and more prolonged resilience under climate change compared to shallower
-reefs. Additionally, [-@liu2024] suggest that rubble instability is inversely correlated
-with reef depth, possibly limiting the larval recruitment capacity of shallow reefs. A
-caveat to these findings is the quality of the bathymetry data used to calculate depth
-refugia benefits in ADRIA. This data (GBRMPA [-@gbr10gb2020]) is derived from satellite
-imagery and is limited in its alignment with the established GBRMPA reef outlines used in
-the investigation to characterise reef locations. As a result, 842 reefs (22% of the 3806)
-were removed from the analyses before depth comparisons due to having less than 5% coverage
-of depth data. Additionally, deriving estimates of depth from satellite imagery is prone to
-high degrees of uncertainty. Data adopted for the given assessment are said to be accurate
-up to 15m from Mean Sea Level [@gbr10gb2020]. Furthermore, an estimated median depth is
-determined for each reef, using the established GBRMPA reef outlines to provide an
-indication of “true” reef extent. Therefore, the estimates of reef depths are taken as a
-useful indication rather than an accurate and precise report of reef depths across the GBR.
-
-Current reef restoration and intervention-investigation efforts on the Great Barrier Reef,
-such as deployment of coral seeding and fragment devices target reefs with suitable
-restoration sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. One
-of the main depth constraints is being able to visually identify the target site from the
-surface for deployment and ongoing monitoring, in combination with factors such as
-deployment method and tourism return value. Our results suggest that of the reefs analysed
-within the 1-10m depth range (1800 reefs) 74% (1328) of reefs fall into the low and medium
-clusters (across all GCMs at the GBRMPA management region scale), with many unable to
-maintain positive carbonate budgets under future conditions. Reef intervention planning is a
-complex and challenging decision making process [@anthony2020], and our results suggest that
-deployment site depth is an important factor to consider when assessing the long-term
-resilience of reef sites.
+reefs. Additionally, [@liu2024] suggest that rubble instability is inversely correlated with
+reef depth, possibly limiting the juvenile recruitment capacity of shallow reefs. A caveat
+to these findings is the quality of the bathymetry data used to calculate median reef depth.
+This data (GBRMPA [-@gbr10gb2020]) is derived from satellite imagery and is limited in its
+alignment with the established GBRMPA reef outlines used in the investigation to
+characterise reef locations. As a result, 842 reefs (22% of 3806 reefs) were removed from
+the analyses before depth comparisons due to having less than 5% coverage of depth data.
+Additionally, deriving estimates of depth from satellite imagery is prone to high degrees of
+uncertainty. Data adopted for the given assessment are said to be accurate up to 15m from
+Mean Sea Level [@gbr10gb2020]. Furthermore, an estimated median depth is determined for each
+reef, using the established GBRMPA reef outlines to provide an indication of “true” reef
+extent. Therefore, the estimates of reef depths are taken as a useful indication rather than
+an accurate and precise report of reef depths across the GBR.
+
+Current reef restoration and intervention-investigation efforts on the GBR, such as
+deployment of coral seeding and fragment devices, target reefs with suitable restoration
+sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. One of the main
+constraints on deployment depth is visual identification of target sites from the surface
+for deployment and ongoing monitoring, in combination with factors such as deployment method
+and tourism return value. Our results suggest that of the reefs analysed within the 1-10m
+depth range (1800 reefs), 74% (1328) of reefs fall into the low and medium clusters (across
+all GCMs at the GBRMPA management region scale), with many unable to maintain positive
+carbonate budgets under future conditions. Reef intervention planning is a complex and
+challenging decision making process [@anthony2020], and our results suggest that deployment
+site depth is an important factor to consider when assessing the long-term resilience of
+deployment sites.
 
@@
 
-It is a strongly held conclusion in coral reef ecology that a primary facet of reef resilience 
-is the degree of larval connectivity between reefs and the supply of recruits that a 
-reef receives following disturbance [@hock2017] **expand citations**. It was expected that resilient reefs would
-have greater incoming than outgoing larval connectivity to promote recovery in years 
-following thermal stress, while non-resilient reefs would have greater outgoing than 
-incoming connectivity inhibiting recruitment of corals ability post thermal stress. In 
-contrast, our results suggest that there are few differences between resilient and 
-non-resilient reefs in connectivity metrics such as the ratio of outgoing to incoming larval 
-connectivity and total connectivity strength. Hock et al. [-@hock2017] used larval 
-connectivity modelling to identify resilient reefs that may supply up to 47% of the wider 
-Great Barrier Reef ecosystem with larvae following disturbance. A critique of this 
-approach [@bode2018] is that results obtained are highly sensitive to the biophysical 
-dispersal model used, limiting the application of specific identified reefs. Reef depth was
-not considered in these investigations of reef network resilience. These investigations 
-were performed using prior generations of larval connectivity models parameterised for 
-2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods respectively. Using updated 
-1km resolution larval connectivity across the whole GBR, with a limited temporal sample of
-particle flows, our results suggest that larval connectivity alone is not as important for
-reef resilience and recovery as environmental refugia from thermal stress such as depth. 
-Our findings may differ due to the highly uncertain nature of connectivity methods used 
-**citation**, the way larval flows and juvenile recruitment are implemented in ADRIA - 
-CoralBlox, and the magnitude of early bleaching events decreasing the breeding capacity 
-of strongly connected reefs. Further improvements in connectivity modelling are necessary 
-to provide a robust comparison of the factors influencing reef resilience.
-
-Five different GCMs were included in analyses to capture uncertainty in climate system
-responses to increasing atmospheric carbon dioxide levels. The large differences in cover
-timeseries seen across the GCMs suggest that it is important to consider this uncertainty in
-analyses of biological climate change responses. This is supported by recent literature
-suggesting an effective approach to capturing climate change uncertainty is to model climate
-change responses using a range of climate models separately [@shepherd2018]. However, the
-patterns identified between low, medium and high clusters of reefs suggest that the
-importance of depth refugia is consistent across scenarios. Similarly, at the management
-area scale, only 1% of reefs were assigned a ‘low’ and ‘high’ cluster in different GCMs,
-suggesting that intrinsic reef properties can prevent high cover resilient reefs from
-crashing under a different future climate scenario.
+It is a strongly held conclusion in coral reef ecology that a primary facet of reef
+resilience is the degree of larval connectivity between reefs and the supply of recruits
+that a reef receives following disturbance [@hock2017] **expand citations**. It was expected
+that resilient reefs would have greater incoming than outgoing larval connectivity to
+promote recovery in years following thermal stress, while non-resilient reefs would have
+greater outgoing than incoming connectivity inhibiting recruitment of corals post thermal
+stress. In contrast, our results suggest that there are few differences between resilient
+and non-resilient reefs in connectivity metrics such as the ratio of outgoing to incoming
+larval connectivity and total connectivity strength. Furthermore, our results suggest no
+relationship between connectivity and the ability of reefs to maintain positive carbonate
+budgets under future conditions. There has been contrasting evidence [@bode2018; @hock2017]
+surrounding whether recent generation connectivity modelling is able to identify reefs that
+are important for recovery processes. A key separation of these investigations is their use
+of differing larval connectivity models. Reef depth was not considered in these
+investigations of reef network resilience. These investigations were performed using prior
+generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and
+1996-2002 [@bode2018] time periods. Using updated 1km resolution larval connectivity across
+the whole GBR, with a limited temporal sample of particle flows, our results suggest that
+larval connectivity alone is not as important for reef resilience and recovery as
+environmental refugia from thermal stress such as depth. Our findings may differ due to the
+highly uncertain nature of connectivity methods used **citation**, the way larval flows and
+juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early
+bleaching events decreasing the breeding capacity of strongly connected reefs. Further
+improvements and research in connectivity modelling are necessary to provide a robust
+comparison of all factors influencing reef resilience.
 
@@
 these diameters over timesteps through growth. Due to the availability of quality future
-projected data we do not consider the impacts of waves, cyclones and currents on coral
-colony survival and bleaching (insert citations for waves affecting survival and bleaching).
-We do not consider the impacts of Crown of Thorns Starfish (CoTS) on coral survival and reef
-resilience (insert citation for cots affecting corals). Furthermore, there are multiple
-caveats to acknowledge in the data sources used in this investigation. Uncertainty in
-connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress
-projections are likely to influence the results obtained in this investigation. To limit the
-influence of bathymetry data on results, reefs with less than 5% data coverage are removed
-from analyses. The DHW data used in this investigation have not been bias corrected for the
-Great Barrier Reef region and is part of a wider Australian dataset [@dixon2022] developed
-using statistical downscaling. We investigate a range of future climate responses and
-thermal projections to account for a range of possible futures, and our results suggest
-the factors that influence reef resilience are consistent across these scenarios.
+projected data we do not consider the impacts of waves, cyclones, currents and Crown of
+Thorns Starfish (CoTS) on coral colony survival and bleaching (**insert citations for waves
+affecting survival and bleaching**). Uncertainty in connectivity modelling outputs,
+satellite-derived bathymetry data and future thermal stress projections are likely to
+influence the results obtained in this investigation. Incorporating further improvements in
+connectivity modelling and understanding of the influence of climate change on reef
+connectivity would improve the comparison of connectivity as an important factor for reef
+resilience. The DHW data used in this investigation have not been bias corrected for the
+Great Barrier Reef region and are part of a wider Australian dataset [@dixon2022] developed
+using statistical downscaling. We investigate a range of future climate responses, thermal
+projections and ecological parameterisations of ADRIA - CoralBlox to account for many
+possible futures, and our results suggest the factors that influence reef resilience are
+consistent across these scenarios.
 
@@
 the purpose of this investigation is to assess the relative influence of reef
-characteristics on future resilience and highlight possible outcomes under highly uncertain
-future scenarios, rather than provide spatially explicit predictions of future resilience.
+characteristics on future resilience and highlight possible outcomes under uncertain future
+scenarios. We do not aim to provide spatially explicit predictions of future resilience.
 
 Further analyses could build on the findings of this study by analysing the impacts of
-prioritising reef depth in reef restoration intervention decision making. The ADRIA platform
-is developed as a modelling tool to incorporate multi-criteria decision analysis (MCDA) and
-ecosystem scenario modelling into reef restoration decision analysis. The platform allows
-for the investigation of different reef characteristics to be targetted in decision making
-and models the evolving outcomes as a result of reef interventions at various locations. The
+prioritising reef depth in restoration intervention decision making. The ADRIA platform is
+developed as a modelling tool to incorporate multi-criteria decision analysis (MCDA) and
+ecosystem scenario modelling into reef restoration decision support. The platform allows for
+the investigation of different reef characteristics to be targetted in decision making and
+models the evolving outcomes as a result of reef interventions at various locations. The
 capability of ADRIA-CoralBlox could be further expanded by incorporating the impacts of
@@
 
+![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
+The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
+the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
+2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
+width="`{julia} ecs_width`" height="500" align="center"}
+
 ## ADRIA - CoralBlox
@@
 
-![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
-analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
-represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
-represented five times (for each GCM), with each GCM displayed
-horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
-width="`{julia} timeseries_width`"}
-
 ## ACCESS-ESM1-5
@@
 
+```{=html}
 <!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
@@
 violin_width\`"} -->
+```
 

### 2025-07-22 paper/paper_draft.qmd
Reinstate DHW-tolerance content into paper and ensure figs match results

@@
 their inclusion were based on evaluation by Grose et al. [-@grose2023]. Grose et al.
-[-@grose2023] found these GCMs to rank highly, among 50 GCMs, in recreation of historical atmospheric temperature and precipitation conditions in the Australasian region.
-While this assessment does not consider oceanic data, Grose et al.
-[@-grose2023] provide a region-specific selection mechanism which we use as an indicator of general performance of GCMs for the region.
+[-@grose2023] found these GCMs to rank highly, among 50 GCMs, in recreation of historical
+atmospheric temperature and precipitation conditions in the Australasian region. While this
+assessment does not consider oceanic data, Grose et al. \[\@-grose2023\] provide a
+region-specific selection mechanism which we use as an indicator of general performance of
+GCMs for the region.
 
@@
 
-```{=html}
-<!-- Across the five GCMs, 50% (1812) of reefs, at management region scale, remain in the same
-‘low, medium, high’ cluster assignment. 1757 Reefs (49%) that changed clusters by one level
-across the GCMs (e.g. a reef is assigned ‘low’ and ‘medium’ in different GCMs), while 46
-(1%) reefs changed clusters by two levels across the GCMs (e.g. a reef is assigned ‘low’ and
-‘high’ in different GCMs). -->
-```
+Comparing across GCMs, it is common for reefs to switch cluster level, including from low to
+high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). This is
+expected as spatial differences in GCM DHW timeseries result in reefs being impacted in
+different magnitudes relative to other reefs in their bioregion.
 
@@
 
-Correlation between reef total coral cover and reef DHW timeseries decreases as cluster
-coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total
-cover – DHW timeseries correlation levels (@sfig-access-esm1-5-bioregion-dhwcor;
-@sfig-access-cm2-bioregion-dhwcor; @sfig-ec-earth3-veg-bioregion-dhwcor;
-@sfig-gfdl-cm4-bioregion-dhwcor; @sfig-noresm2-mm-bioregion-dhwcor).
+In many bioregions reefs in the 'low' cover cluster have the lowest cover - DHW timeseries
+correlation levels, while reefs in 'high' clusters have the highest correlation levels
+(@sfig-access-esm1-5-bioregion-dhwcor; @sfig-access-cm2-bioregion-dhwcor;
+@sfig-ec-earth3-veg-bioregion-dhwcor; @sfig-gfdl-cm4-bioregion-dhwcor;
+@sfig-noresm2-mm-bioregion-dhwcor).
 
@@
 
-<!-- In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially 
-lower mean thermal tolerance levels compared to reefs in other clusters. However, many 
-bioregions do not show strong differences in thermal tolerance levels 
-(@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol; 
+Similarly, there are no substantial differences between reef clusters in mean thermal
+tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol;
 @sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol;
-@sfig-noresm2-mm-bioregion-dhwtol). -->
-
-In many bioregions reefs with high area-relative coral cover levels (‘high’ cluster) have
-the lowest initial proportions of habitable area occupied by corals, while reefs in the
-‘low’ cluster often have the highest initial proportions of coral habitable area occupied by
-corals (@sfig-access-esm1-5-bioregion-initialproportion;
+@sfig-noresm2-mm-bioregion-dhwtol).
+
+There are no consistent differences across bioregions and GCMs between clusters in their
+reefs' initial proportion of habitable area occupied by corals
+(@sfig-access-esm1-5-bioregion-initialproportion;
 @sfig-access-cm2-bioregion-initialproportion;
@@
 accumulation into the future for longer.
-<!-- The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels.
-Reefs in low and medium clusters have lower levels of cover – DHW correlation than those in high clusters, due to their initial sharp declines in coral cover combined with low depth – refugia in the face of persistently high thermal stress these reefs do not recover post 2030, leaving little ability to decline further in periods of high thermal stress and recover in periods of low thermal stress.
--->
 
@@
 Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater
-thermal tolerance than reefs in lower coral cover clusters **need to replot tolerance
-values**. This is in contrast with literature suggesting corals have the capacity to adapt
-to increasing climate change pressures [@humanes2022; @lachs2024], including the
-investigation by Bairos-Novak et al. [-@bairos-novak2021] that revealed high heritability of
-bleaching and survival response traits used to inform the distributions of thermal tolerance
-traits used in this investigation. The lack of influence of thermal tolerance on reef
-outcomes is likely due to reef being impacted by overall similar levels of thermal stress,
-combined with the greater importance of factors such as reef depth.
-
-It is a strongly held conclusion in coral reef ecology that a primary facet of reef
-resilience is the degree of larval connectivity between reefs and the supply of recruits
-that a reef receives following disturbance [@hock2017] **expand citations**. It was expected
-that resilient reefs would have greater incoming than outgoing larval connectivity to
-promote recovery in years following thermal stress, while non-resilient reefs would have
-greater outgoing than incoming connectivity inhibiting recruitment of corals post thermal
-stress. In contrast, our results suggest that there are few differences between resilient
-and non-resilient reefs in connectivity metrics such as the ratio of outgoing to incoming
-larval connectivity and total connectivity strength. Furthermore, our results suggest no
-relationship between connectivity and the ability of reefs to maintain positive carbonate
-budgets under future conditions. There has been contrasting evidence [@bode2018; @hock2017]
-surrounding whether recent generation connectivity modelling is able to identify reefs that
-are important for recovery processes. A key separation of these investigations is their use
-of differing larval connectivity models. Reef depth was not considered in these
-investigations of reef network resilience. These investigations were performed using prior
-generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and
-1996-2002 [@bode2018] time periods. Using updated 1km resolution larval connectivity across
-the whole GBR, with a limited temporal sample of particle flows, our results suggest that
-larval connectivity alone is not as important for reef resilience and recovery as
-environmental refugia from thermal stress such as depth. Our findings may differ due to the
-highly uncertain nature of connectivity methods used **citation**, the way larval flows and
-juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early
-bleaching events decreasing the breeding capacity of strongly connected reefs. Further
-improvements and research in connectivity modelling are necessary to provide a robust
-comparison of all factors influencing reef resilience.
+thermal tolerance than reefs in lower coral cover clusters. This is in contrast with
+literature suggesting corals have the capacity to adapt to increasing climate change
+pressures [@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
+[-@bairos-novak2021] that revealed high heritability of bleaching and survival response
+traits, used to inform the distributions of thermal tolerance traits used in this
+investigation. The lack of influence of thermal tolerance on reef outcomes is likely due to
+reefs being impacted by high levels of thermal stress early in timeseries and being unable
+to build thermal tolerance to DHW levels greater than 9°C.
+
+It is a common conclusion in coral reef ecology that a primary facet of reef resilience is
+the degree of larval connectivity between reefs and the supply of recruits that a reef
+receives following disturbance [@hock2017] **expand citations**. In contrast, our results
+suggest that there are few differences between resilient and non-resilient reefs in
+connectivity metrics such as the ratio of outgoing to incoming larval connectivity and total
+connectivity strength. Furthermore, our results suggest no relationship between connectivity
+and the ability of reefs to maintain positive carbonate budgets under future conditions.
+There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent
+generation connectivity modelling is able to identify reefs that are important for recovery
+processes. A key separation of these investigations is their use of differing larval
+connectivity models. Reef depth was not considered in these investigations of reef network
+resilience. These investigations were performed using prior generations of larval
+connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time
+periods. Using updated 1km resolution larval connectivity across the whole GBR, with a
+limited temporal sample of particle flows, our results suggest that larval connectivity
+alone is not as important for reef resilience and recovery as environmental refugia from
+thermal stress such as depth. Our findings may differ due to the highly uncertain nature of
+connectivity methods used **citation**, the way larval flows and juvenile recruitment are
+implemented in ADRIA - CoralBlox, and the magnitude of early bleaching events decreasing the
+breeding capacity of strongly connected reefs. Further improvements and research in
+connectivity modelling are necessary to provide a robust comparison of all factors
+influencing reef resilience.
 
@@
 in larval connectivity networks is an important consideration for reef restoration efforts
-[@anthony2020; @hock2017], our results suggest that resilient reefs do not have greater
-incoming or total connectivity to contribute to their resilience under modelled projected
-conditions. Instead, we suggest that depth, and likely other environmental thermal refugia
-mechanisms contribute greater to overall reef resilience and recovery. We suggest further
-analyses that investigate the benefits of incorporating depth-based resilience into reef
-decision making.
+[@anthony2020; @hock2017], our results suggest that current connectivity modelling methods
+are not able to generate connectivity levels that contribute to reef resilience under
+projected conditions. We suggest further analyses that investigate the benefits of
+incorporating depth-based resilience into reef decision making, as well as further research
+and development in connectivity modelling methods for whole-ecosystem scales.
 
@@
 2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
-width="`{julia} ecs_width`" height="500" align="center"}
+width="`{julia} ecs_width`" align="center"}
+
+![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
+Green indicates a low cover cluster assignemnt, orange represents a medium cover assignment
+and blue represents assignment of a reef to a high coral cover cluster. The vertical width
+of reef elements varies depending on the number of reefs within the bioregion (displayed in
+the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
+ACCESS-CM2, NorESM2-MM and
+GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignment.png){#fig-gcm-bioregion-cluster-assignment
+width="`{julia} timeseries_width`"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-width="`{julia"} violin_width\`"}
-
-```{=html}
-<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
+width="`{julia} violin_width`"}
+
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
 clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
 lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030
-and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest
-median area-relative cover between 2030 and 2040 within each bioregion. Solid lines
-represent the median DHW tolerance value for each cluster. Displays results for
-ACCESS-ESM1-5 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width="`{julia}
-violin_width\`"} -->
-```
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
+width="`{julia} violin_width`"}
 
@@
 
-<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for ACCESS-CM2 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`} -->
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW tolerance value for each cluster. Displays results for ACCESS-CM2
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol
+width="`{julia} violin_width`"}
 
@@
 
-<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for EC-Earth3-Veg GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`} -->
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW tolerance value for each cluster. Displays results for EC-Earth3-Veg
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol
+width="`{julia} violin_width`"}
 
@@
 
-<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for GFDL-CM4 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`} -->
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW tolerance value for each cluster. Displays results for GFDL-CM4
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol
+width="`{julia} violin_width`"}
 
@@
 
-<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion.
-Solid lines represent the median DHW tolerance value for each cluster.
-Displays results for NorESM2-MM GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`} -->
+![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
+clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
+lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
+2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
+median DHW tolerance value for each cluster. Displays results for NorESM2-MM
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol
+width="`{julia} violin_width`"}
 

### 2025-07-22 paper/paper_draft.qmd
Add section to discuss the shortcomings of connectivity implementation
And discuss possible improvements from Vogt-Vincent et al. 2023.

@@
 the degree of larval connectivity between reefs and the supply of recruits that a reef
-receives following disturbance [@hock2017] **expand citations**. In contrast, our results
-suggest that there are few differences between resilient and non-resilient reefs in
+receives following disturbance [@hock2017; @mumby2008; @torres2024]. In contrast, our
+results suggest that there are few differences between resilient and non-resilient reefs in
 connectivity metrics such as the ratio of outgoing to incoming larval connectivity and total
@@
 thermal stress such as depth. Our findings may differ due to the highly uncertain nature of
-connectivity methods used **citation**, the way larval flows and juvenile recruitment are
-implemented in ADRIA - CoralBlox, and the magnitude of early bleaching events decreasing the
-breeding capacity of strongly connected reefs. Further improvements and research in
-connectivity modelling are necessary to provide a robust comparison of all factors
-influencing reef resilience.
+larval connectivity modelling [@vogt-vincent2023], the way larval flows and juvenile
+recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early bleaching
+events decreasing the breeding capacity of strongly connected reefs. In our investigation
+connectivity is implemented as a time-mean measure of reef connectivity over all available
+days. Recent analysis of daily reef larval connectivity data suggests that time-mean
+connectivity may not be suitable for capturing the seasonal, ecological time scale,
+connectivity patterns between locations due to the high daily variability in connectivity
+data [@vogt-vincent2023]. This is supported by the connectivity data used in our
+investigation, which have large relative standard deviations for connectivity between reefs
+**figure**. By incorporating connectivity using methods that capture ecological-timescale
+patterns in reef-reef larval dispersal, such as cumulated implicit connectivity
+[@vogt-vincent2023], our investigation may find increased importance of both depth and reef
+connectivity for resilience, in line with [@hock2017; @torres2024]. Further improvements and
+research in connectivity modelling are necessary to provide a robust comparison of all
+factors influencing reef resilience.
 

### 2025-07-23 paper/paper_draft.qmd
Further information about connectivity methods and possible improvements

--- 2025-07-22 paper/paper_draft.qmd
@@
 
+Twenty-four total days of connectivity data were used in this investigation, 2015, 2016,
+2018 and 2019 are represented represented by 3 daily connectivity matrices each, while 2017
+and 2020 are represented with 5 daily matrices each. Connectivity levels are implemented in
+ADRIA - CoralBlox as mean over the 24 days for each location.
+
 ### Depth estimation
@@
 generation connectivity modelling is able to identify reefs that are important for recovery
-processes. A key separation of these investigations is their use of differing larval
-connectivity models. Reef depth was not considered in these investigations of reef network
-resilience. These investigations were performed using prior generations of larval
-connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time
-periods. Using updated 1km resolution larval connectivity across the whole GBR, with a
-limited temporal sample of particle flows, our results suggest that larval connectivity
-alone is not as important for reef resilience and recovery as environmental refugia from
-thermal stress such as depth. Our findings may differ due to the highly uncertain nature of
-connectivity methods used **citation**, the way larval flows and juvenile recruitment are
-implemented in ADRIA - CoralBlox, and the magnitude of early bleaching events decreasing the
-breeding capacity of strongly connected reefs. Further improvements and research in
+processes, with findings dependent on the larval connectivity model used. These
+investigations were performed using prior generations of larval connectivity models
+parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods. Using
+updated 1km resolution larval connectivity across the whole GBR, with a limited temporal
+sample of particle flows, our results suggest that larval connectivity alone is not as
+important for reef resilience and recovery as environmental refugia from thermal stress such
+as depth.
+
+Our findings on the importance of connectivity may differ due to the highly uncertain nature
+of larval connectivity modelling [@vogt-vincent2023], the way larval flows and juvenile
+recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early bleaching
+events decreasing the breeding capacity of strongly connected reefs. Analysing daily
+connectivity data Vogt-Vincent et al. [-@vogt-vincent2023] suggest that time-mean
+connectivity may not be suitable for capturing the seasonal - ecological time scale,
+connectivity between locations due to the high daily variability in connectivity data. This
+is supported by the connectivity data used in our investigation, which have large relative
+standard deviations for connectivity between reefs over the 24 days used **figure**. Using
+alternative summarisation methods that capture ecological-timescale patterns in
+coral larval dispersal, such as cumulated implicit connectivity [@vogt-vincent2023],
+future investigations may find increased importance of both depth and reef connectivity for
+resilience, in line with [@hock2017; @torres2024]. Further improvements and research in
 connectivity modelling are necessary to provide a robust comparison of all factors

### 2025-07-26 paper/paper_draft.qmd
Add supplementary figure to show high daily variation in connectivity

@@
 is supported by the connectivity data used in our investigation, which have large relative
-standard deviations for connectivity between reefs over the 24 days used **figure**. Using
+standard deviations for connectivity between reefs over the 24 days used [@sfig-connectivity-rsd]. Using
 alternative summarisation methods that capture ecological-timescale patterns in
@@
 projected data we do not consider the impacts of waves, cyclones, currents and Crown of
-Thorns Starfish (CoTS) on coral colony survival and bleaching (**insert citations for waves
-affecting survival and bleaching**). Uncertainty in connectivity modelling outputs,
+Thorns Starfish (CoTS) on coral colony survival and bleaching [**Deaker et al**; **Massel and Done**]. Uncertainty in connectivity modelling outputs,
 satellite-derived bathymetry data and future thermal stress projections are likely to
@@
 
+![Heatmaps indicating reef connectivity relative standard deviation (RSD %). Reef connectivity relative
+standard deviation represents the reef standard deviation connection strength as a percentage
+of reef mean connection strength.
+Lighter colours indicate higher RSD % values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd width="`{julia} timeseries_width`"}
+
 ## ADRIA - CoralBlox

### 2025-07-26 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -269,36 +269,48 @@ all_conn_data = concatenatecubes(all_conn_data, Dim{:conn_name}(conn_names))
 std_conn = mapslices(std, all_conn_data, dims=[:conn_name])
 rstd_conn = std_conn ./ mean_conn .* 100
 
+# fig = Figure()
+# ax = Axis(
+#     fig[1,1],
+#     xlabel="",
+#     ylabel=""
+# )
+# hm = heatmap!(ax, rstd_conn[1:100,1:100])
+# Colorbar(fig[1,2], hm, label="std_conn / mean_conn * 100")
+
+# all_conn_data = readcubedata(all_conn_data)
+# n_boot = 200
+# n_matrices = size(all_conn_data)[3]
+
+# bootstrap_means = Array{Float64, 3}(undef, 3806, 3806, n_boot)
+
+# for b in 1:n_boot
+#     sample_indices = sample(1:n_matrices, n_matrices, replace=true)
+#     sample_matrices = view(all_conn_data, :, :, sample_indices)
+
+#     bootstrap_means[:, :, b] .= dropdims(mean(sample_matrices, dims=3), dims=3)
+# end
+
+# mean_matrix = dropdims(mean(bootstrap_means, dims=3), dims=3)
+# stdev_matrix = dropdims(std(bootstrap_means, dims=3), dims=3)
+# bootstrap_means = nothing
+
+# rsd_matrix = stdev_matrix ./ mean_matrix .* 100
+rstd_matrix = rstd_conn
 fig = Figure()
 ax = Axis(
     fig[1,1],
     xlabel="",
     ylabel=""
 )
-hm = heatmap!(ax, rstd_conn[1:100,1:100])
-Colorbar(fig[1,2], hm, label="std_conn / mean_conn * 100")
+hm = heatmap!(ax, rstd_matrix)
+Colorbar(fig[1,2], hm, label="Relative standard deviation connection strength [%]")
+save(
+    joinpath(output_path, "figs/connectivity_rsd_percent.png"),
+    fig,
+    px_per_unit=dpi
+)
 
-
-
-all_conn_data = readcubedata(all_conn_data)
-n_boot = 200
-n_matrices = size(all_conn_data)[3]
-
-bootstrap_means = Array{Float64, 3}(undef, 3806, 3806, n_boot)
-
-for b in 1:n_boot
-    sample_indices = sample(1:n_matrices, n_matrices, replace=true)
[…]

### 2025-07-26 paper/paper_draft.qmd
Proof reading edits for discussion section.

@@
 responses to change. This is supported by recent literature suggesting an effective approach
-to capturing climate change uncertainty is to model climate change responses using a range
-of climate models separately [@shepherd2018]. Despite large differences in coral cover
-across GCMs, the patterns identified between low, medium and high clusters of reefs suggest
-that the importance of depth refugia is consistent across scenarios.
+to capturing climate change uncertainty is to model responses using a range of GCMs
+separately [@shepherd2018]. Despite large differences in coral cover across GCMs, the
+patterns identified between low, medium and high clusters of reefs suggest that the
+importance of depth refugia is consistent across scenarios.
 
@@
 coral cover exceeding levels likely required to maintain positive carbonate budgets.
-Movement of shallow reefs towards negative cabonate budgets under increasing future thermal
-stress over time may contribute to phase shifts in reef dominant CaCO~3~ production.
-Shifting from coral driven to coralline encrusting algae driven production, or to bioerosion
-dominated systems with rapid erosion of physical reef frameworks [@dudgeon2010; @perry2008].
-While reefs at increased depths may be able to maintain coral driven CaCO~3~ production and
-accumulation into the future for longer.
+Movement of shallow reefs towards negative cabonate budgets in the future may contribute to
+phase shifts in reef dominant CaCO~3~ production. Shifting from coral driven to encrusting
+algae driven production, or to bioerosion dominated systems with rapid erosion of physical
+reef frameworks [@dudgeon2010; @perry2008]. While reefs at increased depths may be able to
+maintain coral driven CaCO~3~ production and accumulation into the future for longer.
 
@@
 refugia benefits and more prolonged resilience under climate change compared to shallower
-reefs. Additionally, [@liu2024] suggest that rubble instability is inversely correlated with
-reef depth, possibly limiting the juvenile recruitment capacity of shallow reefs. A caveat
-to these findings is the quality of the bathymetry data used to calculate median reef depth.
-This data (GBRMPA [-@gbr10gb2020]) is derived from satellite imagery and is limited in its
-alignment with the established GBRMPA reef outlines used in the investigation to
-characterise reef locations. As a result, 842 reefs (22% of 3806 reefs) were removed from
-the analyses before depth comparisons due to having less than 5% coverage of depth data.
-Additionally, deriving estimates of depth from satellite imagery is prone to high degrees of
-uncertainty. Data adopted for the given assessment are said to be accurate up to 15m from
-Mean Sea Level [@gbr10gb2020]. Furthermore, an estimated median depth is determined for each
-reef, using the established GBRMPA reef outlines to provide an indication of “true” reef
-extent. Therefore, the estimates of reef depths are taken as a useful indication rather than
-an accurate and precise report of reef depths across the GBR.
+reefs. Additionally, Lui, Callaghanand Baldock [-@liu2024] suggest that rubble instability
+is inversely correlated with reef depth, possibly limiting the juvenile recruitment capacity
+of shallow reefs. A caveat to these depth-resilience findings is the quality of the
+bathymetry data used to calculate median reef depth. These data (GBRMPA [-@gbr10gb2020]) are
+derived from satellite imagery and are limited in their alignment with the established
+GBRMPA reef outlines used in the investigation to characterise reef locations. As a result,
+842 reefs (22% of 3806 reefs) were removed from the depth-related analyses due to having
+less than 5% coverage of depth data. Additionally, deriving estimates of depth from
+satellite imagery is prone to high degrees of uncertainty. Data adopted for the given
+assessment are said to be accurate up to 15m from Mean Sea Level [@gbr10gb2020].
+Furthermore, an estimated median depth is determined for each reef, using the established
+GBRMPA reef outlines to provide an indication of “true” reef extent. Therefore, the
+estimates of reef depths are taken as a useful indication rather than an accurate and
+precise report of reef depths across the GBR.
 
@@
 [-@bairos-novak2021] that revealed high heritability of bleaching and survival response
-traits, used to inform the distributions of thermal tolerance traits used in this
-investigation. The lack of influence of thermal tolerance on reef outcomes is likely due to
-reefs being impacted by high levels of thermal stress early in timeseries and being unable
-to build thermal tolerance to DHW levels greater than 9°C.
+traits, used to inform thermal tolerance trait distributions in this investigation. The lack
+of influence of thermal tolerance on reef outcomes is likely due to reefs being impacted by
+high levels of thermal stress early in timeseries and being unable to build thermal
+tolerance to DHW levels greater than 9°C-weeks.
 
@@
 sample of particle flows, our results suggest that larval connectivity alone is not as
-important for reef resilience and recovery as environmental refugia from thermal stress such
-as depth.
+important for reef resilience and recovery as environmental refugia such as depth.
 
@@
 connectivity data Vogt-Vincent et al. [-@vogt-vincent2023] suggest that time-mean
-connectivity may not be suitable for capturing the seasonal - ecological time scale,
-connectivity between locations due to the high daily variability in connectivity data. This
-is supported by the connectivity data used in our investigation, which have large relative
-standard deviations for connectivity between reefs over the 24 days used [@sfig-connectivity-rsd]. Using
-alternative summarisation methods that capture ecological-timescale patterns in
-coral larval dispersal, such as cumulated implicit connectivity [@vogt-vincent2023],
-future investigations may find increased importance of both depth and reef connectivity for
-resilience, in line with [@hock2017; @torres2024]. Further improvements and research in
-connectivity modelling are necessary to provide a robust comparison of all factors
-influencing reef resilience.
+connectivity may not be suitable for capturing the seasonal - ecological time scale
+connectivity between locations due to high daily variability in connectivity data. This is
+supported by the connectivity data used in our investigation, which have large relative
+standard deviations for connectivity between reefs over the 24 days used
+[@sfig-connectivity-rsd]. Using alternative summarisation methods that capture
+ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
+connectivity [@vogt-vincent2023], future investigations may find increased importance of
+both depth and reef connectivity for resilience, in line with other investigations
+[@hock2017; @torres2024]. Further improvements and research in connectivity modelling are
+necessary to provide a robust comparison of all factors influencing reef resilience.
 
 There are multiple caveats in how coral ecosystem dynamics are modelled in this
-investigation. We model coral colonies as objects with circular diameter values and track
-these diameters over timesteps through growth. Due to the availability of quality future
-projected data we do not consider the impacts of waves, cyclones, currents and Crown of
-Thorns Starfish (CoTS) on coral colony survival and bleaching [**Deaker et al**; **Massel and Done**]. Uncertainty in connectivity modelling outputs,
-satellite-derived bathymetry data and future thermal stress projections are likely to
-influence the results obtained in this investigation. Incorporating further improvements in
-connectivity modelling and understanding of the influence of climate change on reef
-connectivity would improve the comparison of connectivity as an important factor for reef
-resilience. The DHW data used in this investigation have not been bias corrected for the
-Great Barrier Reef region and are part of a wider Australian dataset [@dixon2022] developed
-using statistical downscaling. We investigate a range of future climate responses, thermal
-projections and ecological parameterisations of ADRIA - CoralBlox to account for many
-possible futures, and our results suggest the factors that influence reef resilience are
-consistent across these scenarios.
+investigation. We model coral colonies as circular diameter values and track these diameters
+over timesteps through growth. Due to the availability of quality future projected data we
+do not consider the impacts of waves, cyclones, currents and Crown of Thorns Starfish (CoTS)
+on coral colony survival and bleaching [@massel1993; @deaker2022]. Uncertainty in
+connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress
+projections are likely to influence the results obtained in this investigation.
+Incorporating further improvements in connectivity modelling and understanding of the
+influence of climate change on reef connectivity would improve the comparison of
+connectivity as an important factor for reef resilience. The DHW data used in this
+investigation have not been bias corrected for the Great Barrier Reef region and are part of
+a wider Australian dataset [@dixon2022] developed using statistical downscaling. We
+investigate a range of future climate responses, thermal projections and ecological
+parameterisations of ADRIA - CoralBlox to account for many possible futures, and our results
+suggest the factors that influence reef resilience are consistent across these scenarios.
 
@@
 the investigation of different reef characteristics to be targetted in decision making and
-models the evolving outcomes as a result of reef interventions at various locations. The
+models the evolving outcomes as a result of interventions at various locations. The
 capability of ADRIA-CoralBlox could be further expanded by incorporating the impacts of
-waves, cyclones, CoTS and currents into reef resilience investigations [@lin2023;
+waves, cyclones, CoTS and currents into future resilience investigations [@lin2023;
 @mcclanahan2005; @grimaldi2022; @liu2024]. Additionally, the investigation could be enhanced
-by incorporating future ocean acidification into considerations of coral carbonate budgets
-required for healthy habitat production.
+by incorporating ocean acidification projections into analyses of coral carbonate budgets.
 
@@
 ACCESS-CM2, NorESM2-MM and
-GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignment.png){#fig-gcm-bioregion-cluster-assignment
+GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
 width="`{julia} timeseries_width`"}
 
-![Heatmaps indicating reef connectivity relative standard deviation (RSD %). Reef connectivity relative
-standard deviation represents the reef standard deviation connection strength as a percentage
-of reef mean connection strength.
-Lighter colours indicate higher RSD % values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd width="`{julia} timeseries_width`"}
+![Heatmaps indicating reef connectivity relative standard deviation (RSD %). Reef
+connectivity relative standard deviation represents the reef standard deviation connection
+strength as a percentage of reef mean connection strength. Lighter colours indicate higher
+RSD %
+values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
+width="`{julia} timeseries_width`"}
 

### 2025-07-28 paper/paper_draft.qmd
Updated paper abstract and conclusion paragraphs

@@
 abstract: |
-    Coral reefs globally face unprecedented threats from climate change, with the Great Barrier Reef (GBR) experiencing severe declines in coral cover from thermal stress events.
-Understanding which reefs exhibit resilience to climate impacts is critical for conservation planning and intervention strategies.
-A scenario-based population modelling approach was adopted with larval connectivity dynamics, thermal adaptation, and environmental factors to assess coral reef resilience across GBR locations under future climate projections.
-Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities, three distinct reef trajectories are identified: resilient reefs maintaining coral cover through 2050, intermediate reefs with moderate declines, and vulnerable reefs experiencing severe degradation.
-Contrary to expectations, larval connectivity patterns did not substantially differentiate resilient from vulnerable reefs.
-Instead, reef depth emerged as the primary predictor of resilience, with deeper reefs benefiting from thermal refugia that reduced bleaching impacts.
-Initial coral cover also influenced trajectories, with reefs having lower initial cover showing greater relative resilience.
-Our findings suggest that depth provides critical protection against thermal stress, contrasting current restoration practices that primarily target easily accessible shallow sites.
-These results have important implications for reef management, indicating that depth refugia should be prioritized for further consideration in conservation planning alongside connectivity considerations to maximize coral survival under continuing climate change.
+    Coral reefs globally face unprecedented threats from climate change, with the Great Barrier 
+    Reef (GBR) experiencing severe declines in coral cover from thermal stress events. 
+    Understanding which reefs exhibit resilience to climate impacts is critical for conservation 
+    planning and intervention strategies. A scenario-based population modelling approach was 
+    adopted with larval connectivity dynamics, thermal adaptation, and environmental factors 
+    to assess coral reef resilience across GBR locations under future climate projections. 
+    Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities, 
+    we analysed reef cover timeseries and the ability of reefs to maintain positive carbonate 
+    production budgets under future conditions. Contrary to expectations, larval connectivity 
+    patterns did not correlate with increases in maintainence of positive carbonate budgets. 
+    Instead, reef depth emerged as the primary predictor of cover-timeseries resilience and 
+    maintainence of positive carbonate budgets, with deeper reefs benefiting from thermal 
+    refugia that reduce bleaching impacts. Our findings suggest that depth provides critical 
+    protection against thermal stress, contrasting current restoration practices that primarily 
+    target easily accessible shallow sites. These results have important implications for 
+    reef management, indicating that depth refugia should be prioritized for further 
+    consideration in conservation planning alongside connectivity considerations to maximize 
+    coral survival under continuing climate change.
 keywords:
@@
 @skirving2020]. DHWs were represented by a selection of five Global Climate Models (GCMs)
-from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6; **citation**).
-These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4, and
-their inclusion were based on evaluation by Grose et al. [-@grose2023]. Grose et al.
-[-@grose2023] found these GCMs to rank highly, among 50 GCMs, in recreation of historical
-atmospheric temperature and precipitation conditions in the Australasian region. While this
-assessment does not consider oceanic data, Grose et al. \[\@-grose2023\] provide a
-region-specific selection mechanism which we use as an indicator of general performance of
-GCMs for the region.
+from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6). These five GCMs
+were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4, and their inclusion
+were based on evaluation by Grose et al. [-@grose2023]. Grose et al. [-@grose2023] found
+these GCMs to rank highly, among 50 GCMs, in recreation of historical atmospheric
+temperature and precipitation conditions in the Australasian region. While this assessment
+does not consider oceanic data, Grose et al. \[\@-grose2023\] provide a region-specific
+selection mechanism which we use as an indicator of general performance of GCMs for the
+region.
 
@@
 
-# Conclusions
-
-Overall, our results suggest that when modelled as part of a large and complex ecosystem,
-reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in
-support of depth as a form of refugia for shallow reefs. While protecting ‘key node’ reefs
-in larval connectivity networks is an important consideration for reef restoration efforts
-[@anthony2020; @hock2017], our results suggest that current connectivity modelling methods
-are not able to generate connectivity levels that contribute to reef resilience under
-projected conditions. We suggest further analyses that investigate the benefits of
-incorporating depth-based resilience into reef decision making, as well as further research
-and development in connectivity modelling methods for whole-ecosystem scales.
+In conclusion, our results suggest that when modelled as part of a large and complex
+ecosystem, reef depth is a key factor contributing to ongoing reef resilience. We provide
+evidence in support of depth as a form of thermal refugia for shallow-water reefs on the
+GBR. While protecting ‘key node’ reefs in larval connectivity networks is an important
+consideration for reef restoration efforts [@anthony2020; @hock2017], our results suggest
+that current connectivity modelling methods are not able to generate connectivity that
+contributes to reef resilience under projected conditions. We suggest further analyses that
+investigate the benefits of incorporating depth-based resilience into reef decision making,
+as well as further research and development in connectivity modelling methods for
+whole-ecosystem scales.
 

### 2025-08-04 paper/paper_draft.qmd
Slight expansion of the connectivity section

@@
 
-Twenty-four total days of connectivity data were used in this investigation, 2015, 2016,
-2018 and 2019 are represented represented by 3 daily connectivity matrices each, while 2017
-and 2020 are represented with 5 daily matrices each. Connectivity levels are implemented in
-ADRIA - CoralBlox as mean over the 24 days for each location.
+Connectivity data from 24 days in total were used in this investigation. These data span six
+years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices, while
+2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity strengths are
+implemented in ADRIA-CoralBlox as the mean of all available data for each location (i.e.,
+all 24 days). While the connectivity strengths do not vary from year to year within the
+simulation, they do vary between reefs of varying sizes, providing sufficient heterogeneity
+to capture spatial patterns in larval dispersal and settlement dynamics. The spatial
+variability also enables investigations into the influence of connectivity strength and its
+role in driving recovery processes.
 

### 2025-08-04 paper/paper_draft.qmd
Updates to fix figure sizing and word rendering

@@
 include("../src/common.jl")
+include("../src/plotting_functions.jl")
 
@@
 site at Cape
-Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
-width="`{julia} map_width`"}
+Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}
 
@@
 median reef depth level in metres. Displays results from median timeseries using
-ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
-width="`{julia} carb_width`"}
+ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate width=15.9cm}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 
-![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
+<!-- ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
 The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
@@
 2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
-width="`{julia} ecs_width`" align="center"}
+width="`{julia} ecs_width`"} -->
+
+![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
+The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
+the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al., 2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs width=10cm}
 
@@
 GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate
-width="`{julia} carb_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries
-width="`{julia} timeseries_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi
-width="`{julia} violin_width`"}
+width=15.9cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity
-width="`{julia} violin_width`"}
+width=15.9cm}

### 2025-08-04 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -297,7 +297,7 @@ rstd_conn = std_conn ./ mean_conn .* 100
 
 # rsd_matrix = stdev_matrix ./ mean_matrix .* 100
 rstd_matrix = rstd_conn
-fig = Figure()
+fig = Figure(size = (15.9*cm, 15.9*cm), fontsize=fontsize)
 ax = Axis(
     fig[1,1],
     xlabel="",

### 2025-08-04 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -22,7 +22,7 @@ ecs_values = Dict(
     "NorESM2-MM" => 2.5
 )
 ecs = ecs_plot(collect(values(ecs_values)), [2.5, 5.1], [2.1, 7.7], collect(keys(ecs_values)))
-save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit=dpi)
+save(joinpath(output_path, "figs/ecs_plot.png"), ecs, pt_per_unit=1)
 
 # GBR map plot - methods
 investigation_reefs = context_layers[

### 2025-08-04 src/common.jl

@@ -31,10 +31,12 @@ import GeoFormatTypes as GFT
 import ArchGDAL as AG
 import GeoInterface as GI
 using ADRIA
+using TOML
 
 include("plotting_functions.jl")
 include("ADRIA_DataCube_functions.jl")
 
+config = TOML.parsefile("config.toml")
 gbr_domain_path = config["domain"]["domain_dir"]
 output_path = config["results"]["output_dir"]
 

### 2025-08-04 src/plotting_functions.jl

@@ -11,21 +11,22 @@ using TOML
 config = TOML.parsefile("config.toml")
 
 # Define figure formatting constants
-fontsize = 7
-dpi = 400
+fontsize = 6
+dpi = 300
 
 # Define figure sizing constants for different figure types
-fig_sizes = Dict{String,Real}(
-    "violin_width" => 17,
-    "carb_width" => 25,
-    "map_height" => 18,
-    "map_width" => 18,
+# Maximum figure size in word document with 2.54cm margins is 15.9cm (if images are larger, word will shrink them)
+fig_sizes = Dict{String, Union{Float64, Int64}}(
+    "violin_width" => 15.9,
+    "carb_width" => 15.9,
+    "map_height" => 15.9,
+    "map_width" => 15.9,
     "ecs_width" => 10,
     "ecs_height" => 13,
-    "timeseries_width" => 25,
-    "violin_height" => 14,
-    "carb_height" => 17,
-    "timeseries_height" => 18
+    "timeseries_width" => 15.9,
+    "violin_height" => 13,
+    "carb_height" => 11,
+    "timeseries_height" => 12
 )
 
 # Convert figure sizes from cm to pixel measurement
@@ -197,11 +198,11 @@ Create methods publication figure that displays the ECS values for each GCM inve
 and display the likely/very-likely ranges of ECS values from the IPCC.
 """
 function ecs_plot(
-    ecs_values::Vector{Union{Float64,Int64}},
-    low_conf_range::Vector{Float64},
-    high_conf_range::Vector{Float64},
-    GCM_labels::Vector{String};
-    fig_sizes::Dict=fig_sizes,
+    ecs_values::Vector{Union{Float64, Int64}}, 
+    low_conf_range::Vector{Float64}, 
+    high_conf_range::Vector{Float64}, 
+    GCM_labels::Vector{String}; 
+    fig_sizes::Dict=fig_sizes, 
     fontsize=fontsize
 )
     fig_x_size = fig_sizes["ecs_width"]
@@ -667,8 +668,8 @@ in the y direction in figure.
 function grouped_GCM_cluster_timeseries_plots(
     timeseries_array::YAXArray,
     dataframe::DataFrame,
-    cluster_col::Union{String,Symbol},
-    grouping::Union{String,Symbol},
+    cluster_col::Union{String, Symbol},
+    grouping::Union{String, Symbol},
     length_t::UnitRange;
     fig_sizes::Dict=fig_sizes,
[…]

### 2025-08-05 paper/paper_draft.qmd
Improvements to plotting and rendering plots correctly to word

@@
 median reef depth level in metres. Displays results from median timeseries using
-ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate width=15.9cm}
+ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate width=14.82cm}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
-width=15.9cm}
+width=14.82cm}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-width=15.9cm}
+width=14.82cm}
 
@@
 GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
-width=15.9cm}
+width=14.82cm}
 
@@
 values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
-width=15.9cm}
+width=14.82cm}
 
@@
 ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
-width=15.9cm}
+width=14.82cm}
 
@@
 ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity
-width=15.9cm}
+width=14.82cm}
 
@@
 EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity
-width=15.9cm}
+width=14.82cm}
 
@@
 GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity
-width=15.9cm}
+width=14.82cm}
 
@@
 NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi
-width=15.9cm}
+width=14.82cm}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity
-width=15.9cm}
+width=14.82cm}

### 2025-08-05 src/plotting_functions.jl

@@ -11,24 +11,24 @@ using TOML
 config = TOML.parsefile("config.toml")
 
 # Define figure formatting constants
-fontsize = 5
+fontsize = 6
 dpi = 300
 
 # Define figure sizing constants for different figure types
 # Maximum figure size in word document with 2.54cm margins is 15.9cm (if images are larger, word will shrink them)
 fig_sizes = Dict{String, Union{Float64, Int64}}(
-    "violin_width" => 15.9,
-    "carb_width" => 15.9,
-    "map_height" => 15.9,
-    "map_width" => 15.9,
+    "violin_width" => 14.82,
+    "carb_width" => 14.82,
+    "map_height" => 14.82,
+    "map_width" => 14.82,
     "ecs_width" => 10,
     "ecs_height" => 13,
-    "timeseries_width" => 15.9,
-    "violin_height" => 13,
+    "timeseries_width" => 14.82,
+    "violin_height" => 12,
     "carb_height" => 11,
     "timeseries_height" => 12,
-    "cluster_hm_width" => 15.9,
-    "cluster_hm_height" => 20
+    "cluster_hm_width" => 14.82,
+    "cluster_hm_height" => 18
 )
 
 # Convert figure sizes from cm to pixel measurement
@@ -320,27 +320,41 @@ function grouped_cluster_timeseries_plots(
                 :xticks => (
                     first(length_t):10:last(length_t),
                     string.(collect((first(timesteps):10:last(timesteps))))
-                )
-                # :height => ysize,
-                # :width => xsize
+                ),
+                :spinewidth => 0.5,
+                :ylabelpadding => 2,
+                :xlabelpadding => 2,
+                :xticksize => 2,
+                :yticksize => 2
             )
         )
     end
 
     if grouping != :gbr
-        second_row = findfirst(last.(plot_layout) .== n_col) + 1
-        second_last_row = findfirst(x -> first(x) == maximum(first.(plot_layout)), plot_layout) - 1
-        middle_axes = filter(x -> x isa Axis, fig.content)[second_row:second_last_row]
+        bottom_axes = [last(plot_layout[last.(plot_layout) .== x]) for x in 1:n_col]
+        not_bottom_axes = findall(plot_layout .∉ [bottom_axes])
[…]

### 2025-08-06 paper/paper_draft.qmd
Minor formatting
Separate and make explicit section on DHWs
@eco-ben Please note my comments in this commit too :)

I think we do need more detail on SSP vs RCP, and how DHWs were estimated. Details on DHWs could be addressed by pointing to the relevant analysis script.

@@
 
-## Environmental modelling context
+## Modelling context
 
@@
 definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. In
-total this covers 3806 reef areas across the GBR marine park. Reefs that are outside the
-GBRMPA management areas or are not associated with a GBRMPA reefal bioregion were removed
-from the investigation, leaving 3531 reefs. Annually and spatially averaged Degree Heating
-Week (DHW) data were used to represent future thermal stress at each reef location.
-
-Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the GBR were
-obtained from the HighResCoralStress database [@dixon2022; @dixon2023]. Maximum monthly mean
-DHW levels were calculated from the SST data following NOAA methodology [@liu2017;
-@skirving2020]. DHWs were represented by a selection of five Global Climate Models (GCMs)
-from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6). These five GCMs
-were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4, and their inclusion
-were based on evaluation by Grose et al. [-@grose2023]. Grose et al. [-@grose2023] found
-these GCMs to rank highly, among 50 GCMs, in recreation of historical atmospheric
-temperature and precipitation conditions in the Australasian region. While this assessment
-does not consider oceanic data, Grose et al. \[\@-grose2023\] provide a region-specific
-selection mechanism which we use as an indicator of general performance of GCMs for the
-region.
-
-Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming
-caused by a doubling of carbon dioxide above its pre-industrial concentration
-[@forster2021]. The five GCMs span a range of ECS values within the IPCC assessed likely
-range, and GCM development families, allowing for a range of possible climate futures to be
-explored, capturing the uncertainty in future responses to CO2 increases (@sfig-ecs;
-[@grose2023; @shepherd2018]). The following analyses were performed using each GCM
-separately. SSP 2-4.5 was used as a plausible emission pathway under current emission
-trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020;
-IPCC -@climate2023].
+total, the dataset represents 3806 reef areas across the GBR marine park. Reefs that are
+outside the GBRMPA management areas or are not associated with a GBRMPA reefal bioregion
+were removed from the investigation, leaving 3531 reefs. Annually and spatially averaged
+Degree Heating Week (DHW) data were used to represent future thermal stress at each reef
+location.
 
@@
 
+## Degree Heating Week Trajectories
+
+Future projections of maximum yearly Degree Heating Weeks (DHWs) for each reef were
+estimated from Sea Surface Temperature (SST) data for the GBR. Statistically downscaled 1km
+resolution SST data for five Global Climate Models (GCMs) were obtained from the
+HighResCoralStress database [@dixon2022; @dixon2023]. These five GCMs were EC-Earth3-Veg,
+ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4 and are a part of the Sixth Phase of the
+Coupled Model Intercomparison Project (CMIP6) based on evaluation conducted by Grose et al.
+[-@grose2023]. These GCMs were found to rank highly in the recreation of historical
+atmospheric temperature and precipitation conditions in the Australasian region. While this
+assessment does not consider oceanic data, Grose et al. [-@grose2023] provide a
+region-specific selection mechanism which we use as an indicator of general performance of
+GCMs for the region.
+
+Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
+[@liu2017; @skirving2020], from which maximum yearly DHWs were determined.
+**\[TI: Could you confirm the above is described correctly?\]**
+
+The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
+the IPCC assessed likely range, and GCM development families. The IPCC defines ECS as the
+long term warming caused by a doubling of carbon dioxide above its pre-industrial
+concentration [@forster2021]. The five GCMs therefore allow for a range of possible climate
+futures to be explored, capturing the uncertainty in future responses to CO2 increases
+(@sfig-ecs; [@grose2023; @shepherd2018]).
+
+Shared Socio-economic Pathway 2 (replacing the older RCP 4.5) was used to represent the
+plausible emission pathway under current emission trajectories, with similar atmospheric CO2
+levels remaining until 2050 [@hausfather2020; IPCC -@climate2023].
+\[**TI note: The above needs to be expanded a little.
+IPCC has not been mentioned before at this point either**\]
+
+\[**TI: Needs a figure showing DHW trajectories for GBR!**\]
+
+\[**TI: Needs a table clearly communicating each GCM, ECS value, and what each represent
+(e.g., usual, optimistic scenario, etc)**\]
+
 ## Coral reef ecosystem model - ADRIA-CoralBlox
@@
 Connectivity data from 24 days in total were used in this investigation. These data span six
-years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices, while
-2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity strengths are
-implemented in ADRIA-CoralBlox as the mean of all available data for each location (i.e.,
-all 24 days). While the connectivity strengths do not vary from year to year within the
-simulation, they do vary between reefs of varying sizes, providing sufficient heterogeneity
-to capture spatial patterns in larval dispersal and settlement dynamics. The spatial
-variability also enables investigations into the influence of connectivity strength and its
-role in driving recovery processes.
+years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices,
+while 2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity
+strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
+location (i.e., all 24 days). While the connectivity strengths do not vary from year to year
+within the simulation, they do vary between reefs of varying sizes, providing sufficient
+heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
+spatial variability also enables investigations into the influence of connectivity strength
+and its role in driving recovery processes.
 

### 2025-08-06 paper/paper_draft.qmd
Comments for Future DHW section
Still thinking on section header as there's a slight repetition now.

Need to double check once I have plot generation working but I think the y-axis is wrong for the two figures maybe?

@@
 median reef depth level in metres. Displays results from median timeseries using
-ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate width=14.82cm}
-
-## Global Climate Model future trajectories
-
-Each GCM shows similar relationships between reef clusters and contextual analysis factors,
-thus further comparisons of these clusters for each analysis factor are only shown for
-ACCESS-ESM1-5 (intermediate ECS scenario). Results for the additional GCMs are displayed in
-the supplementary material. However, there are substantial differences in the longevity of
-reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover
-timeseries are displayed for each GCM (displayed clustered at management-area scale to
-preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
+ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
+width="14.82cm"}
+
+## Future DHW trajectories
+
+Each Global Climate Model (GCM) shows similar relationships between reef clusters and
+contextual analysis factors, thus further comparisons of these clusters for each analysis
+factor are only shown for ACCESS-ESM1-5 (an intermediate Equilibrium Climate Sensitivity
+scenario). Results for the additional GCMs are displayed in the supplementary material.
+However, there are substantial differences in the longevity of reef resilience and
+maintenance of coral cover post 2030 between the GCMs, thus coral cover timeseries are
+displayed for each GCM (displayed clustered at management-area scale to preserve coarse
+spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
 
@@
 continuing recovery and decline dynamics up to 2075 under this possible climate future.
-While recovery phases are predominantly seen in the ‘high’ cover cluster, the ‘medium’
-cluster, and to a lesser degree the ‘low’ cluster, also exhibit periods of recovery and
-increasing proportions of coral cover up to 2045. Under NorESM2-MM the Far Northern
-management area does not see coral cover maintenance as high as the three remaining
-management regions. Under the second lowest ECS projection (GFDL-CM4, 2.9°C) all clusters in
-each management area exhibit largely declining future trajectories with periods of recovery
-from 2030 to 2040. ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which results in
-intermediate levels of coral cover maintenance (between those of lower and higher ECS GCMs).
-In Townsville/Whitsunday and Far Northern management areas reefs in the high cluster are
-able to maintain coral cover levels around 20% to 2050 under ACCESS-ESM1-5. Under ACCESS-CM2
-(4.72°C) and EC-Earth3-Veg (4.31°C) GCMs cover trajectories are largely declining in all
-management areas.
+Recovery phases are predominantly seen in the ‘high’ cover cluster. The ‘medium’ cluster,
+and to a lesser degree the ‘low’ cluster, also exhibit periods of recovery and increasing
+proportions of coral cover up to 2045. Under NorESM2-MM the Far Northern management area
+does not see coral cover maintenance as high as the other management regions \[**TI:**
+**Quantify this! How did you determine this and how large/small are the difference in coral
+cover maintenance?**\]. Under the second lowest ECS projection (GFDL-CM4, 2.9°C) all
+clusters in each management area exhibit largely declining future trajectories with periods
+of recovery from 2030 to 2040. ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which
+results in intermediate levels of coral cover maintenance (between those of lower and higher
+ECS GCMs). In Townsville-Whitsunday and Far Northern management areas, reefs in the high
+cluster are able to maintain coral cover levels around 20% to 2050 under ACCESS-ESM1-5.
+Under ACCESS-CM2 (4.72°C) and EC-Earth3-Veg (4.31°C) GCMs cover trajectories are largely
+declining in all management areas.
 
 Under each GCM, in all management areas, low, medium and high cluster reefs have low
-differences between DHW trajectories (@fig-gcm-dhw-trajectories). The highest peak DHW
-levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHW
-timeseries occur under ACCESS-CM2.
+differences between DHW trajectories (@fig-gcm-dhw-trajectories) \[**TI:** **I don't
+understand this sentence - what is meant by reefs have low differences?**\]. The highest
+peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in
+overall DHW timeseries occur under ACCESS-CM2.
+
+![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
+analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
+between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
+represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
+represented five times (for each GCM), with each GCM displayed
+horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
+width="14.82cm"}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
-width=14.82cm}
-
-![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
-analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
-represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
-represented five times (for each GCM), with each GCM displayed
-horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
-width=14.82cm}
+width="14.82cm"}
 

### 2025-08-06 paper/paper_draft.qmd
auto-style correction

@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-width=14.82cm}
+width="14.82cm"}
 
@@
 
+```{=html}
 <!-- ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
@@
 width="`{julia} ecs_width`"} -->
+```
 
@@
 The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
-the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al., 2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs width=10cm}
+the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
+2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
+width="10cm"}
 
@@
 GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
-width=14.82cm}
+width="14.82cm"}
 
@@
 values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
-width=14.82cm}
+width="14.82cm"}
 
@@
 ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
-width=14.82cm}
+width="14.82cm"}
 
@@
 ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity
-width=14.82cm}
+width="14.82cm"}
 
@@
 EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity
-width=14.82cm}
+width="14.82cm"}
 
@@
 GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity
-width=14.82cm}
+width="14.82cm"}
 
@@
 NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi
-width=14.82cm}
+width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity
-width=14.82cm}
+width="14.82cm"}

### 2025-08-06 paper/paper_draft.qmd
Remove julia width variables not needed anymore

@@
 
-```{julia}
-#| include: false
-cd("../src")
-include("../src/common.jl")
-include("../src/plotting_functions.jl")
-
-map_width = fig_sizes["map_width"]
-ecs_width = fig_sizes["ecs_width"]
-timeseries_width = fig_sizes["timeseries_width"]
-violin_width = fig_sizes["violin_width"]
-carb_width = fig_sizes["carb_width"]
-```
-
 # Introduction

### 2025-08-06 paper/paper_draft.qmd
Add details on how DHWs were calculated from functions and [skirving]
Added details from model functions, referring to Skirving et al. (2020), about how DHW were calculated from SST data.

@ConnectedSystems I'm unsure of where the repository link/citation to code fits into the paper best

@@
 Degree Heating Week (DHW) data were used to represent future thermal stress at each reef
-location.
+location. Code used to calculate DHW data and perform analyses involved in this
+investigation can be found at **insert repo citation**.
 
@@
 Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
-[@liu2017; @skirving2020], from which maximum yearly DHWs were determined.
+[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatoloy (MM)
+was calculated as the mean SST for each month over 1985 to 2012, adjusted to centre at year
+1988.2857 (see Skirving et al. [-@skirving2020]). The "HotSpot SST Anomaly" [@skirving2020]
+was calculated as the difference between daily SST values and the maxmimum of a pixel's MM
+climatology (maximum monthly mean). DHW values are then calculated as the 12-week rolling
+sum of positive HotSpot SST Anomaly values for a pixel. 
 **\[TI: Could you confirm the above is described correctly?\]**
@@
 plausible emission pathway under current emission trajectories, with similar atmospheric CO2
-levels remaining until 2050 [@hausfather2020; IPCC -@climate2023].
-\[**TI note: The above needs to be expanded a little.
-IPCC has not been mentioned before at this point either**\]
+levels remaining until 2050 [@hausfather2020; IPCC -@climate2023]. \[**TI note: The above
+needs to be expanded a little. IPCC has not been mentioned before at this point either**\]
 

### 2025-08-06 paper/paper_draft.qmd
Add plotting of a GBR-wide DHW figure for methods section before results

@@
 climatology (maximum monthly mean). DHW values are then calculated as the 12-week rolling
-sum of positive HotSpot SST Anomaly values for a pixel. 
-**\[TI: Could you confirm the above is described correctly?\]**
+sum of positive HotSpot SST Anomaly values for a pixel. **\[TI: Could you confirm the above
+is described correctly?\]**
 
@@
 futures to be explored, capturing the uncertainty in future responses to CO2 increases
-(@sfig-ecs; [@grose2023; @shepherd2018]).
+(@sfig-ecs; @sfig-methods-dhws; [@grose2023; @shepherd2018]).
 
@@
 needs to be expanded a little. IPCC has not been mentioned before at this point either**\]
-
-\[**TI: Needs a figure showing DHW trajectories for GBR!**\]
 
@@
 
-```{=html}
-<!-- ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
-The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
-the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
-2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
-width="`{julia} ecs_width`"} -->
-```
-
 ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
@@
 width="10cm"}
+
+![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
+the different management areas across the Great Barrier Reef. Green represents
+Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
+represents the Townsville-Whitsunday management area. Solid lines represent the
+management-area median timeseries and bands represent the 2.5 to 97.5 percentile confidence
+intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#sfig-methods-dhws
+width="14.82cm"}
 

### 2025-08-06 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -81,3 +81,93 @@ Legend(
     backgroundcolor=bgcol
 )
 save(joinpath(output_path, "figs/region_map.png"), fig, px_per_unit=dpi)
+
+# GBR - wide DHW figure
+dhw_scenarios = open_dataset(joinpath(gbr_domain_path, "DHWs/dhwRCP45.nc"))
+GCMs = dhw_scenarios.dhw.properties["members"]
+
+context_layers = GDF.read(joinpath(output_path, "analysis_context_layers_carbonate.gpkg"))
+gbr_dom = ADRIA.load_domain(gbr_domain_path, "45")
+
+dhw_arrays = [
+    rebuild(gbr_dom.dhw_scens[:, :, i_gcm], dims=(gbr_dom.dhw_scens.timesteps, Dim{:sites}(context_layers.UNIQUE_ID))) for i_gcm in eachindex(GCMs)
+]
+dhw_arrays = concatenatecubes(dhw_arrays, Dim{:GCM}(GCMs))
+dhw_properties = copy(rel_cover_arrays.properties)
+dhw_properties[:is_relative] = false
+dhw_properties[:metric_feature] = "DHW"
+dhw_properties[:metric_unit] = "°C - Weeks"
+dhw_arrays = rebuild(dhw_arrays, metadata = dhw_properties)
+
+context_layers = context_layers[context_layers.management_area .!= "NA", :]
+context_layers = sort(context_layers, :management_area)
+
+dhw_arrays = dhw_arrays[sites=(dhw_arrays.sites .∈ [unique(context_layers.UNIQUE_ID)])]
+
+fig = Figure(
+    size = (fig_sizes["timeseries_width"], fig_sizes["timeseries_height"]),
+    fontsize = fontsize
+)
+plot_layout = [(x, 1) for x in eachindex(GCMs)]
+man_areas_categorical = CategoricalArray(context_layers.management_area)
+for (g, GCM) in enumerate(GCMs)
+    group_timeseries = dhw_arrays[1:50, :, g]
+    plot_layout_xi = plot_layout[g]
+    # ax = _setup_grouped_axes(
+    #         fig,
+    #         plot_layout_xi,
+    #         ([1, 10, 20, 30, 40, 50], string.([2025, 2035, 2045, 2055, 2065, 2075]));
+    #         ylabel="DHW [\u00B0 C]",
+    #         xlabel="",
+    #         title="",
+    #         xsize=nothing,
+    #         ysize=nothing,
[…]

### 2025-08-06 paper/paper_draft.qmd
Expand on GCM information and add basic table with ECS values.

@@
 The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
-the IPCC assessed likely range, and GCM development families. The IPCC defines ECS as the
-long term warming caused by a doubling of carbon dioxide above its pre-industrial
-concentration [@forster2021]. The five GCMs therefore allow for a range of possible climate
-futures to be explored, capturing the uncertainty in future responses to CO2 increases
-(@sfig-ecs; @sfig-methods-dhws; [@grose2023; @shepherd2018]).
-
-Shared Socio-economic Pathway 2 (replacing the older RCP 4.5) was used to represent the
-plausible emission pathway under current emission trajectories, with similar atmospheric CO2
-levels remaining until 2050 [@hausfather2020; IPCC -@climate2023]. \[**TI note: The above
-needs to be expanded a little. IPCC has not been mentioned before at this point either**\]
-
-\[**TI: Needs a table clearly communicating each GCM, ECS value, and what each represent
-(e.g., usual, optimistic scenario, etc)**\]
+the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and GCM
+development families. The IPCC defines ECS as the long term warming caused by a doubling of
+carbon dioxide above its pre-industrial concentration [@forster2021]. The five GCMs
+therefore allow for a range of possible climate futures to be explored, capturing the
+uncertainty in future responses to CO2 increases (@sfig-ecs; @sfig-methods-dhws;
+[@grose2023; @shepherd2018]).
+
+Shared Socio-economic Pathway 2-4.5 (approximate to the previously used RCP 4.5) was used to
+represent the plausible emission pathway under current emission trajectories, with similar
+atmospheric CO2 levels to present day remaining until 2050 [@hausfather2020; IPCC
+-@climate2023]. This SSP trajectory estimates 2.7°C of global atmospheric warming in the
+2081-2100 period relative to 1850-1900.
+
+\[**TI note: The above needs to be expanded a little. IPCC has not been mentioned before at this point either**\]
+
+\[**TI: Needs a table clearly communicating each GCM, ECS value, and what each represent (e.g., usual, optimistic scenario, etc)**\]
+
+| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Individual results displayed |
+|----|----|----|----|
+| EC-Earth3-Veg | 4.31 | High | Supplementary |
+| ACCESS-ESM1-5 | 3.87 | Intermediate | Supplementary |
+| ACCESS-CM2 | 4.72 | High | Main text |
+| GFDL-CM4 | 2.9 | Low | Supplementary |
+| NorESM2-MM | 2.5 | Low | Supplementary |
+
+: Table 1: Information for each GCM used in this investigation including ECS value,
+interpreted relative severity and where results are individual GCM results are displayed. GCMs in context with assessed plausible ranges of ECS values are displayed in [@fig-ecs].
+ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus
+results are displayed in the main text. ECS value sources: .
+
+\[**BG: Need to add my ECS value sources to table caption. (And also cite GCM paper sources).**\]
 
@@
 increase or decrease) rather than the exact quantative relationship is of interest.
-
-<!-- Split and move below to results/discussion -->
 

### 2025-08-07 src/plotting_functions.jl
Fix error in ecs plot reference and adjust DHW figure units label

@@ -211,7 +211,7 @@ Create methods publication figure that displays the ECS values for each GCM inve
 and display the likely/very-likely ranges of ECS values from the IPCC.
 """
 function ecs_plot(
-    ecs_values::Vector{Union{Float64, Int64}}, 
+    ecs_values::Vector{Float64}, 
     low_conf_range::Vector{Float64}, 
     high_conf_range::Vector{Float64}, 
     GCM_labels::Vector{String}; 

### 2025-08-07 src/ADRIA/HighResCoralStress/5_publication_plots.jl
Auto-formatting

@@ -95,14 +95,14 @@ dhw_arrays = [
 dhw_arrays = concatenatecubes(dhw_arrays, Dim{:GCM}(GCMs))
 dhw_arrays = rebuild(dhw_arrays, metadata=dhw_timeseries_properties)
 
-context_layers = context_layers[context_layers.management_area .!= "NA", :]
+context_layers = context_layers[context_layers.management_area.!="NA", :]
 context_layers = sort(context_layers, :management_area)
 
 dhw_arrays = dhw_arrays[sites=(dhw_arrays.sites .∈ [unique(context_layers.UNIQUE_ID)])]
 
 fig = Figure(
-    size = (fig_sizes["grouped_timeseries_width"], fig_sizes["grouped_timeseries_height"]),
-    fontsize = fontsize
+    size=(fig_sizes["timeseries_width"], fig_sizes["timeseries_height"]),
+    fontsize=fontsize
 )
 plot_layout = [(x, 1) for x in eachindex(GCMs)]
 man_areas_categorical = CategoricalArray(context_layers.management_area)
@@ -124,20 +124,21 @@ for (g, GCM) in enumerate(GCMs)
     # )
 
     ADRIA.viz.clustered_scenarios!(
-            fig[plot_layout_xi...],
-            group_timeseries,
-            Vector{Int64}(man_areas_categorical.refs);
-            opts=Dict{Symbol,Any}(:legend => false),
-            axis_opts=Dict(
-                :title => GCM,
-                :xticks => ([1, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50], string.([2025, 2030, 2035, 2040, 2045, 2050, 2055, 2060, 2065, 2070, 2075])),
-                :spinewidth => 0.5,
-                :ylabelpadding => 2,
-                :xlabelpadding => 2,
-                :xticksize => 2,
-                :yticksize => 2
-            )
+        fig[plot_layout_xi...],
+        group_timeseries,
+        Vector{Int64}(man_areas_categorical.refs);
+        opts=Dict{Symbol,Any}(:legend => false),
+        axis_opts=Dict(
+            :title => GCM,
+            :xticks => ([1, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50], string.([2025, 2030, 2035, 2040, 2045, 2050, 2055, 2060, 2065, 2070, 2075])),
+            :spinewidth => 0.5,
+            :ylabelpadding => 2,
+            :xlabelpadding => 2,
+            :xticksize => 2,
+            :yticksize => 2,
[…]

### 2025-08-07 src/plotting_functions.jl
Style plot for publication

@@ -697,10 +697,15 @@ function grouped_GCM_cluster_timeseries_plots(
     fig_sizes::Dict=fig_sizes,
     fontsize::Float64=fontsize
 )
-    fig_x_size = fig_sizes["gcm_timeseries_width"]
-    fig_y_size = fig_sizes["gcm_timeseries_height"]
+    # Adjust width and height just for the aspect ratio
+    # Doesn't seem to affect the word doc output
+    fig_x_size = fig_sizes["timeseries_width"] * 1.2
+    fig_y_size = fig_sizes["timeseries_height"] * 0.95
     n_col = optimum_columns(size(unique(dataframe[:, grouping]), 1))
-    fig, gdf, plot_layout = _setup_grouped_figure(
+
+    # Calculate layout scheme and grouped dataframe, but ignore figure.
+    # It sets a legend using predetermined row numbers but we want more flexibility
+    _, gdf, plot_layout = _setup_grouped_figure(
         dataframe,
         grouping;
         x_fig_size=fig_x_size,
@@ -709,10 +714,16 @@ function grouped_GCM_cluster_timeseries_plots(
         order=[:management_area, :GCM]
     )
 
-    labels = label_lines.("$(first(df.management_area)) - $(first(df.GCM))" for df in gdf; l_length=15)
+    mgmt_area = [first(df.management_area) for df in gdf]
+    mgmt_area = unique(replace.(mgmt_area, " Management Area" => ""))
+    gcm_header = unique([first(df.GCM) for df in gdf])
 
+    # Create custom figure
+    fig = Figure(size=(fig_x_size, fig_y_size), fontsize=fontsize)
+
+    current_row = 0
+    current_col = 0
     for (xi, groupdf) in enumerate(gdf)
-        # println("$(xi)")
         plot_layout_xi = plot_layout[xi]
         groupdf = sort(groupdf, cluster_col)
 
@@ -722,11 +733,7 @@ function grouped_GCM_cluster_timeseries_plots(
         group_timeseries = group_timeseries[locations=(group_timeseries.locations .∈ [groupdf.UNIQUE_ID])]
         group_timeseries = group_timeseries[length_t, indexin(groupdf.UNIQUE_ID, String.(group_timeseries.locations))]
 
-        # group_timeseries_less_than_5 = [all(group_timeseries[:, i].data .< 5) for i in 1:size(group_timeseries, 2)]
-        # group_timeseries_less_than_5_ind = findall(group_timeseries_less_than_5)
[…]

### 2025-08-07 paper/paper_draft.qmd
Fix error in ecs plot reference and adjust DHW figure units label
Table formatting and tweaks

@@
 
-\[**TI note: The above needs to be expanded a little. IPCC has not been mentioned before at this point either**\]
-
-\[**TI: Needs a table clearly communicating each GCM, ECS value, and what each represent (e.g., usual, optimistic scenario, etc)**\]
+\[**TI note: The above needs to be expanded a little. IPCC has not been mentioned before at
+this point either**\]
+
+\[**TI: Needs a table clearly communicating each GCM, ECS value, and what each represent
+(e.g., usual, optimistic scenario, etc)**\]
 
 | Global Climate Model source | ECS value (°C) | Interpreted relative severity | Individual results displayed |
-|----|----|----|----|
+|-----------------------|-----------------------|-----------------------|-----------------------|
 | EC-Earth3-Veg | 4.31 | High | Supplementary |
-| ACCESS-ESM1-5 | 3.87 | Intermediate | Supplementary |
-| ACCESS-CM2 | 4.72 | High | Main text |
+| ACCESS-CM2 | 4.72 | High | Supplementary |
+| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
 | GFDL-CM4 | 2.9 | Low | Supplementary |
@@
 : Table 1: Information for each GCM used in this investigation including ECS value,
-interpreted relative severity and where results are individual GCM results are displayed. GCMs in context with assessed plausible ranges of ECS values are displayed in [@fig-ecs].
+interpreted relative severity and where results are individual GCM results are displayed. GCMs in context with assessed plausible ranges of ECS values are displayed in [@sfig-ecs].
 ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus

### 2025-08-07 paper/paper_draft.qmd
Update subsection header
@eco-ben I changed my mind - the section does describe some methodological aspects so moved this back to under Methods.

@@
 
-## Modelling context
+## Reef representations
 
@@
 site at Cape
-Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}
-
-## Degree Heating Week Trajectories
+Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
+alt="Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points).
+The green polygon represents the Far Northern management area, the yellow polygon represents the Cairns/Cooktown management area, the pink polygon represents the Townsville/Whitsunday management area and the blue polygon represents the Mackay/Capricorn management area.
+The centroid of each reef is represented as a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion.
+An annotation represents the approximate location of the Australian Institute of Marine Science Townsville site at Cape Cleveland."}
+
+## Degree Heating Week trajectories
 

### 2025-08-07 paper/paper_draft.qmd
Fix typo

@@
 Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
-[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatoloy (MM)
+[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatology (MM)
 was calculated as the mean SST for each month over 1985 to 2012, adjusted to centre at year

### 2025-08-07 paper/paper_draft.qmd
Formatting
For TI to flesh out
Slight tweak to discussion intro

@@
 : Table 1: Information for each GCM used in this investigation including ECS value,
-interpreted relative severity and where results are individual GCM results are displayed. GCMs in context with assessed plausible ranges of ECS values are displayed in [@sfig-ecs].
+interpreted relative severity and where results are individual GCM results are displayed.
+GCMs in context with assessed plausible ranges of ECS values are displayed in [@fig-ecs].
 ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus
@@
 
-\[**BG: Need to add my ECS value sources to table caption. (And also cite GCM paper sources).**\]
+\[**BG: Need to add my ECS value sources to table caption. (And also cite GCM paper
+sources).**\]
 
@@
 involving depth as a resilience factor.
+
+\[**TI:** **For Takuya to flesh out**\]
 
@@
 
-Under all GCMs most reefs are projected to suffer substantial declines in coral cover from
-2025 levels. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintanance into
-the future. Differences between low, medium and high reef clusters in cover timeseries are
-most notable under these two GCMs. Maintainance of coral cover into the future is not
-clearly linked to the Equilibrium Climate Sensitivity of each GCM used as ACCESS-ESM1-5 has
-a higher ECS value than GFDL-CM4, with reefs experiencing large continuous declines under
-GFDL-CM4. These large declines are likely due to the high peak thermal stress levels above
-10°C-weeks experienced in the first ten years of the timeseries under GFDL-CM4.
+Under all GCMs most reefs are projected to suffer substantial declines in coral cover
+relative to 2025 levels. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover
+maintenance into the future. Differences between low, medium and high reef clusters in cover
+timeseries are most notable under these two GCMs. Maintainance of coral cover into the
+future is not clearly linked to the Equilibrium Climate Sensitivity of each GCM used as
+ACCESS-ESM1-5 has a higher ECS value than GFDL-CM4, with reefs experiencing large continuous
+declines under GFDL-CM4. These large declines are likely due to the high peak thermal stress
+levels above 10°C-weeks experienced in the first ten years of the timeseries under GFDL-CM4.
 

### 2025-08-07 paper/paper_draft.qmd
Shift description of depth estimation to earlier section
@eco-ben Could you double check the mentioned number of reefs for consistency in the text for depth estimation please?

Shifting text earlier up

@@
 
-## Coral reef ecosystem model - ADRIA-CoralBlox
+## Depth estimation
+
+Median depths for each reef location were extracted from satellite derived bathymetry data
+for the Great Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due
+to varying degrees of alignment between bathymetry data and the defined outlines for GBR
+reefs, reefs with less than 5% coverage of valid bathymetry data were removed from analyses
+involving depth as a resilience factor.
+
+\[**TI:** **For Takuya to flesh out**\]
+
+\[Below moved from discussion - to be reworked for flow\]
+
+These data (GBRMPA [-@gbr10gb2020]) are derived from satellite imagery and can be limited in
+their alignment with the established GBRMPA reef outlines used in the investigation to
+characterise reef locations. As a result, 842 reefs (22% of 3806 reefs) were removed from
+the depth-related analyses due to having less than 5% coverage of depth data. **\[TI to BG:
+is this number of reefs consistent?\]**
+
+Additionally, deriving estimates of depth from satellite imagery is prone to high degrees of
+uncertainty. Data adopted for the given assessment are said to be accurate up to 15m from
+Mean Sea Level [@gbr10gb2020]. Furthermore, an estimated median depth is determined for each
+reef, using the established GBRMPA reef outlines to provide an indication of “true” reef
+extent. Therefore, the estimates of reef depths are taken as a useful indication rather than
+an accurate and precise report of reef depths across the GBR.
+
+## ADRIA-CoralBlox modelling
 
@@
 and its role in driving recovery processes.
-
-### Depth estimation
-
-Median depths for each reef location were extracted from satellite derived bathymetry data
-for the Great Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due
-to varying degrees of alignment between bathymetry data and the defined outlines for GBR
-reefs, reefs with less than 5% coverage of valid bathymetry data were removed from analyses
-involving depth as a resilience factor.
-
-\[**TI:** **For Takuya to flesh out**\]
 
@@
 
-Overall, these findings support the hypothesis that reefs at greater depths will experience
-refugia benefits and more prolonged resilience under climate change compared to shallower
-reefs. Additionally, Lui, Callaghanand Baldock [-@liu2024] suggest that rubble instability
-is inversely correlated with reef depth, possibly limiting the juvenile recruitment capacity
-of shallow reefs. A caveat to these depth-resilience findings is the quality of the
-bathymetry data used to calculate median reef depth. These data (GBRMPA [-@gbr10gb2020]) are
-derived from satellite imagery and are limited in their alignment with the established
-GBRMPA reef outlines used in the investigation to characterise reef locations. As a result,
-842 reefs (22% of 3806 reefs) were removed from the depth-related analyses due to having
-less than 5% coverage of depth data. Additionally, deriving estimates of depth from
-satellite imagery is prone to high degrees of uncertainty. Data adopted for the given
-assessment are said to be accurate up to 15m from Mean Sea Level [@gbr10gb2020].
-Furthermore, an estimated median depth is determined for each reef, using the established
-GBRMPA reef outlines to provide an indication of “true” reef extent. Therefore, the
-estimates of reef depths are taken as a useful indication rather than an accurate and
-precise report of reef depths across the GBR.
+These findings support the hypothesis that reefs at greater depths will exhibit
+characteristics of refugia and more prolonged structural resilience under climate change
+compared to shallower reefs. Additionally, Lui, Callaghan and Baldock [-@liu2024] suggest
+that rubble instability is inversely correlated with reef depth, possibly limiting the
+juvenile recruitment capacity of shallow reefs. A caveat to these depth-resilience findings
+is the quality of the bathymetry data used to calculate median reef depth. As detailed
+previously, estimates of median reef depth are derived from satellite imagery (at $10m^2$
+resolution) which can be subject to high degrees of uncertainty, both in terms of the
+estimated depth at for each pixel as well as their alignment to the established GBRMPA reef
+outlines.
 

### 2025-08-07 paper/paper_draft.qmd
Marking a paragraph to be revisited for clarity

@@
 
-Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater
-thermal tolerance than reefs in lower coral cover clusters. This is in contrast with
-literature suggesting corals have the capacity to adapt to increasing climate change
-pressures [@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
+Our findings do not suggest that reefs in ‘high’ cover clusters have greater thermal
+tolerance than reefs in lower coral cover clusters. This is in contrast with literature
+suggesting corals have the capacity to adapt to increasing climate change pressures
+[@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
 [-@bairos-novak2021] that revealed high heritability of bleaching and survival response
@@
 of influence of thermal tolerance on reef outcomes is likely due to reefs being impacted by
-high levels of thermal stress early in timeseries and being unable to build thermal
-tolerance to DHW levels greater than 9°C-weeks.
+high levels of thermal stress early in projected conditions and being unable to build
+thermal tolerance to DHW levels greater than 9°C-weeks. **\[TI note: This paragraph needs to
+be revisited\]**
 

### 2025-08-07 paper/paper_draft.qmd
auto-format

@@
 site at Cape
-Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
-alt="Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points).
-The green polygon represents the Far Northern management area, the yellow polygon represents the Cairns/Cooktown management area, the pink polygon represents the Townsville/Whitsunday management area and the blue polygon represents the Mackay/Capricorn management area.
-The centroid of each reef is represented as a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion.
-An annotation represents the approximate location of the Australian Institute of Marine Science Townsville site at Cape Cleveland."}
+Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}
 

### 2025-08-07 src/ADRIA/HighResCoralStress/5_publication_plots.jl
Update y axis label for GBR-wide DHW timeseries plot in methods

@@ -19,7 +19,7 @@ ecs_values = Dict(
     "NorESM2-MM" => 2.5
 )
 ecs = ecs_plot(collect(values(ecs_values)), [2.5, 5.1], [2.1, 7.7], collect(keys(ecs_values)))
-save(joinpath(output_path, "figs/ecs_plot.png"), ecs, pt_per_unit=1)
+save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit=dpi)
 
 # GBR map plot - methods
 investigation_reefs = context_layers[
@@ -143,7 +143,7 @@ end
 
 axes_above_bottom = filter(x -> x isa Axis, fig.content)[1:end-1]
 map(x -> hidexdecorations!(x; grid=false, ticks=false), axes_above_bottom)
-map(x -> hideydecorations!(x, ticks=false, ticklabels=false, grid=false), axes_above_bottom)
+map(x -> hideydecorations!(x, ticks=false, ticklabels=false, grid=false), filter(x -> x isa Axis, fig.content))
 linkaxes!(filter(x -> x isa Axis, fig.content)...)
 
 legend_entries = []
@@ -167,4 +167,12 @@ Legend(
     patchsize=(5, 5)
 )
 rowsize!(fig.layout, maximum(first.(plot_layout)) + 1, Relative(0.03))
+feat = dhw_arrays.properties[:metric_feature]
+unit_text = dhw_arrays.properties[:metric_unit]
+Label(
+    fig[:, 0], "$feat [$unit_text]",
+    rotation=π / 2,  # Rotate 90 degrees
+    tellheight=false,
+    tellwidth=true
+)
 save(joinpath(output_path, "figs/methods_dhw_timeseries.png"), fig, px_per_unit=dpi)

### 2025-08-07 paper/paper_draft.qmd
Move GBR-wide DHW figure to methods section and move DHW clustered-results figure to supplementary

@@
 therefore allow for a range of possible climate futures to be explored, capturing the
-uncertainty in future responses to CO2 increases (@sfig-ecs; @sfig-methods-dhws;
+uncertainty in future responses to CO2 increases (@sfig-ecs; @fig-methods-dhws;
 [@grose2023; @shepherd2018]).
@@
 sources).**\]
+
+![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
+the different management areas across the Great Barrier Reef. Green represents
+Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
+represents the Townsville-Whitsunday management area. Solid lines represent the
+management-area median timeseries and bands represent the 2.5 to 97.5 percentile confidence
+intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
+width="14.82cm"}
 
@@
 Under each GCM, in all management areas, low, medium and high cluster reefs have low
-differences between DHW trajectories (@fig-gcm-dhw-trajectories) \[**TI:** **I don't
+differences between DHW trajectories (@sfig-gcm-dhw-trajectories) \[**TI:** **I don't
 understand this sentence - what is meant by reefs have low differences?**\]. The highest
@@
 overall DHW timeseries occur under ACCESS-CM2.
-
-![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
-analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
-represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
-represented five times (for each GCM), with each GCM displayed
-horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
-width="14.82cm"}
 
@@
 
-![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
-the different management areas across the Great Barrier Reef. Green represents
-Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
-represents the Townsville-Whitsunday management area. Solid lines represent the
-management-area median timeseries and bands represent the 2.5 to 97.5 percentile confidence
-intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#sfig-methods-dhws
+![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
+analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
+between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
+represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
+represented five times (for each GCM), with each GCM displayed
+horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
 width="14.82cm"}
@@
 
-![Heatmaps indicating reef connectivity relative standard deviation (RSD %). Reef
+![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef
 connectivity relative standard deviation represents the reef standard deviation connection

### 2025-08-07 paper/paper_draft.qmd
Remove supplementary figures that are just from extra GCMs
Only ACCESS-ESM1-5 has individual results displayed in the main paper text or supplementary results.
This intermediate GCM's results are indicative of other GCMs.
GCM comparison figures of clustering are still included in paper content.

@@
 therefore allow for a range of possible climate futures to be explored, capturing the
-uncertainty in future responses to CO2 increases (@sfig-ecs; @fig-methods-dhws;
-[@grose2023; @shepherd2018]).
+uncertainty in future responses to CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023;
+@shepherd2018]).
 
@@
 GCMs in context with assessed plausible ranges of ECS values are displayed in [@fig-ecs].
-ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus
-results are displayed in the main text. ECS value sources: .
+ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, when
+assessing factors impacting reef resilience these results are indicative of results from all
+GCMs assessed. Therefore, inidividual results for other GCMs are available at **insert repo
+citation**. ECS value sources: .
 
@@
 with greater levels of cover recovery, with persistence to 2050 in some bioregions
-(@sfig-access-esm1-5-bioregion-timeseries; @sfig-access-cm2-bioregion-timeseries;
-@sfig-ec-earth3-veg-bioregion-timeseries; @sfig-gfdl-cm4-bioregion-timeseries;
-@sfig-noresm2-mm-bioregion-timeseries).
+(@sfig-access-esm1-5-bioregion-timeseries).
 
@@
 within the ‘high’ cluster commonly having the greatest median reef depths within the
-bioregion (@fig-access-esm1-5-bioregion-depth; @sfig-access-cm2-bioregion-depth;
-@sfig-ec-earth3-veg-bioregion-depth; @sfig-gfdl-cm4-bioregion-depth;
-@sfig-noresm2-mm-bioregion-depth).
+bioregion (@fig-access-esm1-5-bioregion-depth).
 
@@
 correlation levels, while reefs in 'high' clusters have the highest correlation levels
-(@sfig-access-esm1-5-bioregion-dhwcor; @sfig-access-cm2-bioregion-dhwcor;
-@sfig-ec-earth3-veg-bioregion-dhwcor; @sfig-gfdl-cm4-bioregion-dhwcor;
-@sfig-noresm2-mm-bioregion-dhwcor).
+(@sfig-access-esm1-5-bioregion-dhwcor).
 
@@
 and mean timeseries DHW levels, with clusters having similar mean DHW levels in many
-bioregions (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-cm2-bioregion-dhwmean;
-@sfig-ec-earth3-veg-bioregion-dhwmean; @sfig-gfdl-cm4-bioregion-dhwmean;
-@sfig-noresm2-mm-bioregion-dhwmean).
+bioregions (@sfig-access-esm1-5-bioregion-dhwmean).
 
 Similarly, there are no substantial differences between reef clusters in mean thermal
-tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol;
-@sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol;
-@sfig-noresm2-mm-bioregion-dhwtol).
+tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol).
 
@@
 reefs' initial proportion of habitable area occupied by corals
-(@sfig-access-esm1-5-bioregion-initialproportion;
-@sfig-access-cm2-bioregion-initialproportion;
-@sfig-ec-earth3-veg-bioregion-initialproportion; @sfig-gfdl-cm4-bioregion-initialproportion;
-@sfig-noresm2-mm-bioregion-initialproportion).
+(@sfig-access-esm1-5-bioregion-initialproportion).
 
 Across most bioregions there are not consistent differences between clusters in connectivity
-metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi;
-@sfig-access-cm2-bioregion-logsosi; @sfig-ec-earth3-veg-bioregion-logsosi;
-@sfig-gfdl-cm4-bioregion-logsosi; @sfig-noresm2-mm-bioregion-logsosi) and total connectivity
-strength (@sfig-access-esm1-5-bioregion-totalconnectivity;
-@sfig-access-cm2-bioregion-totalconnectivity;
-@sfig-ec-earth3-veg-bioregion-totalconnectivity; @sfig-gfdl-cm4-bioregion-totalconnectivity;
-@sfig-noresm2-mm-bioregion-totalconnectivity).
+metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi)
+and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
 
@@
 standard deviations for connectivity between reefs over the 24 days used
-[@sfig-connectivity-rsd]. Using alternative summarisation methods that capture
+(@sfig-connectivity-rsd). Using alternative summarisation methods that capture
 ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
@@
 
-### Bioregion scale
+### Bioregion scale clustering
 
@@
 width="14.82cm"}
-
-## ACCESS-CM2
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the
-number of years cover exceeds the carbonate budget threshold. Point colour represents the
-median reef depth level in metres. Displays results from median timeseries using
-ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/depth_carbonate_scatter.png){#sfig-access-cm2-depth-carbonate
-width="14.82cm"}
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
-total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using
-ACCESS-CM2.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/log_total_strength_carbonate_scatter.png){#sfig-access-cm2-conn-carbonate
-width="14.82cm"}
-
-### Bioregion scale
-
-![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
-each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2040 within each
-bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
-to 97.5 percentile confidence intervals. Displays results for ACCESS-CM2
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/bioregion_cover_timeseries.png){#sfig-access-cm2-bioregion-timeseries
-width="14.82cm"}
-
-![Median depth for reefs within each bioregion, separated into clusters assigned by
-timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
-area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
-are clusters with intermediate median area-relative cover between 2030 and 2040 within each
-bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
-between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
-cluster. Displays results for ACCESS-CM2
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/depth_bioregion_violin.png){#sfig-access-cm2-bioregion-depth
-width="14.82cm"}
-
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
-assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
-median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
-(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
-within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW level for each cluster. Displays results for ACCESS-CM2
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwmean
-width="14.82cm"}
-
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median cover – DHW correlation level for each cluster. Displays results
-for ACCESS-CM2
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwcor
-width="14.82cm"}
-
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW tolerance value for each cluster. Displays results for ACCESS-CM2
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol
-width="14.82cm"}
-
-![Initial proportion of coral habitable area occupied by corals for reefs within each
-bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
-are clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median proportion of habitable area occupied for each cluster. Displays
-results for ACCESS-CM2
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-cm2-bioregion-initialproportion
-width="14.82cm"}
-
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines within each violin represent the median log (natural) source – to – sink ratio for
-each cluster and grey points represent the ratio value for each reef. Vertical grey lines
-represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
-incoming connectivity levels. Displays results for ACCESS-CM2
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/so_to_si_bioregion_violin.png){#sfig-access-cm2-bioregion-logsosi
-width="14.82cm"}
-
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
-violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for ACCESS-CM2
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-cm2-bioregion-totalconnectivity
-width="14.82cm"}
-
-## EC-Earth3-Veg
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the
-number of years cover exceeds the carbonate budget threshold. Point colour represents the
-median reef depth level in metres. Displays results from median timeseries using
-EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/depth_carbonate_scatter.png){#sfig-ec-earth3-veg-depth-carbonate
-width="14.82cm"}
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
-total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using
-EC-Earth3-Veg.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/log_total_strength_carbonate_scatter.png){#sfig-ec-earth3-veg-conn-carbonate
-width="14.82cm"}
-
-### Bioregion scale
-
-![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
-each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2040 within each
-bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
-to 97.5 percentile confidence intervals. Displays results for EC-Earth3-Veg
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/bioregion_cover_timeseries.png){#sfig-ec-earth3-veg-bioregion-timeseries
-width="14.82cm"}
-
-![Median depth for reefs within each bioregion, separated into clusters assigned by
-timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
-area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
-are clusters with intermediate median area-relative cover between 2030 and 2040 within each
-bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
-between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
-cluster. Displays results for EC-Earth3-Veg
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/depth_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-depth
-width="14.82cm"}
-
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
-assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
-median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
-(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
-within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW level for each cluster. Displays results for EC-Earth3-Veg
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/mean_dhw_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwmean
-width="14.82cm"}
-
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median cover – DHW correlation level for each cluster. Displays results
-for EC-Earth3-Veg
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwcor
-width="14.82cm"}
-
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW tolerance value for each cluster. Displays results for EC-Earth3-Veg
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol
-width="14.82cm"}
-
-![Initial proportion of coral habitable area occupied by corals for reefs within each
-bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
-are clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median proportion of habitable area occupied for each cluster. Displays
-results for EC-Earth3-Veg
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/initial_proportion_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-initialproportion
-width="14.82cm"}
-
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines within each violin represent the median log (natural) source – to – sink ratio for
-each cluster and grey points represent the ratio value for each reef. Vertical grey lines
-represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
-incoming connectivity levels. Displays results for EC-Earth3-Veg
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/so_to_si_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-logsosi
-width="14.82cm"}
-
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
-violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for EC-Earth3-Veg
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/log_total_strength_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-totalconnectivity
-width="14.82cm"}
-
-## GFDL-CM4
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the
-number of years cover exceeds the carbonate budget threshold. Point colour represents the
-median reef depth level in metres. Displays results from median timeseries using
-GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/depth_carbonate_scatter.png){#sfig-gfdl-cm4-depth-carbonate
-width="14.82cm"}
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
-total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using
-GFDL-CM4.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/log_total_strength_carbonate_scatter.png){#sfig-gfdl-cm4-conn-carbonate
-width="14.82cm"}
-
-### Bioregion scale
-
-![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
-each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2040 within each
-bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
-to 97.5 percentile confidence intervals. Displays results for GFDL-CM4
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/bioregion_cover_timeseries.png){#sfig-gfdl-cm4-bioregion-timeseries
-width="14.82cm"}
-
-![Median depth for reefs within each bioregion, separated into clusters assigned by
-timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
-area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
-are clusters with intermediate median area-relative cover between 2030 and 2040 within each
-bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
-between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
-cluster. Displays results for GFDL-CM4
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/depth_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-depth
-width="14.82cm"}
-
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
-assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
-median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
-(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
-within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW level for each cluster. Displays results for GFDL-CM4
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/mean_dhw_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwmean
-width="14.82cm"}
-
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median cover – DHW correlation level for each cluster. Displays results
-for GFDL-CM4
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwcor
-width="14.82cm"}
-
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW tolerance value for each cluster. Displays results for GFDL-CM4
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol
-width="14.82cm"}
-
-![Initial proportion of coral habitable area occupied by corals for reefs within each
-bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
-are clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median proportion of habitable area occupied for each cluster. Displays
-results for GFDL-CM4
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/initial_proportion_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-initialproportion
-width="14.82cm"}
-
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines within each violin represent the median log (natural) source – to – sink ratio for
-each cluster and grey points represent the ratio value for each reef. Vertical grey lines
-represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
-incoming connectivity levels. Displays results for GFDL-CM4
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/so_to_si_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-logsosi
-width="14.82cm"}
-
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
-violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for GFDL-CM4
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/log_total_strength_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-totalconnectivity
-width="14.82cm"}
-
-## NorESM2-MM
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the
-number of years cover exceeds the carbonate budget threshold. Point colour represents the
-median reef depth level in metres. Displays results from median timeseries using
-NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/depth_carbonate_scatter.png){#sfig-noresm2-mm-depth-carbonate
-width="14.82cm"}
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
-total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using
-NorESM2-MM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/log_total_strength_carbonate_scatter.png){#sfig-noresm2-mm-conn-carbonate
-width="14.82cm"}
-
-### Bioregion scale
-
-![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
-each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2040 within each
-bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
-to 97.5 percentile confidence intervals. Displays results for NorESM2-MM
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/bioregion_cover_timeseries.png){#sfig-noresm2-mm-bioregion-timeseries
-width="14.82cm"}
-
-![Median depth for reefs within each bioregion, separated into clusters assigned by
-timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
-area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
-are clusters with intermediate median area-relative cover between 2030 and 2040 within each
-bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
-between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
-cluster. Displays results for NorESM2-MM
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/depth_bioregion_violin.png){#sfig-noresm2-mm-bioregion-depth
-width="14.82cm"}
-
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
-assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
-median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
-(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
-within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW level for each cluster. Displays results for NorESM2-MM
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/mean_dhw_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwmean
-width="14.82cm"}
-
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median cover – DHW correlation level for each cluster. Displays results
-for NorESM2-MM
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwcor
-width="14.82cm"}
-
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW tolerance value for each cluster. Displays results for NorESM2-MM
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol
-width="14.82cm"}
-
-![Initial proportion of coral habitable area occupied by corals for reefs within each
-bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
-are clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median proportion of habitable area occupied for each cluster. Displays
-results for NorESM2-MM
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/initial_proportion_bioregion_violin.png){#sfig-noresm2-mm-bioregion-initialproportion
-width="14.82cm"}
-
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines within each violin represent the median log (natural) source – to – sink ratio for
-each cluster and grey points represent the ratio value for each reef. Vertical grey lines
-represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
-incoming connectivity levels. Displays results for NorESM2-MM
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/so_to_si_bioregion_violin.png){#sfig-noresm2-mm-bioregion-logsosi
-width="14.82cm"}
-
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
-violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for NorESM2-MM
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/log_total_strength_bioregion_violin.png){#sfig-noresm2-mm-bioregion-totalconnectivity
-width="14.82cm"}

### 2025-08-07 paper/paper_draft.qmd
Expand on DHW section and other small changes
Mark where citation of repository is needed for extra GCM results. Add conclusion paragraph heading.

@@
 was calculated as the difference between daily SST values and the maxmimum of a pixel's MM
-climatology (maximum monthly mean). DHW values are then calculated as the 12-week rolling
-sum of positive HotSpot SST Anomaly values for a pixel. **\[TI: Could you confirm the above
-is described correctly?\]**
+climatology (maximum monthly mean). DHW values were then calculated as the 12-week rolling
+sum of positive HotSpot SST Anomaly values for a pixel. Within each year the maximum of
+monthly mean DHW values was calculated. Reef scale DHW timeseries were extracted by taking
+the average DHW level over pixels touching a reef.
 
@@
 |-----------------------|-----------------------|-----------------------|-----------------------|
-| EC-Earth3-Veg | 4.31 | High | Supplementary |
-| ACCESS-CM2 | 4.72 | High | Supplementary |
+| EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
+| ACCESS-CM2 | 4.72 | High | **insert repo citation** |
 | ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
-| GFDL-CM4 | 2.9 | Low | Supplementary |
-| NorESM2-MM | 2.5 | Low | Supplementary |
+| GFDL-CM4 | 2.9 | Low | **insert repo citation** |
+| NorESM2-MM | 2.5 | Low | **insert repo citation** |
 
@@
 
+# Conclusion
+
 In conclusion, our results suggest that when modelled as part of a large and complex

### 2025-08-08 paper/paper_draft.qmd
Add reference to figure

@@
 The spatial extent of the GBR reefs represented in this investigation follows the reef
-definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. In
-total, the dataset represents 3806 reef areas across the GBR marine park. Reefs that are
-outside the GBRMPA management areas or are not associated with a GBRMPA reefal bioregion
-were removed from the investigation, leaving 3531 reefs. Annually and spatially averaged
-Degree Heating Week (DHW) data were used to represent future thermal stress at each reef
-location. Code used to calculate DHW data and perform analyses involved in this
+definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. An
+indicative map of the GBR marine park including the Marine Park regions and which bioregion
+each reef belongs to is shown in @fig-region-map. In total, the dataset represents 3806 reef
+areas across the GBR marine park. Reefs that are outside the GBRMPA management areas or are
+not associated with a GBRMPA reefal bioregion **\[TI: Ben, cite the bioregion data
+source\]** were removed from the investigation, leaving 3531 reefs. Annually and spatially
+averaged Degree Heating Week (DHW) data were used to represent future thermal stress at each
+reef location. Code used to calculate DHW data and perform analyses involved in this
 investigation can be found at **insert repo citation**.

### 2025-08-08 paper/paper_draft.qmd
Expand DHW description
Add reference to table.

@eco-ben to address comments :)

Revert change to table

@@
 HighResCoralStress database [@dixon2022; @dixon2023]. These five GCMs were EC-Earth3-Veg,
-ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4 and are a part of the Sixth Phase of the
+ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4 and are a part of the Sixth Phase of the
 Coupled Model Intercomparison Project (CMIP6) based on evaluation conducted by Grose et al.
@@
 region-specific selection mechanism which we use as an indicator of general performance of
-GCMs for the region.
-
-Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
-[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatology (MM)
-was calculated as the mean SST for each month over 1985 to 2012, adjusted to centre at year
-1988.2857 (see Skirving et al. [-@skirving2020]). The "HotSpot SST Anomaly" [@skirving2020]
-was calculated as the difference between daily SST values and the maxmimum of a pixel's MM
-climatology (maximum monthly mean). DHW values were then calculated as the 12-week rolling
-sum of positive HotSpot SST Anomaly values for a pixel. Within each year the maximum of
-monthly mean DHW values was calculated. Reef scale DHW timeseries were extracted by taking
-the average DHW level over pixels touching a reef.
+GCMs for the region. An overview of the selected GCMs are provided in @tbl-gcms. The process
+described herein was conducted for all reefs within the GBR Marine Park to create DHW
+projections spanning from 2025 to 2075.
 
@@
 the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and GCM
-development families. The IPCC defines ECS as the long term warming caused by a doubling of
-carbon dioxide above its pre-industrial concentration [@forster2021]. The five GCMs
-therefore allow for a range of possible climate futures to be explored, capturing the
-uncertainty in future responses to CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023;
-@shepherd2018]).
+development families \[**TI: Ben, what does "GCM development families" mean?**\]. The IPCC
+defines ECS as the long term warming caused by a doubling of carbon dioxide above its
+pre-industrial concentration [@forster2021]. The five GCMs therefore allow for a range of
+possible climate futures to be explored, capturing the uncertainty in future responses to
+CO2 increases (@fig-ecs; @sfig-methods-dhws; [@grose2023; @shepherd2018]) **\[TI: Missing
+figure reference?\]**. Projections using Shared Socio-economic Pathway (SSP) 2-4.5 was used
+to represent the plausible emission pathway. It represents a moderate emissions scenario
+with continued CO2 emissions comparable to present day until 2050, after which emissions
+gradually decline. Under this scenario, atmospheric concentrations approximately reach
+540ppm by 2100 [@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to
+4.31°C of global atmospheric warming in the 2081-2100 period relative to 1850-1900.
 
-Shared Socio-economic Pathway 2-4.5 (approximate to the previously used RCP 4.5) was used to
-represent the plausible emission pathway under current emission trajectories, with similar
-atmospheric CO2 levels to present day remaining until 2050 [@hausfather2020; IPCC
--@climate2023]. This SSP trajectory estimates 2.7°C of global atmospheric warming in the
-2081-2100 period relative to 1850-1900.
+DHW climatological baselines were calculated from the SST data following NOAA methodology
+[@liu2017; @skirving2020]. For each pixel of SST data, the Monthly Mean SST climatology was
+calculated by computing the mean SST value for each calendar month (January through
+December) across the 28-year baseline period from 1985 to 2012. This climatological baseline
+was then temporally adjusted to center at year 1988.2857, which represents the midpoint of
+the reference period and accounts for any long-term trends within the baseline years
+themselves. The adjustment ensures that the climatology represents conditions at a specific
+temporal reference point rather than being influenced by gradual warming or cooling trends
+that may have occurred during the 1985-2012 period. The resulting monthly climatologies
+serve as a standardized reference against which current SST conditions can be compared to
+identify thermal anomalies and assess coral bleaching risk, following the methodology
+established by Skirving et al. [-@skirving2020].
 
-\[**TI note: The above needs to be expanded a little. IPCC has not been mentioned before at
-this point either**\]
+**\[TI: Ben, could you provide more details in the paragraph above please? What resolution
+is the data in? 10m\^2?\]**
 
-\[**TI: Needs a table clearly communicating each GCM, ECS value, and what each represent
-(e.g., usual, optimistic scenario, etc)**\]
+Degree Heating Weeks (DHWs) were then derived using the "HotSpot SST Anomaly" approach
+[@skirving2020]. The "HotSpot SST Anomaly" represents the thermal stress experienced by
+coral reefs and is calculated as the difference between daily SST values and the maximum of
+a pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean
+temperature). This approach uses the annual maximum temperature as the baseline because
+corals are adapted to withstand their local warmest conditions under normal seasonal cycles.
+When temperatures exceed this seasonal maximum, corals experience thermal stress that can
+lead to bleaching. Only positive anomalies are considered relevant for coral stress, as
+temperatures below the seasonal maximum do not contribute to bleaching risk.
 
-| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Individual results displayed |
-|-----------------------|-----------------------|-----------------------|-----------------------|
+DHW values on a per-pixel basis were then calculated as the 12-week rolling sum of positive
+HotSpot SST Anomaly values, expressed in units of °C-weeks. The 12-week accumulation period
+reflects the cumulative nature of coral thermal stress. Brief temperature spikes may be
+tolerable, but sustained or repeated exposure to elevated temperatures causes progressively
+greater physiological stress and bleaching severity. DHW values integrate both the magnitude
+and duration of thermal stress: a moderate anomaly (e.g., 1°C) sustained for 12 weeks
+produces the same DHW value as a severe anomaly (e.g., 3°C) lasting 4 weeks, though the
+biological impacts may differ. DHW estimates for each indicative reef (see @greatba2022)
+were then determined by taking the mean DHW value for all pixels within each reef outline.
+
+**\[TI: Ben, I did my best to expand on DHW calculations and detail HotSpot SST anomaly,
+could you please check?\]**
+
+::: {#tbl-gcms}
+| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
+|-----------------------------|----------------|-------------------------------|------------------|
 | EC-Earth3-Veg               | 4.31           | High                          | **insert repo citation**    |
@@
 
-: Table 1: Information for each GCM used in this investigation including ECS value,
-interpreted relative severity and where results are individual GCM results are displayed.
-GCMs in context with assessed plausible ranges of ECS values are displayed in [@fig-ecs].
-ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, when
-assessing factors impacting reef resilience these results are indicative of results from all
-GCMs assessed. Therefore, inidividual results for other GCMs are available at **insert repo
-citation**. ECS value sources: .
+: Information for each GCM used in this investigation including ECS value, interpreted
+relative severity and where results are individual GCM results are found. GCMs in context
+with assessed plausible ranges of ECS values are displayed in [@sfig-ecs] **\[TI: Missing
+figure?\]**. ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS
+values, thus results are displayed in the main text. ECS value sources: .
+:::
 
@@
 Under each GCM, in all management areas, low, medium and high cluster reefs have low
-differences between DHW trajectories (@sfig-gcm-dhw-trajectories) \[**TI:** **I don't
+differences between DHW trajectories (@fig-gcm-dhw-trajectories) \[**TI:** **I don't
 understand this sentence - what is meant by reefs have low differences?**\]. The highest
@@
 overall DHW timeseries occur under ACCESS-CM2.
+
+![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
+analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
+between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
+represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
+represented five times (for each GCM), with each GCM displayed
+horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
+width="14.82cm"}
 
@@
 standard deviations for connectivity between reefs over the 24 days used
-(@sfig-connectivity-rsd). Using alternative summarisation methods that capture
+[@sfig-connectivity-rsd]. Using alternative summarisation methods that capture
 ecological-timescale patterns in coral larval dispersal, such as cumulated implicit

### 2025-08-08 paper/paper_draft.qmd
Expand depth estimation method

@@
 
-Median depths for each reef location were extracted from satellite derived bathymetry data
-for the Great Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due
-to varying degrees of alignment between bathymetry data and the defined outlines for GBR
-reefs, reefs with less than 5% coverage of valid bathymetry data were removed from analyses
-involving depth as a resilience factor.
+Reef depth characteristics were extracted using 10m resolution bathymetry data from the
+Great Barrier Reef Marine Park Authority (GBRMPA [-@gbr10gb2020]). For each reef, bathymetry
+data (in raster format) were spatially matched with reef polygon features through geometric
+intersection analysis. Depth values within each reef polygon were summarized using zonal
+statistics to calculate minimum, mean, median, maximum, and standard deviation of depth
+values. All depth values were converted to positive values (depths below sea level). The
+median depth was used to provide an indicative depth value for each reef.
 
-\[**TI:** **For Takuya to flesh out**\]
+As bathymetry data are derived from satellite imagery they can be limited in their alignment
+with the established GBRMPA reef outlines used in the investigation to characterise reef
+locations. Quality control flags were assigned to identify potential data limitations: reefs
+with no overlapping bathymetry data, reefs with minimum depth values above sea level
+(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
+5% of the reef polygon area. These reefs with insufficient data coverage were removed from
+analyses (842 reefs of 3806 reefs, or 22%) **\[TI: BG to update\]**.
 
-\[Below moved from discussion - to be reworked for flow\]
+While data adopted for the given assessment are said to be accurate up to 15m from Mean Sea
+Level [@gbr10gb2020], there are many sources of uncertainty in the depth estimates used for
+this study. There is potential misalignment between GBRMPA reef outlines, as well as the
+usual challenges of deriving data from satellite imagery. In the case of bathymetry,
+estimates are subject to different bottom types (rock, sand, seagrass, etc) and how these
+affect reflectance, the water penetration depth of satellite sensors, influence of local
+conditions (e.g., turbidity and wave activity), and many other factors. The resulting depth
+estimates are therefore highly uncertain themselves and are only adopted as a useful
+indication rather than an accurate and precise report of reef depths across the GBR.
 
-These data (GBRMPA [-@gbr10gb2020]) are derived from satellite imagery and can be limited in
-their alignment with the established GBRMPA reef outlines used in the investigation to
-characterise reef locations. As a result, 842 reefs (22% of 3806 reefs) were removed from
-the depth-related analyses due to having less than 5% coverage of depth data. **\[TI to BG:
-is this number of reefs consistent?\]**
-
-Additionally, deriving estimates of depth from satellite imagery is prone to high degrees of
-uncertainty. Data adopted for the given assessment are said to be accurate up to 15m from
-Mean Sea Level [@gbr10gb2020]. Furthermore, an estimated median depth is determined for each
-reef, using the established GBRMPA reef outlines to provide an indication of “true” reef
-extent. Therefore, the estimates of reef depths are taken as a useful indication rather than
-an accurate and precise report of reef depths across the GBR.
+**\[TI: TODO cite Canonical Reefs repository\]**
 

### 2025-08-08 paper/paper_draft.qmd
Add section on scenario modelling
Add table quantifying the distances between low and high manag clusters

@@
 
+### TODO: Section on scenario modelling
+
+**[TI and BG to flesh out]**
+
+For each GCM, ran 4096 reference scenarios ("counterfactuals")...
+
 ### Factors influencing bleaching mortality
@@
 different magnitudes relative to other reefs in their bioregion.
+
+```{julia}
+#| echo: false
+#| warning: false
+#| message: false
+#| results: asis
+#| label: tbl-cluster-cid
+#| tbl-cap: Complexity invariant distance (CID) between low and high cluster median timeseries in each management area under each GCM.
+CID values are calculated for percentage cover timeseries (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) timeseries (@fig-gcm-dhw-trajectories).
+Complexity invariant distance represents the euclidean distance between timeseries, corrected by the complexity of the two timeseries.
+CID values for percentage cover and DHW timeseries are not directly comparable as the timeseries use different units.
+
+using PrettyTables, Markdown
+cd("../src")
+include("../src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl"); # Quantify low-high cluster differences using CID metric.
+
+io = IOBuffer()
+
+header = ["GCM", "Management area", "CID - cover", "CID - DHW"]
+pretty_table(io, distances, backend = Val(:markdown), header = header)
+
+md_string = (String(take!(io)))
+Markdown.parse(md_string)
+```
 

### 2025-08-08 src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl

@@ -1,6 +1,7 @@
 include("../../common.jl")
 
 context_layers = GDF.read(joinpath(output_path, "analysis_context_layers_carbonate.gpkg"))
+context_layers = context_layers[context_layers.management_area .!= "NA", :]
 
 dhw_scenarios = open_dataset(joinpath(gbr_domain_path, "DHWs/dhwRCP45.nc"))
 GCMs = dhw_scenarios.dhw.properties["members"]
@@ -11,7 +12,7 @@ areas = gbr_dom.loc_data.area
 all_levels = vec(collect(Iterators.product(GCMs, unique(context_layers.management_area))))
 distances = DataFrame(GCM = first.(all_levels), management_area = last.(all_levels), CID_cover = zeros(length(all_levels)), CID_dhw = zeros(length(all_levels)))
 
-for GCM in GCMs
+for (i_gcm, GCM) in enumerate(GCMs)
 
     absolute_cover = readcubedata(open_dataset(joinpath(output_path, "processed_model_outputs/median_cover_$(GCM).nc")).layer)
     relative_cover = percentage_cover_timeseries(areas, absolute_cover)[1:50, :]
@@ -42,13 +43,14 @@ for GCM in GCMs
         distances[
             (distances.GCM .== GCM) .& 
             (distances.management_area .== man_area),
-        :CID_cover] .= man_area_cid_cover 
+        :CID_cover] .= round(man_area_cid_cover, digits=2) 
 
         distances[
             (distances.GCM .== GCM) .& 
             (distances.management_area .== man_area),
-        :CID_dhw] .= man_area_cid_dhw
+        :CID_dhw] .= round(man_area_cid_dhw, digits=2)
     end
 end
 
 sort!(distances, [:management_area, :GCM])
+distances.management_area = replace.(distances.management_area, ["Management Area" => ""])

### 2025-08-09 paper/paper_draft.qmd
Add quantification of the influence of reef features on cluster assigns
Added quantification of cluster-level ~ reef factor affects (such as depth and connectivity) via a multinomial logistic regression (provided by Econometrics.jl pkg). This is an extension of binomial logistic regression.

This regression is performed individually for each GCM. Only ACCESS-ESM1-5 results are displayed in the paper.

Added table of model coefficients to the results section of paper but have not added these values into text or discussed values yet.

@@
 | Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
-|-----------------------------|----------------|-------------------------------|------------------|
+|-------------------------|--------------------|---------------------------|--------------------|
 | EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
@@
 
-**[TI and BG to flesh out]**
+**\[TI and BG to flesh out\]**
 
@@
 width="14.82cm"}
+
+```{julia}
+#| echo: false
+#| warning: false
+#| message: false
+#| results: asis
+#| label: tbl-access-esm1-5-bioregion-regression
+#| tbl-cap: Multinomial logistic regression coefficients for the statistical model containing median reef depth, natural-log total connectivity strength, natural-log source-to-sink ratio and ACCESS-ESM1-5 mean timeseries DHW value as predictor variables.
+ACCESS-ESM1-5 bioregion scale reef cluster assignment is the response variable with three levels, 'low' (regression reference level), 'medium' and 'high'.
+
+using PrettyTables, Markdown
+cd("../src")
+
+include("../src/common.jl")
+
+cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/ACCESS-ESM1-5_bioregion_cluster_regression_coefficients.csv"), DataFrame)
+cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])
+
+for name in names(cluster_regression)
+    if isa(cluster_regression[:, name], Vector{Float64})
+        cluster_regression[:, name] = round.(cluster_regression[:, name]; sigdigits=2)
+    end
+end
+
+io = IOBuffer()
+
+header = ["Response level ~ Term", "β estimate", "SE", "t-value", "Pr > |t|", "2.5%", "97.5%"]
+pretty_table(io, cluster_regression, backend = Val(:markdown), header = header)
+
+md_string = (String(take!(io)))
+Markdown.parse(md_string)
+```
 

### 2025-08-09 src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl

@@ -55,4 +55,4 @@ for (i_gcm, GCM) in enumerate(GCMs)
 end
 
 sort!(distances, [:management_area, :GCM])
-distances.management_area = replace.(distances.management_area, ["Management Area" => ""])
+distances.management_area = replace.(distances.management_area, [" Management Area" => ""])

### 2025-08-09 src/ADRIA/HighResCoralStress/7_multinomial_regression.jl

@@ -1,0 +1,35 @@
+using Econometrics, CategoricalArrays, CSV
+
+include("../../common.jl")
+
+context_layers = GDF.read(joinpath(output_path, "analysis_context_layers_carbonate.gpkg"))
+context_layers.log_so_to_si = log10.(context_layers.so_to_si)
+context_layers.log_total_strength = log10.(context_layers.total_strength)
+
+
+dhw_scenarios = open_dataset(joinpath(gbr_domain_path, "DHWs/dhwRCP45.nc"))
+GCMs = dhw_scenarios.dhw.properties["members"]
+
+for GCM in GCMs
+    context_layers[!, "$(GCM)_bioregion_cluster_cats"] = categorical(context_layers[:, "$(GCM)_bioregion_cluster_cats"])
+
+    lhs = Term(Symbol("$(GCM)_bioregion_cluster_cats"))
+    rhs_terms = [
+        Term(:depth_med),
+        Term(:log_total_strength),
+        Term(:log_so_to_si),
+        Term(Symbol("$(GCM)_mean_dhw"))
+    ]
+
+    f = FormulaTerm(lhs, sum(rhs_terms))
+
+    model = fit(
+        EconometricModel,
+        f,
+        context_layers,
+        contrasts = Dict(Symbol("$(GCM)_bioregion_cluster_cats") => DummyCoding(base = "low"))
+    )
+
+    coeftab = DataFrame(coeftable(model))
+    CSV.write(joinpath(output_path, "cluster_regression_outputs/$(GCM)_bioregion_cluster_regression_coefficients.csv"), coeftab)
+end

### 2025-08-09 paper/paper_draft.qmd
Fix missing figure references

@@
 The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
-the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and GCM
+the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and a range of  GCM
 development families \[**TI: Ben, what does "GCM development families" mean?**\]. The IPCC
@@
 possible climate futures to be explored, capturing the uncertainty in future responses to
-CO2 increases (@fig-ecs; @sfig-methods-dhws; [@grose2023; @shepherd2018]) **\[TI: Missing
-figure reference?\]**. Projections using Shared Socio-economic Pathway (SSP) 2-4.5 was used
+CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using Shared Socio-economic Pathway (SSP) 2-4.5 was used
 to represent the plausible emission pathway. It represents a moderate emissions scenario
@@
 relative severity and where results are individual GCM results are found. GCMs in context
-with assessed plausible ranges of ECS values are displayed in [@sfig-ecs] **\[TI: Missing
-figure?\]**. ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS
+with assessed plausible ranges of ECS values are displayed in [@sfig-ecs]. ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS
 values, thus results are displayed in the main text. ECS value sources: .

### 2025-08-09 paper/paper_draft.qmd
Add small details about DHW methods and make notes for self

@@
 Future projections of maximum yearly Degree Heating Weeks (DHWs) for each reef were
-estimated from Sea Surface Temperature (SST) data for the GBR. Statistically downscaled 1km
-resolution SST data for five Global Climate Models (GCMs) were obtained from the
+estimated from Sea Surface Temperature (SST) data for the GBR. Statistically downscaled
+1km^2^ resolution SST data for five Global Climate Models (GCMs) were obtained from the
 HighResCoralStress database [@dixon2022; @dixon2023]. These five GCMs were EC-Earth3-Veg,
@@
 The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
-the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and a range of  GCM
-development families \[**TI: Ben, what does "GCM development families" mean?**\]. The IPCC
-defines ECS as the long term warming caused by a doubling of carbon dioxide above its
+the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and a range of
+GCM development families \[**TI: Ben, what does "GCM development families" mean?**\]. The
+IPCC defines ECS as the long term warming caused by a doubling of carbon dioxide above its
 pre-industrial concentration [@forster2021]. The five GCMs therefore allow for a range of
 possible climate futures to be explored, capturing the uncertainty in future responses to
-CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using Shared Socio-economic Pathway (SSP) 2-4.5 was used
-to represent the plausible emission pathway. It represents a moderate emissions scenario
-with continued CO2 emissions comparable to present day until 2050, after which emissions
-gradually decline. Under this scenario, atmospheric concentrations approximately reach
-540ppm by 2100 [@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to
-4.31°C of global atmospheric warming in the 2081-2100 period relative to 1850-1900.
+CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using
+Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission
+pathway. It represents a moderate emissions scenario with continued CO2 emissions comparable
+to present day until 2050, after which emissions gradually decline. Under this scenario,
+atmospheric concentrations approximately reach 540ppm by 2100 [@hausfather2020; IPCC
+-@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in
+the 2081-2100 period relative to 1850-1900.
 
-DHW climatological baselines were calculated from the SST data following NOAA methodology
-[@liu2017; @skirving2020]. For each pixel of SST data, the Monthly Mean SST climatology was
-calculated by computing the mean SST value for each calendar month (January through
-December) across the 28-year baseline period from 1985 to 2012. This climatological baseline
-was then temporally adjusted to center at year 1988.2857, which represents the midpoint of
-the reference period and accounts for any long-term trends within the baseline years
-themselves. The adjustment ensures that the climatology represents conditions at a specific
-temporal reference point rather than being influenced by gradual warming or cooling trends
-that may have occurred during the 1985-2012 period. The resulting monthly climatologies
-serve as a standardized reference against which current SST conditions can be compared to
-identify thermal anomalies and assess coral bleaching risk, following the methodology
-established by Skirving et al. [-@skirving2020].
-
-**\[TI: Ben, could you provide more details in the paragraph above please? What resolution
-is the data in? 10m\^2?\]**
+Monthly mean SST climatological baselines, for each 1km^2^ pixel, were calculated from the
+daily SST data following NOAA methodology [@liu2017; @skirving2020]. For each pixel of SST
+data, the Monthly Mean SST climatology was calculated by computing the mean SST value for
+each calendar month (January through December) across the 28-year baseline period from 1985
+to 2012. For each month separately, this climatological baseline was then adjusted to center
+at year 1988.2857, which attempts to account for any long-term trends within the baseline
+years themselves (see Skirving et al. [@skirving2020]). The adjustment ensures that the
+climatology represents conditions at a specific temporal reference point rather than being
+influenced by gradual warming or cooling trends that may have occurred during the 1985-2012
+period. The resulting monthly climatologies serve as a standardized reference against which
+current SST conditions can be compared to identify thermal anomalies and assess coral
+bleaching risk, following the methodology established by Skirving et al. [-@skirving2020].
 
@@
 a pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean
-temperature). This approach uses the annual maximum temperature as the baseline because
-corals are adapted to withstand their local warmest conditions under normal seasonal cycles.
-When temperatures exceed this seasonal maximum, corals experience thermal stress that can
-lead to bleaching. Only positive anomalies are considered relevant for coral stress, as
-temperatures below the seasonal maximum do not contribute to bleaching risk.
+SST). This approach uses the annual maximum temperature as the baseline because corals are
+adapted to withstand their local warmest conditions under normal seasonal cycles. When
+temperatures exceed this seasonal maximum, corals experience thermal stress that can lead to
+bleaching. Only positive anomalies are considered relevant for coral stress, as temperatures
+below the seasonal maximum do not contribute to bleaching risk.
 
-DHW values on a per-pixel basis were then calculated as the 12-week rolling sum of positive
-HotSpot SST Anomaly values, expressed in units of °C-weeks. The 12-week accumulation period
-reflects the cumulative nature of coral thermal stress. Brief temperature spikes may be
-tolerable, but sustained or repeated exposure to elevated temperatures causes progressively
-greater physiological stress and bleaching severity. DHW values integrate both the magnitude
-and duration of thermal stress: a moderate anomaly (e.g., 1°C) sustained for 12 weeks
-produces the same DHW value as a severe anomaly (e.g., 3°C) lasting 4 weeks, though the
-biological impacts may differ. DHW estimates for each indicative reef (see @greatba2022)
-were then determined by taking the mean DHW value for all pixels within each reef outline.
-
-**\[TI: Ben, I did my best to expand on DHW calculations and detail HotSpot SST anomaly,
-could you please check?\]**
+DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week
+rolling sum of positive HotSpot SST Anomaly values, expressed in units of °C-weeks. The
+12-week accumulation period reflects the cumulative nature of coral thermal stress. Brief
+temperature spikes may be tolerable, but sustained or repeated exposure to elevated
+temperatures causes progressively greater physiological stress and bleaching severity. DHW
+values integrate both the magnitude and duration of thermal stress: a moderate anomaly
+(e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly (e.g.,
+3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for each
+indicative reef (see @greatba2022) were then determined by taking the mean DHW value for all
+pixels touching each reef outline.
 
@@
 | Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
-|-------------------------|--------------------|---------------------------|--------------------|
+|------------------------|----------------------|--------------------------|----------------------|
 | EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
@@
 relative severity and where results are individual GCM results are found. GCMs in context
-with assessed plausible ranges of ECS values are displayed in [@sfig-ecs]. ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS
-values, thus results are displayed in the main text. ECS value sources: .
+with assessed plausible ranges of ECS values are displayed in [@sfig-ecs]. ACCESS-ESM1-5 is
+taken as an intermediate model based on the range of ECS values, thus results are displayed
+in the main text. ECS value sources: .
 :::
@@
 
+\[**BG: Need to add quantification results to text for timeseries differences.**\]
+
 ## Bioregion scale clustering
@@
 ```
+
+\[**BG: Need to add quantification results to text for regressions.**\]
 

### 2025-08-09 paper/paper_draft.qmd
Updated number of reefs and citations
@ConnectedSystems I have made a couple of new comments about depth numbers

@@
 The spatial extent of the GBR reefs represented in this investigation follows the reef
-definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. An
-indicative map of the GBR marine park including the Marine Park regions and which bioregion
-each reef belongs to is shown in @fig-region-map. In total, the dataset represents 3806 reef
-areas across the GBR marine park. Reefs that are outside the GBRMPA management areas or are
-not associated with a GBRMPA reefal bioregion **\[TI: Ben, cite the bioregion data
-source\]** were removed from the investigation, leaving 3531 reefs. Annually and spatially
-averaged Degree Heating Week (DHW) data were used to represent future thermal stress at each
-reef location. Code used to calculate DHW data and perform analyses involved in this
-investigation can be found at **insert repo citation**.
+definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
+[@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park
+management regions and which reefal bioregion each reef belongs to is shown in
+@fig-region-map [@GBRMPA2024; @GBRMPA2001]. This investigation adopts the GBR reef definition
+used in Bozec et al. [-@bozec2025], which includes 3806 reefs across the GBR. Reefs that are not
+associated with GBRMPA management areas or reefal bioregions were removed from the
+investigation. Additionally, reefs with poor quality bathymetry data coverage or fewer than
+three reefs per bioregion were removed from analyses (see Methods - Depth estimation). As a
+result, a total of 2429 individual reefs were included in this investigation. Annually and
+spatially averaged Degree Heating Week (DHW) data were used to represent future thermal
+stress at each reef location. Code used to calculate DHW data and perform analyses involved
+in this investigation can be found at **insert repo citation**.
+
+\[**BG: Updated number of reefs and introduced original set of reefs with 3806 to set scene for justified removal of reefs.**\]
+
+\[**BG: I am having issues with citations not appearing for datasets like GBRMPA ones.**\]
 
@@
 represents the Townsville/Whitsunday management area and the blue polygon represents the
-Mackay/Capricorn management area. The centroid of each reef is represented as a point for
-visual clarity, and is coloured according to its GBRMPA reefal bioregion. An annotation
-represents the approximate location of the Australian Institute of Marine Science Townsville
-site at Cape
-Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}
+Mackay/Capricorn management area [@GBRMPA2024]. The centroid of each reef is represented as a
+point for visual clarity, and is coloured according to its GBRMPA reefal bioregion
+[@GBRMPA2001]. All 2429 reefs included in this investigation are represented in this figure. An
+annotation represents the approximate location of the Australian Institute of Marine Science
+Townsville site at Cape Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}
 
@@
 GCMs for the region. An overview of the selected GCMs are provided in @tbl-gcms. The process
-described herein was conducted for all reefs within the GBR Marine Park to create DHW
-projections spanning from 2025 to 2075.
+described herein was conducted for all 2429 reefs to create DHW projections spanning from
+2025 to 2075.
 
@@
 3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for each
-indicative reef (see @greatba2022) were then determined by taking the mean DHW value for all
+indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for all
 pixels touching each reef outline.
@@
 | Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
-|------------------------|----------------------|--------------------------|----------------------|
+|-----------------------|-----------------------|-------------------------|-----------------------|
 | EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
@@
 Reef depth characteristics were extracted using 10m resolution bathymetry data from the
-Great Barrier Reef Marine Park Authority (GBRMPA [-@gbr10gb2020]). For each reef, bathymetry
+Great Barrier Reef Marine Park Authority (GBRMPA [-@GBRMPA2020]). For each reef, bathymetry
 data (in raster format) were spatially matched with reef polygon features through geometric
@@
 5% of the reef polygon area. These reefs with insufficient data coverage were removed from
-analyses (842 reefs of 3806 reefs, or 22%) **\[TI: BG to update\]**.
+analyses (842, or 22%, reefs of original 3806 reefs used in Bozec et al. [@bozec2025]).
+
+**\[BG: I have updated now, does it make sense referring to the original 3806 reefs (I have referred to this 3806 set of reefs in the first paragraph of the methods)?\]**
 
 While data adopted for the given assessment are said to be accurate up to 15m from Mean Sea
-Level [@gbr10gb2020], there are many sources of uncertainty in the depth estimates used for
+Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for
 this study. There is potential misalignment between GBRMPA reef outlines, as well as the
@@
 for deployment and ongoing monitoring, in combination with factors such as deployment method
-and tourism return value. Our results suggest that of the reefs analysed within the 1-10m
-depth range (1800 reefs), 74% (1328) of reefs fall into the low and medium clusters (across
-all GCMs at the GBRMPA management region scale), with many unable to maintain positive
-carbonate budgets under future conditions. Reef intervention planning is a complex and
-challenging decision making process [@anthony2020], and our results suggest that deployment
-site depth is an important factor to consider when assessing the long-term resilience of
-deployment sites.
+and tourism return value. Our results suggest that of the assessed reefs ocurring within the
+1-10m depth range (1736 reefs), 62% (1082) of reefs fall into the low and medium clusters
+(across all GCMs at the GBRMPA management region scale), with many unable to maintain
+positive carbonate budgets under future conditions. Reef intervention planning is a complex
+and challenging decision making process [@anthony2020], and our results suggest that
+deployment site depth is an important factor to consider when assessing the long-term
+resilience of deployment sites.
 

### 2025-08-09 paper/paper_draft.qmd
auto-format

@@
 definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
-[@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park
-management regions and which reefal bioregion each reef belongs to is shown in
-@fig-region-map [@GBRMPA2024; @GBRMPA2001]. This investigation adopts the GBR reef definition
-used in Bozec et al. [-@bozec2025], which includes 3806 reefs across the GBR. Reefs that are not
+[@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park management
+regions and which reefal bioregion each reef belongs to is shown in [@fig-region-map;
+@GBRMPA2024; @GBRMPA2001]. This investigation adopts the GBR reef definition used in Bozec
+et al. [-@bozec2025], which includes 3806 reefs across the GBR. Reefs that are not
 associated with GBRMPA management areas or reefal bioregions were removed from the
@@
 
-\[**BG: Updated number of reefs and introduced original set of reefs with 3806 to set scene for justified removal of reefs.**\]
+\[**BG: Updated number of reefs and introduced original set of reefs with 3806 to set scene
+for justified removal of reefs.**\]
 
@@
 represents the Townsville/Whitsunday management area and the blue polygon represents the
-Mackay/Capricorn management area [@GBRMPA2024]. The centroid of each reef is represented as a
-point for visual clarity, and is coloured according to its GBRMPA reefal bioregion
-[@GBRMPA2001]. All 2429 reefs included in this investigation are represented in this figure. An
-annotation represents the approximate location of the Australian Institute of Marine Science
-Townsville site at Cape Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}
+Mackay/Capricorn management area [@GBRMPA2024]. The centroid of each reef is represented as
+a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion
+[@GBRMPA2001]. All 2429 reefs included in this investigation are represented in this figure.
+An annotation represents the approximate location of the Australian Institute of Marine
+Science Townsville site at Cape
+Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}
 
@@
 | Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
-|-----------------------|-----------------------|-------------------------|-----------------------|
+|-----------------------|-----------------------|------------------------|-----------------------|
 | EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
@@
 
-**\[BG: I have updated now, does it make sense referring to the original 3806 reefs (I have referred to this 3806 set of reefs in the first paragraph of the methods)?\]**
+**\[BG: I have updated now, does it make sense referring to the original 3806 reefs (I have
+referred to this 3806 set of reefs in the first paragraph of the methods)?\]**
 

### 2025-08-09 paper/paper_draft.qmd
95th percentile description

@@
 represents the Townsville-Whitsunday management area. Solid lines represent the
-management-area median timeseries and bands represent the 2.5 to 97.5 percentile confidence
+management-area median timeseries and bands represent the 95th percentile confidence
 intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
@@
 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
-represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
-represented five times (for each GCM), with each GCM displayed
+represent the 95th percentile confidence intervals. Each management area is represented five
+times (for each GCM), with each GCM displayed
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
@@
 2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
-represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
-represented five times (for each GCM), with each GCM displayed
+represent the 95th percentile confidence intervals. Each management area is represented five
+times (for each GCM), with each GCM displayed
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories

### 2025-08-09 paper/paper_draft.qmd
Fix typo and more "natural" description of nlog scale
Correct typo: assignemnt -> assignment

Correct grammar: "source - to - sink" (using em dash, with space) to "source-to-sink" (en dash, no space).

@@
 ![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
-Green indicates a low cover cluster assignemnt, orange represents a medium cover assignment
+Green indicates a low cover cluster assignment, orange represents a medium cover assignment
 and blue represents assignment of a reef to a high coral cover cluster. The vertical width
@@
 2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef log (natural)
+Bracketed x-axis values represent the Spearman's correlation between reef natural log of
 total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. Point colour represents log (natural) scaled reef total connectivity strength.
-Displays results from median timeseries using
+threshold. Colour of each point represents the natural log of scaled reef total connectivity
+strength. Displays results from median timeseries using
 ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
@@
 clusters with the highest median area-relative cover between 2030 and 2040 within each
-bioregion. Solid lines represent the cluster median timeseries and bands represent the 2.5
-to 97.5 percentile confidence intervals. Displays results for ACCESS-ESM1-5
+bioregion. Solid lines represent the cluster median timeseries and bands represent the 95th
+percentile confidence intervals. Displays results for ACCESS-ESM1-5
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
@@
 
-![Log (natural) source – to – sink connectivity ratios for reefs within each bioregion,
+![Source-to-sink connectivity ratios (in natural log scale) for reefs within each bioregion,
 separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
@@
 the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines within each violin represent the median log (natural) source – to – sink ratio for
-each cluster and grey points represent the ratio value for each reef. Vertical grey lines
-represent a log (natural) source – to – sink ratio of 0 indicating equal outgoing and
-incoming connectivity levels. Displays results for ACCESS-ESM1-5
+lines within each violin represent the median source-to-sink ratio for each cluster and grey
+points represent the ratio value for each reef. Vertical grey lines represent a
+source-to-sink ratio of 0 (in natural log scale) indicating equal outgoing and incoming
+connectivity levels. Displays results for ACCESS-ESM1-5
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
@@
 
-![Log (natural) total connectivity strength for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines within each
-violin represent the median log (natural) total connectivity strength for each cluster.
-Displays results for ACCESS-ESM1-5
+![Total connectivity strength (in natural log scale) for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2040 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+lines within each violin represent the median natural log of total connectivity strength for
+each cluster. Displays results for ACCESS-ESM1-5
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity

### 2025-08-10 paper/paper_draft.qmd
Fix typo
Update new results filename to match regression outputs

@@
 
-cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/ACCESS-ESM1-5_bioregion_cluster_regression_coefficients.csv"), DataFrame)
+cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/bioregion_cluster_regression_coefficients.csv"), DataFrame)
 cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])
@@
 coral cover exceeding levels likely required to maintain positive carbonate budgets.
-Movement of shallow reefs towards negative cabonate budgets in the future may contribute to
+Movement of shallow reefs towards negative carbonate budgets in the future may contribute to
 phase shifts in reef dominant CaCO~3~ production. Shifting from coral driven to encrusting

### 2025-08-10 paper/paper_draft.qmd
Update reef description section

@@
 
-## Reef representations
+## Reef definitions
 
@@
 [@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park management
-regions and which reefal bioregion each reef belongs to is shown in [@fig-region-map;
-@GBRMPA2024; @GBRMPA2001]. This investigation adopts the GBR reef definition used in Bozec
-et al. [-@bozec2025], which includes 3806 reefs across the GBR. Reefs that are not
-associated with GBRMPA management areas or reefal bioregions were removed from the
-investigation. Additionally, reefs with poor quality bathymetry data coverage or fewer than
-three reefs per bioregion were removed from analyses (see Methods - Depth estimation). As a
-result, a total of 2429 individual reefs were included in this investigation. Annually and
-spatially averaged Degree Heating Week (DHW) data were used to represent future thermal
-stress at each reef location. Code used to calculate DHW data and perform analyses involved
-in this investigation can be found at **insert repo citation**.
+areas [@GBRMPA2024] and the corresponding bioregion for each reef is shown in
+[@fig-region-map; @GBRMPA2001]. This investigation adopts the GBR reef outlines as published
+by GBRMPA [-@GBRMPA2022], which defines 3806 reefs across the GBR.
 
-\[**BG: Updated number of reefs and introduced original set of reefs with 3806 to set scene
-for justified removal of reefs.**\]
+Depth characteristics for each reef were extracted using 10m resolution bathymetry data made
+available in GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched
+with the 3806 reef outlines through geometric intersection analysis. Depth values within
+each reef polygon were summarized using zonal statistics to calculate minimum, mean, median,
+maximum, and standard deviation of depth values. All depth values were converted to positive
+values (depths below sea level). The median depth was used to provide an indicative depth
+value for each reef. Code, and the resulting depth estimates, are available at **\[cite
+Canonical Reefs repo\]**.
+
+While data adopted for the given assessment are said to be accurate up to 15m from Mean Sea
+Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for
+this study. These are outlined further in the Discussion. Notably, the adopted depth
+estimates were derived from bathymetries based on satellite imagery. Available data can be
+limited in their alignment with the established GBRMPA reef outlines used to characterise
+reef locations. Quality control flags were assigned to identify potential data limitations:
+reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level
+(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
+5% of the reef polygon area. This removed 842 reefs, or 22%, from the initial set of 3806
+reefs. Furthermore, reefs that are not associated with GBRMPA management areas [@GBRMPA2024]
+or reefal bioregions [@GBRMPA2001] were also removed from the investigation. Bioregions
+which contained fewer than three reefs were also excluded. As a result, 1377 reefs were
+excluded (36%), leaving a total of 2429 remaining for the purpose of this investigation.
 
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points). The green polygon represents the Far Northern management area,
-the yellow polygon represents the Cairns/Cooktown management area, the pink polygon
-represents the Townsville/Whitsunday management area and the blue polygon represents the
-Mackay/Capricorn management area [@GBRMPA2024]. The centroid of each reef is represented as
-a point for visual clarity, and is coloured according to its GBRMPA reefal bioregion
-[@GBRMPA2001]. All 2429 reefs included in this investigation are represented in this figure.
-An annotation represents the approximate location of the Australian Institute of Marine
-Science Townsville site at Cape
-Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map}
+considered reefs (points). Colour-coded areas outline GBR marine park management regions,
+where green represents the Far Northern management region, yellow represents
+Cairns/Cooktown, pink covers Townsville/Whitsunday and blue covers Mackay/Capricorn
+[@GBRMPA2024]. Reef centroids are marked individually for visual clarity, and are coloured
+according to its bioregion [@GBRMPA2001]. All 2429 reefs included in this investigation are
+represented in this figure. An annotation represents the approximate location of the
+Australian Institute of Marine Science Townsville site at Cape
+Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
+fig-align="center" width="14.8cm"}
 

### 2025-08-10 paper/paper_draft.qmd
Placeholder for citation to Canonical Reefs

@@
 GCMs for the region. An overview of the selected GCMs are provided in @tbl-gcms. The process
-described herein was conducted for all 2429 reefs to create DHW projections spanning from
-2025 to 2075.
+described here was conducted for all 2429 reefs to create DHW projections spanning from 2025
+to 2075. Code used to calculate DHW data and perform analyses involved in this investigation
+can be found at **insert repo citation**.
 

### 2025-08-10 paper/paper_draft.qmd
Add note for @eco-ben

@@
 
-## Depth estimation
-
+**\[TI: Ben, best to use the same colours consistently for each management region. Blue,
+yellow/orange, green and pink were used in for the map.\]**
 Reef depth characteristics were extracted using 10m resolution bathymetry data from the

### 2025-08-10 paper/paper_draft.qmd
Draft restructure of assessment methods section

@@
 yellow/orange, green and pink were used in for the map.\]**
-Reef depth characteristics were extracted using 10m resolution bathymetry data from the
-Great Barrier Reef Marine Park Authority (GBRMPA [-@GBRMPA2020]). For each reef, bathymetry
-data (in raster format) were spatially matched with reef polygon features through geometric
-intersection analysis. Depth values within each reef polygon were summarized using zonal
-statistics to calculate minimum, mean, median, maximum, and standard deviation of depth
-values. All depth values were converted to positive values (depths below sea level). The
-median depth was used to provide an indicative depth value for each reef.
 
-As bathymetry data are derived from satellite imagery they can be limited in their alignment
-with the established GBRMPA reef outlines used in the investigation to characterise reef
-locations. Quality control flags were assigned to identify potential data limitations: reefs
-with no overlapping bathymetry data, reefs with minimum depth values above sea level
-(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
-5% of the reef polygon area. These reefs with insufficient data coverage were removed from
-analyses (842, or 22%, reefs of original 3806 reefs used in Bozec et al. [@bozec2025]).
+## Assessment framework
 
-**\[BG: I have updated now, does it make sense referring to the original 3806 reefs (I have
-referred to this 3806 set of reefs in the first paragraph of the methods)?\]**
+An exploratory scenario modelling approach is adopted for this investigation. The method
+involves exploring a wide range of plausible futures under different assumptions of
+environmental (climatic) conditions and ecological factors. Exploratory scenario modelling
+embraces uncertainty as an inherent characteristic of complex environmental systems
+[@lempert2010] and is a core methodology underpinning the development of robust and adaptive
+management strategies [@haasnoot2013].
 
-While data adopted for the given assessment are said to be accurate up to 15m from Mean Sea
-Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for
-this study. There is potential misalignment between GBRMPA reef outlines, as well as the
-usual challenges of deriving data from satellite imagery. In the case of bathymetry,
-estimates are subject to different bottom types (rock, sand, seagrass, etc) and how these
-affect reflectance, the water penetration depth of satellite sensors, influence of local
-conditions (e.g., turbidity and wave activity), and many other factors. The resulting depth
-estimates are therefore highly uncertain themselves and are only adopted as a useful
-indication rather than an accurate and precise report of reef depths across the GBR.
+Exploratory modelling approaches have gained favour in recent years as precise long-term
+predictions of future conditions are often impossible in complex systems like coral reefs.
+Multiple interacting and compounding sources of uncertainty, and a lack of broad agreement
+as to their likelihood, create inherently uncertain outcomes. Rather than attempting to
+forecast specific outcomes, exploratory modelling aims to systematically explore many
+possible futures to identify patterns and, in management contexts, robust strategies that
+perform well across those diverse conditions, as well as conditions in which such strategies
+may fail. Such an exploratory approach lends itself well to the purpose of the
+investigation. Specifically, to assess the role of DHW, connectivity, and depth to identify
+the environmental and reef characteristics that support structural resilience.
 
-**\[TI: TODO cite Canonical Reefs repository\]**
+To apply exploratory scenario modelling, the approach employed a modelling framework
+involving two separate systems: ADRIA (the Adaptive Dynamic Reef Interventin Algorithms
+platform) and CoralBlox. ADRIA is a multi-criteria decision support platform designed to
+help reef managers address climate change challenges in coral reef systems [@iwanaga2023].
+The ADRIA platform provides functionality for scenario generation and analysis as well as
+providing the technical infrastructure to couple environmental and ecosystem
+representations.
 
-## ADRIA-CoralBlox modelling
+CoralBlox is a computationally efficient coral population model. It simulates
+functional/morphological groups of corals over its life cycle, competing for available space
+over time [@ribeirodealmeida2024]. The coupled framework is referred to as ADRIA-CoralBlox.
+The coral demographic representation and associated model implementation are further
+detailed in the supplementary material.
 
-ADRIA.jl is a decision support platform that combines scenario analysis with biotic and
-abiotic processes such as bleaching responses, thermal tolerance and flows of larvae between
-reefs [@iwanaga2023]. CoralBlox.jl is a coral population growth and mortality model that
-simulates groups of corals growing in diameter and competing for limited space over time
-[@ribeirodealmeida2024]. We combine these tools to model the populations of corals across
-the GBR. Details on how coral demographic processes are implemented in ADRIA - CoralBlox can
-be found in the supplementary material.
-
-### TODO: Section on scenario modelling
+### Scenario modelling
 

### 2025-08-10 paper/paper_draft.qmd
auto-format and figure alignment

@@
 header = ["GCM", "Management area", "CID - cover", "CID - DHW"]
-pretty_table(io, distances, backend = Val(:markdown), header = header)
+pretty_table(io, distances, backend=Val(:markdown), header=header)
 
@@
 header = ["Response level ~ Term", "β estimate", "SE", "t-value", "Pr > |t|", "2.5%", "97.5%"]
-pretty_table(io, cluster_regression, backend = Val(:markdown), header = header)
+pretty_table(io, cluster_regression, backend=Val(:markdown), header=header)
 
@@
 2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
-width="10cm"}
+fig-align="center" width="10cm"}
+
+![Depth cutoff for reefs](images/reef_depth_included_cutoff.png){#sfig-depth-cutoff
+fig-align="center" width="14.8cm" height="9.5cm"}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
-![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
-Green indicates a low cover cluster assignment, orange represents a medium cover assignment
-and blue represents assignment of a reef to a high coral cover cluster. The vertical width
-of reef elements varies depending on the number of reefs within the bioregion (displayed in
-the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
-ACCESS-CM2, NorESM2-MM and
+![![](images/paste-1.png)Heatmaps indicating reef cluster assignments within each bioregion
+across the five GCMs. Green indicates a low cover cluster assignment, orange represents a
+medium cover assignment and blue represents assignment of a reef to a high coral cover
+cluster. The vertical width of reef elements varies depending on the number of reefs within
+the bioregion (displayed in the y axis). The x axis represents the different GCM levels
+(EC-Earth3-Veg, ACCESS-ESM1-5, ACCESS-CM2, NorESM2-MM and
 GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
-width="14.82cm"}
+fig-align="center" width="14.82cm"}

### 2025-08-10 paper/paper_draft.qmd
Add limitation section

@@
 
+## Limitations
+
 There are multiple caveats in how coral ecosystem dynamics are modelled in this
@@
 suggest the factors that influence reef resilience are consistent across these scenarios.
+
+Additionally, it is currently not possible to obtain highly accurate and precise estimates
+of reef depth at the GBR-scale. Data adopted for the given assessment are said to be
+accurate up to 15m from Mean Sea Level [@GBRMPA2020], however there are many sources of
+uncertainty in the depth estimates used for this study. Satellite-derived estimates are
+subject to different bottom types (rock, sand, seagrass, etc) and how these affect
+reflectance, the water penetration depth of satellite sensors, influence of local conditions
+(e.g., turbidity and wave activity), among many other factors.
+
+In addition to the usual challenges of deriving data from satellite imagery, it is
+acknowledged that there is high potential for misalignment between the bathymetry data and
+GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton], for example, identified 120 false
+positives, where features identified as reefs were in actuality sand banks or rocky reefs
+(rather than coral reefs). Reefs with bathymetry data of less than 5% of its indicative area
+were excluded from analysis to ensure analyses were not conducted on reefs with no data
+coverage (see @sfig-depth-cutoff). The existing GBRMPA reef outlines were adopted to align
+with other ongoing modelling and analyses conducted as part of the Reef Restoration and
+Adaptation Program (RRAP; <https://gbrrestoration.org>) **\[TODO: PROPER CITATION OF
+RRAP\]**. The median depths for each indicative reef area were extracted from bathymetry
+data using zonal statistics and depth values beyond the 15m range were included. The
+resulting depth estimates are therefore highly uncertain and are only adopted as a useful
+indication for the purpose of the presented analysis. They are not intended to be an
+accurate and precise report of reef depths across the GBR.
+
+**\[TODO - rewrite/expand paragraphs below for flow\]**
 

### 2025-08-10 paper/paper_draft.qmd
Center figure

@@
 intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 
-cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/bioregion_cluster_regression_coefficients.csv"), DataFrame)
+cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/ACCESS-ESM1-5_bioregion_cluster_regression_coefficients.csv"), DataFrame)
 cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])
@@
 
-## ADRIA - CoralBlox
+## ADRIA-CoralBlox
 

### 2025-08-10 paper/paper_draft.qmd
Re-order and flesh out sections
Added an initial stub in supplementary to describe model parameterisation and sampling.

@@
 
+### Scenario modelling
+
 To apply exploratory scenario modelling, the approach employed a modelling framework
@@
 providing the technical infrastructure to couple environmental and ecosystem
-representations.
+representations. CoralBlox is a computationally efficient coral population model. It
+simulates functional/morphological groups of corals over its life cycle, competing for
+available space over time [@ribeirodealmeida2024]. The coupled framework is referred to as
+ADRIA-CoralBlox.
 
-CoralBlox is a computationally efficient coral population model. It simulates
-functional/morphological groups of corals over its life cycle, competing for available space
-over time [@ribeirodealmeida2024]. The coupled framework is referred to as ADRIA-CoralBlox.
 The coral demographic representation and associated model implementation are further
-detailed in the supplementary material.
+detailed in the supplementary material. Of important note, however, is that the
+representation of bleaching mortalities follow Bozec et al., [-@bozec2022] albeit with a
+scaling coefficient to incorporate the amelioration effect that depth may have, following
+Baird et al., [@baird2018]. The scaling reduces the proportion of coral colonies impacted by
+high heat stress as depth increases. Tropical cyclones and impact of wave activity on reefs
+were not included in this investigation.
 
-### Scenario modelling
+ADRIA-CoralBlox was run for 4096 scenarios for each of the five GCMs (20,480 total model
+runs). Here, a scenario represents a unique combination of assumed environmental (namely one
+of the five DHW trajectories) and ecological factors including coral growth and mortality
+rates, coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol'
+sampling method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi
+Monte Carlo approach which balances scenario exploration with improved convergence
+properties (compared to pseudo-random sampling). A detailed comparative analysis of the
+sampling methods can be found in [@kucherenko2015].
 
-**\[TI and BG to flesh out\]**
-
-For each GCM, ran 4096 reference scenarios ("counterfactuals")...
-
-### Factors influencing bleaching mortality
-
-In ADRIA we track the thermal tolerance of each functional group and size class as a
-truncated normal distribution that is updated in each timestep following growth and
-recruitment. This distribution determines the proportion of the population on a reef that is
-susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
-Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
-[-@bairos-novak2021].
-
-Tropical cyclones and impact of wave activity to reefs were not included in this
-investigation. We scale coral bleaching impacts by a coefficient determined by the median
-depth of each reef location, following Baird et al. [@baird2018], reducing the proportion of
-coral colonies on a reef impacted by high heat stress as depth increases.
-
-### Connectivity modelling
-
-\*\* need information on GBR1 connectivity used \*\*
-
-Connectivity data from 24 days in total were used in this investigation. These data span six
-years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices,
-while 2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity
-strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
-location (i.e., all 24 days). While the connectivity strengths do not vary from year to year
-within the simulation, they do vary between reefs of varying sizes, providing sufficient
-heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
-spatial variability also enables investigations into the influence of connectivity strength
-and its role in driving recovery processes.
-
-## Timeseries analysis
-
-ADRIA-CoralBlox was run for 4096 **sampled** scenarios for each of the five GCMs (20,480
-total model runs). A median absolute coral cover timeseries for each reef was calculated for
-each GCM. For timeseries clustering reef cover timeseries were scaled by the total area of
-the reef to represent cover as a percentage of the total reef area. The proportion of each
-functional group occupying the reef (group evenness) was also investigated as a metric for
-timeseries analysis, but was found to not sufficiently capture the declined condition of
-reefs suffering from very low absolute coral cover.
-
-### Carbonate budget analysis
-
-Using median coral cover timeseries for each reef we calculated the number of years each
-reef maintains coral cover above a given percent threshold. The threshold represents the
-level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
-$\beta_{0}$ to indicate the budget equilibrium). Greater number of years above $\beta_{0}$
-therefore suggests greater resilience and opportunity for recovery.
-
-Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
-[@desbiens2021]. Given in situ carbonate budgets are influenced by (1) a range of processes;
-(2) the variety of approaches that could be used to measure those processes; and (3) the
-uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
-single precise $\beta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
-$\beta_{0}$ value for each individual reef.
-
-Given the uncertainties present, the proportion of reefs that display capacity to maintain
-coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of 10 to
-20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
-[-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of the
-lower and upper bounds respectively. Robustness of the conclusions drawn to the uncertainty
-in the precise value of $\beta_{0}$ for all reefs can then be assessed by using the
-indicative range.
-
-The relationship between the number of years above $\beta_{0}$ and median reef depth was
-then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
-adopted as reef depth and connectivity strength distributions are expected to be non-normal
-and highly skewed. Furthermore, reefs are naturally of different types and experience
-different conditions, and so the monotonic trends (whether the relationship consistently
-increase or decrease) rather than the exact quantative relationship is of interest.
+For the purpose of scenario assessment, the resulting timeseries for each model run were
+scaled by the total area of the reef to represent cover as a percentage of the total
+estimated reef area. The proportion of each functional group occupying the reef (group
+evenness) was also investigated as a metric for timeseries analysis, but was found to not
+sufficiently capture the declined condition of reefs suffering from very low absolute coral
+cover **\[TI: Ben, is the sentence here really important to include?\]**. These timeseries
+of coral cover were then clustered based on their temporal behaviour.
 
@@
 under each GCM.
+
+### Carbonate budget analysis
+
+Using median coral cover timeseries for each reef we calculated the number of years each
+reef maintains coral cover above a given percent threshold. The threshold represents the
+level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
+$\beta_{0}$ to indicate the budget equilibrium). Greater number of years above $\beta_{0}$
+therefore suggests greater resilience and opportunity for recovery.
+
+Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
+[@desbiens2021]. Given in situ carbonate budgets are influenced by (1) a range of processes;
+(2) the variety of approaches that could be used to measure those processes; and (3) the
+uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
+single precise $\beta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
+$\beta_{0}$ value for each individual reef.
+
+Given the uncertainties present, the proportion of modelled reefs that display capacity to
+maintain coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of
+10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
+al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of
+the lower and upper bounds respectively. Robustness of the conclusions drawn to the
+uncertainty in the precise value of $\beta_{0}$ for all reefs can then be assessed by using
+the indicative range.
+
+The relationship between the number of years above $\beta_{0}$ and median reef depth was
+then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
+adopted as reef depth and connectivity strength distributions are expected to be non-normal
+and highly skewed. Furthermore, reefs are naturally of different types and experience
+different conditions, and so the monotonic trends (whether the relationship consistently
+increase or decrease) rather than the exact quantative relationship was of interest for this
+analysis.
+
+### Connectivity modelling
+
+\*\* need information on GBR1 connectivity used \*\*
+
+Connectivity data from 24 days in total were used in this investigation. These data span six
+years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices,
+while 2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity
+strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
+location (i.e., all 24 days). While the connectivity strengths do not vary from year to year
+within the simulation, they do vary between reefs of varying sizes, providing sufficient
+heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
+spatial variability also enables investigations into the influence of connectivity strength
+and its role in driving recovery processes.
 
@@
 
+### Scenario generation
+
+Scenarios were sampled from the range of environmental and ecological factors using the
+low-discrepancy Sobol' sampling method [@sobol1967; @sobol1993] with Owen scrambling
+[@owen1995]. A base of 2 and padding of 32 is used for the Owen scrambling. Ecological
+factors were sampled using a +/- 10% range relative to their nominal (assumed best guess)
+value.
+
 ### Model parameterisation
@@
 ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
+
+**Bleaching mortality**
+
+In ADRIA we track the thermal tolerance of each functional group and size class as a
+truncated normal distribution that is updated in each timestep following growth and
+recruitment. This distribution determines the proportion of the population on a reef that is
+susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
+Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
+[-@bairos-novak2021].
 

### 2025-08-10 paper/paper_draft.qmd
Center figures

@@
 ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 
@@
 horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 

### 2025-08-10 paper/paper_draft.qmd
Minor tweak to wording

@@
 limited in their alignment with the established GBRMPA reef outlines used to characterise
-reef locations. Quality control flags were assigned to identify potential data limitations:
-reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level
-(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
-5% of the reef polygon area. This removed 842 reefs, or 22%, from the initial set of 3806
-reefs. Furthermore, reefs that are not associated with GBRMPA management areas [@GBRMPA2024]
-or reefal bioregions [@GBRMPA2001] were also removed from the investigation. Bioregions
-which contained fewer than three reefs were also excluded. As a result, 1377 reefs were
-excluded (36%), leaving a total of 2429 remaining for the purpose of this investigation.
+reef locations and their areal extent. Quality control flags were assigned to identify
+potential data limitations: reefs with no overlapping bathymetry data, reefs with minimum
+depth values above sea level (indicating potential data artifacts), and reefs where
+bathymetry pixels covered less than 5% of the reef polygon area. This removed 842 reefs, or
+22%, from the initial set of 3806 reefs. Furthermore, reefs that are not associated with
+GBRMPA management areas [@GBRMPA2024] or reefal bioregions [@GBRMPA2001] were also removed
+from the investigation. Bioregions which contained fewer than three reefs were also
+excluded. As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for
+the purpose of this investigation.
 
@@
 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-width="14.82cm"}
+fig-align="center" width="14.82cm"}
 

### 2025-08-10 paper/paper_draft.qmd
Remove unnecessary detail

@@
 pathway. It represents a moderate emissions scenario with continued CO2 emissions comparable
-to present day until 2050, after which emissions gradually decline. Under this scenario,
-atmospheric concentrations approximately reach 540ppm by 2100 [@hausfather2020; IPCC
+to present day until 2050, after which emissions gradually decline [@hausfather2020; IPCC
 -@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in

### 2025-08-10 paper/paper_draft.qmd
Add text and references on GCM development families

@@
 The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
-the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and a range of
-GCM development families \[**TI: Ben, what does "GCM development families" mean?**\]. The
-IPCC defines ECS as the long term warming caused by a doubling of carbon dioxide above its
-pre-industrial concentration [@forster2021]. The five GCMs therefore allow for a range of
-possible climate futures to be explored, capturing the uncertainty in future responses to
-CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using
-Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission
-pathway. It represents a moderate emissions scenario with continued CO2 emissions comparable
-to present day until 2050, after which emissions gradually decline [@hausfather2020; IPCC
--@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in
-the 2081-2100 period relative to 1850-1900.
+the Intergovernmental Panel on Climate Change (IPCC) assessed likely range. The IPCC defines
+ECS as the long term warming caused by a doubling of carbon dioxide above its pre-industrial
+concentration [@forster2021]. GCM development institutions regularly share aspects of model
+development. Brunner et al. [-@brunner2020] assessed the independence of 33 models,
+quantitatively classifying models into 'model development families' based on patterns in
+atmospheric temperature and sea level pressure. By selecting five GCMs for investigation
+that span a range of four 'model development families' [@brunner2020] (note: we assume
+GFDL-CM4 aligns with GFDL-ESM4; ACCESS-ESM1-5 and ACCESS-CM2 occupy the same family), we are
+able to assess climate projections over a broad range of independently derived futures
+[@abramowitz2019]. The selected GCMs therefore allow for a range of possible climate futures
+to be explored, capturing the uncertainty in future responses to CO2 increases (@sfig-ecs;
+@fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using Shared Socio-economic
+Pathway (SSP) 2-4.5 was used to represent the plausible emission pathway. It represents a
+moderate emissions scenario with continued CO2 emissions comparable to present day until
+2050, after which emissions gradually decline [@hausfather2020; IPCC -@climate2023]. The
+selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in the 2081-2100
+period relative to 1850-1900.
 
@@
 Timeseries clustering analyses were performed at the reefal bioregion scale (defined in
-\[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::reefal-marine-bioregions/about\]).
-Additional analyses were also performed at larger spatial scales, such as the GBRMPA
-management regions and whole-of-GBR scale. These were found to lead to identical conclusions
-and so are not shown here. Results of these analyses can be found at \[**insert citation for
-repository**\] for those interested.
+GBRMPA [-@GBRMPA2001]). Additional analyses were also performed at larger spatial scales,
+such as the GBRMPA management regions and whole-of-GBR scale. These were found to lead to
+identical conclusions and so are not shown here. Results of these analyses can be found at
+\[**insert citation for repository**\] for those interested.
 

### 2025-08-10 paper/paper_draft.qmd
Updated ECS values for GCMs and sources
Found an error in the GFDL-CM4 ECS value, text will need updating accordingly

@@
 ::: {#tbl-gcms}
-| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
+| Global Climate Model source | ECS value (K) | Interpreted relative severity | Results found in |
 |-----------------------|-----------------------|------------------------|-----------------------|
-| EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
-| ACCESS-CM2 | 4.72 | High | **insert repo citation** |
+| EC-Earth3-Veg | 4.30 | High | **insert repo citation** |
+| ACCESS-CM2 | 4.66 | High | **insert repo citation** |
+| GFDL-CM4 | 4.1 | High | **insert repo citation** |
 | ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
-| GFDL-CM4 | 2.9 | Low | **insert repo citation** |
 | NorESM2-MM | 2.5 | Low | **insert repo citation** |
 
-: Information for each GCM used in this investigation including ECS value, interpreted
-relative severity and where results are individual GCM results are found. GCMs in context
-with assessed plausible ranges of ECS values are displayed in [@sfig-ecs]. ACCESS-ESM1-5 is
-taken as an intermediate model based on the range of ECS values, thus results are displayed
-in the main text. ECS value sources: .
+: Information for each GCM used in this investigation including Equilibrium Climate
+Sensitivity (ECS) value, interpreted relative severity and where results are individual GCM
+results are found. GCMs in context with assessed plausible ranges of ECS values are
+displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the
+very-likely ECS range and was taken as an intermediate model with results displayed in the
+main text. ECS values obtained from: [@sentman2025; @grose2023; @seland2020; @ziehn2020;
+@wyser2020].
 :::
-
-\[**BG: Need to add my ECS value sources to table caption. (And also cite GCM paper
-sources).**\]
 

### 2025-08-10 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -12,11 +12,11 @@ context_layers = GDF.read(joinpath(output_path, "analysis_context_layers_carbona
 
 # ECS plot - methods
 ecs_values = Dict(
-    "EC-Earth3-Veg" => 4.31,
-    "ACCESS-ESM1-5" => 3.87,
-    "ACCESS-CM2" => 4.72,
-    "GFDL-CM4" => 2.9,
-    "NorESM2-MM" => 2.5
+    "EC-Earth3-Veg" => 4.30, # Wyser et al. (2020). On the increased climate sensitivity in the EC-Earth model from CMIP5 to CMIP6
+    "ACCESS-ESM1-5" => 3.87, # Ziehn et al. (2020). The Australian Earth System Model: ACCESS-ESM1.5
+    "ACCESS-CM2" => 4.66, # Grose et al. (2020). A CMIP6-based multi-model downscaling ensemble to underpin climate change services in Australia
+    "GFDL-CM4" => 4.1, # Sentman et al. (2025). Quantifying Equilibrium Climate Sensitivity to Atmospheric Chemistry and Composition Representations in GFDL-CM4.0 and GFDL-ESM4.1 
+    "NorESM2-MM" => 2.5 # Seland et al. (2020). Overview of the Norwegian Earth System Model (NorESM2) and key climate response of CMIP6 DECK, historical, and scenario simulations
 )
 ecs = ecs_plot(collect(values(ecs_values)), [2.5, 5.1], [2.1, 7.7], collect(keys(ecs_values)))
 save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit=dpi)

### 2025-08-10 src/plotting_functions.jl

@@ -231,7 +231,7 @@ function ecs_plot(
     fig = Figure(size=(fig_x_size, fig_y_size), fontsize=fontsize)
     ax = Axis(
         fig[1, 1],
-        ylabel="Equilibrium Climate Sensitivity (°C)",
+        ylabel="Equilibrium Climate Sensitivity (K)",
         height=10cm,
         width=8cm
     )

### 2025-08-10 paper/paper_draft.qmd
Adjust text to reflect the new ECS values and quantification
Reflect quantification of low-high cluster timeseries differences using CID metric.

@@
 
-## Future DHW trajectories
+## Reef trajectories across futures
 
@@
 factor are only shown for ACCESS-ESM1-5 (an intermediate Equilibrium Climate Sensitivity
-scenario). Results for the additional GCMs are displayed in the supplementary material.
-However, there are substantial differences in the longevity of reef resilience and
-maintenance of coral cover post 2030 between the GCMs, thus coral cover timeseries are
-displayed for each GCM (displayed clustered at management-area scale to preserve coarse
-spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
+scenario [@sfig-ecs]). Results for the additional GCMs can be found at \[**BG: Insert
+repository citation.**\]. However, there are substantial differences in the longevity of
+reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover
+timeseries are displayed for each GCM (displayed clustered at management-area scale to
+preserve coarse spatial differences in cover trajectories) (@fig-gcm-cover-trajectories).
 
@@
 and to a lesser degree the ‘low’ cluster, also exhibit periods of recovery and increasing
-proportions of coral cover up to 2045. Under NorESM2-MM the Far Northern management area
-does not see coral cover maintenance as high as the other management regions \[**TI:**
-**Quantify this! How did you determine this and how large/small are the difference in coral
-cover maintenance?**\]. Under the second lowest ECS projection (GFDL-CM4, 2.9°C) all
-clusters in each management area exhibit largely declining future trajectories with periods
-of recovery from 2030 to 2040. ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which
+proportions of coral cover up to 2045. Under NorESM2-MM the Far Northern management area has
+lower CID distances between low and high cover clusters than in other management areas
+[@tbl-cluster-cid], this is reflected in the low degree of cover maintainence
+[@fig-gcm-cover-trajectories]. ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which
 results in intermediate levels of coral cover maintenance (between those of lower and higher
-ECS GCMs). In Townsville-Whitsunday and Far Northern management areas, reefs in the high
-cluster are able to maintain coral cover levels around 20% to 2050 under ACCESS-ESM1-5.
-Under ACCESS-CM2 (4.72°C) and EC-Earth3-Veg (4.31°C) GCMs cover trajectories are largely
-declining in all management areas.
+ECS GCMs) [@fig-gcm-cover-trajectories], reflected in intermediate CID distance values
+within most management areas [@tbl-cluster-cid]. In Townsville-Whitsunday and Far Northern
+management areas, reefs in the high cluster are able to maintain coral cover levels around
+20% to 2050 under ACCESS-ESM1-5. Under ACCESS-CM2 (4.66K), EC-Earth3-Veg (4.30K) and
+GFDL-CM4 (4.1K) GCMs cover trajectories are largely declining in all management areas,
+reflected in lower CID distance values than other GCMs [@tbl-cluster-cid].
 
-Under each GCM, in all management areas, low, medium and high cluster reefs have low
-differences between DHW trajectories (@fig-gcm-dhw-trajectories) \[**TI:** **I don't
-understand this sentence - what is meant by reefs have low differences?**\]. The highest
-peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in
-overall DHW timeseries occur under ACCESS-CM2.
+Under each GCM, in all management areas, low, medium and high cluster reefs have low levels
+of distinction between DHW trajectories (@fig-gcm-dhw-trajectories). The highest peak DHW
+levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs
+timeseries occur under ACCESS-CM2 [@fig-methods-dhws].
 
@@
 high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). This is
-expected as spatial differences in GCM DHW timeseries result in reefs being impacted in
-different magnitudes relative to other reefs in their bioregion.
+expected as spatial differences in GCM DHW timeseries result in reefs being impacted at
+different relative magnitudes within their management area across GCMs.
 
@@
 Complexity invariant distance represents the euclidean distance between timeseries, corrected by the complexity of the two timeseries.
+CID values are used to quantify overall differences between these two cluster levels at management area and GCM levels.
 CID values for percentage cover and DHW timeseries are not directly comparable as the timeseries use different units.
@@
 ```
-
-\[**BG: Need to add quantification results to text for timeseries differences.**\]
 
@@
 maintenance into the future. Differences between low, medium and high reef clusters in cover
-timeseries are most notable under these two GCMs. Maintainance of coral cover into the
-future is not clearly linked to the Equilibrium Climate Sensitivity of each GCM used as
-ACCESS-ESM1-5 has a higher ECS value than GFDL-CM4, with reefs experiencing large continuous
-declines under GFDL-CM4. These large declines are likely due to the high peak thermal stress
-levels above 10°C-weeks experienced in the first ten years of the timeseries under GFDL-CM4.
+timeseries are most notable under these two GCMs [@tbl-cluster-cid;
+@fig-gcm-cover-trajectories]. Maintainance of coral cover into the future is linked to the
+Equilibrium Climate Sensitivity of the GCM used as levels of future recovery and timespan of
+cover maintainance increase as GCM ECS increases [@fig-gcm-cover-trajectories]. Under
+high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2) large declines and lower rates of
+recovery in high cover clusters are common compared to lower-ECS GCMs.
 
 The large differences in cover timeseries seen across the GCMs suggest that it is important
-to consider this uncertainty in future conditions when assessing possible biological
-responses to change. This is supported by recent literature suggesting an effective approach
-to capturing climate change uncertainty is to model responses using a range of GCMs
-separately [@shepherd2018]. Despite large differences in coral cover across GCMs, the
-patterns identified between low, medium and high clusters of reefs suggest that the
-importance of depth refugia is consistent across scenarios.
+to consider uncertainty in future conditions when assessing possible biological responses to
+change. This is supported by recent literature suggesting an effective approach to capturing
+climate change uncertainty is to model responses using GCMs separately [@shepherd2018].
+Despite large differences in coral cover across GCMs, the patterns identified between low,
+medium and high clusters of reefs suggest that the relative importance of environmental and
+biological factors such as depth refugia, connectivity and surface DHW levels is consistent
+across scenarios.
 

### 2025-08-10 paper/paper_draft.qmd
Add quantification of cluster assignment consistency

@@
 Comparing across GCMs, it is common for reefs to switch cluster level, including from low to
-high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). This is
-expected as spatial differences in GCM DHW timeseries result in reefs being impacted at
-different relative magnitudes within their management area across GCMs.
+high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). Of 2429
+reefs, 20% (503) of reefs have consistent management area scale cluster assignment across
+all GCMs. This high assignment variability across GCMs is expected as spatial differences in
+GCM DHW timeseries result in reefs being impacted at different relative magnitudes within
+their management area across GCMs.
 
@@
 ```
+
+\[**BG: Need to ensure that methods explain why I use CID here to quantify differences
+between low and high cluster median timeseries.**\]
 

### 2025-08-10 paper/paper_draft.qmd
Quantify average number of low clustered reefs across GCMs

@@
 
-Under all GCMs most reefs are projected to suffer substantial declines in coral cover
-relative to 2025 levels. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover
-maintenance into the future. Differences between low, medium and high reef clusters in cover
-timeseries are most notable under these two GCMs [@tbl-cluster-cid;
+Under all GCMs many reefs are projected to suffer substantial declines in coral cover
+relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the
+lowest cover level cluster across GCMs. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most
+coral cover maintenance into the future. Differences between low, medium and high reef
+clusters in cover timeseries are most notable under these two GCMs [@tbl-cluster-cid;
 @fig-gcm-cover-trajectories]. Maintainance of coral cover into the future is linked to the

### 2025-08-10 paper/paper_draft.qmd
Add quantification of consistently clustered reefs
Also justify why different clustering scales are used/displayed in results section.
Also explain that CID is used to quantify the difference between low and high clusters at management area scale under each GCM for comparisons.

--- 2025-08-10 paper/paper_draft.qmd
@@
 considered reefs (points). Colour-coded areas outline GBR marine park management regions,
-where green represents the Far Northern management region, yellow represents
-Cairns/Cooktown, pink covers Townsville/Whitsunday and blue covers Mackay/Capricorn
+where orange represents the Far Northern management region, green represents
+Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
 [@GBRMPA2024]. Reef centroids are marked individually for visual clarity, and are coloured
@@
 
-**\[TI: Ben, best to use the same colours consistently for each management region. Blue,
-yellow/orange, green and pink were used in for the map.\]**
-
 ## Assessment framework
@@
 
-Timeseries clustering analyses were performed at the reefal bioregion scale (defined in
-GBRMPA [-@GBRMPA2001]). Additional analyses were also performed at larger spatial scales,
-such as the GBRMPA management regions and whole-of-GBR scale. These were found to lead to
-identical conclusions and so are not shown here. Results of these analyses can be found at
-\[**insert citation for repository**\] for those interested.
+Timeseries clustering analyses were performed at the management area and reefal bioregion
+scale (defined in GBRMPA [-@GBRMPA2001]). Additional analyses were also performed at the
+whole-of-GBR scale. These were found to lead to identical conclusions and so are not shown
+here. To compare timeseries clustering results across GCMs, management area scale clustering
+results are used to preserve coarse scale latitudinal differences between regions, while
+maintaining ease of comparison and visualisation. These comparisons include quantification
+of differences between low and high cover clusters across management regions under each GCM
+using the Complexity-Invariant Distance between cluster median timeseries. To assess how
+different reef characteristics influence timeseries clustering at a finer scale, bioregion
+results are used to capture patterns occurring within individual clusters of reefs. Results
+of all analyses at all clustering scales can be found at \[**insert citation for
+repository**\] for those interested.
 
@@
 Under each GCM, in all management areas, low, medium and high cluster reefs have low levels
-of distinction between DHW trajectories (@fig-gcm-dhw-trajectories). The highest peak DHW
+of distinction between DHW trajectories (@sfig-gcm-dhw-trajectories). The highest peak DHW
 levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs
 timeseries occur under ACCESS-CM2 [@fig-methods-dhws].
-
-![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
-analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
-represent the 95th percentile confidence intervals. Each management area is represented five
-times (for each GCM), with each GCM displayed
-horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
-fig-align="center" width="14.82cm"}
 
@@
 Comparing across GCMs, it is common for reefs to switch cluster level, including from low to
-high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). This is
-expected as spatial differences in GCM DHW timeseries result in reefs being impacted at
-different relative magnitudes within their management area across GCMs.
+high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). Of 2429
+reefs, 20% (503) of reefs have consistent management area scale cluster assignment across
+all GCMs. Of the 503 consistently assigned reefs, 49% are within the Far Northern management
+area, with 7, 13 and 31% occurring in the Cairns/Cooktown, Townsville/Whitsunday and
+Mackay/Capricorn management areas respectively [@sfig-gcm-cluster-map]. Of the 503
+consistently assigned reefs, 32, 7 and 61% are clustered into low, medium and high clusters
+respectively. High assignment variability across GCMs is expected as spatial differences in
+GCM DHW timeseries result in reefs being impacted at different relative magnitudes within
+their management area across GCMs.
 
@@
 
-Under all GCMs most reefs are projected to suffer substantial declines in coral cover
-relative to 2025 levels. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover
-maintenance into the future. Differences between low, medium and high reef clusters in cover
-timeseries are most notable under these two GCMs [@tbl-cluster-cid;
-@fig-gcm-cover-trajectories]. Maintainance of coral cover into the future is linked to the
-Equilibrium Climate Sensitivity of the GCM used as levels of future recovery and timespan of
-cover maintainance increase as GCM ECS increases [@fig-gcm-cover-trajectories]. Under
-high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2) large declines and lower rates of
-recovery in high cover clusters are common compared to lower-ECS GCMs.
+Under all GCMs many reefs are projected to suffer substantial declines in coral cover
+relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the
+lowest cover level cluster at the management area scale across GCMs. NorESM2-MM and
+ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future. Differences
+between low, medium and high reef clusters in cover timeseries are most notable under these
+two GCMs [@tbl-cluster-cid; @fig-gcm-cover-trajectories]. Maintainance of coral cover into
+the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of
+future recovery and timespan of cover maintainance increase as GCM ECS increases
+[@fig-gcm-cover-trajectories]. Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
+large declines and lower rates of recovery in high cover clusters are common compared to
+lower-ECS GCMs.
 
@@
 
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by management area scale cluster assignment.
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2024]. Reef centroids are
+marked individually for visual clarity. Reefs that do not have a consistent cluster
+assignment level across all GCMs at mangement area scale are gray. All consistently
+clustered reefs are coloured according to their management area scale cluster assignment.
+Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
+cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
+investigation are represented in this figure. An annotation represents the approximate
+location of the Australian Institute of Marine Science Townsville site at Cape
+Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
+fig-align="center" width="14.82cm"}
+
 ![![](images/paste-1.png)Heatmaps indicating reef cluster assignments within each bioregion

### 2025-08-10 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -294,3 +294,9 @@ sorted_vals = sort(context_layers, :man_area_consistent_reefs, by = x -> order[x
 gbr_assignment_map = map_gbr_reefs(sorted_vals, :man_area_consistent_reefs, consistent_reefs_colors, "Cluster assignment across GCMs")
 
 save(joinpath(output_path, "figs/gcm_cluster_assignment_map.png"), gbr_assignment_map, px_per_unit=dpi)
+
+n_consistent_reefs = combine(groupby(context_layers[context_layers.man_area_consistent_reefs .!="variable", :], :management_area), nrow => :nrow)
+n_consistent_reefs.percentage = n_consistent_reefs.nrow ./ sum(n_consistent_reefs.nrow) .* 100
+
+n_consistent_reefs = combine(groupby(context_layers[context_layers.man_area_consistent_reefs .!="variable", :], :man_area_consistent_reefs), nrow => :nrow)
+n_consistent_reefs.percentage = n_consistent_reefs.nrow ./ sum(n_consistent_reefs.nrow) .* 100

### 2025-08-10 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -21,11 +21,9 @@ ecs_values = Dict(
 ecs = ecs_plot(collect(values(ecs_values)), [2.5, 5.1], [2.1, 7.7], collect(keys(ecs_values)))
 save(joinpath(output_path, "figs/ecs_plot.png"), ecs, px_per_unit=dpi)
 
-reef_colors = distinguishable_colors(length(unique(investigation_reefs.bioregion)))
-
 # GBR map plot - methods
 bioregion_colors = distinguishable_colors(length(unique(context_layers.bioregion)));
-gbr_methods_map = map_gbr_reefs(context_layers, :bioregion, bioregion_colors)
+gbr_methods_map = map_gbr_reefs(context_layers, :bioregion, bioregion_colors, "Bioregions")
 
 save(joinpath(output_path, "figs/region_map.png"), gbr_methods_map, px_per_unit=dpi)
 

### 2025-08-10 paper/paper_draft.qmd
Minor adjustments to paper and 3_ script to ensure smooth run

@@
 scaled by the total area of the reef to represent cover as a percentage of the total
-estimated reef area. The proportion of each functional group occupying the reef (group
-evenness) was also investigated as a metric for timeseries analysis, but was found to not
-sufficiently capture the declined condition of reefs suffering from very low absolute coral
-cover **\[TI: Ben, is the sentence here really important to include?\]**. These timeseries
+estimated reef area. These timeseries
 of coral cover were then clustered based on their temporal behaviour.
@@
 #| tbl-cap: Complexity invariant distance (CID) between low and high cluster median timeseries in each management area under each GCM.
-CID values are calculated for percentage cover timeseries (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) timeseries (@fig-gcm-dhw-trajectories).
+CID values are calculated for percentage cover timeseries (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) timeseries (@sfig-gcm-dhw-trajectories).
 Complexity invariant distance represents the euclidean distance between timeseries, corrected by the complexity of the two timeseries.
@@
 
-using PrettyTables, Markdown
-cd("../src")
+# using PrettyTables, Markdown
+# cd("../src")
 
-include("../src/common.jl")
+# include("../src/common.jl")
 
-cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/ACCESS-ESM1-5_bioregion_cluster_regression_coefficients.csv"), DataFrame)
-cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])
+# cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/ACCESS-ESM1-5_bioregion_cluster_regression_coefficients.csv"), DataFrame)
+# cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])
 
-for name in names(cluster_regression)
-    if isa(cluster_regression[:, name], Vector{Float64})
-        cluster_regression[:, name] = round.(cluster_regression[:, name]; sigdigits=2)
-    end
-end
+# for name in names(cluster_regression)
+#     if isa(cluster_regression[:, name], Vector{Float64})
+#         cluster_regression[:, name] = round.(cluster_regression[:, name]; sigdigits=2)
+#     end
+# end
 
-io = IOBuffer()
+# io = IOBuffer()
 
-header = ["Response level ~ Term", "β estimate", "SE", "t-value", "Pr > |t|", "2.5%", "97.5%"]
-pretty_table(io, cluster_regression, backend=Val(:markdown), header=header)
+# header = ["Response level ~ Term", "β estimate", "SE", "t-value", "Pr > |t|", "2.5%", "97.5%"]
+# pretty_table(io, cluster_regression, backend=Val(:markdown), header=header)
 
-md_string = (String(take!(io)))
-Markdown.parse(md_string)
+# md_string = (String(take!(io)))
+# Markdown.parse(md_string)
 ```
@@
 
-Our findings do not suggest that reefs in ‘high’ cover clusters have greater thermal
+Our findings suggest that reefs in ‘high’ cover clusters do not have greater thermal
 tolerance than reefs in lower coral cover clusters. This is in contrast with literature
@@
 of influence of thermal tolerance on reef outcomes is likely due to reefs being impacted by
-high levels of thermal stress early in projected conditions and being unable to build
+high levels of thermal stress early in projected timeseries and being unable to build
 thermal tolerance to DHW levels greater than 9°C-weeks. **\[TI note: This paragraph needs to
@@
 parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods. Using
-updated 1km resolution larval connectivity across the whole GBR, with a limited temporal
+updated 1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal
 sample of particle flows, our results suggest that larval connectivity alone is not as
@@
 
-![Depth cutoff for reefs](images/reef_depth_included_cutoff.png){#sfig-depth-cutoff
+![Depth cutoff for reefs](../outputs/ADRIA_results/HighResCoralStress/figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
 fig-align="center" width="14.8cm" height="9.5cm"}
@@
 
-![![](images/paste-1.png)Heatmaps indicating reef cluster assignments within each bioregion
+![Heatmaps indicating reef cluster assignments within each bioregion
 across the five GCMs. Green indicates a low cover cluster assignment, orange represents a

### 2025-08-10 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -204,7 +204,7 @@ context_layers.total_strength .= convert.(Float64, context_layers.total_strength
 context_layers.total_count .= convert.(Int64, context_layers.total_count)
 context_layers.total_comb .= convert.(Float64, context_layers.total_comb)
 context_layers.so_to_si .= convert.(Float64, context_layers.so_to_si)
-context_layers.man_area_consistent_reefs .= convert.(String, context_layers.so_to_si)
+context_layers.man_area_consistent_reefs .= convert.(String, context_layers.man_area_consistent_reefs)
 
 GDF.write(joinpath(output_path, "analysis_context_layers_carbonate.gpkg"), context_layers; crs=GFT.EPSG(7844), overwrite=true)
 

### 2025-08-10 src/ADRIA/HighResCoralStress/7_multinomial_regression.jl
Initial working pass at a bayesian ordinal mixed effects model
Using Turing.jl. Project has updated package requirements

@@ -2,6 +2,7 @@
 using CSV
 using CategoricalArrays
 using Econometrics, StatsModels
+using MixedModels
 
 include("../../common.jl")
 
@@ -17,14 +18,14 @@ GCMs = dhw_scenarios.dhw.properties["members"]
 # reef, depth, connectivity, dhw, cluster and GCM
 
 gcm_dhw_cols = [Symbol("$(GCM)_mean_dhw") for GCM in GCMs]
-gcm_bioregion_cluster_cols = [Symbol("$(GCM)_bioregion_cluster_cats") for GCM in GCMs]
+gcm_bioregion_cluster_cols = [Symbol("$(GCM)_bioregion_clusters") for GCM in GCMs]
 
 collated_reef_properties = Vector{DataFrame}(undef, length(GCMs))
-target_cols = [:UNIQUE_ID, :GBRMPA_ID, :depth_med, :log_total_strength, :log_so_to_si]
+target_cols = [:UNIQUE_ID, :GBRMPA_ID, :depth_med, :log_total_strength, :log_so_to_si, :bioregion]
 reef_properties = context_layers[:, target_cols]
 for (i, GCM) in enumerate(GCMs)
     dhw_col = Symbol("$(GCM)_mean_dhw")
-    bio_cluster_col = Symbol("$(GCM)_bioregion_cluster_cats")
+    bio_cluster_col = Symbol("$(GCM)_bioregion_clusters")
 
     bio_cluster_details = context_layers[:, [dhw_col, bio_cluster_col]]
     rename!(bio_cluster_details, dhw_col => :mean_dhw, bio_cluster_col => :cluster)
@@ -39,29 +40,114 @@ end
 
 reef_properties = vcat(collated_reef_properties...)
 reef_properties.GCM .= categorical(reef_properties.GCM)
+reef_properties.bioregion .= categorical(reef_properties.bioregion)
 
-lhs = Term(:cluster)
-rhs_terms = [
-    Term(:depth_med),
-    Term(:log_total_strength),
-    Term(:log_so_to_si),
-    Term(:mean_dhw),
-    Term(:GCM)
-]
+# # lhs = Term(:cluster)
+# # rhs_terms = [
+# #     Term(:depth_med),
+# #     Term(:log_total_strength),
+# #     Term(:log_so_to_si),
+# #     Term(:mean_dhw),
+# #     (1|Term(:GCM)),
+# #     (1|Term(:bioregion))
+# # ]
 
-f = FormulaTerm(lhs, sum(rhs_terms))
[…]

### 2025-08-11 paper/paper_draft.qmd
Manually update GBRMPA citations

@@
 [@grimaldi2022]. The GBR faces severe projected coral cover declines under climate change
-[@bozec2022]. These coral cover declines will be compounded by ocean acidification,
-intensifying tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012;
-@fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24 Summer mass
-bleaching event may be signalling a shift towards this reef future, with some level of
-bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs) [@cantin2024].
+[@bozec2025; @bozec2022]. These coral cover declines will be compounded by ocean
+acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks
+[@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24
+Summer mass bleaching event may be signalling a shift towards this reef future, with some
+level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
+[@cantin2024].
 
@@
 [@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park management
-areas [@GBRMPA2024] and the corresponding bioregion for each reef is shown in
-[@fig-region-map; @GBRMPA2001]. This investigation adopts the GBR reef outlines as published
+areas [@GBRMPA2007] and the corresponding bioregion for each reef is shown in
+(@fig-region-map; [@GBRMPA2024]). This investigation adopts the GBR reef outlines as published
 by GBRMPA [-@GBRMPA2022], which defines 3806 reefs across the GBR.
@@
 22%, from the initial set of 3806 reefs. Furthermore, reefs that are not associated with
-GBRMPA management areas [@GBRMPA2024] or reefal bioregions [@GBRMPA2001] were also removed
+GBRMPA management areas [@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed
 from the investigation. Bioregions which contained fewer than three reefs were also
@@
 Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
-[@GBRMPA2024]. Reef centroids are marked individually for visual clarity, and are coloured
-according to its bioregion [@GBRMPA2001]. All 2429 reefs included in this investigation are
+[@GBRMPA2007]. Reef centroids are marked individually for visual clarity, and are coloured
+according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
 represented in this figure. An annotation represents the approximate location of the
@@
 scaled by the total area of the reef to represent cover as a percentage of the total
-estimated reef area. These timeseries
-of coral cover were then clustered based on their temporal behaviour.
+estimated reef area. These timeseries of coral cover were then clustered based on their
+temporal behaviour.
 
@@
 Timeseries clustering analyses were performed at the management area and reefal bioregion
-scale (defined in GBRMPA [-@GBRMPA2001]). Additional analyses were also performed at the
+scale (defined in GBRMPA [-@GBRMPA2024]). Additional analyses were also performed at the
 whole-of-GBR scale. These were found to lead to identical conclusions and so are not shown
@@
 with other ongoing modelling and analyses conducted as part of the Reef Restoration and
-Adaptation Program (RRAP; <https://gbrrestoration.org>) **\[TODO: PROPER CITATION OF
+Adaptation Program \[RRAP; <https://gbrrestoration.org>\] **\[TODO: PROPER CITATION OF
 RRAP\]**. The median depths for each indicative reef area were extracted from bathymetry
@@
 waves, cyclones, CoTS and currents into future resilience investigations [@lin2023;
-@mcclanahan2005; @grimaldi2022; @liu2024]. Additionally, the investigation could be enhanced
-by incorporating ocean acidification projections into analyses of coral carbonate budgets.
+@mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024]. Additionally, the investigation
+could be enhanced by incorporating ocean acidification projections into analyses of coral
+carbonate budgets.
 
@@
 
-![Depth cutoff for reefs](../outputs/ADRIA_results/HighResCoralStress/figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
+![Depth cutoff for
+reefs](../outputs/ADRIA_results/HighResCoralStress/figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
 fig-align="center" width="14.8cm" height="9.5cm"}
@@
 Far Northern management region, green represents Cairns/Cooktown, red covers
-Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2024]. Reef centroids are
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
 marked individually for visual clarity. Reefs that do not have a consistent cluster
@@
 
-![Heatmaps indicating reef cluster assignments within each bioregion
-across the five GCMs. Green indicates a low cover cluster assignment, orange represents a
-medium cover assignment and blue represents assignment of a reef to a high coral cover
-cluster. The vertical width of reef elements varies depending on the number of reefs within
-the bioregion (displayed in the y axis). The x axis represents the different GCM levels
-(EC-Earth3-Veg, ACCESS-ESM1-5, ACCESS-CM2, NorESM2-MM and
+![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
+Green indicates a low cover cluster assignment, orange represents a medium cover assignment
+and blue represents assignment of a reef to a high coral cover cluster. The vertical width
+of reef elements varies depending on the number of reefs within the bioregion (displayed in
+the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
+ACCESS-CM2, NorESM2-MM and
 GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment

### 2025-08-11 paper/paper_draft.qmd
Slight updates to DHW-tolerance paragraph and ADRIA-platform paragraph

@@
 areas [@GBRMPA2007] and the corresponding bioregion for each reef is shown in
-(@fig-region-map; [@GBRMPA2024]). This investigation adopts the GBR reef outlines as published
-by GBRMPA [-@GBRMPA2022], which defines 3806 reefs across the GBR.
+(@fig-region-map; [@GBRMPA2024]). This investigation adopts the GBR reef outlines as
+published by GBRMPA [-@GBRMPA2022], which defines 3806 reefs across the GBR.
 
@@
 the purpose of this investigation.
-
-\[**BG: I am having issues with citations not appearing for datasets like GBRMPA ones.**\]
 
@@
 [-@bairos-novak2021] that revealed high heritability of bleaching and survival response
-traits, used to inform thermal tolerance trait distributions in this investigation. The lack
-of influence of thermal tolerance on reef outcomes is likely due to reefs being impacted by
-high levels of thermal stress early in projected timeseries and being unable to build
-thermal tolerance to DHW levels greater than 9°C-weeks. **\[TI note: This paragraph needs to
-be revisited\]**
+traits, used to inform thermal tolerance trait distributions in this investigation. The low
+importance of thermal tolerance on cover outcomes may be due to reefs experiencing high
+levels of thermal stress early in projected timeseries. High - early timeseries thermal
+stress events may prevent the intergenerational adaptation of corals to thermal stress and
+prevent thermal tolerance from reaching levels greater than 9°C-weeks. **\[TI note: This
+paragraph needs to be revisited\]**
 
@@
 **\[TODO - rewrite/expand paragraphs below for flow\]** 
-
-ADRIA - CoralBlox has not been calibrated or validated at the GBR-wide scale. Accordingly,
-the purpose of this investigation is to assess the relative influence of reef
-characteristics on future resilience and highlight possible outcomes under uncertain future
-scenarios. We do not aim to provide spatially explicit predictions of future resilience.
-
-Further analyses could build on the findings of this study by analysing the impacts of
-prioritising reef depth in restoration intervention decision making. The ADRIA platform is
-developed as a modelling tool to incorporate multi-criteria decision analysis (MCDA) and
-ecosystem scenario modelling into reef restoration decision support. The platform allows for
-the investigation of different reef characteristics to be targetted in decision making and
-models the evolving outcomes as a result of interventions at various locations. The
-capability of ADRIA-CoralBlox could be further expanded by incorporating the impacts of
-waves, cyclones, CoTS and currents into future resilience investigations [@lin2023;
-@mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024]. Additionally, the investigation
-could be enhanced by incorporating ocean acidification projections into analyses of coral
-carbonate budgets.
+As ADRIA - CoralBlox has not been
+validated at the GBR-wide scale, we aim to assess the relative influence of reef
+characteristics on resilience under future change rather than provide spatially explicit
+predictions of reef outcomes into the future. Using this approach we suggest that median
+reef depth is an important factor for reef resilience under thermal stress. Improvements in
+remote sensing approaches for broad scale bathymetry measurement, and understanding of how
+depth impacts experienced thermal stress on reefs will further enhance investigations of
+depth as a critical factor for reef resilience. Additional analyses could build on the
+findings of this study by assessing the impacts of prioritising reef depth in reef
+restoration decision making. The ADRIA platform is developed as a modelling tool to
+incorporate multi-criteria decision analysis (MCDA) and ecosystem scenario modelling into
+reef restoration decision support. This platform allows for different intervention
+priorities to be dynamically targetted in decision making, while modelling the evolving
+outcomes as a result of interventions. The capability of ADRIA-CoralBlox could be further
+expanded by incorporating the impacts of waves, cyclones, CoTS and currents into future
+resilience investigations [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022;
+@liu2024]. Additionally, the investigation could be enhanced by incorporating ocean
+acidification projections into analyses of coral carbonate budgets [@eyre2018].
 

### 2025-08-12 paper/paper_draft.qmd
Remove redundant and repetitious mention of reef outlines
Adjust reef definition text for flow

@@
 definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
-[@GBRMPA2022]. An indicative map of the GBR marine park including the Marine Park management
-areas [@GBRMPA2007] and the corresponding bioregion for each reef is shown in
-(@fig-region-map; [@GBRMPA2024]). This investigation adopts the GBR reef outlines as
-published by GBRMPA [-@GBRMPA2022], which defines 3806 reefs across the GBR.
+[@GBRMPA2022]. The reef definitions define 3806 reefs across the GBR. An indicative map of
+the GBR marine park including the Marine Park management areas [@GBRMPA2007] and the
+corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
 
@@
 with the 3806 reef outlines through geometric intersection analysis. Depth values within
-each reef polygon were summarized using zonal statistics to calculate minimum, mean, median,
-maximum, and standard deviation of depth values. All depth values were converted to positive
-values (depths below sea level). The median depth was used to provide an indicative depth
-value for each reef. Code, and the resulting depth estimates, are available at **\[cite
-Canonical Reefs repo\]**.
+each reef polygon were summarized using zonal statistics. All depth values were converted to
+positive values (depths below sea level). The median depth was used to provide an indicative
+depth value for each reef. Code, and the resulting depth estimates, are available at
+**\[cite Canonical Reefs repo\]**.
 
-While data adopted for the given assessment are said to be accurate up to 15m from Mean Sea
-Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for
-this study. These are outlined further in the Discussion. Notably, the adopted depth
-estimates were derived from bathymetries based on satellite imagery. Available data can be
-limited in their alignment with the established GBRMPA reef outlines used to characterise
-reef locations and their areal extent. Quality control flags were assigned to identify
-potential data limitations: reefs with no overlapping bathymetry data, reefs with minimum
-depth values above sea level (indicating potential data artifacts), and reefs where
-bathymetry pixels covered less than 5% of the reef polygon area. This removed 842 reefs, or
-22%, from the initial set of 3806 reefs. Furthermore, reefs that are not associated with
-GBRMPA management areas [@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed
-from the investigation. Bioregions which contained fewer than three reefs were also
-excluded. As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for
-the purpose of this investigation.
+While the bathymetry data adopted for the given assessment are said to be accurate up to 15m
+from Mean Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth
+estimates used for this study. These are outlined further in the Discussion. Notably, the
+adopted depth estimates were derived from bathymetries based on satellite imagery. The
+bathymetry data can be limited in their alignment with the established GBRMPA reef outlines
+used to characterise reef locations and their areal extent. A Quality Assessment and Control
+process identified reefs with potential data limitations: reefs with no overlapping
+bathymetry data, reefs with minimum depth values above sea level (indicating potential data
+artifacts), and reefs where bathymetry pixels covered less than 5% of the reef polygon area.
+This process removed 842 reefs, or 22%, from the initial set of 3806 reefs. Furthermore,
+reefs that are not associated with GBRMPA management areas [@GBRMPA2007] or reefal
+bioregions [@GBRMPA2024] were also removed from the investigation. Bioregions which
+contained fewer than three reefs were also excluded. As a result, 1377 reefs were excluded
+(36%), leaving a total of 2429 remaining for the purpose of this investigation.
 

### 2025-08-12 paper/paper_draft.qmd
Adjust GCM description for brevity and flow

@@
 HighResCoralStress database [@dixon2022; @dixon2023]. These five GCMs were EC-Earth3-Veg,
-ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4 and are a part of the Sixth Phase of the
-Coupled Model Intercomparison Project (CMIP6) based on evaluation conducted by Grose et al.
-[-@grose2023]. These GCMs were found to rank highly in the recreation of historical
-atmospheric temperature and precipitation conditions in the Australasian region. While this
-assessment does not consider oceanic data, Grose et al. [-@grose2023] provide a
-region-specific selection mechanism which we use as an indicator of general performance of
-GCMs for the region. An overview of the selected GCMs are provided in @tbl-gcms. The process
-described here was conducted for all 2429 reefs to create DHW projections spanning from 2025
-to 2075. Code used to calculate DHW data and perform analyses involved in this investigation
-can be found at **insert repo citation**.
+ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4. The selected GCMs are a part of the
+Sixth Phase of the Coupled Model Intercomparison Project (CMIP6), spanning four 'model
+development families' as defined by Brunner et al., [-@brunner2020].
 
-The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
-the Intergovernmental Panel on Climate Change (IPCC) assessed likely range. The IPCC defines
-ECS as the long term warming caused by a doubling of carbon dioxide above its pre-industrial
-concentration [@forster2021]. GCM development institutions regularly share aspects of model
-development. Brunner et al. [-@brunner2020] assessed the independence of 33 models,
-quantitatively classifying models into 'model development families' based on patterns in
-atmospheric temperature and sea level pressure. By selecting five GCMs for investigation
-that span a range of four 'model development families' [@brunner2020] (note: we assume
-GFDL-CM4 aligns with GFDL-ESM4; ACCESS-ESM1-5 and ACCESS-CM2 occupy the same family), we are
-able to assess climate projections over a broad range of independently derived futures
-[@abramowitz2019]. The selected GCMs therefore allow for a range of possible climate futures
-to be explored, capturing the uncertainty in future responses to CO2 increases (@sfig-ecs;
-@fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using Shared Socio-economic
-Pathway (SSP) 2-4.5 was used to represent the plausible emission pathway. It represents a
-moderate emissions scenario with continued CO2 emissions comparable to present day until
-2050, after which emissions gradually decline [@hausfather2020; IPCC -@climate2023]. The
-selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in the 2081-2100
-period relative to 1850-1900.
+These GCMs were selected based on based on evaluation conducted by Grose et al.,
+[-@grose2023], indicating their ability to recreate historical atmospheric temperature and
+precipitation conditions in the Australasian region. They span a range of Equilibrium
+Climate Sensitivity (ECS) values within the Intergovernmental Panel on Climate Change (IPCC)
+assessed likely range. The IPCC defines ECS as the long term warming caused by a doubling of
+carbon dioxide above its pre-industrial concentration [@forster2021]. While this assessment
+does not consider oceanic data, Grose et al. [-@grose2023] provide a region-specific
+selection mechanism which we use as an indicator of general performance of GCMs for the
+region. An overview of the selected GCMs are provided in @tbl-gcms. Note here that Grose et
+al., [-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023]
+provides data based on GFDL-CM4. Similarly, data for ACCESS-CM2 was used as a stand-in for
+ACCESS-ESM1-5. These substitutions are assumed appropriate given they share the same
+fundamental representation of the physical climate system.
+
+Projections using Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the
+plausible emission pathway. It represents a moderate emissions scenario with continued CO2
+emissions comparable to present day until 2050, after which emissions gradually decline
+[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.31°C **\[TI:
+Use K or Celcius?\]** of global atmospheric warming in the 2081-2100 period relative to
+1850-1900. The use of this range of GCMs therefore allow for a range of possible climate
+futures to be explored, capturing the uncertainty in future responses to CO2 increases
+(@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]) and enables the assessment of
+model projected coral reef behaviour over a broad range of independently derived climate
+futures [@abramowitz2019].
 
@@
 indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for all
-pixels touching each reef outline.
+pixels touching each reef outline. The process described here was conducted for all 2429
+reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
+and perform analyses involved in this investigation can be found at **\[insert repo
+citation\]**.
 

### 2025-08-12 paper/paper_draft.qmd
Add comment for @eco-ben :)

@@
 main text. ECS values obtained from: [@sentman2025; @grose2023; @seland2020; @ziehn2020;
-@wyser2020].
+@wyser2020]. **\[TI: Ben, I would add this to the table directly in the ECS value column
+(ECS value and source). The table should also be ordered by ECS value (high to low)\]**
 :::
@@
 
-**\[TODO - rewrite/expand paragraphs below for flow\]**
-As ADRIA - CoralBlox has not been
+**\[TODO - rewrite/expand paragraphs below for flow\]** As ADRIA-CoralBlox has not been
 validated at the GBR-wide scale, we aim to assess the relative influence of reef

### 2025-08-12 paper/paper_draft.qmd
Expand limitation section
I think the connectivity angle warrants further description here too @eco-ben

@@
 reflectance, the water penetration depth of satellite sensors, influence of local conditions
-(e.g., turbidity and wave activity), among many other factors.
+(e.g., turbidity and wave activity), among many other factors. The median depths for each
+indicative reef area were extracted from bathymetry data using zonal statistics and depth
+values beyond the stated 15m accuracy threshold [@GBRMPA2020] were included. The resulting
+depth estimates are therefore highly uncertain and are only adopted as a useful indication
+for the purpose of the presented analysis. They are not intended to be an accurate and
+precise report of reef depths across the GBR.
 
@@
 Adaptation Program \[RRAP; <https://gbrrestoration.org>\] **\[TODO: PROPER CITATION OF
-RRAP\]**. The median depths for each indicative reef area were extracted from bathymetry
-data using zonal statistics and depth values beyond the 15m range were included. The
-resulting depth estimates are therefore highly uncertain and are only adopted as a useful
-indication for the purpose of the presented analysis. They are not intended to be an
-accurate and precise report of reef depths across the GBR.
+RRAP\]**.
 
-**\[TODO - rewrite/expand paragraphs below for flow\]** As ADRIA-CoralBlox has not been
-validated at the GBR-wide scale, we aim to assess the relative influence of reef
-characteristics on resilience under future change rather than provide spatially explicit
-predictions of reef outcomes into the future. Using this approach we suggest that median
-reef depth is an important factor for reef resilience under thermal stress. Improvements in
-remote sensing approaches for broad scale bathymetry measurement, and understanding of how
-depth impacts experienced thermal stress on reefs will further enhance investigations of
-depth as a critical factor for reef resilience. Additional analyses could build on the
-findings of this study by assessing the impacts of prioritising reef depth in reef
-restoration decision making. The ADRIA platform is developed as a modelling tool to
-incorporate multi-criteria decision analysis (MCDA) and ecosystem scenario modelling into
-reef restoration decision support. This platform allows for different intervention
-priorities to be dynamically targetted in decision making, while modelling the evolving
-outcomes as a result of interventions. The capability of ADRIA-CoralBlox could be further
-expanded by incorporating the impacts of waves, cyclones, CoTS and currents into future
-resilience investigations [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022;
-@liu2024]. Additionally, the investigation could be enhanced by incorporating ocean
-acidification projections into analyses of coral carbonate budgets [@eyre2018].
+The modelling conducted with ADRIA-CoralBlox itself is subject to many uncertainties. For
+one, a formal mechanistic and spatial validation of the model represents an area for future
+refinement, and is the focus of a future publication. Indicative results are included in the
+supplementary **\[TI: For Pedro to include! :`D`\].** The consistency of projected patterns
+with known coral-climate relationships and reef characteristics provides confidence in the
+model's ability to meaningfully capture ecological signals at the GBR-scale. The mechanistic
+basis of the model, combined with qualitative assessment of model behavior, supports the
+robustness of our findings for understanding broad-scale coral cover responses to climatic
+drivers. The aim here, however, was to assess the relative influence of reef characteristics
+on structural resilience under future conditions, rather than provide spatially explicit and
+highly accurate and precise predictions of reef outcomes. Using this approach we suggest
+that reef depths is an important factor for reef resilience under thermal stress.
+
+Improvements in remote sensing approaches for broad scale bathymetry measurement, and
+understanding of how depth impacts experienced thermal stress on reefs will further enhance
+investigations of depth as a critical factor for reef resilience. Additional analyses could
+build on the findings of this study by assessing the impacts of prioritising reef depth in
+reef restoration decision making. Future analyses could incorporate further environmental
+and ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn
+Starfish [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
 

### 2025-08-12 paper/paper_draft.qmd
Small tweak to conclusion
To be revisited once all complete

@@
 
-In conclusion, our results suggest that when modelled as part of a large and complex
+The results presented herein suggest that when modelled as part of a large and complex
 ecosystem, reef depth is a key factor contributing to ongoing reef resilience. We provide
@@
 that current connectivity modelling methods are not able to generate connectivity that
-contributes to reef resilience under projected conditions. We suggest further analyses that
-investigate the benefits of incorporating depth-based resilience into reef decision making,
-as well as further research and development in connectivity modelling methods for
-whole-ecosystem scales.
+contributes to reef resilience under projected conditions **\[TI: TO BE REVISITED\]**. We
+suggest further analyses that investigate the benefits of incorporating depth-based
+resilience into reef decision making, as well as further research and development in
+connectivity modelling methods for whole-ecosystem scales.
 

### 2025-08-12 paper/paper_draft.qmd
Fix ECS units and sources in table

@@
 emissions comparable to present day until 2050, after which emissions gradually decline
-[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.31°C **\[TI:
-Use K or Celcius?\]** of global atmospheric warming in the 2081-2100 period relative to
+[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in the 2081-2100 period relative to
 1850-1900. The use of this range of GCMs therefore allow for a range of possible climate
@@
 ::: {#tbl-gcms}
-| Global Climate Model source | ECS value (K) | Interpreted relative severity | Results found in |
+| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
 |-----------------------|-----------------------|------------------------|-----------------------|
-| EC-Earth3-Veg | 4.30 | High | **insert repo citation** |
-| ACCESS-CM2 | 4.66 | High | **insert repo citation** |
-| GFDL-CM4 | 4.1 | High | **insert repo citation** |
-| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
-| NorESM2-MM | 2.5 | Low | **insert repo citation** |
+| ACCESS-CM2 | 4.66 [@grose2023]| High | **insert repo citation** |
+| EC-Earth3-Veg | 4.30 [@wyser2020]| High | **insert repo citation** |
+| GFDL-CM4 | 4.1 [@sentman2025]| High | **insert repo citation** |
+| ACCESS-ESM1-5 | 3.87 [@ziehn2020]| Intermediate | Main text |
+| NorESM2-MM | 2.5 [@seland2020]| Low | **insert repo citation** |
 
@@
 very-likely ECS range and was taken as an intermediate model with results displayed in the
-main text. ECS values obtained from: [@sentman2025; @grose2023; @seland2020; @ziehn2020;
-@wyser2020]. **\[TI: Ben, I would add this to the table directly in the ECS value column
-(ECS value and source). The table should also be ordered by ECS value (high to low)\]**
+main text.
 :::
@@
 management areas, reefs in the high cluster are able to maintain coral cover levels around
-20% to 2050 under ACCESS-ESM1-5. Under ACCESS-CM2 (4.66K), EC-Earth3-Veg (4.30K) and
-GFDL-CM4 (4.1K) GCMs cover trajectories are largely declining in all management areas,
+20% to 2050 under ACCESS-ESM1-5. Under ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and
+GFDL-CM4 (4.1°C) GCMs cover trajectories are largely declining in all management areas,
 reflected in lower CID distance values than other GCMs [@tbl-cluster-cid].

### 2025-08-12 paper/paper_draft.qmd
Expand on connectivity data/implementation caveats
@ConnectedSystems

@@
 emissions comparable to present day until 2050, after which emissions gradually decline
-[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in the 2081-2100 period relative to
-1850-1900. The use of this range of GCMs therefore allow for a range of possible climate
-futures to be explored, capturing the uncertainty in future responses to CO2 increases
-(@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]) and enables the assessment of
-model projected coral reef behaviour over a broad range of independently derived climate
-futures [@abramowitz2019].
+[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global
+atmospheric warming in the 2081-2100 period relative to 1850-1900. The use of this range of
+GCMs therefore allow for a range of possible climate futures to be explored, capturing the
+uncertainty in future responses to CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023;
+@shepherd2018]) and enables the assessment of model projected coral reef behaviour over a
+broad range of independently derived climate futures [@abramowitz2019].
 
@@
 |-----------------------|-----------------------|------------------------|-----------------------|
-| ACCESS-CM2 | 4.66 [@grose2023]| High | **insert repo citation** |
-| EC-Earth3-Veg | 4.30 [@wyser2020]| High | **insert repo citation** |
-| GFDL-CM4 | 4.1 [@sentman2025]| High | **insert repo citation** |
-| ACCESS-ESM1-5 | 3.87 [@ziehn2020]| Intermediate | Main text |
-| NorESM2-MM | 2.5 [@seland2020]| Low | **insert repo citation** |
+| ACCESS-CM2 | 4.66 [@grose2023] | High | **insert repo citation** |
+| EC-Earth3-Veg | 4.30 [@wyser2020] | High | **insert repo citation** |
+| GFDL-CM4 | 4.1 [@sentman2025] | High | **insert repo citation** |
+| ACCESS-ESM1-5 | 3.87 [@ziehn2020] | Intermediate | Main text |
+| NorESM2-MM | 2.5 [@seland2020] | Low | **insert repo citation** |
 
@@
 There are multiple caveats in how coral ecosystem dynamics are modelled in this
-investigation. We model coral colonies as circular diameter values and track these diameters
-over timesteps through growth. Due to the availability of quality future projected data we
-do not consider the impacts of waves, cyclones, currents and Crown of Thorns Starfish (CoTS)
-on coral colony survival and bleaching [@massel1993; @deaker2022]. Uncertainty in
-connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress
-projections are likely to influence the results obtained in this investigation.
-Incorporating further improvements in connectivity modelling and understanding of the
-influence of climate change on reef connectivity would improve the comparison of
-connectivity as an important factor for reef resilience. The DHW data used in this
-investigation have not been bias corrected for the Great Barrier Reef region and are part of
-a wider Australian dataset [@dixon2022] developed using statistical downscaling. We
-investigate a range of future climate responses, thermal projections and ecological
-parameterisations of ADRIA - CoralBlox to account for many possible futures, and our results
-suggest the factors that influence reef resilience are consistent across these scenarios.
+investigation. We model coral colonies as circular diameter values that are tracked over
+timesteps through growth. Due to the availability of quality future projected data we do not
+consider the impacts of waves, cyclones, currents and Crown of Thorns Starfish (CoTS) on
+coral colony survival and bleaching [@massel1993; @deaker2022]. Uncertainty in connectivity
+modelling outputs, satellite-derived bathymetry data and future thermal stress projections
+are likely to influence the results obtained in this investigation. While the resolution of
+connectivity data used in this investigation improves upon data used in comparable studies
+[@bozec2025], the time-mean implementation used may not effectively capture long term
+patterns [@vogt-vincent2023]. Using alternative connectivity implementation methods that
+better capture the ecological-timescale trends in reef connections rather than the high
+daily variability, would improve confidence in the connectivity findings of this
+investigation [@vogt-vincent2023]. The DHW data used in this investigation have not been
+bias corrected for the Great Barrier Reef region and are part of a wider Australian dataset
+[@dixon2022] developed using statistical downscaling. We investigate a range of future
+climate responses, thermal projections and ecological parameterisations of ADRIA - CoralBlox
+to account for many possible futures, and our results suggest the factors that influence
+reef resilience are consistent across these scenarios.
 

### 2025-08-13 paper/paper_draft.qmd
Reorder methods sections
Add initial bayesian regression methods paragraph and update log info

@@
 
+### Connectivity modelling
+
+\*\* need information on GBR1 connectivity used \*\*
+
+Connectivity data from 24 days in total were used in this investigation. These data span six
+years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices,
+while 2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity
+strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
+location (i.e., all 24 days). While the connectivity strengths do not vary from year to year
+within the simulation, they do vary between reefs of varying sizes, providing sufficient
+heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
+spatial variability also enables investigations into the influence of connectivity strength
+and its role in driving recovery processes.
+
+### Carbonate budget analysis
+
+Using median coral cover timeseries for each reef we calculated the number of years each
+reef maintains coral cover above a given percent threshold. The threshold represents the
+level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
+$\beta_{0}$ to indicate the budget equilibrium). Greater number of years above $\beta_{0}$
+therefore suggests greater resilience and opportunity for recovery.
+
+Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
+[@desbiens2021]. Given in situ carbonate budgets are influenced by (1) a range of processes;
+(2) the variety of approaches that could be used to measure those processes; and (3) the
+uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
+single precise $\beta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
+$\beta_{0}$ value for each individual reef.
+
+Given the uncertainties present, the proportion of modelled reefs that display capacity to
+maintain coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of
+10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
+al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of
+the lower and upper bounds respectively. Robustness of the conclusions drawn to the
+uncertainty in the precise value of $\beta_{0}$ for all reefs can then be assessed by using
+the indicative range.
+
+The relationship between the number of years above $\beta_{0}$ and median reef depth was
+then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
+adopted as reef depth and connectivity strength distributions are expected to be non-normal
+and highly skewed. Furthermore, reefs are naturally of different types and experience
+different conditions, and so the monotonic trends (whether the relationship consistently
+increase or decrease) rather than the exact quantative relationship was of interest for this
+analysis.
+
 ### Timeseries clustering
@@
 
-### Carbonate budget analysis
-
-Using median coral cover timeseries for each reef we calculated the number of years each
-reef maintains coral cover above a given percent threshold. The threshold represents the
-level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
-$\beta_{0}$ to indicate the budget equilibrium). Greater number of years above $\beta_{0}$
-therefore suggests greater resilience and opportunity for recovery.
-
-Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
-[@desbiens2021]. Given in situ carbonate budgets are influenced by (1) a range of processes;
-(2) the variety of approaches that could be used to measure those processes; and (3) the
-uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
-single precise $\beta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
-$\beta_{0}$ value for each individual reef.
-
-Given the uncertainties present, the proportion of modelled reefs that display capacity to
-maintain coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of
-10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
-al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of
-the lower and upper bounds respectively. Robustness of the conclusions drawn to the
-uncertainty in the precise value of $\beta_{0}$ for all reefs can then be assessed by using
-the indicative range.
-
-The relationship between the number of years above $\beta_{0}$ and median reef depth was
-then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
-adopted as reef depth and connectivity strength distributions are expected to be non-normal
-and highly skewed. Furthermore, reefs are naturally of different types and experience
-different conditions, and so the monotonic trends (whether the relationship consistently
-increase or decrease) rather than the exact quantative relationship was of interest for this
-analysis.
-
-### Connectivity modelling
-
-\*\* need information on GBR1 connectivity used \*\*
-
-Connectivity data from 24 days in total were used in this investigation. These data span six
-years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices,
-while 2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity
-strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
-location (i.e., all 24 days). While the connectivity strengths do not vary from year to year
-within the simulation, they do vary between reefs of varying sizes, providing sufficient
-heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
-spatial variability also enables investigations into the influence of connectivity strength
-and its role in driving recovery processes.
+To quantify the influence of reef characteristics on cluster assignment we used a Bayesian
+ordinal mixed regression approach. Using Turing.jl [@fjelde2025] we model the influence of
+five predictors, median depth, log total connectivity strength, log source to sink ratio,
+mean DHW, log reef area and mean DHW tolerance level on cluster assignment, including random
+intercepts for levels of **bioregion** and GCM identity.
 
@@
 being unable to maintain coral cover above threshold levels as the threshold increases, with
-values becoming increasingly right-skewed. The natural log of total connectivity strength
+values becoming increasingly right-skewed. The base-10 log of total connectivity strength
 was found to have no correlation with the number of years a reef maintains cover above the
@@
 #| label: tbl-access-esm1-5-bioregion-regression
-#| tbl-cap: Multinomial logistic regression coefficients for the statistical model containing median reef depth, natural-log total connectivity strength, natural-log source-to-sink ratio and ACCESS-ESM1-5 mean timeseries DHW value as predictor variables.
+#| tbl-cap: Multinomial logistic regression coefficients for the statistical model containing median reef depth, base-10-log total connectivity strength, base-10-log source-to-sink ratio and ACCESS-ESM1-5 mean timeseries DHW value as predictor variables.
 ACCESS-ESM1-5 bioregion scale reef cluster assignment is the response variable with three levels, 'low' (regression reference level), 'medium' and 'high'.
@@
 2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef natural log of
+Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
 total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. Colour of each point represents the natural log of scaled reef total connectivity
+threshold. Colour of each point represents the base-10 log of scaled reef total connectivity
 strength. Displays results from median timeseries using
@@
 
-![Source-to-sink connectivity ratios (in natural log scale) for reefs within each bioregion,
+![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion,
 separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
@@
 points represent the ratio value for each reef. Vertical grey lines represent a
-source-to-sink ratio of 0 (in natural log scale) indicating equal outgoing and incoming
+source-to-sink ratio of 0 (in base-10 log scale) indicating equal outgoing and incoming
 connectivity levels. Displays results for ACCESS-ESM1-5
@@
 
-![Total connectivity strength (in natural log scale) for reefs within each bioregion,
+![Total connectivity strength (in base-10 log scale) for reefs within each bioregion,
 separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
@@
 the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines within each violin represent the median natural log of total connectivity strength for
+lines within each violin represent the median base-10 log of total connectivity strength for
 each cluster. Displays results for ACCESS-ESM1-5

### 2025-08-13 paper/paper_draft.qmd
Change mathematical notation and update clust assignment/regression info

@@
 level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
-$\beta_{0}$ to indicate the budget equilibrium). Greater number of years above $\beta_{0}$
+$\theta_{0}$ to indicate the budget equilibrium). Greater number of years above $\theta_{0}$
 therefore suggests greater resilience and opportunity for recovery.
@@
 uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
-single precise $\beta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
-$\beta_{0}$ value for each individual reef.
+single precise $\theta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
+$\theta_{0}$ value for each individual reef.
 
 Given the uncertainties present, the proportion of modelled reefs that display capacity to
-maintain coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of
-10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
+maintain coral cover above a given $\theta_{0}$ threshold is examined. An indicative range
+of 10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
 al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of
 the lower and upper bounds respectively. Robustness of the conclusions drawn to the
-uncertainty in the precise value of $\beta_{0}$ for all reefs can then be assessed by using
+uncertainty in the precise value of $\theta_{0}$ for all reefs can then be assessed by using
 the indicative range.
 
-The relationship between the number of years above $\beta_{0}$ and median reef depth was
+The relationship between the number of years above $\theta_{0}$ and median reef depth was
 then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
@@
 clustered reefs into three clusters based on their temporal behaviour as indicated by coral
-cover over time. The Complexity-Invariant Distance (CID) between each timeseries was
-calculated to identify timeseries that behave similarly [@batista2014]. The CID corrects the
-Euclidean distance between pairs of timeseries (which accounts for magnitude differences)
-with the complexity of each timeseries (obtained through a measure of their variability) to
-ensure reefs are clustered based on their underlying temporal dynamics rather than simply
-their average coral cover. The process creates a distance matrix of n \* n dimensions (where
-n is the number of timeseries in the group) that is clustered using a k-medoids clustering
-algorithm [cf. @steinmann2020].
+cover over time, using timeseries from 2025-2075. The Complexity-Invariant Distance (CID)
+between each timeseries was calculated to identify timeseries that behave similarly
+[@batista2014]. The CID corrects the Euclidean distance between pairs of timeseries (which
+accounts for magnitude differences) with the complexity of each timeseries (obtained through
+a measure of their variability) to ensure reefs are clustered based on their underlying
+temporal dynamics rather than simply their average coral cover. The process creates a
+distance matrix of n \* n dimensions (where n is the number of timeseries in the group) that
+is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The three reef
+clusters are assigned a qualitative level from "low", "medium" and "high" based on their
+relative median timeseries over the 2030-2050 period. Assigning cluster labels based on this
+period prevents cluster labels being assigned during the steeply declining period from
+2025-2030 and during the post-2050 period when many reefs have cover below 5% of their area.
 
@@
 
-To quantify the influence of reef characteristics on cluster assignment we used a Bayesian
-ordinal mixed regression approach. Using Turing.jl [@fjelde2025] we model the influence of
-five predictors, median depth, log total connectivity strength, log source to sink ratio,
-mean DHW, log reef area and mean DHW tolerance level on cluster assignment, including random
-intercepts for levels of **bioregion** and GCM identity.
+We used a Bayesian ordinal hierarchical regression model to quantify the influence of reef
+characteristics on reef cluster assignment. Using Turing.jl [@fjelde2025] we model the
+influence of five predictors, median depth, log total connectivity strength, log source to
+sink ratio, mean DHW, log reef area and mean DHW tolerance level on cluster assignment,
+including random intercepts for levels of **bioregion** and GCM identity. Based on initial
+analyses suggesting higher cover clusters have reefs with greater depths, we constrain the
+$\beta_{depth}$ coefficient prior to positive values. Similarly, we constrain the
+$\beta_{DHW}$ coefficient prior to negative values as we do not expect increasing DHW levels to
+increase cluster assignment level.
 
@@
 
-As one might expect, the number of years experience cover above $\beta_{0}$ (the assumed
-positive carbonate budget threshold) substantially decreases as $\beta_{0}$ increases. The
+As one might expect, the number of years experience cover above $\theta_{0}$ (the assumed
+positive carbonate budget threshold) substantially decreases as $\theta_{0}$ increases. The
 distribution of number of years above carbonate-cover thresholds is right-skewed, with many
@@
 [@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintainence correlation
-decreases as $\beta_{0}$ increases. This is likely due to an increasing number of reefs
+decreases as $\theta_{0}$ increases. This is likely due to an increasing number of reefs
 being unable to maintain coral cover above threshold levels as the threshold increases, with

### 2025-08-14 paper/paper_draft.qmd
Reshuffle results section and add linear regression notes

@@
 
-We used a Bayesian ordinal hierarchical regression model to quantify the influence of reef
-characteristics on reef cluster assignment. Using Turing.jl [@fjelde2025] we model the
-influence of five predictors, median depth, log total connectivity strength, log source to
-sink ratio, mean DHW, log reef area and mean DHW tolerance level on cluster assignment,
-including random intercepts for levels of **bioregion** and GCM identity. Based on initial
-analyses suggesting higher cover clusters have reefs with greater depths, we constrain the
-$\beta_{depth}$ coefficient prior to positive values. Similarly, we constrain the
-$\beta_{DHW}$ coefficient prior to negative values as we do not expect increasing DHW levels to
-increase cluster assignment level.
+We used a multinomial linear regression model to quantify the influence of reef
+characteristics on reef cluster assignment. We model the
+influence of seven predictors, median depth, log total connectivity strength, log source to
+sink ratio, mean DHW, log reef area, mean DHW tolerance level and GCM on cluster assignment.
 
@@
 
-In many bioregions, median reef depth decreases as cluster coral cover decreases, with reefs
-within the ‘high’ cluster commonly having the greatest median reef depths within the
-bioregion (@fig-access-esm1-5-bioregion-depth).
-
-![Median depth for reefs within each bioregion, separated into clusters assigned by
-timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
-area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
-are clusters with intermediate median area-relative cover between 2030 and 2040 within each
-bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
-between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
-cluster. Displays results for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-fig-align="center" width="14.82cm"}
-
 ```{julia}
@@
 \[**BG: Need to add quantification results to text for regressions.**\]
+
+In many bioregions, median reef depth decreases as cluster coral cover decreases, with reefs
+within the ‘high’ cluster commonly having the greatest median reef depths within the
+bioregion (@fig-access-esm1-5-bioregion-depth).
+
+![Median depth for reefs within each bioregion, separated into clusters assigned by
+timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
+area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
+are clusters with intermediate median area-relative cover between 2030 and 2040 within each
+bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
+between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
+cluster. Displays results for ACCESS-ESM1-5
+GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
+fig-align="center" width="14.82cm"}
 

### 2025-08-14 paper/paper_draft.qmd
Update remaining commented paragraphs and figure caption for depths

@@
     Reef (GBR) experiencing severe declines in coral cover from thermal stress events.
-    Understanding which reefs exhibit resilience to climate impacts is critical for conservation
+    Understanding drivers behind reef resilience to climate impacts is critical for conservation
     planning and intervention strategies. A scenario-based population modelling approach was
@@
 We used a multinomial linear regression model to quantify the influence of reef
-characteristics on reef cluster assignment. We model the
-influence of seven predictors, median depth, log total connectivity strength, log source to
-sink ratio, mean DHW, log reef area, mean DHW tolerance level and GCM on cluster assignment.
+characteristics on reef cluster assignment. We model the influence of seven predictors,
+median depth, log total connectivity strength, log source to sink ratio, mean DHW, log reef
+area, mean DHW tolerance level and GCM on cluster assignment.
 
@@
 
-The results presented herein suggest that when modelled as part of a large and complex
-ecosystem, reef depth is a key factor contributing to ongoing reef resilience. We provide
-evidence in support of depth as a form of thermal refugia for shallow-water reefs on the
-GBR. While protecting ‘key node’ reefs in larval connectivity networks is an important
-consideration for reef restoration efforts [@anthony2020; @hock2017], our results suggest
-that current connectivity modelling methods are not able to generate connectivity that
-contributes to reef resilience under projected conditions **\[TI: TO BE REVISITED\]**. We
-suggest further analyses that investigate the benefits of incorporating depth-based
-resilience into reef decision making, as well as further research and development in
-connectivity modelling methods for whole-ecosystem scales.
+The results presented suggest that when modelled as part of a large and complex ecosystem,
+reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in
+support of depth as a form of thermal refugia for shallow-water reefs on the GBR. While
+protecting ‘key node’ reefs in larval connectivity networks is an important consideration
+for reef restoration efforts [@anthony2020; @hock2017], current connectivity modelling
+methods, and our modelling framework, suggest that connectivity may not be as important for
+reef resilience under projected conditions as factors such as depth **\[TI: TO BE
+REVISITED\]**. We suggest further analyses that investigate the benefits of incorporating
+depth-based resilience into reef intervention decision making, as well as further research
+and development in connectivity modelling methods for whole-ecosystem scales.
 
@@
 
-![Depth cutoff for
-reefs](../outputs/ADRIA_results/HighResCoralStress/figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
+![Distribution of depth data coverage levels across 3806 possible reefs. Reefs below the 5%
+data coverage threshold (represented by the red vertical line) were removed from the
+investigation.](../outputs/ADRIA_results/HighResCoralStress/figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
 fig-align="center" width="14.8cm" height="9.5cm"}

### 2025-08-14 paper/paper_draft.qmd
Update .qmd file to respect new figures directory

@@
 Australian Institute of Marine Science Townsville site at Cape
-Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/region_map.png){#fig-region-map
+Cleveland.](../figs/region_map.png){#fig-region-map
 fig-align="center" width="14.8cm"}
@@
 management-area median timeseries and bands represent the 95th percentile confidence
-intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
+intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws
 fig-align="center" width="14.82cm"}
@@
 median reef depth level in metres. Displays results from median timeseries using
-ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
+ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
 fig-align="center" width="14.82cm"}
@@
 times (for each GCM), with each GCM displayed
-horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
+horizontally.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
 fig-align="center" width="14.82cm"}
@@
 cluster. Displays results for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
+GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
 fig-align="center" width="14.82cm"}
@@
 the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
-2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
+2021).](../figs/ecs_plot.png){#sfig-ecs
 fig-align="center" width="10cm"}
@@
 data coverage threshold (represented by the red vertical line) were removed from the
-investigation.](../outputs/ADRIA_results/HighResCoralStress/figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
+investigation.](../figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
 fig-align="center" width="14.8cm" height="9.5cm"}
@@
 represented five times (for each GCM), with each GCM displayed
-horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
+horizontally.](../figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
 fig-align="center" width="14.82cm"}
@@
 location of the Australian Institute of Marine Science Townsville site at Cape
-Cleveland.](../outputs/ADRIA_results/HighResCoralStress/figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
+Cleveland.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
 fig-align="center" width="14.82cm"}
@@
 ACCESS-CM2, NorESM2-MM and
-GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
+GFDL-CM4).](../figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
 fig-align="center" width="14.82cm"}
@@
 RSD %
-values.](../outputs/ADRIA_results/HighResCoralStress/figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
+values.](../figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
 fig-align="center" width="14.82cm"}
@@
 strength. Displays results from median timeseries using
-ACCESS-ESM1-5.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
+ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
 fig-align="center" width="14.82cm"}
@@
 percentile confidence intervals. Displays results for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
+GCM.](../figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
 fig-align="center" width="14.82cm"}
@@
 for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
+GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
 fig-align="center" width="14.82cm"}
@@
 median DHW level for each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
+GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
 fig-align="center" width="14.82cm"}
@@
 median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
+GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
 fig-align="center" width="14.82cm"}
@@
 results for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
+GCM.](../figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
 fig-align="center" width="14.82cm"}
@@
 connectivity levels. Displays results for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
+GCM.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
 fig-align="center" width="14.82cm"}
@@
 each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
+GCM.](../figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
 fig-align="center" width="14.82cm"}

### 2025-08-14 paper/paper_draft.qmd
Update methods with information on source-to-sink ratio calculation
and format doc

@@
 Australian Institute of Marine Science Townsville site at Cape
-Cleveland.](../figs/region_map.png){#fig-region-map
-fig-align="center" width="14.8cm"}
+Cleveland.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
 
@@
 management-area median timeseries and bands represent the 95th percentile confidence
-intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws
-fig-align="center" width="14.82cm"}
+intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws fig-align="center"
+width="14.82cm"}
 
@@
 occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and
-total strength of larval connections between reefs. To analyse the DHW - tolerance levels of
-reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep \* taxa
-\* reef \* scenario matrix. The mean timeseries DHW - tolerance was calculated over the
-first four scenarios for each GCM (four from 4096 scenarios per GCM) due to computational
-restraints, and then used to calculate an overall mean DHW – tolerance value for each reef
-under each GCM.
+total strength of all larval connections between reefs. To analyse the DHW - tolerance
+levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep
+\* taxa \* reef \* scenario matrix. The mean timeseries DHW - tolerance was calculated over
+the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to
+computational restraints, and then used to calculate an overall mean DHW – tolerance value
+for each reef under each GCM.
+
+The ratio of source-to-sink connectivity for a target reef is calculated using @eq-so-to-si,
+and represents the strength of the reef's outgoing larval flow relative to it's incoming
+larval flow. Incoming connections in this calculation, do not directly represent the larval
+supply gained as the population from which connections are coming from is not represented. A
+source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef
+has greater outgoing than incoming larval flow.
+
+$$
+O:I = \frac{\frac{S_O}{N_O}}{\frac{S_I}{N_I}}
+$$ {#eq-so-to-si}
+
+Where:
+
+-   $S$ denotes the total strength of connections.
+
+-   $N$ denotes the number of connections.
+
+-   $O$ denotes outgoing (source) connections from the target reef.
+
+-   $I$ denotes incoming (sink) connections to the target reef.
 
@@
 the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
-2021).](../figs/ecs_plot.png){#sfig-ecs
-fig-align="center" width="10cm"}
+2021).](../figs/ecs_plot.png){#sfig-ecs fig-align="center" width="10cm"}
 
@@
 location of the Australian Institute of Marine Science Townsville site at Cape
-Cleveland.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
-fig-align="center" width="14.82cm"}
+Cleveland.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map fig-align="center"
+width="14.82cm"}
 
@@
 strength as a percentage of reef mean connection strength. Lighter colours indicate higher
-RSD %
-values.](../figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
+RSD % values.](../figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
 fig-align="center" width="14.82cm"}

### 2025-08-14 paper/paper_draft.qmd
Additional small details for Source:Sink connectivity ratio

@@
 
-The ratio of source-to-sink connectivity for a target reef is calculated using @eq-so-to-si,
-and represents the strength of the reef's outgoing larval flow relative to it's incoming
-larval flow. Incoming connections in this calculation, do not directly represent the larval
-supply gained as the population from which connections are coming from is not represented. A
-source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef
-has greater outgoing than incoming larval flow.
+The ratio of source-to-sink connectivity ($O:I$) for a target reef is calculated using
+@eq-so-to-si, and represents the strength of the reef's outgoing larval flow relative to
+it's incoming larval flow. If a reef has no incoming connections, the $O:I$ equals the
+$\frac{S_O}{N_O}$ value. Incoming connections in this calculation, do not directly represent
+the larval supply gained as the population from which connections are coming from is not
+represented. A source-to-sink ratio greater than 1 (a value greater than 0 on a log scale)
+indicates a reef has greater outgoing than incoming larval flow.
 

### 2025-08-14 paper/paper_draft.qmd
Collapse bioregion visual results into a single paragraph
Add methods detail to reflect processing of data from NOAA methodology

@@
 temperatures exceed this seasonal maximum, corals experience thermal stress that can lead to
-bleaching. Only positive anomalies are considered relevant for coral stress, as temperatures
-below the seasonal maximum do not contribute to bleaching risk.
+bleaching. Only positive anomalies, greater than 1°C, are considered relevant for coral
+stress, as temperatures below the seasonal maximum do not contribute to bleaching risk.
 
 DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week
-rolling sum of positive HotSpot SST Anomaly values, expressed in units of °C-weeks. The
-12-week accumulation period reflects the cumulative nature of coral thermal stress. Brief
-temperature spikes may be tolerable, but sustained or repeated exposure to elevated
-temperatures causes progressively greater physiological stress and bleaching severity. DHW
-values integrate both the magnitude and duration of thermal stress: a moderate anomaly
-(e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly (e.g.,
-3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for each
-indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for all
-pixels touching each reef outline. The process described here was conducted for all 2429
-reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
-and perform analyses involved in this investigation can be found at **\[insert repo
-citation\]**.
+rolling sum of positive HotSpot SST Anomaly values that are greater than 1°C, expressed in
+units of °C-weeks. The 12-week accumulation period reflects the cumulative nature of coral
+thermal stress. Brief temperature spikes may be tolerable, but sustained or repeated
+exposure to elevated temperatures causes progressively greater physiological stress and
+bleaching severity. DHW values integrate both the magnitude and duration of thermal stress:
+a moderate anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a
+severe anomaly (e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW
+estimates for each indicative reef (see @GBRMPA2022) were then determined by taking the mean
+DHW value for all pixels touching each reef outline. The process described here was
+conducted for all 2429 reefs to create DHW projections spanning from 2025 to 2075. Code used
+to calculate DHW data and perform analyses involved in this investigation can be found at
+**\[insert repo citation\]**.
 
@@
 correlation levels, while reefs in 'high' clusters have the highest correlation levels
-(@sfig-access-esm1-5-bioregion-dhwcor).
-
-Conversely, there are no consistent patterns across bioregions in reef area-relative cover
-and mean timeseries DHW levels, with clusters having similar mean DHW levels in many
-bioregions (@sfig-access-esm1-5-bioregion-dhwmean).
-
+(@sfig-access-esm1-5-bioregion-dhwcor). Conversely, there are no consistent patterns across
+bioregions in reef area-relative cover and mean timeseries DHW levels, with clusters having
+similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean).
 Similarly, there are no substantial differences between reef clusters in mean thermal
-tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol).
-
-There are no consistent differences across bioregions and GCMs between clusters in their
-reefs' initial proportion of habitable area occupied by corals
-(@sfig-access-esm1-5-bioregion-initialproportion).
-
-Across most bioregions there are not consistent differences between clusters in connectivity
-metrics such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi)
-and total connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
+tolerance levels @sfig-access-esm1-5-bioregion-dhwtol). There are no consistent differences
+across bioregions and GCMs between clusters in their reefs' initial proportion of habitable
+area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion). Across most
+bioregions there are not consistent differences between clusters in connectivity metrics
+such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and total
+connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
 

### 2025-08-14 paper/paper_draft.qmd
Update DHW limitations section
Add comment for @ConnectedSystems

@@
 suggesting corals have the capacity to adapt to increasing climate change pressures
-[@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
+[@humanes2022; @lachs2024; @lachs2023], including the investigation by Bairos-Novak et al.
 [-@bairos-novak2021] that revealed high heritability of bleaching and survival response
@@
 bias corrected for the Great Barrier Reef region and are part of a wider Australian dataset
-[@dixon2022] developed using statistical downscaling. We investigate a range of future
+[@dixon2022] developed using statistical downscaling. Additionally, Lachs et al.
+[@lachs2021] suggest the utility of DHW levels for prediction of coral bleaching can be
+improved by reducing the threshold for HotSpot Anomaly values from MMM +1 to MMM, and
+reducing the accumulation window from 12 weeks to 8 weeks. We investigate a range of future
 climate responses, thermal projections and ecological parameterisations of ADRIA - CoralBlox
@@
 **Bleaching mortality**
-
+**\[BG: Has this section been completed?\]**
 In ADRIA we track the thermal tolerance of each functional group and size class as a

### 2025-08-14 paper/paper_draft.qmd
Adjust wording when talking about deployment considerations

@@
 and challenging decision making process [@anthony2020], and our results suggest that
-deployment site depth is an important factor to consider when assessing the long-term
+deployment site depth may be an important factor to additionally consider when assessing the long-term
 resilience of deployment sites.

### 2025-08-14 paper/paper_draft.qmd
Add repository citation to the manuscript

@@
 to calculate DHW data and perform analyses involved in this investigation can be found at
-**\[insert repo citation\]**.
+Grier and Iwanaga [-@grier2025].
 
@@
 |-----------------------|-----------------------|------------------------|-----------------------|
-| ACCESS-CM2 | 4.66 [@grose2023] | High | **insert repo citation** |
-| EC-Earth3-Veg | 4.30 [@wyser2020] | High | **insert repo citation** |
-| GFDL-CM4 | 4.1 [@sentman2025] | High | **insert repo citation** |
+| ACCESS-CM2                  | 4.66 [@grose2023]  | High                          | [@grier2025]     |
+| EC-Earth3-Veg               | 4.30 [@wyser2020]  | High                          | [@grier2025]     |
+| GFDL-CM4                    | 4.1 [@sentman2025] | High                          | [@grier2025]     |
 | ACCESS-ESM1-5               | 3.87 [@ziehn2020]  | Intermediate                  | Main text        |
-| NorESM2-MM | 2.5 [@seland2020] | Low | **insert repo citation** |
+| NorESM2-MM                  | 2.5 [@seland2020]  | Low                           | [@grier2025]     |
 
@@
 results are used to capture patterns occurring within individual clusters of reefs. Results
-of all analyses at all clustering scales can be found at \[**insert citation for
-repository**\] for those interested.
+of all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for
+those interested.
 
@@
 factor are only shown for ACCESS-ESM1-5 (an intermediate Equilibrium Climate Sensitivity
-scenario [@sfig-ecs]). Results for the additional GCMs can be found at \[**BG: Insert
-repository citation.**\]. However, there are substantial differences in the longevity of
-reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover
+scenario [@sfig-ecs]). Results for the additional GCMs can be found at Grier and Iwanaga
+[-@grier2025]. However, there are substantial differences in the longevity of reef
+resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover
 timeseries are displayed for each GCM (displayed clustered at management-area scale to
@@
 and challenging decision making process [@anthony2020], and our results suggest that
-deployment site depth may be an important factor to additionally consider when assessing the long-term
-resilience of deployment sites.
+deployment site depth may be an important factor to additionally consider when assessing the
+long-term resilience of deployment sites.
 
@@
 
-**Bleaching mortality**
-**\[BG: Has this section been completed?\]**
-In ADRIA we track the thermal tolerance of each functional group and size class as a
-truncated normal distribution that is updated in each timestep following growth and
-recruitment. This distribution determines the proportion of the population on a reef that is
-susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
-Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
-[-@bairos-novak2021].
+**Bleaching mortality** **\[BG: Has this section been completed?\]** In ADRIA we track the
+thermal tolerance of each functional group and size class as a truncated normal distribution
+that is updated in each timestep following growth and recruitment. This distribution
+determines the proportion of the population on a reef that is susceptible to bleaching (i.e.
+has a thermal threshold below the experienced DHW value). Starting distributions for thermal
+tolerance levels are informed by Bairos-Novak et al. [-@bairos-novak2021].
 

### 2025-08-14 paper/paper_draft.qmd
Add RRAP citation and manually update years in .bib where missing
Sometimes citations carried over from Zotero are missing years and will render in word as n.d.

@@
 acknowledged that there is high potential for misalignment between the bathymetry data and
-GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton], for example, identified 120 false
-positives, where features identified as reefs were in actuality sand banks or rocky reefs
-(rather than coral reefs). Reefs with bathymetry data of less than 5% of its indicative area
-were excluded from analysis to ensure analyses were not conducted on reefs with no data
-coverage (see @sfig-depth-cutoff). The existing GBRMPA reef outlines were adopted to align
-with other ongoing modelling and analyses conducted as part of the Reef Restoration and
-Adaptation Program \[RRAP; <https://gbrrestoration.org>\] **\[TODO: PROPER CITATION OF
-RRAP\]**.
+GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton2025], for example, identified 120
+false positives, where features identified as reefs were in actuality sand banks or rocky
+reefs (rather than coral reefs). Reefs with bathymetry data of less than 5% of its
+indicative area were excluded from analysis to ensure analyses were not conducted on reefs
+with no data coverage (see @sfig-depth-cutoff). The existing GBRMPA reef outlines were
+adopted to align with other ongoing modelling and analyses conducted as part of the Reef
+Restoration and Adaptation Program (<https://gbrrestoration.org>; [@thereef]).
 

### 2025-08-15 paper/paper_draft.qmd
Add important information on coral groups that are represented
Added to supplementary incase people are looking to see what groups we use data from.
Fix typos
variations of "maintainence" to maintenance

@@
     production budgets under future conditions. Contrary to expectations, larval connectivity
-    patterns did not correlate with increases in maintainence of positive carbonate budgets.
+    patterns did not correlate with increases in maintenance of positive carbonate budgets.
     Instead, reef depth emerged as the primary predictor of cover-timeseries resilience and
-    maintainence of positive carbonate budgets, with deeper reefs benefiting from thermal
+    maintenance of positive carbonate budgets, with deeper reefs benefiting from thermal
     refugia that reduce bleaching impacts. Our findings suggest that depth provides critical
@@
 with the number of years a reef maintains coral cover above the required threshold
-[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintainence correlation
+[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintenance correlation
 decreases as $\theta_{0}$ increases. This is likely due to an increasing number of reefs
@@
 required thresholds [@sfig-access-esm1-5-conn-carbonate]. Log connectivity strength -
-carbonate budget maintainence correlation slightly decreases as the required carbonate
-budget threshold increases.
+carbonate budget maintenance correlation slightly decreases as the required carbonate budget
+threshold increases.
 
@@
 lower CID distances between low and high cover clusters than in other management areas
-[@tbl-cluster-cid], this is reflected in the low degree of cover maintainence
+[@tbl-cluster-cid], this is reflected in the low degree of cover maintenance
 [@fig-gcm-cover-trajectories]. ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which
@@
 between low, medium and high reef clusters in cover timeseries are most notable under these
-two GCMs [@tbl-cluster-cid; @fig-gcm-cover-trajectories]. Maintainance of coral cover into
+two GCMs [@tbl-cluster-cid; @fig-gcm-cover-trajectories]. Maintenance of coral cover into
 the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of
-future recovery and timespan of cover maintainance increase as GCM ECS increases
+future recovery and timespan of cover maintenance increase as GCM ECS increases
 [@fig-gcm-cover-trajectories]. Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
@@
 
-CoralBlox uses user-defined size classes that influence size-dependent growth and mortality
-rates, through which the coral colonies progress as they grow in diameter. Within ADRIA, we
-define the distributions of these parameters, and the size classes based on ecological
-monitoring data from the Ecological Intelligence for Reef Restoration Program (EcoRRAP)
-([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
+In this investigation we model five functional groups common to the GBR, tabular Acropora,
+corymbose Acropora, corymbose non-Acropora, small massives and large massives. We do not
+model arborscent Acropora forms due to their distinct life history from other morphological
+groups. CoralBlox uses user-defined size classes that influence size-dependent growth and
+mortality rates, through which the coral colonies progress as they grow in diameter. Within
+ADRIA, we define the distributions of these parameters, and the size classes based on
+ecological monitoring data from the Ecological Intelligence for Reef Restoration Program
+(EcoRRAP) ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
 

### 2025-08-15 paper/paper_draft.qmd
Update figure captions for all figures and ensure ECS figure is accurate

@@
 according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
-represented in this figure. An annotation represents the approximate location of the
-Australian Institute of Marine Science Townsville site at Cape
-Cleveland.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
+represented in this figure. Annotations represent major coastal settlements along the GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
 
@@
 : Information for each GCM used in this investigation including Equilibrium Climate
-Sensitivity (ECS) value, interpreted relative severity and where results are individual GCM
+Sensitivity (ECS) value, interpreted relative severity and where results for an individual GCM
 results are found. GCMs in context with assessed plausible ranges of ECS values are
@@
 
-The ratio of source-to-sink connectivity ($O:I$) for a target reef is calculated using
-@eq-so-to-si, and represents the strength of the reef's outgoing larval flow relative to
-it's incoming larval flow. If a reef has no incoming connections, the $O:I$ equals the
+The ratio of source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's outgoing larval flow relative to
+it's incoming larval flow (@eq-so-to-si). If a reef has no incoming connections, the $O:I$ equals the
 $\frac{S_O}{N_O}$ value. Incoming connections in this calculation, do not directly represent
@@
 ![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025
-to 1. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+to 2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
 Bracketed x-axis values represent the Spearman's correlation between reef depth and the
@@
 GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
+between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2060 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the cluster median timeseries and bands
 represent the 95th percentile confidence intervals. Each management area is represented five
@@
 timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
-area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
-are clusters with intermediate median area-relative cover between 2030 and 2040 within each
+area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange)
+are clusters with intermediate median area-relative cover between 2030 and 2060 within each
 bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
-between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
-cluster. Displays results for ACCESS-ESM1-5
+between 2030 and 2060 within each bioregion. Solid lines represent the median depth for each
+cluster across reefs and bands represent the distribution of depth values within each cluster. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
@@
 
-![Distribution of depth data coverage levels across 3806 possible reefs. Reefs below the 5%
+![Distribution of GBRMPA [-@GBRMPA2020] satellite derived depth data coverage levels across 3806 possible reefs. Reefs below the 5%
 data coverage threshold (represented by the red vertical line) were removed from the
@@
 analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
+between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2060 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the cluster median timeseries and bands
 represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
@@
 marked individually for visual clarity. Reefs that do not have a consistent cluster
-assignment level across all GCMs at mangement area scale are gray. All consistently
+assignment level across all GCMs at mangement area scale are coloured grey. All consistently
 clustered reefs are coloured according to their management area scale cluster assignment.
@@
 cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
-investigation are represented in this figure. An annotation represents the approximate
-location of the Australian Institute of Marine Science Townsville site at Cape
-Cleveland.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map fig-align="center"
+investigation are represented in this figure. Annotations represent major coastal settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map fig-align="center"
 width="14.82cm"}
@@
 and blue represents assignment of a reef to a high coral cover cluster. The vertical width
-of reef elements varies depending on the number of reefs within the bioregion (displayed in
+of reef elements varies depending on the number of reefs within the bioregion (displayed on
 the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
@@
 ![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2099. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+2075. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
 Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
 total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. Colour of each point represents the base-10 log of scaled reef total connectivity
+threshold. The colour of each point represents the base-10 log of scaled reef total connectivity
 strength. Displays results from median timeseries using
@@
 ![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2040 within
+(green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
 each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2040 within each
+area-relative cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2060 within each
 bioregion. Solid lines represent the cluster median timeseries and bands represent the 95th
@@
 separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
+clusters with the lowest median area-relative cover between 2030 and 2060 within each
 bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median cover – DHW correlation level for each cluster. Displays results
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
+lines represent the median cover – DHW correlation level for each cluster and bands represent the distribution of correlation levels within each cluster. Displays results
 for ACCESS-ESM1-5
@@
 assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
-median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
-(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
+median area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters
+(orange) are clusters with intermediate median area-relative cover between 2030 and 2060
 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW level for each cluster. Displays results for ACCESS-ESM1-5
+area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the
+median DHW level for each cluster and bands represent the distribution of mean DHW levels within each cluster. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
@@
 
-![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
+![Mean timeseries DHW tolerance value, from 2035 to 2075, for reefs within each bioregion, separated into
 clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
+lowest median area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’
 clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
-median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5
+2060 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the
+median DHW tolerance value for each cluster and bands represent the distribution of DHW-tolerance levels within each cluster. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
@@
 bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
-are clusters with the lowest median area-relative cover between 2030 and 2040 within each
+are clusters with the lowest median area-relative cover between 2030 and 2060 within each
 bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines represent the median proportion of habitable area occupied for each cluster. Displays
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
+lines represent the median proportion of habitable area occupied for each cluster and bands represent the distribution of occupied area values within each cluster. Displays
 results for ACCESS-ESM1-5
@@
 separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
+clusters with the lowest median area-relative cover between 2030 and 2060 within each
 bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
-lines within each violin represent the median source-to-sink ratio for each cluster and grey
-points represent the ratio value for each reef. Vertical grey lines represent a
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
+lines within each violin represent the median source-to-sink ratio for each cluster and bands represent the distribution of source-to-sink ratios within each cluster.
+The vertical grey line represent a
 source-to-sink ratio of 0 (in base-10 log scale) indicating equal outgoing and incoming
@@
 separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2040 within each
+clusters with the lowest median area-relative cover between 2030 and 2060 within each
 bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
 lines within each violin represent the median base-10 log of total connectivity strength for
-each cluster. Displays results for ACCESS-ESM1-5
+each cluster and bands represent the distribution of connectivity strength values within each cluster. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity

### 2025-08-15 src/plotting_functions.jl

@@ -232,7 +232,7 @@ function ecs_plot(
     fig = Figure(size=(fig_x_size, fig_y_size), fontsize=fontsize)
     ax = Axis(
         fig[1, 1],
-        ylabel="Equilibrium Climate Sensitivity (K)",
+        ylabel="Equilibrium Climate Sensitivity (\u00B0C)",
         height=10cm,
         width=8cm
     )
@@ -240,12 +240,12 @@ function ecs_plot(
     poly!(
         ax,
         [(0.98, high_min), (1.02, high_min), (1.02, high_max), (0.98, high_max)];
-        color=(:red, 0.2), linestyle=:dash, strokewidth=1.5, label="likely"
+        color=(:red, 0.2), linestyle=:dash, strokewidth=1.5, label="very likely"
     )
     poly!(
         ax,
         [(0.98, low_min), (1.02, low_min), (1.02, low_max), (0.98, low_max)];
-        color=(:red, 0.6), strokewidth=1.5, label="very likely"
+        color=(:red, 0.6), strokewidth=1.5, label="likely"
     )
     scatter!(ax, ones(length(ecs_values)), ecs_values, markersize=15, color=:black)
     GCM_label.(fill(1.06, length(ecs_values)), ecs_values, GCM_labels)

### 2025-08-15 paper/paper_draft.qmd
Update mistake in the cluster labelling timeperiod details

@@
 clusters are assigned a qualitative level from "low", "medium" and "high" based on their
-relative median timeseries over the 2030-2050 period. Assigning cluster labels based on this
+relative median timeseries over the 2030-2060 period. Assigning cluster labels based on this
 period prevents cluster labels being assigned during the steeply declining period from
-2025-2030 and during the post-2050 period when many reefs have cover below 5% of their area.
+2025-2030 and during the post-2060 period when many reefs have cover below 5% of their area.
 

### 2025-08-15 paper/paper_draft.qmd
Add source of carrying capacity estimates
Plus auto-format
Minor tweak

@@
 corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
+Estimates of coral carrying capacity for each reef were taken from prior analyses undertaken
+in [@bozec2022].
 
@@
 according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
-represented in this figure. Annotations represent major coastal settlements along the GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
+represented in this figure. Annotations represent major coastal settlements along the
+GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
 
@@
 : Information for each GCM used in this investigation including Equilibrium Climate
-Sensitivity (ECS) value, interpreted relative severity and where results for an individual GCM
-results are found. GCMs in context with assessed plausible ranges of ECS values are
+Sensitivity (ECS) value, interpreted relative severity and where results for an individual
+GCM results are found. GCMs in context with assessed plausible ranges of ECS values are
 displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the
@@
 Monte Carlo approach which balances scenario exploration with improved convergence
-properties (compared to pseudo-random sampling). A detailed comparative analysis of the
+properties compared to pseudo-random sampling. A detailed comparative analysis of the
 sampling methods can be found in [@kucherenko2015].
@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025
-to 2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
 Bracketed x-axis values represent the Spearman's correlation between reef depth and the
@@
 intermediate median area-relative cover between 2030 and 2060 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the cluster median timeseries and bands
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2060 within each bioregion. Solid lines represent the cluster median timeseries and bands
 represent the 95th percentile confidence intervals. Each management area is represented five
@@
 between 2030 and 2060 within each bioregion. Solid lines represent the median depth for each
-cluster across reefs and bands represent the distribution of depth values within each cluster. Displays results for ACCESS-ESM1-5
+cluster across reefs and bands represent the distribution of depth values within each
+cluster. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
@@
 
-![Distribution of GBRMPA [-@GBRMPA2020] satellite derived depth data coverage levels across 3806 possible reefs. Reefs below the 5%
-data coverage threshold (represented by the red vertical line) were removed from the
+![Distribution of GBRMPA [-@GBRMPA2020] satellite derived depth data coverage levels across
+3806 possible reefs. Reefs below the 5% data coverage threshold (represented by the red
+vertical line) were removed from the
 investigation.](../figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
@@
 intermediate median area-relative cover between 2030 and 2060 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the cluster median timeseries and bands
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2060 within each bioregion. Solid lines represent the cluster median timeseries and bands
 represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
@@
 cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
-investigation are represented in this figure. Annotations represent major coastal settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map fig-align="center"
-width="14.82cm"}
+investigation are represented in this figure. Annotations represent major coastal
+settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
+fig-align="center" width="14.82cm"}
 
@@
 total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. The colour of each point represents the base-10 log of scaled reef total connectivity
-strength. Displays results from median timeseries using
+threshold. The colour of each point represents the base-10 log of scaled reef total
+connectivity strength. Displays results from median timeseries using
 ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
@@
 the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines represent the median cover – DHW correlation level for each cluster and bands represent the distribution of correlation levels within each cluster. Displays results
-for ACCESS-ESM1-5
+lines represent the median cover – DHW correlation level for each cluster and bands
+represent the distribution of correlation levels within each cluster. Displays results for
+ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
@@
 area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the
-median DHW level for each cluster and bands represent the distribution of mean DHW levels within each cluster. Displays results for ACCESS-ESM1-5
+median DHW level for each cluster and bands represent the distribution of mean DHW levels
+within each cluster. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
@@
 
-![Mean timeseries DHW tolerance value, from 2035 to 2075, for reefs within each bioregion, separated into
-clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
-lowest median area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’
-clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
-2060 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the
-median DHW tolerance value for each cluster and bands represent the distribution of DHW-tolerance levels within each cluster. Displays results for ACCESS-ESM1-5
+![Mean timeseries DHW tolerance value, from 2035 to 2075, for reefs within each bioregion,
+separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2060 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
+lines represent the median DHW tolerance value for each cluster and bands represent the
+distribution of DHW-tolerance levels within each cluster. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
@@
 the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines represent the median proportion of habitable area occupied for each cluster and bands represent the distribution of occupied area values within each cluster. Displays
-results for ACCESS-ESM1-5
+lines represent the median proportion of habitable area occupied for each cluster and bands
+represent the distribution of occupied area values within each cluster. Displays results for
+ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
@@
 the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median source-to-sink ratio for each cluster and bands represent the distribution of source-to-sink ratios within each cluster.
-The vertical grey line represent a
-source-to-sink ratio of 0 (in base-10 log scale) indicating equal outgoing and incoming
-connectivity levels. Displays results for ACCESS-ESM1-5
+lines within each violin represent the median source-to-sink ratio for each cluster and
+bands represent the distribution of source-to-sink ratios within each cluster. The vertical
+grey line represent a source-to-sink ratio of 0 (in base-10 log scale) indicating equal
+outgoing and incoming connectivity levels. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
@@
 lines within each violin represent the median base-10 log of total connectivity strength for
-each cluster and bands represent the distribution of connectivity strength values within each cluster. Displays results for ACCESS-ESM1-5
+each cluster and bands represent the distribution of connectivity strength values within
+each cluster. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity

### 2025-08-15 paper/paper_draft.qmd
Move description of connectivity related aspect to same section
Also note comment for @eco-ben

@@
 
+### Connectivity modelling
+
+\*\* need information on GBR1 connectivity used \*\*
+
+Connectivity data from 24 days in total were used in this investigation. These data span six
+years from 2015 to 2020. The years 2015, 2016, 2018 and 2019 are each represented by
+connectivity matrices covering spawning periods over three days in each year (12 days in
+total), while 2017 and 2020 are each represented by five spawning days each, coming to a
+total of 22 days of connectivity matrices. Indicative connectivity strengths are implemented
+in ADRIA-CoralBlox as the mean of all available data for each location (i.e., mean of all 22
+spawning days). While the connectivity strengths do not vary from year to year within each
+simulation, they do vary between reefs whiuch are of varying sizes, providing sufficient
+heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
+spatial variability also enables investigations into the influence of connectivity strength
+and its role in driving recovery processes.
+
+The ratio of source-to-sink connectivity ($O:I$) for a target reef represents the strength
+of the reef's outgoing larval flow relative to it's incoming larval flow (@eq-so-to-si). If
+a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value. Incoming
+connections in this calculation, do not directly represent the larval supply gained as the
+population from which connections are coming from is not represented. A source-to-sink ratio
+greater than 1 (a value greater than 0 on a log scale) indicates a reef has greater outgoing
+than incoming larval flow.
+
+$$ O:I = \frac{(S_O/N_O)}{(S_I/N_I)} $$
+
+Where:
+
+-   $S$ is the sum of outgoing and incoming connections, indicating the total connectivity
+    strength.
+
+-   $N$ denotes the number of connections.
+
+-   $O$ denotes outgoing (source) connections from a reef.
+
+-   $I$ denotes incoming (sink) connections to a reef.
+
 ## Assessment framework
@@
 temporal behaviour.
-
-### Connectivity modelling
-
-\*\* need information on GBR1 connectivity used \*\*
-
-Connectivity data from 24 days in total were used in this investigation. These data span six
-years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices,
-while 2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity
-strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
-location (i.e., all 24 days). While the connectivity strengths do not vary from year to year
-within the simulation, they do vary between reefs of varying sizes, providing sufficient
-heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
-spatial variability also enables investigations into the influence of connectivity strength
-and its role in driving recovery processes.
-
-### Carbonate budget analysis
-
-Using median coral cover timeseries for each reef we calculated the number of years each
-reef maintains coral cover above a given percent threshold. The threshold represents the
-level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
-$\theta_{0}$ to indicate the budget equilibrium). Greater number of years above $\theta_{0}$
-therefore suggests greater resilience and opportunity for recovery.
-
-Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
-[@desbiens2021]. Given in situ carbonate budgets are influenced by (1) a range of processes;
-(2) the variety of approaches that could be used to measure those processes; and (3) the
-uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
-single precise $\theta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
-$\theta_{0}$ value for each individual reef.
-
-Given the uncertainties present, the proportion of modelled reefs that display capacity to
-maintain coral cover above a given $\theta_{0}$ threshold is examined. An indicative range
-of 10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
-al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of
-the lower and upper bounds respectively. Robustness of the conclusions drawn to the
-uncertainty in the precise value of $\theta_{0}$ for all reefs can then be assessed by using
-the indicative range.
-
-The relationship between the number of years above $\theta_{0}$ and median reef depth was
-then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
-adopted as reef depth and connectivity strength distributions are expected to be non-normal
-and highly skewed. Furthermore, reefs are naturally of different types and experience
-different conditions, and so the monotonic trends (whether the relationship consistently
-increase or decrease) rather than the exact quantative relationship was of interest for this
-analysis.
 
@@
 between low, medium and high coral cover clusters. These characteristics include reef median
-depth, mean timeseries DHW, mean timeseries DHW – tolerance level, Pearson’s correlation
+depth, mean timeseries DHW, mean timeseries DHW tolerance level, Pearson’s correlation
 between total coral cover and inversed DHW timeseries, proportion of coral habitable area
 occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and
-total strength of all larval connections between reefs. To analyse the DHW - tolerance
-levels of reefs, heritable DHW – tolerance values were tracked over timeseries in a timestep
-\* taxa \* reef \* scenario matrix. The mean timeseries DHW - tolerance was calculated over
-the first four scenarios for each GCM (four from 4096 scenarios per GCM) due to
-computational restraints, and then used to calculate an overall mean DHW – tolerance value
-for each reef under each GCM.
-
-The ratio of source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's outgoing larval flow relative to
-it's incoming larval flow (@eq-so-to-si). If a reef has no incoming connections, the $O:I$ equals the
-$\frac{S_O}{N_O}$ value. Incoming connections in this calculation, do not directly represent
-the larval supply gained as the population from which connections are coming from is not
-represented. A source-to-sink ratio greater than 1 (a value greater than 0 on a log scale)
-indicates a reef has greater outgoing than incoming larval flow.
-
-$$
-O:I = \frac{\frac{S_O}{N_O}}{\frac{S_I}{N_I}}
-$$ {#eq-so-to-si}
-
-Where:
-
--   $S$ denotes the total strength of connections.
-
--   $N$ denotes the number of connections.
-
--   $O$ denotes outgoing (source) connections from the target reef.
-
--   $I$ denotes incoming (sink) connections to the target reef.
+total strength of all larval connections between reefs. To analyse the DHW tolerance levels
+of reefs, heritable DHW tolerance values were tracked over timeseries in a matrix of shape
+timestep \* taxa \* reef \* scenario matrix. The mean timeseries DHW tolerance was
+calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due
+to computational restraints, and then used to calculate an overall mean DHW tolerance value
+for each reef under each GCM. **\[TI: Ben, is the last sentence here necessary?\]**
 
@@
 area, mean DHW tolerance level and GCM on cluster assignment.
+
+### Carbonate budget analysis
+
+Using median coral cover timeseries for each reef we calculated the number of years each
+reef maintains coral cover above a given percent threshold. The threshold represents the
+level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
+$\theta_{0}$ to indicate the budget equilibrium). Greater number of years above $\theta_{0}$
+therefore suggests greater resilience and opportunity for recovery.
+
+Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
+[@desbiens2021]. Given in situ carbonate budgets are influenced by (1) a range of processes;
+(2) the variety of approaches that could be used to measure those processes; and (3) the
+uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
+single precise $\theta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
+$\theta_{0}$ value for each individual reef.
+
+Given the uncertainties present, the proportion of modelled reefs that display capacity to
+maintain coral cover above a given $\theta_{0}$ threshold is examined. An indicative range
+of 10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
+al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of
+the lower and upper bounds respectively. Robustness of the conclusions drawn to the
+uncertainty in the precise value of $\theta_{0}$ for all reefs can then be assessed by using
+the indicative range.
+
+The relationship between the number of years above $\theta_{0}$ and median reef depth was
+then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
+adopted as reef depth and connectivity strength distributions are expected to be non-normal
+and highly skewed. Furthermore, reefs are naturally of different types and experience
+different conditions, and so the monotonic trends (whether the relationship consistently
+increase or decrease) rather than the exact quantitative relationship was of interest for
+this analysis.
 

### 2025-08-15 paper/paper_draft.qmd
Correct number of connectivity/spawning days represented

@@
 connectivity matrices covering spawning periods over three days in each year (12 days in
-total), while 2017 and 2020 are each represented by five spawning days each, coming to a
-total of 22 days of connectivity matrices. Indicative connectivity strengths are implemented
-in ADRIA-CoralBlox as the mean of all available data for each location (i.e., mean of all 22
+total), while 2017 and 2020 are each represented by six spawning days each, coming to a
+total of 24 days of connectivity matrices. Indicative connectivity strengths are implemented
+in ADRIA-CoralBlox as the mean of all available data for each location (i.e., mean of all 24
 spawning days). While the connectivity strengths do not vary from year to year within each
-simulation, they do vary between reefs whiuch are of varying sizes, providing sufficient
+simulation, they do vary between reefs which are of varying sizes, providing sufficient
 heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The

### 2025-08-15 src/ADRIA/HighResCoralStress/7_rf_analysis.jl
Update RF analysis to use train/test split
Arrives at more consistent and interesting results and better aligned with standard practice.

@@ -91,16 +91,71 @@ sp_cors = Dict(
 rng = Random.seed!(76)
 rf = @load RandomForestClassifier pkg = "DecisionTree"
 model = rf(; rng=rng)
-mach = MLJ.machine(model, X2, y2)
+
+train_size = ceil(Int64, nrow(X2) * 0.6)
+shuffle_set = shuffle(1:nrow(X2))
+
+train_X = X2[shuffle_set[1:train_size], :]
+test_X = X2[shuffle_set[train_size+1:end], :]
+train_y = y2[shuffle_set[1:train_size]]
+test_y = y2[shuffle_set[train_size+1:end]]
+
+mach = MLJ.machine(model, train_X, train_y)
 fit!(mach)
 
-cluster_est = MLJ.predict(mach, X2)
-y_pred_mode = predict_mode(mach, X2)
-
-μ_accuracy = mean(y_pred_mode .== y2)
+cluster_est = MLJ.predict(mach, train_X)
+y_pred_mode = predict_mode(mach, train_X)
+μ_accuracy = mean(y_pred_mode .== train_y)
 @info μ_accuracy  # 0.99
 
-cm = confusion_matrix(y_pred_mode, y2)
+cluster_est = MLJ.predict(mach, test_X)
+y_pred_mode = predict_mode(mach, test_X)
+
+μ_accuracy = mean(y_pred_mode .== test_y)
+@info μ_accuracy  # 0.66
+
+cm = confusion_matrix(y_pred_mode, test_y)
+cm.mat
+
+# Helper to get offdiagonal values from matrix
+offdiag_iter(A) = (ι for ι in CartesianIndices(A) if ι[1] ≠ ι[2])
+
+class_names = ["Low", "Med", "High"]
+for i in 1:3
+    class_name = class_names[i]
+
+    # True Positives (TP) - the diagonal
+    tp = cm.mat[i, i]
+
+    # False Positives (FP)
+    # Predicted as class i but actually other classes
+    fp = sum(cm.mat[i, :]) - tp
+
+    # False Negatives (FN)
+    # Actually class i, but predicted as others
+    fn = sum(cm.mat[:, i]) - tp
+
+    # True Negatives (TN): everything else
+    total_samples = sum(cm.mat)
+    tn = total_samples - tp - fp - fn
+
+    precision = tp / (tp + fp)
+    recall = tp / (tp + fn)
+    f1 = 2 * (precision * recall) / (precision + recall)
+
+    println("""
[…]

### 2025-08-15 paper/paper_draft.qmd

@@
 of reefs, heritable DHW tolerance values were tracked over timeseries in a matrix of shape
-timestep \* taxa \* reef \* scenario matrix. The mean timeseries DHW tolerance was
-calculated over the first four scenarios for each GCM (four from 4096 scenarios per GCM) due
-to computational restraints, and then used to calculate an overall mean DHW tolerance value
-for each reef under each GCM. **\[TI: Ben, is the last sentence here necessary?\]**
+timestep \* taxa \* reef \* scenario matrix.
 

### 2025-08-15 paper/paper_draft.qmd
Combine paras
Paragraphs are three sentences minimum
Move carbonate budget results
Flow should match the order in which they were introduced in the method section

@@
 properties compared to pseudo-random sampling. A detailed comparative analysis of the
-sampling methods can be found in [@kucherenko2015].
-
-For the purpose of scenario assessment, the resulting timeseries for each model run were
-scaled by the total area of the reef to represent cover as a percentage of the total
-estimated reef area. These timeseries of coral cover were then clustered based on their
-temporal behaviour.
+sampling methods can be found in [@kucherenko2015]. For the purpose of scenario assessment,
+the resulting timeseries for each model run were scaled by the total area of the reef to
+represent cover as a percentage of the total estimated reef area. These timeseries of coral
+cover were then clustered based on their temporal behaviour.
 
@@
 # Results
-
-## Reef carbonate budget
-
-As one might expect, the number of years experience cover above $\theta_{0}$ (the assumed
-positive carbonate budget threshold) substantially decreases as $\theta_{0}$ increases. The
-distribution of number of years above carbonate-cover thresholds is right-skewed, with many
-reefs experiencing low numbers of years above thresholds.
-
-Reefs with greater median depth levels maintain coral cover above indicative carbonate
-budget levels for a longer time frame compared to reefs with shallower median depths
-[@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate positive correlation
-with the number of years a reef maintains coral cover above the required threshold
-[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintenance correlation
-decreases as $\theta_{0}$ increases. This is likely due to an increasing number of reefs
-being unable to maintain coral cover above threshold levels as the threshold increases, with
-values becoming increasingly right-skewed. The base-10 log of total connectivity strength
-was found to have no correlation with the number of years a reef maintains cover above the
-required thresholds [@sfig-access-esm1-5-conn-carbonate]. Log connectivity strength -
-carbonate budget maintenance correlation slightly decreases as the required carbonate budget
-threshold increases.
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the
-number of years cover exceeds the carbonate budget threshold. Point colour represents the
-median reef depth level in metres. Displays results from median timeseries using
-ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
-fig-align="center" width="14.82cm"}
 
@@
 Similarly, there are no substantial differences between reef clusters in mean thermal
-tolerance levels @sfig-access-esm1-5-bioregion-dhwtol). There are no consistent differences
+tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol). There are no consistent differences
 across bioregions and GCMs between clusters in their reefs' initial proportion of habitable
@@
 connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
+
+## Reef carbonate budget
+
+As one might expect, the number of years experience cover above $\theta_{0}$ (the assumed
+positive carbonate budget threshold) substantially decreases as $\theta_{0}$ increases. The
+distribution of number of years above carbonate-cover thresholds is right-skewed, with many
+reefs experiencing low numbers of years above thresholds.
+
+Reefs with greater median depth levels maintain coral cover above indicative carbonate
+budget levels for a longer time frame compared to reefs with shallower median depths
+[@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate positive correlation
+with the number of years a reef maintains coral cover above the required threshold
+[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintenance correlation
+decreases as $\theta_{0}$ increases. This is likely due to an increasing number of reefs
+being unable to maintain coral cover above threshold levels as the threshold increases, with
+values becoming increasingly right-skewed. The base-10 log of total connectivity strength
+was found to have no correlation with the number of years a reef maintains cover above the
+required thresholds [@sfig-access-esm1-5-conn-carbonate]. Log connectivity strength -
+carbonate budget maintenance correlation slightly decreases as the required carbonate budget
+threshold increases.
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the
+number of years cover exceeds the carbonate budget threshold. Point colour represents the
+median reef depth level in metres. Displays results from median timeseries using
+ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
+alt="Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2075.
+The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents the median reef depth level in metres.
+Displays results from median timeseries using ACCESS-ESM1-5."
+fig-align="center" width="14.82cm"}
+
+## Partial Dependence
+
+The bioregion variable was excluded from partial dependence analysis due to its categorical
+nature providing limited interpretable information. The decision to exclude bioregions from
+the analysis is also justified by a low feature importance score (discussed
 

### 2025-08-15 paper/paper_draft.qmd
Add section describing partial dependence analysis

@@
 
-We used a multinomial linear regression model to quantify the influence of reef
-characteristics on reef cluster assignment. We model the influence of seven predictors,
-median depth, log total connectivity strength, log source to sink ratio, mean DHW, log reef
-area, mean DHW tolerance level and GCM on cluster assignment.
+### Partial Dependence Analysis
+
+A Partial Dependence Analysis was conducted to understand the relationship between
+individual features and time series cluster predictions using a trained Random Forest (RF)
+classifier [@friedman2001]. The analysis utilised the reef characteristics of interest
+including the median reef depth, mean DHW for the given scenario, total connectivity
+strength, and the outgoing-to-incoming connectivity ratio (\$O:I\$). The full dataset
+consisted of the timeseries classification of each of the 2429 reefs under the five GCMs
+explored, for a total of 12,145 samples. The dataset was randomly split into training (60%)
+and testing (40%) subsets to ensure model generalisability. The RF classifier achieved a 99%
+accuracy on the training set and 66% on the test set.
+
+While the 99% accuracy suggests the classifier is overfit to the training data, the 66% test
+accuracy indicates a meaningful relationship between modelled reef characteristics and their
+assigned clusters has been captured. A 3-fold cross-validation was also conducted, arriving
+at a similar 67% accuracy rate. The consistent level of accuracy across test and
+cross-validation demonstrates the generalised performance of the RF classifier is reliable.
+Furthermore, F1 scores for Low, Medium, and High were determined to be 0.7, 0.57 and 0.68
+respectively, indicating balanced performance across the cluster categories. Lower
+performance with the Medium cluster reflect the inherent difficulty of classifying
+transitional states in natural systems. For management applications, this level of
+performance provides valuable decision support when combined with expert knowledge and the
+model's probabilistic outputs.
+
+Partial dependence analysis was performed by applying the trained model to the test dataset.
+Values for individual reef characteristic were systematically (one-at-a-time) varied across
+a grid of 50 equally spaced points spanning its range, while all other features were left at
+their modelled values. The procedure creates (1) a modified test dataset, where the target
+reef characteristic was set to the grid value for all samples, (2) generates probabilistic
+predictions for all three cluster classes using the trained RF classifier, and (3) the mean
+predicted probability for each class was calculated across all test observations. The median
+was also assessed (not shown) but was found not to affect the interpretation of the analysis
+results. The process isolates the marginal effect of each feature by averaging over the
+natural distribution of all other features in the test dataset.
 

### 2025-08-15 paper/paper_draft.qmd
Move to match order in methods section

@@
 
+## Partial Dependence
+
+The bioregion variable was excluded from partial dependence analysis due to its categorical
+nature providing limited interpretable information. The decision to exclude bioregions from
+the analysis is also justified by a low feature importance score.
+
+![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
+Dependence Plots for reef characteristics of interest. Results for bioregions were excluded
+as they were found to be
+uninformative.](../figs/ts_cluster_rf_feature_analysis.png){#ts-cluster-pdp
+alt="Feature importance scores (Panel A) of the Random Forest classifier, and Partial Dependence Plots for reef characteristics of interest.
+Results for bioregions were excluded as they were found to be uninformative."
+fig-align="center" width="9.2cm"}
+
 ## Reef carbonate budget
@@
 ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
-alt="Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to 2075.
-The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents the median reef depth level in metres.
-Displays results from median timeseries using ACCESS-ESM1-5."
-fig-align="center" width="14.82cm"}
-
-## Partial Dependence
-
-The bioregion variable was excluded from partial dependence analysis due to its categorical
-nature providing limited interpretable information. The decision to exclude bioregions from
-the analysis is also justified by a low feature importance score (discussed
+fig-align="center" width="14.82cm"}
 

### 2025-08-15 paper/paper_draft.qmd
Initial go at incorporating rf analysis into results section
Have added text about results gained from rf analysis and pdps. Also moved rf figure to supplementary section.

@@
 
-### Partial Dependence Analysis
-
-A Partial Dependence Analysis was conducted to understand the relationship between
-individual features and time series cluster predictions using a trained Random Forest (RF)
-classifier [@friedman2001]. The analysis utilised the reef characteristics of interest
-including the median reef depth, mean DHW for the given scenario, total connectivity
-strength, and the outgoing-to-incoming connectivity ratio (\$O:I\$). The full dataset
-consisted of the timeseries classification of each of the 2429 reefs under the five GCMs
-explored, for a total of 12,145 samples. The dataset was randomly split into training (60%)
-and testing (40%) subsets to ensure model generalisability. The RF classifier achieved a 99%
-accuracy on the training set and 66% on the test set.
+#### Partial Dependence Analysis
+
+Partial Dependence Analysis was conducted to understand the relationship between individual
+features and time series cluster predictions using a trained Random Forest (RF) classifier
+[@friedman2001]. The analysis utilised the reef characteristics of interest including the
+median reef depth, mean DHW for the given GCM, total connectivity strength, and the
+outgoing-to-incoming connectivity ratio (\$O:I\$). The full dataset consisted of the
+timeseries cluster assignment of each of the 2429 reefs under the five GCMs explored, for a
+total of 12,145 samples. The dataset was randomly split into training (60%) and testing
+(40%) subsets to ensure model generalisability. The RF classifier achieved a 99% accuracy on
+the training set and 66% on the test set.
 
@@
 cross-validation demonstrates the generalised performance of the RF classifier is reliable.
-Furthermore, F1 scores for Low, Medium, and High were determined to be 0.7, 0.57 and 0.68
-respectively, indicating balanced performance across the cluster categories. Lower
+Furthermore, F1 performance scores for Low, Medium, and High were determined to be 0.7, 0.57
+and 0.68 respectively, indicating balanced performance across the cluster categories. Lower
 performance with the Medium cluster reflect the inherent difficulty of classifying
@@
 predicted probability for each class was calculated across all test observations. The median
-was also assessed (not shown) but was found not to affect the interpretation of the analysis
-results. The process isolates the marginal effect of each feature by averaging over the
-natural distribution of all other features in the test dataset.
+probability was also assessed (not shown) but was found not to affect the interpretation of
+the analysis results. The process isolates the marginal effect of each feature by averaging
+over the natural distribution of all other features in the test dataset.
 
@@
 
-```{julia}
-#| echo: false
-#| warning: false
-#| message: false
-#| results: asis
-#| label: tbl-access-esm1-5-bioregion-regression
-#| tbl-cap: Multinomial logistic regression coefficients for the statistical model containing median reef depth, base-10-log total connectivity strength, base-10-log source-to-sink ratio and ACCESS-ESM1-5 mean timeseries DHW value as predictor variables.
-ACCESS-ESM1-5 bioregion scale reef cluster assignment is the response variable with three levels, 'low' (regression reference level), 'medium' and 'high'.
-
-# using PrettyTables, Markdown
-# cd("../src")
-
-# include("../src/common.jl")
-
-# cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/ACCESS-ESM1-5_bioregion_cluster_regression_coefficients.csv"), DataFrame)
-# cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])
-
-# for name in names(cluster_regression)
-#     if isa(cluster_regression[:, name], Vector{Float64})
-#         cluster_regression[:, name] = round.(cluster_regression[:, name]; sigdigits=2)
-#     end
-# end
-
-# io = IOBuffer()
-
-# header = ["Response level ~ Term", "β estimate", "SE", "t-value", "Pr > |t|", "2.5%", "97.5%"]
-# pretty_table(io, cluster_regression, backend=Val(:markdown), header=header)
-
-# md_string = (String(take!(io)))
-# Markdown.parse(md_string)
-```
-
-\[**BG: Need to add quantification results to text for regressions.**\]
-
 In many bioregions, median reef depth decreases as cluster coral cover decreases, with reefs
@@
 
-## Partial Dependence
+### Partial Dependence
 
@@
 nature providing limited interpretable information. The decision to exclude bioregions from
-the analysis is also justified by a low feature importance score.
-
-![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
-Dependence Plots for reef characteristics of interest. Results for bioregions were excluded
-as they were found to be
-uninformative.](../figs/ts_cluster_rf_feature_analysis.png){#ts-cluster-pdp
-alt="Feature importance scores (Panel A) of the Random Forest classifier, and Partial Dependence Plots for reef characteristics of interest.
-Results for bioregions were excluded as they were found to be uninformative."
-fig-align="center" width="9.2cm"}
+the analysis is also justified by a low feature importance score (9.9%). Reef median depth
+and mean DHW level have the highest feature importance scores, accounting for 25.7% and
+23.7% predictive importance respectively. The probability of reefs being clustered into low
+and high clusters is greatest at shallow and deep depths respectively, with medium cluster
+reefs experiencing lower variation in assignment probability across depth
+[@sfig-ts-cluster-pdp]. The carrying capacity (total habitable area) accounts for 14.3%
+feature importance. Total strength and source-to-sink ratio connectivity metrics account for
+13.3% and 13.0% feature importance respectively. Partial dependence plots for carrying
+capacity, total connectivity strength and source-to-sink ratio indicate that their influence
+on cluster assignments is concentrated at the low range of predictor values
+[@sfig-ts-cluster-pdp]. This aligns with the right-skewed distributions of values across
+reefs for these three predictor variables. **\[BG: Will add either predictor distributions
+to these sub plots, or just in a general variable distribution plot in the supplementary
+material.\]**
 
@@
 
+![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
+Dependence Plots for reef characteristics of interest. Results for bioregions were excluded
+as they were found to be
+uninformative.](../figs/ts_cluster_rf_feature_analysis.png){#sfig-ts-cluster-pdp
+fig-align="center" width="9.2cm"}
+
 ![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef

### 2025-08-16 paper/paper_draft.qmd
Add equation cross reference to get label
Align to "predictors" over "features" and "characteristics"

@@
 
-$$ O:I = \frac{(S_O/N_O)}{(S_I/N_I)} $$
+$$
+O:I = \frac{(S_O/N_O)}{(S_I/N_I)}
+$$ {#eq-so-to-si}
 
@@
 features and time series cluster predictions using a trained Random Forest (RF) classifier
-[@friedman2001]. The analysis utilised the reef characteristics of interest including the
-median reef depth, mean DHW for the given GCM, total connectivity strength, and the
-outgoing-to-incoming connectivity ratio (\$O:I\$). The full dataset consisted of the
-timeseries cluster assignment of each of the 2429 reefs under the five GCMs explored, for a
-total of 12,145 samples. The dataset was randomly split into training (60%) and testing
-(40%) subsets to ensure model generalisability. The RF classifier achieved a 99% accuracy on
-the training set and 66% on the test set.
+[@friedman2001]. The analysis utilised the reef characteristics of interest as the
+predictors, including the median reef depth, mean DHW for the given GCM, total connectivity
+strength, and the outgoing-to-incoming connectivity ratio (\$O:I\$). The full dataset
+consisted of the timeseries cluster assignment of each of the 2429 reefs under the five GCMs
+explored, for a total of 12,145 samples. The dataset was randomly split into training (60%)
+and testing (40%) subsets to ensure model generalisability. The RF classifier achieved a 99%
+accuracy on the training set and 66% on the test set.
 
@@
 Partial dependence analysis was performed by applying the trained model to the test dataset.
-Values for individual reef characteristic were systematically (one-at-a-time) varied across
-a grid of 50 equally spaced points spanning its range, while all other features were left at
-their modelled values. The procedure creates (1) a modified test dataset, where the target
-reef characteristic was set to the grid value for all samples, (2) generates probabilistic
-predictions for all three cluster classes using the trained RF classifier, and (3) the mean
-predicted probability for each class was calculated across all test observations. The median
-probability was also assessed (not shown) but was found not to affect the interpretation of
-the analysis results. The process isolates the marginal effect of each feature by averaging
-over the natural distribution of all other features in the test dataset.
+Values for individual predictors were systematically (one-at-a-time) varied across a grid of
+50 equally spaced points spanning its range, while all other features were left at their
+modelled values. The procedure creates (1) a modified test dataset, where the target
+predictor was set to the grid value for all samples, (2) generates probabilistic predictions
+for all three cluster classes using the trained RF classifier, and (3) the mean predicted
+probability for each class was calculated across all test observations. The median was also
+assessed (not shown) but was found not to substantially influence the interpretation of the
+analysis results. The process isolates the marginal effect of each predictor by averaging
+over the natural distribution of all other representative reef characteristics in the test
+dataset.
 

### 2025-08-16 paper/paper_draft.qmd
Correcting timeseries to time series
Following advice online:

https://english.stackexchange.com/a/570738

@@
     Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities,
-    we analysed reef cover timeseries and the ability of reefs to maintain positive carbonate
+    we analysed reef cover time series and the ability of reefs to maintain positive carbonate
     production budgets under future conditions. Contrary to expectations, larval connectivity
     patterns did not correlate with increases in maintenance of positive carbonate budgets.
-    Instead, reef depth emerged as the primary predictor of cover-timeseries resilience and
+    Instead, reef depth emerged as the primary predictor of cover-time series resilience and
     maintenance of positive carbonate budgets, with deeper reefs benefiting from thermal
@@
 
-![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
+![Degree Heating Week time series (in °C - Weeks) for the GCMs selected. Colours represent
 the different management areas across the Great Barrier Reef. Green represents
@@
 represents the Townsville-Whitsunday management area. Solid lines represent the
-management-area median timeseries and bands represent the 95th percentile confidence
+management-area median time series and bands represent the 95th percentile confidence
 intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws fig-align="center"
@@
 sampling methods can be found in [@kucherenko2015]. For the purpose of scenario assessment,
-the resulting timeseries for each model run were scaled by the total area of the reef to
-represent cover as a percentage of the total estimated reef area. These timeseries of coral
+the resulting time series for each model run were scaled by the total area of the reef to
+represent cover as a percentage of the total estimated reef area. These time series of coral
 cover were then clustered based on their temporal behaviour.
 
-### Timeseries clustering
+### Time series clustering
 
@@
 predictors, including the median reef depth, mean DHW for the given GCM, total connectivity
-strength, and the outgoing-to-incoming connectivity ratio (\$O:I\$). The full dataset
-consisted of the timeseries cluster assignment of each of the 2429 reefs under the five GCMs
-explored, for a total of 12,145 samples. The dataset was randomly split into training (60%)
-and testing (40%) subsets to ensure model generalisability. The RF classifier achieved a 99%
-accuracy on the training set and 66% on the test set.
+strength, and the outgoing-to-incoming connectivity ratio. The full dataset consisted of the
+time series cluster assignment of each of the 2429 reefs under the five GCMs explored, for a
+total of 12,145 samples. The dataset was randomly split into training (60%) and testing
+(40%) subsets to ensure model generalisability. The RF classifier achieved a 99% accuracy on
+the training set and 66% on the test set.
 
@@
 
-Using median coral cover timeseries for each reef we calculated the number of years each
+Using median coral cover time series for each reef we calculated the number of years each
 reef maintains coral cover above a given percent threshold. The threshold represents the
@@
 levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs
-timeseries occur under ACCESS-CM2 [@fig-methods-dhws].
-
-![Reef area-relative coral cover timeseries clustered within each management area, for each
+time series occur under ACCESS-CM2 [@fig-methods-dhws].
+
+![Reef area-relative coral cover time series clustered within each management area, for each
 GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
@@
 clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2060 within each bioregion. Solid lines represent the cluster median timeseries and bands
+2060 within each bioregion. Solid lines represent the cluster median time series and bands
 represent the 95th percentile confidence intervals. Each management area is represented five
@@
 
-Across many bioregions timeseries clustering identified a ‘low’ cluster containing reefs
+Across many bioregions time series clustering identified a ‘low’ cluster containing reefs
 that suffer larger declines and generally have lower levels of coral cover than the other
@@
 
-In many bioregions reefs in the 'low' cover cluster have the lowest cover - DHW timeseries
+In many bioregions reefs in the 'low' cover cluster have the lowest cover - DHW time series
 correlation levels, while reefs in 'high' clusters have the highest correlation levels
 (@sfig-access-esm1-5-bioregion-dhwcor). Conversely, there are no consistent patterns across
-bioregions in reef area-relative cover and mean timeseries DHW levels, with clusters having
+bioregions in reef area-relative cover and mean time series DHW levels, with clusters having
 similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean).
@@
 importance of thermal tolerance on cover outcomes may be due to reefs experiencing high
-levels of thermal stress early in projected timeseries. High - early timeseries thermal
+levels of thermal stress early in projected time series. High - early time series thermal
 stress events may prevent the intergenerational adaptation of corals to thermal stress and
@@
 
-![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
+![Reef Degree Heating Week time series clustered within each management area, for each GCM
 analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
@@
 clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2060 within each bioregion. Solid lines represent the cluster median timeseries and bands
+2060 within each bioregion. Solid lines represent the cluster median time series and bands
 represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
@@
 threshold. The colour of each point represents the base-10 log of scaled reef total
-connectivity strength. Displays results from median timeseries using
+connectivity strength. Displays results from median time series using
 ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
@@
 
-![Reef area-relative coral cover timeseries clustered within each bioregion. ‘Low’ clusters
+![Reef area-relative coral cover time series clustered within each bioregion. ‘Low’ clusters
 (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
@@
 clusters with the highest median area-relative cover between 2030 and 2060 within each
-bioregion. Solid lines represent the cluster median timeseries and bands represent the 95th
+bioregion. Solid lines represent the cluster median time series and bands represent the 95th
 percentile confidence intervals. Displays results for ACCESS-ESM1-5
@@
 ![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
 clusters with the lowest median area-relative cover between 2030 and 2060 within each
@@
 
-![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
-assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
+![Mean time series DHW values for reefs within each bioregion, separated into clusters
+assigned by time series clustering. ‘Low’ clusters (green) are clusters with the lowest
 median area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters
@@
 
-![Mean timeseries DHW tolerance value, from 2035 to 2075, for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+![Mean time series DHW tolerance value, from 2035 to 2075, for reefs within each bioregion,
+separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
 clusters with the lowest median area-relative cover between 2030 and 2060 within each
@@
 ![Initial proportion of coral habitable area occupied by corals for reefs within each
-bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green)
-are clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines represent the median proportion of habitable area occupied for each cluster and bands
-represent the distribution of occupied area values within each cluster. Displays results for
-ACCESS-ESM1-5
+bioregion, separated into clusters assigned by time series clustering. ‘Low’ clusters
+(green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
+each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
+area-relative cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2060 within each
+bioregion. Solid lines represent the median proportion of habitable area occupied for each
+cluster and bands represent the distribution of occupied area values within each cluster.
+Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
@@
 ![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
 clusters with the lowest median area-relative cover between 2030 and 2060 within each
@@
 ![Total connectivity strength (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are
+separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
 clusters with the lowest median area-relative cover between 2030 and 2060 within each

### 2025-08-16 paper/paper_draft.qmd
Simplifying notation
Streamlining time series clustering description
Removing some unnecessary detail

Implementation details, e.g., about size and shape of matrices, are not necessary for this kind of paper. If needed, they can be explained in supplementaries.

Add section in supplementary for expanded info on time series clustering (may remove, as it's described in cited paper...).

Also some comments for @eco-ben

@@
 $$
-O:I = \frac{(S_O/N_O)}{(S_I/N_I)}
+O:I = \frac{S_O/N_O}{S_I/N_I}
 $$ {#eq-so-to-si}
@@
 
-To identify groups of reefs that are resilient, intermediate, and non-resilient, we
-clustered reefs into three clusters based on their temporal behaviour as indicated by coral
-cover over time, using timeseries from 2025-2075. The Complexity-Invariant Distance (CID)
-between each timeseries was calculated to identify timeseries that behave similarly
-[@batista2014]. The CID corrects the Euclidean distance between pairs of timeseries (which
-accounts for magnitude differences) with the complexity of each timeseries (obtained through
-a measure of their variability) to ensure reefs are clustered based on their underlying
-temporal dynamics rather than simply their average coral cover. The process creates a
-distance matrix of n \* n dimensions (where n is the number of timeseries in the group) that
-is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The three reef
-clusters are assigned a qualitative level from "low", "medium" and "high" based on their
-relative median timeseries over the 2030-2060 period. Assigning cluster labels based on this
-period prevents cluster labels being assigned during the steeply declining period from
-2025-2030 and during the post-2060 period when many reefs have cover below 5% of their area.
-
-Timeseries clustering analyses were performed at the management area and reefal bioregion
-scale (defined in GBRMPA [-@GBRMPA2024]). Additional analyses were also performed at the
-whole-of-GBR scale. These were found to lead to identical conclusions and so are not shown
-here. To compare timeseries clustering results across GCMs, management area scale clustering
-results are used to preserve coarse scale latitudinal differences between regions, while
-maintaining ease of comparison and visualisation. These comparisons include quantification
-of differences between low and high cover clusters across management regions under each GCM
-using the Complexity-Invariant Distance between cluster median timeseries. To assess how
-different reef characteristics influence timeseries clustering at a finer scale, bioregion
-results are used to capture patterns occurring within individual clusters of reefs. Results
-of all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for
-those interested.
-
-Reefs in each timeseries cluster were compared to identify characteristics that differ
-between low, medium and high coral cover clusters. These characteristics include reef median
-depth, mean timeseries DHW, mean timeseries DHW tolerance level, Pearson’s correlation
-between total coral cover and inversed DHW timeseries, proportion of coral habitable area
-occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and
-total strength of all larval connections between reefs. To analyse the DHW tolerance levels
-of reefs, heritable DHW tolerance values were tracked over timeseries in a matrix of shape
-timestep \* taxa \* reef \* scenario matrix.
+Reefs were clustered into three qualitative categories based on their temporal behaviour
+indicated by coral cover over time. The three categories were Low, Medium, and High,
+indicating their relative ability to maintain coral cover and thus their structural
+resilience. The Complexity-Invariant Distance (CID) between each time series was calculated
+to identify similarities in temporal behaviour [@batista2014]. The CID applies a correction
+factor to the Euclidean distance between pairs of time series to obtain a measure of their
+similarity or dissimilarity. The adopted approach ensures reefs are clustered based on their
+temporal dynamics as opposed to, for example, naively clustering by their mean coral cover.
+Clustering similar time series is achieved through the use of k-medoids clustering [cf.
+@steinmann2020]. Further details on the time series clustering approach are found in the
+supplementary materials.
+
+The time series clustering was applied over the time frame between 2030 and 2060. Spatially,
+the analyses were conducted for each GBR management area and at the scale of each reefal
+bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
+whole-of-GBR scale but were found to lead to identical results **\[TI: Ben, compared to
+what, the bioregion or the management area results?\]** and so are not shown here. To
+compare time series clustering results across GCMs, management area scale clustering results
+are used to preserve coarse scale latitudinal differences between regions, while maintaining
+ease of comparison and visualisation. These comparisons include quantification of
+differences between low and high cover clusters across management regions under each GCM
+using the CID between cluster median time series. To assess how different reef
+characteristics influence time series clustering at a finer spatial scale, bioregion results
+are used to capture patterns occurring within individual clusters of reefs. Results of all
+analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for those
+interested.
+
+Reefs in each time series cluster were compared to identify characteristics that differ
+between Low, Medium and High categories. These characteristics include reef median depth,
+mean time series DHW, mean time series DHW tolerance level **\[TI: Ben, still correct? Still
+included somewhere?\]**, Pearson’s correlation between total coral cover and inverse DHW
+time series, proportion of coral habitable area occupied by corals in the first timestep,
+ratio of source-to-sink larval connectivity and total strength of all larval connections
+between reefs.
 
@@
 
+### Time series clustering
+
+**\[TI: To be revisited\]**
+
+The CID corrects the Euclidean distance between pairs of time series (which accounts for
+magnitude differences) with the complexity of each time series (obtained through a measure
+of their variability) to ensure reefs are clustered based on their underlying temporal
+dynamics rather than simply their average coral cover.
+
+The process creates a distance matrix of n \* n dimensions (where n is the number of time
+series in the group) that is clustered using a k-medoids clustering algorithm [cf.
+@steinmann2020]. The three reef clusters are assigned a qualitative categories from Low,
+Medium and High.
+
 ## ACCESS-ESM1-5

### 2025-08-16 paper/paper_draft.qmd
Reinsert contextual detail around clustering
Correct typo

@@
 
-The time series clustering was applied over the time frame between 2030 and 2060. Spatially,
-the analyses were conducted for each GBR management area and at the scale of each reefal
+The time series clustering was applied over the time frame between 2030 and 2060. The
+selected time frame prevents the classification from being overly influenced by any steep
+declines in the initial years of simulations, and avoids the post-2060 time period where
+reefs are projected to be under severe stress and in decline [@bozec2025]. Spatially, the
+analyses were conducted for each GBR management area and at the scale of each reefal
 bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
@@
 characteristics of refugia and more prolonged structural resilience under climate change
-compared to shallower reefs. Additionally, Lui, Callaghan and Baldock [-@liu2024] suggest
+compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest
 that rubble instability is inversely correlated with reef depth, possibly limiting the

### 2025-08-16 paper/paper_draft.qmd
Standardizing text
low medium high -> Low Medium High
management area -> Management area

clusters in "low clusters" -> categories
The above is to avoid confusion:
- Reef clusters, time series clusters

features -> reef characteristics
This is to avoid confusion between reef features (their spatial definitions) and features in the sense of inputs/factors of an ML model

@@
 [@GBRMPA2022]. The reef definitions define 3806 reefs across the GBR. An indicative map of
-the GBR marine park including the Marine Park management areas [@GBRMPA2007] and the
+the GBR marine park including the Marine Park Management areas [@GBRMPA2007] and the
 corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
@@
 This process removed 842 reefs, or 22%, from the initial set of 3806 reefs. Furthermore,
-reefs that are not associated with GBRMPA management areas [@GBRMPA2007] or reefal
+reefs that are not associated with GBRMPA Management areas [@GBRMPA2007] or reefal
 bioregions [@GBRMPA2024] were also removed from the investigation. Bioregions which
@@
 
-![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all
 considered reefs (points). Colour-coded areas outline GBR marine park management regions,
@@
 ![Degree Heating Week time series (in °C - Weeks) for the GCMs selected. Colours represent
-the different management areas across the Great Barrier Reef. Green represents
+the different Management areas across the Great Barrier Reef. Green represents
 Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
-represents the Townsville-Whitsunday management area. Solid lines represent the
+represents the Townsville-Whitsunday Management area. Solid lines represent the
 management-area median time series and bands represent the 95th percentile confidence
@@
 reefs are projected to be under severe stress and in decline [@bozec2025]. Spatially, the
-analyses were conducted for each GBR management area and at the scale of each reefal
+analyses were conducted for each GBR Management area and at the scale of each reefal
 bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
 whole-of-GBR scale but were found to lead to identical results **\[TI: Ben, compared to
-what, the bioregion or the management area results?\]** and so are not shown here. To
-compare time series clustering results across GCMs, management area scale clustering results
+what, the bioregion or the Management area results?\]** and so are not shown here. To
+compare time series clustering results across GCMs, Management area scale clustering results
 are used to preserve coarse scale latitudinal differences between regions, while maintaining
@@
 #| label: tbl-cluster-cid
-#| tbl-cap: Complexity invariant distance (CID) between low and high cluster median timeseries in each management area under each GCM.
-CID values are calculated for percentage cover timeseries (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) timeseries (@sfig-gcm-dhw-trajectories).
-Complexity invariant distance represents the euclidean distance between timeseries, corrected by the complexity of the two timeseries.
+#| tbl-cap: Complexity invariant distance (CID) between low and high cluster median time series in each management area under each GCM.
+CID values are calculated for percentage cover time series (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) time series (@sfig-gcm-dhw-trajectories).
+Complexity invariant distance represents the euclidean distance between time series, corrected by the complexity of the two time series.
 CID values are used to quantify overall differences between these two cluster levels at management area and GCM levels.
-CID values for percentage cover and DHW timeseries are not directly comparable as the timeseries use different units.
+CID values for percentage cover and DHW time series are not directly comparable as the time series use different units.
 
@@
 number of years cover exceeds the carbonate budget threshold. Point colour represents the
-median reef depth level in metres. Displays results from median timeseries using
+median reef depth level in metres. Displays results from median time series using
 ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
@@
 ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future. Differences
-between low, medium and high reef clusters in cover timeseries are most notable under these
+between Low, Medium and High reef clusters in cover time series are most notable under these
 two GCMs [@tbl-cluster-cid; @fig-gcm-cover-trajectories]. Maintenance of coral cover into
@@
 
-The large differences in cover timeseries seen across the GCMs suggest that it is important
+The large differences in cover time series seen across the GCMs suggest that it is important
 to consider uncertainty in future conditions when assessing possible biological responses to
@@
 Reefs in different clusters largely do not differ in mean modelled DHW levels experienced,
-and exhibit overall similar DHW timeseries. While these reefs experience similar magnitude
+and exhibit overall similar DHW time series. While these reefs experience similar magnitude
 DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress

### 2025-08-16 paper/paper_draft.qmd
Tidy up time series discussion

@@
 
-Each Global Climate Model (GCM) shows similar relationships between reef clusters and
-contextual analysis factors, thus further comparisons of these clusters for each analysis
-factor are only shown for ACCESS-ESM1-5 (an intermediate Equilibrium Climate Sensitivity
-scenario [@sfig-ecs]). Results for the additional GCMs can be found at Grier and Iwanaga
-[-@grier2025]. However, there are substantial differences in the longevity of reef
-resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover
-timeseries are displayed for each GCM (displayed clustered at management-area scale to
-preserve coarse spatial differences in cover trajectories) (@fig-gcm-cover-trajectories).
-
+There were substantial differences in the maintenance of coral cover post 2030 between the
+GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs by
+their categorisation (Low, Medium and High). Results are displayed at the Management area
+scale to illustrate the spatial differences in cover trajectories. Of the GCMs explored,
 NorESM2-MM has the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit
-continuing recovery and decline dynamics up to 2075 under this possible climate future.
-Recovery phases are predominantly seen in the ‘high’ cover cluster. The ‘medium’ cluster,
-and to a lesser degree the ‘low’ cluster, also exhibit periods of recovery and increasing
-proportions of coral cover up to 2045. Under NorESM2-MM the Far Northern management area has
-lower CID distances between low and high cover clusters than in other management areas
-[@tbl-cluster-cid], this is reflected in the low degree of cover maintenance
-[@fig-gcm-cover-trajectories]. ACCESS-ESM1-5 has an intermediate ECS value of 3.87°C which
-results in intermediate levels of coral cover maintenance (between those of lower and higher
-ECS GCMs) [@fig-gcm-cover-trajectories], reflected in intermediate CID distance values
-within most management areas [@tbl-cluster-cid]. In Townsville-Whitsunday and Far Northern
-management areas, reefs in the high cluster are able to maintain coral cover levels around
-20% to 2050 under ACCESS-ESM1-5. Under ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and
-GFDL-CM4 (4.1°C) GCMs cover trajectories are largely declining in all management areas,
-reflected in lower CID distance values than other GCMs [@tbl-cluster-cid].
-
-Under each GCM, in all management areas, low, medium and high cluster reefs have low levels
-of distinction between DHW trajectories (@sfig-gcm-dhw-trajectories). The highest peak DHW
-levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs
-time series occur under ACCESS-CM2 [@fig-methods-dhws].
-
-![Reef area-relative coral cover time series clustered within each management area, for each
-GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2060 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2060 within each bioregion. Solid lines represent the cluster median time series and bands
-represent the 95th percentile confidence intervals. Each management area is represented five
-times (for each GCM), with each GCM displayed
-horizontally.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
-fig-align="center" width="14.82cm"}
-
-Comparing across GCMs, it is common for reefs to switch cluster level, including from low to
-high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). Of 2429
-reefs, 20% (503) of reefs have consistent management area scale cluster assignment across
-all GCMs. Of the 503 consistently assigned reefs, 49% are within the Far Northern management
-area, with 7, 13 and 31% occurring in the Cairns/Cooktown, Townsville/Whitsunday and
-Mackay/Capricorn management areas respectively [@sfig-gcm-cluster-map]. Of the 503
-consistently assigned reefs, 32, 7 and 61% are clustered into low, medium and high clusters
-respectively. High assignment variability across GCMs is expected as spatial differences in
-GCM DHW timeseries result in reefs being impacted at different relative magnitudes within
-their management area across GCMs.
+continuing recovery and decline dynamics up to 2075 under this hypothetical climate future.
+
+Unsurprisingly, recovery phases are predominantly seen in the reefs in the High category,
+with Medium and Low exhibiting lesser probability of such periods of recovery. Generally,
+recovery and increases in coral cover are visible in simulated results up to 2045. Under
+NorESM2-MM, the Far Northern Management area were found to have the most similar temporal
+behaviour between Low and High categories compared to other Management areas
+[@tbl-cluster-cid] due to the low degree of coral cover [@fig-gcm-cover-trajectories].
+
+Intermediate levels of coral cover maintenance can be seen in ACCESS-ESM1-5 (ECS value of
+3.87°C) when compared to the other GCMs (of higher and lower ECS values). Under these
+intermediate conditions (in relative terms), there is potential for reefs in the High
+category to maintain coral cover levels around 20% to 2050. The highest peak DHW levels
+occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs time
+series occur under ACCESS-CM2 [@fig-methods-dhws]. Under conditions represented by high ECS
+value GCMs - specifically, ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and GFDL-CM4
+(4.1°C) - all reefs are largely in decline across all management areas from 2055
+[@tbl-cluster-cid].
+
+![Time series of coral cover (relative to reef area) categorised within each Management area
+(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. The
+time series are categorised as "Low" (green), "Medium" (in orange), and "High" median cover
+(in blue). Solid lines represent the cluster median time series and bands represent the 95th
+percentile confidence
+intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
+fig-align="center" width="14.82cm"}
+
+**\[TI: Ben, Just noticed - we need to make the rows (Management areas) go from North to
+South!\]**
+
+Comparing across GCMs, it is common for reefs to switch between categories, including from
+Low to High and vice versa (@sfig-gcm-bioregion-cluster-assignment). Of 2429 reefs, 20%
+(503) of reefs have consistent category assignment across all GCMs. Of the 503 consistently
+assigned reefs, 49% are within the Far Northern Management area, with 7%, 13% and 31%
+occurring in the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management
+areas respectively [@sfig-gcm-cluster-map]. Of the 503 consistently assigned reefs, 32%, 7%
+and 61% are clustered into Low, Medium and High clusters respectively. High assignment
+variability across GCMs is expected as spatial differences in a given GCM's DHW trajectory
+result in reefs being impacted at different relative magnitudes within each Management
+areas.
 

### 2025-08-16 paper/paper_draft.qmd
Tidy up bioregion scale

@@
 
-## Bioregion scale clustering
-
-Across many bioregions time series clustering identified a ‘low’ cluster containing reefs
-that suffer larger declines and generally have lower levels of coral cover than the other
-clusters, a ‘medium’ cluster with intermediate levels of coral cover, and a ‘high’ cluster
-with greater levels of cover recovery, with persistence to 2050 in some bioregions
-(@sfig-access-esm1-5-bioregion-timeseries).
-
-In many bioregions, median reef depth decreases as cluster coral cover decreases, with reefs
-within the ‘high’ cluster commonly having the greatest median reef depths within the
-bioregion (@fig-access-esm1-5-bioregion-depth).
-
-![Median depth for reefs within each bioregion, separated into clusters assigned by
-timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
-area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange)
-are clusters with intermediate median area-relative cover between 2030 and 2060 within each
-bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
-between 2030 and 2060 within each bioregion. Solid lines represent the median depth for each
-cluster across reefs and bands represent the distribution of depth values within each
-cluster. Displays results for ACCESS-ESM1-5
+### Bioregion scale clustering
+
+In contrast to the broad temporal behaviour at the Management area scale, the relationship
+between reef characteristics **\[TI: Ben, I think this is what you meant by "contextual
+analysis factors"? depth, connectivity, dhw, carrying capacity etc?\]** and reefs' assigned
+categories were found to be similar at the bioregion scale **\[TI: Ben, please confirm my
+changes/edits are correct\]**. Results are therefore only shown and discussed for
+ACCESS-ESM1-5, an intermediate Equilibrium Climate Sensitivity scenario [@sfig-ecs]. Those
+interested in results for the other assessed GCMs are referred to Grier and Iwanaga
+[-@grier2025]. Across bioregions, reefs in the High category not only had greater levels of
+coral recovery but displayed persistence to 2050 [@sfig-access-esm1-5-bioregion-timeseries].
+Reefs in the High category were consistently found to have the greatest median reef depths
+across bioregions [@fig-access-esm1-5-bioregion-depth].
+
+![Median depth for reefs within each bioregion, separated into clusters assigned by time
+series clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative
+cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters
+with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030
+and 2060 within each bioregion. Solid lines represent the median depth for each cluster
+across reefs and bands represent the distribution of depth values within each cluster.
+Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
@@
 
-In many bioregions reefs in the 'low' cover cluster have the lowest cover - DHW time series
-correlation levels, while reefs in 'high' clusters have the highest correlation levels
+In many bioregions reefs in the Low category have the lowest correlation between coral cover
+and DHW whereas reefs in the High category were found to have the strongest correlation
 (@sfig-access-esm1-5-bioregion-dhwcor). Conversely, there are no consistent patterns across
-bioregions in reef area-relative cover and mean time series DHW levels, with clusters having
-similar mean DHW levels in many bioregions (@sfig-access-esm1-5-bioregion-dhwmean).
-Similarly, there are no substantial differences between reef clusters in mean thermal
-tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol). There are no consistent differences
-across bioregions and GCMs between clusters in their reefs' initial proportion of habitable
-area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion). Across most
-bioregions there are not consistent differences between clusters in connectivity metrics
-such as source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and total
-connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
-
-### Partial Dependence
+bioregions when comparing their temporal behaviour with respect to their reef area, relative
+cover, and mean of DHWs (@sfig-access-esm1-5-bioregion-dhwmean). There were no consistent
+differences across bioregions and GCMs between clusters in their reefs' initial proportion
+of habitable area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion).
+Across most bioregions there were not consistent differences between clusters in
+connectivity metrics such as source-to-sink connectivity ratio
+(@sfig-access-esm1-5-bioregion-logsosi) and total connectivity strength
+(@sfig-access-esm1-5-bioregion-totalconnectivity).
+
+**\[TI: Note, I'm not sure if this section is interesting enough to keep now... let's
+discuss.\]**
 

### 2025-08-16 paper/paper_draft.qmd
Expand on partial dependence analysis
Bring important figure back to main text

@@
 
-The bioregion variable was excluded from partial dependence analysis due to its categorical
-nature providing limited interpretable information. The decision to exclude bioregions from
-the analysis is also justified by a low feature importance score (9.9%). Reef median depth
-and mean DHW level have the highest feature importance scores, accounting for 25.7% and
-23.7% predictive importance respectively. The probability of reefs being clustered into low
-and high clusters is greatest at shallow and deep depths respectively, with medium cluster
-reefs experiencing lower variation in assignment probability across depth
-[@sfig-ts-cluster-pdp]. The carrying capacity (total habitable area) accounts for 14.3%
-feature importance. Total strength and source-to-sink ratio connectivity metrics account for
-13.3% and 13.0% feature importance respectively. Partial dependence plots for carrying
-capacity, total connectivity strength and source-to-sink ratio indicate that their influence
-on cluster assignments is concentrated at the low range of predictor values
-[@sfig-ts-cluster-pdp]. This aligns with the right-skewed distributions of values across
-reefs for these three predictor variables. **\[BG: Will add either predictor distributions
-to these sub plots, or just in a general variable distribution plot in the supplementary
-material.\]**
-
-## Reef carbonate budget
-
-As one might expect, the number of years experience cover above $\theta_{0}$ (the assumed
-positive carbonate budget threshold) substantially decreases as $\theta_{0}$ increases. The
-distribution of number of years above carbonate-cover thresholds is right-skewed, with many
-reefs experiencing low numbers of years above thresholds.
-
-Reefs with greater median depth levels maintain coral cover above indicative carbonate
-budget levels for a longer time frame compared to reefs with shallower median depths
-[@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate positive correlation
-with the number of years a reef maintains coral cover above the required threshold
-[@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget maintenance correlation
-decreases as $\theta_{0}$ increases. This is likely due to an increasing number of reefs
-being unable to maintain coral cover above threshold levels as the threshold increases, with
-values becoming increasingly right-skewed. The base-10 log of total connectivity strength
-was found to have no correlation with the number of years a reef maintains cover above the
-required thresholds [@sfig-access-esm1-5-conn-carbonate]. Log connectivity strength -
-carbonate budget maintenance correlation slightly decreases as the required carbonate budget
-threshold increases.
+### Partial dependence
+
+A Partial Dependence Analysis was conducted using a Random Forest classifier to identify
+reef characteristics that influence its temporal behaviour, and thus its cluster assignment
+into Low, Medium, or High. These include, for each of the 2429 reefs assessed, the
+indicative median reef depth, the mean DHW experienced, its coral carrying capacity, total
+connectivity strength and source-to-sink ratio. Reefs' bioregion membership was excluded
+from this analysis due to its categorical nature providing limited interpretable
+information, and is further justified by its low feature importance score of 10%, the lowest
+of all predictors [-@fig-ts-cluster-pdp, Panel A]. Reef median depth and mean DHW level have
+the highest feature importance scores, accounting for 25% and 23% predictive importance
+respectively. The carrying capacity of a reef accounts for 14.3% feature importance.
+Connectivity strength and source-to-sink ratio both had feature importance scores of \~13%.
+
+Reefs have the greatest probability of being clustered into Low if shallow, and High at
+greater depths, with medium cluster reefs exhibiting a lower, and stable, variation in
+assignment probability across depth ranges [@fig-ts-cluster-pdp, Panel B]. A large increase
+in the probability of a reef being categorised as High can be seen between 10 and 12 meters
+depth. This is at the edge of what is feasible with current technologies and restoration
+approaches **\[TI: Citation here\]**, but indicates a depth range that could be adopted to
+maximise longevity and benefits of, for example, coral seeding activities. With regard to
+DHWs, assignment probability is roughly equal across the three categories up to 6 DHW. A
+sharp delineation can be seen \> 6 DHW when comparing High with other categories, with lower
+assignment probability (\~25%) compared to Medium and Low (\~40%).
+
+Carrying capacity, source-to-sink ratio and total connectivity strength and indicate that
+their influence on cluster assignments is concentrated at the low range of predictor values
+[@fig-ts-cluster-pdp]. This aligns with the right-skewed distributions of values across
+reefs for these three predictor variables. Beyond this lower range, the partial dependence
+for these reef characteristics becomes near constant, indicating that interactions with
+other reef characteristics are occurring at these values which is also evidenced by their
+intermediate feature importance scores.
+
+**\[BG: Will add either predictor distributions to these sub plots, or just in a general
+variable distribution plot in the supplementary material.\]**
+
+![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
+Dependence Plots for reef characteristics of interest indicating the probability of a reef
+being classified to one of the three categories (Panel B). Partial Dependence Plots for
+bioregions were excluded as they were found to be
+uninformative.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp
+fig-align="center" width="9.2cm"}
 
@@
 
-![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
-Dependence Plots for reef characteristics of interest. Results for bioregions were excluded
-as they were found to be
-uninformative.](../figs/ts_cluster_rf_feature_analysis.png){#sfig-ts-cluster-pdp
-fig-align="center" width="9.2cm"}
-
 ![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef

### 2025-08-16 paper/paper_draft.qmd
attempt cleanup of reef carbonate budget

@@
 
+## Reef carbonate budget
+
+Reef median depth has a moderate positive correlation with the number of years a reef
+maintains coral cover above the assumed carbonate budget threshold required to sustain live
+coral cover ($\theta_{0}$). Greater median depth is a key characteristic defining reefs that
+sustain coral cover above $\theta_{0}$ [@fig-access-esm1-5-depth-carbonate]. Unsurprisingly,
+the number of years above $\theta_0$ substantially decreases as $\theta_0$ is increased, as
+does the Spearman's correlation. This is likely due to an increasing number of reefs being
+unable to maintain coral cover above $\theta_0$ as the assumed threshold is increased, with
+values **\[TI: Ben, could you clarify which values? Coral cover or years above
+threshold?\]** becoming increasingly right-skewed. In contrast, log10-transformed total
+connectivity strength ($\text{log10}(S)$) was found to have no correlation with the number
+of years a reef maintains cover above the required thresholds
+[@sfig-access-esm1-5-conn-carbonate] **\[TI: Ben, because we are comparing depth and
+connectivity, this figure needs to be shown in the main text\]**. The correlation between
+$\text{log10}(S)$ and $\theta_0$ slightly decreases as the assumed threshold for $\theta_0$
+increases.
+
 ![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to

### 2025-08-16 paper/paper_draft.qmd
Add note for all authors!
Correct timeseries clustering timespan to 2025-2075

@@
 
-The time series clustering was applied over the time frame between 2030 and 2060. The
-selected time frame prevents the classification from being overly influenced by any steep
-declines in the initial years of simulations, and avoids the post-2060 time period where
-reefs are projected to be under severe stress and in decline [@bozec2025]. Spatially, the
-analyses were conducted for each GBR Management area and at the scale of each reefal
+The time series clustering was applied over the time frame between 2025 and 2075. Spatially,
+the analyses were conducted for each GBR management area and at the scale of each reefal
 bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
@@
 paragraph needs to be revisited\]**
+
+**\[TI note: Important to speak to interesting depth range at edge of where coral planting
+might feasibly/viably occur with current approaches\]**
 
@@
 series in the group) that is clustered using a k-medoids clustering algorithm [cf.
-@steinmann2020]. The three reef clusters are assigned a qualitative categories from Low,
-Medium and High.
+@steinmann2020]. The three reef clusters are labelled with qualitative-ordered categories
+from Low, Medium and High based on their median cover relative to each other cluster over
+the 2030-2060 period.The selected time frame prevents the classification from being overly
+influenced by any steep declines in the initial years of simulations, and avoids the
+post-2060 time period where reefs are projected to be under severe stress and in a declined
+state [@bozec2025].
 

### 2025-08-16 paper/paper_draft.qmd
Update carbonate budget plots to indicate mean number of years
Highlight the right-skewedness of the number of years above thresholds

@@
 does the Spearman's correlation. This is likely due to an increasing number of reefs being
-unable to maintain coral cover above $\theta_0$ as the assumed threshold is increased, with
-values **\[TI: Ben, could you clarify which values? Coral cover or years above
-threshold?\]** becoming increasingly right-skewed. In contrast, log10-transformed total
-connectivity strength ($\text{log10}(S)$) was found to have no correlation with the number
-of years a reef maintains cover above the required thresholds
-[@sfig-access-esm1-5-conn-carbonate] **\[TI: Ben, because we are comparing depth and
-connectivity, this figure needs to be shown in the main text\]**. The correlation between
-$\text{log10}(S)$ and $\theta_0$ slightly decreases as the assumed threshold for $\theta_0$
-increases.
+unable to maintain coral cover above $\theta_0$ as it is increased, with the distribution of
+years above threshold becoming increasingly right-skewed
+[@fig-access-esm1-5-depth-carbonate; @fig-access-esm1-5-conn-carbonate]. In contrast,
+log10-transformed total connectivity strength ($\text{log10}(S)$) was found to have no
+correlation with the number of years a reef maintains cover above the required thresholds
+[@fig-access-esm1-5-conn-carbonate]. The correlation between $\text{log10}(S)$ and
+$\theta_0$ slightly decreases as the assumed threshold for $\theta_0$ increases.
 
@@
 number of years cover exceeds the carbonate budget threshold. Point colour represents the
-median reef depth level in metres. Displays results from median time series using
+median reef depth level in metres. Red points represent the mean number of years above a
+carbonate threshold across reefs. Displays results from median time series using
 ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
 fig-align="center" width="14.82cm"}
+
+![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
+2075. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
+total connectivity strength and the number of years cover exceeds the carbonate budget
+threshold. The colour of each point represents the base-10 log of scaled reef total
+connectivity strength. Red points represent the mean number of years above a carbonate
+threshold across reefs. Displays results from median time series using
+ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#fig-access-esm1-5-conn-carbonate
+fig-align="center" width="14.82cm"}
+
+**\[BG: I could combine these two plots into a single larger figure maybe, since it's quite
+easy to see the contrasting depth vs connectivity patterns with colours even when zoomed
+out.\]**
 
@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2075. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
-total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. The colour of each point represents the base-10 log of scaled reef total
-connectivity strength. Displays results from median time series using
-ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
-fig-align="center" width="14.82cm"}
-
 ### Bioregion scale clustering

### 2025-08-16 src/plotting_functions.jl

@@ -905,7 +905,7 @@ function carbonate_budget_variable_scatter(
     color_label::String="",
     fig_sizes::Dict=fig_sizes,
     fontsize::Float64=fontsize,
-    alpha::Union{Float64,Int64}=0.5
+    alpha_c::Union{Float64,Int64}=0.5
 )
     x_fig_size = fig_sizes["carb_width"]
     y_fig_size = fig_sizes["carb_height"]
@@ -916,10 +916,16 @@ function carbonate_budget_variable_scatter(
     # Get the default colormap (as a gradient with 256 colors)
     base_cmap = cgrad(:viridis, 256; rev=true)
     # Convert all colors to RGBA with alpha = 0.4 (adjust as needed)
-    transparent_colors = [RGBA(c.r, c.g, c.b, alpha) for c in base_cmap.colors]
+    transparent_colors = [RGBA(c.r, c.g, c.b, alpha_c) for c in base_cmap.colors]
     # Wrap into a ColorScheme object
     transparent_cmap = ColorScheme(transparent_colors)
 
+    theta_means = combine(groupby(long_df, carbonate_budget_col)) do sdf
+        (; 
+            x = first(sdf[:, carbonate_budget_col]),
+            y = mean(sdf[:, year_col])
+        )
+    end
 
     fig = Figure(size=(x_fig_size, y_fig_size), fontsize=fontsize)
     ax = Axis(
@@ -939,13 +945,17 @@ function carbonate_budget_variable_scatter(
         jitter_width=1
     )
     rain.plots[1].colormap = transparent_cmap
+    rainclouds!(
+        ax,
+        theta_means.x,
+        theta_means.y;
+        color = (:red, 0.8),
+        markersize=8,
+        show_median=false,
+        clouds=nothing,
+        plot_boxplots=false
+    )
 
-    # scat = scatter!(
-    #     ACCESS_ESM1_5_long.variable,
-    #     ACCESS_ESM1_5_long.value,
-    #     color=ACCESS_ESM1_5_long.depth_med,
-    #     alpha = 0.5
-    # )
     Colorbar(fig[1, 2], rain, label=color_label)
 
     return fig

### 2025-08-16 paper/paper_draft.qmd
Address minor comment

@@
 bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
-whole-of-GBR scale but were found to lead to identical results **\[TI: Ben, compared to
-what, the bioregion or the Management area results?\]** and so are not shown here. To
+whole-of-GBR scale but were found to lead to identical conclusions about characteristics influencing cluster cover compared to management area and bioregion scale analyses, and so are not shown here.
+To
 compare time series clustering results across GCMs, Management area scale clustering results

### 2025-08-16 paper/paper_draft.qmd
Address bioregion scale comments. Changes were suitable

@@
 bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
-whole-of-GBR scale but were found to lead to identical conclusions about characteristics influencing cluster cover compared to management area and bioregion scale analyses, and so are not shown here.
-To
-compare time series clustering results across GCMs, Management area scale clustering results
-are used to preserve coarse scale latitudinal differences between regions, while maintaining
-ease of comparison and visualisation. These comparisons include quantification of
-differences between low and high cover clusters across management regions under each GCM
-using the CID between cluster median time series. To assess how different reef
-characteristics influence time series clustering at a finer spatial scale, bioregion results
-are used to capture patterns occurring within individual clusters of reefs. Results of all
-analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for those
-interested.
+whole-of-GBR scale but were found to lead to identical conclusions about characteristics
+influencing cluster cover compared to management area and bioregion scale analyses, and so
+are not shown here. To compare time series clustering results across GCMs, Management area
+scale clustering results are used to preserve coarse scale latitudinal differences between
+regions, while maintaining ease of comparison and visualisation. These comparisons include
+quantification of differences between low and high cover clusters across management regions
+under each GCM using the CID between cluster median time series. To assess how different
+reef characteristics influence time series clustering at a finer spatial scale, bioregion
+results are used to capture patterns occurring within individual clusters of reefs. Results
+of all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for
+those interested.
 
@@
 In contrast to the broad temporal behaviour at the Management area scale, the relationship
-between reef characteristics **\[TI: Ben, I think this is what you meant by "contextual
-analysis factors"? depth, connectivity, dhw, carrying capacity etc?\]** and reefs' assigned
-categories were found to be similar at the bioregion scale **\[TI: Ben, please confirm my
-changes/edits are correct\]**. Results are therefore only shown and discussed for
-ACCESS-ESM1-5, an intermediate Equilibrium Climate Sensitivity scenario [@sfig-ecs]. Those
-interested in results for the other assessed GCMs are referred to Grier and Iwanaga
-[-@grier2025]. Across bioregions, reefs in the High category not only had greater levels of
-coral recovery but displayed persistence to 2050 [@sfig-access-esm1-5-bioregion-timeseries].
-Reefs in the High category were consistently found to have the greatest median reef depths
-across bioregions [@fig-access-esm1-5-bioregion-depth].
+between reef characteristics and reefs' assigned categories were found to be similar at the
+bioregion scale across GCMs. Results are only shown and discussed for ACCESS-ESM1-5, an
+intermediate Equilibrium Climate Sensitivity scenario [@sfig-ecs]. Those interested in
+results for the other assessed GCMs are referred to Grier and Iwanaga [-@grier2025]. Across
+bioregions, reefs in the High category not only had greater levels of coral recovery but
+displayed persistence to 2050 [@sfig-access-esm1-5-bioregion-timeseries]. Reefs in the High
+category were consistently found to have the greatest median reef depths across bioregions
+[@fig-access-esm1-5-bioregion-depth].
 
@@
 (@sfig-access-esm1-5-bioregion-dhwcor). Conversely, there are no consistent patterns across
-bioregions when comparing their temporal behaviour with respect to their reef area, relative
-cover, and mean of DHWs (@sfig-access-esm1-5-bioregion-dhwmean). There were no consistent
-differences across bioregions and GCMs between clusters in their reefs' initial proportion
-of habitable area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion).
-Across most bioregions there were not consistent differences between clusters in
-connectivity metrics such as source-to-sink connectivity ratio
-(@sfig-access-esm1-5-bioregion-logsosi) and total connectivity strength
-(@sfig-access-esm1-5-bioregion-totalconnectivity).
+bioregions when comparing their temporal behaviour with respect to their reef area and mean
+of DHWs (@sfig-access-esm1-5-bioregion-dhwmean). There were no consistent differences across
+bioregions and GCMs between clusters in their reefs' initial proportion of habitable area
+occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion). Across most bioregions
+there were not consistent differences between clusters in connectivity metrics such as
+source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and total
+connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
 

### 2025-08-17 paper/paper_draft.qmd
auto-format
Plus minor tweak to figure caption

@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef depth and the
-number of years cover exceeds the carbonate budget threshold. Point colour represents the
-median reef depth level in metres. Red points represent the mean number of years above a
-carbonate threshold across reefs. Displays results from median time series using
+![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075.
+The assessed carbonate budget thresholds range from 10 to 20% of total reef area. Bracketed
+x-axis values represent the Spearman's correlation between reef depth and the number of
+years cover exceeds the carbonate budget threshold. Point colour represents the median reef
+depth in metres. Red points represent the mean number of years above an assumed carbonate
+budget threshold across reefs. Note that deeper reefs are better able to maintain cover
+above the indicative carbonate budget threshold. Displays results from median time series
+using
 ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate

### 2025-08-17 src/ADRIA/HighResCoralStress/2_timeseries_clustering_absolute.jl

@@ -29,7 +29,7 @@ context_layers = context_layers[context_layers.inclusion_flag, :]
 
 n_clusters = 3
 bioregion_numbers = combine(groupby(context_layers, :bioregion), nrow => :nrow)
-removed_bioregions = bioregion_numbers[bioregion_numbers.nrow .< n_clusters, :bioregion]
+removed_bioregions = bioregion_numbers[bioregion_numbers.nrow.<n_clusters, :bioregion]
 context_layers.inclusion_flag = (context_layers.inclusion_flag) .& (context_layers.bioregion .∉ [removed_bioregions])
 context_layers = context_layers[context_layers.inclusion_flag, :]
 

### 2025-08-17 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -8,8 +8,10 @@ using ArchGDAL
 
 include("../../common.jl")
 
-change_ADRIA_debug(true) # Change ADRIA debug mode to true to extract DHW tolerance data from runs 
+# Change ADRIA debug mode to true to extract DHW tolerance data from runs
 # (removes parallel processing)
+change_ADRIA_debug(true)
+
 
 using ADRIA
 
@@ -21,7 +23,7 @@ gbr_dom = ADRIA.load_domain(gbr_domain_path, "45")
 dhw_scenarios = open_dataset(joinpath(gbr_domain_path, "DHWs/dhwRCP45.nc"))
 GCMs = dhw_scenarios.dhw.properties["members"]
 gbr_dom.loc_data.geometry = Vector{ArchGDAL.IGeometry}(gbr_dom.loc_data.geometry) # Need to recast gbr_dom geometry col for ADRIA.run_scenarios(). Possibly issue with GeoDataFrames version.
-gbr_dom_filtered = gbr_dom.loc_data[gbr_dom.loc_data.UNIQUE_ID .∈ [context_layers.UNIQUE_ID], :]
+gbr_dom_filtered = gbr_dom.loc_data[gbr_dom.loc_data.UNIQUE_ID.∈[context_layers.UNIQUE_ID], :]
 filtered_indices = indexin(gbr_dom_filtered.UNIQUE_ID, gbr_dom.loc_data.UNIQUE_ID)
 
 # 1. Attach connectivity data to context_layers
@@ -159,11 +161,11 @@ for (i_gcm, GCM) in enumerate(GCMs)
     scens = CSV.read(joinpath(output_path, "HighResCoralStress_ADRIA_scens_$(GCM).csv"), DataFrame)
     scens = scens[1:4, :]
     scens.wave_scenario .= 1.0
-    
-    rs_dhw = ADRIA.run_scenarios(gbr_dom, scens, "45")
-    dhw_tol_log = Float64.(mapslices(median, rs_dhw.coral_dhw_tol_log, dims = [:scenarios, :species]))
 
-    dhw_tol_mean = dropdims(mean(dhw_tol_log[10:end, :], dims = 1), dims = 1).data
+    rs_dhw = ADRIA.run_scenarios(gbr_dom, scens, "45")
+    dhw_tol_log = Float64.(mapslices(median, rs_dhw.coral_dhw_tol_log, dims=[:scenarios, :species]))
+
[…]

### 2025-08-17 src/ADRIA/HighResCoralStress/5_publication_plots.jl

@@ -10,11 +10,11 @@ context_layers = GDF.read(joinpath(output_path, "analysis_context_layers_carbona
 
 # ECS plot - methods
 ecs_values = Dict(
-    "EC-Earth3-Veg" => 4.30, # Wyser et al. (2020). On the increased climate sensitivity in the EC-Earth model from CMIP5 to CMIP6
-    "ACCESS-ESM1-5" => 3.87, # Ziehn et al. (2020). The Australian Earth System Model: ACCESS-ESM1.5
-    "ACCESS-CM2" => 4.66, # Grose et al. (2020). A CMIP6-based multi-model downscaling ensemble to underpin climate change services in Australia
-    "GFDL-CM4" => 4.1, # Sentman et al. (2025). Quantifying Equilibrium Climate Sensitivity to Atmospheric Chemistry and Composition Representations in GFDL-CM4.0 and GFDL-ESM4.1 
-    "NorESM2-MM" => 2.5 # Seland et al. (2020). Overview of the Norwegian Earth System Model (NorESM2) and key climate response of CMIP6 DECK, historical, and scenario simulations
+    "EC-Earth3-Veg" => 4.30,  # Wyser et al. (2020). On the increased climate sensitivity in the EC-Earth model from CMIP5 to CMIP6
+    "ACCESS-ESM1-5" => 3.87,  # Ziehn et al. (2020). The Australian Earth System Model: ACCESS-ESM1.5
+    "ACCESS-CM2" => 4.66,  # Grose et al. (2020). A CMIP6-based multi-model downscaling ensemble to underpin climate change services in Australia
+    "GFDL-CM4" => 4.1,  # Sentman et al. (2025). Quantifying Equilibrium Climate Sensitivity to Atmospheric Chemistry and Composition Representations in GFDL-CM4.0 and GFDL-ESM4.1
+    "NorESM2-MM" => 2.5  # Seland et al. (2020). Overview of the Norwegian Earth System Model (NorESM2) and key climate response of CMIP6 DECK, historical, and scenario simulations
 )
 ecs = ecs_plot(collect(values(ecs_values)), [2.5, 5.1], [2.1, 7.7], collect(keys(ecs_values)))
 save(joinpath(figs_path, "ecs_plot.png"), ecs, px_per_unit=dpi)
[…]

### 2025-08-17 src/ADRIA/HighResCoralStress/5_publication_plots.jl
Adjust height of figure to avoid squashing subplots

@@ -47,7 +47,7 @@ context_layers = sort(context_layers, :management_area)
 dhw_arrays = dhw_arrays[sites=At(context_layers.UNIQUE_ID)]
 
 fig = Figure(
-    size=(fig_sizes["gcm_timeseries_width"], fig_sizes["gcm_timeseries_height"]),
+    size=(fig_sizes["gcm_timeseries_width"], fig_sizes["gcm_timeseries_height"] * 1.3),
     fontsize=fontsize
 )
 plot_layout = [(x, 1) for x in eachindex(GCMs)]

### 2025-08-17 paper/paper_draft.qmd
Further tweak to avoid ambiguous description
I avoid "this" because sometimes it becomes unclear what "this" refers to.

@@
 
-Carrying capacity, source-to-sink ratio and total connectivity strength and indicate that
-their influence on cluster assignments is concentrated at the low range of predictor values
-[@fig-ts-cluster-pdp]. This aligns with the right-skewed distributions of values across
-reefs for these three predictor variables. Beyond this lower range, the partial dependence
-for these reef characteristics becomes near constant, indicating that interactions with
-other reef characteristics are occurring at these values which is also evidenced by their
-intermediate feature importance scores.
+Analyses for carrying capacity, source-to-sink ratio and total connectivity strength
+indicate that their influence on its categorical assignment is concentrated at the low range
+of predictor values [@fig-ts-cluster-pdp]. This aligns with the right-skewed distributions
+of values across reefs for these three predictor variables. Beyond this lower range, the
+partial dependence for these reef characteristics becomes near constant, contrary to their
+feature importance scores which suggest these characteristics do contribute important
+information to predictions. The contrasting outcomes indicate that interactions between
+other reef characteristics are driving behaviour rather than a strong influence from a
+single individual characteristic.
 

### 2025-08-17 src/ADRIA/HighResCoralStress/7_rf_analysis.jl
Update RF figure code to produce 2-layout figure
Update to produce figure with combined layout. To ensure consistent fontsize/figure width sizing when rendering in word

@@ -266,7 +266,7 @@ function partial_dependence_multiclass(machine, data, feature_col; n_grid=50)
     return (grid=collect(grid), class_values=results)
 end
 
-function plot_multiclass_pd(pdp_results::OrderedDict, matching_reef_df::DataFrame)
+function plot_multiclass_pd(pdp_results::OrderedDict, matching_reef_df::DataFrame; fig=Figure(size=(800,500)))
     feature_names = keys(pdp_results)
     readable_names = Dict(
         "mean_dhw" => "Mean DHW",
@@ -283,7 +283,6 @@ function plot_multiclass_pd(pdp_results::OrderedDict, matching_reef_df::DataFram
     # Color palette for classes (low, med, high)
     colors = [(:green, 0.4), (:orange, 0.4), (:blue, 0.4)]
 
-    fig = Figure(size=(800, 500))
     r = 1
     c = 1
     for fn in feature_names
@@ -353,12 +352,23 @@ function plot_multiclass_pd(pdp_results::OrderedDict, matching_reef_df::DataFram
         fig[n_rows+1, :],
         [PolyElement(color=col, alpha=0.8) for col in colors],
         ["Low", "Medium", "High"],
-        nbanks=3,
+        orientation=:horizontal
     )
 
-    rowsize!(fig.layout, n_rows + 1, Auto(0.25))
+    # if isa(fig, GridLayout)
+    #     rowsize!(fig, n_rows+1, Relative(0.15))
+    #     for j in 1:3
+    #         colsize!(fig, j, Relative(1/3))
+    #     end
+    # else
+    #     rowsize!(fig.layout, n_rows+1, Relative(0.15))
+    #     for j in 1:3
+    #         colsize!(fig.layout, j, Relative(1/3))
+    #     end
+    # end
 
-    Label(fig[1:2, 0], "Probability", rotation=π / 2)
+    # Label(fig[1:2, -1], "Probability", rotation=π / 2)
+    Label(fig[0, 1:3], "Partial Dependence", font=:bold)
 
     return fig
 end
@@ -369,30 +379,42 @@ for n in names(X2)
 end
 
 # Plot feature importances
-f1, ax, sp = barplot(
+figure = Figure(
+    size = (fig_sizes["cluster_hm_width"], fig_sizes["cluster_hm_height"] - 3centimetre), 
+    fontsize=fontsize
+)
+gr1 = GridLayout(figure[1,1])
+ax = Axis(
+    gr1[1,1], 
[…]

### 2025-08-17 paper/paper_draft.qmd
Expand on PDP figure caption

@@
 sharp delineation can be seen \> 6 DHW when comparing High with other categories, with lower
-assignment probability (\~25%) compared to Medium and Low (\~40%).
+assignment probability (\~25%) compared to Medium and Low (\~40%) [@fig-ts-cluster-pdp,
+Panel B].
 
@@
 
-**\[BG: Will add either predictor distributions to these sub plots, or just in a general
-variable distribution plot in the supplementary material.\]**
-
 ![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
-Dependence Plots for reef characteristics of interest indicating the probability of a reef
-being classified to one of the three categories (Panel B). Partial Dependence Plots for
-bioregions were excluded as they were found to be
-uninformative.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp
-fig-align="center" width="9.2cm"}
+Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a
+reef being classified to one of the three categories (Panel B). Partial Dependence Plots for
+bioregions were excluded as they were found to be uninformative. PDPs indicate the
+probability of a reef from the test dataset being clustered into each cluster category
+depending on the predictor value on the x axis, when adjusted for values of other
+predictors. Green, orange and blue lines indicate cluster assignment probability for Low,
+Medium and High clusters respectively. Transparent grey points above probability lines
+represent the predictor values present in the test dataset, providing a rough indication of
+predcitor value distribution across
+reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center"
+width="14.82cm"}
 

### 2025-08-17 paper/paper_draft.qmd
Update prediction performance plots and insert section into results

@@
 
-### Partial dependence
+#### Partial dependence
 
@@
 single individual characteristic.
+
+Assessing random forest prediction performance reveals increasing performance as bioregion
+mean reef depth and carrying capacity increase [@sfig-rf-predictor-perf]. This highlights
+where there is unexplained variation between reefs that contributes to cluster assignment
+and reef cover outcomes but is not captured by our included predictor variables.
 
@@
 
+![Scatter plots indicating the bioregion test-prediction accuracy (proportion of reefs in
+each bioregion assigned correct clusters) from the Random Forest model. Plot panels
+represent the bioregion accuracy across various predictor ranges and bioregion attributes,
+such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength,
+Source-to-sink ratio and the number of reefs in each
+bioregion.](../figs/rf_performance_across_predictors.png){#sfig-rf-predictor-perf
+fig-align="center" width="14.82cm"}
+
 ![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef

### 2025-08-17 src/ADRIA/HighResCoralStress/7_rf_analysis.jl

@@ -445,42 +445,42 @@ fig = Figure(
 ax = Axis(
     fig[1,1],
     ylabel = "Mean bioregion accuracy",
-    xlabel = "Mean bioregion depth",
+    xlabel = "Mean reef depth [m]",
     backgroundcolor=bgcol
 )
 Makie.scatter!(ax, perf_by_bio.depth, perf_by_bio.acc, color=bioregion_colors)
 ax = Axis(
     fig[1,2],
     ylabel = "Mean bioregion accuracy",
-    xlabel = "Mean bioregion carrying capacity",
+    xlabel = "Mean carrying capacity [km²]",
     backgroundcolor=bgcol
 )
 Makie.scatter!(ax, perf_by_bio.size, perf_by_bio.acc, color=bioregion_colors)
 ax = Axis(
     fig[2,1],
-    ylabel = "Mean bioregion accuracy",
-    xlabel = "Mean bioregion DHW",
+    ylabel = "Bioregion accuracy",
+    xlabel = "Mean DHW [\u00B0C - Weeks]",
     backgroundcolor=bgcol
 )
 Makie.scatter!(ax, perf_by_bio.dhw, perf_by_bio.acc, color=bioregion_colors)
 ax = Axis(
     fig[2,2],
-    ylabel = "Mean bioregion accuracy",
-    xlabel = "Mean bioregion connectivity strength",
+    ylabel = "Bioregion accuracy",
+    xlabel = "Mean total connectivity strength",
     backgroundcolor=bgcol
 )
 Makie.scatter!(ax, perf_by_bio.n, perf_by_bio.acc, color=bioregion_colors)
 ax = Axis(
     fig[3,1],
-    ylabel = "Mean bioregion accuracy",
-    xlabel = "Mean bioregion source to sink ratio",
+    ylabel = "Bioregion accuracy",
+    xlabel = "Mean source-to-sink ratio",
     backgroundcolor=bgcol
 )
 Makie.scatter!(ax, perf_by_bio.so_to_si, perf_by_bio.acc, color=bioregion_colors)
 ax = Axis(
     fig[3,2],
-    ylabel = "Mean bioregion accuracy",
-    xlabel = "Bioregion number of reefs",
+    ylabel = "Bioregion accuracy",
+    xlabel = "Number of reefs per bioregion",
     backgroundcolor=bgcol
 )
 Makie.scatter!(ax, perf_by_bio.n, perf_by_bio.acc, color=bioregion_colors)

### 2025-08-17 paper/paper_draft.qmd
Reshuffle methods section
@ConnectedSystems I have reshuffled methods paper section to have connectivity methods after introducing the model because we mention ADRIA-CoralBlox implementation of conn in that section before we have introduced the modelling platform.

Also removed results/discussion for DHW-tolerance. DHW-tolerance is now only mentioned in intro and supplementary methods

@@
 available in GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched
-with the 3806 reef outlines through geometric intersection analysis. Depth values within
-each reef polygon were summarized using zonal statistics. All depth values were converted to
-positive values (depths below sea level). The median depth was used to provide an indicative
-depth value for each reef. Code, and the resulting depth estimates, are available at
-**\[cite Canonical Reefs repo\]**.
+with the 3806 reef outlines through geometric intersections. All depth values were converted
+to positive values (depths below sea level). The median depth was used to provide an
+indicative depth value for each reef. Code, and the resulting depth estimates, are available
+at **\[cite Canonical Reefs repo\]**.
 
@@
 bioregions [@GBRMPA2024] were also removed from the investigation. Bioregions which
-contained fewer than three reefs were also excluded. As a result, 1377 reefs were excluded
-(36%), leaving a total of 2429 remaining for the purpose of this investigation.
+contained fewer than three reefs after these processes were also excluded. As a result, 1377
+reefs were excluded (36%), leaving a total of 2429 remaining for the purpose of this
+investigation.
 
@@
 
-These GCMs were selected based on based on evaluation conducted by Grose et al.,
-[-@grose2023], indicating their ability to recreate historical atmospheric temperature and
-precipitation conditions in the Australasian region. They span a range of Equilibrium
-Climate Sensitivity (ECS) values within the Intergovernmental Panel on Climate Change (IPCC)
-assessed likely range. The IPCC defines ECS as the long term warming caused by a doubling of
-carbon dioxide above its pre-industrial concentration [@forster2021]. While this assessment
-does not consider oceanic data, Grose et al. [-@grose2023] provide a region-specific
-selection mechanism which we use as an indicator of general performance of GCMs for the
-region. An overview of the selected GCMs are provided in @tbl-gcms. Note here that Grose et
-al., [-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023]
-provides data based on GFDL-CM4. Similarly, data for ACCESS-CM2 was used as a stand-in for
-ACCESS-ESM1-5. These substitutions are assumed appropriate given they share the same
+These GCMs were selected based on evaluation conducted by Grose et al., [-@grose2023],
+indicating their ability to recreate historical atmospheric temperature and precipitation
+conditions in the Australasian region. They span a range of Equilibrium Climate Sensitivity
+(ECS) values within the Intergovernmental Panel on Climate Change (IPCC) assessed likely
+range. The IPCC defines ECS as the long term warming caused by a doubling of carbon dioxide
+above its pre-industrial concentration [@forster2021]. While this assessment does not
+consider oceanic data, Grose et al. [-@grose2023] provide a region-specific selection
+mechanism which we use as an indicator of general performance of GCMs for the region. An
+overview of the selected GCMs are provided in @tbl-gcms. Note here that Grose et al.,
+[-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides
+data based on GFDL-CM4. This substitution is assumed appropriate given they share the same
 fundamental representation of the physical climate system.
@@
 emissions comparable to present day until 2050, after which emissions gradually decline
-[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global
-atmospheric warming in the 2081-2100 period relative to 1850-1900. The use of this range of
-GCMs therefore allow for a range of possible climate futures to be explored, capturing the
+[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.66°C of global
+atmospheric warming in the 2081-2100 period relative to 1850-1900. The use of these GCMs
+therefore allow for a range of possible climate futures to be explored, capturing the
 uncertainty in future responses to CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023;
@@
 
-Degree Heating Weeks (DHWs) were then derived using the "HotSpot SST Anomaly" approach
-[@skirving2020]. The "HotSpot SST Anomaly" represents the thermal stress experienced by
-coral reefs and is calculated as the difference between daily SST values and the maximum of
-a pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean
+Degree Heating Weeks (DHWs) were derived using the "HotSpot SST Anomaly" approach
+[@skirving2020]. The "HotSpot SST Anomaly" represents thermal stress experienced by coral
+reefs and is calculated as the difference between daily SST values and the maximum of a
+pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean
 SST). This approach uses the annual maximum temperature as the baseline because corals are
@@
 DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week
-rolling sum of positive HotSpot SST Anomaly values that are greater than 1°C, expressed in
-units of °C-weeks. The 12-week accumulation period reflects the cumulative nature of coral
-thermal stress. Brief temperature spikes may be tolerable, but sustained or repeated
-exposure to elevated temperatures causes progressively greater physiological stress and
-bleaching severity. DHW values integrate both the magnitude and duration of thermal stress:
-a moderate anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a
-severe anomaly (e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW
-estimates for each indicative reef (see @GBRMPA2022) were then determined by taking the mean
-DHW value for all pixels touching each reef outline. The process described here was
-conducted for all 2429 reefs to create DHW projections spanning from 2025 to 2075. Code used
-to calculate DHW data and perform analyses involved in this investigation can be found at
-Grier and Iwanaga [-@grier2025].
+rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in units of
+°C-weeks. The 12-week accumulation period reflects the cumulative nature of coral thermal
+stress. Brief temperature spikes may be tolerable, but sustained or repeated exposure to
+elevated temperatures causes progressively greater physiological stress and bleaching
+severity. DHW values integrate both the magnitude and duration of thermal stress: a moderate
+anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly
+(e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for
+each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for
+all pixels touching each reef outline. The process described here was conducted for all 2429
+reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
+and perform analyses involved in this investigation can be found at Grier and Iwanaga
+[-@grier2025].
 
@@
 width="14.82cm"}
-
-### Connectivity modelling
-
-\*\* need information on GBR1 connectivity used \*\*
-
-Connectivity data from 24 days in total were used in this investigation. These data span six
-years from 2015 to 2020. The years 2015, 2016, 2018 and 2019 are each represented by
-connectivity matrices covering spawning periods over three days in each year (12 days in
-total), while 2017 and 2020 are each represented by six spawning days each, coming to a
-total of 24 days of connectivity matrices. Indicative connectivity strengths are implemented
-in ADRIA-CoralBlox as the mean of all available data for each location (i.e., mean of all 24
-spawning days). While the connectivity strengths do not vary from year to year within each
-simulation, they do vary between reefs which are of varying sizes, providing sufficient
-heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. The
-spatial variability also enables investigations into the influence of connectivity strength
-and its role in driving recovery processes.
-
-The ratio of source-to-sink connectivity ($O:I$) for a target reef represents the strength
-of the reef's outgoing larval flow relative to it's incoming larval flow (@eq-so-to-si). If
-a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value. Incoming
-connections in this calculation, do not directly represent the larval supply gained as the
-population from which connections are coming from is not represented. A source-to-sink ratio
-greater than 1 (a value greater than 0 on a log scale) indicates a reef has greater outgoing
-than incoming larval flow.
-
-$$
-O:I = \frac{S_O/N_O}{S_I/N_I}
-$$ {#eq-so-to-si}
-
-Where:
-
--   $S$ is the sum of outgoing and incoming connections, indicating the total connectivity
-    strength.
-
--   $N$ denotes the number of connections.
-
--   $O$ denotes outgoing (source) connections from a reef.
-
--   $I$ denotes incoming (sink) connections to a reef.
 
@@
 
-ADRIA-CoralBlox was run for 4096 scenarios for each of the five GCMs (20,480 total model
-runs). Here, a scenario represents a unique combination of assumed environmental (namely one
-of the five DHW trajectories) and ecological factors including coral growth and mortality
-rates, coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol'
-sampling method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi
-Monte Carlo approach which balances scenario exploration with improved convergence
-properties compared to pseudo-random sampling. A detailed comparative analysis of the
-sampling methods can be found in [@kucherenko2015]. For the purpose of scenario assessment,
-the resulting time series for each model run were scaled by the total area of the reef to
-represent cover as a percentage of the total estimated reef area. These time series of coral
-cover were then clustered based on their temporal behaviour.
+ADRIA-CoralBlox was run for 4096 scenarios for each GCM (20,480 total model runs). Here, a
+scenario represents a unique combination of assumed environmental (namely one of the five
+DHW trajectories) and ecological factors including coral growth and mortality rates, and
+coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol' sampling
+method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi Monte Carlo
+approach which balances scenario exploration with improved convergence properties compared
+to pseudo-random sampling. A detailed comparative analysis of the sampling methods can be
+found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
+cover time series for each model run were scaled by the total area of each reef to represent
+cover as a percentage of the total estimated reef area. The scenario-median timeseries for
+each reef was used for further analyses. These time series of coral cover were then
+clustered based on their temporal behaviour.
+
+### Connectivity modelling
+
+\*\* need information on GBR1 connectivity used \*\*
+
+Connectivity data from 24 days in total were used in this investigation to estimate coral
+larval flows. These data span six years from 2015 to 2020. The years 2015, 2016, 2018 and
+2019 are each represented by connectivity matrices covering spawning periods over three days
+in each year (12 days in total), while 2017 and 2020 are each represented by six spawning
+days each, coming to a total of 24 days of connectivity matrices. Indicative connectivity
+strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
+location (i.e., mean of all 24 spawning days). While the connectivity strengths do not vary
+from year to year within each simulation, they do vary between reefs which are of varying
+sizes, providing sufficient heterogeneity to capture spatial patterns in larval dispersal
+and settlement dynamics. The spatial variability also enables investigations into the
+influence of connectivity strength and its role in driving recovery processes.
+
+To assess the impact of reef connectivity on modelled outcomes we summarise inter-reef
+connections using the total strength of connections and the ratio of source-to-sink
+connectivity for each reef. The ratio of source-to-sink connectivity ($O:I$) for a target
+reef represents the strength of the reef's outgoing larval flow relative to it's incoming
+larval flow (@eq-so-to-si). If a reef has no incoming connections, the $O:I$ equals the
+$S_O/N_O$ value. Incoming connections in this calculation, do not directly represent the
+larval supply gained as the population from which connections are coming from is not
+represented. A source-to-sink ratio greater than 1 (a value greater than 0 on a log scale)
+indicates a reef has greater outgoing than incoming larval flow.
+
+$$
+O:I = \frac{S_O/N_O}{S_I/N_I}
+$$ {#eq-so-to-si}
+
+Where:
+
+-   $S$ is the sum of outgoing and incoming connections, indicating the total connectivity
+    strength.
+
+-   $N$ denotes the number of connections.
+
+-   $O$ denotes outgoing (source) connections from a reef.
+
+-   $I$ denotes incoming (sink) connections to a reef.
 
@@
 The time series clustering was applied over the time frame between 2025 and 2075. Spatially,
-the analyses were conducted for each GBR management area and at the scale of each reefal
-bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
+the clustering analyses were conducted for each GBR management area and at the scale of each
+reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
 whole-of-GBR scale but were found to lead to identical conclusions about characteristics
 influencing cluster cover compared to management area and bioregion scale analyses, and so
-are not shown here. To compare time series clustering results across GCMs, Management area
+are not shown here. To compare time series clustering results across GCMs, management area
 scale clustering results are used to preserve coarse scale latitudinal differences between
@@
 reef characteristics influence time series clustering at a finer spatial scale, bioregion
-results are used to capture patterns occurring within individual clusters of reefs. Results
-of all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for
+results are used to capture patterns occurring within individual groups of reefs. Results of
+all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for
 those interested.
@@
 between Low, Medium and High categories. These characteristics include reef median depth,
-mean time series DHW, mean time series DHW tolerance level **\[TI: Ben, still correct? Still
-included somewhere?\]**, Pearson’s correlation between total coral cover and inverse DHW
-time series, proportion of coral habitable area occupied by corals in the first timestep,
-ratio of source-to-sink larval connectivity and total strength of all larval connections
-between reefs.
+mean time series DHW, Pearson’s correlation between total coral cover and inverse DHW time
+series, proportion of coral habitable area occupied by corals in the first timestep, ratio
+of source-to-sink larval connectivity and total strength of all larval connections between
+reefs.
 
@@
 
-Using median coral cover time series for each reef we calculated the number of years each
-reef maintains coral cover above a given percent threshold. The threshold represents the
-level of live coral cover necessary to maintain a positive carbonate budget (denoted here as
+Using coral cover time series for each reef we calculated the number of years each reef
+maintains coral cover above a given percent threshold. The threshold represents the level of
+live coral cover necessary to maintain a positive carbonate budget (denoted here as
 $\theta_{0}$ to indicate the budget equilibrium). Greater number of years above $\theta_{0}$
@@
 
-Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
-[@desbiens2021]. Given in situ carbonate budgets are influenced by (1) a range of processes;
-(2) the variety of approaches that could be used to measure those processes; and (3) the
-uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
-single precise $\theta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
-$\theta_{0}$ value for each individual reef.
+Recent analyses suggest a general threshold of \~17% live coral cover in the case of the
+mid-shelf and offshore GBR reefs [@desbiens2021]. Given in situ carbonate budgets are
+influenced by (1) a range of processes; (2) the variety of approaches that could be used to
+measure those processes; and (3) the uncertainty surrounding these, it would be unreasonable
+to assume all reefs adhere to a single precise $\theta_{0}$ value. Concurrently, it is
+difficult to ascertain a suitable $\theta_{0}$ value for each individual reef.
 
@@
 fig-align="center" width="14.82cm"}
-
-**\[BG: I could combine these two plots into a single larger figure maybe, since it's quite
-easy to see the contrasting depth vs connectivity patterns with colours even when zoomed
-out.\]**
 
@@
 long-term resilience of deployment sites.
-
-Our findings suggest that reefs in ‘high’ cover clusters do not have greater thermal
-tolerance than reefs in lower coral cover clusters. This is in contrast with literature
-suggesting corals have the capacity to adapt to increasing climate change pressures
-[@humanes2022; @lachs2024; @lachs2023], including the investigation by Bairos-Novak et al.
-[-@bairos-novak2021] that revealed high heritability of bleaching and survival response
-traits, used to inform thermal tolerance trait distributions in this investigation. The low
-importance of thermal tolerance on cover outcomes may be due to reefs experiencing high
-levels of thermal stress early in projected time series. High - early time series thermal
-stress events may prevent the intergenerational adaptation of corals to thermal stress and
-prevent thermal tolerance from reaching levels greater than 9°C-weeks. **\[TI note: This
-paragraph needs to be revisited\]**
 
@@
 of reef depth at the GBR-scale. Data adopted for the given assessment are said to be
-accurate up to 15m from Mean Sea Level [@GBRMPA2020], however there are many sources of
-uncertainty in the depth estimates used for this study. Satellite-derived estimates are
-subject to different bottom types (rock, sand, seagrass, etc) and how these affect
-reflectance, the water penetration depth of satellite sensors, influence of local conditions
-(e.g., turbidity and wave activity), among many other factors. The median depths for each
-indicative reef area were extracted from bathymetry data using zonal statistics and depth
-values beyond the stated 15m accuracy threshold [@GBRMPA2020] were included. The resulting
-depth estimates are therefore highly uncertain and are only adopted as a useful indication
-for the purpose of the presented analysis. They are not intended to be an accurate and
-precise report of reef depths across the GBR.
+accurate up to 15m from Mean Sea Level [@GBRMPA2020; @li2021], however there are many
+sources of uncertainty in the depth estimates used for this study. Satellite-derived
+estimates are subject to different bottom types (rock, sand, seagrass, etc) and how these
+affect reflectance, the water penetration depth of satellite sensors, influence of local
+conditions (e.g., turbidity and wave activity), among many other factors. The median depths
+for each indicative reef area were extracted from bathymetry data using zonal statistics and
+depth values beyond the stated 15m accuracy threshold [@GBRMPA2020] were included. The
+resulting depth estimates are therefore highly uncertain and are only adopted as a useful
+indication for the purpose of the presented analysis. They are not intended to be an
+accurate and precise report of reef depths across the GBR.
 
@@
 
-CoralBlox model incorporates linear extension (growth) and background mortality rates that
-are dependent on the size and functional group of a coral colony. Environmental disturbances
-and reproduction are not directly considered within CoralBlox. Instead, these factors are
-considered by making changes to the distribution of colonies within CoralBlox timesteps
-using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
-Within ADRIA, we incorporate coral life history and environmental events in the following
-order: coral colony growth; coral reproduction; larval connectivity and settlement; and
-coral bleaching due to heat stress. As ADRIA and CoralBlox are coupled together to represent
-the system, we refer to both as ADRIA-CoralBlox.
+The CoralBlox model incorporates linear extension (growth) and background mortality rates
+that are dependent on the size and functional group of a coral colony. Environmental
+disturbances and reproduction are not directly considered within CoralBlox. Instead, these
+factors are considered by making changes to the distribution of colonies within CoralBlox
+timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform
+[@iwanaga2023]. Within ADRIA, we incorporate coral life history and environmental events in
+the following order: coral colony growth; coral reproduction; larval connectivity and
+settlement; and coral bleaching due to heat stress. As ADRIA and CoralBlox are coupled
+together to represent the system, we refer to both as ADRIA-CoralBlox.
 
@@
 
-**Bleaching mortality** **\[BG: Has this section been completed?\]** In ADRIA we track the
-thermal tolerance of each functional group and size class as a truncated normal distribution
-that is updated in each timestep following growth and recruitment. This distribution
-determines the proportion of the population on a reef that is susceptible to bleaching (i.e.
-has a thermal threshold below the experienced DHW value). Starting distributions for thermal
-tolerance levels are informed by Bairos-Novak et al. [-@bairos-novak2021].
+In ADRIA we track the thermal tolerance of each functional group and size class as a
+truncated normal distribution that is updated in each timestep following growth and
+recruitment. This distribution determines the proportion of the population on a reef that is
+susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
+Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
+[-@bairos-novak2021].
 
@@
 
-**\[TI: To be revisited\]**
-
-The CID corrects the Euclidean distance between pairs of time series (which accounts for
-magnitude differences) with the complexity of each time series (obtained through a measure
-of their variability) to ensure reefs are clustered based on their underlying temporal
-dynamics rather than simply their average coral cover.
-
-The process creates a distance matrix of n \* n dimensions (where n is the number of time
-series in the group) that is clustered using a k-medoids clustering algorithm [cf.
-@steinmann2020]. The three reef clusters are labelled with qualitative-ordered categories
-from Low, Medium and High based on their median cover relative to each other cluster over
-the 2030-2060 period.The selected time frame prevents the classification from being overly
-influenced by any steep declines in the initial years of simulations, and avoids the
-post-2060 time period where reefs are projected to be under severe stress and in a declined
-state [@bozec2025].
+The CID timeseries clustering metric corrects the Euclidean distance between pairs of time
+series (which accounts for magnitude differences) with the complexity of each time series
+(obtained through a measure of their variability) to ensure reefs are clustered based on
+their underlying temporal dynamics rather than simply their average coral cover. The process
+creates a distance matrix of n \* n dimensions (where n is the number of time series in the
+group) that is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The
+three reef clusters are labelled with qualitative-ordered categories from Low, Medium and
+High based on their median cover relative to each other cluster over the 2030-2060 period.
+The selected time frame prevents the classification from being overly influenced by any
+steep declines in the initial years of simulations, and avoids the post-2060 time period
+where reefs are projected to be under severe stress and in a declined state [@bozec2025].
 
@@
 GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-fig-align="center" width="14.82cm"}
-
-![Mean time series DHW tolerance value, from 2035 to 2075, for reefs within each bioregion,
-separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines represent the median DHW tolerance value for each cluster and bands represent the
-distribution of DHW-tolerance levels within each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
 fig-align="center" width="14.82cm"}

### 2025-08-17 paper/paper_draft.qmd
Mainly correctly explain depth ranges for current deployments
Emphasise the possibility of expanding deployments to the 10-15m depth range to enhance survival

@@
 assignment probability across depth ranges [@fig-ts-cluster-pdp, Panel B]. A large increase
-in the probability of a reef being categorised as High can be seen between 10 and 12 meters
-depth. This is at the edge of what is feasible with current technologies and restoration
-approaches **\[TI: Citation here\]**, but indicates a depth range that could be adopted to
-maximise longevity and benefits of, for example, coral seeding activities. With regard to
-DHWs, assignment probability is roughly equal across the three categories up to 6 DHW. A
-sharp delineation can be seen \> 6 DHW when comparing High with other categories, with lower
-assignment probability (\~25%) compared to Medium and Low (\~40%) [@fig-ts-cluster-pdp,
-Panel B].
+in the probability of a reef being categorised as High can be seen between 10 and 15 meters
+depth. This is at the edge of the depth range used in current deployment efforts
+[@howlett2021; @randall2021; @whitman2024], but indicates a depth range that could be
+adopted to maximise longevity and benefits of, for example, coral seeding activities. With
+regard to DHWs, assignment probability is roughly equal across the three categories up to 6
+DHW. A sharp delineation can be seen \> 6 DHW when comparing High with other categories,
+with lower assignment probability (\~25%) compared to Medium and Low (\~40%)
+[@fig-ts-cluster-pdp, Panel B].
 
@@
 DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress
-events depends on reef depth. Our results suggest that within shallow-water reef ecosystems
-(non-mesophotic, depth \< 30m), depth contributes greatly to reef resilience and the ability
-of the reef to maintain positive carbonate budgets under future conditions. While similar
-findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses
-have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia
-[@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al. [-@venegas2019]
-found no association between depth and the alleviation of heat stress across a range of
-shallow reefs in the Pacific. Reefs at shallow depths experience no, or few, years with
-coral cover exceeding levels likely required to maintain positive carbonate budgets.
-Movement of shallow reefs towards negative carbonate budgets in the future may contribute to
-phase shifts in reef dominant CaCO~3~ production. Shifting from coral driven to encrusting
-algae driven production, or to bioerosion dominated systems with rapid erosion of physical
-reef frameworks [@dudgeon2010; @perry2008]. While reefs at increased depths may be able to
-maintain coral driven CaCO~3~ production and accumulation into the future for longer.
+events depends on reef depth. Reefs at deeper depths are likely to be clustered into High
+cover clusters. Reefs at shallow depths experience no, or few, years with coral cover
+exceeding levels likely required to maintain positive carbonate budgets. Movement of shallow
+reefs towards negative carbonate budgets in the future may contribute to phase shifts in
+reef dominant CaCO~3~ production. Shifting from coral driven to encrusting algae driven
+production, or to bioerosion dominated systems with rapid erosion of physical reef
+frameworks [@dudgeon2010; @perry2008]. While reefs at increased depths may be able to
+maintain coral driven CaCO~3~ production and accumulation into the future for longer. Our
+results suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m),
+depth contributes greatly to reef resilience and the ability of the reef to maintain
+positive carbonate budgets under future conditions. While similar findings have been
+demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014] regions,
+depth refugia analyses have often focussed on the potential of mesophotic reefs (\> 30m
+deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas
+et al. [-@venegas2019] found no association between depth and the alleviation of heat stress
+across a range of shallow reefs in the Pacific.
 
@@
 deployment of coral seeding and fragment devices, target reefs with suitable restoration
-sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. One of the main
-constraints on deployment depth is visual identification of target sites from the surface
-for deployment and ongoing monitoring, in combination with factors such as deployment method
-and tourism return value. Our results suggest that of the assessed reefs ocurring within the
-1-10m depth range (1736 reefs), 62% (1082) of reefs fall into the low and medium clusters
-(across all GCMs at the GBRMPA management region scale), with many unable to maintain
-positive carbonate budgets under future conditions. Reef intervention planning is a complex
+sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
+no explicit justifications for this depth range, restoration depth is likely constrained by
+snorkeling and diving logistical accessibility, visual identification of sites from the
+surface, in combination with tourism return value. Our results suggest that of the assessed
+reefs ocurring within the 1-10m depth range (1736 reefs), 62% (1082) of reefs fall into the
+low and medium clusters (across all GCMs at the GBRMPA management region scale), with many
+unable to maintain positive carbonate budgets under future conditions. Partial dependence
+analysis revealed a range of depths from 10-15m where the probability of a reef being
+clustered into the High cover category increased substatially. Considering this 10-15m depth
+range when assessing possible restoration sites may enhance restoration success, while still
+maintaining effective logistical access to sites. Reef intervention planning is a complex
 and challenging decision making process [@anthony2020], and our results suggest that
@@
 long-term resilience of deployment sites.
-
-**\[TI note: Important to speak to interesting depth range at edge of where coral planting
-might feasibly/viably occur with current approaches\]**
 

### 2025-08-17 paper/paper_draft.qmd
Expand on role of 10-15m depth range

@@
 clustered into the High cover category increased substatially. Considering this 10-15m depth
-range when assessing possible restoration sites may enhance restoration success, while still
-maintaining effective logistical access to sites. Reef intervention planning is a complex
-and challenging decision making process [@anthony2020], and our results suggest that
-deployment site depth may be an important factor to additionally consider when assessing the
-long-term resilience of deployment sites.
+range when assessing possible restoration sites may reduce the exposure of planted and
+seeeded corals to high thermal stress, while still maintaining effective logistical access
+to sites. Reef intervention planning is a complex and challenging decision making process
+[@anthony2020], and our results suggest that deployment site depth may be an important
+factor to additionally consider when assessing the long-term resilience of deployment sites.
 

### 2025-08-17 paper/paper_draft.qmd
Update carbonate budget results to reflect joint figure

@@
 
-**\[TI: Ben, Just noticed - we need to make the rows (Management areas) go from North to
-South!\]**
-
 Comparing across GCMs, it is common for reefs to switch between categories, including from
@@
 years above threshold becoming increasingly right-skewed
-[@fig-access-esm1-5-depth-carbonate; @fig-access-esm1-5-conn-carbonate]. In contrast,
-log10-transformed total connectivity strength ($\text{log10}(S)$) was found to have no
-correlation with the number of years a reef maintains cover above the required thresholds
-[@fig-access-esm1-5-conn-carbonate]. The correlation between $\text{log10}(S)$ and
+[@fig-access-esm1-5-depth-carbonate]. In contrast, log10-transformed total connectivity
+strength ($\text{log10}(S)$) was found to have no correlation with the number of years a
+reef maintains cover above the required thresholds
+[@fig-access-esm1-5-depth-conn-carbonate]. The correlation between $\text{log10}(S)$ and
 $\theta_0$ slightly decreases as the assumed threshold for $\theta_0$ increases.
@@
 years cover exceeds the carbonate budget threshold. Point colour represents the median reef
-depth in metres. Red points represent the mean number of years above an assumed carbonate
-budget threshold across reefs. Note that deeper reefs are better able to maintain cover
-above the indicative carbonate budget threshold. Displays results from median time series
-using
-ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
-fig-align="center" width="14.82cm"}
-
-![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
-2075. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
-total connectivity strength and the number of years cover exceeds the carbonate budget
-threshold. The colour of each point represents the base-10 log of scaled reef total
-connectivity strength. Red points represent the mean number of years above a carbonate
-threshold across reefs. Displays results from median time series using
-ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#fig-access-esm1-5-conn-carbonate
+depth in metres in the left-hand panel, and log total connectivity strength in the
+right-hand panel. Red points represent the mean number of years above an assumed carbonate
+budget threshold across reefs. Deeper reefs are better able to maintain cover above the
+indicative carbonate budget threshold, while there is no considerable relationship between
+connectivity strength and carbonate budget maintenance. Displays results from median time
+series using
+ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
 fig-align="center" width="14.82cm"}
@@
 for reef restoration efforts [@anthony2020; @hock2017], current connectivity modelling
-methods, and our modelling framework, suggest that connectivity may not be as important for
-reef resilience under projected conditions as factors such as depth **\[TI: TO BE
-REVISITED\]**. We suggest further analyses that investigate the benefits of incorporating
-depth-based resilience into reef intervention decision making, as well as further research
-and development in connectivity modelling methods for whole-ecosystem scales.
+methods, in combination with our modelling framework, suggest that connectivity may not be
+as important for reef resilience under projected conditions as environmental factors such as
+depth and thermal stress levels. We suggest further analyses that investigate the benefits
+of incorporating depth-based resilience into reef intervention decision making, as well as
+further research and development in connectivity modelling methods for whole-ecosystem
+scales.
 

### 2025-08-17 paper/paper_draft.qmd
Various proof-reading changes and improvements

@@
 cover and community complexity [@perry2012; @desbiens2021], environmental processes, and
-ocean chemistry [@perry2015; @eyre2018]. For Great Barrier Reef mid and outer shelf reefs,
-maintaining positive carbonate budgets requires approximately 17% live coral cover
-[@desbiens2021].
+ocean chemistry [@perry2015; @eyre2018]. For GBR mid-shelf and offshore reefs, maintaining
+positive carbonate budgets requires approximately 17% live coral cover [@desbiens2021].
 
@@
 ![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all
-considered reefs (points). Colour-coded areas outline GBR marine park management regions,
+considered reefs (points). Colour-coded polygons outline GBR marine park management regions,
 where orange represents the Far Northern management region, green represents
 Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
-[@GBRMPA2007]. Reef centroids are marked individually for visual clarity, and are coloured
+[@GBRMPA2007]. Reef centroids are marked individually for visual clarity and are coloured
 according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
@@
 (ECS) values within the Intergovernmental Panel on Climate Change (IPCC) assessed likely
-range. The IPCC defines ECS as the long term warming caused by a doubling of carbon dioxide
+range. The IPCC defines ECS as the long-term warming caused by a doubling of carbon dioxide
 above its pre-industrial concentration [@forster2021]. While this assessment does not
@@
 mechanism which we use as an indicator of general performance of GCMs for the region. An
-overview of the selected GCMs are provided in @tbl-gcms. Note here that Grose et al.,
+overview of the selected GCMs is provided in @tbl-gcms. Note here that Grose et al.,
 [-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides
@@
 
-Projections using Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the
-plausible emission pathway. It represents a moderate emissions scenario with continued CO2
-emissions comparable to present day until 2050, after which emissions gradually decline
+Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission
+pathway. It represents a moderate emissions scenario with continued CO~2~ emissions
+comparable to present day until 2050, after which emissions gradually decline
 [@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.66°C of global
 atmospheric warming in the 2081-2100 period relative to 1850-1900. The use of these GCMs
-therefore allow for a range of possible climate futures to be explored, capturing the
-uncertainty in future responses to CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023;
-@shepherd2018]) and enables the assessment of model projected coral reef behaviour over a
-broad range of independently derived climate futures [@abramowitz2019].
+therefore allow for a range of possible climate futures to be explored, capturing
+uncertainty in future responses to CO~2~ increases (@sfig-ecs; @fig-methods-dhws;
+[@grose2023; @shepherd2018]) and enables the assessment of modelled coral reef behaviour
+over a broad range of independently derived climate futures [@abramowitz2019].
 
@@
 each calendar month (January through December) across the 28-year baseline period from 1985
-to 2012. For each month separately, this climatological baseline was then adjusted to center
-at year 1988.2857, which attempts to account for any long-term trends within the baseline
-years themselves (see Skirving et al. [@skirving2020]). The adjustment ensures that the
+to 2012. For each month separately, this climatological baseline was adjusted to centre at
+year 1988.2857, which attempts to account for any long-term trends within the baseline years
+themselves (see Skirving et al. [@skirving2020]). The adjustment ensures that the
 climatology represents conditions at a specific temporal reference point rather than being
@@
 
-::: {#tbl-gcms}
 | Global Climate Model source | ECS value (°C)     | Interpreted relative severity | Results found in |
@@
 very-likely ECS range and was taken as an intermediate model with results displayed in the
-main text.
-:::
+main text. {#tbl-gcms}
 
@@
 
-An exploratory scenario modelling approach is adopted for this investigation. The method
+An exploratory scenario modelling approach was adopted for this investigation. The method
 involves exploring a wide range of plausible futures under different assumptions of
@@
 forecast specific outcomes, exploratory modelling aims to systematically explore many
-possible futures to identify patterns and, in management contexts, robust strategies that
-perform well across those diverse conditions, as well as conditions in which such strategies
-may fail. Such an exploratory approach lends itself well to the purpose of the
-investigation. Specifically, to assess the role of DHW, connectivity, and depth to identify
-the environmental and reef characteristics that support structural resilience.
+possible futures to identify patterns. Allowing for the identification of robust management
+strategies that perform well across those diverse conditions, as well as conditions in which
+such strategies may fail. Such an exploratory approach lends itself well to the purpose of
+the investigation. Specifically, to assess the role of thermal stress, connectivity, and
+depth to identify the environmental and reef characteristics that support structural
+resilience.
 
@@
 
-To apply exploratory scenario modelling, the approach employed a modelling framework
-involving two separate systems: ADRIA (the Adaptive Dynamic Reef Interventin Algorithms
-platform) and CoralBlox. ADRIA is a multi-criteria decision support platform designed to
-help reef managers address climate change challenges in coral reef systems [@iwanaga2023].
-The ADRIA platform provides functionality for scenario generation and analysis as well as
-providing the technical infrastructure to couple environmental and ecosystem
-representations. CoralBlox is a computationally efficient coral population model. It
-simulates functional/morphological groups of corals over its life cycle, competing for
-available space over time [@ribeirodealmeida2024]. The coupled framework is referred to as
+To apply exploratory scenario modelling, we employed a modelling framework involving two
+separate systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and
+CoralBlox. ADRIA is a multi-criteria decision support platform designed to help reef
+managers address climate change challenges in coral reef systems [@iwanaga2023]. The ADRIA
+platform provides functionality for scenario generation and analysis as well as providing
+the technical infrastructure to couple environmental and ecosystem representations.
+CoralBlox is a computationally efficient coral population model. It simulates
+functional/morphological groups of corals over their life cycles, competing for available
+space over time [@ribeirodealmeida2024]. The coupled framework is referred to as
 ADRIA-CoralBlox.
@@
 detailed in the supplementary material. Of important note, however, is that the
-representation of bleaching mortalities follow Bozec et al., [-@bozec2022] albeit with a
+representation of bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a
 scaling coefficient to incorporate the amelioration effect that depth may have, following
-Baird et al., [@baird2018]. The scaling reduces the proportion of coral colonies impacted by
-high heat stress as depth increases. Tropical cyclones and impact of wave activity on reefs
-were not included in this investigation.
+Baird et al., [@baird2018]. This depth-scaling reduces the proportion of coral colonies
+impacted by high heat stress as depth increases. The impacts of tropical cyclones and wave
+activity on reefs were not included in this investigation.
 
@@
 
-\*\* need information on GBR1 connectivity used \*\*
+\*\* need information on generation of GBR1 connectivity used \*\*
 
@@
 location (i.e., mean of all 24 spawning days). While the connectivity strengths do not vary
-from year to year within each simulation, they do vary between reefs which are of varying
-sizes, providing sufficient heterogeneity to capture spatial patterns in larval dispersal
-and settlement dynamics. The spatial variability also enables investigations into the
-influence of connectivity strength and its role in driving recovery processes.
+from year to year within each ADRIA-CoralBlox simulation, they do vary between reefs which
+are of varying sizes, providing sufficient heterogeneity to capture spatial patterns in
+larval dispersal and settlement dynamics. This spatial variability also enables
+investigations into the influence of connectivity strength and its role in driving recovery
+processes.
 
@@
 
--   $S$ is the sum of outgoing and incoming connections, indicating the total connectivity
+-   $S$ is the sum of outgoing and incoming connectivity, indicating the total connectivity
     strength.
@@
 whole-of-GBR scale but were found to lead to identical conclusions about characteristics
-influencing cluster cover compared to management area and bioregion scale analyses, and so
+influencing cluster cover compared to management area and bioregion scale analyses and so
 are not shown here. To compare time series clustering results across GCMs, management area
@@
 Partial Dependence Analysis was conducted to understand the relationship between individual
-features and time series cluster predictions using a trained Random Forest (RF) classifier
-[@friedman2001]. The analysis utilised the reef characteristics of interest as the
-predictors, including the median reef depth, mean DHW for the given GCM, total connectivity
-strength, and the outgoing-to-incoming connectivity ratio. The full dataset consisted of the
-time series cluster assignment of each of the 2429 reefs under the five GCMs explored, for a
-total of 12,145 samples. The dataset was randomly split into training (60%) and testing
-(40%) subsets to ensure model generalisability. The RF classifier achieved a 99% accuracy on
-the training set and 66% on the test set.
-
-While the 99% accuracy suggests the classifier is overfit to the training data, the 66% test
+features and bioregion-scale time series cluster predictions using a trained Random Forest
+(RF) classifier [@friedman2001]. The analysis utilised the reef characteristics of interest
+as the predictors, including the median reef depth, mean DHW for the given GCM, total
+connectivity strength, and the outgoing-to-incoming connectivity ratio. The full dataset
+consisted of the time series cluster assignment of each of the 2429 reefs under the five
+GCMs explored, for a total of 12,145 samples. The dataset was randomly split into training
+(60%) and testing (40%) subsets to ensure model generalisability. The RF classifier achieved
+99% accuracy on the training set and 66% on the test set.
+
+While 99% accuracy suggests the classifier is overfit to the training data, the 66% test
 accuracy indicates a meaningful relationship between modelled reef characteristics and their
@@
 cross-validation demonstrates the generalised performance of the RF classifier is reliable.
-Furthermore, F1 performance scores for Low, Medium, and High were determined to be 0.7, 0.57
-and 0.68 respectively, indicating balanced performance across the cluster categories. Lower
-performance with the Medium cluster reflect the inherent difficulty of classifying
-transitional states in natural systems. For management applications, this level of
-performance provides valuable decision support when combined with expert knowledge and the
-model's probabilistic outputs.
+Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
+0.7, 0.57 and 0.68 respectively, indicating balanced performance across the cluster
+categories. Lower performance with the Medium cluster reflects the inherent difficulty of
+classifying transitional states in natural systems. For management applications, this level
+of performance provides valuable decision support when combined with expert knowledge and
+the model's probabilistic outputs.
 
@@
 Values for individual predictors were systematically (one-at-a-time) varied across a grid of
-50 equally spaced points spanning its range, while all other features were left at their
-modelled values. The procedure creates (1) a modified test dataset, where the target
-predictor was set to the grid value for all samples, (2) generates probabilistic predictions
+50 equally spaced points spanning the predictor's range, while all other features were left
+at their modelled values. The procedure creates (1) a modified test dataset, where the
+target predictor was set to the grid value for all samples, (2) probabilistic predictions
 for all three cluster classes using the trained RF classifier, and (3) the mean predicted
-probability for each class was calculated across all test observations. The median was also
-assessed (not shown) but was found not to substantially influence the interpretation of the
-analysis results. The process isolates the marginal effect of each predictor by averaging
-over the natural distribution of all other representative reef characteristics in the test
-dataset.
+probability for each class across all test observations. The median was also assessed (not
+shown) but was found not to substantially influence the interpretation of results. The
+process isolates the marginal effect of each predictor by averaging over the natural
+distribution of all other representative reef characteristics in the test dataset.
 
@@
 $\theta_{0}$ to indicate the budget equilibrium). Greater number of years above $\theta_{0}$
-therefore suggests greater resilience and opportunity for recovery.
+suggests greater resilience and opportunity for recovery.
 
@@
 
-The relationship between the number of years above $\theta_{0}$ and median reef depth was
-then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
-adopted as reef depth and connectivity strength distributions are expected to be non-normal
-and highly skewed. Furthermore, reefs are naturally of different types and experience
-different conditions, and so the monotonic trends (whether the relationship consistently
-increase or decrease) rather than the exact quantitative relationship was of interest for
-this analysis.
+The relationships between the number of years above $\theta_{0}$ and characteristics such as
+median reef depth and Log-10 total connectivity strength were then assessed with Spearman's
+rank correlation. Spearman's correlation coefficient was adopted as reef depth and
+connectivity strength distributions are expected to be non-normal and highly skewed.
+Furthermore, reefs are naturally of different types and experience different conditions, and
+so the monotonic trends (whether the relationship consistently increase or decrease) rather
+than the exact quantitative relationship was of interest for this analysis.
 
@@
 There were substantial differences in the maintenance of coral cover post 2030 between the
-GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs by
-their categorisation (Low, Medium and High). Results are displayed at the Management area
-scale to illustrate the spatial differences in cover trajectories. Of the GCMs explored,
-NorESM2-MM has the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit
-continuing recovery and decline dynamics up to 2075 under this hypothetical climate future.
-
-Unsurprisingly, recovery phases are predominantly seen in the reefs in the High category,
-with Medium and Low exhibiting lesser probability of such periods of recovery. Generally,
-recovery and increases in coral cover are visible in simulated results up to 2045. Under
-NorESM2-MM, the Far Northern Management area were found to have the most similar temporal
-behaviour between Low and High categories compared to other Management areas
-[@tbl-cluster-cid] due to the low degree of coral cover [@fig-gcm-cover-trajectories].
+GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs
+across clusters (Low, Medium and High).
+
+Of the GCMs explored, NorESM2-MM had the lowest Equilibrium Climate Sensitivity (2.5°C) and
+reefs exhibit continuing recovery and decline dynamics up to 2075 under this hypothetical
+climate future. Unsurprisingly, recovery phases were predominantly seen in the reefs in the
+High category, with Medium and Low exhibiting lesser probability of such periods of
+recovery. Generally, recovery and increases in coral cover were visible in simulated results
+up to 2045. Under NorESM2-MM, the Far Northern Management area were found to have the most
+similar temporal behaviour between Low and High categories compared to other Management
+areas (@tbl-cluster-cid) due to the low degree of coral cover overall
+(@fig-gcm-cover-trajectories).
 
@@
 occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs time
-series occur under ACCESS-CM2 [@fig-methods-dhws]. Under conditions represented by high ECS
+series occur under ACCESS-CM2 (@fig-methods-dhws). Under conditions represented by high ECS
 value GCMs - specifically, ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and GFDL-CM4
 (4.1°C) - all reefs are largely in decline across all management areas from 2055
-[@tbl-cluster-cid].
+(@tbl-cluster-cid).
 
@@
 occurring in the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management
-areas respectively [@sfig-gcm-cluster-map]. Of the 503 consistently assigned reefs, 32%, 7%
-and 61% are clustered into Low, Medium and High clusters respectively. High assignment
-variability across GCMs is expected as spatial differences in a given GCM's DHW trajectory
-result in reefs being impacted at different relative magnitudes within each Management
-areas.
+areas respectively (@sfig-gcm-cluster-map). Of the 503 consistently assigned reefs, 32%, 7%
+and 61% are clustered into Low, Medium and High clusters respectively. High levels of
+assignment variability across GCMs are expected as due to spatial differences in each given
+GCM’s DHW trajectories.
 
@@
 CID values are calculated for percentage cover time series (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) time series (@sfig-gcm-dhw-trajectories).
-Complexity invariant distance represents the euclidean distance between time series, corrected by the complexity of the two time series.
+Complexity invariant distance represents the Euclidean distance between time series, corrected by the complexity of the two time series.
 CID values are used to quantify overall differences between these two cluster levels at management area and GCM levels.
@@
 In contrast to the broad temporal behaviour at the Management area scale, the relationship
-between reef characteristics and reefs' assigned categories were found to be similar at the
+between reef characteristics and assigned categories were found to be similar at the
 bioregion scale across GCMs. Results are only shown and discussed for ACCESS-ESM1-5, an
-intermediate Equilibrium Climate Sensitivity scenario [@sfig-ecs]. Those interested in
-results for the other assessed GCMs are referred to Grier and Iwanaga [-@grier2025]. Across
-bioregions, reefs in the High category not only had greater levels of coral recovery but
-displayed persistence to 2050 [@sfig-access-esm1-5-bioregion-timeseries]. Reefs in the High
-category were consistently found to have the greatest median reef depths across bioregions
-[@fig-access-esm1-5-bioregion-depth].
+intermediate ECS scenario (@sfig-ecs). Those interested in results for the other assessed
+GCMs are referred to Grier and Iwanaga [-@grier2025]. Across bioregions, reefs in the High
+category not only had greater levels of coral recovery but displayed persistence to 2050
+(@sfig-access-esm1-5-bioregion-timeseries). Reefs in the High category were consistently
+found to have the greatest median reef depths across bioregions
+(@fig-access-esm1-5-bioregion-depth).
 
@@
 In many bioregions reefs in the Low category have the lowest correlation between coral cover
-and DHW whereas reefs in the High category were found to have the strongest correlation
-(@sfig-access-esm1-5-bioregion-dhwcor). Conversely, there are no consistent patterns across
-bioregions when comparing their temporal behaviour with respect to their reef area and mean
-of DHWs (@sfig-access-esm1-5-bioregion-dhwmean). There were no consistent differences across
-bioregions and GCMs between clusters in their reefs' initial proportion of habitable area
-occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion). Across most bioregions
-there were not consistent differences between clusters in connectivity metrics such as
-source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and total
+and inverse-DHW time series whereas reefs in the High category were found to have the
+strongest correlation (@sfig-access-esm1-5-bioregion-dhwcor). Across six of the 29
+bioregions reef mean DHW levels increased as cluster cover decreased
+(@sfig-access-esm1-5-bioregion-dhwmean). There were no consistent patterns across bioregions
+in their reefs' initial proportion of habitable area occupied by corals and cluster
+assignment (@sfig-access-esm1-5-bioregion-initialproportion). Across most bioregions there
+were not consistent differences between clusters in connectivity metrics such as Log-10
+source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 total
 connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
-
-**\[TI: Note, I'm not sure if this section is interesting enough to keep now... let's
-discuss.\]**
 
@@
 reef characteristics that influence its temporal behaviour, and thus its cluster assignment
-into Low, Medium, or High. These include, for each of the 2429 reefs assessed, the
-indicative median reef depth, the mean DHW experienced, its coral carrying capacity, total
-connectivity strength and source-to-sink ratio. Reefs' bioregion membership was excluded
-from this analysis due to its categorical nature providing limited interpretable
-information, and is further justified by its low feature importance score of 10%, the lowest
-of all predictors [-@fig-ts-cluster-pdp, Panel A]. Reef median depth and mean DHW level have
-the highest feature importance scores, accounting for 25% and 23% predictive importance
-respectively. The carrying capacity of a reef accounts for 14.3% feature importance.
-Connectivity strength and source-to-sink ratio both had feature importance scores of \~13%.
+into Low, Medium, or High. Bioregion classification was excluded from this analysis as a
+predictor due to its categorical nature providing limited interpretable information, and is
+further justified by its low feature importance score of 10%, the lowest of all predictors
+(@fig-ts-cluster-pdp; Panel A). Reef median depth and mean DHW level have the highest
+feature importance scores, accounting for 25% and 23% predictive importance respectively.
+The carrying capacity of a reef accounts for 14.3% feature importance. Connectivity strength
+and source-to-sink ratio both had feature importance scores of \~13%.
 
 Reefs have the greatest probability of being clustered into Low if shallow, and High at
-greater depths, with medium cluster reefs exhibiting a lower, and stable, variation in
-assignment probability across depth ranges [@fig-ts-cluster-pdp, Panel B]. A large increase
-in the probability of a reef being categorised as High can be seen between 10 and 15 meters
-depth. This is at the edge of the depth range used in current deployment efforts
-[@howlett2021; @randall2021; @whitman2024], but indicates a depth range that could be
-adopted to maximise longevity and benefits of, for example, coral seeding activities. With
-regard to DHWs, assignment probability is roughly equal across the three categories up to 6
-DHW. A sharp delineation can be seen \> 6 DHW when comparing High with other categories,
-with lower assignment probability (\~25%) compared to Medium and Low (\~40%)
-[@fig-ts-cluster-pdp, Panel B].
+greater depths, with medium cluster reefs exhibiting a lower, and more stable, assignment
+probability across depth ranges (@fig-ts-cluster-pdp; Panel B). A large increase in the
+probability of a reef being categorised as High can be seen between 10 and 15 meters depth.
+This is at the edge of the depth range used in current deployment efforts [@howlett2021;
+@randall2021; @whitman2024] but indicates a depth range that could be adopted to maximise
+longevity and benefits of, for example, coral seeding activities. Across mean DHW values,
+assignment probability is roughly equal across the three categories up to 6 DHW. A sharp
+delineation can be seen \> 6 DHW when comparing High with other categories, with lower
+assignment probability (\~25%) compared to Medium and Low (\~40%) (@fig-ts-cluster-pdp;
+Panel B).
 
@@
 indicate that their influence on its categorical assignment is concentrated at the low range
-of predictor values [@fig-ts-cluster-pdp]. This aligns with the right-skewed distributions
+of predictor values (@fig-ts-cluster-pdp). This aligns with the right-skewed distributions
 of values across reefs for these three predictor variables. Beyond this lower range, the
@@
 
-Assessing random forest prediction performance reveals increasing performance as bioregion
-mean reef depth and carrying capacity increase [@sfig-rf-predictor-perf]. This highlights
-where there is unexplained variation between reefs that contributes to cluster assignment
-and reef cover outcomes but is not captured by our included predictor variables.
+Assessing random forest prediction accuracy across predictor values, summarised by
+bioregions, reveals increasing performance as bioregion mean reef depth and carrying
+capacity increase (@sfig-rf-predictor-perf). This highlights where there is unexplained
+variation between reefs that contributes to cluster assignment and reef cover outcomes but
+is not captured by our included predictor variables.
 
@@
 represent the predictor values present in the test dataset, providing a rough indication of
-predcitor value distribution across
+predictor value distribution across
 reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center"
@@
 
-Reef median depth has a moderate positive correlation with the number of years a reef
+Reef median depth had a moderate positive correlation with the number of years a reef
 maintains coral cover above the assumed carbonate budget threshold required to sustain live
-coral cover ($\theta_{0}$). Greater median depth is a key characteristic defining reefs that
-sustain coral cover above $\theta_{0}$ [@fig-access-esm1-5-depth-carbonate]. Unsurprisingly,
-the number of years above $\theta_0$ substantially decreases as $\theta_0$ is increased, as
-does the Spearman's correlation. This is likely due to an increasing number of reefs being
-unable to maintain coral cover above $\theta_0$ as it is increased, with the distribution of
-years above threshold becoming increasingly right-skewed
-[@fig-access-esm1-5-depth-carbonate]. In contrast, log10-transformed total connectivity
-strength ($\text{log10}(S)$) was found to have no correlation with the number of years a
-reef maintains cover above the required thresholds
-[@fig-access-esm1-5-depth-conn-carbonate]. The correlation between $\text{log10}(S)$ and
-$\theta_0$ slightly decreases as the assumed threshold for $\theta_0$ increases.
-
-![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075.
-The assessed carbonate budget thresholds range from 10 to 20% of total reef area. Bracketed
-x-axis values represent the Spearman's correlation between reef depth and the number of
-years cover exceeds the carbonate budget threshold. Point colour represents the median reef
-depth in metres in the left-hand panel, and log total connectivity strength in the
-right-hand panel. Red points represent the mean number of years above an assumed carbonate
-budget threshold across reefs. Deeper reefs are better able to maintain cover above the
-indicative carbonate budget threshold, while there is no considerable relationship between
-connectivity strength and carbonate budget maintenance. Displays results from median time
-series using
+coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
+that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate).
+Unsurprisingly, the number of years above $\theta_0$ substantially decreased as $\theta_0$
+is increased, as does the Spearman's correlation. Decreasing correlation levels are likely
+due to an increasing number of reefs being unable to maintain coral cover above $\theta_0$
+as it is increased, with the distribution of years above threshold becoming increasingly
+right-skewed (@fig-access-esm1-5-depth-conn-carbonate). In contrast, log10-transformed total
+connectivity strength ($\text{log10}(S)$) was found to have no correlation with the number
+of years a reef maintains cover above the required thresholds
+(@fig-access-esm1-5-depth-conn-carbonate). The correlation between $\text{log10}(S)$ and
+$\theta_0$ slightly increased as the assumed threshold for $\theta_0$ increased.
+
+![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
+(y-axis). The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef variables (depth -
+left and Log-10 connectivity strength - right) and the number of years cover exceeds the
+carbonate budget threshold. Point colour represents the median reef depth in metres in the
+left-hand panel, and Log-10 total connectivity strength in the right-hand panel. Red points
+represent the mean number of years above an assumed carbonate budget threshold across reefs.
+Deeper reefs are better able to maintain cover above the indicative carbonate budget
+threshold, while there is no considerable relationship between connectivity strength and
+carbonate budget maintenance. Displays results from median time series using
 ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
@@
 between Low, Medium and High reef clusters in cover time series are most notable under these
-two GCMs [@tbl-cluster-cid; @fig-gcm-cover-trajectories]. Maintenance of coral cover into
+two GCMs (@tbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into
 the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of
 future recovery and timespan of cover maintenance increase as GCM ECS increases
-[@fig-gcm-cover-trajectories]. Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
+(@fig-gcm-cover-trajectories). Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
 large declines and lower rates of recovery in high cover clusters are common compared to
@@
 
-Reefs in different clusters largely do not differ in mean modelled DHW levels experienced,
+Reefs in different clusters largely do not differ in mean modelled DHW levels experienced
 and exhibit overall similar DHW time series. While these reefs experience similar magnitude
@@
 compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest
-that rubble instability is inversely correlated with reef depth, possibly limiting the
-juvenile recruitment capacity of shallow reefs. A caveat to these depth-resilience findings
-is the quality of the bathymetry data used to calculate median reef depth. As detailed
-previously, estimates of median reef depth are derived from satellite imagery (at $10m^2$
-resolution) which can be subject to high degrees of uncertainty, both in terms of the
-estimated depth at for each pixel as well as their alignment to the established GBRMPA reef
-outlines.
+that rubble instability is inversely correlated with reef depth, possibly limiting juvenile
+recruitment capacity of shallow reefs. A caveat to these depth-resilience findings is the
+quality of the bathymetry data used to calculate median reef depth. As detailed previously,
+estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution)
+which can be subject to high degrees of uncertainty, both in terms of the estimated depth at
+for each pixel as well as their alignment to the established GBRMPA reef outlines.
 
@@
 no explicit justifications for this depth range, restoration depth is likely constrained by
-snorkeling and diving logistical accessibility, visual identification of sites from the
-surface, in combination with tourism return value. Our results suggest that of the assessed
-reefs ocurring within the 1-10m depth range (1736 reefs), 62% (1082) of reefs fall into the
-low and medium clusters (across all GCMs at the GBRMPA management region scale), with many
-unable to maintain positive carbonate budgets under future conditions. Partial dependence
-analysis revealed a range of depths from 10-15m where the probability of a reef being
-clustered into the High cover category increased substatially. Considering this 10-15m depth
-range when assessing possible restoration sites may reduce the exposure of planted and
-seeeded corals to high thermal stress, while still maintaining effective logistical access
-to sites. Reef intervention planning is a complex and challenging decision making process
-[@anthony2020], and our results suggest that deployment site depth may be an important
-factor to additionally consider when assessing the long-term resilience of deployment sites.
+snorkelling and diving deployment and monitoring logistical accessibility, visual
+identification of sites from the surface, in combination with tourism return value. Our
+results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
+reefs), 62% (1082) of reefs fall into the low and medium clusters (across all GCMs at the
+GBRMPA management region scale), with many unable to maintain positive carbonate budgets
+under future conditions. Partial dependence analysis revealed a range of depths from 10-15m
+where the probability of a reef being clustered into the High cover category increased
+substatially. Considering this 10-15m depth range when assessing possible restoration sites
+may reduce the exposure of planted and seeded corals to high thermal stress, while still
+maintaining effective logistical access to sites. Reef intervention planning is a complex
+and challenging decision-making process [@anthony2020], and our results suggest that
+deployment site depth may be an important factor to additionally consider when assessing the
+long-term resilience of sites.
 
@@
 receives following disturbance [@hock2017; @mumby2008; @torres2024]. In contrast, our
-results suggest that there are few differences between resilient and non-resilient reefs in
-connectivity metrics such as the ratio of outgoing to incoming larval connectivity and total
-connectivity strength. Furthermore, our results suggest no relationship between connectivity
-and the ability of reefs to maintain positive carbonate budgets under future conditions.
-There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent
-generation connectivity modelling is able to identify reefs that are important for recovery
-processes, with findings dependent on the larval connectivity model used. These
-investigations were performed using prior generations of larval connectivity models
-parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods. Using
-updated 1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal
-sample of particle flows, our results suggest that larval connectivity alone is not as
-important for reef resilience and recovery as environmental refugia such as depth.
+results suggest that while connectivity metrics show some levels of cluster predictor
+importance, there are few differences between resilient and non-resilient reefs in metrics
+such as source-to-sink connectivity ratio and total connectivity strength. Furthermore, our
+results suggest no relationship between connectivity strength and the ability of reefs to
+maintain positive carbonate budgets under future conditions. There has been contrasting
+evidence [@bode2018; @hock2017] surrounding whether recent generation connectivity modelling
+is able to identify reefs that are important for recovery processes, with findings dependent
+on the larval connectivity model used. These investigations were performed using prior
+generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and
+1996-2002 [@bode2018] time periods. Using updated 1km^2^ resolution larval connectivity
+across the whole GBR, with a limited temporal sample of particle flows, our results suggest
+that larval connectivity alone is not as important for reef resilience and recovery as
+environmental refugia such as depth.
 
@@
 timesteps through growth. Due to the availability of quality future projected data we do not
-consider the impacts of waves, cyclones, currents and Crown of Thorns Starfish (CoTS) on
-coral colony survival and bleaching [@massel1993; @deaker2022]. Uncertainty in connectivity
-modelling outputs, satellite-derived bathymetry data and future thermal stress projections
-are likely to influence the results obtained in this investigation. While the resolution of
-connectivity data used in this investigation improves upon data used in comparable studies
-[@bozec2025], the time-mean implementation used may not effectively capture long term
-patterns [@vogt-vincent2023]. Using alternative connectivity implementation methods that
-better capture the ecological-timescale trends in reef connections rather than the high
-daily variability, would improve confidence in the connectivity findings of this
-investigation [@vogt-vincent2023]. The DHW data used in this investigation have not been
-bias corrected for the Great Barrier Reef region and are part of a wider Australian dataset
-[@dixon2022] developed using statistical downscaling. Additionally, Lachs et al.
-[@lachs2021] suggest the utility of DHW levels for prediction of coral bleaching can be
-improved by reducing the threshold for HotSpot Anomaly values from MMM +1 to MMM, and
-reducing the accumulation window from 12 weeks to 8 weeks. We investigate a range of future
-climate responses, thermal projections and ecological parameterisations of ADRIA - CoralBlox
-to account for many possible futures, and our results suggest the factors that influence
-reef resilience are consistent across these scenarios.
+consider other important impacts such as waves, cyclones, currents and Crown of Thorns
+Starfish (CoTS) on coral colony survival and bleaching [@massel1993; @deaker2022].
+Uncertainty in connectivity modelling outputs, satellite-derived bathymetry data and future
+thermal stress projections are likely to influence the results obtained in this
+investigation. While the resolution of connectivity data used in this investigation improves
+upon data used in comparable studies [@bozec2025], the time-mean implementation used may not
+effectively capture long term patterns [@vogt-vincent2023]. Using alternative connectivity
+implementation methods that better capture the ecological-timescale trends in reef
+connections rather than the high daily variability, would improve confidence in the
+connectivity findings of this investigation [@vogt-vincent2023]. The DHW data used in this
+investigation have not been bias corrected for the Great Barrier Reef region and are part of
+a wider Australian dataset [@dixon2022] developed using statistical downscaling.
+Additionally, Lachs et al. [@lachs2021] suggest the utility of DHW levels for prediction of
+coral bleaching can be improved by reducing the threshold for HotSpot Anomaly values from
+MMM +1 to MMM and reducing the accumulation window from 12 weeks to 8 weeks. We investigate
+a range of future climate responses, thermal projections and ecological parameterisations of
+ADRIA - CoralBlox to account for many possible futures, and our results suggest the factors
+that influence reef resilience are consistent across these scenarios.
 
@@
 sources of uncertainty in the depth estimates used for this study. Satellite-derived
-estimates are subject to different bottom types (rock, sand, seagrass, etc) and how these
-affect reflectance, the water penetration depth of satellite sensors, influence of local
+estimates are subject to different bottom types (rock, sand, seagrass, etc) and their effect
+on reflectance, the water penetration depth of satellite sensors, influence of local
 conditions (e.g., turbidity and wave activity), among many other factors. The median depths
@@
 GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton2025], for example, identified 120
-false positives, where features identified as reefs were in actuality sand banks or rocky
-reefs (rather than coral reefs). Reefs with bathymetry data of less than 5% of its
-indicative area were excluded from analysis to ensure analyses were not conducted on reefs
-with no data coverage (see @sfig-depth-cutoff). The existing GBRMPA reef outlines were
-adopted to align with other ongoing modelling and analyses conducted as part of the Reef
-Restoration and Adaptation Program (<https://gbrrestoration.org>; [@thereef]).
+false positives, where features identified as reefs were sand banks or rocky reefs (rather
+than coral reefs). Reefs with bathymetry data of less than 5% of its indicative area were
+excluded from analysis to ensure analyses were not conducted on reefs with no data coverage
+(see @sfig-depth-cutoff). The existing GBRMPA reef outlines were adopted to align with other
+ongoing modelling and analyses conducted as part of the Reef Restoration and Adaptation
+Program (<https://gbrrestoration.org>; [@thereef]).
 
@@
 one, a formal mechanistic and spatial validation of the model represents an area for future
-refinement, and is the focus of a future publication. Indicative results are included in the
+refinement and is the focus of a future publication. Indicative results are included in the
 supplementary **\[TI: For Pedro to include! :`D`\].** The consistency of projected patterns
@@
 on structural resilience under future conditions, rather than provide spatially explicit and
-highly accurate and precise predictions of reef outcomes. Using this approach we suggest
-that reef depths is an important factor for reef resilience under thermal stress.
-
-Improvements in remote sensing approaches for broad scale bathymetry measurement, and
+precise predictions of reef outcomes. Using this approach, we suggest that reef depth is an
+important factor for reef resilience under thermal stress.
+
+Improvements in remote sensing approaches for broad scale bathymetry measurement and
 understanding of how depth impacts experienced thermal stress on reefs will further enhance
@@
 build on the findings of this study by assessing the impacts of prioritising reef depth in
-reef restoration decision making. Future analyses could incorporate further environmental
-and ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn
-Starfish [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
+reef restoration decision making. Future analyses could incorporate other environmental and
+ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn Starfish
+[@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
 
@@
 corymbose Acropora, corymbose non-Acropora, small massives and large massives. We do not
-model arborscent Acropora forms due to their distinct life history from other morphological
+model arborescent Acropora forms due to their distinct life history from other morphological
 groups. CoralBlox uses user-defined size classes that influence size-dependent growth and
@@
 The selected time frame prevents the classification from being overly influenced by any
-steep declines in the initial years of simulations, and avoids the post-2060 time period
+steep declines in the initial years of simulations and avoids the post-2060 time period
 where reefs are projected to be under severe stress and in a declined state [@bozec2025].

### 2025-08-17 paper/paper_draft.qmd
Standardise cluster language
Ensure that "cluster" is used when talking about time series clustering allocated categories, and associated analyses that revolve around these low, medium, high clusters.

@@
 Reefs in each time series cluster were compared to identify characteristics that differ
-between Low, Medium and High categories. These characteristics include reef median depth,
+between Low, Medium and High clusters. These characteristics include reef median depth,
 mean time series DHW, Pearson’s correlation between total coral cover and inverse DHW time
@@
 climate future. Unsurprisingly, recovery phases were predominantly seen in the reefs in the
-High category, with Medium and Low exhibiting lesser probability of such periods of
+High cluster, with Medium and Low exhibiting lesser probability of such periods of
 recovery. Generally, recovery and increases in coral cover were visible in simulated results
 up to 2045. Under NorESM2-MM, the Far Northern Management area were found to have the most
-similar temporal behaviour between Low and High categories compared to other Management
+similar temporal behaviour between Low and High clusters compared to other Management
 areas (@tbl-cluster-cid) due to the low degree of coral cover overall
@@
 intermediate conditions (in relative terms), there is potential for reefs in the High
-category to maintain coral cover levels around 20% to 2050. The highest peak DHW levels
+cluster to maintain coral cover levels around 20% to 2050. The highest peak DHW levels
 occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs time
@@
 
-Comparing across GCMs, it is common for reefs to switch between categories, including from
+Comparing across GCMs, it is common for reefs to switch between clusters, including from
 Low to High and vice versa (@sfig-gcm-bioregion-cluster-assignment). Of 2429 reefs, 20%
-(503) of reefs have consistent category assignment across all GCMs. Of the 503 consistently
+(503) of reefs have consistent cluster assignment across all GCMs. Of the 503 consistently
 assigned reefs, 49% are within the Far Northern Management area, with 7%, 13% and 31%
@@
 In contrast to the broad temporal behaviour at the Management area scale, the relationship
-between reef characteristics and assigned categories were found to be similar at the
+between reef characteristics and assigned clusters were found to be similar at the
 bioregion scale across GCMs. Results are only shown and discussed for ACCESS-ESM1-5, an
@@
 GCMs are referred to Grier and Iwanaga [-@grier2025]. Across bioregions, reefs in the High
-category not only had greater levels of coral recovery but displayed persistence to 2050
-(@sfig-access-esm1-5-bioregion-timeseries). Reefs in the High category were consistently
+cluster not only had greater levels of coral recovery but displayed persistence to 2050
+(@sfig-access-esm1-5-bioregion-timeseries). Reefs in the High cluster were consistently
 found to have the greatest median reef depths across bioregions
@@
 
-In many bioregions reefs in the Low category have the lowest correlation between coral cover
-and inverse-DHW time series whereas reefs in the High category were found to have the
+In many bioregions reefs in the Low cluster have the lowest correlation between coral cover
+and inverse-DHW time series whereas reefs in the High cluster were found to have the
 strongest correlation (@sfig-access-esm1-5-bioregion-dhwcor). Across six of the 29
@@
 longevity and benefits of, for example, coral seeding activities. Across mean DHW values,
-assignment probability is roughly equal across the three categories up to 6 DHW. A sharp
-delineation can be seen \> 6 DHW when comparing High with other categories, with lower
+assignment probability is roughly equal across the three clusters up to 6 DHW. A sharp
+delineation can be seen \> 6 DHW when comparing High with other clusters, with lower
 assignment probability (\~25%) compared to Medium and Low (\~40%) (@fig-ts-cluster-pdp;
@@
 Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a
-reef being classified to one of the three categories (Panel B). Partial Dependence Plots for
+reef being classified to one of the three clusters (Panel B). Partial Dependence Plots for
 bioregions were excluded as they were found to be uninformative. PDPs indicate the
-probability of a reef from the test dataset being clustered into each cluster category
+probability of a reef from the test dataset being clustered into each category
 depending on the predictor value on the x axis, when adjusted for values of other
@@
 under future conditions. Partial dependence analysis revealed a range of depths from 10-15m
-where the probability of a reef being clustered into the High cover category increased
+where the probability of a reef being clustered into the High cover cluster increased
 substatially. Considering this 10-15m depth range when assessing possible restoration sites
@@
 group) that is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The
-three reef clusters are labelled with qualitative-ordered categories from Low, Medium and
+three reef clusters are labelled with qualitative-ordered clusters from Low, Medium and
 High based on their median cover relative to each other cluster over the 2030-2060 period.

### 2025-08-22 paper/paper_draft.qmd
Add scatter plot that shows the distributions of reef depth and incoming
connectivity. The colour indicates the mean carbonate budget maintenance level across theta0 values.

@@
 
+![Scatter plot indicating reef median depth (metres) and Log10 weighted incoming connectivity for each reef.
+Point colours represent the mean number of years each reef maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover.
+Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
+fig-align="center" width="10cm"}
+
 ### Bioregion scale clustering

### 2025-08-22 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -112,6 +112,17 @@ for (i_gcm, GCM) in enumerate(GCMs)
     #     total_connectivity_carbonate_scatter,
     #     px_per_unit=dpi
     # )
+    gcm_threshold_columns = ["$(GCM)_years_above_$(x)" for x in 10:20]
+    context_layers[!, "$(GCM)_mean_positive_years"] = vec(mean(Matrix(context_layers[:, gcm_threshold_columns]), dims=2))
+    fig, ax, scat = scatter(context_layers.depth_med, context_layers[:, "$(GCM)_weighted_incoming_conn_log"], color=context_layers[:, "$(GCM)_mean_positive_years"], alpha=0.5)
+    Colorbar(fig[1,2], scat, label="Mean number of positive carbonate budget years \nacross θ")
+    ax.ylabel = "Log weighted incoming connectivity"
+    ax.xlabel = "Median depth [m]"
+    save(
+        joinpath(fig_out_dir, "depth_conn_mean_carbonate_budget.png"),
+        fig,
+        px_per_unit=dpi
+    )
 end
 
 man_area_gcm_cluster_cols = [Symbol("$(GCM)_management_area_clusters") for GCM in GCMs]

### 2025-08-22 paper/paper_draft.qmd
Add two-way interaction PDP plot to paper and move CID table to sup

@@
     key: sfig
+  custom:
+  - kind: float
+    reference-prefix: STable
+    key: stbl
 editor:
@@
 similar temporal behaviour between Low and High clusters compared to other Management
-areas (@tbl-cluster-cid) due to the low degree of coral cover overall
+areas (@stbl-cluster-cid) due to the low degree of coral cover overall
 (@fig-gcm-cover-trajectories).
@@
 (4.1°C) - all reefs are largely in decline across all management areas from 2055
-(@tbl-cluster-cid).
+(@stbl-cluster-cid).
 
@@
 GCM’s DHW trajectories.
-
-```{julia}
-#| echo: false
-#| warning: false
-#| message: false
-#| results: asis
-#| label: tbl-cluster-cid
-#| tbl-cap: Complexity invariant distance (CID) between low and high cluster median time series in each management area under each GCM.
-CID values are calculated for percentage cover time series (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) time series (@sfig-gcm-dhw-trajectories).
-Complexity invariant distance represents the Euclidean distance between time series, corrected by the complexity of the two time series.
-CID values are used to quantify overall differences between these two cluster levels at management area and GCM levels.
-CID values for percentage cover and DHW time series are not directly comparable as the time series use different units.
-
-using PrettyTables, Markdown
-cd("../src")
-include("../src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl"); # Quantify low-high cluster differences using CID metric.
-
-io = IOBuffer()
-
-header = ["GCM", "Management area", "CID - cover", "CID - DHW"]
-pretty_table(io, distances, backend=Val(:markdown), header=header)
-
-md_string = (String(take!(io)))
-Markdown.parse(md_string)
-```
 
@@
 reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center"
+width="14.82cm"}
+
+![Partial dependence plot indicating the probability of cluster assignment along interacting values of median reef depth (metres) and Log10 weighted incoming connectivity.
+Colour indicates the probability of assignment to each cluster, with lighter colours indicating higher probability of assignment.
+Panel A shows the probability of assignment for the Low cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability for the High cluster category.
+Probability values for each cluster are generated by the random forest classifier using each combination of depth and incoming connectivity values along the axes at 50 grid points.
+The actual distributions of depth and incoming connectivity values are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_conn_pdp.png){#fig-ts-cluster-pdp-twoway fig-align="center"
 width="14.82cm"}
@@
 between Low, Medium and High reef clusters in cover time series are most notable under these
-two GCMs (@tbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into
+two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into
 the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of
@@
 
+```{julia}
+#| echo: false
+#| warning: false
+#| message: false
+#| results: asis
+#| label: stbl-cluster-cid
+#| tbl-cap: Complexity invariant distance (CID) between low and high cluster median time series in each management area under each GCM.
+CID values are calculated for percentage cover time series (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) time series (@sfig-gcm-dhw-trajectories).
+Complexity invariant distance represents the Euclidean distance between time series, corrected by the complexity of the two time series.
+CID values are used to quantify overall differences between these two cluster levels at management area and GCM levels.
+CID values for percentage cover and DHW time series are not directly comparable as the time series use different units.
+
+using PrettyTables, Markdown
+cd("../src")
+include("../src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl"); # Quantify low-high cluster differences using CID metric.
+
+io = IOBuffer()
+
+header = ["GCM", "Management area", "CID - cover", "CID - DHW"]
+pretty_table(io, distances, backend=Val(:markdown), header=header)
+
+md_string = (String(take!(io)))
+Markdown.parse(md_string)
+```
+
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all

### 2025-08-22 src/ADRIA/HighResCoralStress/7_rf_analysis.jl

@@ -512,14 +512,35 @@ for (c, class_label) in enumerate(["Low", "Medium", "High"])
         colormap=base_cmap
     )
     abc = ["A","B","C"]
-    Label(gridlayout[1,1, Top()], "($(abc[c])) $(class_label) cluster \n ")
+    Label(gridlayout[1,1, Top()], "($(abc[c])) $(class_label) cluster \n ", font=:bold)
 end
 
 # ax.ytickformat = x -> string.(round.(10 .^ x; digits = 2))
 Colorbar(fig[0,:], limits=color_range, colormap=base_cmap, label="Probability of target cluster assignment", size=6, spinewidth=0.0, vertical=false)
 Label(fig[1, 0], "Log10 weighted incoming connectivity", tellwidth=false, tellheight=false, rotation=π / 2)
-Label(fig[2, 1:3], "Median depth [m]", tellheight=false, tellwidth=false)
+Label(fig[2, 1:3], "Median depth [m]\n ", tellheight=false, tellwidth=false)
 rowsize!(fig.layout, 2, Relative(0.01))
+rowsize!(fig.layout, 0, Relative(0.01))
+
+gridlayout2 = GridLayout(fig[3, 1:3])
+ax2 = Axis(
+    gridlayout2[1, 1],
+    ylabel="",
+    xlabel="Median depth [m]"
+)
+hist!(ax2, test_X.depth_med; color=(:gray))
+Label(gridlayout2[1,1, TopLeft()], "D", font=:bold)
+
+ax3 = Axis(
+    gridlayout2[1, 2],
+    ylabel="",
+    xlabel="Log10 weighted incoming connectivity"
+)
+hist!(ax3, test_X.weighted_incoming_conn; color=(:gray))
+Label(gridlayout2[1,2, TopLeft()], "E", font=:bold)
+
+Label(fig[3, 0], "Number of samples", tellwidth=false, tellheight=false, rotation=π / 2)
+rowsize!(fig.layout, 3, Relative(0.25))
 colsize!(fig.layout, 0, Relative(0.01))
 
 save(

### 2025-08-25 paper/paper_draft.qmd
Update connectivity sections to reflect weighted connectivity metrics
Include results for the interaction between depth and incoming connectivity on clustering and it's implications for restoration efforts etc.

@@
 in each year (12 days in total), while 2017 and 2020 are each represented by six spawning
-days each, coming to a total of 24 days of connectivity matrices. Indicative connectivity
+days each, coming to a total of 24 days of connectivity matrices.
+The values in these matrices indicate the probability of larval transfer between each pair of reefs in the GBR, herein referred to as connectivity strengths.
+Indicative connectivity
 strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
@@
 To assess the impact of reef connectivity on modelled outcomes we summarise inter-reef
-connections using the total strength of connections and the ratio of source-to-sink
-connectivity for each reef. The ratio of source-to-sink connectivity ($O:I$) for a target
+connections using weighted connectivity metrics (incoming and outgoing) and the ratio of source-to-sink
+connectivity for each reef.
+Weighted incoming connectivity is calculated by summing the product of each connection strength incoming to a target reef and the mean timeseries absolute coral cover (km^2^) of each matching source reef.
+This metric provides an approximation of overall larval flow into a reef, with high values indicating the target reef is supplied high volumes of larvae via strong connections and low values indicating the target reef has weak (or no) incoming connections or is supplied by small source populations.
+Weighted outgoing connectivity is calculated as the product of outgoing connectivity strength from a target reef and the mean timeseries absolute coral cover (km^2^) of the target reef, representing the larval flow leaving the target reef population.
+A limitation of these weighted connectivity metrics is that they do not incorporate the proportion of the source reef's population that is reproducing and producing larvae, instead taking the total coral cover area as an indicator of larval productivity.
+The ratio of source-to-sink connectivity ($O:I$) for a target
 reef represents the strength of the reef's outgoing larval flow relative to it's incoming
-larval flow (@eq-so-to-si). If a reef has no incoming connections, the $O:I$ equals the
-$S_O/N_O$ value. Incoming connections in this calculation, do not directly represent the
-larval supply gained as the population from which connections are coming from is not
+larval flow.
+This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$.
+Where S represents the sum of connectivity pobabilities, N represents the number of connections, O denotes outgoing connectivity from the target reef and I denotes incoming connectivity to the target reef.
+If a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value.
+Incoming connections in this calculation, do not directly represent the
+larval supply gained as the breeding populations from which connections are coming from are not
 represented. A source-to-sink ratio greater than 1 (a value greater than 0 on a log scale)
 indicates a reef has greater outgoing than incoming larval flow.
-
-$$
-O:I = \frac{S_O/N_O}{S_I/N_I}
-$$ {#eq-so-to-si}
-
-Where:
-
--   $S$ is the sum of outgoing and incoming connectivity, indicating the total connectivity
-    strength.
-
--   $N$ denotes the number of connections.
-
--   $O$ denotes outgoing (source) connections from a reef.
-
--   $I$ denotes incoming (sink) connections to a reef.
 
@@
 series, proportion of coral habitable area occupied by corals in the first timestep, ratio
-of source-to-sink larval connectivity and total strength of all larval connections between
-reefs.
+of source-to-sink larval connectivity and weighted incoming connectivity.
 
@@
 
-Partial Dependence Analysis was conducted to understand the relationship between individual
-features and bioregion-scale time series cluster predictions using a trained Random Forest
+Partial Dependence Analysis was conducted to understand the relationship between features and bioregion-scale time series cluster predictions using a trained Random Forest
 (RF) classifier [@friedman2001]. The analysis utilised the reef characteristics of interest
-as the predictors, including the median reef depth, mean DHW for the given GCM, total
-connectivity strength, and the outgoing-to-incoming connectivity ratio. The full dataset
+as the predictors, including the median reef depth, mean DHW for the given GCM, Log10 - weighted incoming connectivity, Log10 - weighted outgoing connectivity, and Log10 - outgoing-to-incoming connectivity ratio.
+The full dataset
 consisted of the time series cluster assignment of each of the 2429 reefs under the five
@@
 (60%) and testing (40%) subsets to ensure model generalisability. The RF classifier achieved
-99% accuracy on the training set and 66% on the test set.
+99% accuracy on the training set and 62% on the test set.
 
@@
 Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
-0.7, 0.57 and 0.68 respectively, indicating balanced performance across the cluster
+0.7, 0.5 and 0.65 respectively, indicating balanced performance across the cluster
 categories. Lower performance with the Medium cluster reflects the inherent difficulty of
@@
 process isolates the marginal effect of each predictor by averaging over the natural
-distribution of all other representative reef characteristics in the test dataset.
+distribution of all other representative reef characteristics in the test dataset. Additionally,
+to assess possible interaction between reef depth and incoming connectivity, two-way partial
+dependence analysis was performed on grids along the range of these two features.
 
@@
 were not consistent differences between clusters in connectivity metrics such as Log-10
-source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 total
-connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
+source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming).
 
@@
 predictor due to its categorical nature providing limited interpretable information, and is
-further justified by its low feature importance score of 10%, the lowest of all predictors
+further justified by its low feature importance score of 9%, the lowest of all predictors
 (@fig-ts-cluster-pdp; Panel A). Reef median depth and mean DHW level have the highest
-feature importance scores, accounting for 25% and 23% predictive importance respectively.
-The carrying capacity of a reef accounts for 14.3% feature importance. Connectivity strength
-and source-to-sink ratio both had feature importance scores of \~13%.
+feature importance scores, accounting for 25% and 16% predictive importance respectively.
+Weighted incoming and outgoing connectivity (Log10) features account for \~13.6% feature importance.
+The carrying capacity of a reef accounts for 12.3% feature importance. Reef source-to-sink ratio (Log10) both had feature importance scores of \~10%.
 
@@
 longevity and benefits of, for example, coral seeding activities. Across mean DHW values,
-assignment probability is roughly equal across the three clusters up to 6 DHW. A sharp
-delineation can be seen \> 6 DHW when comparing High with other clusters, with lower
+assignment probability is roughly equal across the three clusters up to 5 DHW. A sharp
+delineation can be seen \> 5 DHW when comparing High with other clusters, with lower
 assignment probability (\~25%) compared to Medium and Low (\~40%) (@fig-ts-cluster-pdp;
@@
 
-Analyses for carrying capacity, source-to-sink ratio and total connectivity strength
-indicate that their influence on its categorical assignment is concentrated at the low range
-of predictor values (@fig-ts-cluster-pdp). This aligns with the right-skewed distributions
-of values across reefs for these three predictor variables. Beyond this lower range, the
-partial dependence for these reef characteristics becomes near constant, contrary to their
+Analyses for source-to-sink ratio and weighted incoming and outgoing connectivity metrics suggest that reefs with greater outgoing connectivity and lower incoming connectivity levels have higher probability of being clustered into the Low cluster category compared to other reefs.
+Additionally, two-way analyses revealed an interaction between reef depth and incoming connectivity in determining cluster category assignment, particularly at the high depth range (@fig-ts-cluster-pdp-twoway).
+Two-way analyses revealed that reefs at greater than 10m depth are unlikely to be clustered into the Low cluster category, regardless of their incoming connectivity levels.
+However, at greater than 10m depth reefs with higher incoming connectivity are more likely to be assigned to a High cluster, while reefs with low incoming connectivity are more likely to be assigned to a Medium cover cluster (@fig-ts-cluster-pdp-twoway).
+
+Individual feature analysis for carrying capacity indicates that its influence on cluster assignment is concentrated at the low range
+of predictor values (@fig-ts-cluster-pdp). This aligns with the right-skewed distribution
+of carrying capacity across reefs for these three predictor variables. Beyond this low-end range, the
+partial dependence becomes near constant, contrary to their
 feature importance scores which suggest these characteristics do contribute important
@@
 Assessing random forest prediction accuracy across predictor values, summarised by
-bioregions, reveals increasing performance as bioregion mean reef depth and carrying
-capacity increase (@sfig-rf-predictor-perf). This highlights where there is unexplained
-variation between reefs that contributes to cluster assignment and reef cover outcomes but
+bioregions, reveals increasing performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf). This highlights that there may be unexplained
+variation between reefs in shallow bioregions that contributes to cluster assignment and reef cover outcomes but
 is not captured by our included predictor variables.
@@
 Probability values for each cluster are generated by the random forest classifier using each combination of depth and incoming connectivity values along the axes at 50 grid points.
-The actual distributions of depth and incoming connectivity values are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_conn_pdp.png){#fig-ts-cluster-pdp-twoway fig-align="center"
+The actual distributions of depth and incoming connectivity values for reefs are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_conn_pdp.png){#fig-ts-cluster-pdp-twoway fig-align="center"
 width="14.82cm"}
@@
 coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
-that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate).
+that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate; @sfig-access-esm1-5-mean-carb-budget).
 Unsurprisingly, the number of years above $\theta_0$ substantially decreased as $\theta_0$
@@
 results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
-reefs), 62% (1082) of reefs fall into the low and medium clusters (across all GCMs at the
+reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the
 GBRMPA management region scale), with many unable to maintain positive carbonate budgets
@@
 where the probability of a reef being clustered into the High cover cluster increased
-substatially. Considering this 10-15m depth range when assessing possible restoration sites
+substatially.
+Additionally, two-way partial dependence analysis revealed that high incoming connectivity is important for High cluster assignment for reefs at depths of \>10m.
+Considering this 10-15m depth range, and targetting well connected reefs, when assessing possible restoration sites
 may reduce the exposure of planted and seeded corals to high thermal stress, while still
-maintaining effective logistical access to sites. Reef intervention planning is a complex
+maintaining effective logistical access to sites.
+Although transient, and difficult to measure, properties such as reef connectivity are likely to increase uncertainty in intervention planning to a greater degree than environmental characteristics such as reef depth.
+Reef intervention planning is a complex
 and challenging decision-making process [@anthony2020], and our results suggest that
@@
 importance, there are few differences between resilient and non-resilient reefs in metrics
-such as source-to-sink connectivity ratio and total connectivity strength. Furthermore, our
+such as source-to-sink connectivity ratio and total connectivity strength.
+While there is interaction between incoming connectivity and depth in reef cluster prediction, according to available input data, there are few reefs in the GBR that occur at depths \>10m and have Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget), resulting in low importance of connectivity as an individual feature for clustering across the GBR.
+Furthermore, our
 results suggest no relationship between connectivity strength and the ability of reefs to
@@
 generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and
-1996-2002 [@bode2018] time periods. Using updated 1km^2^ resolution larval connectivity
+1996-2002 [@bode2018] time periods, without considering the influence of reef depth on resilience. Using updated 1km^2^ resolution larval connectivity
 across the whole GBR, with a limited temporal sample of particle flows, our results suggest
-that larval connectivity alone is not as important for reef resilience and recovery as
-environmental refugia such as depth.
+that larval connectivity alone may not be important or reef resilience and recovery, but should be considered in combination with more influential factors such as depth.
 
@@
 [@hock2017; @torres2024]. Further improvements and research in connectivity modelling are
-necessary to provide a robust comparison of all factors influencing reef resilience.
+necessary when incorporating connectivity as a supplementary factor in reef resilience and intervention-planning analyses.
 
@@
 
-![Total connectivity strength (in base-10 log scale) for reefs within each bioregion,
+![Weighted incoming connectivity (in base-10 log scale) for reefs within each bioregion,
 separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
@@
 the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median base-10 log of total connectivity strength for
-each cluster and bands represent the distribution of connectivity strength values within
+lines within each violin represent the median base-10 log of weighted incoming connectivity for
+each cluster and bands represent the distribution of connectivity values within
 each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/log_total_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-totalconnectivity
-fig-align="center" width="14.82cm"}
+GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_incoming_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedincoming
+fig-align="center" width="14.82cm"}

### 2025-08-25 src/ADRIA/HighResCoralStress/7_rf_analysis.jl

@@ -129,7 +129,7 @@ cluster_est = MLJ.predict(mach, test_X)
 y_pred_mode = predict_mode(mach, test_X)
 
 μ_accuracy = mean(y_pred_mode .== test_y)
-@info μ_accuracy  # 0.66
+@info μ_accuracy  # 0.62
 
 cm = confusion_matrix(y_pred_mode, test_y)
 cm.mat
@@ -173,16 +173,17 @@ end
 
 cv = CV(nfolds=3, rng=123)
 evaluate!(mach, resampling=cv, measure=[MLJ.accuracy, MLJ.cross_entropy])
-# Accuracy: 0.669
-# LogLoss: 0.751
+# Accuracy: 0.606
+# LogLoss: 0.853
 
 feat_imports = feature_importances(mach)
-#       :depth_med => 0.2516920696138505
-#        :mean_dhw => 0.24192024951943078
-#      :abs_k_area => 0.14411108965272595
-#  :total_strength => 0.13292360681207943
-#        :so_to_si => 0.12930894620395628
-#       :bioregion => 0.10004403819795683
+#               :depth_med => 0.23860533087232372
+#                :mean_dhw => 0.16479623325258205
+#  :weighted_incoming_conn => 0.136410744763997
+#  :weighted_outgoing_conn => 0.1362327788209799
+#              :abs_k_area => 0.12357937667819203
+#            :log_so_to_si => 0.1069541180323328
+#               :bioregion => 0.09342141757959256
 # The precise values of the above are subject to change but the order of features is
 # robust.
 

### 2025-08-25 paper/paper_draft.qmd
Add caveat around not including the influence of light/depth on growth
Something in this commit seems to have broken the VSCode visual editor line wrapping setting

@@
     maintenance of positive carbonate budgets, with deeper reefs benefiting from thermal
-    refugia that reduce bleaching impacts. Our findings suggest that depth provides critical
+    refugia that reduce bleaching impacts. Interaction between reef depth and incoming connectivity was found to influence reef temporal behaviour. Our findings suggest that depth provides critical
     protection against thermal stress, contrasting current restoration practices that primarily
@@
 
-Climate change is impacting species survival, persistence and ecosystem functions globally,
-including coral reefs. Coral reefs are vulnerable to increasing magnitude and variation in
-environmental stressors such as ocean temperature, acidification and nutrient loading
-[@foster2021; @gattuso2014]. Mass bleaching and mortality events linked to climate change
-can cause reef-building coral population declines, possibly leading to long-term and
-large-scale coral-macroalgae regime shifts [@arif2022; @wild2011]. Climate impacts on coral
-reefs are, and will continue to, decrease the ability of coral reefs to provide ecological
-functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well
-as ecosystem services such as food, protection, tourism and Indigenous cultural value
-[@eddy2021; @stoeckl2021].
+Climate change is impacting species survival, persistence and ecosystem functions globally, including coral reefs.
+Coral reefs are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading [@foster2021; @gattuso2014].
+Mass bleaching and mortality events linked to climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
+Climate impacts on coral reefs are, and will continue to, decrease the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well as ecosystem services such as food, protection, tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
 
-Understanding the characteristics of reefs that will persist under projected climate
-conditions requires examining reef resilience across multiple scales and processes.
-Structural resilience - the capacity to maintain coral populations and avoid ecosystem
-regime shifts - depends on three interconnected mechanisms. First, the ability of individual
-corals to survive thermal stress. Second, the connectivity networks that enable
-recolonisation after disturbances. Third, the maintenance of the carbonate framework that
-provides reef structure. We aim to assess how these mechanisms interact under projected
-climate conditions to identify the characteristics of structurally resilient reefs through
-scenario-based coral population modelling for the Great Barrier Reef ecosystem.
+Understanding the characteristics of reefs that will persist under projected climate conditions requires examining reef resilience across multiple scales and processes.
+Structural resilience - the capacity to maintain coral populations and avoid ecosystem regime shifts - depends on three interconnected mechanisms.
+First, the ability of individual corals to survive thermal stress.
+Second, the connectivity networks that enable recolonisation after disturbances.
+Third, the maintenance of the carbonate framework that provides reef structure.
+We aim to assess how these mechanisms interact under projected climate conditions to identify the characteristics of structurally resilient reefs through scenario-based coral population modelling for the Great Barrier Reef ecosystem.
 
-The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of
-thousands of individual reefs. They are interconnected through coral and fish larval
-dispersal patterns mediated by hydrodynamic, spatial, and ecological processes
-[@grimaldi2022]. The GBR faces severe projected coral cover declines under climate change
-[@bozec2025; @bozec2022]. These coral cover declines will be compounded by ocean
-acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks
-[@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24
-Summer mass bleaching event may be signalling a shift towards this reef future, with some
-level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
-[@cantin2024].
+The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of thousands of individual reefs.
+They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@grimaldi2022].
+The GBR faces severe projected coral cover declines under climate change [@bozec2025; @bozec2022].
+These coral cover declines will be compounded by ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
+The 2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs) [@cantin2024].
 
-At the individual coral scale, survival during thermal stress events depends on both
-environmental and biological factors. Environmental factors can either amplify or reduce
-thermal stress exposure. Depth has been suggested as one crucial factor that can provide a
-refuge from thermal stress [@álvarez-noriega2018; @baird2018; @smith2014]. Biological
-factors including coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005],
-and thermal tolerance through acclimation and inheritance [@humanes2022; @lachs2024] all
-influence survival outcomes. Importantly, corals demonstrate adaptive capacity to develop
-thermal tolerance that could delay widespread bleaching under moderate emission scenarios
-[@bairos-novak2021; @humanes2022], representing a crucial mechanism for reef persistence.
+At the individual coral scale, survival during thermal stress events depends on both environmental and biological factors.
+Environmental factors can either amplify or reduce thermal stress exposure.
+Depth has been suggested as one crucial factor that can provide a refuge from thermal stress [@álvarez-noriega2018; @baird2018; @smith2014].
+Biological factors including coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and thermal tolerance through acclimation and inheritance [@humanes2022; @lachs2024] all influence survival outcomes.
+Importantly, corals demonstrate adaptive capacity to develop thermal tolerance that could delay widespread bleaching under moderate emission scenarios [@bairos-novak2021; @humanes2022], representing a crucial mechanism for reef persistence.
 
-Beyond individual survival, reef-scale resilience depends on connectivity networks that
-enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017]. However,
-connectivity creates both strengths and vulnerabilities. Larval source populations that
-export more larvae than they import are essential for system-wide recovery, providing larvae
-that enable recolonization at distant locations [@hock2017; @thomas2015]. Yet these source
-reefs are paradoxically more vulnerable individually, relying heavily on local recruitment
-for their own recovery. When disturbances impact major source populations, cascading effects
-reduce larval export and slow recovery throughout the connected network [@figueiredo2022;
-@hock2017; @munday2009].
+Beyond individual survival, reef-scale resilience depends on connectivity networks that enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017].
+However, connectivity creates both strengths and vulnerabilities.
+Larval source populations that export more larvae than they import are essential for system-wide recovery, providing larvae that enable recolonization at distant locations [@hock2017; @thomas2015].
+Yet these source reefs are paradoxically more vulnerable individually, relying heavily on local recruitment for their own recovery.
+When disturbances impact major source populations, cascading effects reduce larval export and slow recovery throughout the connected network [@figueiredo2022; @hock2017; @munday2009].
 
-Long-term reef viability requires not only coral survival and recolonization, but also
-maintenance of the physical reef structure through positive carbonate budgets. Scleractinian
-corals build the primary habitat framework, but reef persistence depends on the balance
-between carbonate accumulation [@perry2015] and loss through bioerosion, physical damage
-[@kenyon2023], and dissolution [@eyre2014; @eyre2018]. This balance is influenced by coral
-cover and community complexity [@perry2012; @desbiens2021], environmental processes, and
-ocean chemistry [@perry2015; @eyre2018]. For GBR mid-shelf and offshore reefs, maintaining
-positive carbonate budgets requires approximately 17% live coral cover [@desbiens2021].
+Long-term reef viability requires not only coral survival and recolonization, but also maintenance of the physical reef structure through positive carbonate budgets.
+Scleractinian corals build the primary habitat framework, but reef persistence depends on the balance between carbonate accumulation [@perry2015] and loss through bioerosion, physical damage [@kenyon2023], and dissolution [@eyre2014; @eyre2018].
+This balance is influenced by coral cover and community complexity [@perry2012; @desbiens2021], environmental processes, and ocean chemistry [@perry2015; @eyre2018].
+For GBR mid-shelf and offshore reefs, maintaining positive carbonate budgets requires approximately 17% live coral cover [@desbiens2021].
 
-Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response
-research enable integrated investigation of how these multiple factors interact to determine
-climate resilience. By incorporating the latest coral population models
-[@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections
-[@dixon2022], we can examine which factors most strongly influence reef persistence under
-different scenarios. While connectivity has been emphasized as critical for GBR resilience
-[@hock2017], and remains an important consideration, our integrated modelling reveals depth
-may play a fundamental role in determining maintenance of reef coral populations and
-positive carbonate budgets under current projections of climate change.
+Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response research enable integrated investigation of how these multiple factors interact to determine climate resilience.
+By incorporating the latest coral population models [@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections [@dixon2022], we can examine which factors most strongly influence reef persistence under different scenarios.
+While connectivity has been emphasized as critical for GBR resilience [@hock2017], and remains an important consideration, our integrated modelling reveals depth may play a fundamental role in determining maintenance of reef coral populations and positive carbonate budgets under current projections of climate change.
 
@@
 
-The spatial extent of the GBR reefs represented in this investigation follows the reef
-definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
-[@GBRMPA2022]. The reef definitions define 3806 reefs across the GBR. An indicative map of
-the GBR marine park including the Marine Park Management areas [@GBRMPA2007] and the
-corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
-Estimates of coral carrying capacity for each reef were taken from prior analyses undertaken
-in [@bozec2022].
+The spatial extent of the GBR reefs represented in this investigation follows the reef definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA) [@GBRMPA2022].
+The reef definitions define 3806 reefs across the GBR.
+An indicative map of the GBR marine park including the Marine Park Management areas [@GBRMPA2007] and the corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
+Estimates of coral carrying capacity for each reef were taken from prior analyses undertaken in [@bozec2022].
 
-Depth characteristics for each reef were extracted using 10m resolution bathymetry data made
-available in GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched
-with the 3806 reef outlines through geometric intersections. All depth values were converted
-to positive values (depths below sea level). The median depth was used to provide an
-indicative depth value for each reef. Code, and the resulting depth estimates, are available
-at **\[cite Canonical Reefs repo\]**.
+Depth characteristics for each reef were extracted using 10m resolution bathymetry data made available in GBRMPA [-@GBRMPA2020].
+For each reef, bathymetry data were spatially matched with the 3806 reef outlines through geometric intersections.
+All depth values were converted to positive values (depths below sea level).
+The median depth was used to provide an indicative depth value for each reef.
+Code, and the resulting depth estimates, are available at **\[cite Canonical Reefs repo\]**.
 
-While the bathymetry data adopted for the given assessment are said to be accurate up to 15m
-from Mean Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth
-estimates used for this study. These are outlined further in the Discussion. Notably, the
-adopted depth estimates were derived from bathymetries based on satellite imagery. The
-bathymetry data can be limited in their alignment with the established GBRMPA reef outlines
-used to characterise reef locations and their areal extent. A Quality Assessment and Control
-process identified reefs with potential data limitations: reefs with no overlapping
-bathymetry data, reefs with minimum depth values above sea level (indicating potential data
-artifacts), and reefs where bathymetry pixels covered less than 5% of the reef polygon area.
-This process removed 842 reefs, or 22%, from the initial set of 3806 reefs. Furthermore,
-reefs that are not associated with GBRMPA Management areas [@GBRMPA2007] or reefal
-bioregions [@GBRMPA2024] were also removed from the investigation. Bioregions which
-contained fewer than three reefs after these processes were also excluded. As a result, 1377
-reefs were excluded (36%), leaving a total of 2429 remaining for the purpose of this
-investigation.
+While the bathymetry data adopted for the given assessment are said to be accurate up to 15m from Mean Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for this study.
+These are outlined further in the Discussion.
+Notably, the adopted depth estimates were derived from bathymetries based on satellite imagery.
+The bathymetry data can be limited in their alignment with the established GBRMPA reef outlines used to characterise reef locations and their areal extent.
+A Quality Assessment and Control process identified reefs with potential data limitations: reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level (indicating potential data artifacts), and reefs where bathymetry pixels covered less than 5% of the reef polygon area.
+This process removed 842 reefs, or 22%, from the initial set of 3806 reefs.
+Furthermore, reefs that are not associated with GBRMPA Management areas [@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed from the investigation.
+Bioregions which contained fewer than three reefs after these processes were also excluded.
+As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for the purpose of this investigation.
 
-![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all
-considered reefs (points). Colour-coded polygons outline GBR marine park management regions,
-where orange represents the Far Northern management region, green represents
-Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
-[@GBRMPA2007]. Reef centroids are marked individually for visual clarity and are coloured
-according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
-represented in this figure. Annotations represent major coastal settlements along the
-GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
+![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all considered reefs (points).
+Colour-coded polygons outline GBR marine park management regions, where orange represents the Far Northern management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007].
+Reef centroids are marked individually for visual clarity and are coloured according to its bioregion [@GBRMPA2024].
+All 2429 reefs included in this investigation are represented in this figure.
+Annotations represent major coastal settlements along the GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
 
@@
 
-Future projections of maximum yearly Degree Heating Weeks (DHWs) for each reef were
-estimated from Sea Surface Temperature (SST) data for the GBR. Statistically downscaled
-1km^2^ resolution SST data for five Global Climate Models (GCMs) were obtained from the
-HighResCoralStress database [@dixon2022; @dixon2023]. These five GCMs were EC-Earth3-Veg,
-ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4. The selected GCMs are a part of the
-Sixth Phase of the Coupled Model Intercomparison Project (CMIP6), spanning four 'model
-development families' as defined by Brunner et al., [-@brunner2020].
+Future projections of maximum yearly Degree Heating Weeks (DHWs) for each reef were estimated from Sea Surface Temperature (SST) data for the GBR.
+Statistically downscaled 1km^2^ resolution SST data for five Global Climate Models (GCMs) were obtained from the HighResCoralStress database [@dixon2022; @dixon2023].
+These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4.
+The selected GCMs are a part of the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6), spanning four 'model development families' as defined by Brunner et al., [-@brunner2020].
 
-These GCMs were selected based on evaluation conducted by Grose et al., [-@grose2023],
-indicating their ability to recreate historical atmospheric temperature and precipitation
-conditions in the Australasian region. They span a range of Equilibrium Climate Sensitivity
-(ECS) values within the Intergovernmental Panel on Climate Change (IPCC) assessed likely
-range. The IPCC defines ECS as the long-term warming caused by a doubling of carbon dioxide
-above its pre-industrial concentration [@forster2021]. While this assessment does not
-consider oceanic data, Grose et al. [-@grose2023] provide a region-specific selection
-mechanism which we use as an indicator of general performance of GCMs for the region. An
-overview of the selected GCMs is provided in @tbl-gcms. Note here that Grose et al.,
-[-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides
-data based on GFDL-CM4. This substitution is assumed appropriate given they share the same
-fundamental representation of the physical climate system.
+These GCMs were selected based on evaluation conducted by Grose et al., [-@grose2023], indicating their ability to recreate historical atmospheric temperature and precipitation conditions in the Australasian region.
+They span a range of Equilibrium Climate Sensitivity (ECS) values within the Intergovernmental Panel on Climate Change (IPCC) assessed likely range.
+The IPCC defines ECS as the long-term warming caused by a doubling of carbon dioxide above its pre-industrial concentration [@forster2021].
+While this assessment does not consider oceanic data, Grose et al.
+[-@grose2023] provide a region-specific selection mechanism which we use as an indicator of general performance of GCMs for the region.
+An overview of the selected GCMs is provided in @tbl-gcms.
+Note here that Grose et al., [-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides data based on GFDL-CM4.
+This substitution is assumed appropriate given they share the same fundamental representation of the physical climate system.
 
-Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission
-pathway. It represents a moderate emissions scenario with continued CO~2~ emissions
-comparable to present day until 2050, after which emissions gradually decline
-[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.66°C of global
-atmospheric warming in the 2081-2100 period relative to 1850-1900. The use of these GCMs
-therefore allow for a range of possible climate futures to be explored, capturing
-uncertainty in future responses to CO~2~ increases (@sfig-ecs; @fig-methods-dhws;
-[@grose2023; @shepherd2018]) and enables the assessment of modelled coral reef behaviour
-over a broad range of independently derived climate futures [@abramowitz2019].
+Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission pathway.
+It represents a moderate emissions scenario with continued CO~2~ emissions comparable to present day until 2050, after which emissions gradually decline [@hausfather2020; IPCC -@climate2023].
+The selected GCMs represent 2.5°C to 4.66°C of global atmospheric warming in the 2081-2100 period relative to 1850-1900.
+The use of these GCMs therefore allow for a range of possible climate futures to be explored, capturing uncertainty in future responses to CO~2~ increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]) and enables the assessment of modelled coral reef behaviour over a broad range of independently derived climate futures [@abramowitz2019].
 
-Monthly mean SST climatological baselines, for each 1km^2^ pixel, were calculated from the
-daily SST data following NOAA methodology [@liu2017; @skirving2020]. For each pixel of SST
-data, the Monthly Mean SST climatology was calculated by computing the mean SST value for
-each calendar month (January through December) across the 28-year baseline period from 1985
-to 2012. For each month separately, this climatological baseline was adjusted to centre at
-year 1988.2857, which attempts to account for any long-term trends within the baseline years
-themselves (see Skirving et al. [@skirving2020]). The adjustment ensures that the
-climatology represents conditions at a specific temporal reference point rather than being
-influenced by gradual warming or cooling trends that may have occurred during the 1985-2012
-period. The resulting monthly climatologies serve as a standardized reference against which
-current SST conditions can be compared to identify thermal anomalies and assess coral
-bleaching risk, following the methodology established by Skirving et al. [-@skirving2020].
+Monthly mean SST climatological baselines, for each 1km^2^ pixel, were calculated from the daily SST data following NOAA methodology [@liu2017; @skirving2020].
+For each pixel of SST data, the Monthly Mean SST climatology was calculated by computing the mean SST value for each calendar month (January through December) across the 28-year baseline period from 1985 to 2012.
+For each month separately, this climatological baseline was adjusted to centre at year 1988.2857, which attempts to account for any long-term trends within the baseline years themselves (see Skirving et al.
+[@skirving2020]).
+The adjustment ensures that the climatology represents conditions at a specific temporal reference point rather than being influenced by gradual warming or cooling trends that may have occurred during the 1985-2012 period.
+The resulting monthly climatologies serve as a standardized reference against which current SST conditions can be compared to identify thermal anomalies and assess coral bleaching risk, following the methodology established by Skirving et al.
+[-@skirving2020].
 
-Degree Heating Weeks (DHWs) were derived using the "HotSpot SST Anomaly" approach
-[@skirving2020]. The "HotSpot SST Anomaly" represents thermal stress experienced by coral
-reefs and is calculated as the difference between daily SST values and the maximum of a
-pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean
-SST). This approach uses the annual maximum temperature as the baseline because corals are
-adapted to withstand their local warmest conditions under normal seasonal cycles. When
-temperatures exceed this seasonal maximum, corals experience thermal stress that can lead to
-bleaching. Only positive anomalies, greater than 1°C, are considered relevant for coral
-stress, as temperatures below the seasonal maximum do not contribute to bleaching risk.
+Degree Heating Weeks (DHWs) were derived using the "HotSpot SST Anomaly" approach [@skirving2020].
+The "HotSpot SST Anomaly" represents thermal stress experienced by coral reefs and is calculated as the difference between daily SST values and the maximum of a pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean SST).
+This approach uses the annual maximum temperature as the baseline because corals are adapted to withstand their local warmest conditions under normal seasonal cycles.
+When temperatures exceed this seasonal maximum, corals experience thermal stress that can lead to bleaching.
+Only positive anomalies, greater than 1°C, are considered relevant for coral stress, as temperatures below the seasonal maximum do not contribute to bleaching risk.
 
-DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week
-rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in units of
-°C-weeks. The 12-week accumulation period reflects the cumulative nature of coral thermal
-stress. Brief temperature spikes may be tolerable, but sustained or repeated exposure to
-elevated temperatures causes progressively greater physiological stress and bleaching
-severity. DHW values integrate both the magnitude and duration of thermal stress: a moderate
-anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly
-(e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for
-each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for
-all pixels touching each reef outline. The process described here was conducted for all 2429
-reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
-and perform analyses involved in this investigation can be found at Grier and Iwanaga
-[-@grier2025].
+DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in units of °C-weeks.
+The 12-week accumulation period reflects the cumulative nature of coral thermal stress.
+Brief temperature spikes may be tolerable, but sustained or repeated exposure to elevated temperatures causes progressively greater physiological stress and bleaching severity.
+DHW values integrate both the magnitude and duration of thermal stress: a moderate anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly (e.g., 3°C) lasting 4 weeks, though the biological impacts may differ.
+DHW estimates for each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for all pixels touching each reef outline.
+The process described here was conducted for all 2429 reefs to create DHW projections spanning from 2025 to 2075.
+Code used to calculate DHW data and perform analyses involved in this investigation can be found at Grier and Iwanaga [-@grier2025].
 
 | Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
-|-----------------------|-----------------------|------------------------|-----------------------|
+|------------------|------------------|-------------------|------------------|
 | ACCESS-CM2 | 4.66 [@grose2023] | High | [@grier2025] |
@@
 
-: Information for each GCM used in this investigation including Equilibrium Climate
-Sensitivity (ECS) value, interpreted relative severity and where results for an individual
-GCM results are found. GCMs in context with assessed plausible ranges of ECS values are
-displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the
-very-likely ECS range and was taken as an intermediate model with results displayed in the
-main text. {#tbl-gcms}
+: Information for each GCM used in this investigation including Equilibrium Climate Sensitivity (ECS) value, interpreted relative severity and where results for an individual GCM results are found.
+GCMs in context with assessed plausible ranges of ECS values are displayed in [@sfig-ecs].
+ACCESS-ESM1-5 has an ECS closest to the midpoint of the very-likely ECS range and was taken as an intermediate model with results displayed in the main text.
+{#tbl-gcms}
 
-![Degree Heating Week time series (in °C - Weeks) for the GCMs selected. Colours represent
-the different Management areas across the Great Barrier Reef. Green represents
-Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
-represents the Townsville-Whitsunday Management area. Solid lines represent the
-management-area median time series and bands represent the 95th percentile confidence
-intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws fig-align="center"
-width="14.82cm"}
+![Degree Heating Week time series (in °C - Weeks) for the GCMs selected.
+Colours represent the different Management areas across the Great Barrier Reef.
+Green represents Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red represents the Townsville-Whitsunday Management area.
+Solid lines represent the management-area median time series and bands represent the 95th percentile confidence intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws fig-align="center" width="14.82cm"}
 
@@
 
-An exploratory scenario modelling approach was adopted for this investigation. The method
-involves exploring a wide range of plausible futures under different assumptions of
-environmental (climatic) conditions and ecological factors. Exploratory scenario modelling
-embraces uncertainty as an inherent characteristic of complex environmental systems
-[@lempert2010] and is a core methodology underpinning the development of robust and adaptive
-management strategies [@haasnoot2013].
+An exploratory scenario modelling approach was adopted for this investigation.
+The method involves exploring a wide range of plausible futures under different assumptions of environmental (climatic) conditions and ecological factors.
+Exploratory scenario modelling embraces uncertainty as an inherent characteristic of complex environmental systems [@lempert2010] and is a core methodology underpinning the development of robust and adaptive management strategies [@haasnoot2013].
 
-Exploratory modelling approaches have gained favour in recent years as precise long-term
-predictions of future conditions are often impossible in complex systems like coral reefs.
-Multiple interacting and compounding sources of uncertainty, and a lack of broad agreement
-as to their likelihood, create inherently uncertain outcomes. Rather than attempting to
-forecast specific outcomes, exploratory modelling aims to systematically explore many
-possible futures to identify patterns. Allowing for the identification of robust management
-strategies that perform well across those diverse conditions, as well as conditions in which
-such strategies may fail. Such an exploratory approach lends itself well to the purpose of
-the investigation. Specifically, to assess the role of thermal stress, connectivity, and
-depth to identify the environmental and reef characteristics that support structural
-resilience.
+Exploratory modelling approaches have gained favour in recent years as precise long-term predictions of future conditions are often impossible in complex systems like coral reefs.
+Multiple interacting and compounding sources of uncertainty, and a lack of broad agreement as to their likelihood, create inherently uncertain outcomes.
+Rather than attempting to forecast specific outcomes, exploratory modelling aims to systematically explore many possible futures to identify patterns.
+Allowing for the identification of robust management strategies that perform well across those diverse conditions, as well as conditions in which such strategies may fail.
+Such an exploratory approach lends itself well to the purpose of the investigation.
+Specifically, to assess the role of thermal stress, connectivity, and depth to identify the environmental and reef characteristics that support structural resilience.
 
@@
 
-To apply exploratory scenario modelling, we employed a modelling framework involving two
-separate systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and
-CoralBlox. ADRIA is a multi-criteria decision support platform designed to help reef
-managers address climate change challenges in coral reef systems [@iwanaga2023]. The ADRIA
-platform provides functionality for scenario generation and analysis as well as providing
-the technical infrastructure to couple environmental and ecosystem representations.
-CoralBlox is a computationally efficient coral population model. It simulates
-functional/morphological groups of corals over their life cycles, competing for available
-space over time [@ribeirodealmeida2024]. The coupled framework is referred to as
-ADRIA-CoralBlox.
+To apply exploratory scenario modelling, we employed a modelling framework involving two separate systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and CoralBlox.
+ADRIA is a multi-criteria decision support platform designed to help reef managers address climate change challenges in coral reef systems [@iwanaga2023].
+The ADRIA platform provides functionality for scenario generation and analysis as well as providing the technical infrastructure to couple environmental and ecosystem representations.
+CoralBlox is a computationally efficient coral population model.
+It simulates functional/morphological groups of corals over their life cycles, competing for available space over time [@ribeirodealmeida2024].
+The coupled framework is referred to as ADRIA-CoralBlox.
 
-The coral demographic representation and associated model implementation are further
-detailed in the supplementary material. Of important note, however, is that the
-representation of bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a
-scaling coefficient to incorporate the amelioration effect that depth may have, following
-Baird et al., [@baird2018]. This depth-scaling reduces the proportion of coral colonies
-impacted by high heat stress as depth increases. The impacts of tropical cyclones and wave
-activity on reefs were not included in this investigation.
+The coral demographic representation and associated model implementation are further detailed in the supplementary material.
+Of important note, however, is that the representation of bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient to incorporate the amelioration effect that depth may have, following Baird et al., [@baird2018].
+This depth-scaling reduces the proportion of coral colonies impacted by high heat stress as depth increases.
+The impacts of tropical cyclones and wave activity on reefs were not included in this investigation.
 
-ADRIA-CoralBlox was run for 4096 scenarios for each GCM (20,480 total model runs). Here, a
-scenario represents a unique combination of assumed environmental (namely one of the five
-DHW trajectories) and ecological factors including coral growth and mortality rates, and
-coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol' sampling
-method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi Monte Carlo
-approach which balances scenario exploration with improved convergence properties compared
-to pseudo-random sampling. A detailed comparative analysis of the sampling methods can be
-found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
-cover time series for each model run were scaled by the total area of each reef to represent
-cover as a percentage of the total estimated reef area. The scenario-median timeseries for
-each reef was used for further analyses. These time series of coral cover were then
-clustered based on their temporal behaviour.
+ADRIA-CoralBlox was run for 4096 scenarios for each GCM (20,480 total model runs).
+Here, a scenario represents a unique combination of assumed environmental (namely one of the five DHW trajectories) and ecological factors including coral growth and mortality rates, and coral thermal tolerances.
+Scenarios were generated using the low-discrepancy Sobol' sampling method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi Monte Carlo approach which balances scenario exploration with improved convergence properties compared to pseudo-random sampling.
+A detailed comparative analysis of the sampling methods can be found in [@kucherenko2015].
+For the purpose of scenario assessment, the resulting coral cover time series for each model run were scaled by the total area of each reef to represent cover as a percentage of the total estimated reef area.
+The scenario-median timeseries for each reef was used for further analyses.
+These time series of coral cover were then clustered based on their temporal behaviour.
 
@@
 
-Connectivity data from 24 days in total were used in this investigation to estimate coral
-larval flows. These data span six years from 2015 to 2020. The years 2015, 2016, 2018 and
-2019 are each represented by connectivity matrices covering spawning periods over three days
-in each year (12 days in total), while 2017 and 2020 are each represented by six spawning
-days each, coming to a total of 24 days of connectivity matrices.
+Connectivity data from 24 days in total were used in this investigation to estimate coral larval flows.
+These data span six years from 2015 to 2020.
+The years 2015, 2016, 2018 and 2019 are each represented by connectivity matrices covering spawning periods over three days in each year (12 days in total), while 2017 and 2020 are each represented by six spawning days each, coming to a total of 24 days of connectivity matrices.
 The values in these matrices indicate the probability of larval transfer between each pair of reefs in the GBR, herein referred to as connectivity strengths.
-Indicative connectivity
-strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each
-location (i.e., mean of all 24 spawning days). While the connectivity strengths do not vary
-from year to year within each ADRIA-CoralBlox simulation, they do vary between reefs which
-are of varying sizes, providing sufficient heterogeneity to capture spatial patterns in
-larval dispersal and settlement dynamics. This spatial variability also enables
-investigations into the influence of connectivity strength and its role in driving recovery
-processes.
+Indicative connectivity strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each location (i.e., mean of all 24 spawning days).
+While the connectivity strengths do not vary from year to year within each ADRIA-CoralBlox simulation, they do vary between reefs which are of varying sizes, providing sufficient heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics.
+This spatial variability also enables investigations into the influence of connectivity strength and its role in driving recovery processes.
 
-To assess the impact of reef connectivity on modelled outcomes we summarise inter-reef
-connections using weighted connectivity metrics (incoming and outgoing) and the ratio of source-to-sink
-connectivity for each reef.
+To assess the impact of reef connectivity on modelled outcomes we summarise inter-reef connections using weighted connectivity metrics (incoming and outgoing) and the ratio of source-to-sink connectivity for each reef.
 Weighted incoming connectivity is calculated by summing the product of each connection strength incoming to a target reef and the mean timeseries absolute coral cover (km^2^) of each matching source reef.
@@
 A limitation of these weighted connectivity metrics is that they do not incorporate the proportion of the source reef's population that is reproducing and producing larvae, instead taking the total coral cover area as an indicator of larval productivity.
-The ratio of source-to-sink connectivity ($O:I$) for a target
-reef represents the strength of the reef's outgoing larval flow relative to it's incoming
-larval flow.
+The ratio of source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's outgoing larval flow relative to it's incoming larval flow.
 This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$.
@@
 If a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value.
-Incoming connections in this calculation, do not directly represent the
-larval supply gained as the breeding populations from which connections are coming from are not
-represented. A source-to-sink ratio greater than 1 (a value greater than 0 on a log scale)
-indicates a reef has greater outgoing than incoming larval flow.
+Incoming connections in this calculation, do not directly represent the larval supply gained as the breeding populations from which connections are coming from are not represented.
+A source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming larval flow.
 
@@
 
-Reefs were clustered into three qualitative categories based on their temporal behaviour
-indicated by coral cover over time. The three categories were Low, Medium, and High,
-indicating their relative ability to maintain coral cover and thus their structural
-resilience. The Complexity-Invariant Distance (CID) between each time series was calculated
-to identify similarities in temporal behaviour [@batista2014]. The CID applies a correction
-factor to the Euclidean distance between pairs of time series to obtain a measure of their
-similarity or dissimilarity. The adopted approach ensures reefs are clustered based on their
-temporal dynamics as opposed to, for example, naively clustering by their mean coral cover.
+Reefs were clustered into three qualitative categories based on their temporal behaviour indicated by coral cover over time.
+The three categories were Low, Medium, and High, indicating their relative ability to maintain coral cover and thus their structural resilience.
+The Complexity-Invariant Distance (CID) between each time series was calculated to identify similarities in temporal behaviour [@batista2014].
+The CID applies a correction factor to the Euclidean distance between pairs of time series to obtain a measure of their similarity or dissimilarity.
+The adopted approach ensures reefs are clustered based on their temporal dynamics as opposed to, for example, naively clustering by their mean coral cover.
 Clustering similar time series is achieved through the use of k-medoids clustering [cf.
-@steinmann2020]. Further details on the time series clustering approach are found in the
-supplementary materials.
+@steinmann2020].
+Further details on the time series clustering approach are found in the supplementary materials.
 
-The time series clustering was applied over the time frame between 2025 and 2075. Spatially,
-the clustering analyses were conducted for each GBR management area and at the scale of each
-reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
-whole-of-GBR scale but were found to lead to identical conclusions about characteristics
-influencing cluster cover compared to management area and bioregion scale analyses and so
-are not shown here. To compare time series clustering results across GCMs, management area
-scale clustering results are used to preserve coarse scale latitudinal differences between
-regions, while maintaining ease of comparison and visualisation. These comparisons include
-quantification of differences between low and high cover clusters across management regions
-under each GCM using the CID between cluster median time series. To assess how different
-reef characteristics influence time series clustering at a finer spatial scale, bioregion
-results are used to capture patterns occurring within individual groups of reefs. Results of
-all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for
-those interested.
+The time series clustering was applied over the time frame between 2025 and 2075.
+Spatially, the clustering analyses were conducted for each GBR management area and at the scale of each reefal bioregion (defined in GBRMPA [-@GBRMPA2024]).
+Analyses were also performed at the whole-of-GBR scale but were found to lead to identical conclusions about characteristics influencing cluster cover compared to management area and bioregion scale analyses and so are not shown here.
+To compare time series clustering results across GCMs, management area scale clustering results are used to preserve coarse scale latitudinal differences between regions, while maintaining ease of comparison and visualisation.
+These comparisons include quantification of differences between low and high cover clusters across management regions under each GCM using the CID between cluster median time series.
+To assess how different reef characteristics influence time series clustering at a finer spatial scale, bioregion results are used to capture patterns occurring within individual groups of reefs.
+Results of all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for those interested.
 
-Reefs in each time series cluster were compared to identify characteristics that differ
-between Low, Medium and High clusters. These characteristics include reef median depth,
-mean time series DHW, Pearson’s correlation between total coral cover and inverse DHW time
-series, proportion of coral habitable area occupied by corals in the first timestep, ratio
-of source-to-sink larval connectivity and weighted incoming connectivity.
+Reefs in each time series cluster were compared to identify characteristics that differ between Low, Medium and High clusters.
+These characteristics include reef median depth, mean time series DHW, Pearson’s correlation between total coral cover and inverse DHW time series, proportion of coral habitable area occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and weighted incoming connectivity.
 
@@
 
-Partial Dependence Analysis was conducted to understand the relationship between features and bioregion-scale time series cluster predictions using a trained Random Forest
-(RF) classifier [@friedman2001]. The analysis utilised the reef characteristics of interest
-as the predictors, including the median reef depth, mean DHW for the given GCM, Log10 - weighted incoming connectivity, Log10 - weighted outgoing connectivity, and Log10 - outgoing-to-incoming connectivity ratio.
-The full dataset
-consisted of the time series cluster assignment of each of the 2429 reefs under the five
-GCMs explored, for a total of 12,145 samples. The dataset was randomly split into training
-(60%) and testing (40%) subsets to ensure model generalisability. The RF classifier achieved
-99% accuracy on the training set and 62% on the test set.
+Partial Dependence Analysis was conducted to understand the relationship between features and bioregion-scale time series cluster predictions using a trained Random Forest (RF) classifier [@friedman2001].
+The analysis utilised the reef characteristics of interest as the predictors, including the median reef depth, mean DHW for the given GCM, Log10 - weighted incoming connectivity, Log10 - weighted outgoing connectivity, and Log10 - outgoing-to-incoming connectivity ratio.
+The full dataset consisted of the time series cluster assignment of each of the 2429 reefs under the five GCMs explored, for a total of 12,145 samples.
+The dataset was randomly split into training (60%) and testing (40%) subsets to ensure model generalisability.
+The RF classifier achieved 99% accuracy on the training set and 62% on the test set.
 
-While 99% accuracy suggests the classifier is overfit to the training data, the 66% test
-accuracy indicates a meaningful relationship between modelled reef characteristics and their
-assigned clusters has been captured. A 3-fold cross-validation was also conducted, arriving
-at a similar 67% accuracy rate. The consistent level of accuracy across test and
-cross-validation demonstrates the generalised performance of the RF classifier is reliable.
-Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
-0.7, 0.5 and 0.65 respectively, indicating balanced performance across the cluster
-categories. Lower performance with the Medium cluster reflects the inherent difficulty of
-classifying transitional states in natural systems. For management applications, this level
-of performance provides valuable decision support when combined with expert knowledge and
-the model's probabilistic outputs.
+While 99% accuracy suggests the classifier is overfit to the training data, the 66% test accuracy indicates a meaningful relationship between modelled reef characteristics and their assigned clusters has been captured.
+A 3-fold cross-validation was also conducted, arriving at a similar 67% accuracy rate.
+The consistent level of accuracy across test and cross-validation demonstrates the generalised performance of the RF classifier is reliable.
+Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be 0.7, 0.5 and 0.65 respectively, indicating balanced performance across the cluster categories.
+Lower performance with the Medium cluster reflects the inherent difficulty of classifying transitional states in natural systems.
+For management applications, this level of performance provides valuable decision support when combined with expert knowledge and the model's probabilistic outputs.
 
 Partial dependence analysis was performed by applying the trained model to the test dataset.
-Values for individual predictors were systematically (one-at-a-time) varied across a grid of
-50 equally spaced points spanning the predictor's range, while all other features were left
-at their modelled values. The procedure creates (1) a modified test dataset, where the
-target predictor was set to the grid value for all samples, (2) probabilistic predictions
-for all three cluster classes using the trained RF classifier, and (3) the mean predicted
-probability for each class across all test observations. The median was also assessed (not
-shown) but was found not to substantially influence the interpretation of results. The
-process isolates the marginal effect of each predictor by averaging over the natural
-distribution of all other representative reef characteristics in the test dataset. Additionally,
-to assess possible interaction between reef depth and incoming connectivity, two-way partial
-dependence analysis was performed on grids along the range of these two features.
+Values for individual predictors were systematically (one-at-a-time) varied across a grid of 50 equally spaced points spanning the predictor's range, while all other features were left at their modelled values.
+The procedure creates (1) a modified test dataset, where the target predictor was set to the grid value for all samples, (2) probabilistic predictions for all three cluster classes using the trained RF classifier, and (3) the mean predicted probability for each class across all test observations.
+The median was also assessed (not shown) but was found not to substantially influence the interpretation of results.
+The process isolates the marginal effect of each predictor by averaging over the natural distribution of all other representative reef characteristics in the test dataset.
+Additionally, to assess possible interaction between reef depth and incoming connectivity, two-way partial dependence analysis was performed on grids along the range of these two features.
 
@@
 
-Using coral cover time series for each reef we calculated the number of years each reef
-maintains coral cover above a given percent threshold. The threshold represents the level of
-live coral cover necessary to maintain a positive carbonate budget (denoted here as
-$\theta_{0}$ to indicate the budget equilibrium). Greater number of years above $\theta_{0}$
-suggests greater resilience and opportunity for recovery.
+Using coral cover time series for each reef we calculated the number of years each reef maintains coral cover above a given percent threshold.
+The threshold represents the level of live coral cover necessary to maintain a positive carbonate budget (denoted here as $\theta_{0}$ to indicate the budget equilibrium).
+Greater number of years above $\theta_{0}$ suggests greater resilience and opportunity for recovery.
 
-Recent analyses suggest a general threshold of \~17% live coral cover in the case of the
-mid-shelf and offshore GBR reefs [@desbiens2021]. Given in situ carbonate budgets are
-influenced by (1) a range of processes; (2) the variety of approaches that could be used to
-measure those processes; and (3) the uncertainty surrounding these, it would be unreasonable
-to assume all reefs adhere to a single precise $\theta_{0}$ value. Concurrently, it is
-difficult to ascertain a suitable $\theta_{0}$ value for each individual reef.
+Recent analyses suggest a general threshold of \~17% live coral cover in the case of the mid-shelf and offshore GBR reefs [@desbiens2021].
+Given in situ carbonate budgets are influenced by (1) a range of processes; (2) the variety of approaches that could be used to measure those processes; and (3) the uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a single precise $\theta_{0}$ value.
+Concurrently, it is difficult to ascertain a suitable $\theta_{0}$ value for each individual reef.
 
-Given the uncertainties present, the proportion of modelled reefs that display capacity to
-maintain coral cover above a given $\theta_{0}$ threshold is examined. An indicative range
-of 10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
-al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of
-the lower and upper bounds respectively. Robustness of the conclusions drawn to the
-uncertainty in the precise value of $\theta_{0}$ for all reefs can then be assessed by using
-the indicative range.
+Given the uncertainties present, the proportion of modelled reefs that display capacity to maintain coral cover above a given $\theta_{0}$ threshold is examined.
+An indicative range of 10 to 20% is used (inclusive, with a step size of 1%).
+The range was informed by Perry et al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of the lower and upper bounds respectively.
+Robustness of the conclusions drawn to the uncertainty in the precise value of $\theta_{0}$ for all reefs can then be assessed by using the indicative range.
 
-The relationships between the number of years above $\theta_{0}$ and characteristics such as
-median reef depth and Log-10 total connectivity strength were then assessed with Spearman's
-rank correlation. Spearman's correlation coefficient was adopted as reef depth and
-connectivity strength distributions are expected to be non-normal and highly skewed.
-Furthermore, reefs are naturally of different types and experience different conditions, and
-so the monotonic trends (whether the relationship consistently increase or decrease) rather
-than the exact quantitative relationship was of interest for this analysis.
+The relationships between the number of years above $\theta_{0}$ and characteristics such as median reef depth and Log-10 total connectivity strength were then assessed with Spearman's rank correlation.
+Spearman's correlation coefficient was adopted as reef depth and connectivity strength distributions are expected to be non-normal and highly skewed.
+Furthermore, reefs are naturally of different types and experience different conditions, and so the monotonic trends (whether the relationship consistently increase or decrease) rather than the exact quantitative relationship was of interest for this analysis.
 
@@
 
-There were substantial differences in the maintenance of coral cover post 2030 between the
-GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs
-across clusters (Low, Medium and High).
+There were substantial differences in the maintenance of coral cover post 2030 between the GCMs.
+Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs across clusters (Low, Medium and High).
 
-Of the GCMs explored, NorESM2-MM had the lowest Equilibrium Climate Sensitivity (2.5°C) and
-reefs exhibit continuing recovery and decline dynamics up to 2075 under this hypothetical
-climate future. Unsurprisingly, recovery phases were predominantly seen in the reefs in the
-High cluster, with Medium and Low exhibiting lesser probability of such periods of
-recovery. Generally, recovery and increases in coral cover were visible in simulated results
-up to 2045. Under NorESM2-MM, the Far Northern Management area were found to have the most
-similar temporal behaviour between Low and High clusters compared to other Management
-areas (@stbl-cluster-cid) due to the low degree of coral cover overall
-(@fig-gcm-cover-trajectories).
+Of the GCMs explored, NorESM2-MM had the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline dynamics up to 2075 under this hypothetical climate future.
+Unsurprisingly, recovery phases were predominantly seen in the reefs in the High cluster, with Medium and Low exhibiting lesser probability of such periods of recovery.
+Generally, recovery and increases in coral cover were visible in simulated results up to 2045.
+Under NorESM2-MM, the Far Northern Management area were found to have the most similar temporal behaviour between Low and High clusters compared to other Management areas (@stbl-cluster-cid) due to the low degree of coral cover overall (@fig-gcm-cover-trajectories).
 
-Intermediate levels of coral cover maintenance can be seen in ACCESS-ESM1-5 (ECS value of
-3.87°C) when compared to the other GCMs (of higher and lower ECS values). Under these
-intermediate conditions (in relative terms), there is potential for reefs in the High
-cluster to maintain coral cover levels around 20% to 2050. The highest peak DHW levels
-occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs time
-series occur under ACCESS-CM2 (@fig-methods-dhws). Under conditions represented by high ECS
-value GCMs - specifically, ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and GFDL-CM4
-(4.1°C) - all reefs are largely in decline across all management areas from 2055
-(@stbl-cluster-cid).
+Intermediate levels of coral cover maintenance can be seen in ACCESS-ESM1-5 (ECS value of 3.87°C) when compared to the other GCMs (of higher and lower ECS values).
+Under these intermediate conditions (in relative terms), there is potential for reefs in the High cluster to maintain coral cover levels around 20% to 2050.
+The highest peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs time series occur under ACCESS-CM2 (@fig-methods-dhws).
+Under conditions represented by high ECS value GCMs - specifically, ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and GFDL-CM4 (4.1°C) - all reefs are largely in decline across all management areas from 2055 (@stbl-cluster-cid).
 
-![Time series of coral cover (relative to reef area) categorised within each Management area
-(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. The
-time series are categorised as "Low" (green), "Medium" (in orange), and "High" median cover
-(in blue). Solid lines represent the cluster median time series and bands represent the 95th
-percentile confidence
-intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
-fig-align="center" width="14.82cm"}
+![Time series of coral cover (relative to reef area) categorised within each Management area (rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060.
+The time series are categorised as "Low" (green), "Medium" (in orange), and "High" median cover (in blue).
+Solid lines represent the cluster median time series and bands represent the 95th percentile confidence intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories fig-align="center" width="14.82cm"}
 
-Comparing across GCMs, it is common for reefs to switch between clusters, including from
-Low to High and vice versa (@sfig-gcm-bioregion-cluster-assignment). Of 2429 reefs, 20%
-(503) of reefs have consistent cluster assignment across all GCMs. Of the 503 consistently
-assigned reefs, 49% are within the Far Northern Management area, with 7%, 13% and 31%
-occurring in the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management
-areas respectively (@sfig-gcm-cluster-map). Of the 503 consistently assigned reefs, 32%, 7%
-and 61% are clustered into Low, Medium and High clusters respectively. High levels of
-assignment variability across GCMs are expected as due to spatial differences in each given
-GCM’s DHW trajectories.
+Comparing across GCMs, it is common for reefs to switch between clusters, including from Low to High and vice versa (@sfig-gcm-bioregion-cluster-assignment).
+Of 2429 reefs, 20% (503) of reefs have consistent cluster assignment across all GCMs.
+Of the 503 consistently assigned reefs, 49% are within the Far Northern Management area, with 7%, 13% and 31% occurring in the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas respectively (@sfig-gcm-cluster-map).
+Of the 503 consistently assigned reefs, 32%, 7% and 61% are clustered into Low, Medium and High clusters respectively.
+High levels of assignment variability across GCMs are expected as due to spatial differences in each given GCM’s DHW trajectories.
 
@@
 
-In contrast to the broad temporal behaviour at the Management area scale, the relationship
-between reef characteristics and assigned clusters were found to be similar at the
-bioregion scale across GCMs. Results are only shown and discussed for ACCESS-ESM1-5, an
-intermediate ECS scenario (@sfig-ecs). Those interested in results for the other assessed
-GCMs are referred to Grier and Iwanaga [-@grier2025]. Across bioregions, reefs in the High
-cluster not only had greater levels of coral recovery but displayed persistence to 2050
-(@sfig-access-esm1-5-bioregion-timeseries). Reefs in the High cluster were consistently
-found to have the greatest median reef depths across bioregions
-(@fig-access-esm1-5-bioregion-depth).
+In contrast to the broad temporal behaviour at the Management area scale, the relationship between reef characteristics and assigned clusters were found to be similar at the bioregion scale across GCMs.
+Results are only shown and discussed for ACCESS-ESM1-5, an intermediate ECS scenario (@sfig-ecs).
+Those interested in results for the other assessed GCMs are referred to Grier and Iwanaga [-@grier2025].
+Across bioregions, reefs in the High cluster not only had greater levels of coral recovery but displayed persistence to 2050 (@sfig-access-esm1-5-bioregion-timeseries).
+Reefs in the High cluster were consistently found to have the greatest median reef depths across bioregions (@fig-access-esm1-5-bioregion-depth).
 
-![Median depth for reefs within each bioregion, separated into clusters assigned by time
-series clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative
-cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters
-with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030
-and 2060 within each bioregion. Solid lines represent the median depth for each cluster
-across reefs and bands represent the distribution of depth values within each cluster.
-Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-fig-align="center" width="14.82cm"}
+![Median depth for reefs within each bioregion, separated into clusters assigned by time series clustering.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines represent the median depth for each cluster across reefs and bands represent the distribution of depth values within each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth fig-align="center" width="14.82cm"}
 
-In many bioregions reefs in the Low cluster have the lowest correlation between coral cover
-and inverse-DHW time series whereas reefs in the High cluster were found to have the
-strongest correlation (@sfig-access-esm1-5-bioregion-dhwcor). Across six of the 29
-bioregions reef mean DHW levels increased as cluster cover decreased
-(@sfig-access-esm1-5-bioregion-dhwmean). There were no consistent patterns across bioregions
-in their reefs' initial proportion of habitable area occupied by corals and cluster
-assignment (@sfig-access-esm1-5-bioregion-initialproportion). Across most bioregions there
-were not consistent differences between clusters in connectivity metrics such as Log-10
-source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming).
+In many bioregions reefs in the Low cluster have the lowest correlation between coral cover and inverse-DHW time series whereas reefs in the High cluster were found to have the strongest correlation (@sfig-access-esm1-5-bioregion-dhwcor).
+Across six of the 29 bioregions reef mean DHW levels increased as cluster cover decreased (@sfig-access-esm1-5-bioregion-dhwmean).
+There were no consistent patterns across bioregions in their reefs' initial proportion of habitable area occupied by corals and cluster assignment (@sfig-access-esm1-5-bioregion-initialproportion).
+Across most bioregions there were not consistent differences between clusters in connectivity metrics such as Log-10 source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming).
 
@@
 
-A Partial Dependence Analysis was conducted using a Random Forest classifier to identify
-reef characteristics that influence its temporal behaviour, and thus its cluster assignment
-into Low, Medium, or High. Bioregion classification was excluded from this analysis as a
-predictor due to its categorical nature providing limited interpretable information, and is
-further justified by its low feature importance score of 9%, the lowest of all predictors
-(@fig-ts-cluster-pdp; Panel A). Reef median depth and mean DHW level have the highest
-feature importance scores, accounting for 25% and 16% predictive importance respectively.
+A Partial Dependence Analysis was conducted using a Random Forest classifier to identify reef characteristics that influence its temporal behaviour, and thus its cluster assignment into Low, Medium, or High.
+Bioregion classification was excluded from this analysis as a predictor due to its categorical nature providing limited interpretable information, and is further justified by its low feature importance score of 9%, the lowest of all predictors (@fig-ts-cluster-pdp; Panel A).
+Reef median depth and mean DHW level have the highest feature importance scores, accounting for 25% and 16% predictive importance respectively.
 Weighted incoming and outgoing connectivity (Log10) features account for \~13.6% feature importance.
-The carrying capacity of a reef accounts for 12.3% feature importance. Reef source-to-sink ratio (Log10) both had feature importance scores of \~10%.
+The carrying capacity of a reef accounts for 12.3% feature importance.
+Reef source-to-sink ratio (Log10) both had feature importance scores of \~10%.
 
-Reefs have the greatest probability of being clustered into Low if shallow, and High at
-greater depths, with medium cluster reefs exhibiting a lower, and more stable, assignment
-probability across depth ranges (@fig-ts-cluster-pdp; Panel B). A large increase in the
-probability of a reef being categorised as High can be seen between 10 and 15 meters depth.
-This is at the edge of the depth range used in current deployment efforts [@howlett2021;
-@randall2021; @whitman2024] but indicates a depth range that could be adopted to maximise
-longevity and benefits of, for example, coral seeding activities. Across mean DHW values,
-assignment probability is roughly equal across the three clusters up to 5 DHW. A sharp
-delineation can be seen \> 5 DHW when comparing High with other clusters, with lower
-assignment probability (\~25%) compared to Medium and Low (\~40%) (@fig-ts-cluster-pdp;
-Panel B).
+Reefs have the greatest probability of being clustered into Low if shallow, and High at greater depths, with medium cluster reefs exhibiting a lower, and more stable, assignment probability across depth ranges (@fig-ts-cluster-pdp; Panel B).
+A large increase in the probability of a reef being categorised as High can be seen between 10 and 15 meters depth.
+This is at the edge of the depth range used in current deployment efforts [@howlett2021; @randall2021; @whitman2024] but indicates a depth range that could be adopted to maximise longevity and benefits of, for example, coral seeding activities.
+Across mean DHW values, assignment probability is roughly equal across the three clusters up to 5 DHW.
+A sharp delineation can be seen \> 5 DHW when comparing High with other clusters, with lower assignment probability (\~25%) compared to Medium and Low (\~40%) (@fig-ts-cluster-pdp; Panel B).
 
@@
 
-Individual feature analysis for carrying capacity indicates that its influence on cluster assignment is concentrated at the low range
-of predictor values (@fig-ts-cluster-pdp). This aligns with the right-skewed distribution
-of carrying capacity across reefs for these three predictor variables. Beyond this low-end range, the
-partial dependence becomes near constant, contrary to their
-feature importance scores which suggest these characteristics do contribute important
-information to predictions. The contrasting outcomes indicate that interactions between
-other reef characteristics are driving behaviour rather than a strong influence from a
-single individual characteristic.
+Individual feature analysis for carrying capacity indicates that its influence on cluster assignment is concentrated at the low range of predictor values (@fig-ts-cluster-pdp).
+This aligns with the right-skewed distribution of carrying capacity across reefs for these three predictor variables.
+Beyond this low-end range, the partial dependence becomes near constant, contrary to their feature importance scores which suggest these characteristics do contribute important information to predictions.
+The contrasting outcomes indicate that interactions between other reef characteristics are driving behaviour rather than a strong influence from a single individual characteristic.
 
-Assessing random forest prediction accuracy across predictor values, summarised by
-bioregions, reveals increasing performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf). This highlights that there may be unexplained
-variation between reefs in shallow bioregions that contributes to cluster assignment and reef cover outcomes but
-is not captured by our included predictor variables.
+Assessing random forest prediction accuracy across predictor values, summarised by bioregions, reveals increasing performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf).
+This highlights that there may be unexplained variation between reefs in shallow bioregions that contributes to cluster assignment and reef cover outcomes but is not captured by our included predictor variables.
 
-![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
-Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a
-reef being classified to one of the three clusters (Panel B). Partial Dependence Plots for
-bioregions were excluded as they were found to be uninformative. PDPs indicate the
-probability of a reef from the test dataset being clustered into each category
-depending on the predictor value on the x axis, when adjusted for values of other
-predictors. Green, orange and blue lines indicate cluster assignment probability for Low,
-Medium and High clusters respectively. Transparent grey points above probability lines
-represent the predictor values present in the test dataset, providing a rough indication of
-predictor value distribution across
-reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center"
-width="14.82cm"}
+![Feature importance scores (Panel A) of the Random Forest classifier, and Partial Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a reef being classified to one of the three clusters (Panel B).
+Partial Dependence Plots for bioregions were excluded as they were found to be uninformative.
+PDPs indicate the probability of a reef from the test dataset being clustered into each category depending on the predictor value on the x axis, when adjusted for values of other predictors.
+Green, orange and blue lines indicate cluster assignment probability for Low, Medium and High clusters respectively.
+Transparent grey points above probability lines represent the predictor values present in the test dataset, providing a rough indication of predictor value distribution across reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center" width="14.82cm"}
 
@@
 Probability values for each cluster are generated by the random forest classifier using each combination of depth and incoming connectivity values along the axes at 50 grid points.
-The actual distributions of depth and incoming connectivity values for reefs are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_conn_pdp.png){#fig-ts-cluster-pdp-twoway fig-align="center"
-width="14.82cm"}
+The actual distributions of depth and incoming connectivity values for reefs are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_conn_pdp.png){#fig-ts-cluster-pdp-twoway fig-align="center" width="14.82cm"}
 
@@
 
-Reef median depth had a moderate positive correlation with the number of years a reef
-maintains coral cover above the assumed carbonate budget threshold required to sustain live
-coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
-that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate; @sfig-access-esm1-5-mean-carb-budget).
-Unsurprisingly, the number of years above $\theta_0$ substantially decreased as $\theta_0$
-is increased, as does the Spearman's correlation. Decreasing correlation levels are likely
-due to an increasing number of reefs being unable to maintain coral cover above $\theta_0$
-as it is increased, with the distribution of years above threshold becoming increasingly
-right-skewed (@fig-access-esm1-5-depth-conn-carbonate). In contrast, log10-transformed total
-connectivity strength ($\text{log10}(S)$) was found to have no correlation with the number
-of years a reef maintains cover above the required thresholds
-(@fig-access-esm1-5-depth-conn-carbonate). The correlation between $\text{log10}(S)$ and
-$\theta_0$ slightly increased as the assumed threshold for $\theta_0$ increased.
+Reef median depth had a moderate positive correlation with the number of years a reef maintains coral cover above the assumed carbonate budget threshold required to sustain live coral cover ($\theta_{0}$).
+Greater median depth was a key characteristic defining reefs that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate; @sfig-access-esm1-5-mean-carb-budget).
+Unsurprisingly, the number of years above $\theta_0$ substantially decreased as $\theta_0$ is increased, as does the Spearman's correlation.
+Decreasing correlation levels are likely due to an increasing number of reefs being unable to maintain coral cover above $\theta_0$ as it is increased, with the distribution of years above threshold becoming increasingly right-skewed (@fig-access-esm1-5-depth-conn-carbonate).
+In contrast, log10-transformed total connectivity strength ($\text{log10}(S)$) was found to have no correlation with the number of years a reef maintains cover above the required thresholds (@fig-access-esm1-5-depth-conn-carbonate).
+The correlation between $\text{log10}(S)$ and $\theta_0$ slightly increased as the assumed threshold for $\theta_0$ increased.
 
-![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
-(y-axis). The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef variables (depth -
-left and Log-10 connectivity strength - right) and the number of years cover exceeds the
-carbonate budget threshold. Point colour represents the median reef depth in metres in the
-left-hand panel, and Log-10 total connectivity strength in the right-hand panel. Red points
-represent the mean number of years above an assumed carbonate budget threshold across reefs.
-Deeper reefs are better able to maintain cover above the indicative carbonate budget
-threshold, while there is no considerable relationship between connectivity strength and
-carbonate budget maintenance. Displays results from median time series using
-ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
-fig-align="center" width="14.82cm"}
+![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075 (y-axis).
+The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef variables (depth - left and Log-10 connectivity strength - right) and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents the median reef depth in metres in the left-hand panel, and Log-10 total connectivity strength in the right-hand panel.
+Red points represent the mean number of years above an assumed carbonate budget threshold across reefs.
+Deeper reefs are better able to maintain cover above the indicative carbonate budget threshold, while there is no considerable relationship between connectivity strength and carbonate budget maintenance.
+Displays results from median time series using ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate fig-align="center" width="14.82cm"}
 
@@
 
-Under all GCMs many reefs are projected to suffer substantial declines in coral cover
-relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the
-lowest cover level cluster at the management area scale across GCMs. NorESM2-MM and
-ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future. Differences
-between Low, Medium and High reef clusters in cover time series are most notable under these
-two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into
-the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of
-future recovery and timespan of cover maintenance increase as GCM ECS increases
-(@fig-gcm-cover-trajectories). Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
-large declines and lower rates of recovery in high cover clusters are common compared to
-lower-ECS GCMs.
+Under all GCMs many reefs are projected to suffer substantial declines in coral cover relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the lowest cover level cluster at the management area scale across GCMs.
+NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future.
+Differences between Low, Medium and High reef clusters in cover time series are most notable under these two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories).
+Maintenance of coral cover into the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of future recovery and timespan of cover maintenance increase as GCM ECS increases (@fig-gcm-cover-trajectories).
+Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2) large declines and lower rates of recovery in high cover clusters are common compared to lower-ECS GCMs.
 
-The large differences in cover time series seen across the GCMs suggest that it is important
-to consider uncertainty in future conditions when assessing possible biological responses to
-change. This is supported by recent literature suggesting an effective approach to capturing
-climate change uncertainty is to model responses using GCMs separately [@shepherd2018].
-Despite large differences in coral cover across GCMs, the patterns identified between low,
-medium and high clusters of reefs suggest that the relative importance of environmental and
-biological factors such as depth refugia, connectivity and surface DHW levels is consistent
-across scenarios.
+The large differences in cover time series seen across the GCMs suggest that it is important to consider uncertainty in future conditions when assessing possible biological responses to change.
+This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model responses using GCMs separately [@shepherd2018].
+Despite large differences in coral cover across GCMs, the patterns identified between low, medium and high clusters of reefs suggest that the relative importance of environmental and biological factors such as depth refugia, connectivity and surface DHW levels is consistent across scenarios.
 
-Reefs in different clusters largely do not differ in mean modelled DHW levels experienced
-and exhibit overall similar DHW time series. While these reefs experience similar magnitude
-DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress
-events depends on reef depth. Reefs at deeper depths are likely to be clustered into High
-cover clusters. Reefs at shallow depths experience no, or few, years with coral cover
-exceeding levels likely required to maintain positive carbonate budgets. Movement of shallow
-reefs towards negative carbonate budgets in the future may contribute to phase shifts in
-reef dominant CaCO~3~ production. Shifting from coral driven to encrusting algae driven
-production, or to bioerosion dominated systems with rapid erosion of physical reef
-frameworks [@dudgeon2010; @perry2008]. While reefs at increased depths may be able to
-maintain coral driven CaCO~3~ production and accumulation into the future for longer. Our
-results suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m),
-depth contributes greatly to reef resilience and the ability of the reef to maintain
-positive carbonate budgets under future conditions. While similar findings have been
-demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014] regions,
-depth refugia analyses have often focussed on the potential of mesophotic reefs (\> 30m
-deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas
-et al. [-@venegas2019] found no association between depth and the alleviation of heat stress
-across a range of shallow reefs in the Pacific.
+Reefs in different clusters largely do not differ in mean modelled DHW levels experienced and exhibit overall similar DHW time series.
+While these reefs experience similar magnitude DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress events depends on reef depth.
+Reefs at deeper depths are likely to be clustered into High cover clusters.
+Reefs at shallow depths experience no, or few, years with coral cover exceeding levels likely required to maintain positive carbonate budgets.
+Movement of shallow reefs towards negative carbonate budgets in the future may contribute to phase shifts in reef dominant CaCO~3~ production.
+Shifting from coral driven to encrusting algae driven production, or to bioerosion dominated systems with rapid erosion of physical reef frameworks [@dudgeon2010; @perry2008].
+While reefs at increased depths may be able to maintain coral driven CaCO~3~ production and accumulation into the future for longer.
+Our results suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m), depth contributes greatly to reef resilience and the ability of the reef to maintain positive carbonate budgets under future conditions.
+While similar findings have been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014] regions, depth refugia analyses have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017].
+In contrast, Venegas et al.
+[-@venegas2019] found no association between depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
 
-These findings support the hypothesis that reefs at greater depths will exhibit
-characteristics of refugia and more prolonged structural resilience under climate change
-compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest
-that rubble instability is inversely correlated with reef depth, possibly limiting juvenile
-recruitment capacity of shallow reefs. A caveat to these depth-resilience findings is the
-quality of the bathymetry data used to calculate median reef depth. As detailed previously,
-estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution)
-which can be subject to high degrees of uncertainty, both in terms of the estimated depth at
-for each pixel as well as their alignment to the established GBRMPA reef outlines.
+These findings support the hypothesis that reefs at greater depths will exhibit characteristics of refugia and more prolonged structural resilience under climate change compared to shallower reefs.
+Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest that rubble instability is inversely correlated with reef depth, possibly limiting juvenile recruitment capacity of shallow reefs.
+A caveat to these depth-resilience findings is the quality of the bathymetry data used to calculate median reef depth.
+As detailed previously, estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution) which can be subject to high degrees of uncertainty, both in terms of the estimated depth at for each pixel as well as their alignment to the established GBRMPA reef outlines.
 
-Current reef restoration and intervention-investigation efforts on the GBR, such as
-deployment of coral seeding and fragment devices, target reefs with suitable restoration
-sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
-no explicit justifications for this depth range, restoration depth is likely constrained by
-snorkelling and diving deployment and monitoring logistical accessibility, visual
-identification of sites from the surface, in combination with tourism return value. Our
-results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
-reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the
-GBRMPA management region scale), with many unable to maintain positive carbonate budgets
-under future conditions. Partial dependence analysis revealed a range of depths from 10-15m
-where the probability of a reef being clustered into the High cover cluster increased
-substatially.
+Current reef restoration and intervention-investigation efforts on the GBR, such as deployment of coral seeding and fragment devices, target reefs with suitable restoration sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024].
+While there are no explicit justifications for this depth range, restoration depth is likely constrained by snorkelling and diving deployment and monitoring logistical accessibility, visual identification of sites from the surface, in combination with tourism return value.
+Our results suggest that of the assessed reefs occurring within the 1-10m depth range (1736 reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the GBRMPA management region scale), with many unable to maintain positive carbonate budgets under future conditions.
+Partial dependence analysis revealed a range of depths from 10-15m where the probability of a reef being clustered into the High cover cluster increased substatially.
 Additionally, two-way partial dependence analysis revealed that high incoming connectivity is important for High cluster assignment for reefs at depths of \>10m.
-Considering this 10-15m depth range, and targetting well connected reefs, when assessing possible restoration sites
-may reduce the exposure of planted and seeded corals to high thermal stress, while still
-maintaining effective logistical access to sites.
+Considering this 10-15m depth range, and targetting well connected reefs, when assessing possible restoration sites may reduce the exposure of planted and seeded corals to high thermal stress, while still maintaining effective logistical access to sites.
 Although transient, and difficult to measure, properties such as reef connectivity are likely to increase uncertainty in intervention planning to a greater degree than environmental characteristics such as reef depth.
-Reef intervention planning is a complex
-and challenging decision-making process [@anthony2020], and our results suggest that
-deployment site depth may be an important factor to additionally consider when assessing the
-long-term resilience of sites.
+Reef intervention planning is a complex and challenging decision-making process [@anthony2020], and our results suggest that deployment site depth may be an important factor to additionally consider when assessing the long-term resilience of sites.
 
-It is a common conclusion in coral reef ecology that a primary facet of reef resilience is
-the degree of larval connectivity between reefs and the supply of recruits that a reef
-receives following disturbance [@hock2017; @mumby2008; @torres2024]. In contrast, our
-results suggest that while connectivity metrics show some levels of cluster predictor
-importance, there are few differences between resilient and non-resilient reefs in metrics
-such as source-to-sink connectivity ratio and total connectivity strength.
+It is a common conclusion in coral reef ecology that a primary facet of reef resilience is the degree of larval connectivity between reefs and the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008; @torres2024].
+In contrast, our results suggest that while connectivity metrics show some levels of cluster predictor importance, there are few differences between resilient and non-resilient reefs in metrics such as source-to-sink connectivity ratio and total connectivity strength.
 While there is interaction between incoming connectivity and depth in reef cluster prediction, according to available input data, there are few reefs in the GBR that occur at depths \>10m and have Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget), resulting in low importance of connectivity as an individual feature for clustering across the GBR.
-Furthermore, our
-results suggest no relationship between connectivity strength and the ability of reefs to
-maintain positive carbonate budgets under future conditions. There has been contrasting
-evidence [@bode2018; @hock2017] surrounding whether recent generation connectivity modelling
-is able to identify reefs that are important for recovery processes, with findings dependent
-on the larval connectivity model used. These investigations were performed using prior
-generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and
-1996-2002 [@bode2018] time periods, without considering the influence of reef depth on resilience. Using updated 1km^2^ resolution larval connectivity
-across the whole GBR, with a limited temporal sample of particle flows, our results suggest
-that larval connectivity alone may not be important or reef resilience and recovery, but should be considered in combination with more influential factors such as depth.
+Furthermore, our results suggest no relationship between connectivity strength and the ability of reefs to maintain positive carbonate budgets under future conditions.
+There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent generation connectivity modelling is able to identify reefs that are important for recovery processes, with findings dependent on the larval connectivity model used.
+These investigations were performed using prior generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods, without considering the influence of reef depth on resilience.
+Using updated 1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal sample of particle flows, our results suggest that larval connectivity alone may not be important or reef resilience and recovery, but should be considered in combination with more influential factors such as depth.
 
-Our findings on the importance of connectivity may differ due to the highly uncertain nature
-of larval connectivity modelling [@vogt-vincent2023], the way larval flows and juvenile
-recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early bleaching
-events decreasing the breeding capacity of strongly connected reefs. Analysing daily
-connectivity data Vogt-Vincent et al. [-@vogt-vincent2023] suggest that time-mean
-connectivity may not be suitable for capturing the seasonal - ecological time scale
-connectivity between locations due to high daily variability in connectivity data. This is
-supported by the connectivity data used in our investigation, which have large relative
-standard deviations for connectivity between reefs over the 24 days used
-(@sfig-connectivity-rsd). Using alternative summarisation methods that capture
-ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
-connectivity [@vogt-vincent2023], future investigations may find increased importance of
-both depth and reef connectivity for resilience, in line with other investigations
-[@hock2017; @torres2024]. Further improvements and research in connectivity modelling are
-necessary when incorporating connectivity as a supplementary factor in reef resilience and intervention-planning analyses.
+Our findings on the importance of connectivity may differ due to the highly uncertain nature of larval connectivity modelling [@vogt-vincent2023], the way larval flows and juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early bleaching events decreasing the breeding capacity of strongly connected reefs.
+Analysing daily connectivity data Vogt-Vincent et al.
+[-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for capturing the seasonal - ecological time scale connectivity between locations due to high daily variability in connectivity data.
+This is supported by the connectivity data used in our investigation, which have large relative standard deviations for connectivity between reefs over the 24 days used (@sfig-connectivity-rsd).
+Using alternative summarisation methods that capture ecological-timescale patterns in coral larval dispersal, such as cumulated implicit connectivity [@vogt-vincent2023], future investigations may find increased importance of both depth and reef connectivity for resilience, in line with other investigations [@hock2017; @torres2024].
+Further improvements and research in connectivity modelling are necessary when incorporating connectivity as a supplementary factor in reef resilience and intervention-planning analyses.
 
@@
 
-There are multiple caveats in how coral ecosystem dynamics are modelled in this
-investigation. We model coral colonies as circular diameter values that are tracked over
-timesteps through growth. Due to the availability of quality future projected data we do not
-consider other important impacts such as waves, cyclones, currents and Crown of Thorns
-Starfish (CoTS) on coral colony survival and bleaching [@massel1993; @deaker2022].
-Uncertainty in connectivity modelling outputs, satellite-derived bathymetry data and future
-thermal stress projections are likely to influence the results obtained in this
-investigation. While the resolution of connectivity data used in this investigation improves
-upon data used in comparable studies [@bozec2025], the time-mean implementation used may not
-effectively capture long term patterns [@vogt-vincent2023]. Using alternative connectivity
-implementation methods that better capture the ecological-timescale trends in reef
-connections rather than the high daily variability, would improve confidence in the
-connectivity findings of this investigation [@vogt-vincent2023]. The DHW data used in this
-investigation have not been bias corrected for the Great Barrier Reef region and are part of
-a wider Australian dataset [@dixon2022] developed using statistical downscaling.
-Additionally, Lachs et al. [@lachs2021] suggest the utility of DHW levels for prediction of
-coral bleaching can be improved by reducing the threshold for HotSpot Anomaly values from
-MMM +1 to MMM and reducing the accumulation window from 12 weeks to 8 weeks. We investigate
-a range of future climate responses, thermal projections and ecological parameterisations of
-ADRIA - CoralBlox to account for many possible futures, and our results suggest the factors
-that influence reef resilience are consistent across these scenarios.
+There are multiple caveats in how coral ecosystem dynamics are modelled in this investigation.
+We model coral colonies as circular diameter values that are tracked over timesteps through growth.
+Additionally, we do not model the direct influence of light intensity on coral growth or the negative influence of depth on coral growth rates due to reduced light levels.
+\[**BG: Include citations for influence of depth/light on growth rates**\].
+If included in this investigation, it is possible that reef recovery ability would be reduced at greater depths even though corals at these depths experience refugia from thermal stress.
+Due to the availability of quality future projected data we do not consider other important impacts such as waves, cyclones, currents and Crown of Thorns Starfish (CoTS) on coral colony survival and bleaching [@massel1993; @deaker2022].
 
-Additionally, it is currently not possible to obtain highly accurate and precise estimates
-of reef depth at the GBR-scale. Data adopted for the given assessment are said to be
-accurate up to 15m from Mean Sea Level [@GBRMPA2020; @li2021], however there are many
-sources of uncertainty in the depth estimates used for this study. Satellite-derived
-estimates are subject to different bottom types (rock, sand, seagrass, etc) and their effect
-on reflectance, the water penetration depth of satellite sensors, influence of local
-conditions (e.g., turbidity and wave activity), among many other factors. The median depths
-for each indicative reef area were extracted from bathymetry data using zonal statistics and
-depth values beyond the stated 15m accuracy threshold [@GBRMPA2020] were included. The
-resulting depth estimates are therefore highly uncertain and are only adopted as a useful
-indication for the purpose of the presented analysis. They are not intended to be an
-accurate and precise report of reef depths across the GBR.
+Uncertainty in connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress projections are likely to influence the results obtained in this investigation.
+While the resolution of connectivity data used in this investigation improves upon data used in comparable studies [@bozec2025], the time-mean implementation used may not effectively capture long term patterns [@vogt-vincent2023].
+Using alternative connectivity implementation methods that better capture the ecological-timescale trends in reef connections rather than the high daily variability, would improve confidence in the connectivity findings of this investigation [@vogt-vincent2023].
+The DHW data used in this investigation have not been bias corrected for the Great Barrier Reef region and are part of a wider Australian dataset [@dixon2022] developed using statistical downscaling.
+Additionally, Lachs et al.
+[@lachs2021] suggest the utility of DHW levels for prediction of coral bleaching can be improved by reducing the threshold for HotSpot Anomaly values from MMM +1 to MMM and reducing the accumulation window from 12 weeks to 8 weeks.
+We investigate a range of future climate responses, thermal projections and ecological parameterisations of ADRIA - CoralBlox to account for many possible futures, and our results suggest the factors that influence reef resilience are consistent across these scenarios.
 
-In addition to the usual challenges of deriving data from satellite imagery, it is
-acknowledged that there is high potential for misalignment between the bathymetry data and
-GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton2025], for example, identified 120
-false positives, where features identified as reefs were sand banks or rocky reefs (rather
-than coral reefs). Reefs with bathymetry data of less than 5% of its indicative area were
-excluded from analysis to ensure analyses were not conducted on reefs with no data coverage
-(see @sfig-depth-cutoff). The existing GBRMPA reef outlines were adopted to align with other
-ongoing modelling and analyses conducted as part of the Reef Restoration and Adaptation
-Program (<https://gbrrestoration.org>; [@thereef]).
+Additionally, it is currently not possible to obtain highly accurate and precise estimates of reef depth at the GBR-scale.
+Data adopted for the given assessment are said to be accurate up to 15m from Mean Sea Level [@GBRMPA2020; @li2021], however there are many sources of uncertainty in the depth estimates used for this study.
+Satellite-derived estimates are subject to different bottom types (rock, sand, seagrass, etc) and their effect on reflectance, the water penetration depth of satellite sensors, influence of local conditions (e.g., turbidity and wave activity), among many other factors.
+The median depths for each indicative reef area were extracted from bathymetry data using zonal statistics and depth values beyond the stated 15m accuracy threshold [@GBRMPA2020] were included.
+The resulting depth estimates are therefore highly uncertain and are only adopted as a useful indication for the purpose of the presented analysis.
+They are not intended to be an accurate and precise report of reef depths across the GBR.
 
-The modelling conducted with ADRIA-CoralBlox itself is subject to many uncertainties. For
-one, a formal mechanistic and spatial validation of the model represents an area for future
-refinement and is the focus of a future publication. Indicative results are included in the
-supplementary **\[TI: For Pedro to include! :`D`\].** The consistency of projected patterns
-with known coral-climate relationships and reef characteristics provides confidence in the
-model's ability to meaningfully capture ecological signals at the GBR-scale. The mechanistic
-basis of the model, combined with qualitative assessment of model behavior, supports the
-robustness of our findings for understanding broad-scale coral cover responses to climatic
-drivers. The aim here, however, was to assess the relative influence of reef characteristics
-on structural resilience under future conditions, rather than provide spatially explicit and
-precise predictions of reef outcomes. Using this approach, we suggest that reef depth is an
-important factor for reef resilience under thermal stress.
+In addition to the usual challenges of deriving data from satellite imagery, it is acknowledged that there is high potential for misalignment between the bathymetry data and GBRMPA reef outlines.
+Hammerton and Lawrey [-@hammerton2025], for example, identified 120 false positives, where features identified as reefs were sand banks or rocky reefs (rather than coral reefs).
+Reefs with bathymetry data of less than 5% of its indicative area were excluded from analysis to ensure analyses were not conducted on reefs with no data coverage (see @sfig-depth-cutoff).
+The existing GBRMPA reef outlines were adopted to align with other ongoing modelling and analyses conducted as part of the Reef Restoration and Adaptation Program (<https://gbrrestoration.org>; [@thereef]).
 
-Improvements in remote sensing approaches for broad scale bathymetry measurement and
-understanding of how depth impacts experienced thermal stress on reefs will further enhance
-investigations of depth as a critical factor for reef resilience. Additional analyses could
-build on the findings of this study by assessing the impacts of prioritising reef depth in
-reef restoration decision making. Future analyses could incorporate other environmental and
-ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn Starfish
-[@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
+The modelling conducted with ADRIA-CoralBlox itself is subject to many uncertainties.
+For one, a formal mechanistic and spatial validation of the model represents an area for future refinement and is the focus of a future publication.
+Indicative results are included in the supplementary **\[TI: For Pedro to include!
+:`D`\].** The consistency of projected patterns with known coral-climate relationships and reef characteristics provides confidence in the model's ability to meaningfully capture ecological signals at the GBR-scale.
+The mechanistic basis of the model, combined with qualitative assessment of model behavior, supports the robustness of our findings for understanding broad-scale coral cover responses to climatic drivers.
+The aim here, however, was to assess the relative influence of reef characteristics on structural resilience under future conditions, rather than provide spatially explicit and precise predictions of reef outcomes.
+Using this approach, we suggest that reef depth is an important factor for reef resilience under thermal stress.
+
+Improvements in remote sensing approaches for broad scale bathymetry measurement and understanding of how depth impacts experienced thermal stress on reefs will further enhance investigations of depth as a critical factor for reef resilience.
+Additional analyses could build on the findings of this study by assessing the impacts of prioritising reef depth in reef restoration decision making.
+Future analyses could incorporate other environmental and ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn Starfish [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
 
@@
 
-The results presented suggest that when modelled as part of a large and complex ecosystem,
-reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in
-support of depth as a form of thermal refugia for shallow-water reefs on the GBR. While
-protecting ‘key node’ reefs in larval connectivity networks is an important consideration
-for reef restoration efforts [@anthony2020; @hock2017], current connectivity modelling
-methods, in combination with our modelling framework, suggest that connectivity may not be
-as important for reef resilience under projected conditions as environmental factors such as
-depth and thermal stress levels. We suggest further analyses that investigate the benefits
-of incorporating depth-based resilience into reef intervention decision making, as well as
-further research and development in connectivity modelling methods for whole-ecosystem
-scales.
+The results presented suggest that when modelled as part of a large and complex ecosystem, reef depth is a key factor contributing to ongoing reef resilience.
+We provide evidence in support of depth as a form of thermal refugia for shallow-water reefs on the GBR.
+While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts [@anthony2020; @hock2017], current connectivity modelling methods, in combination with our modelling framework, suggest that connectivity may not be as solely-important for reef resilience under projected conditions as environmental factors such as depth and thermal stress levels.
+We suggest further analyses that investigate the benefits of incorporating depth-based resilience into reef intervention decision making, as well as further research and development in connectivity modelling methods for whole-ecosystem scales.
 
@@
 
+# Acknowledgements
+
+# Conflict of Interest Statement
+
+# Data Availability Statement
+
 # Supplementary Material
@@
 ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
-The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
-the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
-2021).](../figs/ecs_plot.png){#sfig-ecs fig-align="center" width="10cm"}
+The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al., 2021).](../figs/ecs_plot.png){#sfig-ecs fig-align="center" width="10cm"}
 
-![Distribution of GBRMPA [-@GBRMPA2020] satellite derived depth data coverage levels across
-3806 possible reefs. Reefs below the 5% data coverage threshold (represented by the red
-vertical line) were removed from the
-investigation.](../figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
-fig-align="center" width="14.8cm" height="9.5cm"}
+![Distribution of GBRMPA [-@GBRMPA2020] satellite derived depth data coverage levels across 3806 possible reefs.
+Reefs below the 5% data coverage threshold (represented by the red vertical line) were removed from the investigation.](../figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff fig-align="center" width="14.8cm" height="9.5cm"}
 
-![Reef Degree Heating Week time series clustered within each management area, for each GCM
-analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2060 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2060 within each bioregion. Solid lines represent the cluster median time series and bands
-represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
-represented five times (for each GCM), with each GCM displayed
-horizontally.](../figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
-fig-align="center" width="14.82cm"}
+![Reef Degree Heating Week time series clustered within each management area, for each GCM analysed.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines represent the cluster median time series and bands represent the 2.5 to 97.5 percentile confidence intervals.
+Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](../figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories fig-align="center" width="14.82cm"}
 
@@
 
-![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by management area scale cluster assignment.
-Colour-coded areas outline GBR marine park management regions, where orange represents the
-Far Northern management region, green represents Cairns/Cooktown, red covers
-Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Reefs that do not have a consistent cluster
-assignment level across all GCMs at mangement area scale are coloured grey. All consistently
-clustered reefs are coloured according to their management area scale cluster assignment.
-Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
-cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
-investigation are represented in this figure. Annotations represent major coastal
-settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
-fig-align="center" width="14.82cm"}
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points), coloured by management area scale cluster assignment.
+Colour-coded areas outline GBR marine park management regions, where orange represents the Far Northern management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007].
+Reef centroids are marked individually for visual clarity.
+Reefs that do not have a consistent cluster assignment level across all GCMs at mangement area scale are coloured grey.
+All consistently clustered reefs are coloured according to their management area scale cluster assignment.
+Green represents reefs in the low cover cluster, orange represents reefs in the medium cover cluster and blue represents reefs in the high cover cluster.
+All 2429 reefs included in this investigation are represented in this figure.
+Annotations represent major coastal settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map fig-align="center" width="14.82cm"}
 
 ![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
-Green indicates a low cover cluster assignment, orange represents a medium cover assignment
-and blue represents assignment of a reef to a high coral cover cluster. The vertical width
-of reef elements varies depending on the number of reefs within the bioregion (displayed on
-the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
-ACCESS-CM2, NorESM2-MM and
-GFDL-CM4).](../figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
-fig-align="center" width="14.82cm"}
+Green indicates a low cover cluster assignment, orange represents a medium cover assignment and blue represents assignment of a reef to a high coral cover cluster.
+The vertical width of reef elements varies depending on the number of reefs within the bioregion (displayed on the y axis).
+The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5, ACCESS-CM2, NorESM2-MM and GFDL-CM4).](../figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment fig-align="center" width="14.82cm"}
 
-![Scatter plots indicating the bioregion test-prediction accuracy (proportion of reefs in
-each bioregion assigned correct clusters) from the Random Forest model. Plot panels
-represent the bioregion accuracy across various predictor ranges and bioregion attributes,
-such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength,
-Source-to-sink ratio and the number of reefs in each
-bioregion.](../figs/rf_performance_across_predictors.png){#sfig-rf-predictor-perf
-fig-align="center" width="14.82cm"}
+![Scatter plots indicating the bioregion test-prediction accuracy (proportion of reefs in each bioregion assigned correct clusters) from the Random Forest model.
+Plot panels represent the bioregion accuracy across various predictor ranges and bioregion attributes, such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength, Source-to-sink ratio and the number of reefs in each bioregion.](../figs/rf_performance_across_predictors.png){#sfig-rf-predictor-perf fig-align="center" width="14.82cm"}
 
-![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef
-connectivity relative standard deviation represents the reef standard deviation connection
-strength as a percentage of reef mean connection strength. Lighter colours indicate higher
-RSD % values.](../figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
-fig-align="center" width="14.82cm"}
+![Heatmap indicating reef connectivity relative standard deviation (RSD %).
+Reef connectivity relative standard deviation represents the reef standard deviation connection strength as a percentage of reef mean connection strength.
+Lighter colours indicate higher RSD % values.](../figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd fig-align="center" width="14.82cm"}
 
@@
 
-The CoralBlox model incorporates linear extension (growth) and background mortality rates
-that are dependent on the size and functional group of a coral colony. Environmental
-disturbances and reproduction are not directly considered within CoralBlox. Instead, these
-factors are considered by making changes to the distribution of colonies within CoralBlox
-timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform
-[@iwanaga2023]. Within ADRIA, we incorporate coral life history and environmental events in
-the following order: coral colony growth; coral reproduction; larval connectivity and
-settlement; and coral bleaching due to heat stress. As ADRIA and CoralBlox are coupled
-together to represent the system, we refer to both as ADRIA-CoralBlox.
+The CoralBlox model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
+Environmental disturbances and reproduction are not directly considered within CoralBlox.
+Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
+Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
+As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.
 
-Coral fecundity rates are dependent on colony size and functional group following the
-results of Hall & Hughes [-@hall1996]. Coral fertilization rates are not considered within
-this model, however larval survival and viability are incorporated in connectivity modelling
-(see Connectivity modelling). Viable larvae settle at a reef location and are incorporated
-into the model as the smallest size class but are not directly impacted by modelled
-bleaching mortality. There has been contrasting evidence for juvenile corals being immune to
-thermal bleaching events [@depczynski2013], we assume the high background mortality of
-juveniles includes thermal stress [@álvarez-noriega2018].
+Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996].
+Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
+Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality.
+There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
 
@@
 
-Scenarios were sampled from the range of environmental and ecological factors using the
-low-discrepancy Sobol' sampling method [@sobol1967; @sobol1993] with Owen scrambling
-[@owen1995]. A base of 2 and padding of 32 is used for the Owen scrambling. Ecological
-factors were sampled using a +/- 10% range relative to their nominal (assumed best guess)
-value.
+Scenarios were sampled from the range of environmental and ecological factors using the low-discrepancy Sobol' sampling method [@sobol1967; @sobol1993] with Owen scrambling [@owen1995].
+A base of 2 and padding of 32 is used for the Owen scrambling.
+Ecological factors were sampled using a +/- 10% range relative to their nominal (assumed best guess) value.
 
@@
 
-In this investigation we model five functional groups common to the GBR, tabular Acropora,
-corymbose Acropora, corymbose non-Acropora, small massives and large massives. We do not
-model arborescent Acropora forms due to their distinct life history from other morphological
-groups. CoralBlox uses user-defined size classes that influence size-dependent growth and
-mortality rates, through which the coral colonies progress as they grow in diameter. Within
-ADRIA, we define the distributions of these parameters, and the size classes based on
-ecological monitoring data from the Ecological Intelligence for Reef Restoration Program
-(EcoRRAP) ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
+In this investigation we model five functional groups common to the GBR, tabular Acropora, corymbose Acropora, corymbose non-Acropora, small massives and large massives.
+We do not model arborescent Acropora forms due to their distinct life history from other morphological groups.
+CoralBlox uses user-defined size classes that influence size-dependent growth and mortality rates, through which the coral colonies progress as they grow in diameter.
+Within ADRIA, we define the distributions of these parameters, and the size classes based on ecological monitoring data from the Ecological Intelligence for Reef Restoration Program (EcoRRAP) ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
 
-In ADRIA we track the thermal tolerance of each functional group and size class as a
-truncated normal distribution that is updated in each timestep following growth and
-recruitment. This distribution determines the proportion of the population on a reef that is
-susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
+In ADRIA we track the thermal tolerance of each functional group and size class as a truncated normal distribution that is updated in each timestep following growth and recruitment.
+This distribution determines the proportion of the population on a reef that is susceptible to bleaching (i.e.
+has a thermal threshold below the experienced DHW value).
 Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
@@
 
-The CID timeseries clustering metric corrects the Euclidean distance between pairs of time
-series (which accounts for magnitude differences) with the complexity of each time series
-(obtained through a measure of their variability) to ensure reefs are clustered based on
-their underlying temporal dynamics rather than simply their average coral cover. The process
-creates a distance matrix of n \* n dimensions (where n is the number of time series in the
-group) that is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The
-three reef clusters are labelled with qualitative-ordered clusters from Low, Medium and
-High based on their median cover relative to each other cluster over the 2030-2060 period.
-The selected time frame prevents the classification from being overly influenced by any
-steep declines in the initial years of simulations and avoids the post-2060 time period
-where reefs are projected to be under severe stress and in a declined state [@bozec2025].
+The CID timeseries clustering metric corrects the Euclidean distance between pairs of time series (which accounts for magnitude differences) with the complexity of each time series (obtained through a measure of their variability) to ensure reefs are clustered based on their underlying temporal dynamics rather than simply their average coral cover.
+The process creates a distance matrix of n \* n dimensions (where n is the number of time series in the group) that is clustered using a k-medoids clustering algorithm [cf.
+@steinmann2020].
+The three reef clusters are labelled with qualitative-ordered clusters from Low, Medium and High based on their median cover relative to each other cluster over the 2030-2060 period.
+The selected time frame prevents the classification from being overly influenced by any steep declines in the initial years of simulations and avoids the post-2060 time period where reefs are projected to be under severe stress and in a declined state [@bozec2025].
 
@@
 Point colours represent the mean number of years each reef maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover.
-Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
-fig-align="center" width="10cm"}
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget fig-align="center" width="10cm"}
 
@@
 
-![Reef area-relative coral cover time series clustered within each bioregion. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
-each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2060 within each
-bioregion. Solid lines represent the cluster median time series and bands represent the 95th
-percentile confidence intervals. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
-fig-align="center" width="14.82cm"}
+![Reef area-relative coral cover time series clustered within each bioregion.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines represent the cluster median time series and bands represent the 95th percentile confidence intervals.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries fig-align="center" width="14.82cm"}
 
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion,
-separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines represent the median cover – DHW correlation level for each cluster and bands
-represent the distribution of correlation levels within each cluster. Displays results for
-ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor
-fig-align="center" width="14.82cm"}
+![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by time series clustering.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines represent the median cover – DHW correlation level for each cluster and bands represent the distribution of correlation levels within each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor fig-align="center" width="14.82cm"}
 
-![Mean time series DHW values for reefs within each bioregion, separated into clusters
-assigned by time series clustering. ‘Low’ clusters (green) are clusters with the lowest
-median area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters
-(orange) are clusters with intermediate median area-relative cover between 2030 and 2060
-within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the
-median DHW level for each cluster and bands represent the distribution of mean DHW levels
-within each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
-fig-align="center" width="14.82cm"}
+![Mean time series DHW values for reefs within each bioregion, separated into clusters assigned by time series clustering.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines represent the median DHW level for each cluster and bands represent the distribution of mean DHW levels within each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean fig-align="center" width="14.82cm"}
 
-![Initial proportion of coral habitable area occupied by corals for reefs within each
-bioregion, separated into clusters assigned by time series clustering. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
-each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2060 within each
-bioregion. Solid lines represent the median proportion of habitable area occupied for each
-cluster and bands represent the distribution of occupied area values within each cluster.
-Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion
-fig-align="center" width="14.82cm"}
+![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by time series clustering.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines represent the median proportion of habitable area occupied for each cluster and bands represent the distribution of occupied area values within each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion fig-align="center" width="14.82cm"}
 
-![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median source-to-sink ratio for each cluster and
-bands represent the distribution of source-to-sink ratios within each cluster. The vertical
-grey line represent a source-to-sink ratio of 0 (in base-10 log scale) indicating equal
-outgoing and incoming connectivity levels. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
-fig-align="center" width="14.82cm"}
+![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion, separated into clusters assigned by time series clustering.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines within each violin represent the median source-to-sink ratio for each cluster and bands represent the distribution of source-to-sink ratios within each cluster.
+The vertical grey line represent a source-to-sink ratio of 0 (in base-10 log scale) indicating equal outgoing and incoming connectivity levels.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi fig-align="center" width="14.82cm"}
 
-![Weighted incoming connectivity (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median base-10 log of weighted incoming connectivity for
-each cluster and bands represent the distribution of connectivity values within
-each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_incoming_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedincoming
-fig-align="center" width="14.82cm"}
+![Weighted incoming connectivity (in base-10 log scale) for reefs within each bioregion, separated into clusters assigned by time series clustering.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines within each violin represent the median base-10 log of weighted incoming connectivity for each cluster and bands represent the distribution of connectivity values within each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_incoming_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedincoming fig-align="center" width="14.82cm"}

### 2025-08-26 paper/paper_draft.qmd
Add canonical reefs repo
Update formatting of abstract
Add to document settings to ensure that switching to visual mode not req
This should mean that you don't have to switch to visual mode to fix document line formatting.
https://quarto.org/docs/visual-editor/options.html#file-options

@@
     maintenance of positive carbonate budgets, with deeper reefs benefiting from thermal
-    refugia that reduce bleaching impacts. Interaction between reef depth and incoming connectivity was found to influence reef temporal behaviour. Our findings suggest that depth provides critical
-    protection against thermal stress, contrasting current restoration practices that primarily
-    target easily accessible shallow sites. These results have important implications for
-    reef management, indicating that depth refugia should be prioritized for further
-    consideration in conservation planning alongside connectivity considerations to maximize
-    coral survival under continuing climate change.
+    refugia that reduce bleaching impacts. Interaction between reef depth and incoming 
+    connectivity was found to influence reef temporal behaviour. Our findings suggest that 
+    depth provides critical protection against thermal stress, contrasting current restoration
+    practices that primarily target easily accessible shallow sites. These results have 
+    important implications for reef management, indicating that depth refugia should be 
+    prioritized for further consideration in conservation planning alongside connectivity 
+    considerations to maximize coral survival under continuing climate change.
 keywords:
@@
     wrap: 92
+    canonical: true
 ---
@@
 The median depth was used to provide an indicative depth value for each reef.
-Code, and the resulting depth estimates, are available at **\[cite Canonical Reefs repo\]**.
+Code, and the resulting depth estimates, are available at [@iwanaga2025].
 

### 2025-08-28 paper/paper_draft.qmd
Initial paper updates to incorporate tracked changes in online draft

@@
     Coral reefs globally face unprecedented threats from climate change, with the Great Barrier
-    Reef (GBR) experiencing severe declines in coral cover from thermal stress events.
+    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral cover from thermal stress events.
     Understanding drivers behind reef resilience to climate impacts is critical for conservation
@@
     Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities,
-    we analysed reef cover time series and the ability of reefs to maintain positive carbonate
+    we analysed reef coral cover time series and the ability of reefs to maintain positive carbonate
     production budgets under future conditions. Contrary to expectations, larval connectivity
@@
 
-Climate change is impacting species survival, persistence and ecosystem functions globally, including coral reefs.
-Coral reefs are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading [@foster2021; @gattuso2014].
-Mass bleaching and mortality events linked to climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
-Climate impacts on coral reefs are, and will continue to, decrease the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well as ecosystem services such as food, protection, tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
+Climate change is impacting species survival, persistence and ecosystem functions globally.
+This is particularly true for coral reefs, which are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading [@foster2021; @gattuso2014].
+Mass bleaching and mortality events driven by climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
+Climate impacts on coral reefs are decreasing the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well as ecosystem services such as food, protection, tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
 
@@
 The GBR faces severe projected coral cover declines under climate change [@bozec2025; @bozec2022].
-These coral cover declines will be compounded by ocean acidification, intensifying tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
+These coral cover declines will be compounded by ocean acidification, tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
 The 2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs) [@cantin2024].
@@
 Environmental factors can either amplify or reduce thermal stress exposure.
-Depth has been suggested as one crucial factor that can provide a refuge from thermal stress [@álvarez-noriega2018; @baird2018; @smith2014].
+Depth is a crucial factor that can provide a refuge from thermal stress [@álvarez-noriega2018; @baird2018; @smith2014].
 Biological factors including coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and thermal tolerance through acclimation and inheritance [@humanes2022; @lachs2024] all influence survival outcomes.
@@
 This depth-scaling reduces the proportion of coral colonies impacted by high heat stress as depth increases.
-The impacts of tropical cyclones and wave activity on reefs were not included in this investigation.
+The impacts of tropical cyclones, wave activity, Crown of Thorns Starfish or coral disease were not included in this investigation, in order to focus on assessing reef resilience under possible future warming scenarios.
 
@@
 The Complexity-Invariant Distance (CID) between each time series was calculated to identify similarities in temporal behaviour [@batista2014].
-The CID applies a correction factor to the Euclidean distance between pairs of time series to obtain a measure of their similarity or dissimilarity.
+The CID applies a correction factor to the Euclidean distance between pairs of time series to obtain a measure of their similarity.
 The adopted approach ensures reefs are clustered based on their temporal dynamics as opposed to, for example, naively clustering by their mean coral cover.

### 2025-09-02 paper/paper_draft.qmd
Various paper updates
Updated:
- abstract to show interaction with incoming connectivity
- exploratory modelling references
- supplementary figure showing the interaction between depth and outgoing connectivity
- Add initial discussion paragraph outlining high level findings
- Move GCM discussion to later in the flow (need to check if it still flows ok)
- Added discussion around outgoing connectivity and the potential for managers to target reefs with high depth, incoming connectivity and outgoing connectivity
- Added limitation caveat: We did not include depth effects on growth due to decreas

@@
     connectivity was found to influence reef temporal behaviour. Our findings suggest that 
-    depth provides critical protection against thermal stress, contrasting current restoration
-    practices that primarily target easily accessible shallow sites. These results have 
+    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the performance of deep reefs, contrasting current restoration
+    practices that primarily target easily accessible sites in the 1-10m depth range. These results have 
     important implications for reef management, indicating that depth refugia should be 
@@
 This is particularly true for coral reefs, which are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading [@foster2021; @gattuso2014].
-Mass bleaching and mortality events driven by climate change can cause reef-building coral population declines, possibly leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
+Mass bleaching and mortality events driven by climate change can cause reef-building coral population declines [@hughes2017; @hughes2018; @bozec2025], possibly leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
 Climate impacts on coral reefs are decreasing the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well as ecosystem services such as food, protection, tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
@@
 First, the ability of individual corals to survive thermal stress.
-Second, the connectivity networks that enable recolonisation after disturbances.
-Third, the maintenance of the carbonate framework that provides reef structure.
+Second, the connectivity networks that enable recolonisation after disturbances [@hock2017; @mumby2008; @torres2024].
+Third, the maintenance of the carbonate framework that provides reef structure [@perry2012].
 We aim to assess how these mechanisms interact under projected climate conditions to identify the characteristics of structurally resilient reefs through scenario-based coral population modelling for the Great Barrier Reef ecosystem.
@@
 The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of thousands of individual reefs.
-They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@grimaldi2022].
-The GBR faces severe projected coral cover declines under climate change [@bozec2025; @bozec2022].
+They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@cappo2000].
+The GBR faces severe projected coral cover declines under climate change [@bozec2025; @bozec2022; @condie2021].
 These coral cover declines will be compounded by ocean acidification, tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
-The 2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs) [@cantin2024].
+The 2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs) [@australianinstituteofmarinescience2024]; @cantin2024\].
 
@@
 
-An exploratory scenario modelling approach was adopted for this investigation.
-The method involves exploring a wide range of plausible futures under different assumptions of environmental (climatic) conditions and ecological factors.
-Exploratory scenario modelling embraces uncertainty as an inherent characteristic of complex environmental systems [@lempert2010] and is a core methodology underpinning the development of robust and adaptive management strategies [@haasnoot2013].
-
-Exploratory modelling approaches have gained favour in recent years as precise long-term predictions of future conditions are often impossible in complex systems like coral reefs.
+We adapted exploratory scenario modelling approach from robust decision making (RDM) approaches for this investigation.
+In particular, we used parameter sampling and exploratory modelling to investigate a wide range of plausible futures under different assumptions of environmental (climatic) conditions and ecological factors.
+Exploratory modelling approaches have gained favour in recent years as precise long-term predictions of future conditions are often impossible in complex ecological systems [@conradt2024; @lempert2013].
+RDM embraces uncertainty as an inherent characteristic of complex environmental systems [@lempert2010; @lempert2013] and is a core methodology underpinning the development of robust and adaptive management strategies [@haasnoot2013].
+Rather than attempting to forecast specific outcomes, RDM aims to systematically explore many possible futures to identify patterns.
+Allowing for the identification of robust management strategies that perform well across those diverse conditions, as well as conditions in which such strategies may fail.
 Multiple interacting and compounding sources of uncertainty, and a lack of broad agreement as to their likelihood, create inherently uncertain outcomes.
-Rather than attempting to forecast specific outcomes, exploratory modelling aims to systematically explore many possible futures to identify patterns.
-Allowing for the identification of robust management strategies that perform well across those diverse conditions, as well as conditions in which such strategies may fail.
-Such an exploratory approach lends itself well to the purpose of the investigation.
-Specifically, to assess the role of thermal stress, connectivity, and depth to identify the environmental and reef characteristics that support structural resilience.
+While we did not directly model management decision making in this investigation, we used exploratory modelling to identify the environmental and reef characteristics, such as thermal stress, depth and connectivity, that support favourable outcomes such as recovery and resilience.
 
@@
 
-To apply exploratory scenario modelling, we employed a modelling framework involving two separate systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and CoralBlox.
+To apply exploratory scenario modelling, we employed a framework involving two separate systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and CoralBlox.
 ADRIA is a multi-criteria decision support platform designed to help reef managers address climate change challenges in coral reef systems [@iwanaga2023].
@@
 Reefs in each time series cluster were compared to identify characteristics that differ between Low, Medium and High clusters.
-These characteristics include reef median depth, mean time series DHW, Pearson’s correlation between total coral cover and inverse DHW time series, proportion of coral habitable area occupied by corals in the first timestep, ratio of source-to-sink larval connectivity and weighted incoming connectivity.
+These characteristics include reef median depth, mean time series DHW, ratio of source-to-sink larval connectivity, weighted incoming connectivity, weighted outgoing connectivity and reef carrying capacity (coral habitable area).
 
@@
 
-In many bioregions reefs in the Low cluster have the lowest correlation between coral cover and inverse-DHW time series whereas reefs in the High cluster were found to have the strongest correlation (@sfig-access-esm1-5-bioregion-dhwcor).
-Across six of the 29 bioregions reef mean DHW levels increased as cluster cover decreased (@sfig-access-esm1-5-bioregion-dhwmean).
-There were no consistent patterns across bioregions in their reefs' initial proportion of habitable area occupied by corals and cluster assignment (@sfig-access-esm1-5-bioregion-initialproportion).
+Across six of the 29 bioregions reefs in the high cover cluster have lower mean DHW, Log-10 carrying capacity and Log-10 weighted outgoing connectivity values than reefs in other clusters (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-esm1-5-bioregion-carrying-capacity; @sfig-access-esm1-5-bioregion-weightedoutgoing).
+There were no consistent patterns across bioregions in their reefs' Log-10 coral carrying capacity area and cluster assignment (@sfig-access-esm1-5-bioregion-carrying-capacity).
 Across most bioregions there were not consistent differences between clusters in connectivity metrics such as Log-10 source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming).
@@
 
-Analyses for source-to-sink ratio and weighted incoming and outgoing connectivity metrics suggest that reefs with greater outgoing connectivity and lower incoming connectivity levels have higher probability of being clustered into the Low cluster category compared to other reefs.
-Additionally, two-way analyses revealed an interaction between reef depth and incoming connectivity in determining cluster category assignment, particularly at the high depth range (@fig-ts-cluster-pdp-twoway).
-Two-way analyses revealed that reefs at greater than 10m depth are unlikely to be clustered into the Low cluster category, regardless of their incoming connectivity levels.
-However, at greater than 10m depth reefs with higher incoming connectivity are more likely to be assigned to a High cluster, while reefs with low incoming connectivity are more likely to be assigned to a Medium cover cluster (@fig-ts-cluster-pdp-twoway).
-
-Individual feature analysis for carrying capacity indicates that its influence on cluster assignment is concentrated at the low range of predictor values (@fig-ts-cluster-pdp).
-This aligns with the right-skewed distribution of carrying capacity across reefs for these three predictor variables.
-Beyond this low-end range, the partial dependence becomes near constant, contrary to their feature importance scores which suggest these characteristics do contribute important information to predictions.
-The contrasting outcomes indicate that interactions between other reef characteristics are driving behaviour rather than a strong influence from a single individual characteristic.
-
-Assessing random forest prediction accuracy across predictor values, summarised by bioregions, reveals increasing performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf).
-This highlights that there may be unexplained variation between reefs in shallow bioregions that contributes to cluster assignment and reef cover outcomes but is not captured by our included predictor variables.
-
 ![Feature importance scores (Panel A) of the Random Forest classifier, and Partial Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a reef being classified to one of the three clusters (Panel B).
@@
 
+Analyses for source-to-sink ratio and weighted incoming and outgoing connectivity metrics suggest that reefs with greater outgoing connectivity and lower incoming connectivity levels have higher probability of being clustered into the Low cluster category compared to other reefs.
+Additionally, two-way analyses revealed an interaction between reef depth and incoming connectivity in determining cluster category assignment, particularly at the high depth range (@fig-ts-cluster-pdp-twoway-incoming).
+Two-way analyses revealed that reefs at greater than 10m depth are unlikely to be clustered into the Low cluster category, regardless of their incoming connectivity levels.
+However, at greater than 10m depth reefs with higher incoming connectivity are more likely to be assigned to a High cluster, while reefs with low incoming connectivity are more likely to be assigned to a Medium cover cluster (@fig-ts-cluster-pdp-twoway-incoming).
+Two-way analyses, for depth and weighted outgoing connectivity, revealed a slight interaction with the increased low-cluster probability for reefs of high outgoing connectivity primarily concentrated in shallow reefs, while deep reefs with high outgoing connectivity have the greatest probability of being clustered into a high cover cluster (@sfig-ts-cluster-pdp-twoway-outgoing).
+
 ![Partial dependence plot indicating the probability of cluster assignment along interacting values of median reef depth (metres) and Log10 weighted incoming connectivity.
@@
 Probability values for each cluster are generated by the random forest classifier using each combination of depth and incoming connectivity values along the axes at 50 grid points.
-The actual distributions of depth and incoming connectivity values for reefs are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_conn_pdp.png){#fig-ts-cluster-pdp-twoway fig-align="center" width="14.82cm"}
+The actual distributions of depth and incoming connectivity values for reefs are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_incomingconn_pdp.png){#fig-ts-cluster-pdp-twoway-incoming fig-align="center" width="14.82cm"}
+
+Individual feature analysis for carrying capacity indicates that its influence on cluster assignment is concentrated at the low range of predictor values (@fig-ts-cluster-pdp).
+This aligns with the right-skewed distribution of carrying capacity across reefs for these three predictor variables.
+Beyond this low-end range, the partial dependence becomes near constant, indicating that outlier values for these factors are not influential.
+
+Assessing random forest prediction accuracy across bioregions, reveals increasing performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf).
+This highlights that unexplained variation in the test dataset (33% of variation) may be concentrated in shallow bioregions where the available model predictors do not capture differences between clustered reefs.
 
@@
 Decreasing correlation levels are likely due to an increasing number of reefs being unable to maintain coral cover above $\theta_0$ as it is increased, with the distribution of years above threshold becoming increasingly right-skewed (@fig-access-esm1-5-depth-conn-carbonate).
-In contrast, log10-transformed total connectivity strength ($\text{log10}(S)$) was found to have no correlation with the number of years a reef maintains cover above the required thresholds (@fig-access-esm1-5-depth-conn-carbonate).
-The correlation between $\text{log10}(S)$ and $\theta_0$ slightly increased as the assumed threshold for $\theta_0$ increased.
+In contrast, weighted incoming connectivity strength (Log-10 scale) was found to have no correlation with the number of years a reef maintains cover above the required thresholds (@fig-access-esm1-5-depth-conn-carbonate).
 
@@
 The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef variables (depth - left and Log-10 connectivity strength - right) and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents the median reef depth in metres in the left-hand panel, and Log-10 total connectivity strength in the right-hand panel.
+Bracketed x-axis values represent the Spearman's correlation between reef variables (depth - left and Log-10 weighted incoming connectivity - right) and the number of years cover exceeds the carbonate budget threshold.
+Point colour represents the median reef depth in metres in the left-hand panel, and Log-10 weighted incoming connectivity in the right-hand panel.
 Red points represent the mean number of years above an assumed carbonate budget threshold across reefs.
-Deeper reefs are better able to maintain cover above the indicative carbonate budget threshold, while there is no considerable relationship between connectivity strength and carbonate budget maintenance.
+Deeper reefs are better able to maintain cover above the indicative carbonate budget threshold, while there is no considerable relationship between weighted incoming connectivity and carbonate budget maintenance.
 Displays results from median time series using ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate fig-align="center" width="14.82cm"}
@@
 
-Under all GCMs many reefs are projected to suffer substantial declines in coral cover relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the lowest cover level cluster at the management area scale across GCMs.
-NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future.
-Differences between Low, Medium and High reef clusters in cover time series are most notable under these two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories).
-Maintenance of coral cover into the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of future recovery and timespan of cover maintenance increase as GCM ECS increases (@fig-gcm-cover-trajectories).
-Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2) large declines and lower rates of recovery in high cover clusters are common compared to lower-ECS GCMs.
+Our results show increasing reef depth has a strong positive impact on modelled reef resilience in temporal behaviour and maintenance of positive carbonate budgets under possible future conditions.
+Reefs with a median depth of 10m or greater, with high incoming connectivity, are the most likely to be assigned to a high cover time series cluster.
+As an individual feature, incoming connectivity alone does not correlate with maintenance of positive carbonate budgets.
+These findings highlight the importance of depth and incoming connectivity as coupled selection features when assessing potential reef resilience under future thermal stress.
 
-The large differences in cover time series seen across the GCMs suggest that it is important to consider uncertainty in future conditions when assessing possible biological responses to change.
-This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model responses using GCMs separately [@shepherd2018].
-Despite large differences in coral cover across GCMs, the patterns identified between low, medium and high clusters of reefs suggest that the relative importance of environmental and biological factors such as depth refugia, connectivity and surface DHW levels is consistent across scenarios.
-
-Reefs in different clusters largely do not differ in mean modelled DHW levels experienced and exhibit overall similar DHW time series.
+Reefs in different temporal clusters largely do not differ in mean modelled DHW levels experienced and exhibit overall similar DHW time series.
 While these reefs experience similar magnitude DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress events depends on reef depth.
@@
 As detailed previously, estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution) which can be subject to high degrees of uncertainty, both in terms of the estimated depth at for each pixel as well as their alignment to the established GBRMPA reef outlines.
+Additionally, we do not incorporate the light-based
 
@@
 Our results suggest that of the assessed reefs occurring within the 1-10m depth range (1736 reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the GBRMPA management region scale), with many unable to maintain positive carbonate budgets under future conditions.
-Partial dependence analysis revealed a range of depths from 10-15m where the probability of a reef being clustered into the High cover cluster increased substatially.
+Partial dependence analysis revealed a range of depths from 10-15m where the probability of a reef being clustered into the High cover cluster increased substantially.
 Additionally, two-way partial dependence analysis revealed that high incoming connectivity is important for High cluster assignment for reefs at depths of \>10m.
 Considering this 10-15m depth range, and targetting well connected reefs, when assessing possible restoration sites may reduce the exposure of planted and seeded corals to high thermal stress, while still maintaining effective logistical access to sites.
-Although transient, and difficult to measure, properties such as reef connectivity are likely to increase uncertainty in intervention planning to a greater degree than environmental characteristics such as reef depth.
-Reef intervention planning is a complex and challenging decision-making process [@anthony2020], and our results suggest that deployment site depth may be an important factor to additionally consider when assessing the long-term resilience of sites.
+Managers are also likely to consider the positive potential for flow on effects due to outgoing connectivity when selecting intervention sites [@hock2017].
+While reefs with high outgoing connectivity levels were found to have greater probability of being assigned to low cover clusters when assessed individually (@fig-ts-cluster-pdp-twoway-incoming), within the context of reef depth, reefs with high depths and high outgoing connectivity levels had the greatest probability of being clustered into high cover clusters (@sfig-ts-cluster-pdp-twoway-outgoing).
+These results suggests that interventions targetting deep reefs will also benefit from high incoming and outgoing connectivity levels, allowing for high potential for site resilience and outgoing flow of benefits and recovery.
+Transient, and difficult to measure, properties such as reef connectivity are likely to increase uncertainty in intervention planning to a greater degree than environmental characteristics such as reef depth.
+Overall, reef intervention planning is a complex and challenging decision-making process [@anthony2020], and our results suggest that intervention site depth may be an important factor to additionally consider when assessing the long-term resilience of sites.
 
@@
 
+Under all GCMs many reefs are projected to suffer substantial declines in coral cover relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the lowest cover level cluster at the management area scale across GCMs.
+NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future.
+Differences between Low, Medium and High reef clusters in cover time series are most notable under these two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories).
+Maintenance of coral cover into the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of future recovery and timespan of cover maintenance increase as GCM ECS increases (@fig-gcm-cover-trajectories).
+Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2) large declines and lower rates of recovery in high cover clusters are common compared to lower-ECS GCMs.
+
+The large differences in cover time series seen across the GCMs suggest that it is important to consider uncertainty in future conditions when assessing possible biological responses to change.
+This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model responses using GCMs separately [@shepherd2018].
+Despite large differences in coral cover across GCMs, the patterns identified between low, medium and high clusters of reefs suggest that the relative importance of environmental and biological factors such as depth refugia, connectivity and surface DHW levels is consistent across scenarios.
+
 ## Limitations
@@
 We model coral colonies as circular diameter values that are tracked over timesteps through growth.
-Additionally, we do not model the direct influence of light intensity on coral growth or the negative influence of depth on coral growth rates due to reduced light levels.
-\[**BG: Include citations for influence of depth/light on growth rates**\].
-If included in this investigation, it is possible that reef recovery ability would be reduced at greater depths even though corals at these depths experience refugia from thermal stress.
+Additionally, we do not model the direct influence of light intensity on coral growth or the negative influence of depth on coral growth rates due to reduced available light levels.
+[@baker1975; @huston1985; @ruiz-diaz2022].
+If included in this investigation, it is possible that reef recovery ability would be reduced at greater depths, reducing the positive effect of depth refugia for temporal resilience.
+Additionally, reduced growth rates at increased depths may reduce the carbonate budget maintenance of reefs due to lower rates of CaCO~3~ accretion.
 Due to the availability of quality future projected data we do not consider other important impacts such as waves, cyclones, currents and Crown of Thorns Starfish (CoTS) on coral colony survival and bleaching [@massel1993; @deaker2022].
@@
 
+| Metric | Used in | Definition | Justification |
+|------------------|------------------|------------------|------------------|
+| Percentage coral cover time series | Timeseries clustering, Carbonate budget analysis | Total coral cover as a percentage of reef area | To summarise coral population health over time |
+| Median depth | Time series cluster assessment Carbonate budget analysis | Reef median depth as calculated with zonal raster analysis | Depth is a critical form of environmental refugia from high thermal stress |
+| Mean time series DHW | Time series cluster assessment | Reef mean DHW value across time series | Resilient reefs may experience reduced surface DHWs |
+| Source - to - sink connectivity ratio | Time series cluster assessment | Ratio of reef outgoing to incoming connectivity | Reefs with greater source than sink connectivity may have lower recovery |
+| Weighted incoming connectivity | Time series cluster assessment, Carbonate budget analysis | Incoming connectivity strength weighted by mean time series coral cover of source reefs | High incoming larval flow assists reef recovery |
+| Weighted outgoing connectivity | Time series cluster assessment | Outgoing connectivity strength weighted by mean coral cover | High outgoing larval flow may lower recovery capacity of the target reef |
+| Carrying capacity | Time series cluster assessment | Reef habitable area \[m^2^\] | Captures the size of the viable reef extent |
+
+: Quantitative metrics used in this investigation
+
 ```{julia}
@@
 The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5, ACCESS-CM2, NorESM2-MM and GFDL-CM4).](../figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment fig-align="center" width="14.82cm"}
+
+![Partial dependence plot indicating the probability of cluster assignment along interacting values of median reef depth (metres) and Log10 weighted outgoing connectivity.
+Colour indicates the probability of assignment to each cluster, with lighter colours indicating higher probability of assignment.
+Panel A shows the probability of assignment for the Low cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability for the High cluster category.
+Probability values for each cluster are generated by the random forest classifier using each combination of depth and weighted outgoing connectivity values along the axes at 50 grid points.
+The actual distributions of depth and outgoing connectivity values for reefs are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_outgoingconn_pdp.png){#sfig-ts-cluster-pdp-twoway-outgoing fig-align="center" width="14.82cm"}
 
@@
 
-![Total coral cover – DHW Pearson’s correlation levels for reefs within each bioregion, separated into clusters assigned by time series clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines represent the median cover – DHW correlation level for each cluster and bands represent the distribution of correlation levels within each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/dhw_cover_cor_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwcor fig-align="center" width="14.82cm"}
-
 ![Mean time series DHW values for reefs within each bioregion, separated into clusters assigned by time series clustering.
@@
 
-![Initial proportion of coral habitable area occupied by corals for reefs within each bioregion, separated into clusters assigned by time series clustering.
+![Reef carrying capacity (coral habitable area, in base-10 log scale) for reefs within each bioregion, separated into clusters assigned by time series clustering.
 ‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
@@
 ‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines represent the median proportion of habitable area occupied for each cluster and bands represent the distribution of occupied area values within each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/initial_proportion_bioregion_violin.png){#sfig-access-esm1-5-bioregion-initialproportion fig-align="center" width="14.82cm"}
+Solid lines represent the median carrying capacity for each cluster and bands represent the distribution of values within each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/carrying_capacity_bioregion_violin.png){#sfig-access-esm1-5-bioregion-carrying-capacity fig-align="center" width="14.82cm"}
 
@@
 Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_incoming_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedincoming fig-align="center" width="14.82cm"}
+
+![Weighted outgoing connectivity (in base-10 log scale) for reefs within each bioregion, separated into clusters assigned by time series clustering.
+‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
+‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
+Solid lines within each violin represent the median base-10 log of weighted outgoing connectivity for each cluster and bands represent the distribution of connectivity values within each cluster.
+Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_outgoing_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedoutgoing fig-align="center" width="14.82cm"}

### 2025-09-03 src/ADRIA/HighResCoralStress/5_publication_plots.jl
Update the order of DHW timeseries methods plot

@@ -35,9 +35,11 @@ dhw_arrays = [
 dhw_arrays = concatenatecubes(dhw_arrays, Dim{:GCM}(GCMs))
 dhw_arrays = rebuild(dhw_arrays, metadata=dhw_timeseries_properties)
 
-context_layers = sort(context_layers, :management_area)
+context_layers = sort(context_layers, [:management_area_average_latitude]; rev=true)
 
-dhw_arrays = dhw_arrays[sites=At(context_layers.UNIQUE_ID)]
+GCMs = collect(keys(sort(ecs_values, byvalue=true, rev=true)))
+
+dhw_arrays = dhw_arrays[sites=At(context_layers.UNIQUE_ID), GCM=At(GCMs)]
 
 fig = Figure(
     size=(fig_sizes["gcm_timeseries_width"], fig_sizes["gcm_timeseries_height"] * 1.3),
@@ -89,7 +91,7 @@ map(x -> hideydecorations!(x, ticks=false, ticklabels=false, grid=false), filter
 linkaxes!(filter(x -> x isa Axis, fig.content)...)
 
 legend_entries = []
-for (i, col) in enumerate([:green, :orange, :blue, :red])
+for (i, col) in enumerate([:orange, :green, :red, :blue])
     LE = LineElement(; color=col, marker=:circle)
     push!(legend_entries, [LE])
 end
@@ -97,7 +99,7 @@ end
 Legend(
     fig[length(GCMs)+1, 1],
     legend_entries,
-    levels(man_areas_categorical),
+    ["Far Northern", "Cairns/Cooktown", "Mackay/Capricorn", "Townsville/Whitsunday"],
     nbanks=2,
     tellwidth=false,
     padding=(2.0, 2.0, 2.0, 2.0),             # shrink padding inside legend box

### 2025-09-03 paper/paper_draft.qmd
Paper updates from comments
- move to 'intervention' instead of 'restoration'
- Expand more on connectivity interactions with depth and expand on the findings relating to the most suitable targeting strategies for further investigation (need to add in input maps)
- Add section about the need for connectivity model comparisons as well as validation of models and increased yearly sample sizes to improve confidence in connectivity modelling

@@
     connectivity was found to influence reef temporal behaviour. Our findings suggest that 
-    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the performance of deep reefs, contrasting current restoration
+    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the performance of deep reefs, contrasting current intervention
     practices that primarily target easily accessible sites in the 1-10m depth range. These results have 
@@
 
-Current reef restoration and intervention-investigation efforts on the GBR, such as deployment of coral seeding and fragment devices, target reefs with suitable restoration sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024].
-While there are no explicit justifications for this depth range, restoration depth is likely constrained by snorkelling and diving deployment and monitoring logistical accessibility, visual identification of sites from the surface, in combination with tourism return value.
+Current reef restoration and intervention investigation efforts on the GBR, such as deployment of coral seeding and fragment devices, target reefs with suitable sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024].
+While there are no explicit justifications for this depth range, intervention depth is likely constrained by snorkelling and diving deployment and monitoring logistical accessibility, visual identification of sites from the surface, in combination with tourism return value.
 Our results suggest that of the assessed reefs occurring within the 1-10m depth range (1736 reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the GBRMPA management region scale), with many unable to maintain positive carbonate budgets under future conditions.
@@
 Additionally, two-way partial dependence analysis revealed that high incoming connectivity is important for High cluster assignment for reefs at depths of \>10m.
-Considering this 10-15m depth range, and targetting well connected reefs, when assessing possible restoration sites may reduce the exposure of planted and seeded corals to high thermal stress, while still maintaining effective logistical access to sites.
+Considering this 10-15m depth range, and targetting well connected reefs, when assessing possible intervention sites may reduce the exposure of planted and seeded corals to high thermal stress, while still maintaining effective logistical access to sites.
 Managers are also likely to consider the positive potential for flow on effects due to outgoing connectivity when selecting intervention sites [@hock2017].
@@
 
-It is a common conclusion in coral reef ecology that a primary facet of reef resilience is the degree of larval connectivity between reefs and the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008; @torres2024].
-In contrast, our results suggest that while connectivity metrics show some levels of cluster predictor importance, there are few differences between resilient and non-resilient reefs in metrics such as source-to-sink connectivity ratio and total connectivity strength.
-While there is interaction between incoming connectivity and depth in reef cluster prediction, according to available input data, there are few reefs in the GBR that occur at depths \>10m and have Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget), resulting in low importance of connectivity as an individual feature for clustering across the GBR.
-Furthermore, our results suggest no relationship between connectivity strength and the ability of reefs to maintain positive carbonate budgets under future conditions.
+It is a common conclusion in coral reef ecology that a primary facet of reef resilience is the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008; @torres2024].
+Our results suggest that incoming connectivity contributes positively to high cover cluster allocation for reefs over 10m deep.
+At depths of less than 10m thermal stress may be too high for juveniles to contribute to long term recovery.
+While there is interaction between incoming connectivity and depth for reef cluster prediction, according to available input data, there are few reefs in the GBR that occur at depths \>10m and have Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget), resulting in overall low importance of connectivity as an individual feature for clustering across the GBR.
+Furthermore, our results suggest no direct, first order, relationship between weighted incoming connectivity and the ability of reefs to maintain positive carbonate budgets under future conditions.
 There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent generation connectivity modelling is able to identify reefs that are important for recovery processes, with findings dependent on the larval connectivity model used.
@@
 Using updated 1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal sample of particle flows, our results suggest that larval connectivity alone may not be important or reef resilience and recovery, but should be considered in combination with more influential factors such as depth.
+In-depth comparisons and validation of multiple connectivity model outputs would improve certainty and allow for the targetting of reefs by combining abiotic factors such as depth with connectivity.
 
-Our findings on the importance of connectivity may differ due to the highly uncertain nature of larval connectivity modelling [@vogt-vincent2023], the way larval flows and juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early bleaching events decreasing the breeding capacity of strongly connected reefs.
+Our findings on the importance of connectivity may differ from literature due to the highly uncertain nature of larval connectivity modelling [@vogt-vincent2023], the way larval flows and juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early bleaching events decreasing the breeding capacity of strongly connected reefs.
 Analysing daily connectivity data Vogt-Vincent et al.
@@
 [@baker1975; @huston1985; @ruiz-diaz2022].
-If included in this investigation, it is possible that reef recovery ability would be reduced at greater depths, reducing the positive effect of depth refugia for temporal resilience.
+If included in this investigation it is possible that reef recovery ability, via regrowth, would be reduced at greater depths, reducing the positive effect of depth refugia for temporal resilience.
 Additionally, reduced growth rates at increased depths may reduce the carbonate budget maintenance of reefs due to lower rates of CaCO~3~ accretion.
@@
 Using alternative connectivity implementation methods that better capture the ecological-timescale trends in reef connections rather than the high daily variability, would improve confidence in the connectivity findings of this investigation [@vogt-vincent2023].
+Additionally greater year - sample sizes for baseline connectivity data as future computation improvements are made, along with GBR scale validation efforts, will improve confidence in connectivity data for ecological modelling and management applications.
 The DHW data used in this investigation have not been bias corrected for the Great Barrier Reef region and are part of a wider Australian dataset [@dixon2022] developed using statistical downscaling.
@@
 Improvements in remote sensing approaches for broad scale bathymetry measurement and understanding of how depth impacts experienced thermal stress on reefs will further enhance investigations of depth as a critical factor for reef resilience.
-Additional analyses could build on the findings of this study by assessing the impacts of prioritising reef depth in reef restoration decision making.
+Additional analyses could build on the findings of this study by assessing the impacts of prioritising reef depth in reef intervention decision making.
 Future analyses could incorporate other environmental and ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn Starfish [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
@@
 We provide evidence in support of depth as a form of thermal refugia for shallow-water reefs on the GBR.
-While protecting ‘key node’ reefs in larval connectivity networks is an important consideration for reef restoration efforts [@anthony2020; @hock2017], current connectivity modelling methods, in combination with our modelling framework, suggest that connectivity may not be as solely-important for reef resilience under projected conditions as environmental factors such as depth and thermal stress levels.
+Targetting reefs with median depths greater than 10m and high incoming and ougoing larval connections may aid in identifying the most resilient reefs under climate change.
 We suggest further analyses that investigate the benefits of incorporating depth-based resilience into reef intervention decision making, as well as further research and development in connectivity modelling methods for whole-ecosystem scales.

### 2025-09-04 paper/paper_draft.qmd
Update paper citations in discussion and format doc

@@
 Climate change is impacting species survival, persistence and ecosystem functions globally.
-This is particularly true for coral reefs, which are vulnerable to increasing magnitude and variation in environmental stressors such as ocean temperature, acidification and nutrient loading [@foster2021; @gattuso2014].
-Mass bleaching and mortality events driven by climate change can cause reef-building coral population declines [@hughes2017; @hughes2018; @bozec2025], possibly leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
-Climate impacts on coral reefs are decreasing the ability of coral reefs to provide ecological functions such as benthic habitat and nutrient cycling [@forster2021; @williams2019] as well as ecosystem services such as food, protection, tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
+This is particularly true for coral reefs, which are vulnerable to increasing magnitude and
+variation in environmental stressors such as ocean temperature, acidification and nutrient
+loading [@foster2021; @gattuso2014]. Mass bleaching and mortality events driven by climate
+change can cause reef-building coral population declines [@hughes2017; @hughes2018;
+@bozec2025], possibly leading to long-term and large-scale coral-macroalgae regime shifts
+[@arif2022; @wild2011]. Climate impacts on coral reefs are decreasing the ability of coral
+reefs to provide ecological functions such as benthic habitat and nutrient cycling
+[@forster2021; @williams2019] as well as ecosystem services such as food, protection,
+tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
 
-Understanding the characteristics of reefs that will persist under projected climate conditions requires examining reef resilience across multiple scales and processes.
-Structural resilience - the capacity to maintain coral populations and avoid ecosystem regime shifts - depends on three interconnected mechanisms.
-First, the ability of individual corals to survive thermal stress.
-Second, the connectivity networks that enable recolonisation after disturbances [@hock2017; @mumby2008; @torres2024].
-Third, the maintenance of the carbonate framework that provides reef structure [@perry2012].
-We aim to assess how these mechanisms interact under projected climate conditions to identify the characteristics of structurally resilient reefs through scenario-based coral population modelling for the Great Barrier Reef ecosystem.
+Understanding the characteristics of reefs that will persist under projected climate
+conditions requires examining reef resilience across multiple scales and processes.
+Structural resilience - the capacity to maintain coral populations and avoid ecosystem
+regime shifts - depends on three interconnected mechanisms. First, the ability of individual
+corals to survive thermal stress. Second, the connectivity networks that enable
+recolonisation after disturbances [@hock2017; @mumby2008; @torres2024]. Third, the
+maintenance of the carbonate framework that provides reef structure [@perry2012]. We aim to
+assess how these mechanisms interact under projected climate conditions to identify the
+characteristics of structurally resilient reefs through scenario-based coral population
+modelling for the Great Barrier Reef ecosystem.
 
-The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of thousands of individual reefs.
-They are interconnected through coral and fish larval dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@cappo2000].
-The GBR faces severe projected coral cover declines under climate change [@bozec2025; @bozec2022; @condie2021].
-These coral cover declines will be compounded by ocean acidification, tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018].
-The 2023-24 Summer mass bleaching event may be signalling a shift towards this reef future, with some level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs) [@australianinstituteofmarinescience2024]; @cantin2024\].
+The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of
+thousands of individual reefs. They are interconnected through coral and fish larval
+dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@cappo2000].
+The GBR faces severe projected coral cover declines under climate change [@bozec2025;
+@bozec2022; @condie2021]. These coral cover declines will be compounded by ocean
+acidification, tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012;
+@fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24 Summer mass
+bleaching event may be signalling a shift towards this reef future, with some level of
+bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
+[@australianinstituteofmarinescience2024]; @cantin2024\].
 
-At the individual coral scale, survival during thermal stress events depends on both environmental and biological factors.
-Environmental factors can either amplify or reduce thermal stress exposure.
-Depth is a crucial factor that can provide a refuge from thermal stress [@álvarez-noriega2018; @baird2018; @smith2014].
-Biological factors including coral size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and thermal tolerance through acclimation and inheritance [@humanes2022; @lachs2024] all influence survival outcomes.
-Importantly, corals demonstrate adaptive capacity to develop thermal tolerance that could delay widespread bleaching under moderate emission scenarios [@bairos-novak2021; @humanes2022], representing a crucial mechanism for reef persistence.
+At the individual coral scale, survival during thermal stress events depends on both
+environmental and biological factors. Environmental factors can either amplify or reduce
+thermal stress exposure. Depth is a crucial factor that can provide a refuge from thermal
+stress [@álvarez-noriega2018; @baird2018; @smith2014]. Biological factors including coral
+size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and thermal tolerance
+through acclimation and inheritance [@humanes2022; @lachs2024] all influence survival
+outcomes. Importantly, corals demonstrate adaptive capacity to develop thermal tolerance
+that could delay widespread bleaching under moderate emission scenarios [@bairos-novak2021;
+@humanes2022], representing a crucial mechanism for reef persistence.
 
-Beyond individual survival, reef-scale resilience depends on connectivity networks that enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017].
-However, connectivity creates both strengths and vulnerabilities.
-Larval source populations that export more larvae than they import are essential for system-wide recovery, providing larvae that enable recolonization at distant locations [@hock2017; @thomas2015].
-Yet these source reefs are paradoxically more vulnerable individually, relying heavily on local recruitment for their own recovery.
-When disturbances impact major source populations, cascading effects reduce larval export and slow recovery throughout the connected network [@figueiredo2022; @hock2017; @munday2009].
+Beyond individual survival, reef-scale resilience depends on connectivity networks that
+enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017]. However,
+connectivity creates both strengths and vulnerabilities. Larval source populations that
+export more larvae than they import are essential for system-wide recovery, providing larvae
+that enable recolonization at distant locations [@hock2017; @thomas2015]. Yet these source
+reefs are paradoxically more vulnerable individually, relying heavily on local recruitment
+for their own recovery. When disturbances impact major source populations, cascading effects
+reduce larval export and slow recovery throughout the connected network [@figueiredo2022;
+@hock2017; @munday2009].
 
-Long-term reef viability requires not only coral survival and recolonization, but also maintenance of the physical reef structure through positive carbonate budgets.
-Scleractinian corals build the primary habitat framework, but reef persistence depends on the balance between carbonate accumulation [@perry2015] and loss through bioerosion, physical damage [@kenyon2023], and dissolution [@eyre2014; @eyre2018].
-This balance is influenced by coral cover and community complexity [@perry2012; @desbiens2021], environmental processes, and ocean chemistry [@perry2015; @eyre2018].
-For GBR mid-shelf and offshore reefs, maintaining positive carbonate budgets requires approximately 17% live coral cover [@desbiens2021].
+Long-term reef viability requires not only coral survival and recolonization, but also
+maintenance of the physical reef structure through positive carbonate budgets. Scleractinian
+corals build the primary habitat framework, but reef persistence depends on the balance
+between carbonate accumulation [@perry2015] and loss through bioerosion, physical damage
+[@kenyon2023], and dissolution [@eyre2014; @eyre2018]. This balance is influenced by coral
+cover and community complexity [@perry2012; @desbiens2021], environmental processes, and
+ocean chemistry [@perry2015; @eyre2018]. For GBR mid-shelf and offshore reefs, maintaining
+positive carbonate budgets requires approximately 17% live coral cover [@desbiens2021].
 
-Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response research enable integrated investigation of how these multiple factors interact to determine climate resilience.
-By incorporating the latest coral population models [@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections [@dixon2022], we can examine which factors most strongly influence reef persistence under different scenarios.
-While connectivity has been emphasized as critical for GBR resilience [@hock2017], and remains an important consideration, our integrated modelling reveals depth may play a fundamental role in determining maintenance of reef coral populations and positive carbonate budgets under current projections of climate change.
+Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response
+research enable integrated investigation of how these multiple factors interact to determine
+climate resilience. By incorporating the latest coral population models
+[@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections
+[@dixon2022], we can examine which factors most strongly influence reef persistence under
+different scenarios. While connectivity has been emphasized as critical for GBR resilience
+[@hock2017], and remains an important consideration, our integrated modelling reveals depth
+may play a fundamental role in determining maintenance of reef coral populations and
+positive carbonate budgets under current projections of climate change.
 
@@
 
-The spatial extent of the GBR reefs represented in this investigation follows the reef definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA) [@GBRMPA2022].
-The reef definitions define 3806 reefs across the GBR.
-An indicative map of the GBR marine park including the Marine Park Management areas [@GBRMPA2007] and the corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
-Estimates of coral carrying capacity for each reef were taken from prior analyses undertaken in [@bozec2022].
+The spatial extent of the GBR reefs represented in this investigation follows the reef
+definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
+[@GBRMPA2022]. The reef definitions define 3806 reefs across the GBR. An indicative map of
+the GBR marine park including the Marine Park Management areas [@GBRMPA2007] and the
+corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
+Estimates of coral carrying capacity for each reef were taken from prior analyses undertaken
+in [@bozec2022].
 
-Depth characteristics for each reef were extracted using 10m resolution bathymetry data made available in GBRMPA [-@GBRMPA2020].
-For each reef, bathymetry data were spatially matched with the 3806 reef outlines through geometric intersections.
-All depth values were converted to positive values (depths below sea level).
-The median depth was used to provide an indicative depth value for each reef.
-Code, and the resulting depth estimates, are available at [@iwanaga2025].
+Depth characteristics for each reef were extracted using 10m resolution bathymetry data made
+available in GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched
+with the 3806 reef outlines through geometric intersections. All depth values were converted
+to positive values (depths below sea level). The median depth was used to provide an
+indicative depth value for each reef. Code, and the resulting depth estimates, are available
+at [@iwanaga2025].
 
-While the bathymetry data adopted for the given assessment are said to be accurate up to 15m from Mean Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for this study.
-These are outlined further in the Discussion.
-Notably, the adopted depth estimates were derived from bathymetries based on satellite imagery.
-The bathymetry data can be limited in their alignment with the established GBRMPA reef outlines used to characterise reef locations and their areal extent.
-A Quality Assessment and Control process identified reefs with potential data limitations: reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level (indicating potential data artifacts), and reefs where bathymetry pixels covered less than 5% of the reef polygon area.
-This process removed 842 reefs, or 22%, from the initial set of 3806 reefs.
-Furthermore, reefs that are not associated with GBRMPA Management areas [@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed from the investigation.
-Bioregions which contained fewer than three reefs after these processes were also excluded.
-As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for the purpose of this investigation.
+While the bathymetry data adopted for the given assessment are said to be accurate up to 15m
+from Mean Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth
+estimates used for this study. These are outlined further in the Discussion. Notably, the
+adopted depth estimates were derived from bathymetries based on satellite imagery. The
+bathymetry data can be limited in their alignment with the established GBRMPA reef outlines
+used to characterise reef locations and their areal extent. A Quality Assessment and Control
+process identified reefs with potential data limitations: reefs with no overlapping
+bathymetry data, reefs with minimum depth values above sea level (indicating potential data
+artifacts), and reefs where bathymetry pixels covered less than 5% of the reef polygon area.
+This process removed 842 reefs, or 22%, from the initial set of 3806 reefs. Furthermore,
+reefs that are not associated with GBRMPA Management areas [@GBRMPA2007] or reefal
+bioregions [@GBRMPA2024] were also removed from the investigation. Bioregions which
+contained fewer than three reefs after these processes were also excluded. As a result, 1377
+reefs were excluded (36%), leaving a total of 2429 remaining for the purpose of this
+investigation.
 
-![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all considered reefs (points).
-Colour-coded polygons outline GBR marine park management regions, where orange represents the Far Northern management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007].
-Reef centroids are marked individually for visual clarity and are coloured according to its bioregion [@GBRMPA2024].
-All 2429 reefs included in this investigation are represented in this figure.
-Annotations represent major coastal settlements along the GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
+![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all
+considered reefs (points). Colour-coded polygons outline GBR marine park management regions,
+where orange represents the Far Northern management region, green represents
+Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
+[@GBRMPA2007]. Reef centroids are marked individually for visual clarity and are coloured
+according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
+represented in this figure. Annotations represent major coastal settlements along the
+GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
 
@@
 
-Future projections of maximum yearly Degree Heating Weeks (DHWs) for each reef were estimated from Sea Surface Temperature (SST) data for the GBR.
-Statistically downscaled 1km^2^ resolution SST data for five Global Climate Models (GCMs) were obtained from the HighResCoralStress database [@dixon2022; @dixon2023].
-These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4.
-The selected GCMs are a part of the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6), spanning four 'model development families' as defined by Brunner et al., [-@brunner2020].
+Future projections of maximum yearly Degree Heating Weeks (DHWs) for each reef were
+estimated from Sea Surface Temperature (SST) data for the GBR. Statistically downscaled
+1km^2^ resolution SST data for five Global Climate Models (GCMs) were obtained from the
+HighResCoralStress database [@dixon2022; @dixon2023]. These five GCMs were EC-Earth3-Veg,
+ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GFDL-CM4. The selected GCMs are a part of the
+Sixth Phase of the Coupled Model Intercomparison Project (CMIP6), spanning four 'model
+development families' as defined by Brunner et al., [-@brunner2020].
 
-These GCMs were selected based on evaluation conducted by Grose et al., [-@grose2023], indicating their ability to recreate historical atmospheric temperature and precipitation conditions in the Australasian region.
-They span a range of Equilibrium Climate Sensitivity (ECS) values within the Intergovernmental Panel on Climate Change (IPCC) assessed likely range.
-The IPCC defines ECS as the long-term warming caused by a doubling of carbon dioxide above its pre-industrial concentration [@forster2021].
-While this assessment does not consider oceanic data, Grose et al.
-[-@grose2023] provide a region-specific selection mechanism which we use as an indicator of general performance of GCMs for the region.
-An overview of the selected GCMs is provided in @tbl-gcms.
-Note here that Grose et al., [-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides data based on GFDL-CM4.
-This substitution is assumed appropriate given they share the same fundamental representation of the physical climate system.
+These GCMs were selected based on evaluation conducted by Grose et al., [-@grose2023],
+indicating their ability to recreate historical atmospheric temperature and precipitation
+conditions in the Australasian region. They span a range of Equilibrium Climate Sensitivity
+(ECS) values within the Intergovernmental Panel on Climate Change (IPCC) assessed likely
+range. The IPCC defines ECS as the long-term warming caused by a doubling of carbon dioxide
+above its pre-industrial concentration [@forster2021]. While this assessment does not
+consider oceanic data, Grose et al. [-@grose2023] provide a region-specific selection
+mechanism which we use as an indicator of general performance of GCMs for the region. An
+overview of the selected GCMs is provided in @tbl-gcms. Note here that Grose et al.,
+[-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides
+data based on GFDL-CM4. This substitution is assumed appropriate given they share the same
+fundamental representation of the physical climate system.
 
-Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission pathway.
-It represents a moderate emissions scenario with continued CO~2~ emissions comparable to present day until 2050, after which emissions gradually decline [@hausfather2020; IPCC -@climate2023].
-The selected GCMs represent 2.5°C to 4.66°C of global atmospheric warming in the 2081-2100 period relative to 1850-1900.
-The use of these GCMs therefore allow for a range of possible climate futures to be explored, capturing uncertainty in future responses to CO~2~ increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]) and enables the assessment of modelled coral reef behaviour over a broad range of independently derived climate futures [@abramowitz2019].
+Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission
+pathway. It represents a moderate emissions scenario with continued CO~2~ emissions
+comparable to present day until 2050, after which emissions gradually decline
+[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.66°C of global
+atmospheric warming in the 2081-2100 period relative to 1850-1900. The use of these GCMs
+therefore allow for a range of possible climate futures to be explored, capturing
+uncertainty in future responses to CO~2~ increases (@sfig-ecs; @fig-methods-dhws;
+[@grose2023; @shepherd2018]) and enables the assessment of modelled coral reef behaviour
+over a broad range of independently derived climate futures [@abramowitz2019].
 
-Monthly mean SST climatological baselines, for each 1km^2^ pixel, were calculated from the daily SST data following NOAA methodology [@liu2017; @skirving2020].
-For each pixel of SST data, the Monthly Mean SST climatology was calculated by computing the mean SST value for each calendar month (January through December) across the 28-year baseline period from 1985 to 2012.
-For each month separately, this climatological baseline was adjusted to centre at year 1988.2857, which attempts to account for any long-term trends within the baseline years themselves (see Skirving et al.
-[@skirving2020]).
-The adjustment ensures that the climatology represents conditions at a specific temporal reference point rather than being influenced by gradual warming or cooling trends that may have occurred during the 1985-2012 period.
-The resulting monthly climatologies serve as a standardized reference against which current SST conditions can be compared to identify thermal anomalies and assess coral bleaching risk, following the methodology established by Skirving et al.
-[-@skirving2020].
+Monthly mean SST climatological baselines, for each 1km^2^ pixel, were calculated from the
+daily SST data following NOAA methodology [@liu2017; @skirving2020]. For each pixel of SST
+data, the Monthly Mean SST climatology was calculated by computing the mean SST value for
+each calendar month (January through December) across the 28-year baseline period from 1985
+to 2012. For each month separately, this climatological baseline was adjusted to centre at
+year 1988.2857, which attempts to account for any long-term trends within the baseline years
+themselves (see Skirving et al. [@skirving2020]). The adjustment ensures that the
+climatology represents conditions at a specific temporal reference point rather than being
+influenced by gradual warming or cooling trends that may have occurred during the 1985-2012
+period. The resulting monthly climatologies serve as a standardized reference against which
+current SST conditions can be compared to identify thermal anomalies and assess coral
+bleaching risk, following the methodology established by Skirving et al. [-@skirving2020].
 
-Degree Heating Weeks (DHWs) were derived using the "HotSpot SST Anomaly" approach [@skirving2020].
-The "HotSpot SST Anomaly" represents thermal stress experienced by coral reefs and is calculated as the difference between daily SST values and the maximum of a pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean SST).
-This approach uses the annual maximum temperature as the baseline because corals are adapted to withstand their local warmest conditions under normal seasonal cycles.
-When temperatures exceed this seasonal maximum, corals experience thermal stress that can lead to bleaching.
-Only positive anomalies, greater than 1°C, are considered relevant for coral stress, as temperatures below the seasonal maximum do not contribute to bleaching risk.
+Degree Heating Weeks (DHWs) were derived using the "HotSpot SST Anomaly" approach
+[@skirving2020]. The "HotSpot SST Anomaly" represents thermal stress experienced by coral
+reefs and is calculated as the difference between daily SST values and the maximum of a
+pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean
+SST). This approach uses the annual maximum temperature as the baseline because corals are
+adapted to withstand their local warmest conditions under normal seasonal cycles. When
+temperatures exceed this seasonal maximum, corals experience thermal stress that can lead to
+bleaching. Only positive anomalies, greater than 1°C, are considered relevant for coral
+stress, as temperatures below the seasonal maximum do not contribute to bleaching risk.
 
-DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in units of °C-weeks.
-The 12-week accumulation period reflects the cumulative nature of coral thermal stress.
-Brief temperature spikes may be tolerable, but sustained or repeated exposure to elevated temperatures causes progressively greater physiological stress and bleaching severity.
-DHW values integrate both the magnitude and duration of thermal stress: a moderate anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly (e.g., 3°C) lasting 4 weeks, though the biological impacts may differ.
-DHW estimates for each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for all pixels touching each reef outline.
-The process described here was conducted for all 2429 reefs to create DHW projections spanning from 2025 to 2075.
-Code used to calculate DHW data and perform analyses involved in this investigation can be found at Grier and Iwanaga [-@grier2025].
+DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week
+rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in units of
+°C-weeks. The 12-week accumulation period reflects the cumulative nature of coral thermal
+stress. Brief temperature spikes may be tolerable, but sustained or repeated exposure to
+elevated temperatures causes progressively greater physiological stress and bleaching
+severity. DHW values integrate both the magnitude and duration of thermal stress: a moderate
+anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly
+(e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for
+each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for
+all pixels touching each reef outline. The process described here was conducted for all 2429
+reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
+and perform analyses involved in this investigation can be found at Grier and Iwanaga
+[-@grier2025].
 
 | Global Climate Model source | ECS value (°C)     | Interpreted relative severity | Results found in |
-|------------------|------------------|-------------------|------------------|
+|-----------------------|-----------------------|------------------------|-----------------------|
 | ACCESS-CM2                  | 4.66 [@grose2023]  | High                          | [@grier2025]     |
@@
 
-: Information for each GCM used in this investigation including Equilibrium Climate Sensitivity (ECS) value, interpreted relative severity and where results for an individual GCM results are found.
-GCMs in context with assessed plausible ranges of ECS values are displayed in [@sfig-ecs].
-ACCESS-ESM1-5 has an ECS closest to the midpoint of the very-likely ECS range and was taken as an intermediate model with results displayed in the main text.
-{#tbl-gcms}
+: Information for each GCM used in this investigation including Equilibrium Climate
+Sensitivity (ECS) value, interpreted relative severity and where results for an individual
+GCM results are found. GCMs in context with assessed plausible ranges of ECS values are
+displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the
+very-likely ECS range and was taken as an intermediate model with results displayed in the
+main text. {#tbl-gcms}
 
-![Degree Heating Week time series (in °C - Weeks) for the GCMs selected.
-Colours represent the different Management areas across the Great Barrier Reef.
-Green represents Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red represents the Townsville-Whitsunday Management area.
-Solid lines represent the management-area median time series and bands represent the 95th percentile confidence intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws fig-align="center" width="14.82cm"}
+![Degree Heating Week time series (in °C - Weeks) for the GCMs selected. Colours represent
+the different Management areas across the Great Barrier Reef. Green represents
+Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
+represents the Townsville-Whitsunday Management area. Solid lines represent the
+management-area median time series and bands represent the 95th percentile confidence
+intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws fig-align="center"
+width="14.82cm"}
 
@@
 
-We adapted exploratory scenario modelling approach from robust decision making (RDM) approaches for this investigation.
-In particular, we used parameter sampling and exploratory modelling to investigate a wide range of plausible futures under different assumptions of environmental (climatic) conditions and ecological factors.
-Exploratory modelling approaches have gained favour in recent years as precise long-term predictions of future conditions are often impossible in complex ecological systems [@conradt2024; @lempert2013].
-RDM embraces uncertainty as an inherent characteristic of complex environmental systems [@lempert2010; @lempert2013] and is a core methodology underpinning the development of robust and adaptive management strategies [@haasnoot2013].
-Rather than attempting to forecast specific outcomes, RDM aims to systematically explore many possible futures to identify patterns.
-Allowing for the identification of robust management strategies that perform well across those diverse conditions, as well as conditions in which such strategies may fail.
-Multiple interacting and compounding sources of uncertainty, and a lack of broad agreement as to their likelihood, create inherently uncertain outcomes.
-While we did not directly model management decision making in this investigation, we used exploratory modelling to identify the environmental and reef characteristics, such as thermal stress, depth and connectivity, that support favourable outcomes such as recovery and resilience.
+We adapted exploratory scenario modelling approach from robust decision making (RDM)
+approaches for this investigation. In particular, we used parameter sampling and exploratory
+modelling to investigate a wide range of plausible futures under different assumptions of
+environmental (climatic) conditions and ecological factors. Exploratory modelling approaches
+have gained favour in recent years as precise long-term predictions of future conditions are
+often impossible in complex ecological systems [@conradt2024; @lempert2013]. RDM embraces
+uncertainty as an inherent characteristic of complex environmental systems [@lempert2010;
+@lempert2013] and is a core methodology underpinning the development of robust and adaptive
+management strategies [@haasnoot2013]. Rather than attempting to forecast specific outcomes,
+RDM aims to systematically explore many possible futures to identify patterns. Allowing for
+the identification of robust management strategies that perform well across those diverse
+conditions, as well as conditions in which such strategies may fail. Multiple interacting
+and compounding sources of uncertainty, and a lack of broad agreement as to their
+likelihood, create inherently uncertain outcomes. While we did not directly model management
+decision making in this investigation, we used exploratory modelling to identify the
+environmental and reef characteristics, such as thermal stress, depth and connectivity, that
+support favourable outcomes such as recovery and resilience.
 
@@
 
-To apply exploratory scenario modelling, we employed a framework involving two separate systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and CoralBlox.
-ADRIA is a multi-criteria decision support platform designed to help reef managers address climate change challenges in coral reef systems [@iwanaga2023].
-The ADRIA platform provides functionality for scenario generation and analysis as well as providing the technical infrastructure to couple environmental and ecosystem representations.
-CoralBlox is a computationally efficient coral population model.
-It simulates functional/morphological groups of corals over their life cycles, competing for available space over time [@ribeirodealmeida2024].
-The coupled framework is referred to as ADRIA-CoralBlox.
+To apply exploratory scenario modelling, we employed a framework involving two separate
+systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and CoralBlox.
+ADRIA is a multi-criteria decision support platform designed to help reef managers address
+climate change challenges in coral reef systems [@iwanaga2023]. The ADRIA platform provides
+functionality for scenario generation and analysis as well as providing the technical
+infrastructure to couple environmental and ecosystem representations. CoralBlox is a
+computationally efficient coral population model. It simulates functional/morphological
+groups of corals over their life cycles, competing for available space over time
+[@ribeirodealmeida2024]. The coupled framework is referred to as ADRIA-CoralBlox.
 
-The coral demographic representation and associated model implementation are further detailed in the supplementary material.
-Of important note, however, is that the representation of bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient to incorporate the amelioration effect that depth may have, following Baird et al., [@baird2018].
-This depth-scaling reduces the proportion of coral colonies impacted by high heat stress as depth increases.
-The impacts of tropical cyclones, wave activity, Crown of Thorns Starfish or coral disease were not included in this investigation, in order to focus on assessing reef resilience under possible future warming scenarios.
+The coral demographic representation and associated model implementation are further
+detailed in the supplementary material. Of important note, however, is that the
+representation of bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a
+scaling coefficient to incorporate the amelioration effect that depth may have, following
+Baird et al., [@baird2018]. This depth-scaling reduces the proportion of coral colonies
+impacted by high heat stress as depth increases. The impacts of tropical cyclones, wave
+activity, Crown of Thorns Starfish or coral disease were not included in this investigation,
+in order to focus on assessing reef resilience under possible future warming scenarios.
 
-ADRIA-CoralBlox was run for 4096 scenarios for each GCM (20,480 total model runs).
-Here, a scenario represents a unique combination of assumed environmental (namely one of the five DHW trajectories) and ecological factors including coral growth and mortality rates, and coral thermal tolerances.
-Scenarios were generated using the low-discrepancy Sobol' sampling method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi Monte Carlo approach which balances scenario exploration with improved convergence properties compared to pseudo-random sampling.
-A detailed comparative analysis of the sampling methods can be found in [@kucherenko2015].
-For the purpose of scenario assessment, the resulting coral cover time series for each model run were scaled by the total area of each reef to represent cover as a percentage of the total estimated reef area.
-The scenario-median timeseries for each reef was used for further analyses.
-These time series of coral cover were then clustered based on their temporal behaviour.
+ADRIA-CoralBlox was run for 4096 scenarios for each GCM (20,480 total model runs). Here, a
+scenario represents a unique combination of assumed environmental (namely one of the five
+DHW trajectories) and ecological factors including coral growth and mortality rates, and
+coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol' sampling
+method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi Monte Carlo
+approach which balances scenario exploration with improved convergence properties compared
+to pseudo-random sampling. A detailed comparative analysis of the sampling methods can be
+found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
+cover time series for each model run were scaled by the total area of each reef to represent
+cover as a percentage of the total estimated reef area. The scenario-median timeseries for
+each reef was used for further analyses. These time series of coral cover were then
+clustered based on their temporal behaviour.
 
@@
 
-Connectivity data from 24 days in total were used in this investigation to estimate coral larval flows.
-These data span six years from 2015 to 2020.
-The years 2015, 2016, 2018 and 2019 are each represented by connectivity matrices covering spawning periods over three days in each year (12 days in total), while 2017 and 2020 are each represented by six spawning days each, coming to a total of 24 days of connectivity matrices.
-The values in these matrices indicate the probability of larval transfer between each pair of reefs in the GBR, herein referred to as connectivity strengths.
-Indicative connectivity strengths are implemented in ADRIA-CoralBlox as the mean of all available data for each location (i.e., mean of all 24 spawning days).
-While the connectivity strengths do not vary from year to year within each ADRIA-CoralBlox simulation, they do vary between reefs which are of varying sizes, providing sufficient heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics.
-This spatial variability also enables investigations into the influence of connectivity strength and its role in driving recovery processes.
+Connectivity data from 24 days in total were used in this investigation to estimate coral
+larval flows. These data span six years from 2015 to 2020. The years 2015, 2016, 2018 and
+2019 are each represented by connectivity matrices covering spawning periods over three days
+in each year (12 days in total), while 2017 and 2020 are each represented by six spawning
+days each, coming to a total of 24 days of connectivity matrices. The values in these
+matrices indicate the probability of larval transfer between each pair of reefs in the GBR,
+herein referred to as connectivity strengths. Indicative connectivity strengths are
+implemented in ADRIA-CoralBlox as the mean of all available data for each location (i.e.,
+mean of all 24 spawning days). While the connectivity strengths do not vary from year to
+year within each ADRIA-CoralBlox simulation, they do vary between reefs which are of varying
+sizes, providing sufficient heterogeneity to capture spatial patterns in larval dispersal
+and settlement dynamics. This spatial variability also enables investigations into the
+influence of connectivity strength and its role in driving recovery processes.
 
-To assess the impact of reef connectivity on modelled outcomes we summarise inter-reef connections using weighted connectivity metrics (incoming and outgoing) and the ratio of source-to-sink connectivity for each reef.
-Weighted incoming connectivity is calculated by summing the product of each connection strength incoming to a target reef and the mean timeseries absolute coral cover (km^2^) of each matching source reef.
-This metric provides an approximation of overall larval flow into a reef, with high values indicating the target reef is supplied high volumes of larvae via strong connections and low values indicating the target reef has weak (or no) incoming connections or is supplied by small source populations.
-Weighted outgoing connectivity is calculated as the product of outgoing connectivity strength from a target reef and the mean timeseries absolute coral cover (km^2^) of the target reef, representing the larval flow leaving the target reef population.
-A limitation of these weighted connectivity metrics is that they do not incorporate the proportion of the source reef's population that is reproducing and producing larvae, instead taking the total coral cover area as an indicator of larval productivity.
-The ratio of source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's outgoing larval flow relative to it's incoming larval flow.
-This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$.
-Where S represents the sum of connectivity pobabilities, N represents the number of connections, O denotes outgoing connectivity from the target reef and I denotes incoming connectivity to the target reef.
-If a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value.
-Incoming connections in this calculation, do not directly represent the larval supply gained as the breeding populations from which connections are coming from are not represented.
-A source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming larval flow.
+To assess the impact of reef connectivity on modelled outcomes we summarise inter-reef
+connections using weighted connectivity metrics (incoming and outgoing) and the ratio of
+source-to-sink connectivity for each reef. Weighted incoming connectivity is calculated by
+summing the product of each connection strength incoming to a target reef and the mean
+timeseries absolute coral cover (km^2^) of each matching source reef. This metric provides
+an approximation of overall larval flow into a reef, with high values indicating the target
+reef is supplied high volumes of larvae via strong connections and low values indicating the
+target reef has weak (or no) incoming connections or is supplied by small source
+populations. Weighted outgoing connectivity is calculated as the product of outgoing
+connectivity strength from a target reef and the mean timeseries absolute coral cover
+(km^2^) of the target reef, representing the larval flow leaving the target reef population.
+A limitation of these weighted connectivity metrics is that they do not incorporate the
+proportion of the source reef's population that is reproducing and producing larvae, instead
+taking the total coral cover area as an indicator of larval productivity. The ratio of
+source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
+outgoing larval flow relative to it's incoming larval flow. This is calculated as:
+$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where S represents the sum of connectivity pobabilities, N
+represents the number of connections, O denotes outgoing connectivity from the target reef
+and I denotes incoming connectivity to the target reef. If a reef has no incoming
+connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this calculation,
+do not directly represent the larval supply gained as the breeding populations from which
+connections are coming from are not represented. A source-to-sink ratio greater than 1 (a
+value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
+larval flow.
 
@@
 
-Reefs were clustered into three qualitative categories based on their temporal behaviour indicated by coral cover over time.
-The three categories were Low, Medium, and High, indicating their relative ability to maintain coral cover and thus their structural resilience.
-The Complexity-Invariant Distance (CID) between each time series was calculated to identify similarities in temporal behaviour [@batista2014].
-The CID applies a correction factor to the Euclidean distance between pairs of time series to obtain a measure of their similarity.
-The adopted approach ensures reefs are clustered based on their temporal dynamics as opposed to, for example, naively clustering by their mean coral cover.
+Reefs were clustered into three qualitative categories based on their temporal behaviour
+indicated by coral cover over time. The three categories were Low, Medium, and High,
+indicating their relative ability to maintain coral cover and thus their structural
+resilience. The Complexity-Invariant Distance (CID) between each time series was calculated
+to identify similarities in temporal behaviour [@batista2014]. The CID applies a correction
+factor to the Euclidean distance between pairs of time series to obtain a measure of their
+similarity. The adopted approach ensures reefs are clustered based on their temporal
+dynamics as opposed to, for example, naively clustering by their mean coral cover.
 Clustering similar time series is achieved through the use of k-medoids clustering [cf.
-@steinmann2020].
-Further details on the time series clustering approach are found in the supplementary materials.
+@steinmann2020]. Further details on the time series clustering approach are found in the
+supplementary materials.
 
-The time series clustering was applied over the time frame between 2025 and 2075.
-Spatially, the clustering analyses were conducted for each GBR management area and at the scale of each reefal bioregion (defined in GBRMPA [-@GBRMPA2024]).
-Analyses were also performed at the whole-of-GBR scale but were found to lead to identical conclusions about characteristics influencing cluster cover compared to management area and bioregion scale analyses and so are not shown here.
-To compare time series clustering results across GCMs, management area scale clustering results are used to preserve coarse scale latitudinal differences between regions, while maintaining ease of comparison and visualisation.
-These comparisons include quantification of differences between low and high cover clusters across management regions under each GCM using the CID between cluster median time series.
-To assess how different reef characteristics influence time series clustering at a finer spatial scale, bioregion results are used to capture patterns occurring within individual groups of reefs.
-Results of all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for those interested.
+The time series clustering was applied over the time frame between 2025 and 2075. Spatially,
+the clustering analyses were conducted for each GBR management area and at the scale of each
+reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
+whole-of-GBR scale but were found to lead to identical conclusions about characteristics
+influencing cluster cover compared to management area and bioregion scale analyses and so
+are not shown here. To compare time series clustering results across GCMs, management area
+scale clustering results are used to preserve coarse scale latitudinal differences between
+regions, while maintaining ease of comparison and visualisation. These comparisons include
+quantification of differences between low and high cover clusters across management regions
+under each GCM using the CID between cluster median time series. To assess how different
+reef characteristics influence time series clustering at a finer spatial scale, bioregion
+results are used to capture patterns occurring within individual groups of reefs. Results of
+all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for
+those interested.
 
-Reefs in each time series cluster were compared to identify characteristics that differ between Low, Medium and High clusters.
-These characteristics include reef median depth, mean time series DHW, ratio of source-to-sink larval connectivity, weighted incoming connectivity, weighted outgoing connectivity and reef carrying capacity (coral habitable area).
+Reefs in each time series cluster were compared to identify characteristics that differ
+between Low, Medium and High clusters. These characteristics include reef median depth, mean
+time series DHW, ratio of source-to-sink larval connectivity, weighted incoming
+connectivity, weighted outgoing connectivity and reef carrying capacity (coral habitable
+area).
 
@@
 
-Partial Dependence Analysis was conducted to understand the relationship between features and bioregion-scale time series cluster predictions using a trained Random Forest (RF) classifier [@friedman2001].
-The analysis utilised the reef characteristics of interest as the predictors, including the median reef depth, mean DHW for the given GCM, Log10 - weighted incoming connectivity, Log10 - weighted outgoing connectivity, and Log10 - outgoing-to-incoming connectivity ratio.
-The full dataset consisted of the time series cluster assignment of each of the 2429 reefs under the five GCMs explored, for a total of 12,145 samples.
-The dataset was randomly split into training (60%) and testing (40%) subsets to ensure model generalisability.
-The RF classifier achieved 99% accuracy on the training set and 62% on the test set.
+Partial Dependence Analysis was conducted to understand the relationship between features
+and bioregion-scale time series cluster predictions using a trained Random Forest (RF)
+classifier [@friedman2001]. The analysis utilised the reef characteristics of interest as
+the predictors, including the median reef depth, mean DHW for the given GCM, Log10 -
+weighted incoming connectivity, Log10 - weighted outgoing connectivity, and Log10 -
+outgoing-to-incoming connectivity ratio. The full dataset consisted of the time series
+cluster assignment of each of the 2429 reefs under the five GCMs explored, for a total of
+12,145 samples. The dataset was randomly split into training (60%) and testing (40%) subsets
+to ensure model generalisability. The RF classifier achieved 99% accuracy on the training
+set and 62% on the test set.
 
-While 99% accuracy suggests the classifier is overfit to the training data, the 66% test accuracy indicates a meaningful relationship between modelled reef characteristics and their assigned clusters has been captured.
-A 3-fold cross-validation was also conducted, arriving at a similar 67% accuracy rate.
-The consistent level of accuracy across test and cross-validation demonstrates the generalised performance of the RF classifier is reliable.
-Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be 0.7, 0.5 and 0.65 respectively, indicating balanced performance across the cluster categories.
-Lower performance with the Medium cluster reflects the inherent difficulty of classifying transitional states in natural systems.
-For management applications, this level of performance provides valuable decision support when combined with expert knowledge and the model's probabilistic outputs.
+While 99% accuracy suggests the classifier is overfit to the training data, the 66% test
+accuracy indicates a meaningful relationship between modelled reef characteristics and their
+assigned clusters has been captured. A 3-fold cross-validation was also conducted, arriving
+at a similar 67% accuracy rate. The consistent level of accuracy across test and
+cross-validation demonstrates the generalised performance of the RF classifier is reliable.
+Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
+0.7, 0.5 and 0.65 respectively, indicating balanced performance across the cluster
+categories. Lower performance with the Medium cluster reflects the inherent difficulty of
+classifying transitional states in natural systems.
 
 Partial dependence analysis was performed by applying the trained model to the test dataset.
-Values for individual predictors were systematically (one-at-a-time) varied across a grid of 50 equally spaced points spanning the predictor's range, while all other features were left at their modelled values.
-The procedure creates (1) a modified test dataset, where the target predictor was set to the grid value for all samples, (2) probabilistic predictions for all three cluster classes using the trained RF classifier, and (3) the mean predicted probability for each class across all test observations.
-The median was also assessed (not shown) but was found not to substantially influence the interpretation of results.
-The process isolates the marginal effect of each predictor by averaging over the natural distribution of all other representative reef characteristics in the test dataset.
-Additionally, to assess possible interaction between reef depth and incoming connectivity, two-way partial dependence analysis was performed on grids along the range of these two features.
+Values for individual predictors were systematically (one-at-a-time) varied across a grid of
+50 equally spaced points spanning the predictor's range, while all other features were left
+at their modelled values. The procedure creates (1) a modified test dataset, where the
+target predictor was set to the grid value for all samples, (2) probabilistic predictions
+for all three cluster classes using the trained RF classifier, and (3) the mean predicted
+probability for each class across all test observations. The median was also assessed (not
+shown) but was found not to substantially influence the interpretation of results. The
+process isolates the marginal effect of each predictor by averaging over the natural
+distribution of all other representative reef characteristics in the test dataset.
+Additionally, to assess possible interaction between reef depth and incoming connectivity,
+two-way partial dependence analysis was performed on grids along the range of these two
+features.
 
@@
 
-Using coral cover time series for each reef we calculated the number of years each reef maintains coral cover above a given percent threshold.
-The threshold represents the level of live coral cover necessary to maintain a positive carbonate budget (denoted here as $\theta_{0}$ to indicate the budget equilibrium).
-Greater number of years above $\theta_{0}$ suggests greater resilience and opportunity for recovery.
+Using coral cover time series for each reef we calculated the number of years each reef
+maintains coral cover above a given percent threshold. The threshold represents the level of
+live coral cover necessary to maintain a positive carbonate budget (denoted here as
+$\theta_{0}$ to indicate the budget equilibrium). Greater number of years above $\theta_{0}$
+suggests greater resilience and opportunity for recovery.
 
-Recent analyses suggest a general threshold of \~17% live coral cover in the case of the mid-shelf and offshore GBR reefs [@desbiens2021].
-Given in situ carbonate budgets are influenced by (1) a range of processes; (2) the variety of approaches that could be used to measure those processes; and (3) the uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a single precise $\theta_{0}$ value.
-Concurrently, it is difficult to ascertain a suitable $\theta_{0}$ value for each individual reef.
+Recent analyses suggest a general threshold of \~17% live coral cover in the case of the
+mid-shelf and offshore GBR reefs [@desbiens2021]. Given in situ carbonate budgets are
+influenced by (1) a range of processes; (2) the variety of approaches that could be used to
+measure those processes; and (3) the uncertainty surrounding these, it would be unreasonable
+to assume all reefs adhere to a single precise $\theta_{0}$ value. Concurrently, it is
+difficult to ascertain a suitable $\theta_{0}$ value for each individual reef.
 
-Given the uncertainties present, the proportion of modelled reefs that display capacity to maintain coral cover above a given $\theta_{0}$ threshold is examined.
-An indicative range of 10 to 20% is used (inclusive, with a step size of 1%).
-The range was informed by Perry et al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of the lower and upper bounds respectively.
-Robustness of the conclusions drawn to the uncertainty in the precise value of $\theta_{0}$ for all reefs can then be assessed by using the indicative range.
+Given the uncertainties present, the proportion of modelled reefs that display capacity to
+maintain coral cover above a given $\theta_{0}$ threshold is examined. An indicative range
+of 10 to 20% is used (inclusive, with a step size of 1%). The range was informed by Perry et
+al., [-@perry2015] and Desbians et al., [-@desbiens2021] providing plausible indications of
+the lower and upper bounds respectively. Robustness of the conclusions drawn to the
+uncertainty in the precise value of $\theta_{0}$ for all reefs can then be assessed by using
+the indicative range.
 
-The relationships between the number of years above $\theta_{0}$ and characteristics such as median reef depth and Log-10 total connectivity strength were then assessed with Spearman's rank correlation.
-Spearman's correlation coefficient was adopted as reef depth and connectivity strength distributions are expected to be non-normal and highly skewed.
-Furthermore, reefs are naturally of different types and experience different conditions, and so the monotonic trends (whether the relationship consistently increase or decrease) rather than the exact quantitative relationship was of interest for this analysis.
+The relationships between the number of years above $\theta_{0}$ and characteristics such as
+median reef depth and Log-10 total connectivity strength were then assessed with Spearman's
+rank correlation. Spearman's correlation coefficient was adopted as reef depth and
+connectivity strength distributions are expected to be non-normal and highly skewed.
+Furthermore, reefs are naturally of different types and experience different conditions, and
+so the monotonic trends (whether the relationship consistently increase or decrease) rather
+than the exact quantitative relationship was of interest for this analysis.
 
@@
 
-There were substantial differences in the maintenance of coral cover post 2030 between the GCMs.
-Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs across clusters (Low, Medium and High).
+There were substantial differences in the maintenance of coral cover post 2030 between the
+GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs
+across clusters (Low, Medium and High).
 
-Of the GCMs explored, NorESM2-MM had the lowest Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline dynamics up to 2075 under this hypothetical climate future.
-Unsurprisingly, recovery phases were predominantly seen in the reefs in the High cluster, with Medium and Low exhibiting lesser probability of such periods of recovery.
-Generally, recovery and increases in coral cover were visible in simulated results up to 2045.
-Under NorESM2-MM, the Far Northern Management area were found to have the most similar temporal behaviour between Low and High clusters compared to other Management areas (@stbl-cluster-cid) due to the low degree of coral cover overall (@fig-gcm-cover-trajectories).
+Of the GCMs explored, NorESM2-MM had the lowest Equilibrium Climate Sensitivity (2.5°C) and
+reefs exhibit continuing recovery and decline dynamics up to 2075 under this hypothetical
+climate future. Unsurprisingly, recovery phases were predominantly seen in the reefs in the
+High cluster, with Medium and Low exhibiting lesser probability of such periods of recovery.
+Generally, recovery and increases in coral cover were visible in simulated results up to
+2045. Under NorESM2-MM, the Far Northern Management area were found to have the most similar
+temporal behaviour between Low and High clusters compared to other Management areas
+(@stbl-cluster-cid) due to the low degree of coral cover overall
+(@fig-gcm-cover-trajectories).
 
-Intermediate levels of coral cover maintenance can be seen in ACCESS-ESM1-5 (ECS value of 3.87°C) when compared to the other GCMs (of higher and lower ECS values).
-Under these intermediate conditions (in relative terms), there is potential for reefs in the High cluster to maintain coral cover levels around 20% to 2050.
-The highest peak DHW levels occur under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs time series occur under ACCESS-CM2 (@fig-methods-dhws).
-Under conditions represented by high ECS value GCMs - specifically, ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and GFDL-CM4 (4.1°C) - all reefs are largely in decline across all management areas from 2055 (@stbl-cluster-cid).
+Intermediate levels of coral cover maintenance can be seen in ACCESS-ESM1-5 (ECS value of
+3.87°C) when compared to the other GCMs (of higher and lower ECS values). Under these
+intermediate conditions (in relative terms), there is potential for reefs in the High
+cluster to maintain coral cover levels around 20% to 2050. The highest peak DHW levels occur
+under GFDL-CM4 between 2045 and 2050, while greater increases in overall DHWs time series
+occur under ACCESS-CM2 (@fig-methods-dhws). Under conditions represented by high ECS value
+GCMs - specifically, ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and GFDL-CM4 (4.1°C) - all
+reefs are largely in decline across all management areas from 2055 (@stbl-cluster-cid).
 
-![Time series of coral cover (relative to reef area) categorised within each Management area (rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060.
-The time series are categorised as "Low" (green), "Medium" (in orange), and "High" median cover (in blue).
-Solid lines represent the cluster median time series and bands represent the 95th percentile confidence intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories fig-align="center" width="14.82cm"}
+![Time series of coral cover (relative to reef area) categorised within each Management area
+(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. The
+time series are categorised as "Low" (green), "Medium" (in orange), and "High" median cover
+(in blue). Solid lines represent the cluster median time series and bands represent the 95th
+percentile confidence
+intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
+fig-align="center" width="14.82cm"}
 
-Comparing across GCMs, it is common for reefs to switch between clusters, including from Low to High and vice versa (@sfig-gcm-bioregion-cluster-assignment).
-Of 2429 reefs, 20% (503) of reefs have consistent cluster assignment across all GCMs.
-Of the 503 consistently assigned reefs, 49% are within the Far Northern Management area, with 7%, 13% and 31% occurring in the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas respectively (@sfig-gcm-cluster-map).
-Of the 503 consistently assigned reefs, 32%, 7% and 61% are clustered into Low, Medium and High clusters respectively.
-High levels of assignment variability across GCMs are expected as due to spatial differences in each given GCM’s DHW trajectories.
+Comparing across GCMs, it is common for reefs to switch between clusters, including from Low
+to High and vice versa (@sfig-gcm-bioregion-cluster-assignment). Of 2429 reefs, 20% (503) of
+reefs have consistent cluster assignment across all GCMs. Of the 503 consistently assigned
+reefs, 49% are within the Far Northern Management area, with 7%, 13% and 31% occurring in
+the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas
+respectively (@sfig-gcm-cluster-map). Of the 503 consistently assigned reefs, 32%, 7% and
+61% are clustered into Low, Medium and High clusters respectively. High levels of assignment
+variability across GCMs are expected as due to spatial differences in each given GCM’s DHW
+trajectories.
 
@@
 
-In contrast to the broad temporal behaviour at the Management area scale, the relationship between reef characteristics and assigned clusters were found to be similar at the bioregion scale across GCMs.
-Results are only shown and discussed for ACCESS-ESM1-5, an intermediate ECS scenario (@sfig-ecs).
-Those interested in results for the other assessed GCMs are referred to Grier and Iwanaga [-@grier2025].
-Across bioregions, reefs in the High cluster not only had greater levels of coral recovery but displayed persistence to 2050 (@sfig-access-esm1-5-bioregion-timeseries).
-Reefs in the High cluster were consistently found to have the greatest median reef depths across bioregions (@fig-access-esm1-5-bioregion-depth).
+In contrast to the broad temporal behaviour at the Management area scale, the relationship
+between reef characteristics and assigned clusters were found to be similar at the bioregion
+scale across GCMs. Results are only shown and discussed for ACCESS-ESM1-5, an intermediate
+ECS scenario (@sfig-ecs). Those interested in results for the other assessed GCMs are
+referred to Grier and Iwanaga [-@grier2025]. Across bioregions, reefs in the High cluster
+not only had greater levels of coral recovery but displayed persistence to 2050
+(@sfig-access-esm1-5-bioregion-timeseries). Reefs in the High cluster were consistently
+found to have the greatest median reef depths across bioregions
+(@fig-access-esm1-5-bioregion-depth).
 
-![Median depth for reefs within each bioregion, separated into clusters assigned by time series clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines represent the median depth for each cluster across reefs and bands represent the distribution of depth values within each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth fig-align="center" width="14.82cm"}
+![Median depth for reefs within each bioregion, separated into clusters assigned by time
+series clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative
+cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters
+with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
+‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030
+and 2060 within each bioregion. Solid lines represent the median depth for each cluster
+across reefs and bands represent the distribution of depth values within each cluster.
+Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
+fig-align="center" width="14.82cm"}
 
-Across six of the 29 bioregions reefs in the high cover cluster have lower mean DHW, Log-10 carrying capacity and Log-10 weighted outgoing connectivity values than reefs in other clusters (@sfig-access-esm1-5-bioregion-dhwmean; @sfig-access-esm1-5-bioregion-carrying-capacity; @sfig-access-esm1-5-bioregion-weightedoutgoing).
-There were no consistent patterns across bioregions in their reefs' Log-10 coral carrying capacity area and cluster assignment (@sfig-access-esm1-5-bioregion-carrying-capacity).
-Across most bioregions there were not consistent differences between clusters in connectivity metrics such as Log-10 source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming).
+Across six of the 29 bioregions reefs in the high cover cluster have lower mean DHW, Log-10
+carrying capacity and Log-10 weighted outgoing connectivity values than reefs in other
+clusters (@sfig-access-esm1-5-bioregion-dhwmean;
+@sfig-access-esm1-5-bioregion-carrying-capacity;
+@sfig-access-esm1-5-bioregion-weightedoutgoing). There were no consistent patterns across
+bioregions in their reefs' Log-10 coral carrying capacity area and cluster assignment
+(@sfig-access-esm1-5-bioregion-carrying-capacity). Across most bioregions there were not
+consistent differences between clusters in connectivity metrics such as Log-10
+source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10
+weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming).
 
@@
 
-A Partial Dependence Analysis was conducted using a Random Forest classifier to identify reef characteristics that influence its temporal behaviour, and thus its cluster assignment into Low, Medium, or High.
-Bioregion classification was excluded from this analysis as a predictor due to its categorical nature providing limited interpretable information, and is further justified by its low feature importance score of 9%, the lowest of all predictors (@fig-ts-cluster-pdp; Panel A).
-Reef median depth and mean DHW level have the highest feature importance scores, accounting for 25% and 16% predictive importance respectively.
-Weighted incoming and outgoing connectivity (Log10) features account for \~13.6% feature importance.
-The carrying capacity of a reef accounts for 12.3% feature importance.
-Reef source-to-sink ratio (Log10) both had feature importance scores of \~10%.
+A Partial Dependence Analysis was conducted using a Random Forest classifier to identify
+reef characteristics that influence its temporal behaviour, and thus its cluster assignment
+into Low, Medium, or High. Bioregion classification was excluded from this analysis as a
+predictor due to its categorical nature providing limited interpretable information, and is
+further justified by its low feature importance score of 9%, the lowest of all predictors
+(@fig-ts-cluster-pdp; Panel A). Reef median depth and mean DHW level have the highest
+feature importance scores, accounting for 25% and 16% predictive importance respectively.
+Weighted incoming and outgoing connectivity (Log10) features account for \~13.6% feature
+importance. The carrying capacity of a reef accounts for 12.3% feature importance. Reef
+source-to-sink ratio (Log10) both had feature importance scores of \~10%.
 
-Reefs have the greatest probability of being clustered into Low if shallow, and High at greater depths, with medium cluster reefs exhibiting a lower, and more stable, assignment probability across depth ranges (@fig-ts-cluster-pdp; Panel B).
-A large increase in the probability of a reef being categorised as High can be seen between 10 and 15 meters depth.
-This is at the edge of the depth range used in current deployment efforts [@howlett2021; @randall2021; @whitman2024] but indicates a depth range that could be adopted to maximise longevity and benefits of, for example, coral seeding activities.
-Across mean DHW values, assignment probability is roughly equal across the three clusters up to 5 DHW.
-A sharp delineation can be seen \> 5 DHW when comparing High with other clusters, with lower assignment probability (\~25%) compared to Medium and Low (\~40%) (@fig-ts-cluster-pdp; Panel B).
+Reefs have the greatest probability of being clustered into Low if shallow, and High at
+greater depths, with medium cluster reefs exhibiting a lower, and more stable, assignment
+probability across depth ranges (@fig-ts-cluster-pdp; Panel B). A large increase in the
+probability of a reef being categorised as High can be seen between 10 and 15 meters depth.
+This is at the edge of the depth range used in current deployment efforts [@howlett2021;
+@randall2021; @whitman2024] but indicates a depth range that could be adopted to maximise
+longevity and benefits of, for example, coral seeding activities. Across mean DHW values,
+assignment probability is roughly equal across the three clusters up to 5 DHW. A sharp
+delineation can be seen \> 5 DHW when comparing High with other clusters, with lower
+assignment probability (\~25%) compared to Medium and Low (\~40%) (@fig-ts-cluster-pdp;
+Panel B).
 
-![Feature importance scores (Panel A) of the Random Forest classifier, and Partial Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a reef being classified to one of the three clusters (Panel B).
-Partial Dependence Plots for bioregions were excluded as they were found to be uninformative.
-PDPs indicate the probability of a reef from the test dataset being clustered into each category depending on the predictor value on the x axis, when adjusted for values of other predictors.
-Green, orange and blue lines indicate cluster assignment probability for Low, Medium and High clusters respectively.
-Transparent grey points above probability lines represent the predictor values present in the test dataset, providing a rough indication of predictor value distribution across reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center" width="14.82cm"}
+![Feature importance scores (Panel A) of the Random Forest classifier, and Partial
+Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a
+reef being classified to one of the three clusters (Panel B). Partial Dependence Plots for
+bioregions were excluded as they were found to be uninformative. PDPs indicate the
+probability of a reef from the test dataset being clustered into each category depending on
+the predictor value on the x axis, when adjusted for values of other predictors. Green,
+orange and blue lines indicate cluster assignment probability for Low, Medium and High
+clusters respectively. Transparent grey points above probability lines represent the
+predictor values present in the test dataset, providing a rough indication of predictor
+value distribution across
+reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center"
+width="14.82cm"}
 
-Analyses for source-to-sink ratio and weighted incoming and outgoing connectivity metrics suggest that reefs with greater outgoing connectivity and lower incoming connectivity levels have higher probability of being clustered into the Low cluster category compared to other reefs.
-Additionally, two-way analyses revealed an interaction between reef depth and incoming connectivity in determining cluster category assignment, particularly at the high depth range (@fig-ts-cluster-pdp-twoway-incoming).
-Two-way analyses revealed that reefs at greater than 10m depth are unlikely to be clustered into the Low cluster category, regardless of their incoming connectivity levels.
-However, at greater than 10m depth reefs with higher incoming connectivity are more likely to be assigned to a High cluster, while reefs with low incoming connectivity are more likely to be assigned to a Medium cover cluster (@fig-ts-cluster-pdp-twoway-incoming).
-Two-way analyses, for depth and weighted outgoing connectivity, revealed a slight interaction with the increased low-cluster probability for reefs of high outgoing connectivity primarily concentrated in shallow reefs, while deep reefs with high outgoing connectivity have the greatest probability of being clustered into a high cover cluster (@sfig-ts-cluster-pdp-twoway-outgoing).
+Analyses for source-to-sink ratio and weighted incoming and outgoing connectivity metrics
+suggest that reefs with greater outgoing connectivity and lower incoming connectivity levels
+have higher probability of being clustered into the Low cluster category compared to other
+reefs. Additionally, two-way analyses revealed an interaction between reef depth and
+incoming connectivity in determining cluster category assignment, particularly at the high
+depth range (@fig-ts-cluster-pdp-twoway-incoming). Two-way analyses revealed that reefs at
+greater than 10m depth are unlikely to be clustered into the Low cluster category,
+regardless of their incoming connectivity levels. However, at greater than 10m depth reefs
+with higher incoming connectivity are more likely to be assigned to a High cluster, while
+reefs with low incoming connectivity are more likely to be assigned to a Medium cover
+cluster (@fig-ts-cluster-pdp-twoway-incoming). Two-way analyses, for depth and weighted
+outgoing connectivity, revealed a slight interaction with the increased low-cluster
+probability for reefs of high outgoing connectivity primarily concentrated in shallow reefs,
+while deep reefs with high outgoing connectivity have the greatest probability of being
+clustered into a high cover cluster (@sfig-ts-cluster-pdp-twoway-outgoing).
 
-![Partial dependence plot indicating the probability of cluster assignment along interacting values of median reef depth (metres) and Log10 weighted incoming connectivity.
-Colour indicates the probability of assignment to each cluster, with lighter colours indicating higher probability of assignment.
-Panel A shows the probability of assignment for the Low cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability for the High cluster category.
-Probability values for each cluster are generated by the random forest classifier using each combination of depth and incoming connectivity values along the axes at 50 grid points.
-The actual distributions of depth and incoming connectivity values for reefs are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_incomingconn_pdp.png){#fig-ts-cluster-pdp-twoway-incoming fig-align="center" width="14.82cm"}
+![Partial dependence plot indicating the probability of cluster assignment along interacting
+values of median reef depth (metres) and Log10 weighted incoming connectivity. Colour
+indicates the probability of assignment to each cluster, with lighter colours indicating
+higher probability of assignment. Panel A shows the probability of assignment for the Low
+cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability
+for the High cluster category. Probability values for each cluster are generated by the
+random forest classifier using each combination of depth and incoming connectivity values
+along the axes at 50 grid points. The actual distributions of depth and incoming
+connectivity values for reefs are displayed in panels D and E
+respectively.](../figs/ts_cluster_rf_twoway_depth_incomingconn_pdp.png){#fig-ts-cluster-pdp-twoway-incoming
+fig-align="center" width="14.82cm"}
 
-Individual feature analysis for carrying capacity indicates that its influence on cluster assignment is concentrated at the low range of predictor values (@fig-ts-cluster-pdp).
-This aligns with the right-skewed distribution of carrying capacity across reefs for these three predictor variables.
-Beyond this low-end range, the partial dependence becomes near constant, indicating that outlier values for these factors are not influential.
+Individual feature analysis for carrying capacity indicates that its influence on cluster
+assignment is concentrated at the low range of predictor values (@fig-ts-cluster-pdp). This
+aligns with the right-skewed distribution of carrying capacity across reefs for these three
+predictor variables. Beyond this low-end range, the partial dependence becomes near
+constant, indicating that outlier values for these factors are not influential.
 
-Assessing random forest prediction accuracy across bioregions, reveals increasing performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf).
-This highlights that unexplained variation in the test dataset (33% of variation) may be concentrated in shallow bioregions where the available model predictors do not capture differences between clustered reefs.
+Assessing random forest prediction accuracy across bioregions, reveals increasing
+performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf). This
+highlights that unexplained variation in the test dataset (33% of variation) may be
+concentrated in shallow bioregions where the available model predictors do not capture
+differences between clustered reefs.
 
@@
 
-Reef median depth had a moderate positive correlation with the number of years a reef maintains coral cover above the assumed carbonate budget threshold required to sustain live coral cover ($\theta_{0}$).
-Greater median depth was a key characteristic defining reefs that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate; @sfig-access-esm1-5-mean-carb-budget).
-Unsurprisingly, the number of years above $\theta_0$ substantially decreased as $\theta_0$ is increased, as does the Spearman's correlation.
-Decreasing correlation levels are likely due to an increasing number of reefs being unable to maintain coral cover above $\theta_0$ as it is increased, with the distribution of years above threshold becoming increasingly right-skewed (@fig-access-esm1-5-depth-conn-carbonate).
-In contrast, weighted incoming connectivity strength (Log-10 scale) was found to have no correlation with the number of years a reef maintains cover above the required thresholds (@fig-access-esm1-5-depth-conn-carbonate).
+Reef median depth had a moderate positive correlation with the number of years a reef
+maintains coral cover above the assumed carbonate budget threshold required to sustain live
+coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
+that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
+@sfig-access-esm1-5-mean-carb-budget). Unsurprisingly, the number of years above $\theta_0$
+substantially decreased as $\theta_0$ is increased, as does the Spearman's correlation.
+Decreasing correlation levels are likely due to an increasing number of reefs being unable
+to maintain coral cover above $\theta_0$ as it is increased, with the distribution of years
+above threshold becoming increasingly right-skewed
+(@fig-access-esm1-5-depth-conn-carbonate). In contrast, weighted incoming connectivity
+strength (Log-10 scale) was found to have no correlation with the number of years a reef
+maintains cover above the required thresholds (@fig-access-esm1-5-depth-conn-carbonate).
 
-![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075 (y-axis).
-The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef variables (depth - left and Log-10 weighted incoming connectivity - right) and the number of years cover exceeds the carbonate budget threshold.
-Point colour represents the median reef depth in metres in the left-hand panel, and Log-10 weighted incoming connectivity in the right-hand panel.
-Red points represent the mean number of years above an assumed carbonate budget threshold across reefs.
-Deeper reefs are better able to maintain cover above the indicative carbonate budget threshold, while there is no considerable relationship between weighted incoming connectivity and carbonate budget maintenance.
-Displays results from median time series using ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate fig-align="center" width="14.82cm"}
+![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
+(y-axis). The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
+Bracketed x-axis values represent the Spearman's correlation between reef variables (depth -
+left and Log-10 weighted incoming connectivity - right) and the number of years cover
+exceeds the carbonate budget threshold. Point colour represents the median reef depth in
+metres in the left-hand panel, and Log-10 weighted incoming connectivity in the right-hand
+panel. Red points represent the mean number of years above an assumed carbonate budget
+threshold across reefs. Deeper reefs are better able to maintain cover above the indicative
+carbonate budget threshold, while there is no considerable relationship between weighted
+incoming connectivity and carbonate budget maintenance. Displays results from median time
+series using
+ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
+fig-align="center" width="14.82cm"}
 
@@
 
-Our results show increasing reef depth has a strong positive impact on modelled reef resilience in temporal behaviour and maintenance of positive carbonate budgets under possible future conditions.
-Reefs with a median depth of 10m or greater, with high incoming connectivity, are the most likely to be assigned to a high cover time series cluster.
-As an individual feature, incoming connectivity alone does not correlate with maintenance of positive carbonate budgets.
-These findings highlight the importance of depth and incoming connectivity as coupled selection features when assessing potential reef resilience under future thermal stress.
+Our results show increasing reef depth has a strong positive impact on modelled reef
+resilience in temporal behaviour and maintenance of positive carbonate budgets under
+possible future conditions. Reefs with a median depth of 10m or greater, with high incoming
+connectivity, are the most likely to be assigned to a high cover time series cluster. As an
+individual feature, incoming connectivity alone does not correlate with maintenance of
+positive carbonate budgets. These findings highlight the importance of depth and incoming
+connectivity as coupled selection features when assessing potential reef resilience under
+future thermal stress.
 
-Reefs in different temporal clusters largely do not differ in mean modelled DHW levels experienced and exhibit overall similar DHW time series.
-While these reefs experience similar magnitude DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress events depends on reef depth.
-Reefs at deeper depths are likely to be clustered into High cover clusters.
-Reefs at shallow depths experience no, or few, years with coral cover exceeding levels likely required to maintain positive carbonate budgets.
-Movement of shallow reefs towards negative carbonate budgets in the future may contribute to phase shifts in reef dominant CaCO~3~ production.
-Shifting from coral driven to encrusting algae driven production, or to bioerosion dominated systems with rapid erosion of physical reef frameworks [@dudgeon2010; @perry2008].
-While reefs at increased depths may be able to maintain coral driven CaCO~3~ production and accumulation into the future for longer.
-Our results suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m), depth contributes greatly to reef resilience and the ability of the reef to maintain positive carbonate budgets under future conditions.
-While similar findings have been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014] regions, depth refugia analyses have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017].
-In contrast, Venegas et al.
-[-@venegas2019] found no association between depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
+Reefs in different temporal clusters largely do not differ in mean modelled DHW levels
+experienced and exhibit overall similar DHW time series. While these reefs experience
+similar magnitude DHWs based on SST, the proportion of the reefs' coral population impacted
+by heat stress events depends on reef depth. Reefs at deeper depths are likely to be
+clustered into High cover clusters. Reefs at shallow depths experience no, or few, years
+with coral cover exceeding levels likely required to maintain positive carbonate budgets.
+Movement of shallow reefs towards negative carbonate budgets in the future may contribute to
+phase shifts in reef dominant CaCO~3~ production. Shifting from coral driven to encrusting
+algae driven production, or to bioerosion dominated systems with rapid erosion of physical
+reef frameworks [@dudgeon2010; @perry2008]. While reefs at increased depths may be able to
+maintain coral driven CaCO~3~ production and accumulation into the future for longer. Our
+results suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m),
+depth contributes greatly to reef resilience and the ability of the reef to maintain
+positive carbonate budgets under future conditions. While similar findings have been
+demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014] regions,
+depth refugia analyses have often focussed on the potential of mesophotic reefs (\> 30m
+deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas
+et al. [-@venegas2019] found no association between depth and the alleviation of heat stress
+across a range of shallow reefs in the Pacific.
 
-These findings support the hypothesis that reefs at greater depths will exhibit characteristics of refugia and more prolonged structural resilience under climate change compared to shallower reefs.
-Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest that rubble instability is inversely correlated with reef depth, possibly limiting juvenile recruitment capacity of shallow reefs.
-A caveat to these depth-resilience findings is the quality of the bathymetry data used to calculate median reef depth.
-As detailed previously, estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution) which can be subject to high degrees of uncertainty, both in terms of the estimated depth at for each pixel as well as their alignment to the established GBRMPA reef outlines.
-Additionally, we do not incorporate the light-based
+These findings support the hypothesis that reefs at greater depths will exhibit
+characteristics of refugia and more prolonged structural resilience under climate change
+compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest
+that rubble instability is inversely correlated with reef depth, possibly limiting juvenile
+recruitment capacity of shallow reefs. A caveat to these depth-resilience findings is the
+quality of the bathymetry data used to calculate median reef depth. As detailed previously,
+estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution)
+which can be subject to high degrees of uncertainty, both in terms of the estimated depth at
+for each pixel as well as their alignment to the established GBRMPA reef outlines.
+Additionally, we do not incorporate the light-based decreases in coral growth rates as depth
+increases [@baker1975; @huston1985; @ruiz-diaz2022].
 
-Current reef restoration and intervention investigation efforts on the GBR, such as deployment of coral seeding and fragment devices, target reefs with suitable sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024].
-While there are no explicit justifications for this depth range, intervention depth is likely constrained by snorkelling and diving deployment and monitoring logistical accessibility, visual identification of sites from the surface, in combination with tourism return value.
-Our results suggest that of the assessed reefs occurring within the 1-10m depth range (1736 reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the GBRMPA management region scale), with many unable to maintain positive carbonate budgets under future conditions.
-Partial dependence analysis revealed a range of depths from 10-15m where the probability of a reef being clustered into the High cover cluster increased substantially.
-Additionally, two-way partial dependence analysis revealed that high incoming connectivity is important for High cluster assignment for reefs at depths of \>10m.
-Considering this 10-15m depth range, and targetting well connected reefs, when assessing possible intervention sites may reduce the exposure of planted and seeded corals to high thermal stress, while still maintaining effective logistical access to sites.
-Managers are also likely to consider the positive potential for flow on effects due to outgoing connectivity when selecting intervention sites [@hock2017].
-While reefs with high outgoing connectivity levels were found to have greater probability of being assigned to low cover clusters when assessed individually (@fig-ts-cluster-pdp-twoway-incoming), within the context of reef depth, reefs with high depths and high outgoing connectivity levels had the greatest probability of being clustered into high cover clusters (@sfig-ts-cluster-pdp-twoway-outgoing).
-These results suggests that interventions targetting deep reefs will also benefit from high incoming and outgoing connectivity levels, allowing for high potential for site resilience and outgoing flow of benefits and recovery.
-Transient, and difficult to measure, properties such as reef connectivity are likely to increase uncertainty in intervention planning to a greater degree than environmental characteristics such as reef depth.
-Overall, reef intervention planning is a complex and challenging decision-making process [@anthony2020], and our results suggest that intervention site depth may be an important factor to additionally consider when assessing the long-term resilience of sites.
+Current reef restoration and intervention investigation efforts on the GBR, such as
+deployment of coral seeding and fragment devices, target reefs with suitable sites in the
+1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are no explicit
+justifications for this depth range, intervention depth is likely constrained by snorkelling
+and diving deployment and monitoring logistical accessibility, visual identification of
+sites from the surface, in combination with tourism return value. Our results suggest that
+of the assessed reefs occurring within the 1-10m depth range (1736 reefs), 57% (991) of
+reefs fall into the low and medium clusters (across all GCMs at the GBRMPA management region
+scale), with many unable to maintain positive carbonate budgets under future conditions.
+Partial dependence analysis revealed a range of depths from 10-15m where the probability of
+a reef being clustered into the High cover cluster increased substantially. Additionally,
+two-way partial dependence analysis revealed that high incoming connectivity is important
+for High cluster assignment for reefs at depths of \>10m. Considering this 10-15m depth
+range, and targetting well connected reefs, when assessing possible intervention sites may
+reduce the exposure of planted and seeded corals to high thermal stress, while still
+maintaining effective logistical access to sites. Managers are also likely to consider the
+positive potential for flow on effects due to outgoing connectivity when selecting
+intervention sites [@hock2017]. While reefs with high outgoing connectivity levels were
+found to have greater probability of being assigned to low cover clusters when assessed
+individually (@fig-ts-cluster-pdp-twoway-incoming), within the context of reef depth, reefs
+with high depths and high outgoing connectivity levels had the greatest probability of being
+clustered into high cover clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results
+suggests that interventions targetting deep reefs will also benefit from high incoming and
+outgoing connectivity levels, allowing for high potential for site resilience and outgoing
+flow of benefits and recovery. Transient, and difficult to measure, properties such as reef
+connectivity are likely to increase uncertainty in intervention planning to a greater degree
+than environmental characteristics such as reef depth. Overall, reef intervention planning
+is a complex and challenging decision-making process [@anthony2020], and our results suggest
+that intervention site depth may be an important factor to additionally consider when
+assessing the long-term resilience of sites.
 
-It is a common conclusion in coral reef ecology that a primary facet of reef resilience is the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008; @torres2024].
-Our results suggest that incoming connectivity contributes positively to high cover cluster allocation for reefs over 10m deep.
-At depths of less than 10m thermal stress may be too high for juveniles to contribute to long term recovery.
-While there is interaction between incoming connectivity and depth for reef cluster prediction, according to available input data, there are few reefs in the GBR that occur at depths \>10m and have Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget), resulting in overall low importance of connectivity as an individual feature for clustering across the GBR.
-Furthermore, our results suggest no direct, first order, relationship between weighted incoming connectivity and the ability of reefs to maintain positive carbonate budgets under future conditions.
-There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent generation connectivity modelling is able to identify reefs that are important for recovery processes, with findings dependent on the larval connectivity model used.
-These investigations were performed using prior generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods, without considering the influence of reef depth on resilience.
-Using updated 1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal sample of particle flows, our results suggest that larval connectivity alone may not be important or reef resilience and recovery, but should be considered in combination with more influential factors such as depth.
-In-depth comparisons and validation of multiple connectivity model outputs would improve certainty and allow for the targetting of reefs by combining abiotic factors such as depth with connectivity.
+It is a common conclusion in coral reef ecology that a primary facet of reef resilience is
+the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008;
+@torres2024]. Our results suggest that incoming connectivity contributes positively to high
+cover cluster allocation for reefs over 10m deep. At depths of less than 10m thermal stress
+may be too high for juveniles to contribute to long term recovery. While there is
+interaction between incoming connectivity and depth for reef cluster prediction, according
+to available input data, there are few reefs in the GBR that occur at depths \>10m and have
+Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget),
+resulting in overall low importance of connectivity as an individual feature for clustering
+across the GBR. Furthermore, our results suggest no direct, first order, relationship
+between weighted incoming connectivity and the ability of reefs to maintain positive
+carbonate budgets under future conditions. There has been contrasting evidence [@bode2018;
+@hock2017] surrounding whether recent generation connectivity modelling is able to identify
+reefs that are important for recovery processes, with findings dependent on the larval
+connectivity model used. These investigations were performed using prior generations of
+larval connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018]
+time periods, without considering the influence of reef depth on resilience. Using updated
+1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal sample
+of particle flows, our results suggest that larval connectivity alone may not be important
+or reef resilience and recovery, but should be considered in combination with more
+influential factors such as depth. In-depth comparisons and validation of multiple
+connectivity model outputs would improve certainty and allow for the targetting of reefs by
+combining abiotic factors such as depth with connectivity.
 
-Our findings on the importance of connectivity may differ from literature due to the highly uncertain nature of larval connectivity modelling [@vogt-vincent2023], the way larval flows and juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early bleaching events decreasing the breeding capacity of strongly connected reefs.
-Analysing daily connectivity data Vogt-Vincent et al.
-[-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for capturing the seasonal - ecological time scale connectivity between locations due to high daily variability in connectivity data.
-This is supported by the connectivity data used in our investigation, which have large relative standard deviations for connectivity between reefs over the 24 days used (@sfig-connectivity-rsd).
-Using alternative summarisation methods that capture ecological-timescale patterns in coral larval dispersal, such as cumulated implicit connectivity [@vogt-vincent2023], future investigations may find increased importance of both depth and reef connectivity for resilience, in line with other investigations [@hock2017; @torres2024].
-Further improvements and research in connectivity modelling are necessary when incorporating connectivity as a supplementary factor in reef resilience and intervention-planning analyses.
+Our findings on the importance of connectivity may differ from literature due to the highly
+uncertain nature of larval connectivity modelling [@vogt-vincent2023], the way larval flows
+and juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early
+bleaching events decreasing the breeding capacity of strongly connected reefs. Analysing
+daily connectivity data Vogt-Vincent et al. [-@vogt-vincent2023] suggest that time-mean
+connectivity may not be suitable for capturing the seasonal - ecological time scale
+connectivity between locations due to high daily variability in connectivity data. This is
+supported by the connectivity data used in our investigation, which have large relative
+standard deviations for connectivity between reefs over the 24 days used
+(@sfig-connectivity-rsd). Using alternative summarisation methods that capture
+ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
+connectivity [@vogt-vincent2023], future investigations may find increased importance of
+both depth and reef connectivity for resilience, in line with other investigations
+[@hock2017; @torres2024]. Further improvements and research in connectivity modelling are
+necessary when incorporating connectivity as a supplementary factor in reef resilience and
+intervention-planning analyses.
 
-Under all GCMs many reefs are projected to suffer substantial declines in coral cover relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the lowest cover level cluster at the management area scale across GCMs.
-NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future.
-Differences between Low, Medium and High reef clusters in cover time series are most notable under these two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories).
-Maintenance of coral cover into the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of future recovery and timespan of cover maintenance increase as GCM ECS increases (@fig-gcm-cover-trajectories).
-Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2) large declines and lower rates of recovery in high cover clusters are common compared to lower-ECS GCMs.
+Under all GCMs many reefs are projected to suffer substantial declines in coral cover
+relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the
+lowest cover level cluster at the management area scale across GCMs. NorESM2-MM and
+ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future. Differences
+between Low, Medium and High reef clusters in cover time series are most notable under these
+two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into
+the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of
+future recovery and timespan of cover maintenance increase as GCM ECS increases
+(@fig-gcm-cover-trajectories). Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
+large declines and lower rates of recovery in high cover clusters are common compared to
+lower-ECS GCMs.
 
-The large differences in cover time series seen across the GCMs suggest that it is important to consider uncertainty in future conditions when assessing possible biological responses to change.
-This is supported by recent literature suggesting an effective approach to capturing climate change uncertainty is to model responses using GCMs separately [@shepherd2018].
-Despite large differences in coral cover across GCMs, the patterns identified between low, medium and high clusters of reefs suggest that the relative importance of environmental and biological factors such as depth refugia, connectivity and surface DHW levels is consistent across scenarios.
+The large differences in cover time series seen across the GCMs suggest that it is important
+to consider uncertainty in future conditions when assessing possible biological responses to
+change. This is supported by recent literature suggesting an effective approach to capturing
+climate change uncertainty is to model responses using GCMs separately [@shepherd2018].
+Despite large differences in coral cover across GCMs, the patterns identified between low,
+medium and high clusters of reefs suggest that the relative importance of environmental and
+biological factors such as depth refugia, connectivity and surface DHW levels is consistent
+across scenarios.
 
@@
 
-There are multiple caveats in how coral ecosystem dynamics are modelled in this investigation.
-We model coral colonies as circular diameter values that are tracked over timesteps through growth.
-Additionally, we do not model the direct influence of light intensity on coral growth or the negative influence of depth on coral growth rates due to reduced available light levels.
-[@baker1975; @huston1985; @ruiz-diaz2022].
-If included in this investigation it is possible that reef recovery ability, via regrowth, would be reduced at greater depths, reducing the positive effect of depth refugia for temporal resilience.
-Additionally, reduced growth rates at increased depths may reduce the carbonate budget maintenance of reefs due to lower rates of CaCO~3~ accretion.
-Due to the availability of quality future projected data we do not consider other important impacts such as waves, cyclones, currents and Crown of Thorns Starfish (CoTS) on coral colony survival and bleaching [@massel1993; @deaker2022].
+There are multiple caveats in how coral ecosystem dynamics are modelled in this
+investigation. We model coral colonies as circular diameter values that are tracked over
+timesteps through growth. Additionally, we do not model the direct influence of light
+intensity on coral growth or the negative influence of depth on coral growth rates due to
+reduced available light levels [@baker1975; @huston1985; @ruiz-diaz2022]. If included in
+this investigation it is possible that reef recovery ability, via regrowth, would be reduced
+at greater depths, reducing the positive effect of depth refugia for temporal resilience.
+Additionally, reduced growth rates at increased depths may reduce the carbonate budget
+maintenance of reefs due to lower rates of CaCO~3~ accretion. Due to the availability of
+quality future projected data we do not consider other important impacts such as waves,
+cyclones, currents and Crown of Thorns Starfish (CoTS) on coral colony survival and
+bleaching [@massel1993; @deaker2022].
 
-Uncertainty in connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress projections are likely to influence the results obtained in this investigation.
-While the resolution of connectivity data used in this investigation improves upon data used in comparable studies [@bozec2025], the time-mean implementation used may not effectively capture long term patterns [@vogt-vincent2023].
-Using alternative connectivity implementation methods that better capture the ecological-timescale trends in reef connections rather than the high daily variability, would improve confidence in the connectivity findings of this investigation [@vogt-vincent2023].
-Additionally greater year - sample sizes for baseline connectivity data as future computation improvements are made, along with GBR scale validation efforts, will improve confidence in connectivity data for ecological modelling and management applications.
-The DHW data used in this investigation have not been bias corrected for the Great Barrier Reef region and are part of a wider Australian dataset [@dixon2022] developed using statistical downscaling.
-Additionally, Lachs et al.
-[@lachs2021] suggest the utility of DHW levels for prediction of coral bleaching can be improved by reducing the threshold for HotSpot Anomaly values from MMM +1 to MMM and reducing the accumulation window from 12 weeks to 8 weeks.
-We investigate a range of future climate responses, thermal projections and ecological parameterisations of ADRIA - CoralBlox to account for many possible futures, and our results suggest the factors that influence reef resilience are consistent across these scenarios.
+Uncertainty in connectivity modelling outputs, satellite-derived bathymetry data and future
+thermal stress projections are likely to influence the results obtained in this
+investigation. While the resolution of connectivity data used in this investigation improves
+upon data used in comparable studies [@bozec2025], the time-mean implementation used may not
+effectively capture long term patterns [@vogt-vincent2023]. Using alternative connectivity
+implementation methods that better capture the ecological-timescale trends in reef
+connections rather than the high daily variability, would improve confidence in the
+connectivity findings of this investigation [@vogt-vincent2023]. Additionally greater year -
+sample sizes for baseline connectivity data as future computation improvements are made,
+along with GBR scale validation efforts, will improve confidence in connectivity data for
+ecological modelling and management applications. The DHW data used in this investigation
+have not been bias corrected for the Great Barrier Reef region and are part of a wider
+Australian dataset [@dixon2022] developed using statistical downscaling. Additionally, Lachs
+et al. [@lachs2021] suggest the utility of DHW levels for prediction of coral bleaching can
+be improved by reducing the threshold for HotSpot Anomaly values from MMM +1 to MMM and
+reducing the accumulation window from 12 weeks to 8 weeks. We investigate a range of future
+climate responses, thermal projections and ecological parameterisations of ADRIA - CoralBlox
+to account for many possible futures, and our results suggest the factors that influence
+reef resilience are consistent across these scenarios.
 
-Additionally, it is currently not possible to obtain highly accurate and precise estimates of reef depth at the GBR-scale.
-Data adopted for the given assessment are said to be accurate up to 15m from Mean Sea Level [@GBRMPA2020; @li2021], however there are many sources of uncertainty in the depth estimates used for this study.
-Satellite-derived estimates are subject to different bottom types (rock, sand, seagrass, etc) and their effect on reflectance, the water penetration depth of satellite sensors, influence of local conditions (e.g., turbidity and wave activity), among many other factors.
-The median depths for each indicative reef area were extracted from bathymetry data using zonal statistics and depth values beyond the stated 15m accuracy threshold [@GBRMPA2020] were included.
-The resulting depth estimates are therefore highly uncertain and are only adopted as a useful indication for the purpose of the presented analysis.
-They are not intended to be an accurate and precise report of reef depths across the GBR.
+Additionally, it is currently not possible to obtain highly accurate and precise estimates
+of reef depth at the GBR-scale. Data adopted for the given assessment are said to be
+accurate up to 15m from Mean Sea Level [@GBRMPA2020; @li2021], however there are many
+sources of uncertainty in the depth estimates used for this study. Satellite-derived
+estimates are subject to different bottom types (rock, sand, seagrass, etc) and their effect
+on reflectance, the water penetration depth of satellite sensors, influence of local
+conditions (e.g., turbidity and wave activity), among many other factors. The median depths
+for each indicative reef area were extracted from bathymetry data using zonal statistics and
+depth values beyond the stated 15m accuracy threshold [@GBRMPA2020] were included. The
+resulting depth estimates are therefore highly uncertain and are only adopted as a useful
+indication for the purpose of the presented analysis. They are not intended to be an
+accurate and precise report of reef depths across the GBR.
 
-In addition to the usual challenges of deriving data from satellite imagery, it is acknowledged that there is high potential for misalignment between the bathymetry data and GBRMPA reef outlines.
-Hammerton and Lawrey [-@hammerton2025], for example, identified 120 false positives, where features identified as reefs were sand banks or rocky reefs (rather than coral reefs).
-Reefs with bathymetry data of less than 5% of its indicative area were excluded from analysis to ensure analyses were not conducted on reefs with no data coverage (see @sfig-depth-cutoff).
-The existing GBRMPA reef outlines were adopted to align with other ongoing modelling and analyses conducted as part of the Reef Restoration and Adaptation Program (<https://gbrrestoration.org>; [@thereef]).
+In addition to the usual challenges of deriving data from satellite imagery, it is
+acknowledged that there is high potential for misalignment between the bathymetry data and
+GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton2025], for example, identified 120
+false positives, where features identified as reefs were sand banks or rocky reefs (rather
+than coral reefs). Reefs with bathymetry data of less than 5% of its indicative area were
+excluded from analysis to ensure analyses were not conducted on reefs with no data coverage
+(see @sfig-depth-cutoff). The existing GBRMPA reef outlines were adopted to align with other
+ongoing modelling and analyses conducted as part of the Reef Restoration and Adaptation
+Program (<https://gbrrestoration.org>; [@thereef]).
 
-The modelling conducted with ADRIA-CoralBlox itself is subject to many uncertainties.
-For one, a formal mechanistic and spatial validation of the model represents an area for future refinement and is the focus of a future publication.
-Indicative results are included in the supplementary **\[TI: For Pedro to include!
-:`D`\].** The consistency of projected patterns with known coral-climate relationships and reef characteristics provides confidence in the model's ability to meaningfully capture ecological signals at the GBR-scale.
-The mechanistic basis of the model, combined with qualitative assessment of model behavior, supports the robustness of our findings for understanding broad-scale coral cover responses to climatic drivers.
-The aim here, however, was to assess the relative influence of reef characteristics on structural resilience under future conditions, rather than provide spatially explicit and precise predictions of reef outcomes.
-Using this approach, we suggest that reef depth is an important factor for reef resilience under thermal stress.
+The modelling conducted with ADRIA-CoralBlox itself is subject to many uncertainties. For
+one, a formal mechanistic and spatial validation of the model represents an area for future
+refinement and is the focus of a future publication. Indicative results are included in the
+supplementary **\[TI: For Pedro to include! :`D`\].** The consistency of projected patterns
+with known coral-climate relationships and reef characteristics provides confidence in the
+model's ability to meaningfully capture ecological signals at the GBR-scale. The mechanistic
+basis of the model, combined with qualitative assessment of model behavior, supports the
+robustness of our findings for understanding broad-scale coral cover responses to climatic
+drivers. The aim here, however, was to assess the relative influence of reef characteristics
+on structural resilience under future conditions, rather than provide spatially explicit and
+precise predictions of reef outcomes. Using this approach, we suggest that reef depth is an
+important factor for reef resilience under thermal stress.
 
-Improvements in remote sensing approaches for broad scale bathymetry measurement and understanding of how depth impacts experienced thermal stress on reefs will further enhance investigations of depth as a critical factor for reef resilience.
-Additional analyses could build on the findings of this study by assessing the impacts of prioritising reef depth in reef intervention decision making.
-Future analyses could incorporate other environmental and ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn Starfish [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
+Improvements in remote sensing approaches for broad scale bathymetry measurement and
+understanding of how depth impacts experienced thermal stress on reefs will further enhance
+investigations of depth as a critical factor for reef resilience. Additional analyses could
+build on the findings of this study by assessing the impacts of prioritising reef depth in
+reef intervention decision making. Future analyses could incorporate other environmental and
+ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn Starfish
+[@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
 
@@
 
-The results presented suggest that when modelled as part of a large and complex ecosystem, reef depth is a key factor contributing to ongoing reef resilience.
-We provide evidence in support of depth as a form of thermal refugia for shallow-water reefs on the GBR.
-Targetting reefs with median depths greater than 10m and high incoming and ougoing larval connections may aid in identifying the most resilient reefs under climate change.
-We suggest further analyses that investigate the benefits of incorporating depth-based resilience into reef intervention decision making, as well as further research and development in connectivity modelling methods for whole-ecosystem scales.
+The results presented suggest that when modelled as part of a large and complex ecosystem,
+reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in
+support of depth as a form of thermal refugia for shallow-water reefs on the GBR. Targetting
+reefs with median depths greater than 10m and high incoming and ougoing larval connections
+may aid in identifying the most resilient reefs under climate change. We suggest further
+analyses that investigate the benefits of incorporating depth-based resilience into reef
+intervention decision making, as well as further research and development in connectivity
+modelling methods for whole-ecosystem scales.
 
@@
 ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
-The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al., 2021).](../figs/ecs_plot.png){#sfig-ecs fig-align="center" width="10cm"}
+The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
+the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
+2021).](../figs/ecs_plot.png){#sfig-ecs fig-align="center" width="10cm"}
 
-![Distribution of GBRMPA [-@GBRMPA2020] satellite derived depth data coverage levels across 3806 possible reefs.
-Reefs below the 5% data coverage threshold (represented by the red vertical line) were removed from the investigation.](../figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff fig-align="center" width="14.8cm" height="9.5cm"}
+![Distribution of GBRMPA [-@GBRMPA2020] satellite derived depth data coverage levels across
+3806 possible reefs. Reefs below the 5% data coverage threshold (represented by the red
+vertical line) were removed from the
+investigation.](../figs/reef_depth_included_cutoff.png){#sfig-depth-cutoff
+fig-align="center" width="14.8cm" height="9.5cm"}
 
-![Reef Degree Heating Week time series clustered within each management area, for each GCM analysed.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines represent the cluster median time series and bands represent the 2.5 to 97.5 percentile confidence intervals.
-Each management area is represented five times (for each GCM), with each GCM displayed horizontally.](../figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories fig-align="center" width="14.82cm"}
+![Reef Degree Heating Week time series clustered within each management area, for each GCM
+analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
+between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters with
+intermediate median area-relative cover between 2030 and 2060 within each bioregion. ‘High’
+clusters (blue) are clusters with the highest median area-relative cover between 2030 and
+2060 within each bioregion. Solid lines represent the cluster median time series and bands
+represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
+represented five times (for each GCM), with each GCM displayed
+horizontally.](../figs/GCM_dhw_timeseries_plot.png){#sfig-gcm-dhw-trajectories
+fig-align="center" width="14.82cm"}
 
 | Metric | Used in | Definition | Justification |
-|------------------|------------------|------------------|------------------|
+|-----------------------|-----------------------|-----------------------|-----------------------|
 | Percentage coral cover time series | Timeseries clustering, Carbonate budget analysis | Total coral cover as a percentage of reef area | To summarise coral population health over time |
@@
 
-![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all considered reefs (points), coloured by management area scale cluster assignment.
-Colour-coded areas outline GBR marine park management regions, where orange represents the Far Northern management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007].
-Reef centroids are marked individually for visual clarity.
-Reefs that do not have a consistent cluster assignment level across all GCMs at mangement area scale are coloured grey.
-All consistently clustered reefs are coloured according to their management area scale cluster assignment.
-Green represents reefs in the low cover cluster, orange represents reefs in the medium cover cluster and blue represents reefs in the high cover cluster.
-All 2429 reefs included in this investigation are represented in this figure.
-Annotations represent major coastal settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map fig-align="center" width="14.82cm"}
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by management area scale cluster assignment.
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity. Reefs that do not have a consistent cluster
+assignment level across all GCMs at mangement area scale are coloured grey. All consistently
+clustered reefs are coloured according to their management area scale cluster assignment.
+Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
+cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
+investigation are represented in this figure. Annotations represent major coastal
+settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
+fig-align="center" width="14.82cm"}
 
 ![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
-Green indicates a low cover cluster assignment, orange represents a medium cover assignment and blue represents assignment of a reef to a high coral cover cluster.
-The vertical width of reef elements varies depending on the number of reefs within the bioregion (displayed on the y axis).
-The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5, ACCESS-CM2, NorESM2-MM and GFDL-CM4).](../figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment fig-align="center" width="14.82cm"}
+Green indicates a low cover cluster assignment, orange represents a medium cover assignment
+and blue represents assignment of a reef to a high coral cover cluster. The vertical width
+of reef elements varies depending on the number of reefs within the bioregion (displayed on
+the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
+ACCESS-CM2, NorESM2-MM and
+GFDL-CM4).](../figs/GCM_bioregion_cluster_assignments.png){#sfig-gcm-bioregion-cluster-assignment
+fig-align="center" width="14.82cm"}
 
-![Partial dependence plot indicating the probability of cluster assignment along interacting values of median reef depth (metres) and Log10 weighted outgoing connectivity.
-Colour indicates the probability of assignment to each cluster, with lighter colours indicating higher probability of assignment.
-Panel A shows the probability of assignment for the Low cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability for the High cluster category.
-Probability values for each cluster are generated by the random forest classifier using each combination of depth and weighted outgoing connectivity values along the axes at 50 grid points.
-The actual distributions of depth and outgoing connectivity values for reefs are displayed in panels D and E respectively.](../figs/ts_cluster_rf_twoway_depth_outgoingconn_pdp.png){#sfig-ts-cluster-pdp-twoway-outgoing fig-align="center" width="14.82cm"}
+![Partial dependence plot indicating the probability of cluster assignment along interacting
+values of median reef depth (metres) and Log10 weighted outgoing connectivity. Colour
+indicates the probability of assignment to each cluster, with lighter colours indicating
+higher probability of assignment. Panel A shows the probability of assignment for the Low
+cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability
+for the High cluster category. Probability values for each cluster are generated by the
+random forest classifier using each combination of depth and weighted outgoing connectivity
+values along the axes at 50 grid points. The actual distributions of depth and outgoing
+connectivity values for reefs are displayed in panels D and E
+respectively.](../figs/ts_cluster_rf_twoway_depth_outgoingconn_pdp.png){#sfig-ts-cluster-pdp-twoway-outgoing
+fig-align="center" width="14.82cm"}
 
-![Scatter plots indicating the bioregion test-prediction accuracy (proportion of reefs in each bioregion assigned correct clusters) from the Random Forest model.
-Plot panels represent the bioregion accuracy across various predictor ranges and bioregion attributes, such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength, Source-to-sink ratio and the number of reefs in each bioregion.](../figs/rf_performance_across_predictors.png){#sfig-rf-predictor-perf fig-align="center" width="14.82cm"}
+![Scatter plots indicating the bioregion test-prediction accuracy (proportion of reefs in
+each bioregion assigned correct clusters) from the Random Forest model. Plot panels
+represent the bioregion accuracy across various predictor ranges and bioregion attributes,
+such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength,
+Source-to-sink ratio and the number of reefs in each
+bioregion.](../figs/rf_performance_across_predictors.png){#sfig-rf-predictor-perf
+fig-align="center" width="14.82cm"}
 
-![Heatmap indicating reef connectivity relative standard deviation (RSD %).
-Reef connectivity relative standard deviation represents the reef standard deviation connection strength as a percentage of reef mean connection strength.
-Lighter colours indicate higher RSD % values.](../figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd fig-align="center" width="14.82cm"}
+![Heatmap indicating reef connectivity relative standard deviation (RSD %). Reef
+connectivity relative standard deviation represents the reef standard deviation connection
+strength as a percentage of reef mean connection strength. Lighter colours indicate higher
+RSD % values.](../figs/connectivity_rsd_percent.png){#sfig-connectivity-rsd
+fig-align="center" width="14.82cm"}
 
@@
 
-The CoralBlox model incorporates linear extension (growth) and background mortality rates that are dependent on the size and functional group of a coral colony.
-Environmental disturbances and reproduction are not directly considered within CoralBlox.
-Instead, these factors are considered by making changes to the distribution of colonies within CoralBlox timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform [@iwanaga2023].
-Within ADRIA, we incorporate coral life history and environmental events in the following order: coral colony growth; coral reproduction; larval connectivity and settlement; and coral bleaching due to heat stress.
-As ADRIA and CoralBlox are coupled together to represent the system, we refer to both as ADRIA-CoralBlox.
+The CoralBlox model incorporates linear extension (growth) and background mortality rates
+that are dependent on the size and functional group of a coral colony. Environmental
+disturbances and reproduction are not directly considered within CoralBlox. Instead, these
+factors are considered by making changes to the distribution of colonies within CoralBlox
+timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform
+[@iwanaga2023]. Within ADRIA, we incorporate coral life history and environmental events in
+the following order: coral colony growth; coral reproduction; larval connectivity and
+settlement; and coral bleaching due to heat stress. As ADRIA and CoralBlox are coupled
+together to represent the system, we refer to both as ADRIA-CoralBlox.
 
-Coral fecundity rates are dependent on colony size and functional group following the results of Hall & Hughes [-@hall1996].
-Coral fertilization rates are not considered within this model, however larval survival and viability are incorporated in connectivity modelling (see Connectivity modelling).
-Viable larvae settle at a reef location and are incorporated into the model as the smallest size class but are not directly impacted by modelled bleaching mortality.
-There has been contrasting evidence for juvenile corals being immune to thermal bleaching events [@depczynski2013], we assume the high background mortality of juveniles includes thermal stress [@álvarez-noriega2018].
+Coral fecundity rates are dependent on colony size and functional group following the
+results of Hall & Hughes [-@hall1996]. Coral fertilization rates are not considered within
+this model, however larval survival and viability are incorporated in connectivity modelling
+(see Connectivity modelling). Viable larvae settle at a reef location and are incorporated
+into the model as the smallest size class but are not directly impacted by modelled
+bleaching mortality. There has been contrasting evidence for juvenile corals being immune to
+thermal bleaching events [@depczynski2013], we assume the high background mortality of
+juveniles includes thermal stress [@álvarez-noriega2018].
 
@@
 
-Scenarios were sampled from the range of environmental and ecological factors using the low-discrepancy Sobol' sampling method [@sobol1967; @sobol1993] with Owen scrambling [@owen1995].
-A base of 2 and padding of 32 is used for the Owen scrambling.
-Ecological factors were sampled using a +/- 10% range relative to their nominal (assumed best guess) value.
+Scenarios were sampled from the range of environmental and ecological factors using the
+low-discrepancy Sobol' sampling method [@sobol1967; @sobol1993] with Owen scrambling
+[@owen1995]. A base of 2 and padding of 32 is used for the Owen scrambling. Ecological
+factors were sampled using a +/- 10% range relative to their nominal (assumed best guess)
+value.
 
@@
 
-In this investigation we model five functional groups common to the GBR, tabular Acropora, corymbose Acropora, corymbose non-Acropora, small massives and large massives.
-We do not model arborescent Acropora forms due to their distinct life history from other morphological groups.
-CoralBlox uses user-defined size classes that influence size-dependent growth and mortality rates, through which the coral colonies progress as they grow in diameter.
-Within ADRIA, we define the distributions of these parameters, and the size classes based on ecological monitoring data from the Ecological Intelligence for Reef Restoration Program (EcoRRAP) ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
+In this investigation we model five functional groups common to the GBR, tabular Acropora,
+corymbose Acropora, corymbose non-Acropora, small massives and large massives. We do not
+model arborescent Acropora forms due to their distinct life history from other morphological
+groups. CoralBlox uses user-defined size classes that influence size-dependent growth and
+mortality rates, through which the coral colonies progress as they grow in diameter. Within
+ADRIA, we define the distributions of these parameters, and the size classes based on
+ecological monitoring data from the Ecological Intelligence for Reef Restoration Program
+(EcoRRAP) ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
 
-In ADRIA we track the thermal tolerance of each functional group and size class as a truncated normal distribution that is updated in each timestep following growth and recruitment.
-This distribution determines the proportion of the population on a reef that is susceptible to bleaching (i.e.
-has a thermal threshold below the experienced DHW value).
+In ADRIA we track the thermal tolerance of each functional group and size class as a
+truncated normal distribution that is updated in each timestep following growth and
+recruitment. This distribution determines the proportion of the population on a reef that is
+susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
 Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
@@
 
-The CID timeseries clustering metric corrects the Euclidean distance between pairs of time series (which accounts for magnitude differences) with the complexity of each time series (obtained through a measure of their variability) to ensure reefs are clustered based on their underlying temporal dynamics rather than simply their average coral cover.
-The process creates a distance matrix of n \* n dimensions (where n is the number of time series in the group) that is clustered using a k-medoids clustering algorithm [cf.
-@steinmann2020].
-The three reef clusters are labelled with qualitative-ordered clusters from Low, Medium and High based on their median cover relative to each other cluster over the 2030-2060 period.
-The selected time frame prevents the classification from being overly influenced by any steep declines in the initial years of simulations and avoids the post-2060 time period where reefs are projected to be under severe stress and in a declined state [@bozec2025].
+The CID timeseries clustering metric corrects the Euclidean distance between pairs of time
+series (which accounts for magnitude differences) with the complexity of each time series
+(obtained through a measure of their variability) to ensure reefs are clustered based on
+their underlying temporal dynamics rather than simply their average coral cover. The process
+creates a distance matrix of n \* n dimensions (where n is the number of time series in the
+group) that is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The
+three reef clusters are labelled with qualitative-ordered clusters from Low, Medium and High
+based on their median cover relative to each other cluster over the 2030-2060 period. The
+selected time frame prevents the classification from being overly influenced by any steep
+declines in the initial years of simulations and avoids the post-2060 time period where
+reefs are projected to be under severe stress and in a declined state [@bozec2025].
 
@@
 
-![Scatter plot indicating reef median depth (metres) and Log10 weighted incoming connectivity for each reef.
-Point colours represent the mean number of years each reef maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget fig-align="center" width="10cm"}
+![Scatter plot indicating reef median depth (metres) and Log10 weighted incoming
+connectivity for each reef. Point colours represent the mean number of years each reef
+maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover.
+Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
+fig-align="center" width="10cm"}
 
@@
 
-![Reef area-relative coral cover time series clustered within each bioregion.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines represent the cluster median time series and bands represent the 95th percentile confidence intervals.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries fig-align="center" width="14.82cm"}
+![Reef area-relative coral cover time series clustered within each bioregion. ‘Low’ clusters
+(green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
+each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
+area-relative cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2060 within each
+bioregion. Solid lines represent the cluster median time series and bands represent the 95th
+percentile confidence intervals. Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
+fig-align="center" width="14.82cm"}
 
-![Mean time series DHW values for reefs within each bioregion, separated into clusters assigned by time series clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines represent the median DHW level for each cluster and bands represent the distribution of mean DHW levels within each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean fig-align="center" width="14.82cm"}
+![Mean time series DHW values for reefs within each bioregion, separated into clusters
+assigned by time series clustering. ‘Low’ clusters (green) are clusters with the lowest
+median area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters
+(orange) are clusters with intermediate median area-relative cover between 2030 and 2060
+within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
+area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the
+median DHW level for each cluster and bands represent the distribution of mean DHW levels
+within each cluster. Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
+fig-align="center" width="14.82cm"}
 
-![Reef carrying capacity (coral habitable area, in base-10 log scale) for reefs within each bioregion, separated into clusters assigned by time series clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines represent the median carrying capacity for each cluster and bands represent the distribution of values within each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/carrying_capacity_bioregion_violin.png){#sfig-access-esm1-5-bioregion-carrying-capacity fig-align="center" width="14.82cm"}
+![Reef carrying capacity (coral habitable area, in base-10 log scale) for reefs within each
+bioregion, separated into clusters assigned by time series clustering. ‘Low’ clusters
+(green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
+each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
+area-relative cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are
+clusters with the highest median area-relative cover between 2030 and 2060 within each
+bioregion. Solid lines represent the median carrying capacity for each cluster and bands
+represent the distribution of values within each cluster. Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/bioregion/carrying_capacity_bioregion_violin.png){#sfig-access-esm1-5-bioregion-carrying-capacity
+fig-align="center" width="14.82cm"}
 
-![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion, separated into clusters assigned by time series clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines within each violin represent the median source-to-sink ratio for each cluster and bands represent the distribution of source-to-sink ratios within each cluster.
-The vertical grey line represent a source-to-sink ratio of 0 (in base-10 log scale) indicating equal outgoing and incoming connectivity levels.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi fig-align="center" width="14.82cm"}
+![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion,
+separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2060 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
+lines within each violin represent the median source-to-sink ratio for each cluster and
+bands represent the distribution of source-to-sink ratios within each cluster. The vertical
+grey line represent a source-to-sink ratio of 0 (in base-10 log scale) indicating equal
+outgoing and incoming connectivity levels. Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
+fig-align="center" width="14.82cm"}
 
-![Weighted incoming connectivity (in base-10 log scale) for reefs within each bioregion, separated into clusters assigned by time series clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines within each violin represent the median base-10 log of weighted incoming connectivity for each cluster and bands represent the distribution of connectivity values within each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_incoming_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedincoming fig-align="center" width="14.82cm"}
+![Weighted incoming connectivity (in base-10 log scale) for reefs within each bioregion,
+separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2060 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
+lines within each violin represent the median base-10 log of weighted incoming connectivity
+for each cluster and bands represent the distribution of connectivity values within each
+cluster. Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_incoming_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedincoming
+fig-align="center" width="14.82cm"}
 
-![Weighted outgoing connectivity (in base-10 log scale) for reefs within each bioregion, separated into clusters assigned by time series clustering.
-‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2060 within each bioregion.
-‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2060 within each bioregion.
-Solid lines within each violin represent the median base-10 log of weighted outgoing connectivity for each cluster and bands represent the distribution of connectivity values within each cluster.
-Displays results for ACCESS-ESM1-5 GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_outgoing_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedoutgoing fig-align="center" width="14.82cm"}
+![Weighted outgoing connectivity (in base-10 log scale) for reefs within each bioregion,
+separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2060 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
+lines within each violin represent the median base-10 log of weighted outgoing connectivity
+for each cluster and bands represent the distribution of connectivity values within each
+cluster. Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_outgoing_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedoutgoing
+fig-align="center" width="14.82cm"}

### 2025-09-09 paper/paper_draft.qmd
Add map plot files to paper. Still need to add to discussion
Also regenerate all figures

@@
 
-To assess the impact of reef connectivity on modelled outcomes we summarise inter-reef
-connections using weighted connectivity metrics (incoming and outgoing) and the ratio of
-source-to-sink connectivity for each reef. Weighted incoming connectivity is calculated by
+To assess the impact of reef connectivity on modelled outcomes we summarise incoming
+connectivity (weighted incoming connectivity), outgoing connectivity (outgoing connection strength), the ratio of
+source-to-sink connectivity, and larval retention probability for each reef. Weighted incoming connectivity is calculated by
 summing the product of each connection strength incoming to a target reef and the mean
@@
 target reef has weak (or no) incoming connections or is supplied by small source
-populations. Weighted outgoing connectivity is calculated as the product of outgoing
-connectivity strength from a target reef and the mean timeseries absolute coral cover
-(km^2^) of the target reef, representing the larval flow leaving the target reef population.
-A limitation of these weighted connectivity metrics is that they do not incorporate the
+populations. A limitation of weighted incoming connectivity is it does not incorporate the
 proportion of the source reef's population that is reproducing and producing larvae, instead
-taking the total coral cover area as an indicator of larval productivity. The ratio of
+taking the total coral cover area as an indicator of larval productivity.
+Outgoing connection strength is calculated as the sum of all outgoing transition probabilities from a target reef.
+Outgoing connection strength has a theoretical maximum of one (all larvae reach settlement on sink reefs), however the large size of the GBR combined with larval mortality considerations result in outgoing connection strength values much lower than one.
+The ratio of
 source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
@@
 value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
-larval flow.
+larval flow. Reef larval retention probability indicates the proportion of spawned larvae from a target reef that remain to settlement.
 
@@
 between Low, Medium and High clusters. These characteristics include reef median depth, mean
-time series DHW, ratio of source-to-sink larval connectivity, weighted incoming
-connectivity, weighted outgoing connectivity and reef carrying capacity (coral habitable
+time series DHW, weighted incoming
+connectivity, outgoing connection strength, ratio of source-to-sink larval connectivity, larval retention probability and reef carrying capacity (coral habitable
 area).
@@
 
-Across six of the 29 bioregions reefs in the high cover cluster have lower mean DHW, Log-10
-carrying capacity and Log-10 weighted outgoing connectivity values than reefs in other
-clusters (@sfig-access-esm1-5-bioregion-dhwmean;
-@sfig-access-esm1-5-bioregion-carrying-capacity;
-@sfig-access-esm1-5-bioregion-weightedoutgoing). There were no consistent patterns across
-bioregions in their reefs' Log-10 coral carrying capacity area and cluster assignment
-(@sfig-access-esm1-5-bioregion-carrying-capacity). Across most bioregions there were not
-consistent differences between clusters in connectivity metrics such as Log-10
-source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10
-weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming).
+Across bioregions there were no consistent patterns between reef clusters in mean DHW values (@sfig-access-esm1-5-bioregion-dhwmean), Log-10
+weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming), Log-10 outgoing connection strength (@sfig-access-esm1-5-bioregion-outoingconn), Log-10
+source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 larval retention probability (@sfig-access-esm1-5-bioregion-selfconn).
+Across six of the 29 bioregions reefs in the high cover cluster have lower Log-10
+carrying capacity values than reefs in other
+clusters (@sfig-access-esm1-5-bioregion-carrying-capacity).
 
@@
 further justified by its low feature importance score of 9%, the lowest of all predictors
-(@fig-ts-cluster-pdp; Panel A). Reef median depth and mean DHW level have the highest
-feature importance scores, accounting for 25% and 16% predictive importance respectively.
-Weighted incoming and outgoing connectivity (Log10) features account for \~13.6% feature
-importance. The carrying capacity of a reef accounts for 12.3% feature importance. Reef
-source-to-sink ratio (Log10) both had feature importance scores of \~10%.
+(@fig-ts-cluster-pdp; Panel A). Reef median depth, mean DHW level and weighted incoming connectivity (Log10) have the highest
+feature importance scores, accounting for 22%, 17% and 14% predictive importance respectively.
+The carrying capacity of a reef accounts for 12% feature importance, while outgoing connection strength, source-to-sink ratio and larval retention account for 10%, 9% and 7% respectively.
 
@@
 
-Analyses for source-to-sink ratio and weighted incoming and outgoing connectivity metrics
+Analyses for source-to-sink ratio and incoming and outgoing connectivity metrics
 suggest that reefs with greater outgoing connectivity and lower incoming connectivity levels
@@
 reefs with low incoming connectivity are more likely to be assigned to a Medium cover
-cluster (@fig-ts-cluster-pdp-twoway-incoming). Two-way analyses, for depth and weighted
-outgoing connectivity, revealed a slight interaction with the increased low-cluster
-probability for reefs of high outgoing connectivity primarily concentrated in shallow reefs,
-while deep reefs with high outgoing connectivity have the greatest probability of being
+cluster (@fig-ts-cluster-pdp-twoway-incoming).
+Two-way analyses, for depth and outgoing connection strength, revealed a slight interaction with deep reefs with high outgoing connectivity having the greatest probability of being
 clustered into a high cover cluster (@sfig-ts-cluster-pdp-twoway-outgoing).
@@
 positive potential for flow on effects due to outgoing connectivity when selecting
-intervention sites [@hock2017]. While reefs with high outgoing connectivity levels were
-found to have greater probability of being assigned to low cover clusters when assessed
-individually (@fig-ts-cluster-pdp-twoway-incoming), within the context of reef depth, reefs
+intervention sites [@hock2017]. Within the context of reef depth, reefs
 with high depths and high outgoing connectivity levels had the greatest probability of being
@@
 
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by median reef depth.
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity. Lighter colours represent greater reef depth values than darker colours. All 2429 reefs included in this
+investigation are represented in this figure. Annotations represent major coastal
+settlements along the GBR.](../figs/depth_med_input_map.png){#sfig-depth-map
+fig-align="center" width="14.82cm"}
+
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by reef carrying capacity (coral habitable area).
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity. Lighter colours represent greater carrying capacity area values than darker colours. All 2429 reefs included in this
+investigation are represented in this figure. Annotations represent major coastal
+settlements along the GBR.](../figs/abs_k_area_input_map.png){#sfig-abs-k-area-map
+fig-align="center" width="14.82cm"}
+
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by outgoing connection strength (Log10).
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity. Lighter colours represent higher outgoing connection strength values than darker colours. All 2429 reefs included in this
+investigation are represented in this figure. Annotations represent major coastal
+settlements along the GBR.](../figs/log_out_strength_input_map.png){#sfig-outgoing-conn-map
+fig-align="center" width="14.82cm"}
+
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by source-to-sink connectivity ratio (Log10).
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity.
+Lighter colours represent higher source-to-sink values than darker colours.
+Source-to-sink ratio values above zero (one on normal scale) indicate a reef has greater outgoing than incoming connectivity.
+All 2429 reefs included in this
+investigation are represented in this figure. Annotations represent major coastal
+settlements along the GBR.](../figs/log_so_to_si_input_map.png){#sfig-sotosi-conn-map
+fig-align="center" width="14.82cm"}
+
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by larval retention probability (Log10).
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity. Lighter colours represent higher probability of retaining spawned larvae than darker colours. All 2429 reefs included in this
+investigation are represented in this figure. Annotations represent major coastal
+settlements along the GBR.](../figs/log_self_strength_input_map.png){#sfig-self-conn-map
+fig-align="center" width="14.82cm"}
+
 ## ADRIA-CoralBlox
@@
 
-![Weighted outgoing connectivity (in base-10 log scale) for reefs within each bioregion,
+![Outgoing connection strength (in base-10 log scale) for reefs within each bioregion,
 separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
@@
 the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median base-10 log of weighted outgoing connectivity
+lines within each violin represent the median base-10 log of outgoing connection strength
 for each cluster and bands represent the distribution of connectivity values within each
 cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_outgoing_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedoutgoing
-fig-align="center" width="14.82cm"}
+GCM.](../figs/ACCESS-ESM1-5/bioregion/outgoing_strength_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-outgoingconn
+fig-align="center" width="14.82cm"}
+
+![Larval retention probability (in base-10 log scale) for reefs within each bioregion,
+separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
+clusters with the lowest median area-relative cover between 2030 and 2060 within each
+bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
+cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
+the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
+lines within each violin represent the median base-10 log of larval retention probability
+for each cluster and bands represent the distribution of probability values within each
+cluster. Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/bioregion/self_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-selfconn
+fig-align="center" width="14.82cm"}
+
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by median number of years exceeding positive carbonate budget threshold.
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity.
+Reefs that have a median positive carbonate budget year value of 0 years are coloured in grey.
+All other reefs are coloured according to their median years across threshold values, with lighter colours representing greater number of years with positive carbonate budgets than darker colours.
+All 2429 reefs included in this
+investigation are represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal
+settlements along the GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
+fig-align="center" width="14.82cm"}
+
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by mean time series DHW value.
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity. Lighter colours represent higher mean DHW values than darker colours. All 2429 reefs included in this
+investigation are represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal
+settlements along the GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map
+fig-align="center" width="14.82cm"}
+
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by weighted incoming connectivity levels (Log10).
+Colour-coded areas outline GBR marine park management regions, where orange represents the
+Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity. Lighter colours represent higher weighted incoming connectivity values than darker colours. All 2429 reefs included in this
+investigation are represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal
+settlements along the GBR.](../figs/ACCESS-ESM1-5/weighted_incoming_conn_input_map.png){#sfig-incoming-conn-map
+fig-align="center" width="14.82cm"}

### 2025-09-09 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -28,7 +28,7 @@ year_cols = Vector{String}()
 conn_cols = Vector{String}()
 for GCM in GCMs
     context_layers[:, "$(GCM)_weighted_incoming_conn_log"] = log10.(context_layers[:, "$(GCM)_weighted_incoming_conn"]) 
-    context_layers[:, "$(GCM)_weighted_outgoing_conn_log"] = log10.(context_layers[:, "$(GCM)_weighted_outgoing_conn"]) 
+    # context_layers[:, "$(GCM)_weighted_outgoing_conn_log"] = log10.(context_layers[:, "$(GCM)_weighted_outgoing_conn"]) 
     
     push!(conn_cols, "$(GCM)_weighted_incoming_conn_log")
     for threshold in thresholds
@@ -37,7 +37,7 @@ for GCM in GCMs
 end
 
 reefs_long = stack(
-    context_layers[:, ["UNIQUE_ID", "depth_med", conn_cols..., year_cols...]],
+    context_layers[:, ["UNIQUE_ID", "depth_med", "geometry", conn_cols..., year_cols...]],
     year_cols
 )
 
@@ -162,10 +162,30 @@ for (i_gcm, GCM) in enumerate(GCMs)
         mean_dhw_map,
         px_per_unit=dpi
     )
+
+    median_cover_years = combine(groupby(gcm_reefs_long, :UNIQUE_ID)) do sdf
+        (;
+            geometry = first(sdf.geometry),
+            depth = first(sdf.depth_med),
+            incoming_conn = first(sdf[:, "$(GCM)_weighted_incoming_conn_log"]),
+            median_years = median(sdf.value)
+        )
+    end
+    median_cover_years.median_years = ifelse.(median_cover_years.median_years .== 0.0, missing, median_cover_years.median_years)
+    carbonate_budget_map = map_gbr_reefs_cont(
+        median_cover_years,
+        :median_years,
+        "Number of years exceeding positive carbonate budget threshold"
+    )
+    save(
+        joinpath(fig_out_dir, "median_carbonate_budget_map.png"),
+        carbonate_budget_map,
+        px_per_unit=dpi
+    )
 end
 
 context_layers.abs_k_area = context_layers.area .* context_layers.k ./ 1e6
-vars = [:depth_med, :log_so_to_si, :abs_k_area]
+vars = [:depth_med, :log_so_to_si, :abs_k_area, :log_out_strength, :log_self_strength]
 var_labels = Dict(
[…]

### 2025-09-09 src/plotting_functions.jl

@@ -647,17 +647,17 @@ function cluster_analysis_plots(
         px_per_unit=dpi
     )
 
-    weighted_outgo_conn = grouped_cluster_ridgeline_plot(
-        analysis_layers,
-        Symbol("$(GCM)_$(grouping)_clusters"),
-        grouping, Symbol("$(GCM)_weighted_outgoing_conn_log");
-        xlabel="Log10 weighted outgoing connectivity", ylabel="$(grouping_fn)", overlap=overlap
-    )
-    save(
-        joinpath(fig_out_dir, "$(grouping)", "weighted_outgoing_conn_$(grouping)_violin.png"),
-        weighted_outgo_conn,
-        px_per_unit=dpi
-    )
+    # weighted_outgo_conn = grouped_cluster_ridgeline_plot(
+    #     analysis_layers,
+    #     Symbol("$(GCM)_$(grouping)_clusters"),
+    #     grouping, Symbol("$(GCM)_weighted_outgoing_conn_log");
+    #     xlabel="Log10 weighted outgoing connectivity", ylabel="$(grouping_fn)", overlap=overlap
+    # )
+    # save(
+    #     joinpath(fig_out_dir, "$(grouping)", "weighted_outgoing_conn_$(grouping)_violin.png"),
+    #     weighted_outgo_conn,
+    #     px_per_unit=dpi
+    # )
 
     outgo_conn = grouped_cluster_ridgeline_plot(
         analysis_layers,
@@ -1219,6 +1219,9 @@ function map_gbr_reefs_cont(reef_df, color_col::Union{Symbol, String}, color_bar
     map_height = fig_sizes["map_height"]
     region_col = tuple.([:blue, :green, :orange, :red], fill(0.2, 4)) # Manually set alpha value to 0.3
 
+    missing_reefs = reef_df[ismissing.(reef_df[:, color_col]), :]
+    reef_df = reef_df[.!ismissing.(reef_df[:, color_col]), :]
+
     if color_col == :bioregion
         ordered_reefs = sort(reef_df, :bioregion_average_latitude; rev=true)
     else
@@ -1241,7 +1244,10 @@ function map_gbr_reefs_cont(reef_df, color_col::Union{Symbol, String}, color_bar
     poly!(qld; color=:darkgray)
     poly!(regions.SHAPE, color=region_col)
 
-    scat = scatter!(centroids; color=ordered_reefs[:, color_col], markersize=4)
+    if !isempty(missing_reefs)
[…]

### 2025-09-10 paper/paper_draft.qmd
Add sentence about spatial results for carbonate budget analyses format
Added caveat about spatial uncertainty in depth and connectivity data and not interpreting these results as explicit predictions.

@@
 To assess the impact of reef connectivity on modelled outcomes we summarise incoming
-connectivity (weighted incoming connectivity), outgoing connectivity (outgoing connection strength), the ratio of
-source-to-sink connectivity, and larval retention probability for each reef. Weighted incoming connectivity is calculated by
-summing the product of each connection strength incoming to a target reef and the mean
-timeseries absolute coral cover (km^2^) of each matching source reef. This metric provides
-an approximation of overall larval flow into a reef, with high values indicating the target
-reef is supplied high volumes of larvae via strong connections and low values indicating the
-target reef has weak (or no) incoming connections or is supplied by small source
-populations. A limitation of weighted incoming connectivity is it does not incorporate the
-proportion of the source reef's population that is reproducing and producing larvae, instead
-taking the total coral cover area as an indicator of larval productivity.
-Outgoing connection strength is calculated as the sum of all outgoing transition probabilities from a target reef.
-Outgoing connection strength has a theoretical maximum of one (all larvae reach settlement on sink reefs), however the large size of the GBR combined with larval mortality considerations result in outgoing connection strength values much lower than one.
-The ratio of
+connectivity (weighted incoming connectivity), outgoing connectivity (outgoing connection
+strength), the ratio of source-to-sink connectivity, and larval retention probability for
+each reef. Weighted incoming connectivity is calculated by summing the product of each
+connection strength incoming to a target reef and the mean timeseries absolute coral cover
+(km^2^) of each matching source reef. This metric provides an approximation of overall
+larval flow into a reef, with high values indicating the target reef is supplied high
+volumes of larvae via strong connections and low values indicating the target reef has weak
+(or no) incoming connections or is supplied by small source populations. A limitation of
+weighted incoming connectivity is it does not incorporate the proportion of the source
+reef's population that is reproducing and producing larvae, instead taking the total coral
+cover area as an indicator of larval productivity. Outgoing connection strength is
+calculated as the sum of all outgoing transition probabilities from a target reef. Outgoing
+connection strength has a theoretical maximum of one (all larvae reach settlement on sink
+reefs), however the large size of the GBR combined with larval mortality considerations
+result in outgoing connection strength values much lower than one. The ratio of
 source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
@@
 value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
-larval flow. Reef larval retention probability indicates the proportion of spawned larvae from a target reef that remain to settlement.
+larval flow. Reef larval retention probability indicates the proportion of spawned larvae
+from a target reef that remain to settlement.
 
@@
 between Low, Medium and High clusters. These characteristics include reef median depth, mean
-time series DHW, weighted incoming
-connectivity, outgoing connection strength, ratio of source-to-sink larval connectivity, larval retention probability and reef carrying capacity (coral habitable
-area).
+time series DHW, weighted incoming connectivity, outgoing connection strength, ratio of
+source-to-sink larval connectivity, larval retention probability and reef carrying capacity
+(coral habitable area).
 
@@
 
-Across bioregions there were no consistent patterns between reef clusters in mean DHW values (@sfig-access-esm1-5-bioregion-dhwmean), Log-10
-weighted incoming connectivity (@sfig-access-esm1-5-bioregion-weightedincoming), Log-10 outgoing connection strength (@sfig-access-esm1-5-bioregion-outoingconn), Log-10
-source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 larval retention probability (@sfig-access-esm1-5-bioregion-selfconn).
-Across six of the 29 bioregions reefs in the high cover cluster have lower Log-10
-carrying capacity values than reefs in other
-clusters (@sfig-access-esm1-5-bioregion-carrying-capacity).
+Across bioregions there were no consistent patterns between reef clusters in mean DHW values
+(@sfig-access-esm1-5-bioregion-dhwmean), Log-10 weighted incoming connectivity
+(@sfig-access-esm1-5-bioregion-weightedincoming), Log-10 outgoing connection strength
+(@sfig-access-esm1-5-bioregion-outoingconn), Log-10 source-to-sink connectivity ratio
+(@sfig-access-esm1-5-bioregion-logsosi) and Log-10 larval retention probability
+(@sfig-access-esm1-5-bioregion-selfconn). Across six of the 29 bioregions reefs in the high
+cover cluster have lower Log-10 carrying capacity values than reefs in other clusters
+(@sfig-access-esm1-5-bioregion-carrying-capacity).
 
@@
 further justified by its low feature importance score of 9%, the lowest of all predictors
-(@fig-ts-cluster-pdp; Panel A). Reef median depth, mean DHW level and weighted incoming connectivity (Log10) have the highest
-feature importance scores, accounting for 22%, 17% and 14% predictive importance respectively.
-The carrying capacity of a reef accounts for 12% feature importance, while outgoing connection strength, source-to-sink ratio and larval retention account for 10%, 9% and 7% respectively.
+(@fig-ts-cluster-pdp; Panel A). Reef median depth, mean DHW level and weighted incoming
+connectivity (Log10) have the highest feature importance scores, accounting for 22%, 17% and
+14% predictive importance respectively. The carrying capacity of a reef accounts for 12%
+feature importance, while outgoing connection strength, source-to-sink ratio and larval
+retention account for 10%, 9% and 7% respectively.
 
@@
 
-Analyses for source-to-sink ratio and incoming and outgoing connectivity metrics
-suggest that reefs with greater outgoing connectivity and lower incoming connectivity levels
-have higher probability of being clustered into the Low cluster category compared to other
-reefs. Additionally, two-way analyses revealed an interaction between reef depth and
-incoming connectivity in determining cluster category assignment, particularly at the high
-depth range (@fig-ts-cluster-pdp-twoway-incoming). Two-way analyses revealed that reefs at
-greater than 10m depth are unlikely to be clustered into the Low cluster category,
-regardless of their incoming connectivity levels. However, at greater than 10m depth reefs
-with higher incoming connectivity are more likely to be assigned to a High cluster, while
-reefs with low incoming connectivity are more likely to be assigned to a Medium cover
-cluster (@fig-ts-cluster-pdp-twoway-incoming).
-Two-way analyses, for depth and outgoing connection strength, revealed a slight interaction with deep reefs with high outgoing connectivity having the greatest probability of being
-clustered into a high cover cluster (@sfig-ts-cluster-pdp-twoway-outgoing).
+Analyses for source-to-sink ratio and incoming and outgoing connectivity metrics suggest
+that reefs with greater outgoing connectivity and lower incoming connectivity levels have
+higher probability of being clustered into the Low cluster category compared to other reefs.
+Additionally, two-way analyses revealed an interaction between reef depth and incoming
+connectivity in determining cluster category assignment, particularly at the high depth
+range (@fig-ts-cluster-pdp-twoway-incoming). Two-way analyses revealed that reefs at greater
+than 10m depth are unlikely to be clustered into the Low cluster category, regardless of
+their incoming connectivity levels. However, at greater than 10m depth reefs with higher
+incoming connectivity are more likely to be assigned to a High cluster, while reefs with low
+incoming connectivity are more likely to be assigned to a Medium cover cluster
+(@fig-ts-cluster-pdp-twoway-incoming). Two-way analyses, for depth and outgoing connection
+strength, revealed a slight interaction with deep reefs with high outgoing connectivity
+having the greatest probability of being clustered into a high cover cluster
+(@sfig-ts-cluster-pdp-twoway-outgoing).
 
@@
 algae driven production, or to bioerosion dominated systems with rapid erosion of physical
-reef frameworks [@dudgeon2010; @perry2008]. While reefs at increased depths may be able to
+reef frameworks [@dudgeon2010; @perry2008]. Reefs at increased depths may be able to
 maintain coral driven CaCO~3~ production and accumulation into the future for longer. Our
@@
 depth contributes greatly to reef resilience and the ability of the reef to maintain
-positive carbonate budgets under future conditions. While similar findings have been
-demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014] regions,
-depth refugia analyses have often focussed on the potential of mesophotic reefs (\> 30m
-deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas
-et al. [-@venegas2019] found no association between depth and the alleviation of heat stress
-across a range of shallow reefs in the Pacific.
+positive carbonate budgets under future conditions. Spatially our results indicate that
+positive carbonate budget maintenance, under ACCESS-ESM1-5, and high depth levels were
+concentrated in the Far Northern, offshore Townsville/Whitsunday, and Mackay/Capricorn
+management areas (@sfig-carb-budget-map; @sfig-depth-map). Additionally similar spatial
+patterns were observed for reefs clustered into the high cover cluster category across all
+GCMs (@sfig-gcm-cluster-map). We do not interpret these spatial findings as accurate
+predictions of future resilience due to high uncertainty in input data, particularly depth
+and connectivity. While similar findings have been demonstrated in the Pacific [@smith2014;
+@baird2018] and Indo-Pacific [@bridge2014] regions, depth refugia analyses have often
+focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia
+[@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al. [-@venegas2019]
+found no association between depth and the alleviation of heat stress across a range of
+shallow reefs in the Pacific.
 
@@
 positive potential for flow on effects due to outgoing connectivity when selecting
-intervention sites [@hock2017]. Within the context of reef depth, reefs
-with high depths and high outgoing connectivity levels had the greatest probability of being
-clustered into high cover clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results
-suggests that interventions targetting deep reefs will also benefit from high incoming and
-outgoing connectivity levels, allowing for high potential for site resilience and outgoing
-flow of benefits and recovery. Transient, and difficult to measure, properties such as reef
+intervention sites [@hock2017]. Within the context of reef depth, reefs with high depths and
+high outgoing connectivity levels had the greatest probability of being clustered into high
+cover clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results suggests that
+interventions targetting deep reefs will also benefit from high incoming and outgoing
+connectivity levels, allowing for high potential for site resilience and outgoing flow of
+benefits and recovery. Transient, and difficult to measure, properties such as reef
 connectivity are likely to increase uncertainty in intervention planning to a greater degree
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by median reef depth.
-Colour-coded areas outline GBR marine park management regions, where orange represents the
-Far Northern management region, green represents Cairns/Cooktown, red covers
-Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent greater reef depth values than darker colours. All 2429 reefs included in this
-investigation are represented in this figure. Annotations represent major coastal
-settlements along the GBR.](../figs/depth_med_input_map.png){#sfig-depth-map
+considered reefs (points), coloured by median reef depth. Colour-coded areas outline GBR
+marine park management regions, where orange represents the Far Northern management region,
+green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers
+Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for visual clarity.
+Lighter colours represent greater reef depth values than darker colours. All 2429 reefs
+included in this investigation are represented in this figure. Annotations represent major
+coastal settlements along the GBR.](../figs/depth_med_input_map.png){#sfig-depth-map
 fig-align="center" width="14.82cm"}
@@
 Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent greater carrying capacity area values than darker colours. All 2429 reefs included in this
-investigation are represented in this figure. Annotations represent major coastal
-settlements along the GBR.](../figs/abs_k_area_input_map.png){#sfig-abs-k-area-map
-fig-align="center" width="14.82cm"}
+marked individually for visual clarity. Lighter colours represent greater carrying capacity
+area values than darker colours. All 2429 reefs included in this investigation are
+represented in this figure. Annotations represent major coastal settlements along the
+GBR.](../figs/abs_k_area_input_map.png){#sfig-abs-k-area-map fig-align="center"
+width="14.82cm"}
 
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by outgoing connection strength (Log10).
-Colour-coded areas outline GBR marine park management regions, where orange represents the
-Far Northern management region, green represents Cairns/Cooktown, red covers
-Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent higher outgoing connection strength values than darker colours. All 2429 reefs included in this
-investigation are represented in this figure. Annotations represent major coastal
-settlements along the GBR.](../figs/log_out_strength_input_map.png){#sfig-outgoing-conn-map
-fig-align="center" width="14.82cm"}
+considered reefs (points), coloured by outgoing connection strength (Log10). Colour-coded
+areas outline GBR marine park management regions, where orange represents the Far Northern
+management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
+blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
+visual clarity. Lighter colours represent higher outgoing connection strength values than
+darker colours. All 2429 reefs included in this investigation are represented in this
+figure. Annotations represent major coastal settlements along the
+GBR.](../figs/log_out_strength_input_map.png){#sfig-outgoing-conn-map fig-align="center"
+width="14.82cm"}
 
@@
 Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity.
-Lighter colours represent higher source-to-sink values than darker colours.
-Source-to-sink ratio values above zero (one on normal scale) indicate a reef has greater outgoing than incoming connectivity.
-All 2429 reefs included in this
-investigation are represented in this figure. Annotations represent major coastal
+marked individually for visual clarity. Lighter colours represent higher source-to-sink
+values than darker colours. Source-to-sink ratio values above zero (one on normal scale)
+indicate a reef has greater outgoing than incoming connectivity. All 2429 reefs included in
+this investigation are represented in this figure. Annotations represent major coastal
 settlements along the GBR.](../figs/log_so_to_si_input_map.png){#sfig-sotosi-conn-map
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by larval retention probability (Log10).
-Colour-coded areas outline GBR marine park management regions, where orange represents the
-Far Northern management region, green represents Cairns/Cooktown, red covers
-Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent higher probability of retaining spawned larvae than darker colours. All 2429 reefs included in this
-investigation are represented in this figure. Annotations represent major coastal
-settlements along the GBR.](../figs/log_self_strength_input_map.png){#sfig-self-conn-map
-fig-align="center" width="14.82cm"}
+considered reefs (points), coloured by larval retention probability (Log10). Colour-coded
+areas outline GBR marine park management regions, where orange represents the Far Northern
+management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
+blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
+visual clarity. Lighter colours represent higher probability of retaining spawned larvae
+than darker colours. All 2429 reefs included in this investigation are represented in this
+figure. Annotations represent major coastal settlements along the
+GBR.](../figs/log_self_strength_input_map.png){#sfig-self-conn-map fig-align="center"
+width="14.82cm"}
 
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by median number of years exceeding positive carbonate budget threshold.
-Colour-coded areas outline GBR marine park management regions, where orange represents the
-Far Northern management region, green represents Cairns/Cooktown, red covers
-Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity.
-Reefs that have a median positive carbonate budget year value of 0 years are coloured in grey.
-All other reefs are coloured according to their median years across threshold values, with lighter colours representing greater number of years with positive carbonate budgets than darker colours.
-All 2429 reefs included in this
-investigation are represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal
-settlements along the GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
+considered reefs (points), coloured by median number of years exceeding positive carbonate
+budget threshold. Colour-coded areas outline GBR marine park management regions, where
+orange represents the Far Northern management region, green represents Cairns/Cooktown, red
+covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids
+are marked individually for visual clarity. Reefs that have a median positive carbonate
+budget year value of 0 years are coloured in grey. All other reefs are coloured according to
+their median years across threshold values, with lighter colours representing greater number
+of years with positive carbonate budgets than darker colours. All 2429 reefs included in
+this investigation are represented in this figure. This map depicts values from the
+ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
+GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
 fig-align="center" width="14.82cm"}
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by mean time series DHW value.
-Colour-coded areas outline GBR marine park management regions, where orange represents the
-Far Northern management region, green represents Cairns/Cooktown, red covers
-Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent higher mean DHW values than darker colours. All 2429 reefs included in this
-investigation are represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal
-settlements along the GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map
-fig-align="center" width="14.82cm"}
+considered reefs (points), coloured by mean time series DHW value. Colour-coded areas
+outline GBR marine park management regions, where orange represents the Far Northern
+management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
+blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
+visual clarity. Lighter colours represent higher mean DHW values than darker colours. All
+2429 reefs included in this investigation are represented in this figure. This map depicts
+values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
+GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map fig-align="center"
+width="14.82cm"}
 
@@
 Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent higher weighted incoming connectivity values than darker colours. All 2429 reefs included in this
-investigation are represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal
-settlements along the GBR.](../figs/ACCESS-ESM1-5/weighted_incoming_conn_input_map.png){#sfig-incoming-conn-map
-fig-align="center" width="14.82cm"}
+marked individually for visual clarity. Lighter colours represent higher weighted incoming
+connectivity values than darker colours. All 2429 reefs included in this investigation are
+represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations
+represent major coastal settlements along the
+GBR.](../figs/ACCESS-ESM1-5/weighted_incoming_conn_input_map.png){#sfig-incoming-conn-map
+fig-align="center" width="14.82cm"}

### 2025-09-10 paper/paper_draft.qmd
Add spatial dhw sentence

@@
 concentrated in the Far Northern, offshore Townsville/Whitsunday, and Mackay/Capricorn
-management areas (@sfig-carb-budget-map; @sfig-depth-map). Additionally similar spatial
-patterns were observed for reefs clustered into the high cover cluster category across all
-GCMs (@sfig-gcm-cluster-map). We do not interpret these spatial findings as accurate
-predictions of future resilience due to high uncertainty in input data, particularly depth
-and connectivity. While similar findings have been demonstrated in the Pacific [@smith2014;
-@baird2018] and Indo-Pacific [@bridge2014] regions, depth refugia analyses have often
-focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia
-[@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al. [-@venegas2019]
-found no association between depth and the alleviation of heat stress across a range of
-shallow reefs in the Pacific.
+management areas (@sfig-carb-budget-map; @sfig-depth-map). Resilient reefs in the Far
+Northern management area were exposed to lower mean DHW levels than other reefs under
+ACCESS-ESM1-5 (@sfig-mean-dhw-map). Similar spatial patterns were observed across GCMs for
+reefs clustered into the high cover cluster category (@sfig-gcm-cluster-map). We do not
+interpret these spatial findings as accurate predictions of future resilience due to high
+uncertainty in input data, particularly depth and connectivity. While similar findings have
+been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014]
+regions, depth refugia analyses have often focussed on the potential of mesophotic reefs (\>
+30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast,
+Venegas et al. [-@venegas2019] found no association between depth and the alleviation of
+heat stress across a range of shallow reefs in the Pacific.
 

### 2025-09-10 paper/paper_draft.qmd
Change the plotting framework for carbonate budgets and add to paper doc

@@
 that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
-@sfig-access-esm1-5-mean-carb-budget). Unsurprisingly, the number of years above $\theta_0$
-substantially decreased as $\theta_0$ is increased, as does the Spearman's correlation.
-Decreasing correlation levels are likely due to an increasing number of reefs being unable
-to maintain coral cover above $\theta_0$ as it is increased, with the distribution of years
-above threshold becoming increasingly right-skewed
-(@fig-access-esm1-5-depth-conn-carbonate). In contrast, weighted incoming connectivity
-strength (Log-10 scale) was found to have no correlation with the number of years a reef
-maintains cover above the required thresholds (@fig-access-esm1-5-depth-conn-carbonate).
+@sfig-access-esm1-5-mean-carb-budget; @sfig-access-esm1-5-carb-budget-corr). Unsurprisingly,
+the number of years above $\theta_0$ substantially decreased as $\theta_0$ is increased, as
+does the Spearman's correlation (@sfig-access-esm1-5-carb-budget-corr). Decreasing
+correlation levels are likely due to an increasing number of reefs being unable to maintain
+coral cover above $\theta_0$ as it is increased, with the distribution of years above
+threshold becoming increasingly right-skewed (@fig-access-esm1-5-depth-conn-carbonate). In
+contrast, weighted incoming connectivity strength (Log-10 scale) was found to have no
+correlation with the number of years a reef maintains cover above the required thresholds
+(@fig-access-esm1-5-carb-budget-corr).
 
 ![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
-(y-axis). The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
-Bracketed x-axis values represent the Spearman's correlation between reef variables (depth -
-left and Log-10 weighted incoming connectivity - right) and the number of years cover
-exceeds the carbonate budget threshold. Point colour represents the median reef depth in
-metres in the left-hand panel, and Log-10 weighted incoming connectivity in the right-hand
-panel. Red points represent the mean number of years above an assumed carbonate budget
-threshold across reefs. Deeper reefs are better able to maintain cover above the indicative
-carbonate budget threshold, while there is no considerable relationship between weighted
-incoming connectivity and carbonate budget maintenance. Displays results from median time
-series using
+(y-axis) and reef median depth (left panel) and reef Log10 weighted incoming connectivity
+values (right panel). Point colour represents the threshold assessment values used to assess
+positive carbonate budget status ($\theta_0$). Deeper reefs are better able to maintain
+cover above the indicative carbonate budget threshold, while there is no considerable
+relationship between weighted incoming connectivity and carbonate budget maintenance.
+Displays results from median time series using
 ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
@@
 
+![Bar plot indicating the Spearman's rank correlation values for the number of years above
+carbonate budget threshold and, median reef depth and Log10 weighted incoming connectivity
+values. Depth correlation values are displayed in the left plot, while connectivity
+correlation values are displayed in the right plot. Displays results for ACCESS-ESM1-5
+GCM.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_correlations.png){#sfig-access-esm1-5-carb-budget-corr
+fig-align="center" width="14.82cm"}
+
 ![Scatter plot indicating reef median depth (metres) and Log10 weighted incoming
-connectivity for each reef. Point colours represent the mean number of years each reef
+connectivity for each reef. Point colours represent the median number of years each reef
 maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover.
@@
 GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
-fig-align="center" width="10cm"}
+fig-align="center" width="14.82cm"}
 

### 2025-09-10 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -114,7 +114,8 @@ for (i_gcm, GCM) in enumerate(GCMs)
     )
     
     depth_conn_carbonate_correlations = carbonate_budget_correlations(
-        depth_year_correlation, log_incoming_conn_year_correlation
+        depth_year_correlation, log_incoming_conn_year_correlation;
+        correlation_label="Spearman's rank correlation \n(Reef feature - Number of years above carbonate budget threshold)"
     )
     save(
         joinpath(fig_out_dir, "depth_conn_carbonate_correlations.png"),

### 2025-09-10 paper/paper_draft.qmd
Add citation for thermal stress advancement, and placeholder for connectivity citation

@@
 
-Recent advances in whole-ecosystem larval connectivity modelling and coral thermal response
-research enable integrated investigation of how these multiple factors interact to determine
-climate resilience. By incorporating the latest coral population models
-[@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated climate projections
-[@dixon2022], we can examine which factors most strongly influence reef persistence under
-different scenarios. While connectivity has been emphasized as critical for GBR resilience
-[@hock2017], and remains an important consideration, our integrated modelling reveals depth
-may play a fundamental role in determining maintenance of reef coral populations and
-positive carbonate budgets under current projections of climate change.
+Recent advances in whole-ecosystem larval connectivity modelling **\[Insert GBR1
+connectivity citation.\]** and coral thermal response research [@bairos-novak2021] enable
+integrated investigation of how multiple factors interact to determine climate resilience.
+By incorporating the latest coral population models [@ribeirodealmeida2024], ecosystem-wide
+connectivity data, and updated climate projections [@dixon2022], we can examine which
+factors most strongly influence reef persistence under different scenarios. While
+connectivity has been emphasized as critical for GBR resilience [@hock2017], and remains an
+important consideration, our integrated modelling reveals depth may play a fundamental role
+in determining maintenance of reef coral populations and positive carbonate budgets under
+current projections of climate change.
 

### 2025-09-10 paper/paper_draft.qmd
Add cots control to discussion

@@
 
-Current reef restoration and intervention investigation efforts on the GBR, such as
-deployment of coral seeding and fragment devices, target reefs with suitable sites in the
-1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are no explicit
-justifications for this depth range, intervention depth is likely constrained by snorkelling
-and diving deployment and monitoring logistical accessibility, visual identification of
-sites from the surface, in combination with tourism return value. Our results suggest that
-of the assessed reefs occurring within the 1-10m depth range (1736 reefs), 57% (991) of
-reefs fall into the low and medium clusters (across all GCMs at the GBRMPA management region
-scale), with many unable to maintain positive carbonate budgets under future conditions.
-Partial dependence analysis revealed a range of depths from 10-15m where the probability of
-a reef being clustered into the High cover cluster increased substantially. Additionally,
-two-way partial dependence analysis revealed that high incoming connectivity is important
-for High cluster assignment for reefs at depths of \>10m. Considering this 10-15m depth
-range, and targetting well connected reefs, when assessing possible intervention sites may
-reduce the exposure of planted and seeded corals to high thermal stress, while still
-maintaining effective logistical access to sites. Managers are also likely to consider the
-positive potential for flow on effects due to outgoing connectivity when selecting
-intervention sites [@hock2017]. Within the context of reef depth, reefs with high depths and
-high outgoing connectivity levels had the greatest probability of being clustered into high
-cover clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results suggests that
-interventions targetting deep reefs will also benefit from high incoming and outgoing
-connectivity levels, allowing for high potential for site resilience and outgoing flow of
-benefits and recovery. Transient, and difficult to measure, properties such as reef
-connectivity are likely to increase uncertainty in intervention planning to a greater degree
-than environmental characteristics such as reef depth. Overall, reef intervention planning
-is a complex and challenging decision-making process [@anthony2020], and our results suggest
-that intervention site depth may be an important factor to additionally consider when
-assessing the long-term resilience of sites.
+Current reef restoration and intervention efforts on the GBR, such as deployment of coral
+seeding, fragment devices and Crown of Thorns Starfish control, target reefs with suitable
+sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
+no explicit justifications for this depth range, intervention depth is likely constrained by
+snorkelling and diving deployment and monitoring logistical accessibility, visual
+identification of sites from the surface, in combination with tourism return value. Our
+results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
+reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the
+GBRMPA management region scale), with many unable to maintain positive carbonate budgets
+under future conditions. Partial dependence analysis revealed a range of depths from 10-15m
+where the probability of a reef being clustered into the High cover cluster increased
+substantially. Additionally, two-way partial dependence analysis revealed that high incoming
+connectivity is important for High cluster assignment for reefs at depths of \>10m.
+Considering this 10-15m depth range, and targetting well connected reefs, when assessing
+possible intervention sites may reduce the exposure of planted and seeded corals to high
+thermal stress, while still maintaining effective logistical access to sites. Managers are
+also likely to consider the positive potential for flow on effects due to outgoing
+connectivity when selecting intervention sites [@hock2017]. Within the context of reef
+depth, reefs with high depths and high outgoing connectivity levels had the greatest
+probability of being clustered into high cover clusters
+(@sfig-ts-cluster-pdp-twoway-outgoing). These results suggests that interventions targetting
+deep reefs will also benefit from high incoming and outgoing connectivity levels, allowing
+for high potential for site resilience and outgoing flow of benefits and recovery.
+Transient, and difficult to measure, properties such as reef connectivity are likely to
+increase uncertainty in intervention planning to a greater degree than environmental
+characteristics such as reef depth. Overall, reef intervention planning is a complex and
+challenging decision-making process [@anthony2020], and our results suggest that
+intervention site depth may be an important factor to additionally consider when assessing
+the long-term resilience of sites.
 

### 2025-09-11 paper/paper_draft.qmd
Update map plotting and figure captions to reverse colour gradients

@@
 Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for visual clarity.
-Lighter colours represent greater reef depth values than darker colours. All 2429 reefs
+Darker colours represent greater reef depth values than lighter colours. All 2429 reefs
 included in this investigation are represented in this figure. Annotations represent major
@@
 Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent greater carrying capacity
-area values than darker colours. All 2429 reefs included in this investigation are
+marked individually for visual clarity. Darker colours represent greater carrying capacity
+area values than lighter colours. All 2429 reefs included in this investigation are
 represented in this figure. Annotations represent major coastal settlements along the
@@
 blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
-visual clarity. Lighter colours represent higher outgoing connection strength values than
-darker colours. All 2429 reefs included in this investigation are represented in this
+visual clarity. Darker colours represent higher outgoing connection strength values than
+lighter colours. All 2429 reefs included in this investigation are represented in this
 figure. Annotations represent major coastal settlements along the
@@
 Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent higher source-to-sink
-values than darker colours. Source-to-sink ratio values above zero (one on normal scale)
+marked individually for visual clarity. Darker colours represent higher source-to-sink
+values than lighter colours. Source-to-sink ratio values above zero (one on normal scale)
 indicate a reef has greater outgoing than incoming connectivity. All 2429 reefs included in
@@
 blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
-visual clarity. Lighter colours represent higher probability of retaining spawned larvae
-than darker colours. All 2429 reefs included in this investigation are represented in this
+visual clarity. Darker colours represent higher probability of retaining spawned larvae
+than lighter colours. All 2429 reefs included in this investigation are represented in this
 figure. Annotations represent major coastal settlements along the
@@
 
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by median number of years exceeding positive carbonate
+budget threshold. Colour-coded areas outline GBR marine park management regions, where
+orange represents the Far Northern management region, green represents Cairns/Cooktown, red
+covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids
+are marked individually for visual clarity. Reefs that have a median positive carbonate
+budget year value of 0 years are coloured in grey. All other reefs are coloured according to
+their median years across threshold values, with darker colours representing greater number
+of years with positive carbonate budgets than lighter colours. All 2429 reefs included in
+this investigation are represented in this figure. This map depicts values from the
+ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
+GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
+fig-align="center" width="14.82cm"}
+
 ### Bioregion scale clustering
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by median number of years exceeding positive carbonate
-budget threshold. Colour-coded areas outline GBR marine park management regions, where
-orange represents the Far Northern management region, green represents Cairns/Cooktown, red
-covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids
-are marked individually for visual clarity. Reefs that have a median positive carbonate
-budget year value of 0 years are coloured in grey. All other reefs are coloured according to
-their median years across threshold values, with lighter colours representing greater number
-of years with positive carbonate budgets than darker colours. All 2429 reefs included in
-this investigation are represented in this figure. This map depicts values from the
-ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
-GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
-fig-align="center" width="14.82cm"}
-
-![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
 considered reefs (points), coloured by mean time series DHW value. Colour-coded areas
@@
 blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
-visual clarity. Lighter colours represent higher mean DHW values than darker colours. All
+visual clarity. Darker colours represent higher mean DHW values than lighter colours. All
 2429 reefs included in this investigation are represented in this figure. This map depicts
@@
 Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Lighter colours represent higher weighted incoming
-connectivity values than darker colours. All 2429 reefs included in this investigation are
+marked individually for visual clarity. Darker colours represent higher weighted incoming
+connectivity values than lighter colours. All 2429 reefs included in this investigation are
 represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations

### 2025-09-11 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -131,7 +131,7 @@ for (i_gcm, GCM) in enumerate(GCMs)
     gcm_threshold_columns = ["$(GCM)_years_above_$(x)" for x in 10:20]
     context_layers[!, "$(GCM)_median_positive_years"] = vec(median(Matrix(context_layers[:, gcm_threshold_columns]), dims=2))
     fig, ax, scat = scatter(context_layers.depth_med, context_layers[:, "$(GCM)_weighted_incoming_conn_log"], color=context_layers[:, "$(GCM)_median_positive_years"], alpha=0.5)
-    Colorbar(fig[1,2], scat, label="Median number of positive carbonate budget years \nacross θ")
+    Colorbar(fig[1,2], scat, label="Median number of positive carbonate budget years \nacross θ", spinewidth=0.0)
     ax.ylabel = "Log10 weighted incoming connectivity"
     ax.xlabel = "Median depth [m]"
     save(

### 2025-09-11 src/plotting_functions.jl

@@ -1229,6 +1229,7 @@ function map_gbr_reefs_cont(reef_df, color_col::Union{Symbol, String}, color_bar
     end
 
     centroids = GO.centroid.(ordered_reefs.geometry)
+    color_map = cgrad(:viridis, 256, rev=true)
 
     # GeoMakie currently has a bug where x/y labels never display.
     # We adjust map size to roughly align with the correct projection.
@@ -1247,7 +1248,7 @@ function map_gbr_reefs_cont(reef_df, color_col::Union{Symbol, String}, color_bar
     if !isempty(missing_reefs)
         scat_0 = scatter!(GO.centroid.(missing_reefs.geometry); color=(:gray, 0.4), markersize=4)
     end
-    scat = scatter!(centroids; color=Float64.(ordered_reefs[:, color_col]), markersize=4)
+    scat = scatter!(centroids; color=Float64.(ordered_reefs[:, color_col]), colormap=color_map, markersize=4)
     ax.ylabel = "Latitude"
     ax.xlabel = "Longitude"
 
@@ -1281,7 +1282,7 @@ function map_gbr_reefs_cont(reef_df, color_col::Union{Symbol, String}, color_bar
     Colorbar(
         fig[1, 2],
         limits = extrema(ordered_reefs[:, color_col]),
-        colormap = :viridis,
+        colormap = color_map,
         label=color_bar_label,
         size=6, 
         spinewidth=0.0,

### 2025-09-11 paper/paper_draft.qmd
Proof read of the paper discussion
9202 words with figure/table captions
7619 without

@@
     key: sfig
-  custom:
   - kind: float
@@
 (@sfig-access-esm1-5-bioregion-weightedincoming), Log-10 outgoing connection strength
-(@sfig-access-esm1-5-bioregion-outoingconn), Log-10 source-to-sink connectivity ratio
+(@sfig-access-esm1-5-bioregion-outgoingconn), Log-10 source-to-sink connectivity ratio
 (@sfig-access-esm1-5-bioregion-logsosi) and Log-10 larval retention probability
@@
 correlation with the number of years a reef maintains cover above the required thresholds
-(@fig-access-esm1-5-carb-budget-corr).
+(@sfig-access-esm1-5-carb-budget-corr).
 
@@
 Reefs in different temporal clusters largely do not differ in mean modelled DHW levels
-experienced and exhibit overall similar DHW time series. While these reefs experience
-similar magnitude DHWs based on SST, the proportion of the reefs' coral population impacted
-by heat stress events depends on reef depth. Reefs at deeper depths are likely to be
-clustered into High cover clusters. Reefs at shallow depths experience no, or few, years
-with coral cover exceeding levels likely required to maintain positive carbonate budgets.
-Movement of shallow reefs towards negative carbonate budgets in the future may contribute to
-phase shifts in reef dominant CaCO~3~ production. Shifting from coral driven to encrusting
-algae driven production, or to bioerosion dominated systems with rapid erosion of physical
-reef frameworks [@dudgeon2010; @perry2008]. Reefs at increased depths may be able to
-maintain coral driven CaCO~3~ production and accumulation into the future for longer. Our
-results suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m),
-depth contributes greatly to reef resilience and the ability of the reef to maintain
-positive carbonate budgets under future conditions. Spatially our results indicate that
+experienced and exhibit overall similar DHW time series. While reefs experience similar
+magnitude DHWs based on SST, the proportion of a reefs' coral population impacted by heat
+stress events depends on reef depth. Reefs at deeper depths are likely to be clustered into
+High cover clusters. Reefs at shallow depths experience no, or few, years with coral cover
+exceeding levels likely required to maintain positive carbonate budgets. Movement of shallow
+reefs towards negative carbonate budgets in the future may contribute to phase shifts in
+reef dominant CaCO~3~ production. Shifting from coral driven to encrusting algae driven
+production, or to bioerosion dominated systems with rapid erosion of physical reef
+frameworks [@dudgeon2010; @perry2008]. Reefs at increased depths may be able to maintain
+coral driven CaCO~3~ production and accumulation into the future for longer. Our results
+suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m), depth
+contributes greatly to reef resilience and the ability of reefs to maintain positive
+carbonate budgets under future conditions. Spatially our results indicate that regions of
 positive carbonate budget maintenance, under ACCESS-ESM1-5, and high depth levels were
@@
 Northern management area were exposed to lower mean DHW levels than other reefs under
-ACCESS-ESM1-5 (@sfig-mean-dhw-map). Similar spatial patterns were observed across GCMs for
-reefs clustered into the high cover cluster category (@sfig-gcm-cluster-map). We do not
-interpret these spatial findings as accurate predictions of future resilience due to high
-uncertainty in input data, particularly depth and connectivity. While similar findings have
-been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014]
-regions, depth refugia analyses have often focussed on the potential of mesophotic reefs (\>
-30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast,
-Venegas et al. [-@venegas2019] found no association between depth and the alleviation of
-heat stress across a range of shallow reefs in the Pacific.
-
-These findings support the hypothesis that reefs at greater depths will exhibit
+ACCESS-ESM1-5 (@sfig-mean-dhw-map), however similar spatial patterns were observed across
+GCMs for reefs clustered into the high cover cluster category (@sfig-gcm-cluster-map). We do
+not interpret these spatial findings as accurate predictions of future resilience due to
+high uncertainty in input data, particularly depth and connectivity. While similar findings
+have been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific
+[@bridge2014] regions, depth refugia analyses have often focussed on the potential of
+mesophotic reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015;
+@semmler2017]. In contrast, Venegas et al. [-@venegas2019] found no association between
+depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
+
+Our findings support the hypothesis that reefs at greater depths will exhibit
 characteristics of refugia and more prolonged structural resilience under climate change
@@
 that rubble instability is inversely correlated with reef depth, possibly limiting juvenile
-recruitment capacity of shallow reefs. A caveat to these depth-resilience findings is the
-quality of the bathymetry data used to calculate median reef depth. As detailed previously,
-estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution)
-which can be subject to high degrees of uncertainty, both in terms of the estimated depth at
-for each pixel as well as their alignment to the established GBRMPA reef outlines.
-Additionally, we do not incorporate the light-based decreases in coral growth rates as depth
-increases [@baker1975; @huston1985; @ruiz-diaz2022].
+coral recruitment capacity of shallow reefs. A caveat to our depth-resilience findings is
+the quality of the bathymetry data used to calculate median reef depth. As detailed
+previously, estimates of median reef depth are derived from satellite imagery (at $10m^2$
+resolution) which can be subject to high degrees of uncertainty, both in terms of the
+estimated depth for each pixel as well as their alignment to the established GBRMPA reef
+outlines. Additionally, we do not incorporate light-based decreases in coral growth rates as
+depth increases [@baker1975; @huston1985; @ruiz-diaz2022].
 
 Current reef restoration and intervention efforts on the GBR, such as deployment of coral
-seeding, fragment devices and Crown of Thorns Starfish control, target reefs with suitable
+seeding, coral fragment devices and Crown of Thorns Starfish control, target reefs with
 sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
@@
 results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
-reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the
-GBRMPA management region scale), with many unable to maintain positive carbonate budgets
-under future conditions. Partial dependence analysis revealed a range of depths from 10-15m
-where the probability of a reef being clustered into the High cover cluster increased
-substantially. Additionally, two-way partial dependence analysis revealed that high incoming
-connectivity is important for High cluster assignment for reefs at depths of \>10m.
-Considering this 10-15m depth range, and targetting well connected reefs, when assessing
-possible intervention sites may reduce the exposure of planted and seeded corals to high
-thermal stress, while still maintaining effective logistical access to sites. Managers are
-also likely to consider the positive potential for flow on effects due to outgoing
-connectivity when selecting intervention sites [@hock2017]. Within the context of reef
-depth, reefs with high depths and high outgoing connectivity levels had the greatest
-probability of being clustered into high cover clusters
-(@sfig-ts-cluster-pdp-twoway-outgoing). These results suggests that interventions targetting
-deep reefs will also benefit from high incoming and outgoing connectivity levels, allowing
-for high potential for site resilience and outgoing flow of benefits and recovery.
-Transient, and difficult to measure, properties such as reef connectivity are likely to
-increase uncertainty in intervention planning to a greater degree than environmental
-characteristics such as reef depth. Overall, reef intervention planning is a complex and
-challenging decision-making process [@anthony2020], and our results suggest that
-intervention site depth may be an important factor to additionally consider when assessing
-the long-term resilience of sites.
+reefs), 57% (991) of reefs are consistently clustered into the Low and Medium cover clusters
+across the GCMs (at the GBRMPA management region scale), with many unable to maintain
+positive carbonate budgets under future conditions. Partial dependence analysis revealed a
+range of depths from 10-15m where the probability of a reef being clustered into the High
+cover cluster increased substantially. Additionally, two-way partial dependence analysis
+revealed that high incoming connectivity is important for High cluster assignment for reefs
+at depths of \>10m. Considering this 10-15m depth range when assessing possible intervention
+sites may reduce the exposure of planted and seeded corals to high thermal stress, while
+still maintaining effective logistical access to sites. Managers are also likely to consider
+the potential for positive flow on effects due to outgoing connectivity when selecting
+intervention sites [@hock2017]. Two-way partial dependence analysis revealed reefs with high
+depths and high outgoing connectivity levels have a high probability of being clustered into
+more resilient reef clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results suggest
+that interventions targetting deep reefs will also benefit from high incoming and outgoing
+connectivity levels, allowing for high potential for site resilience and outgoing flow of
+benefits and recovery. Transient, and difficult to measure, properties such as reef
+connectivity are likely to increase uncertainty in intervention planning to a greater degree
+than environmental characteristics such as reef depth. Overall, reef intervention planning
+is a complex and challenging decision-making process [@anthony2020], and our results suggest
+that intervention site depth may be an important factor to additionally consider when
+assessing the long-term resilience of sites.
 
@@
 cover cluster allocation for reefs over 10m deep. At depths of less than 10m thermal stress
-may be too high for juveniles to contribute to long term recovery. While there is
+may be too high for incoming juveniles to contribute to long term recovery. While there is
 interaction between incoming connectivity and depth for reef cluster prediction, according
@@
 or reef resilience and recovery, but should be considered in combination with more
-influential factors such as depth. In-depth comparisons and validation of multiple
+influential factors such as depth. Comprehensive comparisons and validation of multiple
 connectivity model outputs would improve certainty and allow for the targetting of reefs by
@@
 Under all GCMs many reefs are projected to suffer substantial declines in coral cover
-relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the
-lowest cover level cluster at the management area scale across GCMs. NorESM2-MM and
-ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future. Differences
-between Low, Medium and High reef clusters in cover time series are most notable under these
-two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into
-the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of
-future recovery and timespan of cover maintenance increase as GCM ECS increases
+relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the Low
+cover cluster at the management area scale across GCMs. NorESM2-MM and ACCESS-ESM1-5 GCMs
+convey the most coral cover maintenance into the future. Differences between Low, Medium and
+High reef clusters in cover time series are most notable under these two GCMs
+(@stbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into the future
+is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of future
+recovery and timespan of cover maintenance increase as GCM ECS increases
 (@fig-gcm-cover-trajectories). Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
@@
 
-# Conclusion
+## Conclusion
 
@@
 blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
-visual clarity. Darker colours represent higher probability of retaining spawned larvae
-than lighter colours. All 2429 reefs included in this investigation are represented in this
+visual clarity. Darker colours represent higher probability of retaining spawned larvae than
+lighter colours. All 2429 reefs included in this investigation are represented in this
 figure. Annotations represent major coastal settlements along the
@@
 cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/outgoing_strength_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-outgoingconn
+GCM.](../figs/ACCESS-ESM1-5/bioregion/outgoing_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-outgoingconn
 fig-align="center" width="14.82cm"}

### 2025-09-11 src/ADRIA/HighResCoralStress/4_analysis_plots_clustering_carbonate.jl

@@ -326,7 +326,8 @@ reefs_1_to_10_clusters = reefs_1_to_10_clusters[reefs_1_to_10_clusters.variable.
 
 for reef in eachrow(reefs_1_to_10)
     reef_id = reef.UNIQUE_ID
-    reef.low_medium_clusters = all(reefs_1_to_10_clusters[reefs_1_to_10_clusters.UNIQUE_ID.==reef_id, :value] .<= 2.0)
+    # Calculate the number of shallow reefs that are always in low/medium clusters across GCMs
+    reef.low_medium_clusters = all(reefs_1_to_10_clusters[reefs_1_to_10_clusters.UNIQUE_ID.==reef_id, :value] .<= 2.0) 
 end
 
 sum(reefs_1_to_10.low_medium_clusters) / nrow(reefs_1_to_10)

### 2025-09-12 paper/paper_draft.qmd
Adjust abstract formatting
Abstract also needs to be revisited
Rework reef definition paragraphs for flow
Simplify and focus narrative
Exploratory modelling is a feature of Robust Decision Making but probably muddles the narrative here.

@@
     Coral reefs globally face unprecedented threats from climate change, with the Great Barrier
-    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral cover from thermal stress events.
+    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral cover from thermal stress
+    events.
     Understanding drivers behind reef resilience to climate impacts is critical for conservation
@@
     connectivity was found to influence reef temporal behaviour. Our findings suggest that
-    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the performance of deep reefs, contrasting current intervention
+    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the
+    performance of deep reefs, contrasting current intervention
     practices that primarily target easily accessible sites in the 1-10m depth range. These results have
@@
 Depth characteristics for each reef were extracted using 10m resolution bathymetry data made
-available in GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched
-with the 3806 reef outlines through geometric intersections. All depth values were converted
-to positive values (depths below sea level). The median depth was used to provide an
-indicative depth value for each reef. Code, and the resulting depth estimates, are available
-at [@iwanaga2025].
-
-While the bathymetry data adopted for the given assessment are said to be accurate up to 15m
-from Mean Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth
-estimates used for this study. These are outlined further in the Discussion. Notably, the
-adopted depth estimates were derived from bathymetries based on satellite imagery. The
-bathymetry data can be limited in their alignment with the established GBRMPA reef outlines
-used to characterise reef locations and their areal extent. A Quality Assessment and Control
-process identified reefs with potential data limitations: reefs with no overlapping
-bathymetry data, reefs with minimum depth values above sea level (indicating potential data
-artifacts), and reefs where bathymetry pixels covered less than 5% of the reef polygon area.
-This process removed 842 reefs, or 22%, from the initial set of 3806 reefs. Furthermore,
-reefs that are not associated with GBRMPA Management areas [@GBRMPA2007] or reefal
-bioregions [@GBRMPA2024] were also removed from the investigation. Bioregions which
-contained fewer than three reefs after these processes were also excluded. As a result, 1377
-reefs were excluded (36%), leaving a total of 2429 remaining for the purpose of this
-investigation.
+available in GBRMPA [-@GBRMPA2020]. While the bathymetry data adopted for the given
+assessment are said to be accurate up to 15m from Mean Sea Level [@GBRMPA2020], there are
+many sources of uncertainty in the depth estimates used for this study. Notably, the adopted
+depth estimates were derived from bathymetries based on satellite imagery. The bathymetry
+data can be limited in their alignment with the established GBRMPA reef outlines used to
+characterise reef locations and their areal extent. For each reef, bathymetry data were
+spatially matched with the 3806 reef outlines through geometric intersections.
+
+A Quality Assessment and Control process identified reefs with potential data limitations:
+reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level
+(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
+5% of the reef polygon area. This process removed 842 reefs, or 22%, from the initial set of
+3806 reefs. Furthermore, reefs that are not associated with GBRMPA Management areas
+[@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed from the investigation.
+Bioregions which contained fewer than three reefs after these processes were also excluded.
+As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for the
+purpose of this investigation. All depth values were converted to positive values (depths
+below sea level). The median depth was used to provide an indicative depth value for each
+reef. Further limitations are outlined in the Discussion. Code to extract depth estimates,
+and the resulting depth estimates themselves, are available at [@iwanaga2025].
 
@@
 
-We adapted exploratory scenario modelling approach from robust decision making (RDM)
-approaches for this investigation. In particular, we used parameter sampling and exploratory
-modelling to investigate a wide range of plausible futures under different assumptions of
-environmental (climatic) conditions and ecological factors. Exploratory modelling approaches
-have gained favour in recent years as precise long-term predictions of future conditions are
-often impossible in complex ecological systems [@conradt2024; @lempert2013]. RDM embraces
-uncertainty as an inherent characteristic of complex environmental systems [@lempert2010;
-@lempert2013] and is a core methodology underpinning the development of robust and adaptive
-management strategies [@haasnoot2013]. Rather than attempting to forecast specific outcomes,
-RDM aims to systematically explore many possible futures to identify patterns. Allowing for
-the identification of robust management strategies that perform well across those diverse
-conditions, as well as conditions in which such strategies may fail. Multiple interacting
-and compounding sources of uncertainty, and a lack of broad agreement as to their
-likelihood, create inherently uncertain outcomes. While we did not directly model management
-decision making in this investigation, we used exploratory modelling to identify the
-environmental and reef characteristics, such as thermal stress, depth and connectivity, that
-support favourable outcomes such as recovery and resilience.
+We adapted an exploratory scenario modelling approach for this investigation. Specifically,
+we use combinations of model factors to investigate a wide range of potential futures under
+different assumptions of environmental (climatic) and ecological conditions. Exploratory
+modelling approaches have gained favour in recent years to explore the implications of deep
+uncertainty; where there is little or no agreement on the key drivers of a system, the
+extent of the relationship, how best to represent them or their probability distributions
+[@conradt2024; @lempert2013]. Exploratory modelling embraces uncertainty as an inherent
+characteristic of complex environmental systems [@lempert2010; @lempert2013] and is a core
+methodology underpinning the development of robust and adaptive management strategies
+[@haasnoot2013].
+
+Rather than attempting to forecast precise outcomes, the exploratory approach aims to
+systematically search many possible futures to identify patterns that lead to outcomes of
+interest. The approach allows for the identification of robust management strategies that
+perform well across a diversity of future conditions rather than attempting to identify a
+single most optimal strategy. Concurrently, assessing the wide swathe of scenarios allows
+contextual understanding of the conditions in which strategies may fail. Multiple
+interacting and compounding sources of uncertainty, and a lack of broad agreement as to
+their likelihood, create inherently uncertain outcomes. Here, exploratory modelling was
+applied to identify the environmental and reef characteristics, such as thermal stress,
+depth, and connectivity, that support favourable outcomes in reef recovery and resilience.
 

### 2025-09-12 paper/paper_draft.qmd
Changed text to be more direct to shorten

@@
 
-To apply exploratory scenario modelling, we employed a framework involving two separate
-systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and CoralBlox.
-ADRIA is a multi-criteria decision support platform designed to help reef managers address
-climate change challenges in coral reef systems [@iwanaga2023]. The ADRIA platform provides
-functionality for scenario generation and analysis as well as providing the technical
-infrastructure to couple environmental and ecosystem representations. CoralBlox is a
-computationally efficient coral population model. It simulates functional/morphological
-groups of corals over their life cycles, competing for available space over time
-[@ribeirodealmeida2024]. The coupled framework is referred to as ADRIA-CoralBlox.
+Two separate systems were employed to explore scenarios: ADRIA (the Adaptive Dynamic Reef
+Intervention Algorithms platform) and CoralBlox. ADRIA is a multi-criteria decision support
+platform designed for the assessment and analysis of coral reef intervention strategies
+under uncertainty [@iwanaga2023]. The ADRIA platform provides functionality for scenario
+generation and analysis as well as providing the technical infrastructure to couple
+environmental and ecosystem representations. CoralBlox is a computationally efficient coral
+population model. It simulates functional/morphological groups of corals over their life
+cycles, competing for available space over time [@ribeirodealmeida2024]. The coupled
+framework is referred to as ADRIA-CoralBlox.
 
 The coral demographic representation and associated model implementation are further
-detailed in the supplementary material. Of important note, however, is that the
-representation of bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a
-scaling coefficient to incorporate the amelioration effect that depth may have, following
-Baird et al., [@baird2018]. This depth-scaling reduces the proportion of coral colonies
-impacted by high heat stress as depth increases. The impacts of tropical cyclones, wave
-activity, Crown of Thorns Starfish or coral disease were not included in this investigation,
-in order to focus on assessing reef resilience under possible future warming scenarios.
+detailed in the supplementary material. Of important note is that the representation of
+bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient
+to incorporate the amelioration effect that depth may have, following Baird et al.,
+[@baird2018]. This depth-scaling reduces the proportion of coral colonies impacted by high
+heat stress as depth increases. The impacts of tropical cyclones, wave activity, Crown of
+Thorns Starfish or coral disease were not included in this investigation, in order to focus
+on assessing reef resilience under possible future warming scenarios.
 
@@
 coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol' sampling
-method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi Monte Carlo
-approach which balances scenario exploration with improved convergence properties compared
-to pseudo-random sampling. A detailed comparative analysis of the sampling methods can be
-found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
+method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a randomised Quasi Monte
+Carlo approach which balances scenario exploration with improved convergence properties
+compared to pseudo-random sampling. A detailed comparative analysis of sampling methods can
+be found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
 cover time series for each model run were scaled by the total area of each reef to represent

### 2025-09-13 paper/paper_draft.qmd
Render variables with math notation

@@
 outgoing larval flow relative to it's incoming larval flow. This is calculated as:
-$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where S represents the sum of connectivity pobabilities, N
-represents the number of connections, O denotes outgoing connectivity from the target reef
-and I denotes incoming connectivity to the target reef. If a reef has no incoming
+$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of connectivity probabilities,
+$N$ represents the number of connections, $O$ denotes outgoing connectivity from the target
+reef and $I$ denotes incoming connectivity to the target reef. If a reef has no incoming
 connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this calculation,

### 2025-09-13 paper/paper_draft.qmd
Standardize timeseries -> time series
Sometimes timeseries was used, other times it is "time series". The latter was more common so I standardized everything to "time series".

@@
 cover time series for each model run were scaled by the total area of each reef to represent
-cover as a percentage of the total estimated reef area. The scenario-median timeseries for
+cover as a percentage of the total estimated reef area. The scenario-median time series for
 each reef was used for further analyses. These time series of coral cover were then
@@
 each reef. Weighted incoming connectivity is calculated by summing the product of each
-connection strength incoming to a target reef and the mean timeseries absolute coral cover
+connection strength incoming to a target reef and the mean time series absolute coral cover
 (km^2^) of each matching source reef. This metric provides an approximation of overall
@@
 |-----------------------|-----------------------|-----------------------|-----------------------|
-| Percentage coral cover time series | Timeseries clustering, Carbonate budget analysis | Total coral cover as a percentage of reef area | To summarise coral population health over time |
+| Percentage coral cover time series | Time series clustering, Carbonate budget analysis | Total coral cover as a percentage of reef area | To summarise coral population health over time |
 | Median depth | Time series cluster assessment Carbonate budget analysis | Reef median depth as calculated with zonal raster analysis | Depth is a critical form of environmental refugia from high thermal stress |
@@
 
-The CID timeseries clustering metric corrects the Euclidean distance between pairs of time
+The CID time series clustering metric corrects the Euclidean distance between pairs of time
 series (which accounts for magnitude differences) with the complexity of each time series

### 2025-09-13 src/ADRIA/HighResCoralStress/7_rf_analysis.jl
Changes to allow direct run of script
Previously, the script could only be run via line-by-line in the REPL due to variable scoping rules causing an error to occur.

@@ -194,10 +194,10 @@ X2 = X2[:, string.([first(fi) for fi in feat_imports])]
 
 # Plot overview based on Spearman correlation
 f = Figure(size=(800, 500))
-r = 1
-c = 1
-n_rows = 2
-n_cols = 3
+global r = 1
+global c = 1
+global n_rows = 2
+global n_cols = 3
 for t_col in names(X2)
     d = X2[:, t_col]
 

### 2025-09-13 src/ADRIA/HighResCoralStress/7_rf_analysis.jl
Tune hyperparameters

@@ -77,7 +77,7 @@ X2 = coerce(
     :mean_dhw => Continuous,
     :abs_k_area => Continuous,
     :weighted_incoming_conn => Continuous,
-    :log_out_strength => Continuous,
+    # :log_out_strength => Continuous,
     :log_self_strength => Continuous
 )
 
@@ -105,7 +105,7 @@ sp_cors = Dict(
 
 rng = Random.seed!(76)
 rf = @load RandomForestClassifier pkg = "DecisionTree"
-model = rf(; rng=rng)
+model = rf(; rng=rng, sampling_fraction=0.5, n_trees=100, max_depth=15, min_samples_leaf=4)
 
 train_size = ceil(Int64, nrow(X2) * 0.6)
 shuffle_set = shuffle(1:nrow(X2))
@@ -121,13 +121,13 @@ fit!(mach)
 cluster_est = MLJ.predict(mach, train_X)
 y_pred_mode = predict_mode(mach, train_X)
 μ_accuracy = mean(y_pred_mode .== train_y)
-@info μ_accuracy  # 0.99
+@info μ_accuracy  # 0.79
 
 cluster_est = MLJ.predict(mach, test_X)
 y_pred_mode = predict_mode(mach, test_X)
 
 μ_accuracy = mean(y_pred_mode .== test_y)
-@info μ_accuracy  # 0.62
+@info μ_accuracy  # 0.58
 
 cm = confusion_matrix(y_pred_mode, test_y)
 cm.mat
@@ -171,19 +171,19 @@ end
 
 cv = CV(nfolds=3, rng=123)
 evaluate!(mach, resampling=cv, measure=[MLJ.accuracy, MLJ.cross_entropy])
-# Accuracy: 0.606
-# LogLoss: 0.853
+# Accuracy: 0.576
+# LogLoss: 0.91
 
 feat_imports = feature_importances(mach)
-#               :depth_med => 0.23860533087232372
-#                :mean_dhw => 0.16479623325258205
-#  :weighted_incoming_conn => 0.136410744763997
-#  :weighted_outgoing_conn => 0.1362327788209799
-#              :abs_k_area => 0.12357937667819203
-#            :log_so_to_si => 0.1069541180323328
-#               :bioregion => 0.09342141757959256
-# The precise values of the above are subject to change but the order of features is
-# robust.
+#               :depth_med => 0.2962643264332456
+#              :abs_k_area => 0.1433747275450697
[…]

### 2025-09-13 paper/paper_draft.qmd
Updated text describing time series clustering and RF

@@
 
-Reefs were clustered into three qualitative categories based on their temporal behaviour
-indicated by coral cover over time. The three categories were Low, Medium, and High,
-indicating their relative ability to maintain coral cover and thus their structural
-resilience. The Complexity-Invariant Distance (CID) between each time series was calculated
-to identify similarities in temporal behaviour [@batista2014]. The CID applies a correction
-factor to the Euclidean distance between pairs of time series to obtain a measure of their
-similarity. The adopted approach ensures reefs are clustered based on their temporal
-dynamics as opposed to, for example, naively clustering by their mean coral cover.
-Clustering similar time series is achieved through the use of k-medoids clustering [cf.
-@steinmann2020]. Further details on the time series clustering approach are found in the
-supplementary materials.
-
-The time series clustering was applied over the time frame between 2025 and 2075. Spatially,
-the clustering analyses were conducted for each GBR management area and at the scale of each
-reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were also performed at the
-whole-of-GBR scale but were found to lead to identical conclusions about characteristics
-influencing cluster cover compared to management area and bioregion scale analyses and so
-are not shown here. To compare time series clustering results across GCMs, management area
-scale clustering results are used to preserve coarse scale latitudinal differences between
-regions, while maintaining ease of comparison and visualisation. These comparisons include
-quantification of differences between low and high cover clusters across management regions
-under each GCM using the CID between cluster median time series. To assess how different
-reef characteristics influence time series clustering at a finer spatial scale, bioregion
-results are used to capture patterns occurring within individual groups of reefs. Results of
-all analyses at all clustering scales can be found at Grier and Iwanaga [-@grier2025] for
-those interested.
-
-Reefs in each time series cluster were compared to identify characteristics that differ
-between Low, Medium and High clusters. These characteristics include reef median depth, mean
-time series DHW, weighted incoming connectivity, outgoing connection strength, ratio of
-source-to-sink larval connectivity, larval retention probability and reef carrying capacity
-(coral habitable area).
+Reefs were clustered based on the temporal behaviour of their median coral cover time
+series. Put simply, reefs that have similar trends and trajectories are more likely to be
+clustered together. Reefs are clustered into Low, Medium, or High, indicating their relative
+ability to maintain coral cover over time. Reefs in each time series cluster were compared
+to identify characteristics that differ between Low, Medium and High clusters. These
+characteristics include reef median depth, mean time series DHW, weighted incoming
+connectivity, outgoing connection strength, ratio of source-to-sink larval connectivity,
+larval retention probability and reef carrying capacity (coral habitable area).
+
+The Complexity-Invariant Distance (CID) between each time series was calculated to identify
+similarities in temporal behaviour [@batista2014]. The CID applies a correction factor to
+the Euclidean distance between pairs of time series to obtain a measure of their similarity.
+The adopted approach ensures reefs are clustered based on their temporal dynamics as opposed
+to, for example, naively clustering by their mean coral cover. Time series clustering is
+achieved through the use of k-medoids clustering [cf. @steinmann2020]. Further details on
+the time series clustering approach are found in the supplementary materials.
+
+The time series clustering was applied over the time frame between 2025 and 2075. The
+clustering was conducted for three spatial scales: (1) the whole of GBR; (2) each GBR
+management area; and (3) for each reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). The
+analyses was conducted at the different spatial scales as, conceptually, the temporal
+behaviour constituting "low", "medium" or "high" coral cover may differ at the different
+spatial scales. As it was, analyses at the whole-of-GBR scale were found to lead to
+identical conclusions regarding reef characteristics which influence coral cover and so for
+brevity are not shown here.
+
+To compare time series clustering results across GCMs, management area scale clustering
+results are used to preserve coarse scale latitudinal differences between regions, while
+maintaining ease of comparison and visualisation. These comparisons include quantification
+of differences between low and high cover clusters across management regions under each GCM
+using the CID between cluster median time series. To assess how different reef
+characteristics influence time series clustering at a finer spatial scale, bioregion results
+are used to capture patterns occurring within individual groups of reefs. Results of all
+analyses at all spatial scales can be found at Grier and Iwanaga [-@grier2025] for those
+interested.
 
@@
 classifier [@friedman2001]. The analysis utilised the reef characteristics of interest as
-the predictors, including the median reef depth, mean DHW for the given GCM, Log10 -
-weighted incoming connectivity, Log10 - weighted outgoing connectivity, and Log10 -
-outgoing-to-incoming connectivity ratio. The full dataset consisted of the time series
-cluster assignment of each of the 2429 reefs under the five GCMs explored, for a total of
-12,145 samples. The dataset was randomly split into training (60%) and testing (40%) subsets
-to ensure model generalisability. The RF classifier achieved 99% accuracy on the training
-set and 62% on the test set.
-
-While 99% accuracy suggests the classifier is overfit to the training data, the 66% test
-accuracy indicates a meaningful relationship between modelled reef characteristics and their
-assigned clusters has been captured. A 3-fold cross-validation was also conducted, arriving
-at a similar 67% accuracy rate. The consistent level of accuracy across test and
-cross-validation demonstrates the generalised performance of the RF classifier is reliable.
+the predictors, including the median reef depth, mean DHW for the given GCM, log10-weighted
+incoming connectivity, log10-weighted outgoing connectivity, and log10-outgoing-to-incoming
+connectivity ratio. The full dataset consisted of the time series cluster assignment of each
+of the 2429 reefs under the five GCMs explored, for a total of 12,145 samples. The dataset
+was randomly split into training (60%) and testing (40%) subsets to ensure model
+generalisability. The RF classifier achieved 79% accuracy on the training set and 59% on the
+test set.
+
+A 3-fold cross-validation was also conducted, arriving at a similar 57% accuracy rate.
 Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
-0.7, 0.5 and 0.65 respectively, indicating balanced performance across the cluster
-categories. Lower performance with the Medium cluster reflects the inherent difficulty of
-classifying transitional states in natural systems.
+0.68, 0.43 and 0.62 respectively, with precision of 0.77, 0.49 and 0.66 when evaluated with
+the test set (consisting of 4858 samples). Lower performance with the Medium cluster
+reflects the inherent difficulty of classifying transitional states in natural systems. The
+consistent level of accuracy across test and cross-validation demonstrates the generalised
+performance of the RF classifier, while not accurate, was deemed sufficiently informative
+for the purpose of assessing the influence of reef characteristics.
 
@@
 for all three cluster classes using the trained RF classifier, and (3) the mean predicted
-probability for each class across all test observations. The median was also assessed (not
-shown) but was found not to substantially influence the interpretation of results. The
-process isolates the marginal effect of each predictor by averaging over the natural
-distribution of all other representative reef characteristics in the test dataset.
-Additionally, to assess possible interaction between reef depth and incoming connectivity,
-two-way partial dependence analysis was performed on grids along the range of these two
-features.
+probability for each class across all test observations. Use of the median predicted
+probability was also assessed but was found not to substantially influence the
+interpretation of results (and so, are not shown here). The process isolates the marginal
+effect of each predictor by averaging over the natural distribution of all other
+representative reef characteristics in the test dataset. Additionally, to assess possible
+interaction between reef depth and incoming connectivity, two-way partial dependence
+analysis was performed on grids along the range of these two features.
 

### 2025-09-13 paper/paper_draft.qmd
Ensure retained larvae is treated separately, and is not double counted in incoming or outgoing connectivity

--- 2025-09-13 paper/paper_draft.qmd
@@
     Coral reefs globally face unprecedented threats from climate change, with the Great Barrier
-    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral cover from thermal stress
-    events.
+    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral cover from thermal stress events.
     Understanding drivers behind reef resilience to climate impacts is critical for conservation
@@
     connectivity was found to influence reef temporal behaviour. Our findings suggest that 
-    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the
-    performance of deep reefs, contrasting current intervention
+    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the performance of deep reefs, contrasting current intervention
     practices that primarily target easily accessible sites in the 1-10m depth range. These results have 
@@
 Depth characteristics for each reef were extracted using 10m resolution bathymetry data made
-available in GBRMPA [-@GBRMPA2020]. While the bathymetry data adopted for the given
-assessment are said to be accurate up to 15m from Mean Sea Level [@GBRMPA2020], there are
-many sources of uncertainty in the depth estimates used for this study. Notably, the adopted
-depth estimates were derived from bathymetries based on satellite imagery. The bathymetry
-data can be limited in their alignment with the established GBRMPA reef outlines used to
-characterise reef locations and their areal extent. For each reef, bathymetry data were
-spatially matched with the 3806 reef outlines through geometric intersections.
-
-A Quality Assessment and Control process identified reefs with potential data limitations:
-reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level
-(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
-5% of the reef polygon area. This process removed 842 reefs, or 22%, from the initial set of
-3806 reefs. Furthermore, reefs that are not associated with GBRMPA Management areas
-[@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed from the investigation.
-Bioregions which contained fewer than three reefs after these processes were also excluded.
-As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for the
-purpose of this investigation. All depth values were converted to positive values (depths
-below sea level). The median depth was used to provide an indicative depth value for each
-reef. Further limitations are outlined in the Discussion. Code to extract depth estimates,
-and the resulting depth estimates themselves, are available at [@iwanaga2025].
+available in GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched
+with the 3806 reef outlines through geometric intersections. All depth values were converted
+to positive values (depths below sea level). The median depth was used to provide an
+indicative depth value for each reef. Code, and the resulting depth estimates, are available
+at [@iwanaga2025].
+
+While the bathymetry data adopted for the given assessment are said to be accurate up to 15m
+from Mean Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth
+estimates used for this study. These are outlined further in the Discussion. Notably, the
+adopted depth estimates were derived from bathymetries based on satellite imagery. The
+bathymetry data can be limited in their alignment with the established GBRMPA reef outlines
+used to characterise reef locations and their areal extent. A Quality Assessment and Control
+process identified reefs with potential data limitations: reefs with no overlapping
+bathymetry data, reefs with minimum depth values above sea level (indicating potential data
+artifacts), and reefs where bathymetry pixels covered less than 5% of the reef polygon area.
+This process removed 842 reefs, or 22%, from the initial set of 3806 reefs. Furthermore,
+reefs that are not associated with GBRMPA Management areas [@GBRMPA2007] or reefal
+bioregions [@GBRMPA2024] were also removed from the investigation. Bioregions which
+contained fewer than three reefs after these processes were also excluded. As a result, 1377
+reefs were excluded (36%), leaving a total of 2429 remaining for the purpose of this
+investigation.
 
@@
 
-We adapted an exploratory scenario modelling approach for this investigation. Specifically,
-we use combinations of model factors to investigate a wide range of potential futures under
-different assumptions of environmental (climatic) and ecological conditions. Exploratory
-modelling approaches have gained favour in recent years to explore the implications of deep
-uncertainty; where there is little or no agreement on the key drivers of a system, the
-extent of the relationship, how best to represent them or their probability distributions
-[@conradt2024; @lempert2013]. Exploratory modelling embraces uncertainty as an inherent
-characteristic of complex environmental systems [@lempert2010; @lempert2013] and is a core
-methodology underpinning the development of robust and adaptive management strategies
-[@haasnoot2013].
-
-Rather than attempting to forecast precise outcomes, the exploratory approach aims to
-systematically search many possible futures to identify patterns that lead to outcomes of
-interest. The approach allows for the identification of robust management strategies that
-perform well across a diversity of future conditions rather than attempting to identify a
-single most optimal strategy. Concurrently, assessing the wide swathe of scenarios allows
-contextual understanding of the conditions in which strategies may fail. Multiple
-interacting and compounding sources of uncertainty, and a lack of broad agreement as to
-their likelihood, create inherently uncertain outcomes. Here, exploratory modelling was
-applied to identify the environmental and reef characteristics, such as thermal stress,
-depth, and connectivity, that support favourable outcomes in reef recovery and resilience.
+We adapted exploratory scenario modelling approach from robust decision making (RDM)
+approaches for this investigation. In particular, we used parameter sampling and exploratory
+modelling to investigate a wide range of plausible futures under different assumptions of
+environmental (climatic) conditions and ecological factors. Exploratory modelling approaches
+have gained favour in recent years as precise long-term predictions of future conditions are
+often impossible in complex ecological systems [@conradt2024; @lempert2013]. RDM embraces
+uncertainty as an inherent characteristic of complex environmental systems [@lempert2010;
+@lempert2013] and is a core methodology underpinning the development of robust and adaptive
+management strategies [@haasnoot2013]. Rather than attempting to forecast specific outcomes,
+RDM aims to systematically explore many possible futures to identify patterns. Allowing for
+the identification of robust management strategies that perform well across those diverse
+conditions, as well as conditions in which such strategies may fail. Multiple interacting
+and compounding sources of uncertainty, and a lack of broad agreement as to their
+likelihood, create inherently uncertain outcomes. While we did not directly model management
+decision making in this investigation, we used exploratory modelling to identify the
+environmental and reef characteristics, such as thermal stress, depth and connectivity, that
+support favourable outcomes such as recovery and resilience.
 
@@
 
-Two separate systems were employed to explore scenarios: ADRIA (the Adaptive Dynamic Reef
-Intervention Algorithms platform) and CoralBlox. ADRIA is a multi-criteria decision support
-platform designed for the assessment and analysis of coral reef intervention strategies
-under uncertainty [@iwanaga2023]. The ADRIA platform provides functionality for scenario
-generation and analysis as well as providing the technical infrastructure to couple
-environmental and ecosystem representations. CoralBlox is a computationally efficient coral
-population model. It simulates functional/morphological groups of corals over their life
-cycles, competing for available space over time [@ribeirodealmeida2024]. The coupled
-framework is referred to as ADRIA-CoralBlox.
+To apply exploratory scenario modelling, we employed a framework involving two separate
+systems: ADRIA (the Adaptive Dynamic Reef Intervention Algorithms platform) and CoralBlox.
+ADRIA is a multi-criteria decision support platform designed to help reef managers address
+climate change challenges in coral reef systems [@iwanaga2023]. The ADRIA platform provides
+functionality for scenario generation and analysis as well as providing the technical
+infrastructure to couple environmental and ecosystem representations. CoralBlox is a
+computationally efficient coral population model. It simulates functional/morphological
+groups of corals over their life cycles, competing for available space over time
+[@ribeirodealmeida2024]. The coupled framework is referred to as ADRIA-CoralBlox.
 
 The coral demographic representation and associated model implementation are further
-detailed in the supplementary material. Of important note is that the representation of
-bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient
-to incorporate the amelioration effect that depth may have, following Baird et al.,
-[@baird2018]. This depth-scaling reduces the proportion of coral colonies impacted by high
-heat stress as depth increases. The impacts of tropical cyclones, wave activity, Crown of
-Thorns Starfish or coral disease were not included in this investigation, in order to focus
-on assessing reef resilience under possible future warming scenarios.
+detailed in the supplementary material. Of important note, however, is that the
+representation of bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a
+scaling coefficient to incorporate the amelioration effect that depth may have, following
+Baird et al., [@baird2018]. This depth-scaling reduces the proportion of coral colonies
+impacted by high heat stress as depth increases. The impacts of tropical cyclones, wave
+activity, Crown of Thorns Starfish or coral disease were not included in this investigation,
+in order to focus on assessing reef resilience under possible future warming scenarios.
 
@@
 coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol' sampling
-method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a randomised Quasi Monte
-Carlo approach which balances scenario exploration with improved convergence properties
-compared to pseudo-random sampling. A detailed comparative analysis of sampling methods can
-be found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
+method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a random-Quasi Monte Carlo
+approach which balances scenario exploration with improved convergence properties compared
+to pseudo-random sampling. A detailed comparative analysis of the sampling methods can be
+found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
 cover time series for each model run were scaled by the total area of each reef to represent
@@
 each reef. Weighted incoming connectivity is calculated by summing the product of each
-connection strength incoming to a target reef and the mean timeseries absolute coral cover
-(km^2^) of each matching source reef. This metric provides an approximation of overall
-larval flow into a reef, with high values indicating the target reef is supplied high
-volumes of larvae via strong connections and low values indicating the target reef has weak
-(or no) incoming connections or is supplied by small source populations. A limitation of
-weighted incoming connectivity is it does not incorporate the proportion of the source
-reef's population that is reproducing and producing larvae, instead taking the total coral
-cover area as an indicator of larval productivity. Outgoing connection strength is
-calculated as the sum of all outgoing transition probabilities from a target reef. Outgoing
-connection strength has a theoretical maximum of one (all larvae reach settlement on sink
-reefs), however the large size of the GBR combined with larval mortality considerations
-result in outgoing connection strength values much lower than one. The ratio of
-source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
-outgoing larval flow relative to it's incoming larval flow. This is calculated as:
-$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of connectivity probabilities,
-$N$ represents the number of connections, $O$ denotes outgoing connectivity from the target
-reef and $I$ denotes incoming connectivity to the target reef. If a reef has no incoming
-connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this calculation,
-do not directly represent the larval supply gained as the breeding populations from which
-connections are coming from are not represented. A source-to-sink ratio greater than 1 (a
-value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
-larval flow. Reef larval retention probability indicates the proportion of spawned larvae
-from a target reef that remain to settlement.
+connection strength incoming to a target reef (excluding retained larvae from the target
+reef) and the mean timeseries absolute coral cover (km^2^) of each matching source reef.
+This metric provides an approximation of overall larval flow into a reef, with high values
+indicating the target reef is supplied high volumes of larvae via strong connections and low
+values indicating the target reef has weak (or no) incoming connections or is supplied by
+small source populations. A limitation of weighted incoming connectivity is it does not
+incorporate the proportion of the source reef's population that is reproducing and producing
+larvae, instead taking the total coral cover area as an indicator of larval productivity.
+Outgoing connection strength is calculated as the sum of all outgoing transition
+probabilities from a target reef. Outgoing connection strength has a theoretical maximum of
+one (all larvae reach settlement on sink reefs), however the large size of the GBR combined
+with larval mortality considerations result in outgoing connection strength values much
+lower than one. The ratio of source-to-sink connectivity ($O:I$) for a target reef
+represents the strength of the reef's outgoing larval flow relative to it's incoming larval
+flow. This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where S represents the sum of
+connectivity pobabilities, N represents the number of connections, O denotes outgoing
+connectivity from the target reef and I denotes incoming connectivity to the target reef. If
+a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value. Incoming
+connections in this calculation, do not directly represent the larval supply gained as the
+breeding populations from which connections are coming from are not represented. A
+source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef
+has greater outgoing than incoming larval flow. Reef larval retention probability indicates
+the proportion of spawned larvae from a target reef that remain to settlement.
 

### 2025-09-13 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -82,6 +82,7 @@ for reef in eachindex(reefs)
 
     outgoing = outgoing[:, outgoing.Sink .!= reef_id] # Ensure outgoing connectivity does not include retained larvae
     incoming = connectivity_matrix[:, connectivity_matrix.Sink.==reef_id]
+    incoming = incoming[:, incoming.Source .!= reef_id] # Ensure incoming connectivity is only externally sourced larval flow
 
     income_strength = sum(incoming)
     income_count = count(incoming .> 0)

### 2025-09-14 paper/paper_draft.qmd

--- 2025-09-13 paper/paper_draft.qmd
@@
 each reef. Weighted incoming connectivity is calculated by summing the product of each
-connection strength incoming to a target reef and the mean time series absolute coral cover
-(km^2^) of each matching source reef. This metric provides an approximation of overall
-larval flow into a reef, with high values indicating the target reef is supplied high
-volumes of larvae via strong connections and low values indicating the target reef has weak
-(or no) incoming connections or is supplied by small source populations. A limitation of
-weighted incoming connectivity is it does not incorporate the proportion of the source
-reef's population that is reproducing and producing larvae, instead taking the total coral
-cover area as an indicator of larval productivity. Outgoing connection strength is
-calculated as the sum of all outgoing transition probabilities from a target reef. Outgoing
-connection strength has a theoretical maximum of one (all larvae reach settlement on sink
-reefs), however the large size of the GBR combined with larval mortality considerations
-result in outgoing connection strength values much lower than one. The ratio of
-source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
-outgoing larval flow relative to it's incoming larval flow. This is calculated as:
-$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of connectivity probabilities,
-$N$ represents the number of connections, $O$ denotes outgoing connectivity from the target
-reef and $I$ denotes incoming connectivity to the target reef. If a reef has no incoming
-connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this calculation,
-do not directly represent the larval supply gained as the breeding populations from which
-connections are coming from are not represented. A source-to-sink ratio greater than 1 (a
-value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
-larval flow. Reef larval retention probability indicates the proportion of spawned larvae
-from a target reef that remain to settlement.
+connection strength incoming to a target reef (excluding retained larvae from the target
+reef) and the mean timeseries absolute coral cover (km^2^) of each matching source reef.
+This metric provides an approximation of overall larval flow into a reef, with high values
+indicating the target reef is supplied high volumes of larvae via strong connections and low
+values indicating the target reef has weak (or no) incoming connections or is supplied by
+small source populations. A limitation of weighted incoming connectivity is it does not
+incorporate the proportion of the source reef's population that is reproducing and producing
+larvae, instead taking the total coral cover area as an indicator of larval productivity.
+Outgoing connection strength is calculated as the sum of all outgoing transition
+probabilities from a target reef. Outgoing connection strength has a theoretical maximum of
+one (all larvae reach settlement on sink reefs), however the large size of the GBR combined
+with larval mortality considerations result in outgoing connection strength values much
+lower than one. The ratio of source-to-sink connectivity ($O:I$) for a target reef
+represents the strength of the reef's outgoing larval flow relative to it's incoming larval
+flow. This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where S represents the sum of
+connectivity pobabilities, N represents the number of connections, O denotes outgoing
+connectivity from the target reef and I denotes incoming connectivity to the target reef. If
+a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value. Incoming
+connections in this calculation, do not directly represent the larval supply gained as the
+breeding populations from which connections are coming from are not represented. A
+source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef
+has greater outgoing than incoming larval flow. Reef larval retention probability indicates
+the proportion of spawned larvae from a target reef that remain to settlement.
 

### 2025-09-15 paper/paper_draft.qmd
Remove outlier connectivity reefs from post-hoc data analyses

@@
 Bioregions which contained fewer than three reefs after these processes were also excluded.
-As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for the
-purpose of this investigation. All depth values were converted to positive values (depths
+As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining. All depth
+values were converted to positive values (depths
 below sea level). The median depth was used to provide an indicative depth value for each
 reef. Further limitations are outlined in the Discussion. Code to extract depth estimates,
-and the resulting depth estimates themselves, are available at [@iwanaga2025].
+and the resulting depth estimates themselves, are available at [@iwanaga2025]. To ensure
+effective data analysis, reefs with incoming or outgoing connectivity values below the 5th
+percentile were removed from post-hoc analyses, leaving 2197 reefs remaining for display in results.
 
@@
 [@GBRMPA2007]. Reef centroids are marked individually for visual clarity and are coloured
-according to its bioregion [@GBRMPA2024]. All 2429 reefs included in this investigation are
+according to its bioregion [@GBRMPA2024]. All 2197 reefs included in this investigation are
 represented in this figure. Annotations represent major coastal settlements along the
@@
 each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for
-all pixels touching each reef outline. The process described here was conducted for all 2429
+all pixels touching each reef outline. The process described here was conducted for all 2197
 reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
@@
 connectivity ratio. The full dataset consisted of the time series cluster assignment of each
-of the 2429 reefs under the five GCMs explored, for a total of 12,145 samples. The dataset
+of the 2197 reefs under the five GCMs explored, for a total of 12,145 samples. The dataset **[]
 was randomly split into training (60%) and testing (40%) subsets to ensure model
@@
 Comparing across GCMs, it is common for reefs to switch between clusters, including from Low
-to High and vice versa (@sfig-gcm-bioregion-cluster-assignment). Of 2429 reefs, 20% (503) of
-reefs have consistent cluster assignment across all GCMs. Of the 503 consistently assigned
-reefs, 49% are within the Far Northern Management area, with 7%, 13% and 31% occurring in
+to High and vice versa (@sfig-gcm-bioregion-cluster-assignment). Of 2197 reefs, 21% (462) of
+reefs have consistent cluster assignment across all GCMs. Of the 462 consistently assigned
+reefs, 23% are within the Far Northern Management area, with 1%, 55% and 21% occurring in
 the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas
-respectively (@sfig-gcm-cluster-map). Of the 503 consistently assigned reefs, 32%, 7% and
-61% are clustered into Low, Medium and High clusters respectively. High levels of assignment
+respectively (@sfig-gcm-cluster-map). Of the 462 consistently assigned reefs, 34%, 18% and
+47% are clustered into Low, Medium and High clusters respectively. High levels of assignment
 variability across GCMs are expected as due to spatial differences in each given GCM’s DHW
@@
 identification of sites from the surface, in combination with tourism return value. Our
-results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
-reefs), 57% (991) of reefs are consistently clustered into the Low and Medium cover clusters
+results suggest that of the assessed reefs occurring within the 1-10m depth range (1551
+reefs), 59% (920) of reefs are consistently clustered into the Low and Medium cover clusters
 across the GCMs (at the GBRMPA management region scale), with many unable to maintain
@@
 Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
-cluster and blue represents reefs in the high cover cluster. All 2429 reefs included in this
+cluster and blue represents reefs in the high cover cluster. All 2197 reefs included in this
 investigation are represented in this figure. Annotations represent major coastal
@@
 Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for visual clarity.
-Darker colours represent greater reef depth values than lighter colours. All 2429 reefs
+Darker colours represent greater reef depth values than lighter colours. All 2197 reefs
 included in this investigation are represented in this figure. Annotations represent major
@@
 marked individually for visual clarity. Darker colours represent greater carrying capacity
-area values than lighter colours. All 2429 reefs included in this investigation are
+area values than lighter colours. All 2197 reefs included in this investigation are
 represented in this figure. Annotations represent major coastal settlements along the
@@
 visual clarity. Darker colours represent higher outgoing connection strength values than
-lighter colours. All 2429 reefs included in this investigation are represented in this
+lighter colours. All 2197 reefs included in this investigation are represented in this
 figure. Annotations represent major coastal settlements along the
@@
 values than lighter colours. Source-to-sink ratio values above zero (one on normal scale)
-indicate a reef has greater outgoing than incoming connectivity. All 2429 reefs included in
+indicate a reef has greater outgoing than incoming connectivity. All 2197 reefs included in
 this investigation are represented in this figure. Annotations represent major coastal
@@
 visual clarity. Darker colours represent higher probability of retaining spawned larvae than
-lighter colours. All 2429 reefs included in this investigation are represented in this
+lighter colours. All 2197 reefs included in this investigation are represented in this
 figure. Annotations represent major coastal settlements along the
@@
 their median years across threshold values, with darker colours representing greater number
-of years with positive carbonate budgets than lighter colours. All 2429 reefs included in
+of years with positive carbonate budgets than lighter colours. All 2197 reefs included in
 this investigation are represented in this figure. This map depicts values from the
@@
 visual clarity. Darker colours represent higher mean DHW values than lighter colours. All
-2429 reefs included in this investigation are represented in this figure. This map depicts
+2197 reefs included in this investigation are represented in this figure. This map depicts
 values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
@@
 marked individually for visual clarity. Darker colours represent higher weighted incoming
-connectivity values than lighter colours. All 2429 reefs included in this investigation are
+connectivity values than lighter colours. All 2197 reefs included in this investigation are
 represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations

### 2025-09-15 src/ADRIA/HighResCoralStress/3_collating_context_layers.jl

@@ -271,7 +271,8 @@ outliers_removed = (
     (context_layers[:, "ACCESS-ESM1-5_weighted_incoming_conn"] .> quantile(context_layers[:, "ACCESS-ESM1-5_weighted_incoming_conn"], 0.05)) .&
     (context_layers[:, "ACCESS-CM2_weighted_incoming_conn"] .> quantile(context_layers[:, "ACCESS-CM2_weighted_incoming_conn"], 0.05)) .&
     (context_layers[:, "GFDL-CM4_weighted_incoming_conn"] .> quantile(context_layers[:, "GFDL-CM4_weighted_incoming_conn"], 0.05)) .&
-    (context_layers[:, "NorESM2-MM_weighted_incoming_conn"] .> quantile(context_layers[:, "NorESM2-MM_weighted_incoming_conn"], 0.05))
+    (context_layers[:, "NorESM2-MM_weighted_incoming_conn"] .> quantile(context_layers[:, "NorESM2-MM_weighted_incoming_conn"], 0.05)) .&
+    (context_layers.out_strength .> quantile(context_layers.out_strength, 0.05))
 )
 sum(outliers_removed)
 context_layers = context_layers[outliers_removed, :]

### 2025-09-15 paper/paper_draft.qmd
Regenerate figures with outliers removed
Update reef counts throughout paper and reduce emphasis on the connectivity - depth interactions in results/discussion

@@
     refugia that reduce bleaching impacts. Interaction between reef depth and incoming
-    connectivity was found to influence reef temporal behaviour. Our findings suggest that
+    connectivity was found to influence reef temporal behaviour at 15m depth. Our findings suggest that
     depth provides critical protection against thermal stress, with high incoming connectivity enhancing the
@@
 As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining. All depth
-values were converted to positive values (depths
-below sea level). The median depth was used to provide an indicative depth value for each
-reef. Further limitations are outlined in the Discussion. Code to extract depth estimates,
-and the resulting depth estimates themselves, are available at [@iwanaga2025]. To ensure
-effective data analysis, reefs with incoming or outgoing connectivity values below the 5th
-percentile were removed from post-hoc analyses, leaving 2197 reefs remaining for display in results.
+values were converted to positive values (depths below sea level). The median depth was used
+to provide an indicative depth value for each reef. Further limitations are outlined in the
+Discussion. Code to extract depth estimates, and the resulting depth estimates themselves,
+are available at [@iwanaga2025]. To ensure effective data analysis, reefs with incoming or
+outgoing connectivity values below the 5th percentile were removed from post-hoc analyses,
+leaving 2197 reefs remaining for display in results.
 
@@
 connectivity ratio. The full dataset consisted of the time series cluster assignment of each
-of the 2197 reefs under the five GCMs explored, for a total of 12,145 samples. The dataset **[]
-was randomly split into training (60%) and testing (40%) subsets to ensure model
-generalisability. The RF classifier achieved 79% accuracy on the training set and 59% on the
+of the 2197 reefs under the five GCMs explored, for a total of 10,985 samples. The dataset
+\*\*\[\] was randomly split into training (60%) and testing (40%) subsets to ensure model
+generalisability. The RF classifier achieved 80% accuracy on the training set and 59% on the
 test set.
 
-A 3-fold cross-validation was also conducted, arriving at a similar 57% accuracy rate.
+A 3-fold cross-validation was also conducted, arriving at a similar 59% accuracy rate.
 Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
-0.68, 0.43 and 0.62 respectively, with precision of 0.77, 0.49 and 0.66 when evaluated with
-the test set (consisting of 4858 samples). Lower performance with the Medium cluster
+0.70, 0.41 and 0.63 respectively, with precision of 0.77, 0.47 and 0.64 when evaluated with
+the test set (consisting of 4394 samples). Lower performance with the Medium cluster
 reflects the inherent difficulty of classifying transitional states in natural systems. The
@@
 reef characteristics that influence its temporal behaviour, and thus its cluster assignment
-into Low, Medium, or High. Bioregion classification was excluded from this analysis as a
-predictor due to its categorical nature providing limited interpretable information, and is
-further justified by its low feature importance score of 9%, the lowest of all predictors
-(@fig-ts-cluster-pdp; Panel A). Reef median depth, mean DHW level and weighted incoming
-connectivity (Log10) have the highest feature importance scores, accounting for 22%, 17% and
-14% predictive importance respectively. The carrying capacity of a reef accounts for 12%
-feature importance, while outgoing connection strength, source-to-sink ratio and larval
-retention account for 10%, 9% and 7% respectively.
+into Low, Medium, or High. Reef median depth, carrying capacity and mean time series DHW
+level have the highest feature importance scores, accounting for 29%, 15% and 15% predictive
+importance respectively (@fig-ts-cluster-pdp; Panel A). Reef weighted incoming connectivity,
+outgoing connectivity strength, source-to-sink connectivity ratio and larval retention
+probability account for \~12%, 11%, 10% and 8% respectively.
 
@@
 higher probability of being clustered into the Low cluster category compared to other reefs.
-Additionally, two-way analyses revealed an interaction between reef depth and incoming
-connectivity in determining cluster category assignment, particularly at the high depth
-range (@fig-ts-cluster-pdp-twoway-incoming). Two-way analyses revealed that reefs at greater
-than 10m depth are unlikely to be clustered into the Low cluster category, regardless of
-their incoming connectivity levels. However, at greater than 10m depth reefs with higher
-incoming connectivity are more likely to be assigned to a High cluster, while reefs with low
-incoming connectivity are more likely to be assigned to a Medium cover cluster
-(@fig-ts-cluster-pdp-twoway-incoming). Two-way analyses, for depth and outgoing connection
-strength, revealed a slight interaction with deep reefs with high outgoing connectivity
-having the greatest probability of being clustered into a high cover cluster
-(@sfig-ts-cluster-pdp-twoway-outgoing).
+Additionally, two-way analyses revealed little interaction between depth and incoming and
+outgoing connectivity metrics for reef clustering probabilities
+(@fig-ts-cluster-pdp-twoway-incoming; @sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a
+median depth around 15m and high incoming connectivity may benefit slightly, with higher
+probability of High cover cluster assignment compared to 15m - depth reefs with lower
+connectivity.
 
@@
 the potential for positive flow on effects due to outgoing connectivity when selecting
-intervention sites [@hock2017]. Two-way partial dependence analysis revealed reefs with high
-depths and high outgoing connectivity levels have a high probability of being clustered into
-more resilient reef clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results suggest
-that interventions targetting deep reefs will also benefit from high incoming and outgoing
-connectivity levels, allowing for high potential for site resilience and outgoing flow of
-benefits and recovery. Transient, and difficult to measure, properties such as reef
+intervention sites [@hock2017]. Transient, and difficult to measure, properties such as reef
 connectivity are likely to increase uncertainty in intervention planning to a greater degree
@@
 @torres2024]. Our results suggest that incoming connectivity contributes positively to high
-cover cluster allocation for reefs over 10m deep. At depths of less than 10m thermal stress
-may be too high for incoming juveniles to contribute to long term recovery. While there is
-interaction between incoming connectivity and depth for reef cluster prediction, according
-to available input data, there are few reefs in the GBR that occur at depths \>10m and have
-Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget),
-resulting in overall low importance of connectivity as an individual feature for clustering
-across the GBR. Furthermore, our results suggest no direct, first order, relationship
-between weighted incoming connectivity and the ability of reefs to maintain positive
-carbonate budgets under future conditions. There has been contrasting evidence [@bode2018;
-@hock2017] surrounding whether recent generation connectivity modelling is able to identify
-reefs that are important for recovery processes, with findings dependent on the larval
-connectivity model used. These investigations were performed using prior generations of
-larval connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018]
-time periods, without considering the influence of reef depth on resilience. Using updated
-1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal sample
-of particle flows, our results suggest that larval connectivity alone may not be important
-or reef resilience and recovery, but should be considered in combination with more
-influential factors such as depth. Comprehensive comparisons and validation of multiple
-connectivity model outputs would improve certainty and allow for the targetting of reefs by
-combining abiotic factors such as depth with connectivity.
+cover cluster allocation for reefs around 15m deep. However, our results suggest no direct,
+first order, relationship between weighted incoming connectivity and the ability of reefs to
+maintain positive carbonate budgets under future conditions. There has been contrasting
+evidence [@bode2018; @hock2017] surrounding whether recent generation connectivity modelling
+is able to identify reefs that are important for recovery processes, with findings dependent
+on the larval connectivity model used. These investigations were performed using prior
+generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and
+1996-2002 [@bode2018] time periods, without considering the influence of reef depth on
+resilience. Using updated 1km^2^ resolution larval connectivity across the whole GBR, with a
+limited temporal sample of particle flows, our results suggest that larval connectivity
+alone may not be important or reef resilience and recovery, but should be considered in
+combination with more influential factors such as depth. Comprehensive comparisons and
+validation of multiple connectivity model outputs would improve certainty and allow for the
+targetting of reefs by combining abiotic factors such as depth with connectivity.
 
@@
 support of depth as a form of thermal refugia for shallow-water reefs on the GBR. Targetting
-reefs with median depths greater than 10m and high incoming and ougoing larval connections
-may aid in identifying the most resilient reefs under climate change. We suggest further
-analyses that investigate the benefits of incorporating depth-based resilience into reef
-intervention decision making, as well as further research and development in connectivity
-modelling methods for whole-ecosystem scales.
+reefs with median depths greater than 10m may aid in identifying the most resilient reefs
+under climate change. We suggest further analyses that investigate the benefits of
+incorporating depth-based resilience into reef intervention decision making, as well as
+further research and development in connectivity modelling methods for whole-ecosystem
+scales.
 

### 2025-09-15 src/ADRIA/HighResCoralStress/7_rf_analysis.jl

@@ -77,7 +77,7 @@ X2 = coerce(
     :mean_dhw => Continuous,
     :abs_k_area => Continuous,
     :weighted_incoming_conn => Continuous,
-    # :log_out_strength => Continuous,
+    :log_out_strength => Continuous,
     :log_self_strength => Continuous
 )
 
@@ -555,103 +555,104 @@ save(
     px_per_unit=dpi
 )
 
-# test_X.pred_y = y_pred_mode
-# test_X.y = test_y
-# test_X.bioregion = bioregion_cats[shuffle_set[train_size+1:end]]
-# test_X.bioregion_average_lat = reef_properties.bioregion_average_latitude[shuffle_set[train_size+1:end]]
 
-# perf_by_bio = combine(groupby(test_X, :bioregion)) do sdf
-#     (; n=nrow(sdf),
-#         acc=mean(sdf.y .== sdf.pred_y),
-#         size=mean(sdf.abs_k_area),
-#         depth=mean(sdf.depth_med),
-#         dhw=mean(sdf.mean_dhw),
-#         income_conn=mean(sdf.weighted_incoming_conn),
-#         outgoing_conn=mean(sdf.log_out_strength),
-#         self_conn=mean(sdf.log_self_strength),
-#         log_so_to_si=mean(sdf.log_so_to_si),
-#         # bior_ave_lat=mean(sdf.bioregion_average_lat)
-#     )
-# end
-# perf_by_bio = sort(perf_by_bio, :bior_ave_lat, rev=true)
+test_X.pred_y = y_pred_mode
+test_X.y = test_y
+test_X.bioregion = reef_properties.bioregion[shuffle_set[train_size+1:end]]
+test_X.bioregion_average_lat = reef_properties.bioregion_average_latitude[shuffle_set[train_size+1:end]]
 
-# bioregion_colors = distinguishable_colors(nrow(perf_by_bio))
+perf_by_bio = combine(groupby(test_X, :bioregion)) do sdf
+    (; n=nrow(sdf),
+        acc=mean(sdf.y .== sdf.pred_y),
+        size=mean(sdf.abs_k_area),
+        depth=mean(sdf.depth_med),
+        dhw=mean(sdf.mean_dhw),
+        income_conn=mean(sdf.weighted_incoming_conn),
+        outgoing_conn=mean(sdf.log_out_strength),
[…]

### 2025-09-17 paper/paper_draft.qmd
Add interim connectivity sentence as a placeholder
Clarify and format quantitative metrics explanation table.

@@
     Coral reefs globally face unprecedented threats from climate change, with the Great Barrier
-    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral cover from thermal stress
-    events.
+    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral 
+    cover from thermal stress events.
     Understanding drivers behind reef resilience to climate impacts is critical for conservation
@@
 
+::: {#tbl-gcms}
 | Global Climate Model source | ECS value (°C)     | Interpreted relative severity | Results found in |
@@
 
-: Information for each GCM used in this investigation including Equilibrium Climate
+Information for each GCM used in this investigation including Equilibrium Climate
 Sensitivity (ECS) value, interpreted relative severity and where results for an individual
@@
 very-likely ECS range and was taken as an intermediate model with results displayed in the
-main text. {#tbl-gcms}
+main text.
+:::
 
@@
 
-\*\* need information on generation of GBR1 connectivity used \*\*
-
-Connectivity data from 24 days in total were used in this investigation to estimate coral
-larval flows. These data span six years from 2015 to 2020. The years 2015, 2016, 2018 and
-2019 are each represented by connectivity matrices covering spawning periods over three days
-in each year (12 days in total), while 2017 and 2020 are each represented by six spawning
-days each, coming to a total of 24 days of connectivity matrices. The values in these
-matrices indicate the probability of larval transfer between each pair of reefs in the GBR,
-herein referred to as connectivity strengths. Indicative connectivity strengths are
-implemented in ADRIA-CoralBlox as the mean of all available data for each location (i.e.,
-mean of all 24 spawning days). While the connectivity strengths do not vary from year to
-year within each ADRIA-CoralBlox simulation, they do vary between reefs which are of varying
-sizes, providing sufficient heterogeneity to capture spatial patterns in larval dispersal
-and settlement dynamics. This spatial variability also enables investigations into the
-influence of connectivity strength and its role in driving recovery processes.
+Larval transition probability matrices were generated using the EReefs Great Barrier Reef
+1km resolution hydrodynamic model and particle tracking simulations. Connectivity data from
+24 days in total were used in this investigation to estimate coral larval flows. These data
+span six years from 2015 to 2020. The years 2015, 2016, 2018 and 2019 are each represented
+by connectivity matrices covering spawning periods over three days in each year (12 days in
+total), while 2017 and 2020 are each represented by six spawning days each, coming to a
+total of 24 days of connectivity matrices. The values in these matrices indicate the
+probability of larval transfer between each pair of reefs in the GBR, herein referred to as
+connectivity strengths. Indicative connectivity strengths are implemented in ADRIA-CoralBlox
+as the mean of all available data for each location (i.e., mean of all 24 spawning days).
+While the connectivity strengths do not vary from year to year within each ADRIA-CoralBlox
+simulation, they do vary between reefs which are of varying sizes, providing sufficient
+heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. This
+spatial variability also enables investigations into the influence of connectivity strength
+and its role in driving recovery processes.
 
@@
 
+::: {#stbl-metrics}
 | Metric | Used in | Definition | Justification |
 |-----------------------|-----------------------|-----------------------|-----------------------|
-| Percentage coral cover time series | Time series clustering, Carbonate budget analysis | Total coral cover as a percentage of reef area | To summarise coral population health over time |
+| Percentage coral cover time series | Time series clustering, Carbonate budget analysis | Total coral cover as a percentage of reef area | To summarise coral population health over time. |
 | Median depth | Time series cluster assessment Carbonate budget analysis | Reef median depth as calculated with zonal raster analysis | Depth is a critical form of environmental refugia from high thermal stress |
-| Mean time series DHW | Time series cluster assessment | Reef mean DHW value across time series | Resilient reefs may experience reduced surface DHWs |
-| Source - to - sink connectivity ratio | Time series cluster assessment | Ratio of reef outgoing to incoming connectivity | Reefs with greater source than sink connectivity may have lower recovery |
-| Weighted incoming connectivity | Time series cluster assessment, Carbonate budget analysis | Incoming connectivity strength weighted by mean time series coral cover of source reefs | High incoming larval flow assists reef recovery |
-| Weighted outgoing connectivity | Time series cluster assessment | Outgoing connectivity strength weighted by mean coral cover | High outgoing larval flow may lower recovery capacity of the target reef |
-| Carrying capacity | Time series cluster assessment | Reef habitable area \[m^2^\] | Captures the size of the viable reef extent |
-
-: Quantitative metrics used in this investigation
+| Mean time series DHW | Time series cluster assessment | Reef mean DHW value across time series | To quantify the surface thermal stress experienced on each reef over time series. |
+| Source - to - sink connectivity ratio | Time series cluster assessment | Ratio of reef outgoing to incoming connectivity | To examine whether a reef may be a 'net contributor' or 'net receiver' of larvae in the connectivity network.
+|
+| Weighted incoming connectivity | Time series cluster assessment, Carbonate budget analysis | Incoming connectivity strength weighted by mean time series coral cover of source reefs | To approximate the larval flow received by a reef over the projected time series.
+|
+| Outgoing connectivity strength | Time series cluster assessment, Carbonate budget analysis | Sum of a reef's outgoing larval transition probability values.
+| To understand the contribution of a reef to the connectivity network and the possibility for flow-on effects from reef states.
+|
+| Larval retention probability | Time series cluster assessment | Diagonal larval transition matrix values. | To understand the relative proportion of larvae retained on a reef. |
+| Carrying capacity | Time series cluster assessment | Reef habitable area \[m^2^\] | Captures the size of the viable reef extent. |
+
+Quantitative metrics used in this investigation.
+:::
 

### 2025-09-18 paper/paper_draft.qmd
Update Julia-rendered table to ensure proper rendering and label/caption attachment in word output

@@
 bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
-[@australianinstituteofmarinescience2024]; @cantin2024\].
+[@australianinstituteofmarinescience2024; @cantin2024].
 
@@
 #| message: false
-#| results: asis
-#| label: stbl-cluster-cid
-#| tbl-cap: Complexity invariant distance (CID) between low and high cluster median time series in each management area under each GCM.
+#| output: asis
+
+cap = """
+Complexity invariant distance (CID) between low and high cluster median time series in each management area under each GCM.
 CID values are calculated for percentage cover time series (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) time series (@sfig-gcm-dhw-trajectories).
@@
 CID values for percentage cover and DHW time series are not directly comparable as the time series use different units.
-
-using PrettyTables, Markdown
+"""
+using Markdown,Tables,MarkdownTables
 cd("../src")
 include("../src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl"); # Quantify low-high cluster differences using CID metric.
-
-io = IOBuffer()
-
-header = ["GCM", "Management area", "CID - cover", "CID - DHW"]
-pretty_table(io, distances, backend=Val(:markdown), header=header)
-
-md_string = (String(take!(io)))
-Markdown.parse(md_string)
+rename!(distances, 
+    "management_area" => "Management area",
+    "CID_cover" => "CID - cover",
+    "CID_dhw" => "CID - DHW"
+)
+print("""
+::: {.table #stbl-cluster-cid}
+$(markdown_table(distances, String))
+
+$(cap)
+:::
+""")
 ```

### 2025-09-20 paper/paper_draft.qmd
Remove use of 'Structural' resilience to prevent confusion about temporal resilience and maintenance of carbonate budgets

@@
 Understanding the characteristics of reefs that will persist under projected climate
-conditions requires examining reef resilience across multiple scales and processes.
-Structural resilience - the capacity to maintain coral populations and avoid ecosystem
+conditions requires examining reef resilience across multiple scales and processes. Coral
+reef ecosystem resilience - the capacity to maintain coral populations and avoid ecosystem
 regime shifts - depends on three interconnected mechanisms. First, the ability of individual
@@
 recolonisation after disturbances [@hock2017; @mumby2008; @torres2024]. Third, the
-maintenance of the carbonate framework that provides reef structure [@perry2012]. We aim to
-assess how these mechanisms interact under projected climate conditions to identify the
-characteristics of structurally resilient reefs through scenario-based coral population
-modelling for the Great Barrier Reef ecosystem.
+maintenance, and accretion, of the carbonate framework that provides reef structure
+[@perry2012]. We aim to assess how these mechanisms interact under projected climate
+conditions to identify the characteristics of resilient reefs through scenario-based coral
+population modelling for the Great Barrier Reef ecosystem.
 
@@
 Our findings support the hypothesis that reefs at greater depths will exhibit
-characteristics of refugia and more prolonged structural resilience under climate change
-compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest
-that rubble instability is inversely correlated with reef depth, possibly limiting juvenile
-coral recruitment capacity of shallow reefs. A caveat to our depth-resilience findings is
-the quality of the bathymetry data used to calculate median reef depth. As detailed
-previously, estimates of median reef depth are derived from satellite imagery (at $10m^2$
-resolution) which can be subject to high degrees of uncertainty, both in terms of the
-estimated depth for each pixel as well as their alignment to the established GBRMPA reef
-outlines. Additionally, we do not incorporate light-based decreases in coral growth rates as
-depth increases [@baker1975; @huston1985; @ruiz-diaz2022].
+characteristics of refugia and more prolonged resilience under climate change compared to
+shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest that rubble
+instability is inversely correlated with reef depth, possibly limiting juvenile coral
+recruitment capacity of shallow reefs. A caveat to our depth-resilience findings is the
+quality of the bathymetry data used to calculate median reef depth. As detailed previously,
+estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution)
+which can be subject to high degrees of uncertainty, both in terms of the estimated depth
+for each pixel as well as their alignment to the established GBRMPA reef outlines.
+Additionally, we do not incorporate light-based decreases in coral growth rates as depth
+increases [@baker1975; @huston1985; @ruiz-diaz2022].
 
@@
 drivers. The aim here, however, was to assess the relative influence of reef characteristics
-on structural resilience under future conditions, rather than provide spatially explicit and
+on reef resilience under future conditions, rather than provide spatially explicit and
 precise predictions of reef outcomes. Using this approach, we suggest that reef depth is an

### 2025-09-20 paper/paper_draft.qmd
Add acknowledgements and contributions sections to paper
Also add required citations for Makie and Julia (as per websites).

@@
 
+All data preparation, modelling and analyses were performed using the Julia programming
+language (The Julia Project; https://julialang.org/; [@bezanson2017]), with visualisations
+created using the Makie ecosystem [@danisch2021].
+
 ### Scenario modelling
@@
 
+# Author Contributions
+
+**Benjamin Grier:** conceptualisation, data curation, formal analysis, investigation,
+methodology, visualization, writing – original draft, writing – review and editing. **Takuya
+Iwanaga:** conceptualisation, data curation, formal analysis, investigation, methodology,
+visualization, writing – original draft, writing – review and editing.
+**\[BG: To be completed.\]**
+
 # Acknowledgements
 
+We acknowledge the contributions of Barbara Robson and Jessica Benthuysen to manuscript
+preparation. This research was funded by the Reef Restoration and Adaptation Program, and
+facilitated by the Australian Institute of Marine Science. We acknowledge thermal projection
+data sourced from HighResCoralStress datasets, model parameterisation data sourced from the
+Ecological Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition
+probability data derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data
+available from the Great Barrier Reef Marine Park Authority.
+
 # Conflict of Interest Statement
 
+The authors declare no conflicts of interest.
+
 # Data Availability Statement
+
+The full reproducible investigation, and links to required data sources, can be found at
+Grier and Iwanaga [-@grier2025].
 

### 2025-09-24 paper/paper_draft.qmd
add line to link to metrics table
Incoporate references based on connectivity model comparison study

@@
 depth, and connectivity, that support favourable outcomes in reef recovery and resilience.
+Metrics used in analyses can be found in @stbl-metrics.
 
@@
 combination with more influential factors such as depth. Comprehensive comparisons and
-validation of multiple connectivity model outputs would improve certainty and allow for the
-targetting of reefs by combining abiotic factors such as depth with connectivity.
-
-Our findings on the importance of connectivity may differ from literature due to the highly
-uncertain nature of larval connectivity modelling [@vogt-vincent2023], the way larval flows
-and juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early
-bleaching events decreasing the breeding capacity of strongly connected reefs. Analysing
-daily connectivity data Vogt-Vincent et al. [-@vogt-vincent2023] suggest that time-mean
-connectivity may not be suitable for capturing the seasonal - ecological time scale
-connectivity between locations due to high daily variability in connectivity data. This is
-supported by the connectivity data used in our investigation, which have large relative
-standard deviations for connectivity between reefs over the 24 days used
-(@sfig-connectivity-rsd). Using alternative summarisation methods that capture
-ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
+validation of multiple connectivity models, as well as use of a model ensemble, would
+improve certainty and allow for the targetting of reefs by combining abiotic factors such as
+depth with connectivity.
+
+Our findings on the importance of connectivity likely differ from literature due to the
+highly uncertain nature of larval connectivity modelling [@choukroun2025;
+@vogt-vincent2023], the way larval flows and juvenile recruitment are implemented in ADRIA -
+CoralBlox, and the magnitude of early bleaching events decreasing the breeding capacity of
+strongly connected reefs. Analysing daily connectivity data Vogt-Vincent et al.
+[-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for capturing
+the seasonal - ecological time scale connectivity between locations due to high daily
+variability in connectivity data. This is supported by the connectivity data used in our
+investigation, which have large relative standard deviations for connectivity between reefs
+over the 24 days used (@sfig-connectivity-rsd). Using alternative summarisation methods that
+capture ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
 connectivity [@vogt-vincent2023], future investigations may find increased importance of
 both depth and reef connectivity for resilience, in line with other investigations
-[@hock2017; @torres2024]. Further improvements and research in connectivity modelling are
+[@hock2017; @torres2024]. Choukroun et al [-@choukroun2025] performed a comparison of three
+GBR-scale connectivity models, including GBR1, and suggest the use of a model ensemble
+approach to estimate connectivity metrics due to the high sensitivity of connectivity to
+model specification. Further improvements and research in connectivity modelling are
 necessary when incorporating connectivity as a supplementary factor in reef resilience and
@@
 sample sizes for baseline connectivity data as future computation improvements are made,
-along with GBR scale validation efforts, will improve confidence in connectivity data for
-ecological modelling and management applications. The DHW data used in this investigation
-have not been bias corrected for the Great Barrier Reef region and are part of a wider
-Australian dataset [@dixon2022] developed using statistical downscaling. Additionally, Lachs
-et al. [@lachs2021] suggest the utility of DHW levels for prediction of coral bleaching can
-be improved by reducing the threshold for HotSpot Anomaly values from MMM +1 to MMM and
-reducing the accumulation window from 12 weeks to 8 weeks. We investigate a range of future
-climate responses, thermal projections and ecological parameterisations of ADRIA - CoralBlox
-to account for many possible futures, and our results suggest the factors that influence
-reef resilience are consistent across these scenarios.
+along with the derivation of connectivity from an ensemble of biophysical models, will
+improve confidence in connectivity data for ecological modelling and management applications
+[@choukroun2025]. The DHW data used in this investigation have not been bias corrected for
+the Great Barrier Reef region and are part of a wider Australian dataset [@dixon2022]
+developed using statistical downscaling. Additionally, Lachs et al. [@lachs2021] suggest the
+utility of DHW levels for prediction of coral bleaching can be improved by reducing the
+threshold for HotSpot Anomaly values from MMM +1 to MMM and reducing the accumulation window
+from 12 weeks to 8 weeks. We investigate a range of future climate responses, thermal
+projections and ecological parameterisations of ADRIA - CoralBlox to account for many
+possible futures, and our results suggest the factors that influence reef resilience are
+consistent across these scenarios.
 
@@
 Iwanaga:** conceptualisation, data curation, formal analysis, investigation, methodology,
-visualization, writing – original draft, writing – review and editing.
-**\[BG: To be completed.\]**
+visualization, writing – original draft, writing – review and editing. **\[BG: To be
+completed.\]**
 

### 2025-09-25 paper/paper_draft.qmd
Remove use of "category"
@eco-ben , you seem to prefer "cluster" over "category" so to avoid any confusion I have tried to standardize to "cover cluster" when talking about "High/Med/Low" time series clusters.

@@
 Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a
-reef being classified to one of the three clusters (Panel B). Partial Dependence Plots for
-bioregions were excluded as they were found to be uninformative. PDPs indicate the
-probability of a reef from the test dataset being clustered into each category depending on
-the predictor value on the x axis, when adjusted for values of other predictors. Green,
-orange and blue lines indicate cluster assignment probability for Low, Medium and High
-clusters respectively. Transparent grey points above probability lines represent the
-predictor values present in the test dataset, providing a rough indication of predictor
-value distribution across
+reef being classified to one of the three cover clusters (Panel B). Partial Dependence Plots
+for bioregions were excluded as they were found to be uninformative. PDPs indicate the
+probability of a reef from the test dataset being clustered into each cover cluster
+depending on the predictor value on the x axis, when adjusted for values of other
+predictors. Green, orange and blue lines indicate cluster assignment probability for Low,
+Medium and High clusters respectively. Transparent grey points above probability lines
+represent the predictor values present in the test dataset, providing a rough indication of
+predictor value distribution across
 reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center"
@@
 that reefs with greater outgoing connectivity and lower incoming connectivity levels have
-higher probability of being clustered into the Low cluster category compared to other reefs.
+higher probability of being clustered into the Low cover cluster compared to other reefs.
 Additionally, two-way analyses revealed little interaction between depth and incoming and
@@
 ![Partial dependence plot indicating the probability of cluster assignment along interacting
-values of median reef depth (metres) and Log10 weighted incoming connectivity. Colour
+values of median reef depth (metres) and log10-weighted incoming connectivity. Colour
 indicates the probability of assignment to each cluster, with lighter colours indicating
@@
 cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability
-for the High cluster category. Probability values for each cluster are generated by the
-random forest classifier using each combination of depth and incoming connectivity values
-along the axes at 50 grid points. The actual distributions of depth and incoming
-connectivity values for reefs are displayed in panels D and E
+for the High cover cluster. Probability values for each cluster are generated by the random
+forest classifier using each combination of depth and incoming connectivity values along the
+axes at 50 grid points. The actual distributions of depth and incoming connectivity values
+for reefs are displayed in panels D and E
 respectively.](../figs/ts_cluster_rf_twoway_depth_incomingconn_pdp.png){#fig-ts-cluster-pdp-twoway-incoming
@@
 ![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
-(y-axis) and reef median depth (left panel) and reef Log10 weighted incoming connectivity
+(y-axis) and reef median depth (left panel) and reef log10 weighted incoming connectivity
 values (right panel). Point colour represents the threshold assessment values used to assess
@@
 ACCESS-ESM1-5 (@sfig-mean-dhw-map), however similar spatial patterns were observed across
-GCMs for reefs clustered into the high cover cluster category (@sfig-gcm-cluster-map). We do
-not interpret these spatial findings as accurate predictions of future resilience due to
-high uncertainty in input data, particularly depth and connectivity. While similar findings
-have been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific
-[@bridge2014] regions, depth refugia analyses have often focussed on the potential of
-mesophotic reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015;
-@semmler2017]. In contrast, Venegas et al. [-@venegas2019] found no association between
-depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
+GCMs for reefs clustered into the high cover cluster (@sfig-gcm-cluster-map). We do not
+interpret these spatial findings as accurate predictions of future resilience due to high
+uncertainty in input data, particularly depth and connectivity. While similar findings have
+been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014]
+regions, depth refugia analyses have often focussed on the potential of mesophotic reefs (\>
+30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast,
+Venegas et al. [-@venegas2019] found no association between depth and the alleviation of
+heat stress across a range of shallow reefs in the Pacific.
 
@@
 ![Partial dependence plot indicating the probability of cluster assignment along interacting
-values of median reef depth (metres) and Log10 weighted outgoing connectivity. Colour
+values of median reef depth (meters) and log10 weighted outgoing connectivity. Colour
 indicates the probability of assignment to each cluster, with lighter colours indicating
@@
 cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability
-for the High cluster category. Probability values for each cluster are generated by the
-random forest classifier using each combination of depth and weighted outgoing connectivity
-values along the axes at 50 grid points. The actual distributions of depth and outgoing
+for the High cover cluster. Probability values for each cluster are generated by the random
+forest classifier using each combination of depth and weighted outgoing connectivity values
+along the axes at 50 grid points. The actual distributions of depth and outgoing
 connectivity values for reefs are displayed in panels D and E
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by outgoing connection strength (Log10). Colour-coded
+considered reefs (points), coloured by outgoing connection strength (log10). Colour-coded
 areas outline GBR marine park management regions, where orange represents the Far Northern
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by source-to-sink connectivity ratio (Log10).
+considered reefs (points), coloured by source-to-sink connectivity ratio (log10).
 Colour-coded areas outline GBR marine park management regions, where orange represents the
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by larval retention probability (Log10). Colour-coded
+considered reefs (points), coloured by larval retention probability (log10). Colour-coded
 areas outline GBR marine park management regions, where orange represents the Far Northern
@@
 ![Bar plot indicating the Spearman's rank correlation values for the number of years above
-carbonate budget threshold and, median reef depth and Log10 weighted incoming connectivity
+carbonate budget threshold and, median reef depth and log10 weighted incoming connectivity
 values. Depth correlation values are displayed in the left plot, while connectivity
@@
 
-![Scatter plot indicating reef median depth (metres) and Log10 weighted incoming
+![Scatter plot indicating reef median depth (metres) and log10 weighted incoming
 connectivity for each reef. Point colours represent the median number of years each reef

### 2025-09-25 paper/paper_draft.qmd
Reorder sections
Scenario modelling section ends on "clustered based on temporal behaviour" and then jumps to connectivity modelling, then jumps back to time series clustering.

Reordered for a more logical flow.

@@
 language (The Julia Project; https://julialang.org/; [@bezanson2017]), with visualisations
-created using the Makie ecosystem [@danisch2021].
-
-### Scenario modelling
-
-Two separate systems were employed to explore scenarios: ADRIA (the Adaptive Dynamic Reef
-Intervention Algorithms platform) and CoralBlox. ADRIA is a multi-criteria decision support
-platform designed for the assessment and analysis of coral reef intervention strategies
-under uncertainty [@iwanaga2023]. The ADRIA platform provides functionality for scenario
-generation and analysis as well as providing the technical infrastructure to couple
-environmental and ecosystem representations. CoralBlox is a computationally efficient coral
-population model. It simulates functional/morphological groups of corals over their life
-cycles, competing for available space over time [@ribeirodealmeida2024]. The coupled
-framework is referred to as ADRIA-CoralBlox.
-
-The coral demographic representation and associated model implementation are further
-detailed in the supplementary material. Of important note is that the representation of
-bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient
-to incorporate the amelioration effect that depth may have, following Baird et al.,
-[@baird2018]. This depth-scaling reduces the proportion of coral colonies impacted by high
-heat stress as depth increases. The impacts of tropical cyclones, wave activity, Crown of
-Thorns Starfish or coral disease were not included in this investigation, in order to focus
-on assessing reef resilience under possible future warming scenarios.
-
-ADRIA-CoralBlox was run for 4096 scenarios for each GCM (20,480 total model runs). Here, a
-scenario represents a unique combination of assumed environmental (namely one of the five
-DHW trajectories) and ecological factors including coral growth and mortality rates, and
-coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol' sampling
-method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a randomised Quasi Monte
-Carlo approach which balances scenario exploration with improved convergence properties
-compared to pseudo-random sampling. A detailed comparative analysis of sampling methods can
-be found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
-cover time series for each model run were scaled by the total area of each reef to represent
-cover as a percentage of the total estimated reef area. The scenario-median time series for
-each reef was used for further analyses. These time series of coral cover were then
-clustered based on their temporal behaviour.
+created using the Makie plotting ecosystem [@danisch2021].
 
@@
 
+### Scenario modelling
+
+Two separate systems were employed to explore scenarios: ADRIA (the Adaptive Dynamic Reef
+Intervention Algorithms platform) and CoralBlox. ADRIA is a multi-criteria decision support
+platform designed for the assessment and analysis of coral reef intervention strategies
+under uncertainty [@iwanaga2023]. The ADRIA platform provides functionality for scenario
+generation and analysis as well as providing the technical infrastructure to couple
+environmental and ecosystem representations. CoralBlox is a computationally efficient coral
+population model. It simulates functional/morphological groups of corals over their life
+cycles, competing for available space over time [@ribeirodealmeida2024]. The coupled
+framework is referred to as ADRIA-CoralBlox.
+
+The coral demographic representation and associated model implementation are further
+detailed in the supplementary material. Of important note is that the representation of
+bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient
+to incorporate the amelioration effect that depth may have, following Baird et al.,
+[@baird2018]. This depth-scaling reduces the proportion of coral colonies impacted by high
+heat stress as depth increases. The impacts of tropical cyclones, wave activity, Crown of
+Thorns Starfish or coral disease were not included in this investigation, in order to focus
+on assessing reef resilience under possible future warming scenarios.
+
+ADRIA-CoralBlox was run for 4096 scenarios for each GCM (20,480 total model runs). Here, a
+scenario represents a unique combination of assumed environmental (namely one of the five
+DHW trajectories) and ecological factors including coral growth and mortality rates, and
+coral thermal tolerances. Scenarios were generated using the low-discrepancy Sobol' sampling
+method [@sobol1967; @sobol1993] with Owen Scrambling [@owen1995], a randomised Quasi Monte
+Carlo approach which balances scenario exploration with improved convergence properties
+compared to pseudo-random sampling. A detailed comparative analysis of sampling methods can
+be found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
+cover time series for each model run were scaled by the total area of each reef to represent
+cover as a percentage of the total estimated reef area. The scenario-median time series for
+each reef was used for further analyses. These time series of coral cover were then
+clustered based on their temporal behaviour.
+
 ### Time series clustering

### 2025-09-25 paper/paper_draft.qmd
Minor tweaks to wording

@@
 This is particularly true for coral reefs, which are vulnerable to increasing magnitude and
-variation in environmental stressors such as ocean temperature, acidification and nutrient
-loading [@foster2021; @gattuso2014]. Mass bleaching and mortality events driven by climate
-change can cause reef-building coral population declines [@hughes2017; @hughes2018;
-@bozec2025], possibly leading to long-term and large-scale coral-macroalgae regime shifts
-[@arif2022; @wild2011]. Climate impacts on coral reefs are decreasing the ability of coral
-reefs to provide ecological functions such as benthic habitat and nutrient cycling
-[@forster2021; @williams2019] as well as ecosystem services such as food, protection,
-tourism and Indigenous cultural value [@eddy2021; @stoeckl2021].
+variation in environmental stressors such as ocean temperature [@foster2021; @gattuso2014].
+Mass bleaching and associated mortality events driven by climate change can cause
+reef-building coral population declines [@hughes2017; @hughes2018; @bozec2025], possibly
+leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
+Climate impacts on coral reefs are decreasing the ability of coral reefs to provide
+ecological functions such as benthic habitat and nutrient cycling [@forster2021;
+@williams2019] as well as ecosystem services such as food, protection, tourism and
+Indigenous cultural value [@eddy2021; @stoeckl2021].
 
@@
 reef ecosystem resilience - the capacity to maintain coral populations and avoid ecosystem
-regime shifts - depends on three interconnected mechanisms. First, the ability of individual
-corals to survive thermal stress. Second, the connectivity networks that enable
-recolonisation after disturbances [@hock2017; @mumby2008; @torres2024]. Third, the
-maintenance, and accretion, of the carbonate framework that provides reef structure
+regime shifts - is conceptualised to depend on three interconnected mechanisms. First, the
+ability of individual corals to survive thermal stress. Second, the connectivity networks
+that enable recolonisation after disturbances [@hock2017; @mumby2008; @torres2024]. Third,
+the maintenance, and accretion, of the carbonate framework that provides reef structure
 [@perry2012]. We aim to assess how these mechanisms interact under projected climate
@@
 Partial Dependence Analysis was conducted to understand the relationship between features
-and bioregion-scale time series cluster predictions using a trained Random Forest (RF)
-classifier [@friedman2001]. The analysis utilised the reef characteristics of interest as
-the predictors, including the median reef depth, mean DHW for the given GCM, log10-weighted
-incoming connectivity, log10-weighted outgoing connectivity, and log10-outgoing-to-incoming
-connectivity ratio. The full dataset consisted of the time series cluster assignment of each
-of the 2197 reefs under the five GCMs explored, for a total of 10,985 samples. The dataset
-\*\*\[\] was randomly split into training (60%) and testing (40%) subsets to ensure model
-generalisability. The RF classifier achieved 80% accuracy on the training set and 59% on the
-test set.
+and bioregion-scale time series cluster predictions using a Random Forest (RF) classifier
+[@friedman2001]. The analysis utilised the reef characteristics of interest as the
+predictors, including the estimated median reef depth, mean DHW for the given GCM,
+log10-weighted incoming connectivity, log10-weighted outgoing connectivity, and
+log10-outgoing-to-incoming connectivity ratio. The full dataset consisted of the time series
+cluster assignment of each of the 2197 reefs under the five GCMs explored, for a total of
+10,985 samples. The dataset was randomly split into training (60%) and testing (40%) subsets
+to train and assess classification performance. The RF classifier achieved 80% accuracy on
+the training set and 60% on the test set.
 
@@
 Partial dependence analysis was performed by applying the trained model to the test dataset.
-Values for individual predictors were systematically (one-at-a-time) varied across a grid of
+Values for individual predictors were systematically varied (one-at-a-time) across a grid of
 50 equally spaced points spanning the predictor's range, while all other features were left
@@
 probability was also assessed but was found not to substantially influence the
-interpretation of results (and so, are not shown here). The process isolates the marginal
+interpretation of results (and so are not shown here). The process isolates the marginal
 effect of each predictor by averaging over the natural distribution of all other

### 2025-09-25 paper/paper_draft.qmd
Standardize Log-10 to log10
"Log-10" seems strange, I can't find an example where this is the usual notation, particularly with the capitalisation.

log10 is common as it is the "lazy" way of writing log_{10}

@@
 The relationships between the number of years above $\theta_{0}$ and characteristics such as
-median reef depth and Log-10 total connectivity strength were then assessed with Spearman's
+median reef depth and log10 total connectivity strength were then assessed with Spearman's
 rank correlation. Spearman's correlation coefficient was adopted as reef depth and
@@
 Across bioregions there were no consistent patterns between reef clusters in mean DHW values
-(@sfig-access-esm1-5-bioregion-dhwmean), Log-10 weighted incoming connectivity
-(@sfig-access-esm1-5-bioregion-weightedincoming), Log-10 outgoing connection strength
-(@sfig-access-esm1-5-bioregion-outgoingconn), Log-10 source-to-sink connectivity ratio
-(@sfig-access-esm1-5-bioregion-logsosi) and Log-10 larval retention probability
+(@sfig-access-esm1-5-bioregion-dhwmean), log10 weighted incoming connectivity
+(@sfig-access-esm1-5-bioregion-weightedincoming), log10 outgoing connection strength
+(@sfig-access-esm1-5-bioregion-outgoingconn), log10 source-to-sink connectivity ratio
+(@sfig-access-esm1-5-bioregion-logsosi) and log10 larval retention probability
 (@sfig-access-esm1-5-bioregion-selfconn). Across six of the 29 bioregions reefs in the high
-cover cluster have lower Log-10 carrying capacity values than reefs in other clusters
+cover cluster have lower log10 carrying capacity values than reefs in other clusters
 (@sfig-access-esm1-5-bioregion-carrying-capacity).
@@
 threshold becoming increasingly right-skewed (@fig-access-esm1-5-depth-conn-carbonate). In
-contrast, weighted incoming connectivity strength (Log-10 scale) was found to have no
+contrast, weighted incoming connectivity strength (log10 scale) was found to have no
 correlation with the number of years a reef maintains cover above the required thresholds

### 2025-09-25 paper/paper_draft.qmd
Remove errant new line

@@
 GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs
-across clusters (Low, Medium and High).
-
-Of the GCMs explored, NorESM2-MM had the lowest Equilibrium Climate Sensitivity (2.5°C) and
-reefs exhibit continuing recovery and decline dynamics up to 2075 under this hypothetical
-climate future. Unsurprisingly, recovery phases were predominantly seen in the reefs in the
-High cluster, with Medium and Low exhibiting lesser probability of such periods of recovery.
-Generally, recovery and increases in coral cover were visible in simulated results up to
-2045. Under NorESM2-MM, the Far Northern Management area were found to have the most similar
-temporal behaviour between Low and High clusters compared to other Management areas
-(@stbl-cluster-cid) due to the low degree of coral cover overall
-(@fig-gcm-cover-trajectories).
+across clusters (Low, Medium and High). Of the GCMs explored, NorESM2-MM had the lowest
+Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline
+dynamics up to 2075 under this hypothetical climate future. Unsurprisingly, recovery phases
+were predominantly seen in the reefs in the High cover cluster, with Medium and Low
+exhibiting lesser probability of such periods of recovery. Generally, recovery and increases
+in coral cover were visible in simulated results up to 2045. Under NorESM2-MM, the Far
+Northern Management area were found to have the most similar temporal behaviour between Low
+and High clusters compared to other Management areas (@stbl-cluster-cid) due to the low
+degree of coral cover overall (@fig-gcm-cover-trajectories).
 

### 2025-09-25 paper/paper_draft.qmd
Reduce unnecessary repetition

@@
 (rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. The
-time series are categorised as "Low" (green), "Medium" (in orange), and "High" median cover
-(in blue). Solid lines represent the cluster median time series and bands represent the 95th
-percentile confidence
+time series were clustered into "Low" (green), "Medium" (orange), and "High" (blue) clusters
+indicating their relative median coral cover. Solid lines represent the cluster median time
+series and bands represent the 95th percentile confidence
 intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
@@
 
-![Median depth for reefs within each bioregion, separated into clusters assigned by time
-series clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative
-cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters
-with intermediate median area-relative cover between 2030 and 2060 within each bioregion.
-‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030
-and 2060 within each bioregion. Solid lines represent the median depth for each cluster
-across reefs and bands represent the distribution of depth values within each cluster.
-Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
+![Median depth for reefs within each bioregion under ACCESS-ESM1-5, separated into clusters
+assigned by time series clustering. Time series were clustered based on their behaviour
+between 2030 and 2060. Time series with comparatively low median area-relative cover is
+indicated in green, intermediate cover in orange, and high in blue. Solid lines represent
+the median depth for each cluster across reefs and bands represent the distribution of depth
+values within each
+cluster.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
 fig-align="center" width="14.82cm"}

### 2025-09-25 paper/paper_draft.qmd
Grammar, Log-10 to log10

@@
 
-Across bioregions there were no consistent patterns between reef clusters in mean DHW values
-(@sfig-access-esm1-5-bioregion-dhwmean), log10 weighted incoming connectivity
+Across bioregions, there were no consistent patterns between reef clusters in mean DHW
+values (@sfig-access-esm1-5-bioregion-dhwmean), log10-weighted incoming connectivity
 (@sfig-access-esm1-5-bioregion-weightedincoming), log10 outgoing connection strength

### 2025-09-25 paper/paper_draft.qmd
Standardize to "cover cluster"

@@
 A Partial Dependence Analysis was conducted using a Random Forest classifier to identify
-reef characteristics that influence its temporal behaviour, and thus its cluster assignment
-into Low, Medium, or High. Reef median depth, carrying capacity and mean time series DHW
-level have the highest feature importance scores, accounting for 29%, 15% and 15% predictive
-importance respectively (@fig-ts-cluster-pdp; Panel A). Reef weighted incoming connectivity,
-outgoing connectivity strength, source-to-sink connectivity ratio and larval retention
-probability account for \~12%, 11%, 10% and 8% respectively.
+reef characteristics that influence its temporal behaviour, and thus its assignment into
+Low, Medium, or High cover clusters. Reef median depth, carrying capacity and mean time
+series DHW level have the highest feature importance scores, accounting for 29%, 15% and 15%
+predictive importance respectively (@fig-ts-cluster-pdp; Panel A). Area weighted incoming
+connectivity, outgoing connectivity strength, source-to-sink connectivity ratio and larval
+retention probability account for \~12%, 11%, 10% and 8% respectively.
 

### 2025-09-25 paper/paper_draft.qmd
Note for @eco-ben

@@
 that reefs with greater outgoing connectivity and lower incoming connectivity levels have
-higher probability of being clustered into the Low cover cluster compared to other reefs.
+higher probability of being clustered into the Low cover cluster compared to other reefs
+**\[Ben, I disagree with this assessment and the next sentence seems to contradict it?\]**.
 Additionally, two-way analyses revealed little interaction between depth and incoming and

### 2025-09-25 paper/paper_draft.qmd
Reduce repetition in caption
Also removed unnecessary description of implementation

@@
 
-![Partial dependence plot indicating the probability of cluster assignment along interacting
-values of median reef depth (metres) and log10-weighted incoming connectivity. Colour
-indicates the probability of assignment to each cluster, with lighter colours indicating
-higher probability of assignment. Panel A shows the probability of assignment for the Low
-cover cluster, Panel B shows Medium cover cluster and Panel C shows assignment probability
-for the High cover cluster. Probability values for each cluster are generated by the random
-forest classifier using each combination of depth and incoming connectivity values along the
-axes at 50 grid points. The actual distributions of depth and incoming connectivity values
-for reefs are displayed in panels D and E
-respectively.](../figs/ts_cluster_rf_twoway_depth_incomingconn_pdp.png){#fig-ts-cluster-pdp-twoway-incoming
+![Partial Dependence Plot indicating the estimated probability (via Random Forest
+classification) of cluster assignment along interacting values of median reef depth (meters)
+and log10-weighted incoming connectivity. Colour (ranging from dark purple to yellow)
+indicates the probability of assignment to each cluster, with brighter colour indicating
+higher probability of assignment. Panels A, B, and C illustrates the assignment probability
+for Low, Medium, and High cover clusters respectively. The distribution of reef depth and
+incoming connectivity values are shown in Panels D and
+E.](../figs/ts_cluster_rf_twoway_depth_incomingconn_pdp.png){#fig-ts-cluster-pdp-twoway-incoming
 fig-align="center" width="14.82cm"}

### 2025-09-25 paper/paper_draft.qmd
Tweak wording
And note for @eco-ben !

@@
 and log10-weighted incoming connectivity. Colour (ranging from dark purple to yellow)
-indicates the probability of assignment to each cluster, with brighter colour indicating
+indicates the probability of assignment to each cluster, with brighter shades indicating
 higher probability of assignment. Panels A, B, and C illustrates the assignment probability
@@
 predictor variables. Beyond this low-end range, the partial dependence becomes near
-constant, indicating that outlier values for these factors are not influential.
-
-Assessing random forest prediction accuracy across bioregions, reveals increasing
-performance as bioregion mean reef depth increases (@sfig-rf-predictor-perf). This
-highlights that unexplained variation in the test dataset (33% of variation) may be
-concentrated in shallow bioregions where the available model predictors do not capture
-differences between clustered reefs.
+constant, indicating that outlier values for these factors are not influential. Assessing
+random forest prediction accuracy across bioregions, reveals increasing performance as
+bioregion mean reef depth increases (@sfig-rf-predictor-perf). This highlights that
+unexplained variation in the test dataset (33% of variation) may be concentrated in shallow
+bioregions where the available model predictors do not capture differences between clustered
+reefs.
 
@@
 
-![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
-(y-axis) and reef median depth (left panel) and reef log10 weighted incoming connectivity
-values (right panel). Point colour represents the threshold assessment values used to assess
-positive carbonate budget status ($\theta_0$). Deeper reefs are better able to maintain
-cover above the indicative carbonate budget threshold, while there is no considerable
-relationship between weighted incoming connectivity and carbonate budget maintenance.
-Displays results from median time series using
-ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
+![Number of years reef coral cover exceeds the assumed carbonate budget threshold in terms
+of coral cover ($\theta_0$) between 2025 to 2075 (y-axis) under ACCESS-ESM1-5. Left panel
+shows relationship between reef median depth, while the right panel shows the same for
+log10-weighted incoming connectivity values. Point colour (purple to yellow) represents
+($\theta_0$), with brighter shades indicating a higher $\theta_0$. Deeper reefs have
+increased number of years above the considered range of $\theta_0$, while no relationship
+between weighted incoming connectivity and carbonate budget maintenance was found. **\[Ben,
+no x-axis label for Right
+Panel?\]**](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
 fig-align="center" width="14.82cm"}

### 2025-09-25 paper/paper_draft.qmd
Clarify text

@@
 coral driven CaCO~3~ production and accumulation into the future for longer. Our results
-suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m), depth
-contributes greatly to reef resilience and the ability of reefs to maintain positive
-carbonate budgets under future conditions. Spatially our results indicate that regions of
-positive carbonate budget maintenance, under ACCESS-ESM1-5, and high depth levels were
-concentrated in the Far Northern, offshore Townsville/Whitsunday, and Mackay/Capricorn
-management areas (@sfig-carb-budget-map; @sfig-depth-map). Resilient reefs in the Far
-Northern management area were exposed to lower mean DHW levels than other reefs under
-ACCESS-ESM1-5 (@sfig-mean-dhw-map), however similar spatial patterns were observed across
-GCMs for reefs clustered into the high cover cluster (@sfig-gcm-cluster-map). We do not
-interpret these spatial findings as accurate predictions of future resilience due to high
-uncertainty in input data, particularly depth and connectivity. While similar findings have
-been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014]
-regions, depth refugia analyses have often focussed on the potential of mesophotic reefs (\>
-30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast,
-Venegas et al. [-@venegas2019] found no association between depth and the alleviation of
-heat stress across a range of shallow reefs in the Pacific.
+suggest that for non-mesophotic reef ecosystems (i.e., \< 30m), depth contributes greatly to
+reef resilience and the ability of reefs to maintain positive carbonate budgets under future
+conditions. Spatially our results indicate that regions of positive carbonate budget
+maintenance, under ACCESS-ESM1-5, and high depth levels were concentrated in the Far
+Northern, offshore Townsville/Whitsunday, and Mackay/Capricorn management areas
+(@sfig-carb-budget-map; @sfig-depth-map). Resilient reefs in the Far Northern management
+area were exposed to lower mean DHW levels than other reefs under ACCESS-ESM1-5
+(@sfig-mean-dhw-map), however similar spatial patterns were observed across GCMs for reefs
+clustered into the high cover cluster (@sfig-gcm-cluster-map). We do not interpret these
+spatial findings as accurate predictions of future resilience due to high uncertainty in
+input data, particularly depth and connectivity. While similar findings have been
+demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014] regions,
+depth refugia analyses have often focused on the potential of mesophotic reefs (\> 30m deep)
+as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et
+al. [-@venegas2019] found no association between depth and the alleviation of heat stress
+across a range of shallow reefs in the Pacific.
 

### 2025-09-25 paper/paper_draft.qmd
Shorten sentence
End on concrete management advice that summarises findings

@@
 possible future conditions. Reefs with a median depth of 10m or greater, with high incoming
-connectivity, are the most likely to be assigned to a high cover time series cluster. As an
-individual feature, incoming connectivity alone does not correlate with maintenance of
-positive carbonate budgets. These findings highlight the importance of depth and incoming
+connectivity, are the most likely to be assigned to a high cover time series cluster. By
+itself, incoming connectivity alone does not correlate with maintenance of positive
+carbonate budgets. These findings highlight the importance of depth and incoming
 connectivity as coupled selection features when assessing potential reef resilience under
@@
 Our findings support the hypothesis that reefs at greater depths will exhibit
-characteristics of refugia and more prolonged resilience under climate change compared to
-shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest that rubble
-instability is inversely correlated with reef depth, possibly limiting juvenile coral
-recruitment capacity of shallow reefs. A caveat to our depth-resilience findings is the
-quality of the bathymetry data used to calculate median reef depth. As detailed previously,
-estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution)
-which can be subject to high degrees of uncertainty, both in terms of the estimated depth
-for each pixel as well as their alignment to the established GBRMPA reef outlines.
-Additionally, we do not incorporate light-based decreases in coral growth rates as depth
-increases [@baker1975; @huston1985; @ruiz-diaz2022].
-
-Current reef restoration and intervention efforts on the GBR, such as deployment of coral
-seeding, coral fragment devices and Crown of Thorns Starfish control, target reefs with
-sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
-no explicit justifications for this depth range, intervention depth is likely constrained by
-snorkelling and diving deployment and monitoring logistical accessibility, visual
-identification of sites from the surface, in combination with tourism return value. Our
-results suggest that of the assessed reefs occurring within the 1-10m depth range (1551
+characteristics of refugia and prolonged resilience (in terms of coral cover) under climate
+change compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024]
+suggest that rubble instability is inversely correlated with reef depth, possibly limiting
+juvenile coral recruitment capacity of shallow reefs. A caveat to our depth-resilience
+findings is the quality of the bathymetry data used to calculate median reef depth. As
+detailed previously, estimates of median reef depth are derived from satellite imagery (at
+$10m^2$ resolution) which can be subject to high degrees of uncertainty, both in terms of
+the estimated depth for each pixel as well as their alignment to the established GBRMPA reef
+outlines. Additionally, we do not incorporate light-based decreases in coral growth rates as
+depth increases [@baker1975; @huston1985; @ruiz-diaz2022].
+
+Current reef restoration and intervention efforts across the GBR, such as deployment of
+coral seeding, coral fragment devices and Crown of Thorns Starfish control, target reefs
+with sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there
+are no explicit justifications for this depth range, intervention depth is likely
+constrained by snorkelling and diving deployment and monitoring logistical accessibility,
+visual identification of sites from the surface, in combination with tourism return value.
+Our results suggest that of the assessed reefs occurring within the 1-10m depth range (1551
 reefs), 59% (920) of reefs are consistently clustered into the Low and Medium cover clusters
-across the GCMs (at the GBRMPA management region scale), with many unable to maintain
-positive carbonate budgets under future conditions. Partial dependence analysis revealed a
-range of depths from 10-15m where the probability of a reef being clustered into the High
-cover cluster increased substantially. Additionally, two-way partial dependence analysis
-revealed that high incoming connectivity is important for High cluster assignment for reefs
-at depths of \>10m. Considering this 10-15m depth range when assessing possible intervention
-sites may reduce the exposure of planted and seeded corals to high thermal stress, while
-still maintaining effective logistical access to sites. Managers are also likely to consider
-the potential for positive flow on effects due to outgoing connectivity when selecting
-intervention sites [@hock2017]. Transient, and difficult to measure, properties such as reef
-connectivity are likely to increase uncertainty in intervention planning to a greater degree
-than environmental characteristics such as reef depth. Overall, reef intervention planning
-is a complex and challenging decision-making process [@anthony2020], and our results suggest
-that intervention site depth may be an important factor to additionally consider when
-assessing the long-term resilience of sites.
+across the GCMs (at the GBRMPA management region scale), with many found to be unable to
+maintain positive carbonate budgets under projected conditions. Partial dependence analysis
+revealed a range of depths from 10-15m where the probability of a reef being clustered into
+the High cover cluster increased substantially. Additionally, two-way partial dependence
+analysis revealed that high incoming connectivity is important for High cluster assignment
+for reefs at depths of \>10m. Considering this 10-15m depth range when assessing possible
+intervention sites may reduce the exposure of planted and seeded corals to high thermal
+stress, while still maintaining effective logistical access to sites.
 
@@
 validation of multiple connectivity models, as well as use of a model ensemble, would
-improve certainty and allow for the targetting of reefs by combining abiotic factors such as
+improve certainty and allow for the targeting of reefs by combining abiotic factors such as
 depth with connectivity.
@@
 across scenarios.
+
+Given the above, reef managers may consider the potential for positive flow-on effects due
+to outgoing connectivity when selecting intervention sites. The necessary connectivity data,
+however, must first be available to provide a sufficient degree of confidence to support
+such site selection decisions (compare the ongoing discussion in [-@mumby2018] and
+[-@bode2018]). Given connectivity is a transient, and much more difficult, property to
+measure that is subject to comparatively higher sources of uncertainty, depth may be a more
+reliable indicator of long-term resilience, particularly where no further information is
+available.
 

### 2025-09-25 src/plotting_functions.jl
Fix incorrect axis label: carbonate budget scatters

@@ -1471,7 +1471,7 @@ function carbonate_budget_biscatter(
     )
     ax2 = Axis(
         gr1[1,2],
-        ylabel=conn_label
+        xlabel=conn_label
     )
     scat2 = scatter!(
         ax2, 

### 2025-09-25 paper/paper_draft.qmd
Resolved comment about axis labels

@@
 
-![Number of years reef coral cover exceeds the assumed carbonate budget threshold in terms
+\![Number of years reef coral cover exceeds the assumed carbonate budget threshold in terms
 of coral cover ($\theta_0$) between 2025 to 2075 (y-axis) under ACCESS-ESM1-5. Left panel
@@
 increased number of years above the considered range of $\theta_0$, while no relationship
-between weighted incoming connectivity and carbonate budget maintenance was found. **\[Ben,
-no x-axis label for Right
-Panel?\]**](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
+between weighted incoming connectivity and carbonate budget maintenance was found.
+(../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
 fig-align="center" width="14.82cm"}

### 2025-09-25 paper/paper_draft.qmd
Resolve comment on PDP results
@ConnectedSystems I agree with your comment. I must not have updated that sentence since last rf figure revision. I've resolved it now.

@@
 
-Analyses for source-to-sink ratio and incoming and outgoing connectivity metrics suggest
-that reefs with greater outgoing connectivity and lower incoming connectivity levels have
-higher probability of being clustered into the Low cover cluster compared to other reefs
-**\[Ben, I disagree with this assessment and the next sentence seems to contradict it?\]**.
-Additionally, two-way analyses revealed little interaction between depth and incoming and
-outgoing connectivity metrics for reef clustering probabilities
-(@fig-ts-cluster-pdp-twoway-incoming; @sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a
-median depth around 15m and high incoming connectivity may benefit slightly, with higher
-probability of High cover cluster assignment compared to 15m - depth reefs with lower
-connectivity.
+First-order partial dependence analysis showed minimal influence of incoming, outgoing and
+source-to-sink ratio connectivity metrics on cluster assignment probabilities. Two-way
+analyses revealed little interaction between depth and incoming and outgoing connectivity
+metrics for reef clustering probabilities (@fig-ts-cluster-pdp-twoway-incoming;
+@sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a median depth around 15m and high
+incoming connectivity may benefit slightly, with higher probability of High cover cluster
+assignment compared to 15m - depth reefs with lower connectivity.
 

### 2025-09-25 paper/paper_draft.qmd
Objective writing style and remove repetition of "exploratory modelling"

@@
 
-We adapted an exploratory scenario modelling approach for this investigation. Specifically,
-we use combinations of model factors to investigate a wide range of potential futures under
-different assumptions of environmental (climatic) and ecological conditions. Exploratory
-modelling approaches have gained favour in recent years to explore the implications of deep
-uncertainty; where there is little or no agreement on the key drivers of a system, the
-extent of the relationship, how best to represent them or their probability distributions
-[@conradt2024; @lempert2013]. Exploratory modelling embraces uncertainty as an inherent
-characteristic of complex environmental systems [@lempert2010; @lempert2013] and is a core
-methodology underpinning the development of robust and adaptive management strategies
-[@haasnoot2013].
+An exploratory scenario modelling approach was adopted for this investigation. The method
+involves exploring a wide range of potential futures under different assumptions of
+environmental (climatic) and ecological conditions. Exploratory modelling approaches have
+gained favour in recent years to explore the implications of deep uncertainty; where there
+is little or no agreement on the key drivers of a system, the extent of the relationship,
+how best to represent them or their probability distributions [@conradt2024; @lempert2013].
+The approach embraces uncertainty as an inherent characteristic of complex environmental
+systems [@lempert2010; @lempert2013] and is a core methodology underpinning the development
+of robust and adaptive management strategies [@haasnoot2013].
 

### 2025-09-25 paper/paper_draft.qmd
Fix typo

@@
 flow. This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where S represents the sum of
-connectivity pobabilities, N represents the number of connections, O denotes outgoing
+connectivity probabilities, N represents the number of connections, O denotes outgoing
 connectivity from the target reef and I denotes incoming connectivity to the target reef. If

### 2025-09-25 paper/paper_draft.qmd
Minor clarification to recent change

@@
 predictors, including the estimated median reef depth, mean DHW for the given GCM,
-log10-weighted incoming connectivity, log10-weighted outgoing connectivity, and
-log10-outgoing-to-incoming connectivity ratio. The full dataset consisted of the time series
+log10-weighted incoming connectivity, outgoing connectivity, and log10-transformed
+outgoing-to-incoming connectivity ratio. The full dataset consisted of the time series
 cluster assignment of each of the 2197 reefs under the five GCMs explored, for a total of

### 2025-09-25 paper/paper_draft.qmd
Add RF performance metrics

@@
 fig-align="center" width="14.82cm"}
+
+## Random Forest Performance
+
+|               |         |                  |          |
+|---------------|---------|------------------|----------|
+|               |         | **Ground Truth** |          |
+| **Predicted** | **Low** | **Medium**       | **High** |
+| **Low**       | 1371    | 682              | 151      |
+| **Medium**    | 247     | 603              | 340      |
+| **High**      | 97      | 302              | 787      |
+
+: Confusion matrix for the Random Forest classifier used to assess partial dependence.
+Diagonals indicate correctly classified time series clusters. Columns are the "true" cluster
+memberships and indicate the samples that were correctly or incorrectly classified as
+Low/Medium/High. For example, the first column shows the number of samples correctly
+classified into the Low cluster, and the number of Low samples incorrectly classified as
+being in either the Medium or High coral cover clusters. There were 4580 samples used for
+testing.
+
+|              |         |            |          |
+|--------------|---------|------------|----------|
+|              | **Low** | **Medium** | **High** |
+| Test samples | 1715    | 1587       | 1278     |
+| Precision    | 0.622   | 0.507      | 0.664    |
+| Recall       | 0.799   | 0.38       | 0.616    |
+| F1           | 0.7     | 0.434      | 0.639    |
+
+: Performance metrics for the Random Forest classifier for each of the time series clusters.

### 2025-09-25 paper/paper_draft.qmd
Adjust formatting

@@
 |                  |         |            |          |
-|--------------|---------|------------|----------|
+|------------------|---------|------------|----------|
 |                  | **Low** | **Medium** | **High** |
-| Test samples | 1715    | 1587       | 1278     |
-| Precision    | 0.622   | 0.507      | 0.664    |
-| Recall       | 0.799   | 0.38       | 0.616    |
-| F1           | 0.7     | 0.434      | 0.639    |
+| **Test samples** | 1715    | 1587       | 1278     |
+| **Precision**    | 0.622   | 0.507      | 0.664    |
+| **Recall**       | 0.799   | 0.38       | 0.616    |
+| **F1**           | 0.7     | 0.434      | 0.639    |
 

### 2025-09-25 paper/paper_draft.qmd
Add Pedro's content to supplementary and reference to recent Botelho et al calibrated model paper

--- 2025-09-25 paper/paper_draft.qmd
@@
 An exploratory scenario modelling approach was adopted for this investigation. The method
-involves exploring a wide range of potential futures under different assumptions of
-environmental (climatic) and ecological conditions. Exploratory modelling approaches have
-gained favour in recent years to explore the implications of deep uncertainty; where there
-is little or no agreement on the key drivers of a system, the extent of the relationship,
-how best to represent them or their probability distributions [@conradt2024; @lempert2013].
-The approach embraces uncertainty as an inherent characteristic of complex environmental
-systems [@lempert2010; @lempert2013] and is a core methodology underpinning the development
-of robust and adaptive management strategies [@haasnoot2013].
+involves exploring a wide range of potential futures and model parameterisations under
+different assumptions of environmental (climatic) and ecological conditions. Exploratory
+modelling approaches have gained favour in recent years to explore the implications of deep
+uncertainty; where there is little or no agreement on the key drivers of a system, the
+extent of the relationship, how best to represent them or their probability distributions
+[@conradt2024; @lempert2013]. The approach embraces uncertainty as an inherent
+characteristic of complex environmental systems [@lempert2010; @lempert2013] in an attempt
+to address limitations of calibrated ecosystem models with a singular set of parameter
+values [@lubianabotelho2025]. Exploratory scenario modelling is a core methodology
+underpinning the development of robust and adaptive management strategies [@haasnoot2013].
 
@@
 
-\![Number of years reef coral cover exceeds the assumed carbonate budget threshold in terms
+![Number of years reef coral cover exceeds the assumed carbonate budget threshold in terms
 of coral cover ($\theta_0$) between 2025 to 2075 (y-axis) under ACCESS-ESM1-5. Left panel
@@
 increased number of years above the considered range of $\theta_0$, while no relationship
-between weighted incoming connectivity and carbonate budget maintenance was found.
-(../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
+between weighted incoming connectivity and carbonate budget maintenance was
+found.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
 fig-align="center" width="14.82cm"}
@@
 one, a formal mechanistic and spatial validation of the model represents an area for future
-refinement and is the focus of a future publication. Indicative results are included in the
-supplementary **\[TI: For Pedro to include! :`D`\].** The consistency of projected patterns
+refinement and is the focus of a future publication. The consistency of projected patterns
 with known coral-climate relationships and reef characteristics provides confidence in the
 model's ability to meaningfully capture ecological signals at the GBR-scale. The mechanistic
-basis of the model, combined with qualitative assessment of model behavior, supports the
-robustness of our findings for understanding broad-scale coral cover responses to climatic
-drivers. The aim here, however, was to assess the relative influence of reef characteristics
-on reef resilience under future conditions, rather than provide spatially explicit and
-precise predictions of reef outcomes. Using this approach, we suggest that reef depth is an
-important factor for reef resilience under thermal stress.
+basis of the model supports the robustness of our findings for understanding broad-scale
+coral cover responses to climatic drivers. The aim here, however, was to assess the relative
+influence of reef characteristics on reef resilience across a range of future conditions and
+parameterisations, rather than provide spatially explicit and precise predictions of reef
+outcomes. Using this approach, we suggest that reef depth is an important factor for reef
+resilience under thermal stress.
 
@@
 
+### Calibration
+
+The growth and mortality rate parameters of ADRIA-CoralBlox were calibrated using hard coral
+cover and benthic composition data from the Long-Term Monitoring Program (LTMP). From all
+the reefs for which there is LTMP data available, 99 were selected for having at least 4
+observations that span more than 10 years. These locations were randomly split into a
+calibration set (with 73 reefs) and a validation set (with 26 reefs), as evenly spatially
+distributed as possible. The error function used in the calibration process is composed of
+three elements [@eq-calibration]. The first is a Mean Absolute Exponential Error ($MAEE$)
+that captures the difference between modeled and observed hard coral cover. The second is a
+Coral Composition Error ($CCE$) that captures the differences in the benthic composition
+between modeled and observed coral cover. The third ($Err~p~$) is an error that emphasizes
+differences between observed and modelled cover at the beginning and end of the series, as
+well as on peaks and troughs:
+
+$$
+err = MAEE_\sigma_  *  w_1_  +  CEE_t_  *  w_c_  +  Err_p_  *  w_p_
+$$ {#eq-calibration}
+
+[@sfig-reef-scale-calibration] shows a comparison between modeled and observed relative
+coral cover for 6 reefs with distinct disturbance patterns. For each one, a Root Mean Square
+Error (RMSE), the MAEE and Spearman’s Rank Correlation Coefficient (SRCC) is also shown.
+[@sfig-man-area-calibration] presents another comparison between observed and modeled hard
+coral cover aggregated by GBRMPA management area.
+
+![Time series comparing modelled and observed relative coral cover for selected validation
+reefs. These reefs were selected to show distinct disturbance patterns and behaviors. reefs
+(a) and (b), with low heat stress and a single disturbance at the beginning, show the
+model’s ability of reproducing the reef’s recovery under low or no disturbance; reefs (c)
+and (d), with moderate to high heat stress and disturbance events in the middle of the
+considered timeframe, show the model’s ability to reproduce disturbances reasonably well but
+some difficulty in representing the post-disturbance recovery ; reefs (e) and (f) illustrate
+the challenge of reproducing the observed behavior in a high disturbance
+scenario.](../figs/reef_scale_calibration.png){#sfig-reef-scale-calibration
+fig-align="center" width="14.82cm"}
+
+![Comparison between observed and modelled coral relative cover aggregated, for each GBRMPA
+management area, for the calibration set (first row) and validation set (second row). For
+each one the aggregated RMSE and MAE are
+presented.](../figs/management_area_calibration.png){#sfig-man-area-calibration
+fig-align="center" width="14.82cm"}
+
 ### Time series clustering

### 2025-09-25 paper/paper_draft.qmd
Update working title, author list and acknowledgements section

@@
 ---
-title: Think deep for reef resilience
+title: Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change
 author:
@@
           state: QLD
-    attributes:
-        corresponding: true
+  - name: Chinenye Ani
+    email: c.ani@aims.gov.au
+    affiliations:
+        - id: AIMS
+          name: Australian Institute of Marine Science
+          address: Cape Cleveland Rd
+          city: Cape Cleveland
+          state: QLD
+  - name: Pedro Ribeiro De Almeida
+    email: p.ribeirodealmeida@aims.gov.au
+    affiliations:
+        - id: AIMS
+          name: Australian Institute of Marine Science
+          address: Cape Cleveland Rd
+          city: Cape Cleveland
+          state: QLD
+  - name: Sam Matthews
+    email: s.matthews@aims.gov.au
+    affiliations:
+        - id: AIMS
+          name: Australian Institute of Marine Science
+          address: Cape Cleveland Rd
+          city: Cape Cleveland
+          state: QLD
 abstract: |
@@
 visualization, writing – original draft, writing – review and editing. **\[BG: To be
-completed.\]**
+completed.\] ...**
 
@@
 probability data derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data
-available from the Great Barrier Reef Marine Park Authority.
+available from the Great Barrier Reef Marine Park Authority. All authors are funded by the
+Reef Restoration and Adaptation Program **\[BG: To be completed.\]**.
 

### 2025-09-25 paper/paper_draft.qmd
Format rf tables for rendering with labels
@ConnectedSystems for some reason the table got removed by my earlier commit. Had to copy it over again.

@@
 Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
-0.70, 0.41 and 0.63 respectively, with precision of 0.77, 0.47 and 0.64 when evaluated with
-the test set (consisting of 4394 samples). Lower performance with the Medium cluster
-reflects the inherent difficulty of classifying transitional states in natural systems. The
-consistent level of accuracy across test and cross-validation demonstrates the generalised
-performance of the RF classifier, while not accurate, was deemed sufficiently informative
-for the purpose of assessing the influence of reef characteristics.
+0.70, 0.43 and 0.64 respectively, with precision of 0.62, 0.51 and 0.66 when evaluated with
+the test set (consisting of 4394 samples) [@stbl-confusion-matrix;
+@stbl-rf-cluster-performance]. Lower performance with the Medium cluster reflects the
+inherent difficulty of classifying transitional states in natural systems. The consistent
+level of accuracy across test and cross-validation demonstrates the generalised performance
+of the RF classifier, while not accurate, was deemed sufficiently informative for the
+purpose of assessing the influence of reef characteristics.
 
@@
 fig-align="center" width="14.82cm"}
+
+#### Random Forest Performance
+
+::: {#stbl-confusion-matrix}
+|               |         | **Ground Truth** |          |
+|---------------|---------|------------------|----------|
+| **Predicted** | **Low** | **Medium**       | **High** |
+| **Low**       | 1371    | 682              | 151      |
+| **Medium**    | 247     | 603              | 340      |
+| **High**      | 97      | 302              | 787      |
+
+Confusion matrix for the Random Forest classifier used to assess partial dependence.
+Diagonals indicate correctly classified time series clusters. Columns are the "true" cluster
+memberships and indicate the samples that were correctly or incorrectly classified as
+Low/Medium/High. For example, the first column shows the number of samples correctly
+classified into the Low cluster, and the number of Low samples incorrectly classified as
+being in either the Medium or High coral cover clusters. There were 4580 samples used for
+testing.
+:::
+
+::: {#stbl-rf-cluster-performance}
+|                  | **Low** | **Medium** | **High** |
+|------------------|---------|------------|----------|
+| **Test samples** | 1715    | 1587       | 1278     |
+| **Precision**    | 0.622   | 0.507      | 0.664    |
+| **Recall**       | 0.799   | 0.38       | 0.616    |
+| **F1**           | 0.7     | 0.434      | 0.639    |
+
+Performance metrics for the Random Forest classifier for each of the time series clusters.
+:::

### 2025-09-25 paper/paper_draft.qmd
Proof reading of paper for checks and reducing word count
- restructured to move DHW calculation methods and qualitative bioregion scale clustering results to supplementary material
- fixed figure captions that have repetition

@@
 
-Climate change is impacting species survival, persistence and ecosystem functions globally.
-This is particularly true for coral reefs, which are vulnerable to increasing magnitude and
-variation in environmental stressors such as ocean temperature [@foster2021; @gattuso2014].
-Mass bleaching and associated mortality events driven by climate change can cause
-reef-building coral population declines [@hughes2017; @hughes2018; @bozec2025], possibly
-leading to long-term and large-scale coral-macroalgae regime shifts [@arif2022; @wild2011].
-Climate impacts on coral reefs are decreasing the ability of coral reefs to provide
-ecological functions such as benthic habitat and nutrient cycling [@forster2021;
-@williams2019] as well as ecosystem services such as food, protection, tourism and
-Indigenous cultural value [@eddy2021; @stoeckl2021].
-
-Understanding the characteristics of reefs that will persist under projected climate
-conditions requires examining reef resilience across multiple scales and processes. Coral
-reef ecosystem resilience - the capacity to maintain coral populations and avoid ecosystem
-regime shifts - is conceptualised to depend on three interconnected mechanisms. First, the
-ability of individual corals to survive thermal stress. Second, the connectivity networks
-that enable recolonisation after disturbances [@hock2017; @mumby2008; @torres2024]. Third,
-the maintenance, and accretion, of the carbonate framework that provides reef structure
-[@perry2012]. We aim to assess how these mechanisms interact under projected climate
-conditions to identify the characteristics of resilient reefs through scenario-based coral
-population modelling for the Great Barrier Reef ecosystem.
+Climate change is impacting species survival, persistence and ecosystem functions on coral
+reefs, which are vulnerable to increasing magnitude and variation in environmental stressors
+such as ocean temperature [@foster2021; @gattuso2014]. Mass bleaching and associated
+mortality events driven by climate change can cause reef-building coral population declines
+[@hughes2017; @hughes2018; @bozec2025], possibly leading to coral-macroalgae regime shifts
+[@arif2022; @wild2011]. Climate impacts on coral reefs are decreasing the ability of coral
+reefs to provide ecological functions such as benthic habitat and nutrient cycling
+[@forster2021; @williams2019] and services such as food, protection, tourism and Indigenous
+cultural value [@eddy2021; @stoeckl2021].
+
+Coral reef ecosystem resilience - the capacity to maintain coral populations and avoid
+ecosystem regime shifts - is conceptualised to depend on three interconnected mechanisms.
+First, the ability of individual corals to survive thermal stress. Second, the connectivity
+networks that enable recolonisation after disturbances [@hock2017; @mumby2008; @torres2024].
+Third, the maintenance, and accretion, of the carbonate framework that provides reef
+structure [@perry2012]. We aim to assess how these mechanisms interact under projected
+climate conditions to identify the characteristics of resilient reefs through scenario-based
+coral population modelling for the Great Barrier Reef ecosystem.
 
 The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of
-thousands of individual reefs. They are interconnected through coral and fish larval
-dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@cappo2000].
-The GBR faces severe projected coral cover declines under climate change [@bozec2025;
-@bozec2022; @condie2021]. These coral cover declines will be compounded by ocean
-acidification, tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012;
-@fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24 Summer mass
-bleaching event may be signalling a shift towards this reef future, with some level of
-bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
-[@australianinstituteofmarinescience2024; @cantin2024].
+thousands of individual reefs interconnected through larval dispersal patterns mediated by
+hydrodynamic, spatial, and ecological processes [@cappo2000]. The GBR faces severe projected
+coral cover declines under climate change [@bozec2025; @bozec2022; @condie2021]. Coral cover
+declines will be compounded by ocean acidification, tropical cyclones, and crown-of-thorns
+starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011;
+@wolff2018]. The 2023-24 Summer mass bleaching event may be signalling a shift towards this
+reef future, with some level of bleaching recorded on 79% of surveyed reefs (total 1001
+surveyed reefs) [@australianinstituteofmarinescience2024; @cantin2024].
 
@@
 cover and community complexity [@perry2012; @desbiens2021], environmental processes, and
-ocean chemistry [@perry2015; @eyre2018]. For GBR mid-shelf and offshore reefs, maintaining
-positive carbonate budgets requires approximately 17% live coral cover [@desbiens2021].
+ocean chemistry [@perry2015; @eyre2018].
 
@@
 connectivity has been emphasized as critical for GBR resilience [@hock2017], and remains an
-important consideration, our integrated modelling reveals depth may play a fundamental role
-in determining maintenance of reef coral populations and positive carbonate budgets under
+important consideration, our integrated modelling reveals depth plays a fundamental role in
+determining maintenance of reef coral populations and positive carbonate budgets under
 current projections of climate change.
@@
 
-The spatial extent of the GBR reefs represented in this investigation follows the reef
-definitions available via the Great Barrier Reef Marine Park Authority (GBRMPA)
-[@GBRMPA2022]. The reef definitions define 3806 reefs across the GBR. An indicative map of
-the GBR marine park including the Marine Park Management areas [@GBRMPA2007] and the
-corresponding bioregion for each reef is shown in (@fig-region-map; [@GBRMPA2024]).
-Estimates of coral carrying capacity for each reef were taken from prior analyses undertaken
-in [@bozec2022].
+The spatial extent of reefs represented in this investigation follows reef definitions
+available via the Great Barrier Reef Marine Park Authority (GBRMPA) [@GBRMPA2022]. The reef
+definitions define 3806 reefs across the GBR. An indicative map of the GBR marine park
+including the Marine Park Management areas [@GBRMPA2007] and the corresponding bioregion for
+each reef is shown in [@fig-region-map] [@GBRMPA2024]. Estimates of coral carrying capacity
+for each reef were taken from prior analyses undertaken in Bozec et al. [-@bozec2022].
 
@@
 
-These GCMs were selected based on evaluation conducted by Grose et al., [-@grose2023],
-indicating their ability to recreate historical atmospheric temperature and precipitation
-conditions in the Australasian region. They span a range of Equilibrium Climate Sensitivity
-(ECS) values within the Intergovernmental Panel on Climate Change (IPCC) assessed likely
-range. The IPCC defines ECS as the long-term warming caused by a doubling of carbon dioxide
-above its pre-industrial concentration [@forster2021]. While this assessment does not
-consider oceanic data, Grose et al. [-@grose2023] provide a region-specific selection
-mechanism which we use as an indicator of general performance of GCMs for the region. An
-overview of the selected GCMs is provided in @tbl-gcms. Note here that Grose et al.,
-[-@grose2023] assessed GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides
-data based on GFDL-CM4. This substitution is assumed appropriate given they share the same
-fundamental representation of the physical climate system.
+These GCMs were selected based on evaluation by Grose et al., [-@grose2023], indicating
+their ability to recreate historical atmospheric temperature and precipitation conditions in
+the Australasian region. They span a range of Equilibrium Climate Sensitivity (ECS) values
+within the Intergovernmental Panel on Climate Change (IPCC) assessed likely range. The IPCC
+defines ECS as the long-term warming caused by a doubling of carbon dioxide above its
+pre-industrial concentration [@forster2021]. While this assessment does not consider oceanic
+data, Grose et al. [-@grose2023] provide a region-specific selection mechanism which we use
+as an indicator of general performance of GCMs for the region. An overview of the selected
+GCMs is provided in @tbl-gcms. Note here that Grose et al., [-@grose2023] assessed
+GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides data based on GFDL-CM4.
+This substitution is assumed appropriate given they share the same fundamental
+representation of the physical climate system.
 
@@
 [@grose2023; @shepherd2018]) and enables the assessment of modelled coral reef behaviour
-over a broad range of independently derived climate futures [@abramowitz2019].
-
-Monthly mean SST climatological baselines, for each 1km^2^ pixel, were calculated from the
-daily SST data following NOAA methodology [@liu2017; @skirving2020]. For each pixel of SST
-data, the Monthly Mean SST climatology was calculated by computing the mean SST value for
-each calendar month (January through December) across the 28-year baseline period from 1985
-to 2012. For each month separately, this climatological baseline was adjusted to centre at
-year 1988.2857, which attempts to account for any long-term trends within the baseline years
-themselves (see Skirving et al. [@skirving2020]). The adjustment ensures that the
-climatology represents conditions at a specific temporal reference point rather than being
-influenced by gradual warming or cooling trends that may have occurred during the 1985-2012
-period. The resulting monthly climatologies serve as a standardized reference against which
-current SST conditions can be compared to identify thermal anomalies and assess coral
-bleaching risk, following the methodology established by Skirving et al. [-@skirving2020].
-
-Degree Heating Weeks (DHWs) were derived using the "HotSpot SST Anomaly" approach
-[@skirving2020]. The "HotSpot SST Anomaly" represents thermal stress experienced by coral
-reefs and is calculated as the difference between daily SST values and the maximum of a
-pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean
-SST). This approach uses the annual maximum temperature as the baseline because corals are
-adapted to withstand their local warmest conditions under normal seasonal cycles. When
-temperatures exceed this seasonal maximum, corals experience thermal stress that can lead to
-bleaching. Only positive anomalies, greater than 1°C, are considered relevant for coral
-stress, as temperatures below the seasonal maximum do not contribute to bleaching risk.
-
-DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the 12-week
-rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in units of
-°C-weeks. The 12-week accumulation period reflects the cumulative nature of coral thermal
-stress. Brief temperature spikes may be tolerable, but sustained or repeated exposure to
-elevated temperatures causes progressively greater physiological stress and bleaching
-severity. DHW values integrate both the magnitude and duration of thermal stress: a moderate
-anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a severe anomaly
-(e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW estimates for
-each indicative reef (see @GBRMPA2022) were then determined by taking the mean DHW value for
-all pixels touching each reef outline. The process described here was conducted for all 2197
-reefs to create DHW projections spanning from 2025 to 2075. Code used to calculate DHW data
-and perform analyses involved in this investigation can be found at Grier and Iwanaga
-[-@grier2025].
+over a broad range of independently derived climate futures [@abramowitz2019; @brunner2020].
+
+Daily SST data [@dixon2023] were used to calculate climatological baselines and “HotSpot
+Anomaly” values for each pixel following NOAA methodology [@liu2017; @skirving2020].
+Additional information about DHW calculation methods is provided in the supplemental
+material. DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the
+12-week rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in
+units of °C-weeks. The 12-week accumulation period reflects the cumulative nature of coral
+thermal stress. Brief temperature spikes may be tolerable, but sustained or repeated
+exposure to elevated temperatures causes progressively greater physiological stress and
+bleaching severity. DHW values integrate both the magnitude and duration of thermal stress:
+a moderate anomaly (e.g., 1°C) sustained for 12 weeks produces the same DHW value as a
+severe anomaly (e.g., 3°C) lasting 4 weeks, though the biological impacts may differ. DHW
+estimates for each indicative reef (see @GBRMPA2022) were then determined by taking the mean
+DHW value for all pixels touching each reef outline. The process described here was
+conducted for all 2197 reefs to create DHW projections spanning from 2025 to 2075.
 
@@
 depth, and connectivity, that support favourable outcomes in reef recovery and resilience.
-Metrics used in analyses can be found in @stbl-metrics.
 
@@
 language (The Julia Project; https://julialang.org/; [@bezanson2017]), with visualisations
-created using the Makie plotting ecosystem [@danisch2021].
+created using the Makie plotting ecosystem [@danisch2021]. Code used to process DHW data and
+perform analyses involved in this investigation can be found at Grier and Iwanaga
+[-@grier2025].
 
@@
 as the mean of all available data for each location (i.e., mean of all 24 spawning days).
-While the connectivity strengths do not vary from year to year within each ADRIA-CoralBlox
-simulation, they do vary between reefs which are of varying sizes, providing sufficient
-heterogeneity to capture spatial patterns in larval dispersal and settlement dynamics. This
-spatial variability also enables investigations into the influence of connectivity strength
-and its role in driving recovery processes.
+While the connectivity strengths do not vary temporally within each ADRIA-CoralBlox
+simulation, they do vary between reefs. This spatial variability enables investigations into
+the influence of connectivity strength and its role in driving recovery processes.
 
@@
 values indicating the target reef has weak (or no) incoming connections or is supplied by
-small source populations. A limitation of weighted incoming connectivity is it does not
+small source populations. A limitation of weighted incoming connectivity is that it does not
 incorporate the proportion of the source reef's population that is reproducing and producing
@@
 each reef was used for further analyses. These time series of coral cover were then
-clustered based on their temporal behaviour.
+clustered based on their temporal behaviour. Assessment metrics used in analyses can be
+found in @stbl-metrics.
 
@@
 
-The time series clustering was applied over the time frame between 2025 and 2075. The
-clustering was conducted for three spatial scales: (1) the whole of GBR; (2) each GBR
-management area; and (3) for each reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). The
-analyses was conducted at the different spatial scales as, conceptually, the temporal
-behaviour constituting "low", "medium" or "high" coral cover may differ at the different
-spatial scales. As it was, analyses at the whole-of-GBR scale were found to lead to
-identical conclusions regarding reef characteristics which influence coral cover and so for
-brevity are not shown here.
+Time series clustering was applied over the time frame between 2025 and 2075. The clustering
+was conducted for three spatial scales: (1) the whole of GBR; (2) each GBR management area;
+and (3) for each reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). The analyses were
+conducted at the different spatial scales as, conceptually, the temporal behaviour
+constituting "low", "medium" or "high" coral cover may differ at the different spatial
+scales. As it was, analyses at the whole-of-GBR scale were found to lead to identical
+conclusions regarding reef characteristics which influence coral cover and so for brevity
+are not shown here.
 
@@
 outgoing-to-incoming connectivity ratio. The full dataset consisted of the time series
-cluster assignment of each of the 2197 reefs under the five GCMs explored, for a total of
+cluster assignment for each of the 2197 reefs under the five GCMs explored, for a total of
 10,985 samples. The dataset was randomly split into training (60%) and testing (40%) subsets
@@
 
-A 3-fold cross-validation was also conducted, arriving at a similar 59% accuracy rate.
-Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
-0.70, 0.43 and 0.64 respectively, with precision of 0.62, 0.51 and 0.66 when evaluated with
-the test set (consisting of 4394 samples) [@stbl-confusion-matrix;
-@stbl-rf-cluster-performance]. Lower performance with the Medium cluster reflects the
-inherent difficulty of classifying transitional states in natural systems. The consistent
-level of accuracy across test and cross-validation demonstrates the generalised performance
-of the RF classifier, while not accurate, was deemed sufficiently informative for the
-purpose of assessing the influence of reef characteristics.
+A 3-fold cross-validation was also conducted, arriving at a similar 59% accuracy rate. F1
+performance scores for Low, Medium, and High clusters were determined to be 0.70, 0.43 and
+0.64 respectively, with precision of 0.62, 0.51 and 0.66 when evaluated with the test set
+(consisting of 4394 samples) (@stbl-confusion-matrix; @stbl-rf-cluster-performance). Lower
+performance with the Medium cluster reflects the inherent difficulty of classifying
+transitional states in natural systems. The consistent level of accuracy across test and
+cross-validation demonstrates the generalised performance of the RF classifier, while not
+accurate, was deemed sufficiently informative for the purpose of assessing the influence of
+reef characteristics.
 
@@
 representative reef characteristics in the test dataset. Additionally, to assess possible
-interaction between reef depth and incoming connectivity, two-way partial dependence
-analysis was performed on grids along the range of these two features.
+interaction between reef depth and connectivity metrics, two-way partial dependence analysis
+was performed on grids along the ranges of depth and weighted incoming connectivity, and
+depth and outgoing connection strength.
 
@@
 between reef characteristics and assigned clusters were found to be similar at the bioregion
-scale across GCMs. Results are only shown and discussed for ACCESS-ESM1-5, an intermediate
-ECS scenario (@sfig-ecs). Those interested in results for the other assessed GCMs are
-referred to Grier and Iwanaga [-@grier2025]. Across bioregions, reefs in the High cluster
-not only had greater levels of coral recovery but displayed persistence to 2050
-(@sfig-access-esm1-5-bioregion-timeseries). Reefs in the High cluster were consistently
-found to have the greatest median reef depths across bioregions
-(@fig-access-esm1-5-bioregion-depth).
-
-![Median depth for reefs within each bioregion under ACCESS-ESM1-5, separated into clusters
-assigned by time series clustering. Time series were clustered based on their behaviour
-between 2030 and 2060. Time series with comparatively low median area-relative cover is
-indicated in green, intermediate cover in orange, and high in blue. Solid lines represent
-the median depth for each cluster across reefs and bands represent the distribution of depth
-values within each
-cluster.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
-fig-align="center" width="14.82cm"}
-
-Across bioregions, there were no consistent patterns between reef clusters in mean DHW
-values (@sfig-access-esm1-5-bioregion-dhwmean), log10-weighted incoming connectivity
-(@sfig-access-esm1-5-bioregion-weightedincoming), log10 outgoing connection strength
-(@sfig-access-esm1-5-bioregion-outgoingconn), log10 source-to-sink connectivity ratio
-(@sfig-access-esm1-5-bioregion-logsosi) and log10 larval retention probability
-(@sfig-access-esm1-5-bioregion-selfconn). Across six of the 29 bioregions reefs in the high
-cover cluster have lower log10 carrying capacity values than reefs in other clusters
-(@sfig-access-esm1-5-bioregion-carrying-capacity).
+scale across GCMs. Across bioregions, reefs in the High cluster not only had greater levels
+of coral recovery but displayed persistence to 2050
+(@sfig-access-esm1-5-bioregion-timeseries). Qualitative representations of bioregion scale
+clustering results across assessed reef characteristics can be found in the supplementary
+material, with Partial Dependence Analysis results displayed in the main text.
 
@@
 
-A Partial Dependence Analysis was conducted using a Random Forest classifier to identify
-reef characteristics that influence its temporal behaviour, and thus its assignment into
-Low, Medium, or High cover clusters. Reef median depth, carrying capacity and mean time
+Partial Dependence Analysis revealed reef median depth, carrying capacity and mean time
 series DHW level have the highest feature importance scores, accounting for 29%, 15% and 15%
@@
 ![Reef Degree Heating Week time series clustered within each management area, for each GCM
-analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
-between 2030 and 2060 within each bioregion. ‘Medium’ clusters (orange) are clusters with
-intermediate median area-relative cover between 2030 and 2060 within each bioregion. ‘High’
-clusters (blue) are clusters with the highest median area-relative cover between 2030 and
-2060 within each bioregion. Solid lines represent the cluster median time series and bands
-represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
+analysed. Time series were clustered based on their behaviour between 2030 and 2060. Time
+series with comparatively low median area-relative cover is indicated in green, intermediate
+cover in orange, and high in blue. Solid lines represent the cluster median time series and
+bands represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
 represented five times (for each GCM), with each GCM displayed
@@
 
+## Degree Heating Week data processing
+
+Monthly mean SST climatological baselines, for each 1km^2^ pixel, were calculated from the
+daily SST data following NOAA methodology [@liu2017; @skirving2020]. For each pixel of SST
+data, the Monthly Mean SST climatology was calculated by computing the mean SST value for
+each calendar month (January through December) across the 28-year baseline period from 1985
+to 2012. For each month separately, this climatological baseline was adjusted to centre at
+year 1988.2857, which attempts to account for any long-term trends within the baseline years
+themselves (see Skirving et al. [@skirving2020]). The adjustment ensures that the
+climatology represents conditions at a specific temporal reference point rather than being
+influenced by gradual warming or cooling trends that may have occurred during the 1985-2012
+period. The resulting monthly climatologies serve as a standardized reference against which
+current SST conditions can be compared to identify thermal anomalies and assess coral
+bleaching risk, following the methodology established by Skirving et al. [-@skirving2020].
+
+Degree Heating Weeks (DHWs) were derived using the "HotSpot SST Anomaly" approach
+[@skirving2020]. The "HotSpot SST Anomaly" represents thermal stress experienced by coral
+reefs and is calculated as the difference between daily SST values and the maximum of a
+pixel's monthly mean climatology across all twelve months (i.e., the maximum monthly mean
+SST). This approach uses the annual maximum temperature as the baseline because corals are
+adapted to withstand their local warmest conditions under normal seasonal cycles. When
+temperatures exceed this seasonal maximum, corals experience thermal stress that can lead to
+bleaching. Only positive anomalies, greater than 1°C, are considered relevant for coral
+stress, as temperatures below the seasonal maximum do not contribute to bleaching risk.
+
 ## ADRIA-CoralBlox
@@
 
-![Reef area-relative coral cover time series clustered within each bioregion. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
-each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2060 within each
-bioregion. Solid lines represent the cluster median time series and bands represent the 95th
-percentile confidence intervals. Displays results for ACCESS-ESM1-5
+Results are only shown and discussed for ACCESS-ESM1-5, an intermediate ECS scenario
+(@sfig-ecs). Those interested in results for the other assessed GCMs are referred to Grier
+and Iwanaga [-@grier2025]. Reefs in the High cluster were consistently found to have the
+greatest median reef depths across bioregions (@sfig-access-esm1-5-bioregion-depth). Across
+bioregions, there were no consistent patterns between reef clusters in mean DHW values
+(@sfig-access-esm1-5-bioregion-dhwmean), log10-weighted incoming connectivity
+(@sfig-access-esm1-5-bioregion-weightedincoming), log10 outgoing connection strength
+(@sfig-access-esm1-5-bioregion-outgoingconn), log10 source-to-sink connectivity ratio
+(@sfig-access-esm1-5-bioregion-logsosi) and log10 larval retention probability
+(@sfig-access-esm1-5-bioregion-selfconn). Across six of the 29 bioregions reefs in the high
+cover cluster have lower log10 carrying capacity values than reefs in other clusters
+(@sfig-access-esm1-5-bioregion-carrying-capacity).
+
+![Reef area-relative coral cover time series clustered within each bioregion. Time series
+were clustered based on their behaviour between 2030 and 2060. Time series with
+comparatively low median area-relative cover is indicated in green, intermediate cover in
+orange, and high in blue. Solid lines represent the cluster median time series and bands
+represent the 95th percentile confidence intervals. Displays results for ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/bioregion/bioregion_cover_timeseries.png){#sfig-access-esm1-5-bioregion-timeseries
@@
 
+![Median depth for reefs within each bioregion under ACCESS-ESM1-5, separated into clusters
+assigned by time series clustering. Time series were clustered based on their behaviour
+between 2030 and 2060. Time series with comparatively low median area-relative cover is
+indicated in green, intermediate cover in orange, and high in blue. Solid lines represent
+the median depth for each cluster across reefs and bands represent the distribution of depth
+values within each
+cluster.](../figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#sfig-access-esm1-5-bioregion-depth
+fig-align="center" width="14.82cm"}
+
 ![Mean time series DHW values for reefs within each bioregion, separated into clusters
-assigned by time series clustering. ‘Low’ clusters (green) are clusters with the lowest
-median area-relative cover between 2030 and 2060 within each bioregion. ‘Medium’ clusters
-(orange) are clusters with intermediate median area-relative cover between 2030 and 2060
-within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
-area-relative cover between 2030 and 2060 within each bioregion. Solid lines represent the
-median DHW level for each cluster and bands represent the distribution of mean DHW levels
-within each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
+assigned by time series clustering, under ACCESS-ESM1-5. Time series were clustered based on
+their behaviour between 2030 and 2060. Time series with comparatively low median
+area-relative cover is indicated in green, intermediate cover in orange, and high in blue.
+Solid lines represent the median DHW level for each cluster and bands represent the
+distribution of mean DHW levels within each
+cluster.](../figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
 fig-align="center" width="14.82cm"}
@@
 ![Reef carrying capacity (coral habitable area, in base-10 log scale) for reefs within each
-bioregion, separated into clusters assigned by time series clustering. ‘Low’ clusters
-(green) are clusters with the lowest median area-relative cover between 2030 and 2060 within
-each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median
-area-relative cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are
-clusters with the highest median area-relative cover between 2030 and 2060 within each
-bioregion. Solid lines represent the median carrying capacity for each cluster and bands
-represent the distribution of values within each cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/carrying_capacity_bioregion_violin.png){#sfig-access-esm1-5-bioregion-carrying-capacity
+bioregion, separated into clusters assigned by time series clustering, under ACCESS-ESM1-5.
+Time series were clustered based on their behaviour between 2030 and 2060. Time series with
+comparatively low median area-relative cover is indicated in green, intermediate cover in
+orange, and high in blue. Solid lines represent the median carrying capacity for each
+cluster and bands represent the distribution of values within each
+cluster.](../figs/ACCESS-ESM1-5/bioregion/carrying_capacity_bioregion_violin.png){#sfig-access-esm1-5-bioregion-carrying-capacity
 fig-align="center" width="14.82cm"}
@@
 ![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median source-to-sink ratio for each cluster and
-bands represent the distribution of source-to-sink ratios within each cluster. The vertical
-grey line represent a source-to-sink ratio of 0 (in base-10 log scale) indicating equal
-outgoing and incoming connectivity levels. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
+separated into clusters assigned by time series clustering, under ACCESS-ESM1-5. Time series
+were clustered based on their behaviour between 2030 and 2060. Time series with
+comparatively low median area-relative cover is indicated in green, intermediate cover in
+orange, and high in blue. Solid lines within each violin represent the median source-to-sink
+ratio for each cluster and bands represent the distribution of source-to-sink ratios within
+each cluster. The vertical grey line represent a source-to-sink ratio of 0 (in base-10 log
+scale) indicating equal outgoing and incoming connectivity
+levels.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
 fig-align="center" width="14.82cm"}
@@
 ![Weighted incoming connectivity (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median base-10 log of weighted incoming connectivity
-for each cluster and bands represent the distribution of connectivity values within each
-cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/weighted_incoming_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedincoming
+separated into clusters assigned by time series clustering, under ACCESS-ESM1-5. Time series
+were clustered based on their behaviour between 2030 and 2060. Time series with
+comparatively low median area-relative cover is indicated in green, intermediate cover in
+orange, and high in blue. Solid lines within each violin represent the median base-10 log of
+weighted incoming connectivity for each cluster and bands represent the distribution of
+connectivity values within each
+cluster.](../figs/ACCESS-ESM1-5/bioregion/weighted_incoming_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-weightedincoming
 fig-align="center" width="14.82cm"}
@@
 ![Outgoing connection strength (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median base-10 log of outgoing connection strength
-for each cluster and bands represent the distribution of connectivity values within each
-cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/outgoing_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-outgoingconn
+separated into clusters assigned by time series clustering, under ACCESS-ESM1-5. Time series
+were clustered based on their behaviour between 2030 and 2060. Time series with
+comparatively low median area-relative cover is indicated in green, intermediate cover in
+orange, and high in blue. Solid lines within each violin represent the median base-10 log of
+outgoing connection strength for each cluster and bands represent the distribution of
+connectivity values within each
+cluster.](../figs/ACCESS-ESM1-5/bioregion/outgoing_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-outgoingconn
 fig-align="center" width="14.82cm"}
@@
 ![Larval retention probability (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
-clusters with the lowest median area-relative cover between 2030 and 2060 within each
-bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
-cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
-the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
-lines within each violin represent the median base-10 log of larval retention probability
-for each cluster and bands represent the distribution of probability values within each
-cluster. Displays results for ACCESS-ESM1-5
-GCM.](../figs/ACCESS-ESM1-5/bioregion/self_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-selfconn
+separated into clusters assigned by time series clustering, under ACCESS-ESM1-5. Time series
+were clustered based on their behaviour between 2030 and 2060. Time series with
+comparatively low median area-relative cover is indicated in green, intermediate cover in
+orange, and high in blue. Solid lines within each violin represent the median base-10 log of
+larval retention probability for each cluster and bands represent the distribution of
+probability values within each
+cluster.](../figs/ACCESS-ESM1-5/bioregion/self_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-selfconn
 fig-align="center" width="14.82cm"}
@@
 ![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by mean time series DHW value. Colour-coded areas
-outline GBR marine park management regions, where orange represents the Far Northern
-management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
-blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
-visual clarity. Darker colours represent higher mean DHW values than lighter colours. All
-2197 reefs included in this investigation are represented in this figure. This map depicts
-values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
-GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map fig-align="center"
-width="14.82cm"}
-
-![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by weighted incoming connectivity levels (Log10).
+considered reefs (points), coloured by mean time series DHW value under ACCESS-ESM1-5.
 Colour-coded areas outline GBR marine park management regions, where orange represents the
@@
 Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
+marked individually for visual clarity. Darker colours represent higher mean DHW values than
+lighter colours. All 2197 reefs included in this investigation are represented in this
+figure. Annotations represent major coastal settlements along the
+GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map fig-align="center"
+width="14.82cm"}
+
+![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
+considered reefs (points), coloured by weighted incoming connectivity levels (Log10) under
+ACCESS-ESM1-5. Colour-coded areas outline GBR marine park management regions, where orange
+represents the Far Northern management region, green represents Cairns/Cooktown, red covers
+Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
 marked individually for visual clarity. Darker colours represent higher weighted incoming
 connectivity values than lighter colours. All 2197 reefs included in this investigation are
-represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations
-represent major coastal settlements along the
+represented in this figure. Annotations represent major coastal settlements along the
 GBR.](../figs/ACCESS-ESM1-5/weighted_incoming_conn_input_map.png){#sfig-incoming-conn-map

### 2025-10-02 paper/paper_draft.qmd
Reorder to move acknowledgements inline with submission for GCB
Add math notation to connectivity variables

@@
 represents the strength of the reef's outgoing larval flow relative to it's incoming larval
-flow. This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where S represents the sum of
-connectivity probabilities, N represents the number of connections, O denotes outgoing
-connectivity from the target reef and I denotes incoming connectivity to the target reef. If
+flow. This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of
+connectivity probabilities, $N$ represents the number of connections, $O$ denotes outgoing
+connectivity from the target reef and $I$ denotes incoming connectivity to the target reef. If
 a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value. Incoming
@@
 
-# References
-
-::: {#refs}
-:::
-
-# Author Contributions
-
-**Benjamin Grier:** conceptualisation, data curation, formal analysis, investigation,
-methodology, visualization, writing – original draft, writing – review and editing. **Takuya
-Iwanaga:** conceptualisation, data curation, formal analysis, investigation, methodology,
-visualization, writing – original draft, writing – review and editing. **\[BG: To be
-completed.\] ...**
-
 # Acknowledgements
@@
 Reef Restoration and Adaptation Program **\[BG: To be completed.\]**.
+
+# References
+
+::: {#refs}
+:::
+
+# Author Contributions
+
+**Benjamin Grier:** conceptualisation, data curation, formal analysis, investigation,
+methodology, visualization, writing – original draft, writing – review and editing. **Takuya
+Iwanaga:** conceptualisation, data curation, formal analysis, investigation, methodology,
+visualization, writing – original draft, writing – review and editing. **\[BG: To be
+completed.\] ...**
 

### 2025-10-05 paper/paper_draft.qmd
Updates to supplementary material (excluding ADRIA-CoralBlox changes pending)

@@
 represents the strength of the reef's outgoing larval flow relative to it's incoming larval
-flow. This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of
-connectivity probabilities, $N$ represents the number of connections, $O$ denotes outgoing
-connectivity from the target reef and $I$ denotes incoming connectivity to the target reef. If
-a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value. Incoming
-connections in this calculation, do not directly represent the larval supply gained as the
-breeding populations from which connections are coming from are not represented. A
+flow. This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum
+of connectivity probabilities, $N$ represents the number of connections, $O$ denotes
+outgoing connectivity from the target reef and $I$ denotes incoming connectivity to the
+target reef. If a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value.
+Incoming connections in this calculation, do not directly represent the larval supply gained
+as the breeding populations from which connections are coming from are not represented. A
 source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef
@@
 The CID time series clustering metric corrects the Euclidean distance between pairs of time
-series (which accounts for magnitude differences) with the complexity of each time series
-(obtained through a measure of their variability) to ensure reefs are clustered based on
-their underlying temporal dynamics rather than simply their average coral cover. The process
-creates a distance matrix of n \* n dimensions (where n is the number of time series in the
-group) that is clustered using a k-medoids clustering algorithm [cf. @steinmann2020]. The
-three reef clusters are labelled with qualitative-ordered clusters from Low, Medium and High
-based on their median cover relative to each other cluster over the 2030-2060 period. The
-selected time frame prevents the classification from being overly influenced by any steep
-declines in the initial years of simulations and avoids the post-2060 time period where
-reefs are projected to be under severe stress and in a declined state [@bozec2025].
-
-## ACCESS-ESM1-5
+series with their relative complexity (which is the quotient of their variability). This is
+to ensure reefs are clustered based on their underlying temporal dynamics rather than
+aggregating the coral cover across all timesteps. The process creates a n \* n distance
+matrix (where n is the number of time series in the group) that is used as an input to a
+k-medoids clustering algorithm [cf. @steinmann2020]. The three reef clusters are labelled
+with qualitative-ordered labels from Low, Medium and High based on their median cover
+relative to each other cluster over the 2030-2060 period. The selected time frame prevents
+the classification from being overly influenced by any steep declines in the initial years
+of simulations and avoids the post-2060 time period where reefs are projected to be under
+severe stress and in a declined state [@bozec2025].
+
+## ACCESS-ESM1-5 results
+
+ACCESS-ESM1-5 was selected for GCM-level results as an intermediate severity GCM, with an
+ECS value closest to the midpoint of the IPCC likely range of ECS values (3.87 °C). The
+following section includes supplemental results for analyses under this GCM. A comparison of
+results across GCMs can be found in the main text, and individual GCM-level results for
+other GCMs can be found at Grier and Iwanaga [-@grier2025].
 
@@
 connectivity for each reef. Point colours represent the median number of years each reef
-maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover.
+maintains positive carbonate budgets across $theta$ values from 10-20% live coral cover.
 Displays results for ACCESS-ESM1-5
@@
 
+The following section includes bioregion scale clustering results, full results for other
+spatial scales (management area and GBR) can be found at Grier and Iwanaga [-@grier2025].
 Results are only shown and discussed for ACCESS-ESM1-5, an intermediate ECS scenario
@@
 
-#### Random Forest Performance
+## Random Forest Performance
 

### 2025-10-05 paper/paper_draft.qmd
Updates to acknowledgements section

@@
 
-We acknowledge the contributions of Barbara Robson and Jessica Benthuysen to manuscript
-preparation. This research was funded by the Reef Restoration and Adaptation Program, and
-facilitated by the Australian Institute of Marine Science. We acknowledge thermal projection
-data sourced from HighResCoralStress datasets, model parameterisation data sourced from the
-Ecological Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition
-probability data derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data
-available from the Great Barrier Reef Marine Park Authority. All authors are funded by the
-Reef Restoration and Adaptation Program **\[BG: To be completed.\]**.
+The authors acknowledge the Bindal people, Traditional Owners of the land on which the work
+took place at the AIMS Townsville site. The authors acknowledge the contributions of Barbara
+Robson and Jessica Benthuysen to manuscript preparation. This research was funded by the
+Reef Restoration and Adaptation Program, and facilitated by the Australian Institute of
+Marine Science. The authors acknowledge thermal projection data sourced from
+HighResCoralStress datasets, model parameterisation data sourced from the Ecological
+Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition probability data
+derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data available from
+the Great Barrier Reef Marine Park Authority. The eReefs Project is a private-public
+collabroation between Australia's leading operational and scientific research agencies,
+government and corporate Australia. All authors are funded by the Reef Restoration and
+Adaptation Program **\[BG: To be completed.\]**.
 

### 2025-10-05 paper/paper_draft.qmd
Updates to conclusion section

@@
 The results presented suggest that when modelled as part of a large and complex ecosystem,
-reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in
-support of depth as a form of thermal refugia for shallow-water reefs on the GBR. Targetting
-reefs with median depths greater than 10m may aid in identifying the most resilient reefs
-under climate change. We suggest further analyses that investigate the benefits of
+reef depth is a key factor contributing to ongoing reef resilience. This investigation
+provides evidence in support of depth as a form of thermal refugia for shallow-water reefs
+on the GBR. Targeting reefs with median depths greater than 10m may aid in identifying the
+most resilient reefs under climate change. Further analyses that investigate the benefits of
 incorporating depth-based resilience into reef intervention decision making, as well as
 further research and development in connectivity modelling methods for whole-ecosystem
-scales.
+scales are recommended.
 

### 2025-10-05 paper/paper_draft.qmd
Updates to limitations section

@@
 There are multiple caveats in how coral ecosystem dynamics are modelled in this
-investigation. We model coral colonies as circular diameter values that are tracked over
-timesteps through growth. Additionally, we do not model the direct influence of light
-intensity on coral growth or the negative influence of depth on coral growth rates due to
-reduced available light levels [@baker1975; @huston1985; @ruiz-diaz2022]. If included in
-this investigation it is possible that reef recovery ability, via regrowth, would be reduced
-at greater depths, reducing the positive effect of depth refugia for temporal resilience.
-Additionally, reduced growth rates at increased depths may reduce the carbonate budget
-maintenance of reefs due to lower rates of CaCO~3~ accretion. Due to the availability of
-quality future projected data we do not consider other important impacts such as waves,
-cyclones, currents and Crown of Thorns Starfish (CoTS) on coral colony survival and
-bleaching [@massel1993; @deaker2022].
+investigation. Coral colonies are modelled as diameter values that increase over time
+through growth. Additionally, the influence of light intensity on coral growth or the
+negative influence of depth on coral growth rates due to reduced available light levels are
+not modelled in this investigation [@baker1975; @huston1985; @ruiz-diaz2022]. If included in
+this investigation, it is possible that reef recovery ability, via regrowth, would be
+reduced at greater depths, reducing the positive effect of depth refugia for temporal
+resilience. Additionally, reduced growth rates at increased depths may reduce carbonate
+budget maintenance due to lower rates of CaCO~3~ accretion. Due to the availability of
+quality future projected data this investigation does not consider other important impacts
+such as waves, cyclones, ocean currents and Crown of Thorns Starfish (CoTS) on coral colony
+survival and bleaching [@massel1993; @deaker2022].
 
 Uncertainty in connectivity modelling outputs, satellite-derived bathymetry data and future
-thermal stress projections are likely to influence the results obtained in this
-investigation. While the resolution of connectivity data used in this investigation improves
-upon data used in comparable studies [@bozec2025], the time-mean implementation used may not
-effectively capture long term patterns [@vogt-vincent2023]. Using alternative connectivity
+thermal stress projections likely influence the results obtained in this investigation.
+While the resolution of connectivity data used in this investigation improves upon data used
+in comparable studies [@bozec2025], the time-mean implementation used may not effectively
+capture long term patterns [@vogt-vincent2023]. Using alternative connectivity
 implementation methods that better capture the ecological-timescale trends in reef
 connections rather than the high daily variability, would improve confidence in the
-connectivity findings of this investigation [@vogt-vincent2023]. Additionally greater year -
-sample sizes for baseline connectivity data as future computation improvements are made,
-along with the derivation of connectivity from an ensemble of biophysical models, will
-improve confidence in connectivity data for ecological modelling and management applications
-[@choukroun2025]. The DHW data used in this investigation have not been bias corrected for
-the Great Barrier Reef region and are part of a wider Australian dataset [@dixon2022]
-developed using statistical downscaling. Additionally, Lachs et al. [@lachs2021] suggest the
-utility of DHW levels for prediction of coral bleaching can be improved by reducing the
-threshold for HotSpot Anomaly values from MMM +1 to MMM and reducing the accumulation window
-from 12 weeks to 8 weeks. We investigate a range of future climate responses, thermal
-projections and ecological parameterisations of ADRIA - CoralBlox to account for many
-possible futures, and our results suggest the factors that influence reef resilience are
-consistent across these scenarios.
-
-Additionally, it is currently not possible to obtain highly accurate and precise estimates
-of reef depth at the GBR-scale. Data adopted for the given assessment are said to be
-accurate up to 15m from Mean Sea Level [@GBRMPA2020; @li2021], however there are many
-sources of uncertainty in the depth estimates used for this study. Satellite-derived
+connectivity findings of this investigation [@vogt-vincent2023]. Increased samples to inform
+baseline connectivity data, along with the derivation of connectivity from an ensemble of
+biophysical models, would also improve confidence in connectivity data for ecological
+modelling and management applications [@choukroun2025].
+
+DHW data used in this investigation have not been bias corrected for the Great Barrier Reef
+region and are part of a wider Australian dataset [@dixon2022] developed using statistical
+downscaling. Lachs et al. [-@lachs2021] suggest the utility of DHW levels for prediction of
+coral bleaching can be improved by reducing the threshold for HotSpot Anomaly values from
+MMM +1 to MMM and reducing the accumulation window from 12 weeks to 8 weeks. The presented
+analyses assessed a range of future climate responses, thermal projections and ecological
+parameterisations of ADRIA-CoralBlox to account for many possible futures and suggests the
+factors that influence reef resilience are consistent across these scenarios.
+
+Highly accurate and precise estimates of reef depth across the GBR are currently not
+possible to obtain with (publicly) available data. Data adopted for the given assessment are
+said to be accurate up to 15m from Mean Sea Level [@GBRMPA2020; @li2021], however there are
+many sources of uncertainty in the depth estimates used for this study. Satellite-derived
 estimates are subject to different bottom types (rock, sand, seagrass, etc) and their effect
@@
 resulting depth estimates are therefore highly uncertain and are only adopted as a useful
-indication for the purpose of the presented analysis. They are not intended to be an
-accurate and precise report of reef depths across the GBR.
+indication for the purpose of the presented analysis. They are not intended to be accurate
+and precise reef depths across the GBR.
 
@@
 false positives, where features identified as reefs were sand banks or rocky reefs (rather
-than coral reefs). Reefs with bathymetry data of less than 5% of its indicative area were
-excluded from analysis to ensure analyses were not conducted on reefs with no data coverage
-(see @sfig-depth-cutoff). The existing GBRMPA reef outlines were adopted to align with other
-ongoing modelling and analyses conducted as part of the Reef Restoration and Adaptation
-Program (<https://gbrrestoration.org>; [@thereef]).
+than coral reefs). Reefs with bathymetry data covering less than 5% of their indicative area
+were excluded from analyses (see @sfig-depth-cutoff). Existing GBRMPA reef outlines were
+adopted to align with other ongoing modelling and analyses conducted as part of the Reef
+Restoration and Adaptation Program (<https://gbrrestoration.org>; [@thereef]).
 
@@
 model's ability to meaningfully capture ecological signals at the GBR-scale. The mechanistic
-basis of the model supports the robustness of our findings for understanding broad-scale
+basis of the model supports the robustness of these findings for understanding broad-scale
 coral cover responses to climatic drivers. The aim here, however, was to assess the relative
@@
 parameterisations, rather than provide spatially explicit and precise predictions of reef
-outcomes. Using this approach, we suggest that reef depth is an important factor for reef
+outcomes. Using this approach, results suggest reef depth is an important factor for reef
 resilience under thermal stress.
@@
 investigations of depth as a critical factor for reef resilience. Additional analyses could
-build on the findings of this study by assessing the impacts of prioritising reef depth in
-reef intervention decision making. Future analyses could incorporate other environmental and
-ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn Starfish
-[@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
+build on the findings of this study by assessing the impacts of prioritising reef depth for
+reef intervention decision outcomes. Future analyses could incorporate other environmental
+and ecological stressors such as wave activity, ocean acidification, and Crown-of-Thorn
+Starfish [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022; @liu2024; @eyre2018].
 

### 2025-10-05 paper/paper_draft.qmd
Updates for whole discussion section

@@
 
-Our results show increasing reef depth has a strong positive impact on modelled reef
-resilience in temporal behaviour and maintenance of positive carbonate budgets under
-possible future conditions. Reefs with a median depth of 10m or greater, with high incoming
-connectivity, are the most likely to be assigned to a high cover time series cluster. By
-itself, incoming connectivity alone does not correlate with maintenance of positive
-carbonate budgets. These findings highlight the importance of depth and incoming
+This investigation's results show increasing reef depth has a strong positive impact on
+modelled reef resilience in temporal behaviour and maintenance of positive carbonate budgets
+under possible future conditions. Reefs with a median depth of 10m or greater, with high
+incoming connectivity, are the most likely to be assigned to a high cover time series
+cluster. By itself, incoming connectivity alone does not correlate with maintenance of
+positive carbonate budgets. These findings highlight the importance of depth and incoming
 connectivity as coupled selection features when assessing potential reef resilience under
@@
 magnitude DHWs based on SST, the proportion of a reefs' coral population impacted by heat
-stress events depends on reef depth. Reefs at deeper depths are likely to be clustered into
-High cover clusters. Reefs at shallow depths experience no, or few, years with coral cover
-exceeding levels likely required to maintain positive carbonate budgets. Movement of shallow
-reefs towards negative carbonate budgets in the future may contribute to phase shifts in
-reef dominant CaCO~3~ production. Shifting from coral driven to encrusting algae driven
-production, or to bioerosion dominated systems with rapid erosion of physical reef
-frameworks [@dudgeon2010; @perry2008]. Reefs at increased depths may be able to maintain
-coral driven CaCO~3~ production and accumulation into the future for longer. Our results
-suggest that for non-mesophotic reef ecosystems (i.e., \< 30m), depth contributes greatly to
-reef resilience and the ability of reefs to maintain positive carbonate budgets under future
-conditions. Spatially our results indicate that regions of positive carbonate budget
-maintenance, under ACCESS-ESM1-5, and high depth levels were concentrated in the Far
-Northern, offshore Townsville/Whitsunday, and Mackay/Capricorn management areas
-(@sfig-carb-budget-map; @sfig-depth-map). Resilient reefs in the Far Northern management
-area were exposed to lower mean DHW levels than other reefs under ACCESS-ESM1-5
-(@sfig-mean-dhw-map), however similar spatial patterns were observed across GCMs for reefs
-clustered into the high cover cluster (@sfig-gcm-cluster-map). We do not interpret these
-spatial findings as accurate predictions of future resilience due to high uncertainty in
-input data, particularly depth and connectivity. While similar findings have been
-demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014] regions,
-depth refugia analyses have often focused on the potential of mesophotic reefs (\> 30m deep)
-as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et
-al. [-@venegas2019] found no association between depth and the alleviation of heat stress
-across a range of shallow reefs in the Pacific.
-
-Our findings support the hypothesis that reefs at greater depths will exhibit
-characteristics of refugia and prolonged resilience (in terms of coral cover) under climate
-change compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024]
-suggest that rubble instability is inversely correlated with reef depth, possibly limiting
-juvenile coral recruitment capacity of shallow reefs. A caveat to our depth-resilience
-findings is the quality of the bathymetry data used to calculate median reef depth. As
-detailed previously, estimates of median reef depth are derived from satellite imagery (at
-$10m^2$ resolution) which can be subject to high degrees of uncertainty, both in terms of
-the estimated depth for each pixel as well as their alignment to the established GBRMPA reef
-outlines. Additionally, we do not incorporate light-based decreases in coral growth rates as
-depth increases [@baker1975; @huston1985; @ruiz-diaz2022].
+stress events depends on reef depth. Our results suggest that for non-mesophotic reef
+ecosystems (i.e., \< 30m), depth contributes greatly to reef resilience and maintenance
+positive carbonate budgets under future conditions. Movement of shallow reefs towards
+negative carbonate budgets in the future may contribute to phase shifts in reef dominant
+CaCO~3~ production. Shifting from coral driven to encrusting algae driven production, or to
+bioerosion dominated systems with rapid erosion of physical reef frameworks [@dudgeon2010;
+@perry2008]. Reefs at increased depths may be able to maintain coral driven CaCO~3~
+production and accumulation into the future for longer. Spatially these results indicate
+that regions of positive carbonate budget maintenance, under ACCESS-ESM1-5, and high depth
+levels were concentrated in the Far Northern, offshore Townsville/Whitsunday, and
+Mackay/Capricorn management areas (@sfig-depth-map; @sfig-carb-budget-map). Resilient reefs
+in the Far Northern management area were exposed to lower mean DHW levels than other reefs
+under ACCESS-ESM1-5 (@sfig-mean-dhw-map), however similar spatial patterns were observed
+across GCMs for reefs clustered into the high cover cluster (@sfig-gcm-cluster-map). Spatial
+findings are not interpreted as accurate predictions of future resilience due to high
+uncertainty in input data, particularly depth and connectivity. While similar findings have
+been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014]
+regions, depth refugia analyses have often focused on the potential of mesophotic reefs (\>
+30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast,
+Venegas et al. [-@venegas2019] found no association between depth and the alleviation of
+heat stress across a range of shallow reefs in the Pacific.
+
+The results of this investigation support the hypothesis that reefs at greater depths will
+exhibit characteristics of refugia and prolonged resilience (in terms of coral cover) under
+climate change compared to shallower reefs. Additionally, Liu, Callaghan and Baldock
+[-@liu2024] suggest that rubble instability is inversely correlated with reef depth,
+possibly limiting juvenile coral recruitment capacity of shallow reefs. A caveat to
+depth-resilience findings is the quality of the bathymetry data used to calculate median
+reef depth. As detailed previously, estimates of median reef depth are derived from
+satellite imagery (at $10m^2$ resolution) which can be subject to high degrees of
+uncertainty, both in terms of the estimated depth for each pixel as well as their alignment
+to the established GBRMPA reef outlines.
 
@@
 visual identification of sites from the surface, in combination with tourism return value.
-Our results suggest that of the assessed reefs occurring within the 1-10m depth range (1551
-reefs), 59% (920) of reefs are consistently clustered into the Low and Medium cover clusters
-across the GCMs (at the GBRMPA management region scale), with many found to be unable to
-maintain positive carbonate budgets under projected conditions. Partial dependence analysis
-revealed a range of depths from 10-15m where the probability of a reef being clustered into
-the High cover cluster increased substantially. Additionally, two-way partial dependence
-analysis revealed that high incoming connectivity is important for High cluster assignment
-for reefs at depths of \>10m. Considering this 10-15m depth range when assessing possible
-intervention sites may reduce the exposure of planted and seeded corals to high thermal
-stress, while still maintaining effective logistical access to sites.
+Of the assessed reefs occurring within the 1-10m depth range (1551 reefs), 59% (920) of
+reefs are consistently clustered into the Low and Medium cover clusters across the GCMs (at
+the GBRMPA management region scale), with many found to be unable to maintain positive
+carbonate budgets under projected conditions. PDA revealed a range of depths from 10-15m
+where the probability of a reef being clustered into the High cover cluster increased
+substantially. Additionally, two-way partial dependence analysis revealed high incoming
+connectivity is important for High cluster assignment for reefs at depths of \>10m.
+Considering this 10-15m depth range when assessing possible intervention sites may reduce
+the exposure of planted and seeded corals to high thermal stress, while still maintaining
+effective logistical access to sites.
 
@@
 the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008;
-@torres2024]. Our results suggest that incoming connectivity contributes positively to high
-cover cluster allocation for reefs around 15m deep. However, our results suggest no direct,
-first order, relationship between weighted incoming connectivity and the ability of reefs to
-maintain positive carbonate budgets under future conditions. There has been contrasting
-evidence [@bode2018; @hock2017] surrounding whether recent generation connectivity modelling
-is able to identify reefs that are important for recovery processes, with findings dependent
-on the larval connectivity model used. These investigations were performed using prior
-generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and
-1996-2002 [@bode2018] time periods, without considering the influence of reef depth on
-resilience. Using updated 1km^2^ resolution larval connectivity across the whole GBR, with a
-limited temporal sample of particle flows, our results suggest that larval connectivity
-alone may not be important or reef resilience and recovery, but should be considered in
-combination with more influential factors such as depth. Comprehensive comparisons and
-validation of multiple connectivity models, as well as use of a model ensemble, would
-improve certainty and allow for the targeting of reefs by combining abiotic factors such as
-depth with connectivity.
-
-Our findings on the importance of connectivity likely differ from literature due to the
-highly uncertain nature of larval connectivity modelling [@choukroun2025;
-@vogt-vincent2023], the way larval flows and juvenile recruitment are implemented in ADRIA -
-CoralBlox, and the magnitude of early bleaching events decreasing the breeding capacity of
-strongly connected reefs. Analysing daily connectivity data Vogt-Vincent et al.
-[-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for capturing
-the seasonal - ecological time scale connectivity between locations due to high daily
-variability in connectivity data. This is supported by the connectivity data used in our
-investigation, which have large relative standard deviations for connectivity between reefs
-over the 24 days used (@sfig-connectivity-rsd). Using alternative summarisation methods that
-capture ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
+@torres2024]. Two-way partial dependence analyses suggest that incoming and outgoing
+connectivity contribute positively to high cover cluster allocation for reefs around 15m
+deep. However, our results suggest no direct, first order, relationship between weighted
+incoming connectivity and the ability of reefs to maintain positive carbonate budgets under
+future conditions was found. There has been contrasting evidence [@bode2018; @hock2017]
+surrounding whether recent generation connectivity modelling is able to identify reefs that
+are important for recovery processes, with findings dependent on the larval connectivity
+model used. These investigations were performed using prior generations of larval
+connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time
+periods, without considering the influence of reef depth on resilience. Using updated 1km^2^
+resolution larval connectivity across the whole GBR, with a limited temporal sample of
+particle flows, it was found that larval connectivity alone may not be important or reef
+resilience and recovery, but should be considered in combination with more influential
+factors such as depth.
+
+Findings on the importance of connectivity likely differ from literature due to the highly
+uncertain nature of larval connectivity modelling [@choukroun2025; @vogt-vincent2023], the
+way larval flows and juvenile recruitment are implemented in ADRIA - CoralBlox, and the
+magnitude of early bleaching events decreasing the breeding capacity of strongly connected
+reefs. Analysing daily connectivity data Vogt-Vincent et al. [-@vogt-vincent2023] suggest
+that time-mean connectivity may not be suitable for capturing the seasonal - ecological time
+scale connectivity between locations due to high daily variability in connectivity data.
+Connectivity matrices used in this investigation have large relative standard deviations for
+larval transition probabilities between reefs over the 24 days used
+(@sfig-connectivity-rsd). Using alternative summarisation methods that capture
+ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
 connectivity [@vogt-vincent2023], future investigations may find increased importance of
@@
 GBR-scale connectivity models, including GBR1, and suggest the use of a model ensemble
-approach to estimate connectivity metrics due to the high sensitivity of connectivity to
-model specification. Further improvements and research in connectivity modelling are
-necessary when incorporating connectivity as a supplementary factor in reef resilience and
-intervention-planning analyses.
+approach to estimate larval dispersal due to the high sensitivity of connectivity
+predictions to model specification. Further improvements and research in connectivity
+modelling are necessary when incorporating connectivity as a supplementary factor in reef
+resilience and intervention-planning analyses.
 
@@
 High reef clusters in cover time series are most notable under these two GCMs
-(@stbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into the future
+(@fig-gcm-cover-trajectories; @stbl-cluster-cid). Maintenance of coral cover into the future
 is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of future
@@
 
-The large differences in cover time series seen across the GCMs suggest that it is important
-to consider uncertainty in future conditions when assessing possible biological responses to
+Large differences in cover time series seen across the GCMs suggest it is important to
+consider uncertainty in future conditions when assessing possible biological responses to
 change. This is supported by recent literature suggesting an effective approach to capturing
@@
 
-Given the above, reef managers may consider the potential for positive flow-on effects due
-to outgoing connectivity when selecting intervention sites. The necessary connectivity data,
-however, must first be available to provide a sufficient degree of confidence to support
-such site selection decisions (compare the ongoing discussion in [-@mumby2018] and
-[-@bode2018]). Given connectivity is a transient, and much more difficult, property to
-measure that is subject to comparatively higher sources of uncertainty, depth may be a more
-reliable indicator of long-term resilience, particularly where no further information is
-available.
+Reef managers may consider the potential for positive flow-on effects due to outgoing
+connectivity when selecting intervention sites. The necessary connectivity data, however,
+must first be available to provide a sufficient degree of confidence to support such site
+selection decisions (compare the ongoing discussion in Mumby et al. [-@mumby2018], Bode et
+al. [-@bode2018] and Choukroun et al. [-@choukroun2025]). Given connectivity is a transient,
+and much more difficult, property to measure that is subject to comparatively higher sources
+of uncertainty, depth may be a more reliable indicator of long-term resilience, particularly
+where no further information is available.
 

### 2025-10-05 paper/paper_draft.qmd
Updates to PDA/carbonate budget results sections

@@
 series DHW level have the highest feature importance scores, accounting for 29%, 15% and 15%
-predictive importance respectively (@fig-ts-cluster-pdp; Panel A). Area weighted incoming
-connectivity, outgoing connectivity strength, source-to-sink connectivity ratio and larval
-retention probability account for \~12%, 11%, 10% and 8% respectively.
+predictive importance respectively (@fig-ts-cluster-pdp; Panel A). Source-cover weighted
+incoming connectivity, outgoing connectivity strength, source-to-sink connectivity ratio and
+larval retention probability account for \~12%, 11%, 10% and 8% respectively.
 
@@
 Dependence Plots (PDPs) for reef characteristics of interest indicating the probability of a
-reef being classified to one of the three cover clusters (Panel B). Partial Dependence Plots
-for bioregions were excluded as they were found to be uninformative. PDPs indicate the
+reef being classified to one of the three cover clusters (Panel B). PDPs indicate the
 probability of a reef from the test dataset being clustered into each cover cluster
@@
 Medium and High clusters respectively. Transparent grey points above probability lines
-represent the predictor values present in the test dataset, providing a rough indication of
-predictor value distribution across
+represent predictor values present in the test dataset, providing a rough indication of
+predictor value distribution across assessed
 reefs.](../figs/ts_cluster_rf_feature_analysis.png){#fig-ts-cluster-pdp fig-align="center"
@@
 
-First-order partial dependence analysis showed minimal influence of incoming, outgoing and
-source-to-sink ratio connectivity metrics on cluster assignment probabilities. Two-way
-analyses revealed little interaction between depth and incoming and outgoing connectivity
-metrics for reef clustering probabilities (@fig-ts-cluster-pdp-twoway-incoming;
-@sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a median depth around 15m and high
-incoming connectivity may benefit slightly, with higher probability of High cover cluster
-assignment compared to 15m - depth reefs with lower connectivity.
+First-order PDA showed minimal influence of incoming, outgoing and source-to-sink ratio
+connectivity metrics on cluster assignment probabilities. Two-way analyses revealed little
+interaction between depth and incoming and outgoing connectivity metrics for reef clustering
+probabilities (@fig-ts-cluster-pdp-twoway-incoming; @sfig-ts-cluster-pdp-twoway-outgoing).
+Reefs with a median depth around 15m and high incoming connectivity may benefit slightly,
+with higher probability of High cover cluster assignment compared to 15m - depth reefs with
+lower connectivity.
 
@@
 aligns with the right-skewed distribution of carrying capacity across reefs for these three
-predictor variables. Beyond this low-end range, the partial dependence becomes near
-constant, indicating that outlier values for these factors are not influential. Assessing
-random forest prediction accuracy across bioregions, reveals increasing performance as
-bioregion mean reef depth increases (@sfig-rf-predictor-perf). This highlights that
-unexplained variation in the test dataset (33% of variation) may be concentrated in shallow
-bioregions where the available model predictors do not capture differences between clustered
-reefs.
+predictor variables. Beyond this low-end range, partial dependence becomes near constant,
+indicating outlier values for these factors are not influential. Assessing random forest
+prediction accuracy across bioregions, reveals increasing performance as mean bioregion reef
+depth increases (@sfig-rf-predictor-perf). This highlights that unexplained variation in the
+test dataset (33% of variation) may be concentrated in shallow bioregions where available
+model predictors do not capture differences between clustered reefs.
 
@@
 that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
-@sfig-access-esm1-5-mean-carb-budget; @sfig-access-esm1-5-carb-budget-corr). Unsurprisingly,
+@sfig-access-esm1-5-carb-budget-corr; @sfig-access-esm1-5-mean-carb-budget). Unsurprisingly,
 the number of years above $\theta_0$ substantially decreased as $\theta_0$ is increased, as
@@
 of coral cover ($\theta_0$) between 2025 to 2075 (y-axis) under ACCESS-ESM1-5. Left panel
-shows relationship between reef median depth, while the right panel shows the same for
-log10-weighted incoming connectivity values. Point colour (purple to yellow) represents
-($\theta_0$), with brighter shades indicating a higher $\theta_0$. Deeper reefs have
+shows the relationship between reef median depth, while the right panel shows the same for
+log10-weighted incoming connectivity. Point colour (purple to yellow) represents
+($\theta_0$), with brighter shades indicating a higher $\theta_0$. Deeper reefs have an
 increased number of years above the considered range of $\theta_0$, while no relationship

### 2025-10-05 paper/paper_draft.qmd
Updates to rest of results section

@@
 There were substantial differences in the maintenance of coral cover post 2030 between the
-GCMs. Figure [-@fig-gcm-cover-trajectories] illustrates the temporal behaviour of reefs
-across clusters (Low, Medium and High). Of the GCMs explored, NorESM2-MM had the lowest
-Equilibrium Climate Sensitivity (2.5°C) and reefs exhibit continuing recovery and decline
+GCMs (@fig-gcm-cover-trajectories). Of the GCMs explored, NorESM2-MM had the lowest
+ECS (2.5°C) and reefs exhibit continuing recovery and decline
 dynamics up to 2075 under this hypothetical climate future. Unsurprisingly, recovery phases
@@
 in coral cover were visible in simulated results up to 2045. Under NorESM2-MM, the Far
-Northern Management area were found to have the most similar temporal behaviour between Low
+Northern Management area was found to have the most similar temporal behaviour between Low
 and High clusters compared to other Management areas (@stbl-cluster-cid) due to the low
@@
 GCMs - specifically, ACCESS-CM2 (4.66°C), EC-Earth3-Veg (4.30°C) and GFDL-CM4 (4.1°C) - all
-reefs are largely in decline across all management areas from 2055 (@stbl-cluster-cid).
-
-![Time series of coral cover (relative to reef area) categorised within each Management area
-(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. The
-time series were clustered into "Low" (green), "Medium" (orange), and "High" (blue) clusters
-indicating their relative median coral cover. Solid lines represent the cluster median time
-series and bands represent the 95th percentile confidence
+reefs are largely in decline across all management areas from 2035 (@stbl-cluster-cid).
+
+![Time series of coral cover (relative to reef area) clustered within each Management area
+(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. Time series were clustered into "Low" (green), "Medium" (orange), and "High" (blue) clusters
+indicating their relative median coral cover. Solid lines represent cluster median time
+series and bands represent 95th percentile confidence
 intervals.](../figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
@@
 reefs, 23% are within the Far Northern Management area, with 1%, 55% and 21% occurring in
-the Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas
+Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas
 respectively (@sfig-gcm-cluster-map). Of the 462 consistently assigned reefs, 34%, 18% and
@@
 
-In contrast to the broad temporal behaviour at the Management area scale, the relationship
-between reef characteristics and assigned clusters were found to be similar at the bioregion
-scale across GCMs. Across bioregions, reefs in the High cluster not only had greater levels
+Relationships between reef characteristics and bioregion-scale time series clusters were found to be similar across GCMs. Across bioregions, reefs in the High cluster not only had greater levels
 of coral recovery but displayed persistence to 2050

### 2025-10-05 paper/paper_draft.qmd
Updates to methods section

@@
 The spatial extent of reefs represented in this investigation follows reef definitions
-available via the Great Barrier Reef Marine Park Authority (GBRMPA) [@GBRMPA2022]. The reef
-definitions define 3806 reefs across the GBR. An indicative map of the GBR marine park
-including the Marine Park Management areas [@GBRMPA2007] and the corresponding bioregion for
-each reef is shown in [@fig-region-map] [@GBRMPA2024]. Estimates of coral carrying capacity
-for each reef were taken from prior analyses undertaken in Bozec et al. [-@bozec2022].
-
-Depth characteristics for each reef were extracted using 10m resolution bathymetry data made
-available in GBRMPA [-@GBRMPA2020]. While the bathymetry data adopted for the given
-assessment are said to be accurate up to 15m from Mean Sea Level [@GBRMPA2020], there are
-many sources of uncertainty in the depth estimates used for this study. Notably, the adopted
-depth estimates were derived from bathymetries based on satellite imagery. The bathymetry
+available via the Great Barrier Reef Marine Park Authority (GBRMPA), defining 3806 reefs
+across the GBR [@GBRMPA2022] (@fig-region-map). Estimates of coral carrying capacity for
+each reef were taken from prior analyses [@bozec2022].
+
+Depths for each reef were extracted using 10m resolution bathymetry data made available in
+GBRMPA [-@GBRMPA2020]. While the bathymetry data are said to be accurate up to 15m from Mean
+Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used
+for this study. Notably, bathymetry data were derived from satellite imagery. The bathymetry
 data can be limited in their alignment with the established GBRMPA reef outlines used to
 characterise reef locations and their areal extent. For each reef, bathymetry data were
-spatially matched with the 3806 reef outlines through geometric intersections.
+spatially matched with the 3806 reef outlines through geometric intersections. All depth
+values were converted to positive values (depths below sea level). The median depth was used
+to provide an indicative depth value for each reef. Further limitations are outlined in the
+Discussion. Code to extract depth estimates, and the resulting depth estimates themselves,
+are available at [@iwanaga2025].
 
@@
 3806 reefs. Furthermore, reefs that are not associated with GBRMPA Management areas
-[@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were also removed from the investigation.
-Bioregions which contained fewer than three reefs after these processes were also excluded.
-As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining. All depth
-values were converted to positive values (depths below sea level). The median depth was used
-to provide an indicative depth value for each reef. Further limitations are outlined in the
-Discussion. Code to extract depth estimates, and the resulting depth estimates themselves,
-are available at [@iwanaga2025]. To ensure effective data analysis, reefs with incoming or
-outgoing connectivity values below the 5th percentile were removed from post-hoc analyses,
-leaving 2197 reefs remaining for display in results.
+[@GBRMPA2007] or reefal bioregions [@GBRMPA2024] were removed. Bioregions which contained
+fewer than three reefs after these processes were also excluded. As a result, 1377 reefs
+were excluded, leaving a total of 2429 remaining for time series clustering. To ensure
+effective data analysis, reefs with incoming or outgoing connectivity values below the 5th
+percentile were removed from post-hoc analyses, leaving 2197 reefs remaining for display in
+results (@fig-region-map).
 
 ![Map of the Great Barrier Reef region, including GBRMPA Management areas (polygons) and all
-considered reefs (points). Colour-coded polygons outline GBR marine park management regions,
-where orange represents the Far Northern management region, green represents
-Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers Mackay/Capricorn
-[@GBRMPA2007]. Reef centroids are marked individually for visual clarity and are coloured
-according to its bioregion [@GBRMPA2024]. All 2197 reefs included in this investigation are
-represented in this figure. Annotations represent major coastal settlements along the
-GBR.](../figs/region_map.png){#fig-region-map fig-align="center" width="14.8cm"}
+considered reefs (points). Colour-coded polygons outline GBR marine park management regions:
+Far Northern (orange), Cairns-Cooktown (green), Townsville-Whitsunday (blue) and
+Mackay-Capricorn (red) [@GBRMPA2007]. Reef centroids are marked individually for visual
+clarity and are coloured by bioregions [@GBRMPA2024]. All 2197 reefs included in this
+investigation are represented in this figure. Annotations represent major coastal
+settlements along the GBR.](../figs/region_map.png){#fig-region-map fig-align="center"
+width="14.8cm"}
 
@@
 Sixth Phase of the Coupled Model Intercomparison Project (CMIP6), spanning four 'model
-development families' as defined by Brunner et al., [-@brunner2020].
+development families' as defined by Brunner et al., [-@brunner2020]. Shared Socio-economic
+Pathway (SSP) 2-4.5 was used to represent the plausible emission pathway. It represents a
+moderate emissions scenario with continued CO~2~ emissions comparable to present day until
+2050, after which emissions gradually decline [@hausfather2020; IPCC -@climate2023].
 
@@
 defines ECS as the long-term warming caused by a doubling of carbon dioxide above its
-pre-industrial concentration [@forster2021]. While this assessment does not consider oceanic
-data, Grose et al. [-@grose2023] provide a region-specific selection mechanism which we use
-as an indicator of general performance of GCMs for the region. An overview of the selected
-GCMs is provided in @tbl-gcms. Note here that Grose et al., [-@grose2023] assessed
-GFDL-ESM4, whereas Dixon et al., [-@dixon2022; -@dixon2023] provides data based on GFDL-CM4.
-This substitution is assumed appropriate given they share the same fundamental
-representation of the physical climate system.
-
-Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission
-pathway. It represents a moderate emissions scenario with continued CO~2~ emissions
-comparable to present day until 2050, after which emissions gradually decline
-[@hausfather2020; IPCC -@climate2023]. The selected GCMs represent 2.5°C to 4.66°C of global
-atmospheric warming in the 2081-2100 period relative to 1850-1900. The use of these GCMs
-therefore allow for a range of possible climate futures to be explored, capturing
-uncertainty in future responses to CO~2~ increases (@sfig-ecs; @fig-methods-dhws;
-[@grose2023; @shepherd2018]) and enables the assessment of modelled coral reef behaviour
-over a broad range of independently derived climate futures [@abramowitz2019; @brunner2020].
+pre-industrial concentration [@forster2021]. While Grose et al. [-@grose2023] do not
+consider oceanic data, they provide a region-specific selection mechanism which is used as
+an indicator of general performance of GCMs for the region. An overview of the selected GCMs
+is provided in @tbl-gcms. Note here that Grose et al., [-@grose2023] assessed GFDL-ESM4,
+whereas Dixon et al., [-@dixon2022; -@dixon2023] provides data based on GFDL-CM4. This
+substitution is assumed appropriate given they share the same fundamental representation of
+the physical climate system. The use of these GCMs therefore allows for a range of possible
+futures to be explored, capturing uncertainty in future responses to CO~2~ increases
+(@fig-methods-dhws; @sfig-ecs;[@grose2023; @shepherd2018]) and enables the assessment of
+modelled coral reef behaviour over a broad range of independently derived climate futures
+[@abramowitz2019; @brunner2020].
 
@@
 Additional information about DHW calculation methods is provided in the supplemental
-material. DHW values on a per-pixel basis at 1km^2^ resolution were then calculated as the
+material. DHW values on a per-pixel basis at 1km^2^ resolution were calculated as the
 12-week rolling sum of HotSpot SST Anomaly values that are greater than 1°C, expressed in
@@
 GCM results are found. GCMs in context with assessed plausible ranges of ECS values are
-displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the
-very-likely ECS range and was taken as an intermediate model with results displayed in the
-main text.
+displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the likely ECS
+range and was taken as an intermediate model with results displayed in the main text.
 :::
@@
 ![Degree Heating Week time series (in °C - Weeks) for the GCMs selected. Colours represent
-the different Management areas across the Great Barrier Reef. Green represents
-Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
-represents the Townsville-Whitsunday Management area. Solid lines represent the
-management-area median time series and bands represent the 95th percentile confidence
-intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws fig-align="center"
-width="14.82cm"}
+the different Management areas across the Great Barrier Reef: Far Northern (orange),
+Cairns-Cooktown (green), Townsville-Whitsunday (blue) and Mackay-Capricorn (red). Solid
+lines represent management-area median time series and bands represent 95th percentile
+confidence intervals.](../figs/methods_dhw_timeseries.png){#fig-methods-dhws
+fig-align="center" width="14.82cm"}
 
@@
 characteristic of complex environmental systems [@lempert2010; @lempert2013] in an attempt
-to address limitations of calibrated ecosystem models with a singular set of parameter
+to address limitations of calibrated ecosystem models that use a singular set of parameter
 values [@lubianabotelho2025]. Exploratory scenario modelling is a core methodology
 underpinning the development of robust and adaptive management strategies [@haasnoot2013].
-
-Rather than attempting to forecast precise outcomes, the exploratory approach aims to
-systematically search many possible futures to identify patterns that lead to outcomes of
-interest. The approach allows for the identification of robust management strategies that
-perform well across a diversity of future conditions rather than attempting to identify a
-single most optimal strategy. Concurrently, assessing the wide swathe of scenarios allows
-contextual understanding of the conditions in which strategies may fail. Multiple
-interacting and compounding sources of uncertainty, and a lack of broad agreement as to
-their likelihood, create inherently uncertain outcomes. Here, exploratory modelling was
-applied to identify the environmental and reef characteristics, such as thermal stress,
-depth, and connectivity, that support favourable outcomes in reef recovery and resilience.
 
@@
 
-Larval transition probability matrices were generated using the EReefs Great Barrier Reef
-1km resolution hydrodynamic model and particle tracking simulations. Connectivity data from
-24 days in total were used in this investigation to estimate coral larval flows. These data
-span six years from 2015 to 2020. The years 2015, 2016, 2018 and 2019 are each represented
-by connectivity matrices covering spawning periods over three days in each year (12 days in
-total), while 2017 and 2020 are each represented by six spawning days each, coming to a
-total of 24 days of connectivity matrices. The values in these matrices indicate the
-probability of larval transfer between each pair of reefs in the GBR, herein referred to as
-connectivity strengths. Indicative connectivity strengths are implemented in ADRIA-CoralBlox
-as the mean of all available data for each location (i.e., mean of all 24 spawning days).
-While the connectivity strengths do not vary temporally within each ADRIA-CoralBlox
-simulation, they do vary between reefs. This spatial variability enables investigations into
-the influence of connectivity strength and its role in driving recovery processes.
-
-To assess the impact of reef connectivity on modelled outcomes we summarise incoming
-connectivity (weighted incoming connectivity), outgoing connectivity (outgoing connection
-strength), the ratio of source-to-sink connectivity, and larval retention probability for
-each reef. Weighted incoming connectivity is calculated by summing the product of each
-connection strength incoming to a target reef (excluding retained larvae from the target
-reef) and the mean timeseries absolute coral cover (km^2^) of each matching source reef.
-This metric provides an approximation of overall larval flow into a reef, with high values
-indicating the target reef is supplied high volumes of larvae via strong connections and low
-values indicating the target reef has weak (or no) incoming connections or is supplied by
-small source populations. A limitation of weighted incoming connectivity is that it does not
-incorporate the proportion of the source reef's population that is reproducing and producing
-larvae, instead taking the total coral cover area as an indicator of larval productivity.
-Outgoing connection strength is calculated as the sum of all outgoing transition
-probabilities from a target reef. Outgoing connection strength has a theoretical maximum of
-one (all larvae reach settlement on sink reefs), however the large size of the GBR combined
-with larval mortality considerations result in outgoing connection strength values much
-lower than one. The ratio of source-to-sink connectivity ($O:I$) for a target reef
-represents the strength of the reef's outgoing larval flow relative to it's incoming larval
-flow. This is calculated as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum
-of connectivity probabilities, $N$ represents the number of connections, $O$ denotes
-outgoing connectivity from the target reef and $I$ denotes incoming connectivity to the
-target reef. If a reef has no incoming connections, the $O:I$ equals the $S_O/N_O$ value.
-Incoming connections in this calculation, do not directly represent the larval supply gained
-as the breeding populations from which connections are coming from are not represented. A
-source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef
-has greater outgoing than incoming larval flow. Reef larval retention probability indicates
-the proportion of spawned larvae from a target reef that remain to settlement.
+The coral larval connectivity model used in this study comprises 3D hourly velocities from
+the 1 km grid resolution hydrodynamic model (GBR-1 version 2.0) [@steven2019], as input to
+OceanParcels [@delandmeter2019], a particle tracking model. The connectivity model was used
+to simulate larval dispersal and settlement of broadcast-spawning Acropora corals in the
+GBR, following annual mass spawning events in 2015, 2016, 2018, 2019 and split-spawning
+events in 2017 and 2020. Split spawning occurs when the annual reproductive event of a coral
+population is split over two consecutive months. Coral mass spawning usually occurs 4-6 days
+after the full moon during the spring-summer transition in the GBR with variations across
+species and locations. The spawning days identified are: 2015 - November 30, December 1 and
+2; 2016 - November 18, 19 and 20; 2017 - November 8, 9 and 10, December 8, 9 and 10; 2018 –
+November 18, 19, 20; 2019 – November 16, 17, 18; 2020 – November 5, 6 and 7, December 4, 5,
+6.
+
+For each spawning night, particles were released from random locations within each reef
+polygon as neutrally buoyant virtual larvae every 27 seconds from 8:00 pm to 11:00 pm at
+2.25 m below the surface. In each of the reef polygons, 401 particles were released
+resulting in a total of 1,526,206 particles every night of spawning. The model was run for
+30 days with a 3-minute timestep, and the locations of the released particles were updated
+every 15 minutes until the end of the simulation. Larvae were assumed to become competent to
+settle from 4 to 28 days post release with a daily mortality rate of 0.4 [@ani2024], which
+was implemented in 15-minute timestep as probabilistic mortality, corresponding to 0.0053
+mortality rate per timestep. To incorporate the stochastic sensory behaviour of larvae
+during settlement, a 0.01 probability of settlement is assumed when larvae are over a reef
+during the competency period per 15-minute timestep. The information obtained on larvae
+settlement was used to compute a connectivity matrix among reef polygons for each spawning
+night (see Ani et al. [-@ani2024] for more details). A total of 24 connectivity matrices
+were generated for the spawning nights that were considered.
+
+Larval transition matrices indicate the probability of larval transfer between pairs of
+reefs in the GBR, herein referred to as connectivity strengths. Indicative connectivity
+strengths are implemented in ADRIA-CoralBlox as the mean of matrices for each location
+(i.e., mean of all 24 spawning days). While the connectivity strengths do not vary
+temporally within each ADRIA-CoralBlox simulation, spatial variability enables
+investigations into the influence of connectivity strength and its role in driving recovery
+processes.
+
+To assess the impact of reef connectivity on modelled outcomes, connectivity was summarised
+by incoming connectivity (weighted incoming connectivity), outgoing connectivity (outgoing
+connection strength), the ratio of source-to-sink connectivity, and larval retention
+probability for each reef. Weighted incoming connectivity was calculated by summing the
+product of each connection strength incoming to a target reef (excluding retained larvae
+from the target reef) and the mean timeseries absolute coral cover (km^2^) of each matching
+source reef. This metric provides an approximation of overall larval flow into a reef, with
+high values indicating the target reef is supplied high volumes of larvae via strong
+connections and low values indicating the target reef has weak (or no) incoming connections
+or is supplied by small source populations. A limitation of weighted incoming connectivity
+is that it does not incorporate the proportion of the source reef's population that is
+reproducing and producing larvae, instead it takes total coral cover area as an indicator of
+larval productivity. Outgoing connection strength was calculated as the sum of all outgoing
+transition probabilities from a target reef. Outgoing connection strength has a theoretical
+maximum of one (all larvae reach settlement on sink reefs), however the large size of the
+GBR combined with larval mortality result in much lower outgoing connection strength values.
+The ratio of source-to-sink connectivity ($O:I$) for a target reef represents the strength
+of the reef's outgoing larval flow relative to it's incoming larval flow. This is calculated
+as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of connectivity
+probabilities, $N$ represents the number of connections, $O$ denotes outgoing connectivity
+from the target reef and $I$ denotes incoming connectivity to the target reef. If a reef has
+no incoming connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this
+calculation, do not directly represent the larval supply gained as the breeding populations
+from which connections are coming from are not represented. A source-to-sink ratio greater
+than 1 (a value greater than 0 on a log scale) indicates a reef has greater outgoing than
+incoming larval flow. Reef larval retention probability indicates the proportion of spawned
+larvae that settle on their natal reefs.
 
@@
 
-Two separate systems were employed to explore scenarios: ADRIA (the Adaptive Dynamic Reef
-Intervention Algorithms platform) and CoralBlox. ADRIA is a multi-criteria decision support
-platform designed for the assessment and analysis of coral reef intervention strategies
-under uncertainty [@iwanaga2023]. The ADRIA platform provides functionality for scenario
-generation and analysis as well as providing the technical infrastructure to couple
-environmental and ecosystem representations. CoralBlox is a computationally efficient coral
-population model. It simulates functional/morphological groups of corals over their life
-cycles, competing for available space over time [@ribeirodealmeida2024]. The coupled
-framework is referred to as ADRIA-CoralBlox.
+Two systems were employed to explore scenarios: ADRIA (the Adaptive Dynamic Reef
+Intervention Algorithms platform) and CoralBlox, referred to as the coupled framework
+ADRIA-CoralBlox. ADRIA is a multi-criteria decision support platform designed for the
+assessment and analysis of coral reef intervention strategies under uncertainty
+[@iwanaga2023]. The ADRIA platform provides functionality for scenario generation and
+analysis as well as providing technical infrastructure to couple environmental and ecosystem
+representations. CoralBlox is a computationally efficient coral population model. It
+simulates functional/morphological groups of corals over their life cycles, competing for
+available space over time [@ribeirodealmeida2024].
 
 The coral demographic representation and associated model implementation are further
-detailed in the supplementary material. Of important note is that the representation of
-bleaching mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient
-to incorporate the amelioration effect that depth may have, following Baird et al.,
+detailed in the supplementary material. Of note is that the representation of bleaching
+mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient to
+incorporate the amelioration effect that depth may have, following Baird et al.,
 [@baird2018]. This depth-scaling reduces the proportion of coral colonies impacted by high
 heat stress as depth increases. The impacts of tropical cyclones, wave activity, Crown of
-Thorns Starfish or coral disease were not included in this investigation, in order to focus
+Thorns Starfish or coral disease were not included in this investigation in order to focus
 on assessing reef resilience under possible future warming scenarios.
@@
 compared to pseudo-random sampling. A detailed comparative analysis of sampling methods can
-be found in [@kucherenko2015]. For the purpose of scenario assessment, the resulting coral
-cover time series for each model run were scaled by the total area of each reef to represent
-cover as a percentage of the total estimated reef area. The scenario-median time series for
-each reef was used for further analyses. These time series of coral cover were then
-clustered based on their temporal behaviour. Assessment metrics used in analyses can be
-found in @stbl-metrics.
+be found in [@kucherenko2015]. For scenario assessment, coral cover time series for each
+model run were scaled to represent cover as a percentage of the total estimated reef area.
+The scenario-median time series for each reef was used for further analyses. Time series of
+coral cover were then clustered based on their temporal behaviour. Assessment metrics used
+in analyses can be found in @stbl-metrics.
 
@@
 to, for example, naively clustering by their mean coral cover. Time series clustering is
-achieved through the use of k-medoids clustering [cf. @steinmann2020]. Further details on
-the time series clustering approach are found in the supplementary materials.
+achieved using k-medoids clustering [cf. @steinmann2020]. Further details on the time series
+clustering approach are found in the supplementary materials.
 
 Time series clustering was applied over the time frame between 2025 and 2075. The clustering
-was conducted for three spatial scales: (1) the whole of GBR; (2) each GBR management area;
-and (3) for each reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). The analyses were
+was conducted at three spatial scales: (1) the whole of GBR; (2) each GBR management area;
+and (3) for each reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were
 conducted at the different spatial scales as, conceptually, the temporal behaviour
-constituting "low", "medium" or "high" coral cover may differ at the different spatial
-scales. As it was, analyses at the whole-of-GBR scale were found to lead to identical
-conclusions regarding reef characteristics which influence coral cover and so for brevity
-are not shown here.
+constituting "low", "medium" or "high" coral cover may differ at different spatial scales.
+As it was, analyses at the whole-of-GBR scale were found to lead to identical conclusions
+regarding reef characteristics which influence coral cover and so for brevity are not shown
+here.
 
@@
 
-Partial Dependence Analysis was conducted to understand the relationship between features
+Partial Dependence Analysis (PDA) was conducted to understand relationships between features
 and bioregion-scale time series cluster predictions using a Random Forest (RF) classifier
@@
 log10-weighted incoming connectivity, outgoing connectivity, and log10-transformed
-outgoing-to-incoming connectivity ratio. The full dataset consisted of the time series
-cluster assignment for each of the 2197 reefs under the five GCMs explored, for a total of
-10,985 samples. The dataset was randomly split into training (60%) and testing (40%) subsets
-to train and assess classification performance. The RF classifier achieved 80% accuracy on
-the training set and 60% on the test set.
+outgoing-to-incoming connectivity ratio. Conceptually, PDA is related to a Regional
+Sensitivity Analysis [@hornberger1981; @pianosi2016], as model results are assessed to map
+the influence of X - the predictors or model factors - on Y - the modelled outcomes
+according to a metric of interest.
+
+The full dataset consisted of the time series cluster assignment for each of the 2197 reefs
+under the each GCM (totalling 10,985 samples). The dataset was randomly split into training
+(60%) and testing (40%) subsets to train and assess classification performance. The RF
+classifier achieved 80% accuracy on the training set and 60% on the test set.
 
@@
 cross-validation demonstrates the generalised performance of the RF classifier, while not
-accurate, was deemed sufficiently informative for the purpose of assessing the influence of
+accurate, is still sufficiently informative for the purpose of assessing the influence of
 reef characteristics.
@@
 for all three cluster classes using the trained RF classifier, and (3) the mean predicted
-probability for each class across all test observations. Use of the median predicted
-probability was also assessed but was found not to substantially influence the
-interpretation of results (and so are not shown here). The process isolates the marginal
+probability for each class across all test observations. The process isolates the marginal
 effect of each predictor by averaging over the natural distribution of all other
 representative reef characteristics in the test dataset. Additionally, to assess possible
-interaction between reef depth and connectivity metrics, two-way partial dependence analysis
-was performed on grids along the ranges of depth and weighted incoming connectivity, and
-depth and outgoing connection strength.
+interaction between reef depth and connectivity metrics, two-way PDA was performed on grids
+along the ranges of depth and weighted incoming connectivity, and depth and outgoing
+connection strength.
 
@@
 
-Using coral cover time series for each reef we calculated the number of years each reef
-maintains coral cover above a given percent threshold. The threshold represents the level of
+Using coral cover time series for each reef, the number of years each reef maintains coral
+cover above a given percent threshold were calculated. The threshold represents the level of
 live coral cover necessary to maintain a positive carbonate budget (denoted here as
-$\theta_{0}$ to indicate the budget equilibrium). Greater number of years above $\theta_{0}$
-suggests greater resilience and opportunity for recovery.
+$\theta_{0}$ to indicate the budget equilibrium). A greater number of years above
+$\theta_{0}$ suggests greater resilience and opportunity for recovery.
 
 Recent analyses suggest a general threshold of \~17% live coral cover in the case of the
-mid-shelf and offshore GBR reefs [@desbiens2021]. Given in situ carbonate budgets are
+mid-shelf and offshore GBR reefs [@desbiens2021]. Given in-situ carbonate budgets are
 influenced by (1) a range of processes; (2) the variety of approaches that could be used to
@@
 The relationships between the number of years above $\theta_{0}$ and characteristics such as
-median reef depth and log10 total connectivity strength were then assessed with Spearman's
-rank correlation. Spearman's correlation coefficient was adopted as reef depth and
-connectivity strength distributions are expected to be non-normal and highly skewed.
-Furthermore, reefs are naturally of different types and experience different conditions, and
-so the monotonic trends (whether the relationship consistently increase or decrease) rather
-than the exact quantitative relationship was of interest for this analysis.
+median reef depth and log10 total connectivity strength were assessed with Spearman's rank
+correlation. Spearman's correlation was adopted as distributions of reef depths and number
+of years above $\theta_{0}$ were expected to be non-normal and highly skewed. Furthermore,
+reefs are naturally of different types and experience different conditions, and so the
+monotonic trends (whether the relationship consistently increase or decrease) rather than
+the exact quantitative relationship was of interest.
 
@@
 There were substantial differences in the maintenance of coral cover post 2030 between the
-GCMs (@fig-gcm-cover-trajectories). Of the GCMs explored, NorESM2-MM had the lowest
-ECS (2.5°C) and reefs exhibit continuing recovery and decline
-dynamics up to 2075 under this hypothetical climate future. Unsurprisingly, recovery phases
-were predominantly seen in the reefs in the High cover cluster, with Medium and Low
-exhibiting lesser probability of such periods of recovery. Generally, recovery and increases
-in coral cover were visible in simulated results up to 2045. Under NorESM2-MM, the Far
-Northern Management area was found to have the most similar temporal behaviour between Low
-and High clusters compared to other Management areas (@stbl-cluster-cid) due to the low
-degree of coral cover overall (@fig-gcm-cover-trajectories).
+GCMs (@fig-gcm-cover-trajectories). Of the GCMs explored, NorESM2-MM had the lowest ECS
+(2.5°C) and reefs exhibit continuing recovery and decline dynamics up to 2075 under this
+hypothetical climate future. Unsurprisingly, recovery phases were predominantly seen in the
+reefs in the High cover cluster, with Medium and Low exhibiting lesser probability of such
+periods of recovery. Generally, recovery and increases in coral cover were visible in
+simulated results up to 2045. Under NorESM2-MM, the Far Northern Management area was found
+to have the most similar temporal behaviour between Low and High clusters compared to other
+Management areas (@stbl-cluster-cid) due to the low degree of coral cover overall
+(@fig-gcm-cover-trajectories).
 
@@
 ![Time series of coral cover (relative to reef area) clustered within each Management area
-(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. Time series were clustered into "Low" (green), "Medium" (orange), and "High" (blue) clusters
+(rows), for each GCM analysed (columns) based on temporal behaviour over 2030 and 2060. Time
+series were clustered into "Low" (green), "Medium" (orange), and "High" (blue) clusters
 indicating their relative median coral cover. Solid lines represent cluster median time
@@
 reefs, 23% are within the Far Northern Management area, with 1%, 55% and 21% occurring in
-Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas
-respectively (@sfig-gcm-cluster-map). Of the 462 consistently assigned reefs, 34%, 18% and
-47% are clustered into Low, Medium and High clusters respectively. High levels of assignment
+Cairns-Cooktown, Townsville-Whitsunday and Mackay-Capricorn Management areas respectively
+(@sfig-gcm-cluster-map). Of the 462 consistently assigned reefs, 34%, 18% and 47% are
+clustered into Low, Medium and High clusters respectively. High levels of assignment
 variability across GCMs are expected as due to spatial differences in each given GCM’s DHW
@@
 
-Relationships between reef characteristics and bioregion-scale time series clusters were found to be similar across GCMs. Across bioregions, reefs in the High cluster not only had greater levels
-of coral recovery but displayed persistence to 2050
+Relationships between reef characteristics and bioregion-scale time series clusters were
+found to be similar across GCMs. Across bioregions, reefs in the High cluster not only had
+greater levels of coral recovery but displayed persistence to 2050
 (@sfig-access-esm1-5-bioregion-timeseries). Qualitative representations of bioregion scale

### 2025-10-05 paper/paper_draft.qmd
Updates to introduction and abstract

@@
     Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities,
-    we analysed reef coral cover time series and the ability of reefs to maintain positive carbonate
+    reefs were analysed for reef coral cover time series and their ability of reefs to maintain positive carbonate
     production budgets under future conditions. Contrary to expectations, larval connectivity
@@
     refugia that reduce bleaching impacts. Interaction between reef depth and incoming
-    connectivity was found to influence reef temporal behaviour at 15m depth. Our findings suggest that
+    connectivity was found to influence reef temporal behaviour at 15m depth. These findings suggest that
     depth provides critical protection against thermal stress, with high incoming connectivity enhancing the
@@
 Third, the maintenance, and accretion, of the carbonate framework that provides reef
-structure [@perry2012]. We aim to assess how these mechanisms interact under projected
-climate conditions to identify the characteristics of resilient reefs through scenario-based
-coral population modelling for the Great Barrier Reef ecosystem.
-
-The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of
-thousands of individual reefs interconnected through larval dispersal patterns mediated by
-hydrodynamic, spatial, and ecological processes [@cappo2000]. The GBR faces severe projected
-coral cover declines under climate change [@bozec2025; @bozec2022; @condie2021]. Coral cover
-declines will be compounded by ocean acidification, tropical cyclones, and crown-of-thorns
-starfish outbreaks [@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011;
-@wolff2018]. The 2023-24 Summer mass bleaching event may be signalling a shift towards this
-reef future, with some level of bleaching recorded on 79% of surveyed reefs (total 1001
-surveyed reefs) [@australianinstituteofmarinescience2024; @cantin2024].
+structure [@perry2012]. This investigation aims to assess how these mechanisms interact
+under projected climate conditions to identify the characteristics of resilient reefs in the
+Great Barrier Reef (GBR) ecosystem.
+
+The GBR is the world's largest coral reef ecosystem consisting of thousands of individual
+reefs interconnected through larval dispersal patterns mediated by hydrodynamic, spatial,
+and ecological processes [@cappo2000]. The GBR faces severe projected coral cover declines
+under climate change [@bozec2025; @bozec2022; @condie2021]. Coral cover declines will be
+compounded by ocean acidification, tropical cyclones, and crown-of-thorns starfish outbreaks
+[@death2012; @fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24
+Summer mass bleaching event may be signalling a shift towards this reef future, with some
+level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
+[@australianinstituteofmarinescience2024; @cantin2024].
 
 At the individual coral scale, survival during thermal stress events depends on both
-environmental and biological factors. Environmental factors can either amplify or reduce
-thermal stress exposure. Depth is a crucial factor that can provide a refuge from thermal
-stress [@álvarez-noriega2018; @baird2018; @smith2014]. Biological factors including coral
-size [@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and thermal tolerance
-through acclimation and inheritance [@humanes2022; @lachs2024] all influence survival
-outcomes. Importantly, corals demonstrate adaptive capacity to develop thermal tolerance
-that could delay widespread bleaching under moderate emission scenarios [@bairos-novak2021;
-@humanes2022], representing a crucial mechanism for reef persistence.
+environmental and biological factors that can either amplify or reduce thermal stress. Depth
+is a crucial factor that can provide a refuge from thermal stress [@álvarez-noriega2018;
+@baird2018; @smith2014]. Biological factors including coral size [@brandt2009], taxa
+[@álvarez-noriega2018; @mcclanahan2005], and thermal tolerance through acclimation and
+inheritance [@humanes2022; @lachs2024] all influence survival outcomes. Corals demonstrate
+adaptive capacity to develop thermal tolerance that could delay widespread bleaching under
+moderate emission scenarios [@bairos-novak2021; @humanes2022], representing a crucial
+mechanism for reef persistence.
 
 Beyond individual survival, reef-scale resilience depends on connectivity networks that
-enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017]. However,
-connectivity creates both strengths and vulnerabilities. Larval source populations that
-export more larvae than they import are essential for system-wide recovery, providing larvae
-that enable recolonization at distant locations [@hock2017; @thomas2015]. Yet these source
-reefs are paradoxically more vulnerable individually, relying heavily on local recruitment
-for their own recovery. When disturbances impact major source populations, cascading effects
-reduce larval export and slow recovery throughout the connected network [@figueiredo2022;
-@hock2017; @munday2009].
+enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017]. Larval
+source populations that export more larvae than they import are essential for system-wide
+recovery, providing larvae that enable recolonization at distant locations [@hock2017;
+@thomas2015]. Yet these source reefs are paradoxically more vulnerable individually, relying
+heavily on local recruitment for their own recovery. When disturbances impact major source
+populations, cascading effects reduce larval export and slow recovery throughout the
+connected network [@figueiredo2022; @hock2017; @munday2009].
 
 Long-term reef viability requires not only coral survival and recolonization, but also
-maintenance of the physical reef structure through positive carbonate budgets. Scleractinian
+maintenance of physical reef structures through positive carbonate budgets. Scleractinian
 corals build the primary habitat framework, but reef persistence depends on the balance
@@
 
-Recent advances in whole-ecosystem larval connectivity modelling **\[Insert GBR1
-connectivity citation.\]** and coral thermal response research [@bairos-novak2021] enable
-integrated investigation of how multiple factors interact to determine climate resilience.
-By incorporating the latest coral population models [@ribeirodealmeida2024], ecosystem-wide
-connectivity data, and updated climate projections [@dixon2022], we can examine which
-factors most strongly influence reef persistence under different scenarios. While
-connectivity has been emphasized as critical for GBR resilience [@hock2017], and remains an
-important consideration, our integrated modelling reveals depth plays a fundamental role in
-determining maintenance of reef coral populations and positive carbonate budgets under
-current projections of climate change.
+Recent advances in whole-ecosystem larval connectivity modelling [@choukroun2025] and coral
+thermal response research [@bairos-novak2021] enable integrated investigation of how
+multiple factors interact to determine climate resilience. By incorporating the latest coral
+population models [@ribeirodealmeida2024], ecosystem-wide connectivity data, and updated
+climate projections [@dixon2022], we can examine which factors most strongly influence reef
+persistence under different scenarios. While connectivity has been emphasized as critical
+for GBR resilience [@hock2017], and remains an important consideration, integrated modelling
+reveals depth plays a fundamental role for maintenance of reef coral populations and
+positive carbonate budgets under current projections of climate change.
 

### 2025-10-07 paper/paper_draft.qmd
Updates for acknowledgements section

@@
 
-The authors acknowledge the Bindal people, Traditional Owners of the land on which the work
-took place at the AIMS Townsville site. The authors acknowledge the contributions of Barbara
-Robson and Jessica Benthuysen to manuscript preparation. This research was funded by the
-Reef Restoration and Adaptation Program, and facilitated by the Australian Institute of
-Marine Science. The authors acknowledge thermal projection data sourced from
-HighResCoralStress datasets, model parameterisation data sourced from the Ecological
-Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition probability data
-derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data available from
-the Great Barrier Reef Marine Park Authority. The eReefs Project is a private-public
-collabroation between Australia's leading operational and scientific research agencies,
-government and corporate Australia. All authors are funded by the Reef Restoration and
-Adaptation Program **\[BG: To be completed.\]**.
+The authors acknowledge the Traditional Owners of the Sea Country on which the modelling was
+conducted for. The authors additionally acknowledge the Bindal, Jagera, and Ngunnawal
+Peoples on which the authors conducted the model development, analysis and writing. The
+authors acknowledge the contributions of Barbara Robson and Jessica Benthuysen for comments
+provided early in the manuscript preparation. The authors would like to additionally
+acknowledge and thank Shaun Wilson and Juan Carlos Ortiz for discussions around carbonate
+budget thresholds.
+
+This research was funded by the Reef Restoration and Adaptation Program and facilitated by
+the Australian Institute of Marine Science. The authors acknowledge thermal projection data
+sourced from HighResCoralStress datasets, model parameterisation data sourced from the
+Ecological Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition
+probability data derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data
+available from the Great Barrier Reef Marine Park Authority. The eReefs Project is a
+public-private collaboration between Australia’s leading operational and scientific research
+agencies, government, and corporate Australia.
 

### 2025-10-08 paper/paper_draft.qmd
Fix malformed sentence in acknowledgements

@@
 conducted for. The authors additionally acknowledge the Bindal, Jagera, and Ngunnawal
-Peoples on which the authors conducted the model development, analysis and writing. The
-authors acknowledge the contributions of Barbara Robson and Jessica Benthuysen for comments
-provided early in the manuscript preparation. The authors would like to additionally
-acknowledge and thank Shaun Wilson and Juan Carlos Ortiz for discussions around carbonate
-budget thresholds.
+Peoples, the lands on which the authors conducted the model development, analysis, and
+writing. The authors also acknowledge the contributions of Barbara Robson and Jessica
+Benthuysen for comments provided early in the manuscript preparation. The authors would like
+to additionally acknowledge and thank Shaun Wilson and Juan Carlos Ortiz for discussions
+around carbonate budget thresholds.
 

### 2025-10-08 paper/paper_draft.qmd
Updates to messaging of depth-connectivity interaction.

@@
 abstract: |
-    Coral reefs globally face unprecedented threats from climate change, with the Great Barrier
-    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral
-    cover from thermal stress events.
-    Understanding drivers behind reef resilience to climate impacts is critical for conservation
-    planning and intervention strategies. A scenario-based population modelling approach was
-    adopted with larval connectivity dynamics, thermal adaptation, and environmental factors
-    to assess coral reef resilience across GBR locations under future climate projections.
-    Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities,
-    reefs were analysed for reef coral cover time series and their ability of reefs to maintain positive carbonate
-    production budgets under future conditions. Contrary to expectations, larval connectivity
-    patterns did not correlate with increases in maintenance of positive carbonate budgets.
-    Instead, reef depth emerged as the primary predictor of cover-time series resilience and
-    maintenance of positive carbonate budgets, with deeper reefs benefiting from thermal
-    refugia that reduce bleaching impacts. Interaction between reef depth and incoming
-    connectivity was found to influence reef temporal behaviour at 15m depth. These findings suggest that
-    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the
-    performance of deep reefs, contrasting current intervention
-    practices that primarily target easily accessible sites in the 1-10m depth range. These results have
-    important implications for reef management, indicating that depth refugia should be
-    prioritized for further consideration in conservation planning alongside connectivity
-    considerations to maximize coral survival under continuing climate change.
+    Coral reefs globally face unprecedented threats from climate change, with the Great 
+    Barrier Reef (GBR) experiencing cumulative stressors and increasingly severe declines 
+    in coral cover from thermal stress events. Understanding drivers behind reef resilience 
+    to climate impacts is critical for conservation planning and intervention strategies. A 
+    scenario-based population modelling approach was adopted with larval connectivity dynamics, 
+    thermal adaptation, and environmental factors to assess coral reef resilience across GBR 
+    locations under future climate projections. Using five Global Climate Models (GCMs) 
+    spanning five Equilibrium Climate Sensitivities,  reefs were analysed for coral cover 
+    time series and their ability of reefs to maintain positive carbonate production budgets 
+    under future conditions. Contrary to expectations, larval connectivity patterns did not 
+    correlate with increases in maintenance of positive carbonate budgets. Instead, reef depth 
+    emerged as the primary predictor of cover-time series resilience and maintenance of positive 
+    carbonate budgets, with deeper reefs benefiting from thermal refugia that reduce bleaching 
+    impacts. These findings suggest that depth provides critical 
+    protection against thermal stress, contrasting current intervention practices that primarily target easily 
+    accessible sites in the 1-10m depth range. These results have important implications 
+    for reef management, indicating that depth refugia should be prioritized for further 
+    consideration in conservation planning alongside connectivity modelling advancements 
+    to maximize coral survival under continuing climate change. 
 keywords:
@@
 magnitude DHWs based on SST, the proportion of a reefs' coral population impacted by heat
-stress events depends on reef depth. Our results suggest that for non-mesophotic reef
-ecosystems (i.e., \< 30m), depth contributes greatly to reef resilience and maintenance
-positive carbonate budgets under future conditions. Movement of shallow reefs towards
-negative carbonate budgets in the future may contribute to phase shifts in reef dominant
-CaCO~3~ production. Shifting from coral driven to encrusting algae driven production, or to
-bioerosion dominated systems with rapid erosion of physical reef frameworks [@dudgeon2010;
-@perry2008]. Reefs at increased depths may be able to maintain coral driven CaCO~3~
-production and accumulation into the future for longer. Spatially these results indicate
-that regions of positive carbonate budget maintenance, under ACCESS-ESM1-5, and high depth
-levels were concentrated in the Far Northern, offshore Townsville/Whitsunday, and
-Mackay/Capricorn management areas (@sfig-depth-map; @sfig-carb-budget-map). Resilient reefs
-in the Far Northern management area were exposed to lower mean DHW levels than other reefs
-under ACCESS-ESM1-5 (@sfig-mean-dhw-map), however similar spatial patterns were observed
-across GCMs for reefs clustered into the high cover cluster (@sfig-gcm-cluster-map). Spatial
-findings are not interpreted as accurate predictions of future resilience due to high
-uncertainty in input data, particularly depth and connectivity. While similar findings have
-been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014]
-regions, depth refugia analyses have often focused on the potential of mesophotic reefs (\>
-30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast,
-Venegas et al. [-@venegas2019] found no association between depth and the alleviation of
-heat stress across a range of shallow reefs in the Pacific.
+stress events depends on reef depth. Results of this investigation suggest that for
+non-mesophotic reef ecosystems (i.e., \< 30m), depth contributes greatly to reef resilience
+and maintenance positive carbonate budgets under future conditions. Movement of shallow
+reefs towards negative carbonate budgets in the future may contribute to phase shifts in
+reef dominant CaCO~3~ production. Shifting from coral driven to encrusting algae driven
+production, or to bioerosion dominated systems with rapid erosion of physical reef
+frameworks [@dudgeon2010; @perry2008]. Reefs at increased depths may be able to maintain
+coral driven CaCO~3~ production and accumulation into the future for longer. Spatially these
+results indicate that regions of positive carbonate budget maintenance, under ACCESS-ESM1-5,
+and high depth levels were concentrated in the Far Northern, offshore Townsville/Whitsunday,
+and Mackay/Capricorn management areas (@sfig-depth-map; @sfig-carb-budget-map). Resilient
+reefs in the Far Northern management area were exposed to lower mean DHW levels than other
+reefs under ACCESS-ESM1-5 (@sfig-mean-dhw-map), however similar spatial patterns were
+observed across GCMs for reefs clustered into the high cover cluster
+(@sfig-gcm-cluster-map). Spatial findings are not interpreted as accurate predictions of
+future resilience due to high uncertainty in input data, particularly depth and
+connectivity. While similar findings have been demonstrated in the Pacific [@smith2014;
+@baird2018] and Indo-Pacific [@bridge2014] regions, depth refugia analyses have often
+focused on the potential of mesophotic reefs (\> 30m deep) as thermal refugia
+[@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al. [-@venegas2019]
+found no association between depth and the alleviation of heat stress across a range of
+shallow reefs in the Pacific.
 
@@
 where the probability of a reef being clustered into the High cover cluster increased
-substantially. Additionally, two-way partial dependence analysis revealed high incoming
-connectivity is important for High cluster assignment for reefs at depths of \>10m.
-Considering this 10-15m depth range when assessing possible intervention sites may reduce
-the exposure of planted and seeded corals to high thermal stress, while still maintaining
-effective logistical access to sites.
+substantially compared to shallower depths. Considering this 10-15m depth range when
+assessing possible intervention sites may reduce the exposure of planted and seeded corals
+to high thermal stress, while still maintaining effective logistical access to sites.
 
@@
 the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008;
-@torres2024]. Two-way partial dependence analyses suggest that incoming and outgoing
-connectivity contribute positively to high cover cluster allocation for reefs around 15m
-deep. However, our results suggest no direct, first order, relationship between weighted
-incoming connectivity and the ability of reefs to maintain positive carbonate budgets under
-future conditions was found. There has been contrasting evidence [@bode2018; @hock2017]
-surrounding whether recent generation connectivity modelling is able to identify reefs that
-are important for recovery processes, with findings dependent on the larval connectivity
-model used. These investigations were performed using prior generations of larval
-connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time
-periods, without considering the influence of reef depth on resilience. Using updated 1km^2^
-resolution larval connectivity across the whole GBR, with a limited temporal sample of
-particle flows, it was found that larval connectivity alone may not be important or reef
-resilience and recovery, but should be considered in combination with more influential
-factors such as depth.
+@torres2024]. No direct, first order, relationship between weighted incoming connectivity
+and the ability of reefs to maintain positive carbonate budgets under future conditions was
+found. There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent
+generation connectivity modelling is able to identify reefs that are important for recovery
+processes, with findings dependent on the larval connectivity model used. These
+investigations were performed using prior generations of larval connectivity models
+parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods, without
+considering the influence of reef depth on resilience. Using updated 1km^2^ resolution
+larval connectivity across the whole GBR, with a limited temporal sample of particle flows,
+it was found that larval connectivity alone may not be important or reef resilience and
+recovery, but should be considered in combination with more influential factors such as
+depth.
 

### 2025-10-08 paper/paper_draft.qmd
Updates with tracked changes for methods section

@@
 The spatial extent of reefs represented in this investigation follows reef definitions
-available via the Great Barrier Reef Marine Park Authority (GBRMPA), defining 3806 reefs
-across the GBR [@GBRMPA2022] (@fig-region-map). Estimates of coral carrying capacity for
-each reef were taken from prior analyses [@bozec2022].
+available via the Great Barrier Reef Marine Park Authority (GBRMPA). Reef definitions outline 3806 reefs
+across the GBR [@GBRMPA2022] (@fig-region-map). Prior analyses by Bozec et al. [-@bozec2022] provided estimates of coral carrying capacity for each reef that were adopted by this study.
 
@@
 involves exploring a wide range of potential futures and model parameterisations under
-different assumptions of environmental (climatic) and ecological conditions. Exploratory
+different assumptions of climatic and ecological conditions. Exploratory
 modelling approaches have gained favour in recent years to explore the implications of deep
@@
 [@conradt2024; @lempert2013]. The approach embraces uncertainty as an inherent
-characteristic of complex environmental systems [@lempert2010; @lempert2013] in an attempt
+characteristic of complex environmental systems [@lempert2010; @lempert2013] 
 to address limitations of calibrated ecosystem models that use a singular set of parameter
@@
 All data preparation, modelling and analyses were performed using the Julia programming
-language (The Julia Project; https://julialang.org/; [@bezanson2017]), with visualisations
+language [@bezanson2017], with visualisations
 created using the Makie plotting ecosystem [@danisch2021]. Code used to process DHW data and
@@
 The coral larval connectivity model used in this study comprises 3D hourly velocities from
-the 1 km grid resolution hydrodynamic model (GBR-1 version 2.0) [@steven2019], as input to
+the 1 km grid resolution hydrodynamic model [GBR-1 version 2.0; @steven2019], as input to
 OceanParcels [@delandmeter2019], a particle tracking model. The connectivity model was used
@@
 reefs in the GBR, herein referred to as connectivity strengths. Indicative connectivity
-strengths are implemented in ADRIA-CoralBlox as the mean of matrices for each location
+strengths are implemented in ADRIA-CoralBlox (described in the next section) as the mean of matrices for each location
 (i.e., mean of all 24 spawning days). While the connectivity strengths do not vary
@@
 reproducing and producing larvae, instead it takes total coral cover area as an indicator of
-larval productivity. Outgoing connection strength was calculated as the sum of all outgoing
+larval productivity.
+
+Outgoing connection strength was calculated as the sum of all outgoing
 transition probabilities from a target reef. Outgoing connection strength has a theoretical
@@
 detailed in the supplementary material. Of note is that the representation of bleaching
-mortalities followed Bozec et al., [-@bozec2022] albeit with a scaling coefficient to
+mortalities followed Bozec et al., [-@bozec2022] and  albeit with a scaling coefficient to
 incorporate the amelioration effect that depth may have, following Baird et al.,
-[@baird2018]. This depth-scaling reduces the proportion of coral colonies impacted by high
+[-@baird2018]. This depth-scaling reduces the proportion of coral colonies impacted by high
 heat stress as depth increases. The impacts of tropical cyclones, wave activity, Crown of
@@
 The scenario-median time series for each reef was used for further analyses. Time series of
-coral cover were then clustered based on their temporal behaviour. Assessment metrics used
+coral cover were then clustered based on their behaviour. Assessment metrics used
 in analyses can be found in @stbl-metrics.
@@
 
-Reefs were clustered based on the temporal behaviour of their median coral cover time
+Reefs were clustered based on the behaviour of their median coral cover time
 series. Put simply, reefs that have similar trends and trajectories are more likely to be

### 2025-10-08 paper/paper_draft.qmd
Updates for tracked changes to rest of methods, results and discussion

@@
 The spatial extent of reefs represented in this investigation follows reef definitions
-available via the Great Barrier Reef Marine Park Authority (GBRMPA). Reef definitions outline 3806 reefs
-across the GBR [@GBRMPA2022] (@fig-region-map). Prior analyses by Bozec et al. [-@bozec2022] provided estimates of coral carrying capacity for each reef that were adopted by this study.
+available via the Great Barrier Reef Marine Park Authority (GBRMPA). Reef definitions
+outline 3806 reefs across the GBR [@GBRMPA2022] (@fig-region-map). Prior analyses by Bozec
+et al. [-@bozec2022] provided estimates of coral carrying capacity for each reef that were
+adopted by this study.
 
@@
 involves exploring a wide range of potential futures and model parameterisations under
-different assumptions of climatic and ecological conditions. Exploratory
-modelling approaches have gained favour in recent years to explore the implications of deep
+different assumptions of climatic and ecological conditions. Exploratory modelling
+approaches have gained favour in recent years to explore the implications of deep
 uncertainty; where there is little or no agreement on the key drivers of a system, the
@@
 [@conradt2024; @lempert2013]. The approach embraces uncertainty as an inherent
-characteristic of complex environmental systems [@lempert2010; @lempert2013] 
-to address limitations of calibrated ecosystem models that use a singular set of parameter
-values [@lubianabotelho2025]. Exploratory scenario modelling is a core methodology
-underpinning the development of robust and adaptive management strategies [@haasnoot2013].
+characteristic of complex environmental systems [@lempert2010; @lempert2013] to address
+limitations of calibrated ecosystem models that use a singular set of parameter values
+[@lubianabotelho2025]. Exploratory scenario modelling is a core methodology underpinning the
+development of robust and adaptive management strategies [@haasnoot2013].
 
 All data preparation, modelling and analyses were performed using the Julia programming
-language [@bezanson2017], with visualisations
-created using the Makie plotting ecosystem [@danisch2021]. Code used to process DHW data and
-perform analyses involved in this investigation can be found at Grier and Iwanaga
-[-@grier2025].
+language [@bezanson2017], with visualisations created using the Makie plotting ecosystem
+[@danisch2021]. Code used to process DHW data and perform analyses involved in this
+investigation can be found at Grier and Iwanaga [-@grier2025].
 
@@
 reefs in the GBR, herein referred to as connectivity strengths. Indicative connectivity
-strengths are implemented in ADRIA-CoralBlox (described in the next section) as the mean of matrices for each location
-(i.e., mean of all 24 spawning days). While the connectivity strengths do not vary
-temporally within each ADRIA-CoralBlox simulation, spatial variability enables
-investigations into the influence of connectivity strength and its role in driving recovery
-processes.
+strengths are implemented in ADRIA-CoralBlox (described in the next section) as the mean of
+matrices for each location (i.e., mean of all 24 spawning days). While the connectivity
+strengths do not vary temporally within each ADRIA-CoralBlox simulation, spatial variability
+enables investigations into the influence of connectivity strength and its role in driving
+recovery processes.
 
@@
 
-Outgoing connection strength was calculated as the sum of all outgoing
-transition probabilities from a target reef. Outgoing connection strength has a theoretical
-maximum of one (all larvae reach settlement on sink reefs), however the large size of the
-GBR combined with larval mortality result in much lower outgoing connection strength values.
-The ratio of source-to-sink connectivity ($O:I$) for a target reef represents the strength
-of the reef's outgoing larval flow relative to it's incoming larval flow. This is calculated
-as: $O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of connectivity
-probabilities, $N$ represents the number of connections, $O$ denotes outgoing connectivity
-from the target reef and $I$ denotes incoming connectivity to the target reef. If a reef has
-no incoming connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this
-calculation, do not directly represent the larval supply gained as the breeding populations
-from which connections are coming from are not represented. A source-to-sink ratio greater
-than 1 (a value greater than 0 on a log scale) indicates a reef has greater outgoing than
-incoming larval flow. Reef larval retention probability indicates the proportion of spawned
-larvae that settle on their natal reefs.
+Outgoing connection strength was calculated as the sum of all outgoing transition
+probabilities from a target reef. Outgoing connection strength has a theoretical maximum of
+one (all larvae reach settlement on sink reefs), however the large size of the GBR combined
+with larval mortality result in much lower outgoing connection strength values. The ratio of
+source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
+outgoing larval flow relative to it's incoming larval flow. This is calculated as:
+$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of connectivity probabilities,
+$N$ represents the number of connections, $O$ denotes outgoing connectivity from the target
+reef and $I$ denotes incoming connectivity to the target reef. If a reef has no incoming
+connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this calculation,
+do not directly represent the larval supply gained as the breeding populations from which
+connections are coming from are not represented. A source-to-sink ratio greater than 1 (a
+value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
+larval flow. Reef larval retention probability indicates the proportion of spawned larvae
+that settle on their natal reefs.
 
@@
 compared to pseudo-random sampling. A detailed comparative analysis of sampling methods can
-be found in [@kucherenko2015]. For scenario assessment, coral cover time series for each
-model run were scaled to represent cover as a percentage of the total estimated reef area.
-The scenario-median time series for each reef was used for further analyses. Time series of
-coral cover were then clustered based on their behaviour. Assessment metrics used
-in analyses can be found in @stbl-metrics.
+be found in [@lecuyer2018; @kucherenko2015]. For scenario assessment, coral cover time
+series for each model run were scaled to represent cover as a percentage of the total
+estimated reef area. The scenario-median time series for each reef was used for further
+analyses. Time series of coral cover were then clustered based on their behaviour.
+Assessment metrics used in analyses can be found in @stbl-metrics.
 
@@
 
-Reefs were clustered based on the behaviour of their median coral cover time
-series. Put simply, reefs that have similar trends and trajectories are more likely to be
-clustered together. Reefs are clustered into Low, Medium, or High, indicating their relative
-ability to maintain coral cover over time. Reefs in each time series cluster were compared
-to identify characteristics that differ between Low, Medium and High clusters. These
+Reefs were clustered based on the behaviour of their median coral cover time series. Put
+simply, reefs that have similar trends and trajectories are more likely to be clustered
+together. Reefs are clustered into Low, Medium, or High, indicating their relative ability
+to maintain coral cover over time. Reefs in each time series cluster were compared to
+identify characteristics that differ between Low, Medium and High clusters. These
 characteristics include reef median depth, mean time series DHW, weighted incoming
@@
 constituting "low", "medium" or "high" coral cover may differ at different spatial scales.
-As it was, analyses at the whole-of-GBR scale were found to lead to identical conclusions
-regarding reef characteristics which influence coral cover and so for brevity are not shown
-here.
+Analyses at the whole-of-GBR scale were found to lead to identical conclusions regarding
+reef characteristics which influence coral cover and so for brevity are not shown here.
 
@@
 Sensitivity Analysis [@hornberger1981; @pianosi2016], as model results are assessed to map
-the influence of X - the predictors or model factors - on Y - the modelled outcomes
+the influence of $X$ - the predictors or model factors - on $y$ - the modelled outcomes
 according to a metric of interest.
@@
 prediction accuracy across bioregions, reveals increasing performance as mean bioregion reef
-depth increases (@sfig-rf-predictor-perf). This highlights that unexplained variation in the
-test dataset (33% of variation) may be concentrated in shallow bioregions where available
-model predictors do not capture differences between clustered reefs.
+depth increases (@sfig-rf-predictor-perf). Unexplained variation in the test dataset (33% of
+variation) may be concentrated in shallow bioregions where considered model predictors do
+not capture differences between clustered reefs.
 
@@
 
-This investigation's results show increasing reef depth has a strong positive impact on
-modelled reef resilience in temporal behaviour and maintenance of positive carbonate budgets
-under possible future conditions. Reefs with a median depth of 10m or greater, with high
-incoming connectivity, are the most likely to be assigned to a high cover time series
-cluster. By itself, incoming connectivity alone does not correlate with maintenance of
-positive carbonate budgets. These findings highlight the importance of depth and incoming
-connectivity as coupled selection features when assessing potential reef resilience under
-future thermal stress.
+Results show increasing reef depth has a strong positive impact on modelled reef resilience
+in temporal behaviour and maintenance of positive carbonate budgets under possible future
+conditions. Reefs with a median depth of 10m or greater, with high incoming connectivity,
+are the most likely to be assigned to a high cover time series cluster. By itself, incoming
+connectivity alone does not correlate with maintenance of positive carbonate budgets. These
+findings highlight the importance of depth and incoming connectivity as coupled selection
+features when assessing potential reef resilience under future thermal stress.
 
@@
 non-mesophotic reef ecosystems (i.e., \< 30m), depth contributes greatly to reef resilience
-and maintenance positive carbonate budgets under future conditions. Movement of shallow
-reefs towards negative carbonate budgets in the future may contribute to phase shifts in
-reef dominant CaCO~3~ production. Shifting from coral driven to encrusting algae driven
+and maintenance positive carbonate budgets under future conditions.
+
+Movement of shallow reefs towards negative carbonate budgets in the future may contribute to
+phase shifts in dominant sources of CaCO~3~ production. Reefs may switch away from
+coral-driven processes, and CaCO~3~ accretion, to encrusting algae driven CaCO~3~
 production, or to bioerosion dominated systems with rapid erosion of physical reef
 frameworks [@dudgeon2010; @perry2008]. Reefs at increased depths may be able to maintain
-coral driven CaCO~3~ production and accumulation into the future for longer. Spatially these
-results indicate that regions of positive carbonate budget maintenance, under ACCESS-ESM1-5,
-and high depth levels were concentrated in the Far Northern, offshore Townsville/Whitsunday,
-and Mackay/Capricorn management areas (@sfig-depth-map; @sfig-carb-budget-map). Resilient
-reefs in the Far Northern management area were exposed to lower mean DHW levels than other
-reefs under ACCESS-ESM1-5 (@sfig-mean-dhw-map), however similar spatial patterns were
-observed across GCMs for reefs clustered into the high cover cluster
-(@sfig-gcm-cluster-map). Spatial findings are not interpreted as accurate predictions of
-future resilience due to high uncertainty in input data, particularly depth and
-connectivity. While similar findings have been demonstrated in the Pacific [@smith2014;
-@baird2018] and Indo-Pacific [@bridge2014] regions, depth refugia analyses have often
-focused on the potential of mesophotic reefs (\> 30m deep) as thermal refugia
-[@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al. [-@venegas2019]
-found no association between depth and the alleviation of heat stress across a range of
-shallow reefs in the Pacific.
-
-The results of this investigation support the hypothesis that reefs at greater depths will
-exhibit characteristics of refugia and prolonged resilience (in terms of coral cover) under
-climate change compared to shallower reefs. Additionally, Liu, Callaghan and Baldock
-[-@liu2024] suggest that rubble instability is inversely correlated with reef depth,
-possibly limiting juvenile coral recruitment capacity of shallow reefs. A caveat to
-depth-resilience findings is the quality of the bathymetry data used to calculate median
-reef depth. As detailed previously, estimates of median reef depth are derived from
-satellite imagery (at $10m^2$ resolution) which can be subject to high degrees of
-uncertainty, both in terms of the estimated depth for each pixel as well as their alignment
-to the established GBRMPA reef outlines.
+coral driven CaCO~3~ production and accumulation into the future for longer.
+
+Spatially, these results indicate that regions of positive carbonate budget maintenance,
+under ACCESS-ESM1-5, and high depth levels were concentrated in the Far Northern, offshore
+Townsville/Whitsunday, and Mackay/Capricorn management areas (@sfig-depth-map;
+@sfig-carb-budget-map). Resilient reefs in the Far Northern management area were exposed to
+lower mean DHW levels than other reefs under ACCESS-ESM1-5 (@sfig-mean-dhw-map), however
+similar spatial patterns were observed across GCMs for reefs clustered into the high cover
+cluster (@sfig-gcm-cluster-map).
+
+These findings are not to be interpreted as accurate predictions of future resilience due to
+high uncertainty in input data, particularly depth and connectivity. While similar findings
+have been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific
+[@bridge2014] regions, depth refugia analyses have often focused on the potential of
+mesophotic reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015;
+@semmler2017]. In contrast, Venegas et al. [-@venegas2019] found no association between
+depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.
+
+This investigation supports the hypothesis that reefs at greater depths will exhibit
+characteristics of refugia and prolonged resilience (in terms of coral cover) under climate
+change compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024]
+suggest that rubble instability is inversely correlated with reef depth, possibly limiting
+juvenile coral recruitment capacity of shallow reefs. A caveat to depth-resilience findings
+is the quality of the bathymetry data used to calculate median reef depth. As detailed
+previously, estimates of median reef depth are derived from satellite imagery (at 10m^2^
+resolution) which can be subject to high degrees of uncertainty, both in terms of the
+estimated depth for each pixel as well as their alignment to the established GBRMPA reef
+outlines.
 
@@
 it was found that larval connectivity alone may not be important or reef resilience and
-recovery, but should be considered in combination with more influential factors such as
+recovery but should be considered in combination with more influential factors such as
 depth.

### 2025-10-09 paper/paper_draft.qmd
Updates to incorporate tracked changes and add in ADRIA-CoralBlox information

@@
 detailed in the supplementary material. Of note is that the representation of bleaching
-mortalities followed Bozec et al., [-@bozec2022] and albeit with a scaling coefficient to
-incorporate the amelioration effect that depth may have, following Baird et al.,
-[-@baird2018]. This depth-scaling reduces the proportion of coral colonies impacted by high
-heat stress as depth increases. The impacts of tropical cyclones, wave activity, Crown of
-Thorns Starfish or coral disease were not included in this investigation in order to focus
-on assessing reef resilience under possible future warming scenarios.
+mortalities followed Bozec et al., [-@bozec2022] and Baird et al. [-@baird2018] which
+applies a scaling coefficient to incorporate the amelioration effect that depth may have.
+This depth-scaling reduces the proportion of coral colonies impacted by high heat stress as
+depth increases. The impacts of tropical cyclones, wave activity, Crown of Thorns Starfish
+or coral disease were not included in this investigation in order to focus on assessing reef
+resilience under possible future warming scenarios.
 
@@
 indicating outlier values for these factors are not influential. Assessing random forest
-prediction accuracy across bioregions, reveals increasing performance as mean bioregion reef
+prediction accuracy across bioregions reveals increasing performance as mean bioregion reef
 depth increases (@sfig-rf-predictor-perf). Unexplained variation in the test dataset (33% of
@@
 
-Spatially, these results indicate that regions of positive carbonate budget maintenance,
+Spatially these results indicate that regions of positive carbonate budget maintenance,
 under ACCESS-ESM1-5, and high depth levels were concentrated in the Far Northern, offshore
@@
 that are dependent on the size and functional group of a coral colony. Environmental
-disturbances and reproduction are not directly considered within CoralBlox. Instead, these
-factors are considered by making changes to the distribution of colonies within CoralBlox
-timesteps using the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform
-[@iwanaga2023]. Within ADRIA, we incorporate coral life history and environmental events in
+disturbances and reproduction are not directly considered within CoralBlox, and are instead
+provided by the ADRIA (Adaptive Dynamic Reef Intervention Algorithms) platform
+[@iwanaga2023]. Within ADRIA, coral life history and environmental events are implemented in
 the following order: coral colony growth; coral reproduction; larval connectivity and
-settlement; and coral bleaching due to heat stress. As ADRIA and CoralBlox are coupled
-together to represent the system, we refer to both as ADRIA-CoralBlox.
+settlement; and coral bleaching due to heat stress.
 
@@
 bleaching mortality. There has been contrasting evidence for juvenile corals being immune to
-thermal bleaching events [@depczynski2013], we assume the high background mortality of
+thermal bleaching events [@depczynski2013], it is assumed the high background mortality of
 juveniles includes thermal stress [@álvarez-noriega2018].
+
+### Model implementation
+
+ADRIA-CoralBlox implements five functional groups common to the GBR, tabular Acropora,
+corymbose Acropora, corymbose non-Acropora, small massives and large massives. CoralBlox
+uses user-defined size classes that influence size-dependent growth and mortality rates,
+through which the coral colonies progress as they grow in diameter. Size classes were
+initially informed by Bozec et al. [-@bozec2022].
+
+The area of each coral colony is tracked in CoralBlox by the area of a circumference. A
+coral population is then represented by a discretised distribution of **eq** coral
+diameters, composed of smaller uniform distributions, each representing the number of corals
+within a certain diameter range:
+
+**eq**
+
+where **eq** represents the number of intervals used to discretise **eq**, and **eq** and
+**eq** are the diameters of the smallest and biggest coral colonies, in that order. The
+coral cover for the entire population is given by:
+
+**eq**
+
+These are uniform distributions that compose **eq**, a coral block characteristed by a
+diameter density **eq** (the block's height) and a diameter range **eq** (the base of the
+block). Therefore, instead of working with a continuous diameter's distribution, CoralBlox
+updates each coral block separately. A mortality event is modelled as a decrease in a coral
+block's density, and a growth event as an increase in a coral block's diameter range limits.
+Both growth and mortality rates are size class dependent, which means the same growth and
+mortality rates are used for blocks within a size class. Figure S14 shows a model's
+behaviour under low disturbance and no interventions.
+
+![Time series comparing modelled and observed relative coral cover for Ben reef showing a
+recovery process under very low disturbance and no interventions. The observed data used
+here is from the AIMS Long-Term Monitoring Program (LTMP). Error metrics including Root Mean
+Square Error (0.06) and the Spearman Rank Correlation Coefficient (0.9) is also shown. The
+second plot shows the DHW and Cyclone or COTS events. The third plot shows the benthic
+composition for each functional group as a proportion of the reef’s cover at each
+year.](../figs/coralblox_reef_example.png){#sfig-coralblox-example width fig-align="center"
+width="14.82cm"}
+
+In ADRIA we track the thermal tolerance of each functional group and size class as a
+truncated normal distribution that is updated in each timestep following growth and
+recruitment. This distribution determines the proportion of the population on a reef that is
+susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
+Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
+[-@bairos-novak2021] and expert opinion, and are additionally varied in the scenario
+exploration.
 
@@
 
-### Model parameterisation
-
-In this investigation we model five functional groups common to the GBR, tabular Acropora,
-corymbose Acropora, corymbose non-Acropora, small massives and large massives. We do not
-model arborescent Acropora forms due to their distinct life history from other morphological
-groups. CoralBlox uses user-defined size classes that influence size-dependent growth and
-mortality rates, through which the coral colonies progress as they grow in diameter. Within
-ADRIA, we define the distributions of these parameters, and the size classes based on
-ecological monitoring data from the Ecological Intelligence for Reef Restoration Program
-(EcoRRAP) ([@australianinstituteofmarinescience2025; @ribeirodealmeida2024]).
-
-In ADRIA we track the thermal tolerance of each functional group and size class as a
-truncated normal distribution that is updated in each timestep following growth and
-recruitment. This distribution determines the proportion of the population on a reef that is
-susceptible to bleaching (i.e. has a thermal threshold below the experienced DHW value).
-Starting distributions for thermal tolerance levels are informed by Bairos-Novak et al.
-[-@bairos-novak2021].
-
-### Calibration
-
-The growth and mortality rate parameters of ADRIA-CoralBlox were calibrated using hard coral
-cover and benthic composition data from the Long-Term Monitoring Program (LTMP). From all
-the reefs for which there is LTMP data available, 99 were selected for having at least 4
-observations that span more than 10 years. These locations were randomly split into a
-calibration set (with 73 reefs) and a validation set (with 26 reefs), as evenly spatially
-distributed as possible. The error function used in the calibration process is composed of
-three elements [@eq-calibration]. The first is a Mean Absolute Exponential Error ($MAEE$)
-that captures the difference between modeled and observed hard coral cover. The second is a
-Coral Composition Error ($CCE$) that captures the differences in the benthic composition
-between modeled and observed coral cover. The third ($Err~p~$) is an error that emphasizes
-differences between observed and modelled cover at the beginning and end of the series, as
-well as on peaks and troughs:
-
-$$
-err = MAEE_\sigma_  *  w_1_  +  CEE_t_  *  w_c_  +  Err_p_  *  w_p_
-$$ {#eq-calibration}
-
-[@sfig-reef-scale-calibration] shows a comparison between modeled and observed relative
-coral cover for 6 reefs with distinct disturbance patterns. For each one, a Root Mean Square
-Error (RMSE), the MAEE and Spearman’s Rank Correlation Coefficient (SRCC) is also shown.
-[@sfig-man-area-calibration] presents another comparison between observed and modeled hard
-coral cover aggregated by GBRMPA management area.
-
-![Time series comparing modelled and observed relative coral cover for selected validation
-reefs. These reefs were selected to show distinct disturbance patterns and behaviors. reefs
-(a) and (b), with low heat stress and a single disturbance at the beginning, show the
-model’s ability of reproducing the reef’s recovery under low or no disturbance; reefs (c)
-and (d), with moderate to high heat stress and disturbance events in the middle of the
-considered timeframe, show the model’s ability to reproduce disturbances reasonably well but
-some difficulty in representing the post-disturbance recovery ; reefs (e) and (f) illustrate
-the challenge of reproducing the observed behavior in a high disturbance
-scenario.](../figs/reef_scale_calibration.png){#sfig-reef-scale-calibration
-fig-align="center" width="14.82cm"}
-
-![Comparison between observed and modelled coral relative cover aggregated, for each GBRMPA
-management area, for the calibration set (first row) and validation set (second row). For
-each one the aggregated RMSE and MAE are
-presented.](../figs/management_area_calibration.png){#sfig-man-area-calibration
-fig-align="center" width="14.82cm"}
+### Sensitivity analysis
+
+A global sensitivity analysis was performed using Shapley Effects **goda etal** implemented
+in the SAShE.jl package **SAShE citation**. For this analysis, 10,000 samples were simulated
+for a single reef and timestep. Two metrics were considered, difference in coral cover and
+difference in evenness. The factors analysed were heritability, mean colony diameter, linear
+extension, mortality base rate, mean and standard deviation of the tolerance distribution,
+linear extension scale factor, mortality rate scale factor reef habitable area, reef depth,
+DHW, and initial coral cover. @sfig-coralblox-sa shows the result of such analysis for
+different ranges of DHW. In both cases a similar effect takes place: when DHW = 0, initial
+cover is the most influential factor then, when DHW \> 0, depth and DHW start to appear as
+influential factors and, as DHW values get higher, depth becomes more influential in
+detriment of DHW.
 

### 2025-10-10 paper/paper_draft.qmd
Incorporate CoralBlox equations to complete ADRIA-CoralBlox section

@@
 The area of each coral colony is tracked in CoralBlox by the area of a circumference. A
-coral population is then represented by a discretised distribution of **eq** coral
+coral population is then represented by a discretised distribution of $p(x)$ coral
 diameters, composed of smaller uniform distributions, each representing the number of corals
@@
 
-**eq**
-
-where **eq** represents the number of intervals used to discretise **eq**, and **eq** and
-**eq** are the diameters of the smallest and biggest coral colonies, in that order. The
-coral cover for the entire population is given by:
-
-**eq**
-
-These are uniform distributions that compose **eq**, a coral block characteristed by a
-diameter density **eq** (the block's height) and a diameter range **eq** (the base of the
-block). Therefore, instead of working with a continuous diameter's distribution, CoralBlox
-updates each coral block separately. A mortality event is modelled as a decrease in a coral
-block's density, and a growth event as an increase in a coral block's diameter range limits.
-Both growth and mortality rates are size class dependent, which means the same growth and
-mortality rates are used for blocks within a size class. Figure S14 shows a model's
-behaviour under low disturbance and no interventions.
+$$
+\rho(x) =
+\begin{cases}
+\lambda_1, & d_0 < x < d_1 \\
+\vdots & \vdots \\
+\lambda_N, & d_{N-1} < x < d_N \\
+0, & x \notin [d_0, d_N]
+\end{cases}
+$$
+
+where $N$ represents the number of intervals used to discretise $p(x)$, and $d_0$ and $d_N$
+are the diameters of the smallest and biggest coral colonies, in that order. The coral cover
+for the entire population is given by:
+
+$$
+\begin{aligned}
+C &= \int_{d_0}^{d_N} \pi x^2 \rho(x) \, dx \\
+  &= \sum_{n=1}^{N} \pi \lambda_n \int_{d_{n-1}}^{d_n} x^2 \, dx \\
+  &= \sum_{n=1}^{N} \pi \lambda_n \left( \frac{d_n^3 - d_{n-1}^3}{3} \right)
+\end{aligned}
+$$
+
+These are uniform distributions that compose $p(x)$, a coral block characteristed by a
+diameter density $\lambda_n$ (the block's height) and a diameter range $[d_{n-1},d_n]$ (the
+base of the block). Therefore, instead of working with a continuous diameter's distribution,
+CoralBlox updates each coral block separately. A mortality event is modelled as a decrease
+in a coral block's density, and a growth event as an increase in a coral block's diameter
+range limits. Both growth and mortality rates are size class dependent, which means the same
+growth and mortality rates are used for blocks within a size class. @sfig-coralblox-example
+shows a model's behaviour under low disturbance and no interventions.
 

### 2025-10-10 paper/paper_draft.qmd
Update author order, affiliations and contributions

@@
           name: Australian Institute of Marine Science
-          address: Cape Cleveland Rd
-          state: QLD
+          address: Townsville, Queensland, Australia
     attributes:
@@
           name: Australian Institute of Marine Science
-          address: Cape Cleveland Rd
-          city: Cape Cleveland
-          state: QLD
+          address: Townsville, Queensland, Australia
+  - name: Pedro Ribeiro De Almeida
+    email: p.ribeirodealmeida@aims.gov.au
+    affiliations:
+        - id: AIMS
+          name: Australian Institute of Marine Science
+          address: Townsville, Queensland, Australia
   - name: Chinenye Ani
@@
           name: Australian Institute of Marine Science
-          address: Cape Cleveland Rd
-          city: Cape Cleveland
-          state: QLD
-  - name: Pedro Ribeiro De Almeida
-    email: p.ribeirodealmeida@aims.gov.au
-    affiliations:
-        - id: AIMS
-          name: Australian Institute of Marine Science
-          address: Cape Cleveland Rd
-          city: Cape Cleveland
-          state: QLD
+          address: Townsville, Queensland, Australia
   - name: Sam Matthews
@@
           name: Australian Institute of Marine Science
-          address: Cape Cleveland Rd
-          city: Cape Cleveland
-          state: QLD
+          address: Townsville, Queensland, Australia
 abstract: |
@@
 (60%) and testing (40%) subsets to train and assess classification performance. The RF
-classifier achieved 80% accuracy on the training set and 60% on the test set.
-
-A 3-fold cross-validation was also conducted, arriving at a similar 59% accuracy rate. F1
-performance scores for Low, Medium, and High clusters were determined to be 0.70, 0.43 and
-0.64 respectively, with precision of 0.62, 0.51 and 0.66 when evaluated with the test set
+classifier achieved 80% accuracy on the training set and 60% on the test set. A 3-fold
+cross-validation was also conducted, arriving at a similar 59% accuracy rate. F1 performance
+scores for Low, Medium, and High clusters were determined to be 0.70, 0.43 and 0.64
+respectively, with precision of 0.62, 0.51 and 0.66 when evaluated with the test set
 (consisting of 4394 samples) (@stbl-confusion-matrix; @stbl-rf-cluster-performance). Lower
@@
 Iwanaga:** conceptualisation, data curation, formal analysis, investigation, methodology,
-visualization, writing – original draft, writing – review and editing. **\[BG: To be
-completed.\] ...**
+visualization, writing – original draft, writing – review and editing. **Pedro Ribeiro de
+Almeida:** data curation, model development, analysis, writing - methodology, writing -
+review and editing, visualisation. **Chinenye Ani:** data curation, writing - methodology,
+writing - review and editing. **Sam Matthews:** Writing - review and editing.
 
@@
 
-A global sensitivity analysis was performed using Shapley Effects **goda etal** implemented
-in the SAShE.jl package **SAShE citation**. For this analysis, 10,000 samples were simulated
-for a single reef and timestep. Two metrics were considered, difference in coral cover and
-difference in evenness. The factors analysed were heritability, mean colony diameter, linear
-extension, mortality base rate, mean and standard deviation of the tolerance distribution,
-linear extension scale factor, mortality rate scale factor reef habitable area, reef depth,
-DHW, and initial coral cover. @sfig-coralblox-sa shows the result of such analysis for
-different ranges of DHW. In both cases a similar effect takes place: when DHW = 0, initial
-cover is the most influential factor then, when DHW \> 0, depth and DHW start to appear as
-influential factors and, as DHW values get higher, depth becomes more influential in
-detriment of DHW.
+A global sensitivity analysis was performed using Shapley Effects [@goda2021] implemented in
+the SAShE.jl package [@ribeirodealmeida2025a]. For this analysis, 10,000 samples were
+simulated for a single reef and timestep. Two metrics were considered, difference in coral
+cover and difference in evenness. The factors analysed were heritability, mean colony
+diameter, linear extension, mortality base rate, mean and standard deviation of the
+tolerance distribution, linear extension scale factor, mortality rate scale factor reef
+habitable area, reef depth, DHW, and initial coral cover. @sfig-coralblox-sa shows the
+result of such analysis for different ranges of DHW. In both cases a similar effect takes
+place: when DHW = 0, initial cover is the most influential factor then, when DHW \> 0, depth
+and DHW start to appear as influential factors and, as DHW values get higher, depth becomes
+more influential in detriment of DHW.
 
@@
 to ensure reefs are clustered based on their underlying temporal dynamics rather than
-aggregating the coral cover across all timesteps. The process creates a n \* n distance
-matrix (where n is the number of time series in the group) that is used as an input to a
+aggregating the coral cover across all timesteps. The process creates a $n * n$ distance
+matrix (where $n$ is the number of time series in the group) that is used as an input to a
 k-medoids clustering algorithm [cf. @steinmann2020]. The three reef clusters are labelled
@@
 ![Bar plot indicating the Spearman's rank correlation values for the number of years above
-carbonate budget threshold and, median reef depth and log10 weighted incoming connectivity
-values. Depth correlation values are displayed in the left plot, while connectivity
-correlation values are displayed in the right plot. Displays results for ACCESS-ESM1-5
+carbonate budget threshold ($theta$) and, median reef depth and log10 weighted incoming
+connectivity values. Depth correlation values are displayed in the left plot, while
+connectivity correlation values are displayed in the right plot. Displays results for
+ACCESS-ESM1-5
 GCM.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_correlations.png){#sfig-access-esm1-5-carb-budget-corr

### 2025-10-10 paper/paper_draft.qmd
Update with additional corablox figures

@@
 
+![Parametric sensitivity analysis conducted with Shapley effects. Each column reflects
+sampling of different DHW ranges. The first column represents model runs with DHW = 0, and
+the remaining columns represent models runs with DHW valued between 0 and 8, 8 and 16, 16
+and 30, and 0 and 30. The first row shows the Shapley effect for change in coral cover and
+the second for change in evenness of species
+abundance.](../figs/coralblox_sens_analysis.png){#sfig-coralblox-sa width fig-align="center"
+width="14.82cm"}
+
 ### Time series clustering

### 2025-10-10 paper/paper_draft.qmd
Add LTMP citation to figure caption
Update citation formatting

@@
 magnitude of early bleaching events decreasing the breeding capacity of strongly connected
-reefs. Analysing daily connectivity data Vogt-Vincent et al. [-@vogt-vincent2023] suggest
+reefs. Analysing daily connectivity data Vogt-Vincent, Mitarai and Johnson [-@vogt-vincent2023] suggest
 that time-mean connectivity may not be suitable for capturing the seasonal - ecological time
@@
 adopted to align with other ongoing modelling and analyses conducted as part of the Reef
-Restoration and Adaptation Program (<https://gbrrestoration.org>; [@thereef]).
+Restoration and Adaptation Program (<https://gbrrestoration.org>; RRAP [-@thereef]).
 
@@
 year 1988.2857, which attempts to account for any long-term trends within the baseline years
-themselves (see Skirving et al. [@skirving2020]). The adjustment ensures that the
+themselves (see Skirving et al. [-@skirving2020]). The adjustment ensures that the
 climatology represents conditions at a specific temporal reference point rather than being
@@
 recovery process under very low disturbance and no interventions. The observed data used
-here is from the AIMS Long-Term Monitoring Program (LTMP). Error metrics including Root Mean
-Square Error (0.06) and the Spearman Rank Correlation Coefficient (0.9) is also shown. The
-second plot shows the DHW and Cyclone or COTS events. The third plot shows the benthic
+here is from the AIMS Long-Term Monitoring Program (LTMP) . Error metrics including Root
+Mean Square Error (0.06) and the Spearman Rank Correlation Coefficient (0.9) is also shown.
+The second plot shows the DHW and Cyclone or COTS events. The third plot shows the benthic
 composition for each functional group as a proportion of the reef’s cover at each
-year.](../figs/coralblox_reef_example.png){#sfig-coralblox-example width fig-align="center"
-width="14.82cm"}
+year.](../figs/coralblox_reef_example.png){#sfig-coralblox-example
+fig-align="center" width="14.82cm"}
 
@@
 the second for change in evenness of species
-abundance.](../figs/coralblox_sens_analysis.png){#sfig-coralblox-sa width fig-align="center"
-width="14.82cm"}
+abundance.](../figs/coralblox_sens_analysis.png){#sfig-coralblox-sa
+fig-align="center" width="14.82cm"}
 

### 2025-10-10 paper/paper_draft.qmd
Updated abstract

@@
     to climate impacts is critical for conservation planning and intervention strategies. A
-    scenario-based population modelling approach was adopted with larval connectivity dynamics, 
-    thermal adaptation, and environmental factors to assess coral reef resilience across GBR 
-    locations under future climate projections. Using five Global Climate Models (GCMs) 
-    spanning five Equilibrium Climate Sensitivities,  reefs were analysed for coral cover 
-    time series and their ability of reefs to maintain positive carbonate production budgets 
-    under future conditions. Contrary to expectations, larval connectivity patterns did not 
-    correlate with increases in maintenance of positive carbonate budgets. Instead, reef depth 
-    emerged as the primary predictor of cover-time series resilience and maintenance of positive 
-    carbonate budgets, with deeper reefs benefiting from thermal refugia that reduce bleaching 
-    impacts. These findings suggest that depth provides critical 
-    protection against thermal stress, contrasting current intervention practices that primarily target easily 
-    accessible sites in the 1-10m depth range. These results have important implications 
-    for reef management, indicating that depth refugia should be prioritized for further 
-    consideration in conservation planning alongside connectivity modelling advancements 
-    to maximize coral survival under continuing climate change. 
+    scenario-based population modelling approach was adopted with larval connectivity dynamics and
+    environmental factors to assess coral reef resilience across the GBR using projected conditions under
+    five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities. Projected coral
+    cover were analysed for each reefs ability to maintain positive carbonate production budgets under
+    future conditions using coral cover as a proxy. Larval connectivity patterns did not correlate with
+    increases in maintenance of positive carbonate budgets. Instead, reef depth emerged as the primary
+    predictor, with deeper reefs benefitting from thermal refugia that reduce bleaching impacts. These
+    findings suggest that depth is a tangible and pragmatic reef characteristic to consider in future
+    intervention practices for coral reef restoration. These results have important implications for reef
+    management, indicating that depth refugia should be prioritized for further consideration in
+    conservation planning to maximize coral survival under continuing climate change.
+
 keywords:

### 2025-10-10 paper/paper_draft.qmd
Tweak intro

@@
 such as ocean temperature [@foster2021; @gattuso2014]. Mass bleaching and associated
-mortality events driven by climate change can cause reef-building coral population declines
-[@hughes2017; @hughes2018; @bozec2025], possibly leading to coral-macroalgae regime shifts
-[@arif2022; @wild2011]. Climate impacts on coral reefs are decreasing the ability of coral
-reefs to provide ecological functions such as benthic habitat and nutrient cycling
-[@forster2021; @williams2019] and services such as food, protection, tourism and Indigenous
-cultural value [@eddy2021; @stoeckl2021].
-
-Coral reef ecosystem resilience - the capacity to maintain coral populations and avoid
+mortality events driven by climate change can cause coral population declines [@hughes2017;
+@hughes2018; @bozec2025], possibly leading to coral-macroalgae regime shifts [@arif2022;
+@wild2011]. Climate impacts on coral reefs are decreasing the ability of coral reefs to
+provide ecological functions such as benthic habitat and nutrient cycling [@forster2021;
+@williams2019] and services such as food, protection, tourism and Indigenous cultural value
+[@eddy2021; @stoeckl2021].
+
+Here, coral reef ecosystem resilience - the capacity to maintain coral populations and avoid
 ecosystem regime shifts - is conceptualised to depend on three interconnected mechanisms.
@@
 Third, the maintenance, and accretion, of the carbonate framework that provides reef
-structure [@perry2012]. This investigation aims to assess how these mechanisms interact
+structure [@perry2012]. This investigation aims to assess how these mechanisms may interact
 under projected climate conditions to identify the characteristics of resilient reefs in the

### 2025-10-10 paper/paper_draft.qmd
Streamline description

@@
 Depths for each reef were extracted using 10m resolution bathymetry data made available in
-GBRMPA [-@GBRMPA2020]. While the bathymetry data are said to be accurate up to 15m from Mean
+GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched with the 3806
+reef outlines through geometric intersection. All depth values were converted to positive
+values (depths below sea level). The median depth was used to provide an indicative depth
+value for each reef. While the bathymetry data are said to be accurate up to 15m from Mean
 Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used
-for this study. Notably, bathymetry data were derived from satellite imagery. The bathymetry
-data can be limited in their alignment with the established GBRMPA reef outlines used to
-characterise reef locations and their areal extent. For each reef, bathymetry data were
-spatially matched with the 3806 reef outlines through geometric intersections. All depth
-values were converted to positive values (depths below sea level). The median depth was used
-to provide an indicative depth value for each reef. Further limitations are outlined in the
-Discussion. Code to extract depth estimates, and the resulting depth estimates themselves,
-are available at [@iwanaga2025].
+for this study. Notably, bathymetry data were derived from satellite imagery and can be
+limited in their alignment with the established GBRMPA reef outlines used to characterise
+reef locations and their areal extent. Further limitations are outlined in the Discussion.
+Code to extract depth estimates, and the resulting depth estimates themselves, are available
+at [@iwanaga2025].
 

### 2025-10-10 paper/paper_draft.qmd
auto-formatting

@@
 | Global Climate Model source | ECS value (°C)     | Interpreted relative severity | Results found in |
-|-----------------------|-----------------------|------------------------|-----------------------|
+|-----------------------|-----------------------|-----------------------|-----------------------|
 | ACCESS-CM2                  | 4.66 [@grose2023]  | High                          | [@grier2025]     |
@@
 magnitude of early bleaching events decreasing the breeding capacity of strongly connected
-reefs. Analysing daily connectivity data Vogt-Vincent, Mitarai and Johnson [-@vogt-vincent2023] suggest
-that time-mean connectivity may not be suitable for capturing the seasonal - ecological time
-scale connectivity between locations due to high daily variability in connectivity data.
-Connectivity matrices used in this investigation have large relative standard deviations for
-larval transition probabilities between reefs over the 24 days used
-(@sfig-connectivity-rsd). Using alternative summarisation methods that capture
-ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
+reefs. Analysing daily connectivity data Vogt-Vincent, Mitarai and Johnson
+[-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for capturing
+the seasonal - ecological time scale connectivity between locations due to high daily
+variability in connectivity data. Connectivity matrices used in this investigation have
+large relative standard deviations for larval transition probabilities between reefs over
+the 24 days used (@sfig-connectivity-rsd). Using alternative summarisation methods that
+capture ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
 connectivity [@vogt-vincent2023], future investigations may find increased importance of
@@
 composition for each functional group as a proportion of the reef’s cover at each
-year.](../figs/coralblox_reef_example.png){#sfig-coralblox-example
-fig-align="center" width="14.82cm"}
+year.](../figs/coralblox_reef_example.png){#sfig-coralblox-example fig-align="center"
+width="14.82cm"}
 
@@
 the second for change in evenness of species
-abundance.](../figs/coralblox_sens_analysis.png){#sfig-coralblox-sa
-fig-align="center" width="14.82cm"}
+abundance.](../figs/coralblox_sens_analysis.png){#sfig-coralblox-sa fig-align="center"
+width="14.82cm"}
 

### 2025-10-11 paper/paper_draft.qmd
Ensure correct julia version is used by Quarto

@@
 engine: julia
+julia:
+  exeflags: ["+1.11.5"]
 crossref:

### 2025-10-11 paper/paper.qmd
Rename paper document for submission

--- 2025-10-10 paper/paper_draft.qmd
@@
 """
-using Markdown,Tables,MarkdownTables
+using Markdown, Tables, MarkdownTables
 cd("../src")

### 2025-10-12 paper/paper.qmd
Minor revisions to proof read text

@@
     environmental factors to assess coral reef resilience across the GBR using projected conditions under
-    five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities. Projected coral
-    cover were analysed for each reefs ability to maintain positive carbonate production budgets under
-    future conditions using coral cover as a proxy. Larval connectivity patterns did not correlate with
+    five Global Climate Models (GCMs). Projected coral
+    cover was analysed for each reef's ability to maintain positive carbonate production budgets under
+    future conditions, using coral cover as a proxy. Larval connectivity patterns did not correlate with
     increases in maintenance of positive carbonate budgets. Instead, reef depth emerged as the primary
@@
 is provided in @tbl-gcms. Note here that Grose et al., [-@grose2023] assessed GFDL-ESM4,
-whereas Dixon et al., [-@dixon2022; -@dixon2023] provides data based on GFDL-CM4. This
+whereas Dixon et al., [-@dixon2022; -@dixon2023] provide data based on GFDL-CM4. This
 substitution is assumed appropriate given they share the same fundamental representation of
@@
 futures to be explored, capturing uncertainty in future responses to CO~2~ increases
-(@fig-methods-dhws; @sfig-ecs;[@grose2023; @shepherd2018]) and enables the assessment of
+(@fig-methods-dhws; @sfig-ecs; @grose2023; @shepherd2018) and enables the assessment of
 modelled coral reef behaviour over a broad range of independently derived climate futures
@@
 The coral larval connectivity model used in this study comprises 3D hourly velocities from
-the 1 km grid resolution hydrodynamic model [GBR-1 version 2.0; @steven2019], as input to
+the 1 km grid resolution hydrodynamic model (GBR-1 version 2.0; @steven2019), as input to
 OceanParcels [@delandmeter2019], a particle tracking model. The connectivity model was used
@@
 clustered into Low, Medium and High clusters respectively. High levels of assignment
-variability across GCMs are expected as due to spatial differences in each given GCM’s DHW
+variability across GCMs are expected due to spatial differences in each given GCM’s DHW
 trajectories.
@@
 marked individually for visual clarity. Reefs that do not have a consistent cluster
-assignment level across all GCMs at mangement area scale are coloured grey. All consistently
-clustered reefs are coloured according to their management area scale cluster assignment.
-Green represents reefs in the low cover cluster, orange represents reefs in the medium cover
-cluster and blue represents reefs in the high cover cluster. All 2197 reefs included in this
-investigation are represented in this figure. Annotations represent major coastal
-settlements along the GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map
-fig-align="center" width="14.82cm"}
+assignment level across all GCMs at management area scale are coloured grey. All
+consistently clustered reefs are coloured according to their management area scale cluster
+assignment. Green represents reefs in the low cover cluster, orange represents reefs in the
+medium cover cluster and blue represents reefs in the high cover cluster. All 2197 reefs
+included in this investigation are represented in this figure. Annotations represent major
+coastal settlements along the
+GBR.](../figs/gcm_cluster_assignment_map.png){#sfig-gcm-cluster-map fig-align="center"
+width="14.82cm"}
 

### 2025-10-13 paper/paper.qmd
Update theta notation in fig caption
Fix: inline citation

@@
 Code to extract depth estimates, and the resulting depth estimates themselves, are available
-at [@iwanaga2025].
+at @iwanaga2025.
 
@@
 connectivity for each reef. Point colours represent the median number of years each reef
-maintains positive carbonate budgets across $theta$ values from 10-20% live coral cover.
+maintains positive carbonate budgets across $\theta$ values from 10-20% live coral cover.
 Displays results for ACCESS-ESM1-5

### 2025-10-13 paper/paper.qmd
Remove unnecessary parentheses
Fix grammar

@@
 shows the relationship between reef median depth, while the right panel shows the same for
-log10-weighted incoming connectivity. Point colour (purple to yellow) represents
-($\theta_0$), with brighter shades indicating a higher $\theta_0$. Deeper reefs have an
+log10-weighted incoming connectivity. Marker colour (purple to yellow) represents
+$\theta_0$, with brighter shades indicating a higher $\theta_0$. Deeper reefs have an
 increased number of years above the considered range of $\theta_0$, while no relationship
@@
 and the ability of reefs to maintain positive carbonate budgets under future conditions was
-found. There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent
-generation connectivity modelling is able to identify reefs that are important for recovery
+found. There has been contrasting evidence [@bode2018; @hock2017] as to whether current
+connectivity modelling is able to identify reefs that are important for recovery
 processes, with findings dependent on the larval connectivity model used. These

### 2025-10-13 paper/paper.qmd
Update format config
Added authors-block extension

Global Change Biology citation style

Fixed/updated bibtex references

@@
 title: Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change
-author:
+
+authors:
   - name: Benjamin Grier
@@
     affiliations:
-        - id: AIMS
-          name: Australian Institute of Marine Science
-          address: Townsville, Queensland, Australia
+      - ref: aims
+    orcid: 0009-0005-1444-6198
     attributes:
       corresponding: true
+
   - name: Takuya Iwanaga
@@
     affiliations:
-        - id: AIMS
-          name: Australian Institute of Marine Science
-          address: Townsville, Queensland, Australia
+      - ref: aims
+    orcid: 0000-0001-8173-0870
+
   - name: Pedro Ribeiro De Almeida
@@
     affiliations:
-        - id: AIMS
-          name: Australian Institute of Marine Science
-          address: Townsville, Queensland, Australia
+      - ref: aims
+    orcid: 0009-0007-4814-3261
+
   - name: Chinenye Ani
@@
     affiliations:
-        - id: AIMS
-          name: Australian Institute of Marine Science
-          address: Townsville, Queensland, Australia
+      - ref: aims
+    orcid: 0000-0002-2112-0840
+
   - name: Sam Matthews
@@
     affiliations:
-        - id: AIMS
-          name: Australian Institute of Marine Science
-          address: Townsville, Queensland, Australia
+      - ref: aims
+    orcid: 0000-0003-1936-1220
+
+affiliations:
+  - id: aims
+    name: Australian Institute of Marine Science, Townsville, Queensland, Australia
+
 abstract: |
@@
   - Reef connectivity
+
+filters:
+  - _extensions/authors-block
+
 date: last-modified
+
 format:
@@
     journal:
-      name: Journal Name
+      name: Global Change Biology
       formatting: preprint
       cite-style: authoryear
+
 bibliography: references.bib
+csl: global-change-biology.csl
+
 engine: julia
+julia:
+  exeflags: ["+1.11.5"]
+
 crossref:
@@
     key: stbl
+
 editor:

### 2025-10-13 paper/paper.qmd
Reorder last sections
GCB uses CRediT https://authorservices.wiley.com/author-resources/Journal-Authors/open-access/credit.html

Final statements should come before references, previously the references where placed in between.
Fix format/citation style

@@
 adopted to align with other ongoing modelling and analyses conducted as part of the Reef
-Restoration and Adaptation Program (<https://gbrrestoration.org>; RRAP [-@thereef]).
+Restoration and Adaptation Program (<https://gbrrestoration.org>; RRAP -@thereef).
 
@@
 
-# References
-
-::: {#refs}
-:::
-
-# Author Contributions
+# CRediT Statement
 
@@
 Grier and Iwanaga [-@grier2025].
+
+# References
+
+::: {#refs}
+:::
 

### 2025-10-13 paper/paper.qmd
Remove statement from acknowledgement
No ecoRRAP data was used

@@
 the Australian Institute of Marine Science. The authors acknowledge thermal projection data
-sourced from HighResCoralStress datasets, model parameterisation data sourced from the
-Ecological Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition
-probability data derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data
-available from the Great Barrier Reef Marine Park Authority. The eReefs Project is a
-public-private collaboration between Australia’s leading operational and scientific research
-agencies, government, and corporate Australia.
+sourced from HighResCoralStress datasets, larval transition probability data derived from
+the eReefs GBR1 hydrodynamic model, and spatial and depth data available from the Great
+Barrier Reef Marine Park Authority. The eReefs Project is a public-private collaboration
+between Australia’s leading operational and scientific research agencies, government, and
+corporate Australia.
 

### 2025-10-13 paper/paper.qmd
Provide link to available data directly
Fix citation style again!
Updates according to SM's comments. (Not including connectivity related comments until confirmation!)

@@
     increases in maintenance of positive carbonate budgets. Instead, reef depth emerged as the primary
-    predictor, with deeper reefs benefitting from thermal refugia that reduce bleaching impacts. These
+    predictor, with deeper reefs benefitting from reduced thermal exposure. These
     findings suggest that depth is a tangible and pragmatic reef characteristic to consider in future
     intervention practices for coral reef restoration. These results have important implications for reef
-    management, indicating that depth refugia should be prioritized for further consideration in
+    management, indicating that depth should be considered as a key variable in
     conservation planning to maximize coral survival under continuing climate change.
@@
 The GBR is the world's largest coral reef ecosystem consisting of thousands of individual
-reefs interconnected through larval dispersal patterns mediated by hydrodynamic, spatial,
+reefs interconnected through larval dispersal pathways mediated by hydrodynamic, spatial,
 and ecological processes [@cappo2000]. The GBR faces severe projected coral cover declines
@@
 Summer mass bleaching event may be signalling a shift towards this reef future, with some
-level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
-[@australianinstituteofmarinescience2024; @cantin2024].
+level of bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs),
+representing the most widespread bleaching event on the GBR and largest single year decline
+in the history of the Long Term Monitoring Program (LTMP;
+@australianinstituteofmarinescience2024; @cantin2024).
 
 At the individual coral scale, survival during thermal stress events depends on both
-environmental and biological factors that can either amplify or reduce thermal stress. Depth
-is a crucial factor that can provide a refuge from thermal stress [@álvarez-noriega2018;
-@baird2018; @smith2014]. Biological factors including coral size [@brandt2009], taxa
-[@álvarez-noriega2018; @mcclanahan2005], and thermal tolerance through acclimation and
-inheritance [@humanes2022; @lachs2024] all influence survival outcomes. Corals demonstrate
-adaptive capacity to develop thermal tolerance that could delay widespread bleaching under
-moderate emission scenarios [@bairos-novak2021; @humanes2022], representing a crucial
-mechanism for reef persistence.
-
-Beyond individual survival, reef-scale resilience depends on connectivity networks that
-enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017]. Larval
-source populations that export more larvae than they import are essential for system-wide
-recovery, providing larvae that enable recolonization at distant locations [@hock2017;
-@thomas2015]. Yet these source reefs are paradoxically more vulnerable individually, relying
-heavily on local recruitment for their own recovery. When disturbances impact major source
-populations, cascading effects reduce larval export and slow recovery throughout the
-connected network [@figueiredo2022; @hock2017; @munday2009].
+environmental and biological factors that can either amplify or reduce the effects of
+thermal stress. Depth is a crucial factor that can provide a refuge from thermal stress
+[@álvarez-noriega2018; @baird2018; @smith2014]. Biological factors including coral size
+[@brandt2009], taxa [@álvarez-noriega2018; @mcclanahan2005], and thermal tolerance through
+acclimation and inheritance [@humanes2022; @lachs2024] all influence survival outcomes.
+Corals demonstrate adaptive capacity to develop thermal tolerance that could delay
+widespread bleaching under moderate emission scenarios [@bairos-novak2021; @humanes2022],
+representing a crucial mechanism for reef persistence.
+
+Beyond individual survival, reef-scale resilience in part depends on connectivity networks
+that enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017].
+Larval source populations that export more larvae than they import are essential for
+system-wide recovery, providing larvae that enable recolonization at distant locations
+[@hock2017; @thomas2015]. Yet these source reefs are paradoxically more vulnerable
+individually, relying heavily on local recruitment for their own recovery. When disturbances
+impact major source populations, cascading effects reduce larval export and slow recovery
+throughout the connected network [@figueiredo2022; @hock2017; @munday2009].
 
@@
 found. There has been contrasting evidence [@bode2018; @hock2017] as to whether current
-connectivity modelling is able to identify reefs that are important for recovery
-processes, with findings dependent on the larval connectivity model used. These
-investigations were performed using prior generations of larval connectivity models
-parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods, without
-considering the influence of reef depth on resilience. Using updated 1km^2^ resolution
-larval connectivity across the whole GBR, with a limited temporal sample of particle flows,
-it was found that larval connectivity alone may not be important or reef resilience and
-recovery but should be considered in combination with more influential factors such as
-depth.
+connectivity modelling is able to identify reefs that are important for recovery processes,
+with findings dependent on the larval connectivity model used. These investigations were
+performed using prior generations of larval connectivity models parameterised for 2008-2013
+[@hock2017] and 1996-2002 [@bode2018] time periods, without considering the influence of
+reef depth on resilience. Using updated 1km^2^ resolution larval connectivity across the
+whole GBR, with a limited temporal sample of particle flows, it was found that larval
+connectivity alone may not be important or reef resilience and recovery but should be
+considered in combination with more influential factors such as depth.
 
 Findings on the importance of connectivity likely differ from literature due to the highly
-uncertain nature of larval connectivity modelling [@choukroun2025; @vogt-vincent2023], the
-way larval flows and juvenile recruitment are implemented in ADRIA - CoralBlox, and the
-magnitude of early bleaching events decreasing the breeding capacity of strongly connected
-reefs. Analysing daily connectivity data Vogt-Vincent, Mitarai and Johnson
-[-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for capturing
-the seasonal - ecological time scale connectivity between locations due to high daily
-variability in connectivity data. Connectivity matrices used in this investigation have
-large relative standard deviations for larval transition probabilities between reefs over
-the 24 days used (@sfig-connectivity-rsd). Using alternative summarisation methods that
+uncertain nature of larval connectivity modelling [@choukroun2025; @vogt-vincent2023] and
+the way larval flows and juvenile recruitment are implemented in ADRIA - CoralBlox.
+Additionally, and the high magnitude of early bleaching events (2025-2035) may decrease the
+breeding capacity of strongly connected reefs, resulting in reduced importance of
+connectivity in recovery. Analysing daily connectivity data Vogt-Vincent, Mitarai and
+Johnson [-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for
+capturing the seasonal - ecological time scale connectivity between locations due to high
+daily variability in connectivity data. Connectivity matrices used in this investigation
+have large relative standard deviations for larval transition probabilities between reefs
+over the 24 days used (@sfig-connectivity-rsd). Using alternative summarisation methods that
 capture ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
@@
 adopted to align with other ongoing modelling and analyses conducted as part of the Reef
-Restoration and Adaptation Program (<https://gbrrestoration.org>; RRAP -@thereef).
+Restoration and Adaptation Program (<https://gbrrestoration.org>; RRAP [-@thereef]).
 
@@
 The full reproducible investigation, and links to required data sources, can be found at
-Grier and Iwanaga [-@grier2025].
+Grier and Iwanaga ([-@grier2025]; https://doi.org/10.5281/zenodo.17333564).
 

### 2025-10-15 paper/paper.qmd
Updates to script 7 and paper markdown to remove source to sink connectivity ratio from results

@@
 by incoming connectivity (weighted incoming connectivity), outgoing connectivity (outgoing
-connection strength), the ratio of source-to-sink connectivity, and larval retention
+connection strength), and larval retention
 probability for each reef. Weighted incoming connectivity was calculated by summing the
@@
 reproducing and producing larvae, instead it takes total coral cover area as an indicator of
-larval productivity.
-
-Outgoing connection strength was calculated as the sum of all outgoing transition
+larval productivity. Outgoing connection strength was calculated as the sum of all outgoing transition
 probabilities from a target reef. Outgoing connection strength has a theoretical maximum of
 one (all larvae reach settlement on sink reefs), however the large size of the GBR combined
-with larval mortality result in much lower outgoing connection strength values. The ratio of
-source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
-outgoing larval flow relative to it's incoming larval flow. This is calculated as:
-$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of connectivity probabilities,
-$N$ represents the number of connections, $O$ denotes outgoing connectivity from the target
-reef and $I$ denotes incoming connectivity to the target reef. If a reef has no incoming
-connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this calculation,
-do not directly represent the larval supply gained as the breeding populations from which
-connections are coming from are not represented. A source-to-sink ratio greater than 1 (a
-value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
-larval flow. Reef larval retention probability indicates the proportion of spawned larvae
+with larval mortality result in much lower outgoing connection strength values. Reef larval retention probability indicates the proportion of spawned larvae
 that settle on their natal reefs.
@@
 characteristics include reef median depth, mean time series DHW, weighted incoming
-connectivity, outgoing connection strength, ratio of source-to-sink larval connectivity,
+connectivity, outgoing connection strength,
 larval retention probability and reef carrying capacity (coral habitable area).
@@
 cross-validation was also conducted, arriving at a similar 59% accuracy rate. F1 performance
-scores for Low, Medium, and High clusters were determined to be 0.70, 0.43 and 0.64
-respectively, with precision of 0.62, 0.51 and 0.66 when evaluated with the test set
+scores for Low, Medium, and High clusters were determined to be 0.70, 0.42 and 0.63
+respectively, with precision of 0.63, 0.48 and 0.64 when evaluated with the test set
 (consisting of 4394 samples) (@stbl-confusion-matrix; @stbl-rf-cluster-performance). Lower
@@
 Partial Dependence Analysis revealed reef median depth, carrying capacity and mean time
-series DHW level have the highest feature importance scores, accounting for 29%, 15% and 15%
-predictive importance respectively (@fig-ts-cluster-pdp; Panel A). Source-cover weighted
-incoming connectivity, outgoing connectivity strength, source-to-sink connectivity ratio and
-larval retention probability account for \~12%, 11%, 10% and 8% respectively.
+series DHW level have the highest feature importance scores, accounting for 32%, 16% and 15%
+predictive importance respectively (@fig-ts-cluster-pdp; Panel A). Outgoing connectivity strength, Source-cover weighted
+incoming connectivity and
+larval retention probability account for \~14%, 14%, and 10% respectively.
 
@@
 
-First-order PDA showed minimal influence of incoming, outgoing and source-to-sink ratio
+First-order PDA showed minimal influence of incoming and outgoing
 connectivity metrics on cluster assignment probabilities. Two-way analyses revealed little
@@
 | Mean time series DHW | Time series cluster assessment | Reef mean DHW value across time series | To quantify the surface thermal stress experienced on each reef over time series. |
-| Source - to - sink connectivity ratio | Time series cluster assessment | Ratio of reef outgoing to incoming connectivity | To examine whether a reef may be a 'net contributor' or 'net receiver' of larvae in the connectivity network.
-|
 | Weighted incoming connectivity | Time series cluster assessment, Carbonate budget analysis | Incoming connectivity strength weighted by mean time series coral cover of source reefs | To approximate the larval flow received by a reef over the projected time series.
@@
 represent the bioregion accuracy across various predictor ranges and bioregion attributes,
-such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength,
-Source-to-sink ratio and the number of reefs in each
+such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength and the number of reefs in each
 bioregion.](../figs/rf_performance_across_predictors.png){#sfig-rf-predictor-perf
@@
 width="14.82cm"}
-
-![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
-considered reefs (points), coloured by source-to-sink connectivity ratio (log10).
-Colour-coded areas outline GBR marine park management regions, where orange represents the
-Far Northern management region, green represents Cairns/Cooktown, red covers
-Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
-marked individually for visual clarity. Darker colours represent higher source-to-sink
-values than lighter colours. Source-to-sink ratio values above zero (one on normal scale)
-indicate a reef has greater outgoing than incoming connectivity. All 2197 reefs included in
-this investigation are represented in this figure. Annotations represent major coastal
-settlements along the GBR.](../figs/log_so_to_si_input_map.png){#sfig-sotosi-conn-map
-fig-align="center" width="14.82cm"}
 
@@
 (@sfig-access-esm1-5-bioregion-weightedincoming), log10 outgoing connection strength
-(@sfig-access-esm1-5-bioregion-outgoingconn), log10 source-to-sink connectivity ratio
-(@sfig-access-esm1-5-bioregion-logsosi) and log10 larval retention probability
+(@sfig-access-esm1-5-bioregion-outgoingconn) and log10 larval retention probability
 (@sfig-access-esm1-5-bioregion-selfconn). Across six of the 29 bioregions reefs in the high
@@
 cluster.](../figs/ACCESS-ESM1-5/bioregion/carrying_capacity_bioregion_violin.png){#sfig-access-esm1-5-bioregion-carrying-capacity
-fig-align="center" width="14.82cm"}
-
-![Source-to-sink connectivity ratios (in base-10 log scale) for reefs within each bioregion,
-separated into clusters assigned by time series clustering, under ACCESS-ESM1-5. Time series
-were clustered based on their behaviour between 2030 and 2060. Time series with
-comparatively low median area-relative cover is indicated in green, intermediate cover in
-orange, and high in blue. Solid lines within each violin represent the median source-to-sink
-ratio for each cluster and bands represent the distribution of source-to-sink ratios within
-each cluster. The vertical grey line represent a source-to-sink ratio of 0 (in base-10 log
-scale) indicating equal outgoing and incoming connectivity
-levels.](../figs/ACCESS-ESM1-5/bioregion/so_to_si_bioregion_violin.png){#sfig-access-esm1-5-bioregion-logsosi
 fig-align="center" width="14.82cm"}
@@
 | **Predicted** | **Low** | **Medium**       | **High** |
-| **Low**       | 1371    | 682              | 151      |
-| **Medium**    | 247     | 603              | 340      |
-| **High**      | 97      | 302              | 787      |
+| **Low**       | 1336    | 633              | 138      |
+| **Medium**    | 297     | 556              | 310      |
+| **High**      | 78      | 324              | 722      |
 
@@
 | **Test samples** | 1715    | 1587       | 1278     |
-| **Precision**    | 0.622   | 0.507      | 0.664    |
-| **Recall**       | 0.799   | 0.38       | 0.616    |
-| **F1**           | 0.7     | 0.434      | 0.639    |
+| **Precision**    | 0.634   | 0.478      | 0.642    |
+| **Recall**       | 0.781   | 0.367      | 0.617    |
+| **F1**           | 0.7     | 0.416      | 0.629    |
 

### 2025-10-15 src/ADRIA/HighResCoralStress/7_rf_analysis.jl

@@ -27,7 +27,7 @@ gcm_dhw_cols = [Symbol("$(GCM)_mean_dhw") for GCM in GCMs]
 gcm_bioregion_cluster_cols = [Symbol("$(GCM)_bioregion_clusters") for GCM in GCMs]
 
 collated_reef_properties = Vector{DataFrame}(undef, length(GCMs))
-target_cols = [:UNIQUE_ID, :GBRMPA_ID, :depth_med, :log_so_to_si, :bioregion, :bioregion_average_latitude, :log_out_strength, :log_self_strength]
+target_cols = [:UNIQUE_ID, :GBRMPA_ID, :depth_med, :bioregion, :bioregion_average_latitude, :log_out_strength, :log_self_strength]
 reef_properties = context_layers[:, target_cols]
 reef_properties.abs_k_area = context_layers.area .* context_layers.k
 for (i, GCM) in enumerate(GCMs)
@@ -57,7 +57,7 @@ reef_properties.GCM .= categorical(reef_properties.GCM)
 reef_properties.bioregion .= categorical(reef_properties.bioregion)
 reef_properties.abs_k_area ./= 1e6  # Convert to km^2 for clarity
 
-target_cols = [:depth_med, :log_so_to_si, :mean_dhw, :abs_k_area, :weighted_incoming_conn, :log_out_strength, :log_self_strength]
+target_cols = [:depth_med, :mean_dhw, :abs_k_area, :weighted_incoming_conn, :log_out_strength, :log_self_strength]
 Xs = reef_properties[:, target_cols]
 y = vec(reef_properties[:, :cluster])
 y = Int64.(getfield.(y, :ref))
@@ -73,7 +73,6 @@ y2 = categorical(map(x -> d[x], y), levels=["low", "med", "high"], ordered=true)
 X2 = coerce(
     X2,
     :depth_med => Continuous,
-    :log_so_to_si => Continuous,
     :mean_dhw => Continuous,
     :abs_k_area => Continuous,
     :weighted_incoming_conn => Continuous,
@@ -85,7 +84,6 @@ readable_names = OrderedDict(
     "mean_dhw" => "Mean DHW",
     "depth_med" => "Median Depth",
     "abs_k_area" => "Carrying Capacity",
-    "log_so_to_si" => "Log10 Outgoing to Incoming\nConnectivity Ratio",
     "weighted_incoming_conn" => "Log10 Weighted\nIncoming Connectivity",
[…]

### 2025-10-15 paper/paper.qmd
Update to professional email
Incorporate Shaun Wilson's suggestions

@@
   - name: Benjamin Grier
-    email: grierben777@gmail.com
+    email: bengrier1@outlook.com
     affiliations:
@@
     increases in maintenance of positive carbonate budgets. Instead, reef depth emerged as the primary
-    predictor, with deeper reefs benefitting from reduced thermal exposure. These
+    predictor, with deeper reefs (>10m) benefitting from reduced thermal exposure. These
     findings suggest that depth is a tangible and pragmatic reef characteristic to consider in future
@@
 @hughes2018; @bozec2025], possibly leading to coral-macroalgae regime shifts [@arif2022;
-@wild2011]. Climate impacts on coral reefs are decreasing the ability of coral reefs to
+@graham2015]. Climate impacts on coral reefs are decreasing the ability of coral reefs to
 provide ecological functions such as benthic habitat and nutrient cycling [@forster2021;
@@
 by incoming connectivity (weighted incoming connectivity), outgoing connectivity (outgoing
-connection strength), and larval retention
-probability for each reef. Weighted incoming connectivity was calculated by summing the
-product of each connection strength incoming to a target reef (excluding retained larvae
-from the target reef) and the mean timeseries absolute coral cover (km^2^) of each matching
-source reef. This metric provides an approximation of overall larval flow into a reef, with
-high values indicating the target reef is supplied high volumes of larvae via strong
-connections and low values indicating the target reef has weak (or no) incoming connections
-or is supplied by small source populations. A limitation of weighted incoming connectivity
-is that it does not incorporate the proportion of the source reef's population that is
-reproducing and producing larvae, instead it takes total coral cover area as an indicator of
-larval productivity. Outgoing connection strength was calculated as the sum of all outgoing transition
-probabilities from a target reef. Outgoing connection strength has a theoretical maximum of
-one (all larvae reach settlement on sink reefs), however the large size of the GBR combined
-with larval mortality result in much lower outgoing connection strength values. Reef larval retention probability indicates the proportion of spawned larvae
-that settle on their natal reefs.
+connection strength), and larval retention probability for each reef. Weighted incoming
+connectivity was calculated by summing the product of each connection strength incoming to a
+target reef (excluding retained larvae from the target reef) and the mean timeseries
+absolute coral cover (km^2^) of each matching source reef. This metric provides an
+approximation of overall larval flow into a reef, with high values indicating the target
+reef is supplied high volumes of larvae via strong connections and low values indicating the
+target reef has weak (or no) incoming connections or is supplied by small source
+populations. A limitation of weighted incoming connectivity is that it does not incorporate
+the proportion of the source reef's population that is reproducing and producing larvae,
+instead it takes total coral cover area as an indicator of larval productivity. Outgoing
+connection strength was calculated as the sum of all outgoing transition probabilities from
+a target reef. Outgoing connection strength has a theoretical maximum of one (all larvae
+reach settlement on sink reefs), however the large size of the GBR combined with larval
+mortality result in much lower outgoing connection strength values. Reef larval retention
+probability indicates the proportion of spawned larvae that settle on their natal reefs.
 
@@
 characteristics include reef median depth, mean time series DHW, weighted incoming
-connectivity, outgoing connection strength,
-larval retention probability and reef carrying capacity (coral habitable area).
+connectivity, outgoing connection strength, larval retention probability and reef carrying
+capacity (coral habitable area).
 
@@
 reefs in the High cover cluster, with Medium and Low exhibiting lesser probability of such
-periods of recovery. Generally, recovery and increases in coral cover were visible in
-simulated results up to 2045. Under NorESM2-MM, the Far Northern Management area was found
-to have the most similar temporal behaviour between Low and High clusters compared to other
-Management areas (@stbl-cluster-cid) due to the low degree of coral cover overall
+periods of recovery. The High cover cluster exhibits greater resilience despite encompassing
+a broad range of initial coral cover conditions at 2025 (\@fig-gcm-cover-trajectories).
+Generally, recovery and increases in coral cover were visible in simulated results up to
+2045. Under NorESM2-MM, the Far Northern Management area was found to have the most similar
+temporal behaviour between Low and High clusters compared to other Management areas
+(@stbl-cluster-cid) due to the low degree of coral cover overall
 (@fig-gcm-cover-trajectories).
@@
 Partial Dependence Analysis revealed reef median depth, carrying capacity and mean time
-series DHW level have the highest feature importance scores, accounting for 32%, 16% and 15%
-predictive importance respectively (@fig-ts-cluster-pdp; Panel A). Outgoing connectivity strength, Source-cover weighted
-incoming connectivity and
-larval retention probability account for \~14%, 14%, and 10% respectively.
-
-Reefs have the greatest probability of being clustered into Low if shallow, and High at
-greater depths, with medium cluster reefs exhibiting a lower, and more stable, assignment
+series DHW level have the highest feature importance scores for bioregion-scale cluster
+assignment, accounting for 32%, 16% and 15% predictive importance respectively
+(@fig-ts-cluster-pdp; Panel A). Outgoing connectivity strength, Source-cover weighted
+incoming connectivity and larval retention probability account for \~14%, 14%, and 10%
+respectively.
+
+Reefs have the greatest probability of being clustered into Low if shallow (\<10m), and High
+at greater depths, with medium cluster reefs exhibiting a lower, and more stable, assignment
 probability across depth ranges (@fig-ts-cluster-pdp; Panel B). A large increase in the
 probability of a reef being categorised as High can be seen between 10 and 15 meters depth.
-This is at the edge of the depth range used in current deployment efforts [@howlett2021;
-@randall2021; @whitman2024] but indicates a depth range that could be adopted to maximise
-longevity and benefits of, for example, coral seeding activities. Across mean DHW values,
-assignment probability is roughly equal across the three clusters up to 5 DHW. A sharp
-delineation can be seen \> 5 DHW when comparing High with other clusters, with lower
-assignment probability (\~25%) compared to Medium and Low (\~40%) (@fig-ts-cluster-pdp;
-Panel B).
+Across mean DHW values, assignment probability is roughly equal across the three clusters up
+to 5 DHW. A sharp delineation can be seen \> 5 DHW when comparing High with other clusters,
+with lower assignment probability (\~25%) compared to Medium and Low (\~40%)
+(@fig-ts-cluster-pdp; Panel B).
 
@@
 
-First-order PDA showed minimal influence of incoming and outgoing
-connectivity metrics on cluster assignment probabilities. Two-way analyses revealed little
-interaction between depth and incoming and outgoing connectivity metrics for reef clustering
-probabilities (@fig-ts-cluster-pdp-twoway-incoming; @sfig-ts-cluster-pdp-twoway-outgoing).
-Reefs with a median depth around 15m and high incoming connectivity may benefit slightly,
+First-order PDA showed minimal influence of incoming and outgoing connectivity metrics on
+cluster assignment probabilities. Two-way analyses revealed little interaction between depth
+and incoming and outgoing connectivity metrics for reef clustering probabilities
+(@fig-ts-cluster-pdp-twoway-incoming; @sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a
+median depth around 15m may benefit slightly from high incoming and outgoing connectivity,
 with higher probability of High cover cluster assignment compared to 15m - depth reefs with
@@
 Townsville/Whitsunday, and Mackay/Capricorn management areas (@sfig-depth-map;
-@sfig-carb-budget-map). Resilient reefs in the Far Northern management area were exposed to
+@sfig-carb-budget-map). High cover reefs in the Far Northern management area were exposed to
 lower mean DHW levels than other reefs under ACCESS-ESM1-5 (@sfig-mean-dhw-map), however
@@
 Peoples, the lands on which the authors conducted the model development, analysis, and
-writing. The authors also acknowledge the contributions of Barbara Robson and Jessica
-Benthuysen for comments provided early in the manuscript preparation. The authors would like
-to additionally acknowledge and thank Shaun Wilson and Juan Carlos Ortiz for discussions
-around carbonate budget thresholds.
+writing. The authors would like to acknowledge and thank Shaun Wilson for comments and
+discussion during manuscript revision. The authors also acknowledge the contributions of
+Barbara Robson and Jessica Benthuysen for comments provided early in the manuscript
+preparation. The authors would like to additionally acknowledge and thank Shaun Wilson and
+Juan Carlos Ortiz for discussions around carbonate budget thresholds.
 
@@
 represent the bioregion accuracy across various predictor ranges and bioregion attributes,
-such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength and the number of reefs in each
+such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength and
+the number of reefs in each
 bioregion.](../figs/rf_performance_across_predictors.png){#sfig-rf-predictor-perf

### 2025-10-15 paper/paper.qmd
Update with additional comments from Sam

@@
 that enable recolonization after disturbances [@angeler2023; @elmhirst2009; @hock2017].
-Larval source populations that export more larvae than they import are essential for
-system-wide recovery, providing larvae that enable recolonization at distant locations
-[@hock2017; @thomas2015]. Yet these source reefs are paradoxically more vulnerable
-individually, relying heavily on local recruitment for their own recovery. When disturbances
-impact major source populations, cascading effects reduce larval export and slow recovery
-throughout the connected network [@figueiredo2022; @hock2017; @munday2009].
+Larval source populations that have disproportionately numerous and/or strong connections to
+other reefs are essential for system-wide recovery, providing larvae that enable recovery at
+other reefs after disturbance [@hock2017; @thomas2015]. When disturbances impact major
+source populations, cascading effects reduce larval export and slow recovery throughout the
+connected network [@figueiredo2022; @hock2017; @munday2009]. Identifying and protecting
+source reefs has understandably been a major focus of research and management in recent
+years [@greatba2017].
 
@@
 persistence under different scenarios. While connectivity has been emphasized as critical
-for GBR resilience [@hock2017], and remains an important consideration, integrated modelling
-reveals depth plays a fundamental role for maintenance of reef coral populations and
-positive carbonate budgets under current projections of climate change.
+for GBR resilience [@hock2017], and remains an important consideration, our integrated
+modelling approach reveals that depth emerges as a dominant predictor for maintenance of
+reef coral populations and positive carbonate budgets under current projections of climate
+change.
 

### 2025-10-18 paper/paper.qmd
Clarify connectivity particle release
Minor fix to formatting
Tweak wording to address concerns
Also adds a reference

@@
     environmental factors to assess coral reef resilience across the GBR using projected conditions under
-    five Global Climate Models (GCMs). Projected coral
-    cover was analysed for each reef's ability to maintain positive carbonate production budgets under
-    future conditions, using coral cover as a proxy. Larval connectivity patterns did not correlate with
-    increases in maintenance of positive carbonate budgets. Instead, reef depth emerged as the primary
-    predictor, with deeper reefs (>10m) benefitting from reduced thermal exposure. These
-    findings suggest that depth is a tangible and pragmatic reef characteristic to consider in future
-    intervention practices for coral reef restoration. These results have important implications for reef
-    management, indicating that depth should be considered as a key variable in
-    conservation planning to maximize coral survival under continuing climate change.
+    five Global Climate Models (GCMs). Projected coral cover was analysed for each reef's ability to maintain positive
+    carbonate production budgets under future conditions, using coral cover as a proxy. Larval connectivity patterns
+    did not correlate with increases in maintenance of positive carbonate budgets. Instead, reef depth emerged as the
+    primary predictor, with deeper reefs (>10m) benefitting from reduced thermal exposure. These findings suggest that
+    depth is a tangible and pragmatic reef characteristic to consider in future intervention practices for coral reef
+    restoration. These results have important implications for reef management, indicating that depth should be
+    considered as a key variable in conservation planning to maximize coral survival under continuing climate change.
 
@@
 [@conradt2024; @lempert2013]. The approach embraces uncertainty as an inherent
-characteristic of complex environmental systems [@lempert2010; @lempert2013] to address
-limitations of calibrated ecosystem models that use a singular set of parameter values
-[@lubianabotelho2025]. Exploratory scenario modelling is a core methodology underpinning the
-development of robust and adaptive management strategies [@haasnoot2013].
+characteristic of complex environmental systems [@lempert2010; @lempert2013]. Exploratory
+scenario modelling is a core methodology underpinning the development of robust and adaptive
+management strategies [@haasnoot2013].
+
+Recent critiques have raised concerns around the use of calibrated ecological models - which
+often have poor predictive capacity - for decision support [@lubianabotelho2025]. Here, the
+focus is on exploring the climatic and physical context that pertain to management decisions
+to understand the range of conditions under which conclusions hold true, rather than
+providing precise forecasts of future state. These environmental factors often set the
+context which influences ecological outcomes and have more manageable uncertainties than the
+precise ecological parameterisations [@reichert2005].
 
@@
 language [@bezanson2017], with visualisations created using the Makie plotting ecosystem
-[@danisch2021]. Code used to process DHW data and perform analyses involved in this
-investigation can be found at Grier and Iwanaga [-@grier2025].
+[@danisch2021]. Code used to process DHW data, perform analyses, and create figures for this
+investigation are openly published and can be found in Grier and Iwanaga [-@grier2025].
 
@@
 2.25 m below the surface. In each of the reef polygons, 401 particles were released
-resulting in a total of 1,526,206 particles every night of spawning. The model was run for
-30 days with a 3-minute timestep, and the locations of the released particles were updated
-every 15 minutes until the end of the simulation. Larvae were assumed to become competent to
-settle from 4 to 28 days post release with a daily mortality rate of 0.4 [@ani2024], which
-was implemented in 15-minute timestep as probabilistic mortality, corresponding to 0.0053
-mortality rate per timestep. To incorporate the stochastic sensory behaviour of larvae
-during settlement, a 0.01 probability of settlement is assumed when larvae are over a reef
-during the competency period per 15-minute timestep. The information obtained on larvae
-settlement was used to compute a connectivity matrix among reef polygons for each spawning
-night (see Ani et al. [-@ani2024] for more details). A total of 24 connectivity matrices
-were generated for the spawning nights that were considered.
+resulting in a total of 1,526,206 particles every night of spawning across the GBR. The
+model was run for 30 days with a 3-minute timestep, and the locations of the released
+particles were updated every 15 minutes until the end of the simulation. Larvae were assumed
+to become competent to settle from 4 to 28 days post release with a daily mortality rate of
+0.4 [@ani2024], which was implemented in 15-minute timestep as probabilistic mortality,
+corresponding to 0.0053 mortality rate per timestep. To incorporate the stochastic sensory
+behaviour of larvae during settlement, a 0.01 probability of settlement is assumed when
+larvae are over a reef during the competency period per 15-minute timestep. The information
+obtained on larvae settlement was used to compute a connectivity matrix among reef polygons
+for each spawning night (see Ani et al. [-@ani2024] for more details). A total of 24
+connectivity matrices were generated for the spawning nights that were considered.
 
@@
 
-Two systems were employed to explore scenarios: ADRIA (the Adaptive Dynamic Reef
+Two modelling systems were employed to explore scenarios: ADRIA (the Adaptive Dynamic Reef
 Intervention Algorithms platform) and CoralBlox, referred to as the coupled framework

### 2025-10-20 paper/paper.qmd
Incorporate Sam's final changes

@@
 ---
-title: Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change
+title: Depth refugia for reef persistence in the GBR
 
@@
 engine: julia
-julia:
-  exeflags: ["+1.11.5"]
+exeflags: ["--project=."]
 
@@
     canonical: true
+citeproc: true
 ---
@@
 representing the most widespread bleaching event on the GBR and largest single year decline
-in the history of the Long Term Monitoring Program (LTMP;
-@australianinstituteofmarinescience2024; @cantin2024).
+in the history of the Long Term Monitoring Program [LTMP,
+@australianinstituteofmarinescience2024; @cantin2024].
 
@@
 available via the Great Barrier Reef Marine Park Authority (GBRMPA). Reef definitions
-outline 3806 reefs across the GBR [@GBRMPA2022] (@fig-region-map). Prior analyses by Bozec
-et al. [-@bozec2022] provided estimates of coral carrying capacity for each reef that were
-adopted by this study.
+outline 3806 reefs across the GBR (@fig-region-map; GBRMPA [-@GBRMPA2022]). Prior analyses
+by Bozec et al. [-@bozec2022] provided estimates of coral carrying capacity for each reef
+that were adopted by this study.
 
@@
 futures to be explored, capturing uncertainty in future responses to CO~2~ increases
-(@fig-methods-dhws; @sfig-ecs; @grose2023; @shepherd2018) and enables the assessment of
+(@fig-methods-dhws; @sfig-ecs; [@grose2023; @shepherd2018]) and enables the assessment of
 modelled coral reef behaviour over a broad range of independently derived climate futures
@@
 GCM results are found. GCMs in context with assessed plausible ranges of ECS values are
-displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the likely ECS
+displayed in (@sfig-ecs). ACCESS-ESM1-5 has an ECS closest to the midpoint of the likely ECS
 range and was taken as an intermediate model with results displayed in the main text.
@@
 The coral larval connectivity model used in this study comprises 3D hourly velocities from
-the 1 km grid resolution hydrodynamic model (GBR-1 version 2.0; @steven2019), as input to
+the 1 km grid resolution hydrodynamic model [GBR-1 version 2.0, @steven2019], as input to
 OceanParcels [@delandmeter2019], a particle tracking model. The connectivity model was used
@@
 obtained on larvae settlement was used to compute a connectivity matrix among reef polygons
-for each spawning night (see Ani et al. [-@ani2024] for more details). A total of 24
-connectivity matrices were generated for the spawning nights that were considered.
+for each spawning night (see @ani2024 for more details). A total of 24 connectivity matrices
+were generated for the spawning nights that were considered.
 
@@
 was conducted at three spatial scales: (1) the whole of GBR; (2) each GBR management area;
-and (3) for each reefal bioregion (defined in GBRMPA [-@GBRMPA2024]). Analyses were
-conducted at the different spatial scales as, conceptually, the temporal behaviour
-constituting "low", "medium" or "high" coral cover may differ at different spatial scales.
-Analyses at the whole-of-GBR scale were found to lead to identical conclusions regarding
-reef characteristics which influence coral cover and so for brevity are not shown here.
+and (3) for each reefal bioregion (defined in @GBRMPA2024). Analyses were conducted at the
+different spatial scales as, conceptually, the temporal behaviour constituting "low",
+"medium" or "high" coral cover may differ at different spatial scales. Analyses at the
+whole-of-GBR scale were found to lead to identical conclusions regarding reef
+characteristics which influence coral cover and so for brevity are not shown here.
 
@@
 periods of recovery. The High cover cluster exhibits greater resilience despite encompassing
-a broad range of initial coral cover conditions at 2025 (\@fig-gcm-cover-trajectories).
+a broad range of initial coral cover conditions at 2025 (@fig-gcm-cover-trajectories).
 Generally, recovery and increases in coral cover were visible in simulated results up to
@@
 Reef median depth had a moderate positive correlation with the number of years a reef
-maintains coral cover above the assumed carbonate budget threshold required to sustain live
-coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
-that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
+maintains coral cover above the assumed threshold required to sustain a positive carbonate
+budget ($\theta_{0}$). Greater median depth was a key characteristic defining reefs that
+sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
 @sfig-access-esm1-5-carb-budget-corr; @sfig-access-esm1-5-mean-carb-budget). Unsurprisingly,
@@
 whole GBR, with a limited temporal sample of particle flows, it was found that larval
-connectivity alone may not be important or reef resilience and recovery but should be
+connectivity alone may not be enough to support reef resilience and recovery but should be
 considered in combination with more influential factors such as depth.
@@
 the way larval flows and juvenile recruitment are implemented in ADRIA - CoralBlox.
-Additionally, and the high magnitude of early bleaching events (2025-2035) may decrease the
-breeding capacity of strongly connected reefs, resulting in reduced importance of
-connectivity in recovery. Analysing daily connectivity data Vogt-Vincent, Mitarai and
-Johnson [-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for
-capturing the seasonal - ecological time scale connectivity between locations due to high
-daily variability in connectivity data. Connectivity matrices used in this investigation
-have large relative standard deviations for larval transition probabilities between reefs
-over the 24 days used (@sfig-connectivity-rsd). Using alternative summarisation methods that
-capture ecological-timescale patterns in coral larval dispersal, such as cumulated implicit
-connectivity [@vogt-vincent2023], future investigations may find increased importance of
-both depth and reef connectivity for resilience, in line with other investigations
-[@hock2017; @torres2024]. Choukroun et al [-@choukroun2025] performed a comparison of three
-GBR-scale connectivity models, including GBR1, and suggest the use of a model ensemble
-approach to estimate larval dispersal due to the high sensitivity of connectivity
-predictions to model specification. Further improvements and research in connectivity
-modelling are necessary when incorporating connectivity as a supplementary factor in reef
-resilience and intervention-planning analyses.
+Additionally, and the high magnitude of early bleaching events (2025-2035) may increase the
+influence of temperature mediators (i.e. depth) in our simulations decrease the breeding
+capacity of strongly connected reefs, resulting in reduced importance of connectivity in
+recovery. Analysing daily connectivity data Vogt-Vincent, Mitarai and Johnson
+[-@vogt-vincent2023] suggest that time-mean connectivity may not be suitable for capturing
+the seasonal - ecological time scale connectivity between locations due to high daily
+variability in connectivity data. Connectivity matrices used in this investigation have
+large relative standard deviations for larval transition probabilities between reefs over
+the 24 days used (@sfig-connectivity-rsd). Using alternative summarisation methods that
+capture ecological-timescale patterns in coral larval dispersal in future investigations,
+such as cumulated implicit connectivity [@vogt-vincent2023], may find increased importance
+of both depth and reef connectivity for resilience, in line with other studies [@hock2017;
+@torres2024]. Choukroun et al [-@choukroun2025] performed a comparison of three GBR-scale
+connectivity models, including GBR1, and suggest the use of a model ensemble approach to
+estimate larval dispersal due to the high sensitivity of connectivity predictions to model
+specification. Further improvements and research in connectivity modelling are necessary
+when incorporating connectivity as a supplementary factor in reef resilience and
+intervention-planning analyses.
 
@@
 such as waves, cyclones, ocean currents and Crown of Thorns Starfish (CoTS) on coral colony
-survival and bleaching [@massel1993; @deaker2022].
+survival and bleaching [@emslie2024a; @emslie2024b].
 
@@
 adopted to align with other ongoing modelling and analyses conducted as part of the Reef
-Restoration and Adaptation Program (<https://gbrrestoration.org>; RRAP [-@thereef]).
+Restoration and Adaptation Program [<https://gbrrestoration.org>, @thereef].
 
@@
 The full reproducible investigation, and links to required data sources, can be found at
-Grier and Iwanaga ([-@grier2025]; https://doi.org/10.5281/zenodo.17333564).
+Grier and Iwanaga [-@grier2025, https://doi.org/10.5281/zenodo.17333564].
 

### 2025-10-20 paper/paper.qmd
Update Pedro's sensitivity analysis figure

@@
 
-![Parametric sensitivity analysis conducted with Shapley effects. Each column reflects
-sampling of different DHW ranges. The first column represents model runs with DHW = 0, and
-the remaining columns represent models runs with DHW valued between 0 and 8, 8 and 16, 16
-and 30, and 0 and 30. The first row shows the Shapley effect for change in coral cover and
-the second for change in evenness of species
-abundance.](../figs/coralblox_sens_analysis.png){#sfig-coralblox-sa fig-align="center"
+![Parametric sensitivity analysis conducted with Shapley effects.
+Each column reflects the sampling of different DHW ranges.
+The first column represents model runs with DHW = 0, and the remaining columns represent model runs with DHW valued between 0 and 30, 0 and 8, 8 and 16, 16 and 30.
+The first row shows the Shapley effect for relative changes in coral cover and the second for relative changes in evenness of species abundance.
+The five functional group names were abbreviated for readability as TA (tabular Acropora), CA (corymbose Acropora), CNA (corymbose non-Acropora), SM (small massives) and LM (large massives).](../figs/coralblox_sens_analysis.png){#sfig-coralblox-sa fig-align="center"
 width="14.82cm"}
